### 2017-05-03 papers/vph_2016/response_to_review.txt
The model as extracted from the abrg_local repository.

I'd like to thank the reviewer for their comments, which were
constructive and useful. I'll reply to the comments and indicate where
I have changed the manuscript below.

> Reviewer comments:

(Introduction)

> The introduction section depicts clearly the need of such a model.

(Materials & Methods)

> The second section presents a clear architecture of the platform
> components and the overall methodology. However, there is not a strong
> mathematical support of the algorithms used. The BRAHMS and SpineML
> could be just mentioned and not analysed as much, so that the gained
> space could be used for the mathematical background of the
> algorithms.

The description of BRAHMS and SpineML has been reduced. I've added the
equations governing the rate coded neural elements.

> More analysis should be performed regarding the connection
> of the Brain model and the muscular components, as it is there where
> the main novelty of the platform resides; thus, please explain
> thoroughly how the SC Map signal is converted into the 6
> time-dependent moto-neuron activation signals.

I have added additional detail to the description of the SC map -> SBG
conversion.

(Results)

> The results section contains a methodology portion regarding the
> model's training, so please consider of transferring it to the 2nd
> section.

This has been moved.

> Moreover, there is not any reference to the training data
> that were used, i.e. what exactly was the nature of the data input in
> the training process. Finally, a validation protocol of the simulated
> results is not mentioned at all, so please consider of adding any
> error metrics.

I have added a description of the data input for the training
process. I've not mentioned validation because the centroiding step,
ensures that only a single neural element drives the SC to SBG weight
maps and the range of inputs given ensures that every active element
in each weight map is trained.

> The reference section lacks of the titles of the journal papers and
> has to be revised.

I believe I have followed the short format for the bibliography, given
in the VPH2016 extended abstract template, which does not include
journal paper titles and so I have not made any changes here.

### 2017-05-03 papers/integration/abstract.tex
The model as extracted from the abrg_local repository.

% While writing, don't stop for errors
\nonstopmode

%%% This is based on the Frontiers template.
\documentclass{frontiersSCNS}

\usepackage{url,hyperref,lineno,microtype}
\usepackage[english]{babel}
\usepackage{amsmath}
\usepackage[onehalfspacing]{setspace}
\linenumbers

% Trick to define a language alias and permit language = {en} in the .bib file.
% From: http://tex.stackexchange.com/questions/199254/babel-define-language-synonym
\usepackage{letltxmacro}
\LetLtxMacro{\ORIGselectlanguage}{\selectlanguage}
\makeatletter
\DeclareRobustCommand{\selectlanguage}[1]{%
  \@ifundefined{alias@\string#1}
    {\ORIGselectlanguage{#1}}
    {\begingroup\edef\x{\endgroup
       \noexpand\ORIGselectlanguage{\@nameuse{alias@#1}}}\x}%
}
\newcommand{\definelanguagealias}[2]{%
  \@namedef{alias@#1}{#2}%
}
\makeatother
\definelanguagealias{en}{english}
\definelanguagealias{eng}{english}
% End language alias trick

\def\keyFont{\fontsize{8}{11}\helveticabold }
\def\firstAuthorLast{James {et~al.}}
\def\Authors{Sebastian James\,$^{1,2,*}$, Alexander Blenkinsop\,$^{1,2}$, \\
  Alexander Cope\,$^3$, Sean Anderson\,$^{2,4}$, Dimitrios Stanev\,$^5$, \\
  Chris Papapavlou\,$^5$, Konstantinos Moustakas\,$^5$, Kevin Gurney\,$^{1,2}$}
% Affiliations should be keyed to the author's name with superscript
% numbers and be listed as follows: Laboratory, Institute, Department,
% Organization, City, State abbreviation (USA, Canada, Australia), and
% Country (without detailed address information such as city zip codes
% or street names).
%
% If one of the authors has a change of address, list the new address
% below the correspondence details using a superscript symbol and use
% the same symbol to indicate the author in the author list.
\def\Address{\\
$^{1}$Adaptive Behaviour Research Group, Department of Psychology,
  The University of Sheffield, Sheffield, UK \\
$^{2}$Insigneo Institute for in-silico Medicine,
  The University of Sheffield, Sheffield, UK \\
$^{3}$Department of Computer Science,
  The University of Sheffield, Sheffield, UK \\
$^{4}$Department of Automatic Control Systems Engineering,
  The University of Sheffield, Sheffield, UK \\
$^{5}$Department of Computer Science,
  The University of Patras, Patras, Greece \\
}
% The Corresponding Author should be marked with an asterisk. Provide
% the exact contact address (this time including street name and city
% zip code) and email of the corresponding author
\def\corrAuthor{Kevin Gurney}
\def\corrAddress{Department of Psychology, The University of Sheffield,
  Western Bank, Sheffield, S10 2TP, UK}
\def\corrEmail{k.gurney@sheffield.ac.uk}

\begin{document}

% A place for aliases:
\input{sebcommands.tex}

\onecolumn
\firstpage{1}

\title[Integrated brain and biomechanics]{
  Integrating brain and biomechanical models - a new  paradigm
  for understanding  neuro-muscular control
}

\author[\firstAuthorLast ]{\Authors}
\address{}
\correspondance{}
\extraAuth{} % If more than 1 corr. author refer to original template
             % and fill this in

\maketitle
%% END PREAMBLE %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{abstract}
\section{}
To date, realistic models of how the central nervous system governs
behaviour have been restricted in scope to the brain, brainstem or
spinal column, as if these existed as disembodied organs.
Further, the model is often exercised in relation to an in vivo
physiological experiment with input comprising an impulse, a periodic
signal or constant activation, and output as a pattern of neural
activity in one or more neural populations. Any link to behaviour is
inferred only indirectly via these activity patterns.
%
We argue that to discover the principles of operation of neural
systems, it is necessary to express their behaviour in terms of
physical movements of a realistic motor system, and to supply inputs
that mimic sensory experience. To do this with confidence, we must
connect our brain models to neuro-muscular models and provide relevant
visual and proprioceptive feedback signals, thereby closing the loop
of the simulation.
%
This paper describes an effort to develop just such an integrated
brain and biomechanical system using a number of pre-existing
models. It describes a model of the saccadic oculomotor system
incorporating a neuromuscular model of the eye and its six extraocular
muscles. The position of the eye determines how illumination of a
retinotopic input population projects information about the location
of a saccade target into the system.
%
A pre-existing saccadic burst generator model was incorporated into
the system, which generated motoneuron activity patterns suitable for
driving the biomechanical eye. The model was demonstrated to make
accurate saccades to a target luminance under a set of environmental
constraints.
%
Challenges encountered in the development of this model showed the
importance of this integrated modelling approach. Thus, we exposed
shortcomings in individual model components which were only apparent
when these were supplied with the more plausible inputs available in a
closed loop design. Consequently we were able to suggest missing
functionality which the system would require to reproduce more
realistic behaviour.
%
The construction of such closed-loop animal models constitutes a new
paradigm of {\em computational neurobehaviour} and promises a more
thoroughgoing approach to our understanding of the brain's function as
a controller for movement and behaviour.

\tiny
 \keyFont{
   \section{Keywords:}
   integrated brain biomechanics neuromuscular oculomotor saccade basal ganglia
 } % 5 to 8 keywords
\end{abstract}

\end{document}

### 2017-05-03 papers/integration/omm_integ.tex
The model as extracted from the abrg_local repository.

% While writing, don't stop for errors
\nonstopmode

%%% This is based on the Frontiers template.
\documentclass{frontiersSCNS}

\usepackage{url,hyperref,lineno,microtype}
\usepackage[english]{babel}
\usepackage{amsmath}
\usepackage[onehalfspacing]{setspace}
\linenumbers

% Trick to define a language alias and permit language = {en} in the .bib file.
% From: http://tex.stackexchange.com/questions/199254/babel-define-language-synonym
\usepackage{letltxmacro}
\LetLtxMacro{\ORIGselectlanguage}{\selectlanguage}
\makeatletter
\DeclareRobustCommand{\selectlanguage}[1]{%
  \@ifundefined{alias@\string#1}
    {\ORIGselectlanguage{#1}}
    {\begingroup\edef\x{\endgroup
       \noexpand\ORIGselectlanguage{\@nameuse{alias@#1}}}\x}%
}
\newcommand{\definelanguagealias}[2]{%
  \@namedef{alias@#1}{#2}%
}
\makeatother
\definelanguagealias{en}{english}
\definelanguagealias{eng}{english}
% End language alias trick

\def\keyFont{\fontsize{8}{11}\helveticabold }
\def\firstAuthorLast{James {et~al.}}
\def\Authors{Sebastian James\,$^{1,2,*}$, Alexander Blenkinsop\,$^{1,2}$, \\
  Alexander Cope\,$^3$, Sean Anderson\,$^{2,4}$, Dimitrios Stanev\,$^5$, \\
  Chris Papapavlou\,$^5$, Konstantinos Moustakas\,$^5$, Kevin Gurney\,$^{1,2}$}
% Affiliations should be keyed to the author's name with superscript
% numbers and be listed as follows: Laboratory, Institute, Department,
% Organization, City, State abbreviation (USA, Canada, Australia), and
% Country (without detailed address information such as city zip codes
% or street names).
%
% If one of the authors has a change of address, list the new address
% below the correspondence details using a superscript symbol and use
% the same symbol to indicate the author in the author list.
\def\Address{\\
$^{1}$Adaptive Behaviour Research Group, Department of Psychology,
  The University of Sheffield, Sheffield, UK \\
$^{2}$Insigneo Institute for in-silico Medicine,
  The University of Sheffield, Sheffield, UK \\
$^{3}$Department of Computer Science,
  The University of Sheffield, Sheffield, UK \\
$^{4}$Department of Automatic Control Systems Engineering,
  The University of Sheffield, Sheffield, UK \\
$^{5}$Department of Computer Science,
  The University of Patras, Patras, Greece \\
}
% The Corresponding Author should be marked with an asterisk. Provide
% the exact contact address (this time including street name and city
% zip code) and email of the corresponding author
\def\corrAuthor{Kevin Gurney}
\def\corrAddress{Department of Psychology, The University of Sheffield,
  Western Bank, Sheffield, S10 2TP, UK}
\def\corrEmail{k.gurney@sheffield.ac.uk}

\begin{document}

% A place for aliases:
\input{sebcommands.tex}

\onecolumn
\firstpage{1}

\title[Integrated brain and biomechanics]{
  Integrating brain and biomechanical models - a paradigm shift
  towards neuro-muscular control
}

\author[\firstAuthorLast ]{\Authors}
\address{}
\correspondance{}
\extraAuth{} % If more than 1 corr. author refer to original template
             % and fill this in

\maketitle

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% The sections below are for reference only.
%%%
%%% For Original Research Articles, Clinical Trial Articles, and
%%% Technology Reports the section headings should be those
%%% appropriate for your field and the research itself. It is
%%% recommended to organize your manuscript in the following sections
%%% or their equivalents for your field:
%%%
%%% Abstract, Introduction, Material and Methods, Results, and Discussion.
%%%
%%% Please note that the Material and Methods section can be placed in
%%% any of the following ways: before Results, before Discussion or
%%% after Discussion.
%%%
%%% For information about Clinical Trial Registration, please go to
%%% http://www.frontiersin.org/about/AuthorGuidelines#ClinicalTrialRegistration
%%%
%%% For Clinical Case Studies the following sections are mandatory:
%%% Abstract, Introduction, Background, Discussion, and Concluding
%%% Remarks.
%%%
%%% For all other article types there are no mandatory sections.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{abstract}
\section{}
To date, realistic models of how the central nervous system governs
behaviour have been restricted in scope to the brain, brainstem or
spinal column, as if these existed as disembodied organs.
Further, the model is often exercised in relation to an in vivo
physiological experiment with input comprising an impulse, a periodic
signal or constant activation, and output as a pattern of neural
activity in one or more neural populations. Any link to behaviour is
inferred only indirectly via these activity patterns.
%
We argue that to discover the principles of operation of neural
systems, it is necessary to express their behaviour in terms of
physical movements of a realistic motor system, and to supply inputs
that mimic sensory experience. To do this with confidence, we must
connect our brain models to neuro-muscular models and provide relevant
visual and proprioceptive feedback signals, thereby closing the loop
of the simulation.
%
This paper describes an effort to develop just such an integrated
brain and biomechanical system using a number of pre-existing
models. It describes a model of the saccadic oculomotor system
incorporating a neuromuscular model of the eye and its six extraocular
muscles. The position of the eye determines how illumination of a
retinotopic input population projects information about the location
of a saccade target into the system.
%
A pre-existing saccadic burst generator model was incorporated into
the system, which generated motoneuron activity patterns suitable for
driving the biomechanical eye. The model was demonstrated to make
accurate saccades to a target luminance under a set of environmental
constraints.
%
Challenges encountered in the development of this model showed the
importance of this integrated modelling approach. Thus, we exposed
shortcomings in individual model components which were only apparent
when these were supplied with the more plausible inputs available in a
closed loop design. Consequently we were able to suggest missing
functionality which the system would require to reproduce more
realistic behaviour.
%
The construction of such closed-loop animal models constitutes a new
paradigm of {\em computational neurobehaviour} and promises a more
thoroughgoing approach to our understanding of the brain's function as
a controller for movement and behaviour.

\tiny
 \keyFont{
   \section{Keywords:}
   integrated brain biomechanics neuromuscular oculomotor saccade basal ganglia
 } % 5 to 8 keywords
\end{abstract}

\section{Introduction}

% New introduction, tailored to the paradigm shift title.
(New Introduction:)

The field of computational neuroscience has provided
many \emph{systems models} of the brain~\cite{several_models}. We
refer to these as \emph{mechanistic computational models}, meaning
models which consist of populations of neural elements, interconnected
in a biologically plausible manner, which simulate the operation of
the brain.

Whilst they differ in scale and complexity, these models all seek to
describe the fundamental mechanisms behind common animal behaviours
such as locomotion, threat evasion, reaching or feeding. However,
almost none of the models cited here actually reproduce these
behaviours. In each case, the activity in a certain population of
neurons is taken to be representative of a behavioural outcome.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
(Old introduction, which became the VPH mini-paper intro:)
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% Can make comparisons
As mechanistic computational models of brain systems become more
sophisticated we can aspire to make realistic comparisons between the
behaviour of the model and that of the animal or human.

% Short desc of mechanistic computational model
By \emph{mechanistic computational model}, we mean a model which
consists of populations of neural elements, interconnected in a
biologically plausible manner. Such a model may consist of neural
elements that produce a time-dependent membrane voltage and realistic
spiking behaviour (Hodgkin-Huxley, Fizhugh-Nagumo, Izhikevich, Leaky
integrate and fire) in which case the neural element's activity can be
obtained by counting action potentials (or considering their
timing). Alternatively it may (as it does in this work) consist of
rate-coded neural elements, whose activation variable is related to
the spiking rate of a number of neurons (refs).

% Sometimes, ok to just have a brain model
In some cases, it is sufficient to take the activity of an internal
population within the brain model as being representative of the
induced behaviour. For example, a choice made in a \e{go/no-go} task
could be determined from activity in a population within a Basal
Ganglia model
(\mycite{nambu_discharge_1990,kuhn_event-related_2004}). The decision
to \e{go} is selected by a reduction of activity in this population;
maintenance of activity implies \e{no-go}. Error rates in this task
could be compared with experimentally determined error rates in
primate subjects.
% Brain model comparison validates model
If the expression of behaviour by the model is similar when compared
with the experimental data, this serves to validate the model for the
healthy, neuro-typical subject.
% Now describe comparison between model and expt. for diseased
% subject.
If we have confidence in the model's description of the behaviour for
the healthy subject, we can now progress to a comparison between the
model and an unhealthy subject. If we can identify a characteristic
degradation in an aspect of the brain for an unhealthy subject, then
we can seek to modify the model to mirror this degradation. By
comparing the relationship between the model's behaviour as a function
of the degradation parameter with the unhealthy individual's behaviour
as a function of disease progression, we may be able to relate the
disease progression state to the brain parameter and predict the
time-course of the internal degradation of the brain.
% Leave further discussion along these lines to the discussion
% section.

% But sometimes you might need brain and neuromuscular model
Many behaviours are more complex and subtle than a decision. In the
disease state, it may be the dynamics of the movement which is
symptomatic rather than its outcome. A diagnostic task may produce an
outcome whose error rate varies with disease state, but it may also
produce movement characteristics which correlate with the disease
progression such as the slow, jerky or inaccurate movements seen in
Parkinson's Disease. In order to determine the validity of a model
which seeks to describe more complex movements, it is necessary to
express the movement commanded by the brain network as a realistic,
simulated motion by means of a biomechanical model, driven by the
brain model.

% Motivation here is to study movement disorders by means of a
% comparison between healthy subjects, the healthy model and diseased
% subjects and the diseased model.
Our motivation is to study movement disorders using our brain
models. Because the challenge of integrating brain and biomechanical
models has not, to our knowledge, previously been addressed, we chose
to express some of the simplest, and most studied movements made by
vertebrates: the rapid eye movements known as saccades. Saccades
direct the fovea, the region of the eye with the highest spatial
imaging resolution, towards putative targets of interest. Mammals make
frequent saccades; many thousands every day. These movements are often
described as ballistic: They are commanded by activity in the superior
colliculus which encodes an endpoint for the saccade trajectory
(\mycite{wurtz_superior_1971,hepp_monkey_1993}); once initiated, the
saccade proceeds in a relatively direct and stereotyped (though not
always straight) trajectory (\mycite{van_der_stigchel_eye_2006}) to
the endpoint.
% Why am I mentioning curved saccades? Because it shows that saccades
% can exhibit rich behaviour and that modelling them is worthwhile.
However, numerous studies have shown that saccade trajectories are
affected by distractors (\mycite{mcpeek_competition_2003,
port_sequential_2003, van_der_stigchel_recent_2010}) and may be
modified in-flight to the extent that saccades may be seen to perform
significant, sometimes even U-shaped, curves towards or away from
distractors. This shows that whilst saccades are simple compared to
the movements of limbs, they still provide information about a number
of mechanisms within the brain and an effort to model them accurately
is worthwhile.

% Say what we've done here, in short form.
Parkinson's Disease is a progressive neurological disorder whose main
symptoms relate to motor control. These include resting tremor,
slowness of movements (bradykinesia), difficulty in initiating
movement (akinesia) and rigidity (refs). It is considered to be a
disease of the basal ganglia because during its progression, dopamine
producing neurons in the substantia nigra pars compacta die away
(ref), affecting the the striatum which depends on endogenous dopamine
for correct operation (ref). The basal ganglia plays an important role
in decision making and action selection (ref), including the selection
of saccadic eye movements (\mycite{hikosaka_role_2000}). In the later
stages of Parkinson's Disease, patients show more latent saccades to
targets of interest (ref). They have also been documented as showing
poorer performance in the so-called anti-saccade protocol, in which
the subject is instructed to make a saccade \e{away} from a visual
target. Parkinson's Disease patients make significantly more errors;
they will saccade \e{to} the visual target rather than \e{away} from
it more often than healthy control subjects. To investigate the way in
which degradation in the basal ganglia may be causing these defects we
have developed an integrated brain and biomechanical eye model which
we describe here. The model will initially be used to investigate the
deterioration in anti-saccadic movements which is detectable even in
relatively early-stage Parkinson's Disease.

%See \mycite{Rottach_dynamic_1996} for trajectory information in saccades.

%% End of intro here? Or carry on with a description of the physiology
%% of saccadic eye movements?

Many neural populations are involved in the coding of saccadic eye
movements, only a very brief overview is given here; for a recent
review, see \mycite{munoz_commentary:_2002}. One pathway takes
information from the retina directly into the superficial layers of
the superior colliculus in the brainstem (\mycite{?}). Activity within
the superior colliculus then excites neurons in the pons, medulla and
rostral midbrain (\mycite{sparks_brainstem_2002}) and then through
channels to the motor neurons which innervate the extraocular muscles
(\mycite{fuchs_firing_1970,sparks_brainstem_2002}). This direct pathway
is responsible for the low latency saccades called express saccades
(\mycite{?}).

% FEF: \mycite{schall_neural_1999}
Information from the retina is also processed by visual cortex which
feeds through to the frontal eye fields in which activity is related
to reflexive and voluntary
saccades \mycite{schall_neural_1999}. Activity build up in the frontal
eye fields is transferred to the intermediate layers of the superior
colliculus
\mycite{?} and is also processed by the basal ganglia, which
participates in the selection of the winning saccade end point
\mycite{?}.

% On fact that SC doesn't encode oblique/torsional movements:
% \cite{hepp_monkey_1993}

% That means that you need both the expression of movement, and also a
% means by which you can progress the disease in the model.

%If such comparisons are to be made, then the behavioural output of the
%model should be in the form of movements which can be directly
%compared with the biological system. In order to express movements,
%the brain model needs to drive biomechanical neuromuscular models.

%\begin{methods}
\section{Material \& Methods}

% A very short introduction to the section.
The integrated brain and biomechanical model described here is a
development of the model in \mycite{alex_cope_integrative_2015},
referred to here as the \ccg~model. This was a rate-coded neural
network model incorporating retinal populations, frontal eye fields
(FEF), the basal ganglia (BG), and the superior colliculus (SC). In
the \ccg~model, the ``centre of mass'' of the activity in the deep
layers of superior colliculus was assumed to accurately encode the
location of the eye at the end of the saccade~\cite{someone}. This
location was used to recalculate the positions of the luminances in
the eye's frame of reference at each time step. The model included no
brainstem populations other than superior colliculus, nor a
neuromuscular model.

To the \ccg~model, we have added a brainstem model (a ``saccadic burst
generator''), and a biomechanical eye. These will be described below,
but first we will give an explanation of the modelling framework used.

% Section - description of how the model fits together - which
% components it's made from.
\subsection{Model development framework}

% Say the \ccg~model was implemented in matlab-brahms & this one is SpineML.
The \ccg~model was originally developed to run on the BRAHMS model
execution framework
(\mycite{mitchinson_brahms:_2010,mitchinson_brahms_2015}). To run a
BRAHMS model, the researcher must develop \e{BRAHMS components} for
the various neural elements. A BRAHMS component is a programmatically
coded implementation of the behaviour of the component. It may have an
arbitrary number of inputs and outputs and may be written in C, C++,
Python or MATLAB. The \ccg~model's components were hand written in C++
and MATLAB. A BRAHMS \e{SystemML} file describes how the different
components connect together and how data is passed between them
(\mycite{mitchinson_brahms:_2010}). The main BRAHMS program first
reads the SystemML file, then dynamically loads all the required
components before executing the system.

In the current work, the \ccg~model was reproduced using the
declarative SpineML markup language (\mycite{richmond_model_2014}),
with the help of the graphical SpineML model editing software
called SpineCreator
(\mycite{cope_spinecreator:_2016}). SpineML,
which is a development of the NineML specification
(\mycite{incf_task_force_on_multi-scale_modeling_network_2011}),
describes neural populations and their projections in a highly
structured format in which neuron bodies, pre- and post-synapses are
described in terms of \e{SpineML components}. These are similar to the
components provided by BRAHMS, but in this case, the components are an
XML description of the functionality of the component, rather than a
programmatic implementation, with one XML file per component. A
SpineML \e{network layer} file then describes which components are
used in the model, and how they are connected together. Finally, a
number of SpineML \e{experiment layer} files describe how the model
described in the network layer can be executed. In the experiment
layer, the execution duration and timestep can be specified, along
with input conditions, connection lesions and component parameter
updates. A complete description of SpineML is given
in \mycite{richmond_model_2014}.

SpineCreator, in its r\^ole as a graphical editor for the SpineML
format, was used to generate the SpineML files describing the
model. It was also used to generate the diagrams of the model
(e.g. Fig.~\ref{brain_model}).

As a declarative format for model specification, SpineML is agnostic
about how the model is executed. A number of SpineML simulation
engines exist, including DAMSON (\mycite{richmond_damson_2015}), GeNN
(\mycite{nowotny_flexible_2011,nowotny_spineml_2014}) and BRAHMS (used
here). The simulation engine for BRAHMS is called \stob~
(\mycite{cope_spineml_2_brahms_2015-1}). \stob~is a collection of XSLT
stylesheets which first generate and compile C++ BRAHMS components
from the SpineML component layer description files. \stob~then uses
the SpineML network and experiment layer files to generate a BRAHMS
SystemML description of the model. Finally, \stob~executes the model,
now described entirely as a BRAHMS system, via a call to the BRAHMS
binary. A number of additional hand-written components are present
in \stob~providing the inputs (constant inputs, time-varying inputs,
etc) which the modeller specifies in the experiment layer.

In addition to the brain model components, all of which are
code-generated using \stob~as described above, three hand-written
components are integrated into the model: The biomechanical eye model;
a component which computes the centroid of a neural layer; and a
component which takes as inputs the eye's rotational state and the
state of the experimental luminances and projects a retinotopic
activity map into the brain model. Each of these three BRAHMS
components was hand written in C++. To incorporate these components
into the present integrated model, a model-specific modification was
made to the scripts in \stob~(\mycite{cope_spineml_2_brahms_2015}).

Figure \ref{model_framework} shows the workflow, in which the model
specification files (blue box), a combination of SpineML files and C++
code, are processed (green box) into a BRAHMS system (red box).

\subsection{Existing brain model}

The brain model, excluding the brainstem, is a re-implementation of
the \ccg~model. Figure \ref{brain_model} shows the layout of the
populations and the interconnections between them. Each population of
2500 elements is arranged as a 50 by 50 grid which forms a map in a
retinotopic co-ordinate system, roughly matching the known layout of
the superior colliculus (SC). % FIXME: and frontal eye field?

\subsubsection{Components}

(\mycite{robinson_eye_1972}). With the exceptions of the World and
FEF\_add\_noise populations, each neural element represents an
activation whose dynamics depend on the component definition. In the
brain model, there are six different components in use; LINlinear,
LINlinearNoisy, LINret, LINexp, D1MSN and D2MSN.

The LINlinear component governs the activation $a$ with a first order
leaky integrator differential equation:
\[
   \dot{a} = {1 \over \tau}(a_{in}-a)
\]
where $\tau$ is the time constant for the neural activation and
$a_{in}$ is the input to the neural element. $a_{in}$ is defined by an
activation input and a shunting inhibition input according to:
\[
   a_{in} = A(1-s_a)+0.01 R_N
\]
Here, $A$ is the activation input and $s_a$ is the shunting inhibition
state variable whose value is related to the shunting input, $S$ by
\[
   s_a = \begin{cases}
      S & S\leq 1 \\
      1 & S > 1
   \end{cases}
\]
$R_N$ is a random number between 0 and 1 drawn from a
normal distribution and introduces noise to the activation of the
neural element.

The output, $y$, of LINlinear is related to the activation by the
piecewise linear transfer function
\[
   y(a) = \begin{cases}
      0   & a < c \\
      a-c & c \leq a \leq 1+c \\
      1   & a > 1+c
   \end{cases}
\]
where $c$ is a parameter defining the slope of the transfer
function. At this point, the naming scheme for the component becomes
apparent; this is a Leaky Integrator with a linear transfer function.

LINlinearNoisy is identical to LINlinear with the single exception
that the level of noise is increased. This means that the equation for
$a_{in}$ must be rewritten:
\[
   a_{in} = A(1-s_a)+0.2 R_N
\]
The LINret component used for the retinal populations is again similar
to the LINlinear component, but with no intrinsic noise and no
shunting inhibitory input. It has a neural input which is identical to
the activation input $A$:
\[
   a_{in} = A
\]
The LINexp component is a leaky integrator with an exponential
transfer function. It shares the same differential equation with
LINlinear, but has a different input equation and a different output
transfer function. It has the following equation for the neural
element input $a_{in}$:
\[
   a_{in} = [A+N(a-V_{r}^{-})] (1-S) + 0.01 R_N
\]
where $A$ is the activation input and $N$ is an input which is
modulated by $V_{r}^{-}$, a reversal potential, and $a$, the current
activation of the element. These inputs are summed and then reduced by
a factor which is dependent on $S$, the shunting input. As in
LINlinear, $R_N$ introduces normally distributed noise to the element.

The output, $y$, of the LINexp component is given by
\[
   y(a) = \begin{cases}
      \mathrm{e}^{a}-0.9   & \mathrm{e}^a \leq 1+0.9 \\
      1   & \mathrm{e}^a > 1+0.9
   \end{cases}
\]
This component is used in the STN population, as it gives a more
physiologically accurate f-I
behaviour \mycite{wilson_model_2004,bevan_mechanisms_1999,hallworth_apamin-sensitive_2003}
which has been shown to allow the mapping of the basal ganglia network
architecture onto an optimal decision making
model \mycite{bogacz_basal_2007}.

%
% That's the components described. Next up is to have a figure of the
% activity for representative input to the model.
%

\subsubsection{Population activity}

Each population of 2500 neural elements is arranged in a 50 by 50
grid, with positions on the grid representing a retinotopic
mapping. Locations on the grid specify radial and azimuthal angles r
and $\phi$ for the location of activity on the retina relative to the
fovea. r and $\phi$ can be converted into rotations about the $x$ and
$y$ Cartesian axes ($\theta_x$ and $\theta_y$). The result of a
positive rotation about the $x$ axis in a right-handed Cartesian
coordinate system results in an "upward movement" of the fovea's view
of the environment. Note that a positive rotation about the $y$ axis
results in a "leftward movement".

The magnification factor, $M_f$, gives the relationship between the
radial angle r and the retinal neural density. It is given by:
\[
   M_f = {W_{nfs} \over E_2 ln ({W_{fov} \over 2 E_2} + 1)}
\]
where $W_{nfs}$ is the width of the retinotopic neural fields (50),
$W_{fov}$ is the eye's field of view, which is set to 61 degrees, a
reduction from the biophysically accurate 150 degrees due to the small
number of neurons in the retinotopic neural field. $E_2$ is the
eccentricity (in degrees) at which the retinal neural density has
halved compared with the foveal region.

With $M_f$ calculated, the mapping from the retinotopic radial and
angular components, $r$ and $\phi$ to $\theta_x$ and $\theta_y$ is:
\[
   \theta_x = E_2 (e^{{r \over M_f E_2}} - 1).\cos({2 \pi \phi \over
   W_{nfs}}) \tag{1}
\]
\[
   \theta_y = E_2 (e^{{r \over M_f E_2}} - 1).\sin({2 \pi \phi \over W_{nfs}}) \tag{2}
\]

It is straightforward to show that the reverse mapping is given by:
\[
   \phi = {W_{nfs} \over 2 \pi}\arctan({\theta_y\over\theta_x}) \tag{3}
\]
\[
   r = M_f E_2 \ln ({1\over E_2}\sqrt{{\theta_x}^2 + {\theta_y}^2}+1) \tag{4}
\]

Figure \ref{mapping} shows the result of the mapping for a view of two
cross-shaped luminances. One cross illuminates the fovea, which
results in a large comb-shape of activity. The more peripheral cross
produces an indistinct object centered at a larger value of r.

It is important to note that in practice there are edge effects within
the model which prevent this theoretical mapping from holding
perfectly. The most significant of these is the result of the diffuse
excitation from STN to GPe... etc % FIXME Where are the edge effects
                                  % most prevalent? In BG I think

\subsubsection{Network}

Briefly, the model consists of input from the World population
producing activity in an ``express'' pathway to superior colliculus
and simultaneously in cortex, represented here by the FEF
population. The express pathway causes short latency activity in the
superficial superior colliculus, which directly innervates the deeper
layers of the superior colliculus (SC\_deep). Activity in FEF
generates firing in a thalamo-cortico-basal ganglia loop. The output
of the basal ganglia is the substantia nigra pars reticulata (SNr)
which tonically inhibits SC\_deep. If a location of activity in FEF is
able to dominate selection in the basal ganglia circuit, the
corresponding location in SNr will dis-inhibit and activity will build
up in SC\_deep encoding the saccade end point.

Connections shown in red are one to one connections; dark blue
connections indicate a connectivity pattern which ``fans out'' with a 2-D
Gaussian kernel; lighter blue connections from STN to SNr and GPe are
diffuse, all to all connections and connections in green are one to one
connections that decay towards the fovea so that foveal activity in
FEF does not swamp the basal ganglia which would prevent peripheral
luminances from being selected.

Note that SC\_deep contains two recurrent connections; one is
excitatory, with a Gaussian kernel mapping and the other implements
tecto-tectal inhibition, which increases the inhibition between
activity in opposite hemispheres of the field of view (refs). The
tecto-tectal inhibitory connection is \em{not} present in the \ccg
model.

%However, it does not describe deeper, motor regions of the
%brainstem, instead regarding the centroid of the activity in SC as
%being representative of the end point of the saccade
%trajectory \mycite{mays_dissociation_1980,lee_population_1988,van_Opstal_role_1990}.

% Section - description of new brainstem model
\subsection{brainstem model}

Neurons in the deep layers of the superior colliculus called long lead
burst neurons innervate excitatory burst neurons in the reticular
formation (ref). In this model, we implement a network based
on \mycite{gancarz_neural_1998}.

% Section - description of biomechanical model
\subsection{biomechanical eye}

Patras work here.

% Section - description of the integration
\subsection{Integrating the models}

%\end{methods}

\section{Results}

% trajectories, neuron activations (esp. brainstem). latency vs
% dopamine, latency vs gap.

\section{Discussion}

% Be sure to say that ``in future work, it will be possible to
% investigate saccade trajectory modifications in Parkinson's''

\subsection{Subsections}

% Frontiers requires figures to be submitted individually, in the same
% order as they are referred to in the manuscript. Figures will then
% be automatically embedded at the bottom of the submitted
% manuscript. Kindly ensure that each table and figure is mentioned in
% the text and in numerical order. Permission must be obtained for use
% of copyrighted material from other sources (including the
% web). Please note that it is compulsory to follow figure
% instructions. Figures which are not according to the guidelines will
% cause substantial delay during the production process.

% To take part in the Resource Identification Initiative, please cite
% antibodies, genetically modified organisms, software tools, data,
% databases and services using the corresponding catalog number and
% RRID in your current manuscript. For more information about the
% project and for steps on how to search for an RRID, please click
% \href{http://www.frontiersin.org/files/pdf/letter_to_author.pdf}.

% Equations:
%\begin{equation}
%\sum x+ y =Z\label{eq:01}
%\end{equation}

\section*{Disclosure/Conflict-of-Interest Statement}

The authors declare that the research was conducted in the absence of
any commercial or financial relationships that could be construed as a
potential conflict of interest.

\section*{Author Contributions}
%When determining authorship the following criteria should be observed:
%•	Substantial contributions to the conception or design of the work; or the acquisition, analysis, or interpretation of data for the work; AND
%•	Drafting the work or revising it critically for important intellectual content; AND
%•	Final approval of the version to be published ; AND
%•	Agreement to be accountable for all aspects of the work in ensuring that questions related to the accuracy or integrity of any part of the work are appropriately investigated and resolved.
%Contributors who meet fewer than all 4 of the above criteria for authorship should not be listed as authors, but they should be acknowledged. (http://www.icmje.org/roles_a.html)

SJ, AB and AC implemented existing parts of the model in SpineML. AB
developed the saccade generator brainstem model. SJ performed the
technical integration of the biomechanical eye. DS, CP and KM
developed the biomechanical eye model. SJ wrote the manuscript. KG
conceived the experiment. % FIXME: This needs correcting/developing.

\section*{Acknowledgments}

\textit{Funding\textcolon} European Union FP7 Grant 610391 ``NoTremor''.

\section*{Supplemental Data}

Models available on github - include details of branches, commits etc
for running the model.

\selectlanguage{English}
\bibliographystyle{frontiersinSCNS_ENG_HUMS}
% The bibliography NoTremor.bib is the one exported from Zotero.
\bibliography{NoTremor}

%%% Upload the *bib file along with the *tex file and PDF on
%%% submission if the bibliography is not in the main *tex file

\section*{Figures}

%%% Use this if adding the figures directly in the mansucript, if so,
%%% please remember to also upload the files when submitting your
%%% article There is no need for adding the file termination, as long
%%% as you indicate where the file is saved. In the examples below the
%%% files (logo1.jpg and logo2.eps) are in the Frontiers LaTeX folder
%%% If using *.tif files convert them to .jpg or .png

%\begin{figure}[h!]
%\begin{center}
%\includegraphics[width=10cm]{logo1.jpg}% This is a *.jpg file
%\end{center}
% \textbf{\refstepcounter{figure}\label{fig:01} Figure \arabic{figure}.}{ Enter the caption for your figure here.  Repeat as  necessary for each of your figures }
%\end{figure}

%\begin{figure}
%\begin{center}
%\includegraphics[width=10cm]{logo2}% This is an *.eps file
%\end{center}
%\textbf{\refstepcounter{figure}\label{fig:02} Figure \arabic{figure}.}{ Enter the caption for your figure here.  Repeat as  necessary for each of your figures }
%\end{figure}

%%% If you don't add the figures in the LaTeX files, please upload
%%% them when submitting the article.

%%% Frontiers will add the figures at the end of the provisional pdf
%%% automatically

%%% The use of LaTeX coding to draw Diagrams/Figures/Structures should
%%% be avoided. They should be external callouts including graphics.

\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.9\textwidth]{./figures/intro_graphic.png}
\end{center}
\textbf{\refstepcounter{figure}\label{intro_graphic} Figure \arabic{figure}.}
{ An isolated brain model. Crafted inputs are introduced into one of
the model's n state variables. The output of another of the state
variables implies behavioural change or onset.}
\end{figure}

\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.9\textwidth]{./figures/model_framework.png}
\end{center}
\textbf{\refstepcounter{figure}\label{model_framework} Figure \arabic{figure}.}
{ The model framework. The model is specified using a combination of
declarative XML files and hand-coded C++. These original model
specifications are shown within the blue box. b) The green box shows
the processes which are applied to the model specification to produce
the BRAHMS system. Most of the process is defined within the scripts
which make up \stob, but the three hand-written components must be
manually compiled and installed within the BRAHMS Namespace, allowing
the BRAHMS executable to locate them at runtime. c) The red box shows
the resulting BRAHMS system ready to be executed by the BRAHMS
executable. In practice, this call is made by \stob.}
\end{figure}

\begin{figure}[htb!]
\begin{center}
\includegraphics[width=0.9\textwidth]{./figures/mapping.png}
\end{center}
\textbf{\refstepcounter{figure}\label{mapping} Figure \arabic{figure}.}
{ Representative mapping from eye's frame of reference in cartesian
coordinates to retinotopic coordinates. (a) The mapping of luminances
in the eye's frame of reference. The world input is pre-defined by a
JSON configuration file. luminance position, size and shape can be
defined in this file, along with the times at which luminances appear
and disappear. The worldDataMaker.cpp code computes the locations of
the luminances in the eye's frame of reference, given its rotational
state. Here, there are two cross shaped luminances, one at the
fixation point (0,0) and one at a peripheral position (4,-10). (b) The
locations of the luminances in the eye's frame of reference are then
converted into retinotopic coordinates, with centrally located
luminances being represented at low values of $r$ and more peripheral
luminances having higher values of $r$. $phi$ encodes rotational
angle: 12.5 is up, [etc etc]. The output of the World component is fed
into FEF\_add\_noise and into the retinal neuron populations. (c) The
FEF\_add\_noise populations adds a level of noise to the signal
representing processing of the signal in visual cortex. (d) The
activity in FEF is the input to the basal ganglia and one input to
superior collicus.}
\end{figure}

\begin{figure}[htb!]
\begin{center}
\includegraphics[width=0.9\textwidth]{./figures/Brain_Model.png}
\end{center}
\textbf{\refstepcounter{figure}\label{brain_model} Figure \arabic{figure}.}
{ This is the Brain Model}
\end{figure}

\end{document}

### 2017-05-03 papers/vph_2016/abstract.tex
The model as extracted from the abrg_local repository.

%
% This is the VPH 2016 mini paper.
%
% It's an example of using latex for a paper of specified size/layout.
%

% While writing, don't stop for errors
\nonstopmode

% Use the article doc class, with an 11 pt basic font size
\documentclass[11pt, a4paper]{article}

% Makes the main font Nimbus Roman, a Times New Roman lookalike:
%\usepackage{mathptmx}% http://ctan.org/pkg/mathptmx
% OR use this for proper Times New Roman (from msttcorefonts package
% on Ubuntu). Use xelatex instead of pdflatex to compile:
\usepackage{fontspec}
\usepackage{xltxtra}
\usepackage{xunicode}
\defaultfontfeatures{Scale=MatchLowercase,Mapping=tex-text}
\setmainfont{Times New Roman}

% Set margins to match VPH layout
\usepackage[margin=2.5cm]{geometry}

% Multilingual support
\usepackage[english]{babel}

% Nice mathematics
\usepackage{amsmath}

% Control over maketitle
\usepackage{titling}

% Section styling
\usepackage{titlesec}

% Ability to use colour in text
\usepackage[usenames]{color}

% For the \degree symbol
\usepackage{gensymb}

% Allow includegraphics and nice wrapped figures
\usepackage{graphicx}
\usepackage{wrapfig}
\usepackage[outercaption]{sidecap}

% Set formats using titlesec
\titleformat*{\section}{\bfseries\rmfamily}
\titleformat*{\subsection}{\bfseries\itshape\rmfamily}

% thetitle is the number of the section. This sets the distance from
% the number to the section text.
\titlelabel{\thetitle.\hskip0.3em\relax}

% Set title spacing with titlesec, too.  The first {1.0ex plus .2ex
% minus .7ex} sets the spacing above the section title. The second
% {-1.0ex plus 0.2ex} sets the spacing the section title to the
% paragraph.
\titlespacing{\section}{0pc}{1.0ex plus .2ex minus .7ex}{-1.1ex plus 0.2ex}

%% Trick to define a language alias and permit language = {en} in the .bib file.
% From: http://tex.stackexchange.com/questions/199254/babel-define-language-synonym
\usepackage{letltxmacro}
\LetLtxMacro{\ORIGselectlanguage}{\selectlanguage}
\makeatletter
\DeclareRobustCommand{\selectlanguage}[1]{%
  \@ifundefined{alias@\string#1}
    {\ORIGselectlanguage{#1}}
    {\begingroup\edef\x{\endgroup
       \noexpand\ORIGselectlanguage{\@nameuse{alias@#1}}}\x}%
}
\newcommand{\definelanguagealias}[2]{%
  \@namedef{alias@#1}{#2}%
}
\makeatother
\definelanguagealias{en}{english}
\definelanguagealias{eng}{english}
%% End language alias trick

%% Some aliases
\newcommand{\ccg}{Cope-Chambers-Prescott-Gurney}
\newcommand{\brain}{brain}
\newcommand{\stob}{S2B}
% Emphasis and bold.
\newcommand{\e}{\emph}
\newcommand{\mycite}[1]{\cite{#1}}
%% END aliases

% VPH font defs
% fontsize is \fontsize{fontsize}{linespacesize}
\def\authorListFont{\fontsize{11}{11} }
\def\corrAuthorFont{\fontsize{10}{10} }
\def\affiliationListFont{\fontsize{11}{11}\itshape }
\def\titleFont{\fontsize{14}{11} \bfseries }
\def\textFont{\fontsize{11}{11} }
\def\sectionHdrFont{\fontsize{11}{11}\bfseries}
\def\bibFont{\fontsize{10}{10} }
\def\captionFont{\fontsize{10}{10} }

% Caption font size to be small.
\usepackage[font=small,labelfont=bf]{caption}

\def\firstAuthorLast{James {et~al.}}

% Affiliations
\def\Address{\\
\affiliationListFont 1 Adaptive Behaviour Research Group, Department of Psychology,
  The University of Sheffield, Sheffield, UK \\
\affiliationListFont 2 Insigneo Institute for in-silico Medicine,
  The University of Sheffield, Sheffield, UK \\
\affiliationListFont 3 Department of Computer Science,
  The University of Sheffield, Sheffield, UK \\
\affiliationListFont 4 Department of Automatic Control Systems Engineering,
  The University of Sheffield, Sheffield, UK \\
\affiliationListFont 5 Department of Computer Science,
  The University of Patras, Patras, Greece \\
}

% The Corresponding Author should be marked with an asterisk. Provide
% the exact contact address (this time including street name and city
% zip code) and email of the corresponding author
\def\corrAuthor{Kevin Gurney}
\def\corrAddress{Department of Psychology, The University of Sheffield,
  Western Bank, Sheffield, S10 2TP, UK}
\def\corrEmail{k.gurney@sheffield.ac.uk}

% Figure out the font for the author list..
\def\Authors{\authorListFont Sebastian James\,$^{1,2}$, Alexander Blenkinsop\,$^{1,2}$,
  Alexander Cope\,$^3$, Sean Anderson\,$^{2,4}$, \\
  \authorListFont Chris Papapavlou\,$^5$, Konstantinos Moustakas\,$^5$, Kevin
  Gurney\,$^{1,2,*}$ \\[1 ex]  \Address \\
  \corrAuthorFont $^{*}$ Correspondence: \corrEmail}

% No page numbering please
\pagenumbering{gobble}

% A trick to get the bibliography to show up with 1. 2. etc in place
% of [1], [2] etc.:
\makeatletter
\renewcommand\@biblabel[1]{#1.}
\makeatother

% reduce separation between bibliography items if not using natbib:
\let\OLDthebibliography\thebibliography
\renewcommand\thebibliography[1]{
  \OLDthebibliography{#1}
  \setlength{\parskip}{0pt}
  \setlength{\itemsep}{0pt plus 0.3ex}
}

% Set correct font for bibliography (doesn't work yet)
%\renewcommand*{\bibfont}{\bibFont}

% No paragraph indenting to match the VPH format
\setlength{\parindent}{0pt}

% Skip a line after paragraphs
\setlength{\parskip}{0.5\baselineskip}
\onecolumn

% titling definitions
\pretitle{\begin{center}\titleFont}
\posttitle{\par\end{center}\vskip 0em}
\preauthor{ % Fonts are set within \Authors
        \vspace{-1.1cm} % Bring authors up towards title
        \begin{center}
        \begin{tabular}[t]{c}
}
\postauthor{\end{tabular}\par\end{center}}

% Define title, empty date and authors
\title {
  Integrating brain and biomechanics for the study of
  Parkinson's disease
}
\date{} % No date please
\author{\Authors}

%% END OF PREAMBLE

\begin{document}

\setlength{\droptitle}{-1.8cm} % move the title up a suitable amount
\maketitle

\vspace{-1.8cm} % HACK bring the introduction up towards the title. It
                % would be better to do this with titling in \maketitle

\section{Introduction}

\begin{wrapfigure}{r}{0.4\textwidth}
\includegraphics[width=0.4\textwidth]{./figures/model_overview.png}
\caption{The integrated model. The World maker component combines a
pre-defined series of luminances and the eye's rotational state to
produce a retinotopic map of the world in the eye's frame of reference
(an example surface map is shown for two cross-shaped luminances; one
at the fovea and one in the periphery). This is passed into
the \brain~model, which consists of retinal, cortical, basal ganglia
and collicular populations. The output of the \brain~model is encoded
as activity in a superior colliculus population (an example surface
map is shown for two peripheral luminances). Three pairs of brainstem
channels convert this position-encoded information into 6
time-dependent motoneuron signals which drive the eye model, updating
its rotational state.}
\vspace{-10pt}
\label{model_overview}
\end{wrapfigure}

% Can make comparisons
As mechanistic computational models of brain systems become more
sophisticated we can aspire to make realistic comparisons between the
behaviour of the model and that of the animal or human. This motivates
the development of \e{integrated brain and biomechanical systems}, to
express behaviour either in a virtual musculature or in an embodied
robotic system.

% Sometimes, ok to just have a brain model
In some cases, it is sufficient to take the activity of a neural
population as being representative of induced behaviour in the
individual. For example, a choice made in a \e{go/no-go} task could be
determined from activity in a population within a basal ganglia model
\mycite{nambu_discharge_1990,kuhn_event-related_2004}. The decision
to \e{go} is selected by a reduction of activity in this population;
maintenance of activity implies \e{no-go}. Error rates in this task
could be compared with experimentally determined error rates in
primate subjects, validating the model for the healthy subject.
% Now describe comparison between model and expt. for diseased
% subject.
If we can identify a characteristic degradation in the brain of an
unhealthy subject, then we can modify suitable parameters in the model
to reproduce it. By comparing the relationship between the model's
behaviour as a function of the degradation parameters with the
unhealthy individual's behaviour as a function of disease progression,
we may be able to relate the disease progression to the brain state
and predict the time-course of internal changes in the brain.
% Leave further discussion along these lines to the discussion
% section.

% But sometimes you might need brain and neuromuscular model
Of course, many behaviours are more complex than a two-way
decision. In the disease state, it may be the \e{dynamics} of the
movement which progress with time, rather than any movement outcome or
error rate. A diagnostic task may produce movement characteristics
which correlate with disease progression such as the slow, jerky or
inaccurate movements seen in Parkinson's Disease. In order to
determine the validity of a model which describes more complex
movements, it is necessary to express the movement commanded by the
brain network as a realistic, simulated motion by means of a
biomechanical model.

% Say what we've done here, in short form.
Parkinson's Disease (PD) is a progressive neurological disorder whose
main symptoms relate to motor control. These include resting tremor,
slowness of movements (bradykinesia), difficulty in initiating
movement (akinesia) and
rigidity \mycite{galvan_pathophysiology_2008}. It is considered to be
a disease of the basal ganglia because during its progression,
dopamine producing neurons in the substantia nigra pars compacta die
away, affecting the striatum, which depends on endogenous dopamine for
correct operation \mycite{javoy-agid_is_1980}. The basal ganglia plays
an important role in decision making and action
selection \mycite{schultz_reward_2000}, including the selection of
saccadic eye movements
\mycite{hikosaka_role_2000} which direct gaze towards putative targets
of interest. In the later stages of Parkinson's Disease, changes in
eye movement dynamics are observed; patients show more latent saccades
to targets of interest \mycite{chambers_response_2010}. They also
exhibit poorer performance \mycite{kitagawa_relationship_1994} in the
so-called anti-saccade protocol \mycite{munoz_look_2004}, in which the
subject is instructed to make a saccade \e{away} from a visual
target. These progressive changes in saccade dynamics in PD provided
the motivation to develop an integrated brain and biomechanical model
of the saccadic system.

%Parkinson's Disease patients make significantly more
%errors; they will saccade \e{to} the visual target rather
%than \e{away} from it more often than healthy control subjects.

% Motivation here is to study movement disorders by means of a
% comparison between healthy subjects, the healthy model and diseased
% subjects and the diseased model.
%To study PD, we chose to express saccadic eye movements in an
%integrated model.

%\pagebreak

\section{Material \& Methods}

% Add one weight map figure
\begin{wrapfigure}{r}{0.4\textwidth}
\includegraphics[width=0.4\textwidth]{./figures/w50_L.png}
\caption{One of six weight maps. This map makes a transformation from
a rotational position encoded in retinotopic space, where $r$ is
radial eccentricity and phi ($\phi$) is directional angle, extracting
the `leftwards rotation' component. For the left eye, this becomes
the command signal fed into the lateral rectus muscle. Note that $r$
and phi both have arbitrary units which scale from 1 to 50. These map
to $0\degree \leq \phi \leq 360\degree$ and $0\degree \leq r \leq
22\degree$.}
\vspace{-5pt}
\label{left_map}
\end{wrapfigure}

% A very short introduction to the section.
We started from the \ccg~model described
in \mycite{alex_cope_integrative_2015}, referred to here as
the \brain~model. This is a rate-coded neural network model
incorporating retinal populations, frontal eye fields (FEF), the basal
ganglia (BG), and the superior colliculus (SC). Rate-coded neural
elements are described by first order differential equations:
\[
   \dot{a} = {1 \over \tau}(a_{in}-a)
\]
where $\tau$ is the time constant for the neural activation and
$a_{in}$ is the input to the neural element. $a_{in}$ is defined by an
activation input and a shunting inhibition input according to: $a_{in}
= A(1-s_a)+0.01 R_N$. Here, $A$ is the activation input and $s_a$ is
the shunting inhibition state variable whose value is $S$ for $S\leq1$
and $1$ for $S>1$. $R_N$ is a random number between 0 and 1 drawn from
a normal distribution which introduces noise to the activation of the
neural element.

At each time step, the visual state of the `world' (as a retinotopic
map, with two axes $r$, radial eccentricity and $\phi$, directional
angle) is fed into the \brain~model, which then updates the state of
its output population, the SC (also a map). The `centre of mass' of
the activity in SC is assumed to accurately encode the location of the
eye at the end of the saccade \mycite{van_gisbergen_collicular_1987}.

To the \brain~model, we have added a saccadic burst generator (SBG)
model of neural populations in the brainstem's reticular formation,
which convert the position-encoding activity in the SC into motoneuron
signals \mycite{gancarz_neural_1998}, and a biomechanical eye
(Fig. \ref{model_overview}). The rotational state of the eye is used
to recalculate the view of the world in the eye's frame of reference
and then a retinotopic view is fed into back the \brain~model.

% short description of the brainstem model
The SBG is based on the model of two opposing channels described by
Gancarz and Grossberg in \mycite{gancarz_neural_1998}. This model
incorporates an internal inhibitory negative feedback loop and encodes
force in its output motoneurons. When integrating this model with
the \brain~model, it became clear that an inhibitory reset mechanism
was also required for the superior colliculus; without such a reset, a
series of staircase saccades would occur, as seen in SC stimulation
studies \mycite{schiller_single-unit_1972}. Recent evidence of
inhibitory retinotectal connections \mycite{wang_macaque_2010}
supports the inclusion of this connection in the model and makes
possible the removal of the internal negative feedback connection of
the Gancarz and Grossberg model, for which it is hard to find clear
evidence.

Input to the SBG comes from the SC of the \brain~model via
six retinotopic, many-to-one weight maps, an example of which is
shown in Fig.\ref{left_map}.

% EYE MODEL DESCRIPTION HERE
The biomechanical eye model, implemented using the OpenSim framework
\mycite{seth_opensim:_2011}, is anatomically represented by a sphere of
uniform mass distribution which is actuated by six extraocular muscles
(EOMs). The EOMs are arranged in three pairs forming a cone inside the
orbit with the apex being located inside the cranium in a tendonous
ring called the annulus of Zinn. An important feature of the
oculomotor system which greatly affects its overall behavior is the
existence of dynamic EOM pulleys. Their role is to guide the pivot
point of the EOMs. In our model, a pulley for each EOM has been
modeled by a point on the orbit whose location depends on the current
eye orientation.

%EOM dynamics
The force applied by EOMs is controlled by an excitatory signal
supplied by motoneurons in the brainstem. The dynamics of muscular
forces can be split into: 1) The elasticity of the muscles. 2) A delay
between the onset of the afferent excitatory signal and the actual
muscle contraction, caused by the transmission time of the action
potentials and by the necessary calcium release at the muscle
fibres. We developed a custom extraocular muscle model which captures
these features.
%Orbital fat force
Passive forces due to the fatty tissues inside the eye orbit also
affect eye dynamics. Their role is critical in eliminating the
influence of head and body movements. We incorporated a custom torque, $\mathbf{t}$,
which acts like a rotational spring-damper apparatus, resisting
eyeball movements. It has elastic and viscous properties governed by
$\mathbf{t} = -K\mathbf{R}-C\mathbf{U}$ where $\mathbf{R}$ is the
eye's orientation and $\mathbf{U}$ is its angular velocity. $K$ and
$C$ are constants.

% Say this one implemented in SpineML. (Could probably lose most of
% this)
The \brain~and SBG models were produced using SpineCreator
\mycite{cope_spinecreator_2015} and saved in the declarative,
simulator-agnostic markup language
SpineML \mycite{richmond_model_2014}. SpineML\_2\_BRAHMS
(\stob) \mycite{cope_spineml_2_brahms_2015-1} was used to simulate the
model.

%%%%%%%%%%%%%%% RESULTS FIGURE %%%%%%%%%%%%%%%%%%%%
% FIXME: add something about the fact that if the viscosity of the
% eye is too high, then saccades will be hypometric, or slow to
% arrive on target, underlining the need for an adaptive mechanism to
% tune the period during which the motoneuron output is at its
% ``high'' level.
%
% Figure is: Couple of rotation graphs. Taken from the model of branch
% 201605_VPH_2016_results with saccsim on branch
% brahms_201605_VPH_2016_results and SpineML_2_BRAHMS on branch
% NoTremor_Oculomotor_201603.
% Luminances file was:
% {"luminances":[
% {"shape":"cross","widthThetaX":6,"widthThetaY":2,"timeOn":0.15,"timeOff":10,
%  "thetaX":4,"thetaY":-8,"luminance":0.2}
% ]}
% OR:
% {"luminances":[
% {"shape":"cross","widthThetaX":6,"widthThetaY":2,"timeOn":0.15,"timeOff":10,
%  "thetaX":0,"thetaY":8,"luminance":0.2}
% ]}
%
\begin{wrapfigure}{R}{0.55\textwidth}
\includegraphics[width=0.55\textwidth]{./figures/results/20160523/vph_2016/trajectoryRX8RY8.png}
\caption{\textbf{Main graph:} Representative oblique saccade made by the
model from fixation to target locations shown. Data points are shown
at 1 ms intervals. \textbf{Top inset:} Three rotational components of
the trajectory plotted against time (a proportion of the data point
symbols have been omitted for clarity). Fixation and target luminance
positions are plotted as dashed and dotted lines. \textbf{Bottom
inset:} Endpoint scatter --- the latter part (400--800 ms) of 8
repeated simulations showing how noise in the \brain~model affects the
final rotation of the eye.}
\vspace{-10pt}
\label{trajectory}
\end{wrapfigure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Three hand-written components are integrated into the
SpineML \brain~model: the biomechanical eye model; a component which
computes the centroid of a neural layer; and a component which takes
the eye's rotational state and the current visible luminances and
projects a retinotopic activity map into the \brain~model. Each of
these three BRAHMS components was hand written in C++.

% A description of the timestep issue
One challenge we encountered when integrating the eye model had to do
with the simulation time steps. The brain and brainstem models
required a common simulation time step of 1 ms, using a Forward Euler
solution method. The eye model worked optimally with a 25 ms time
step.  To resolve this issue, the eye model component was called on
each 1 ms timestep, but only recomputed its outputs every 25 time
steps.

% This section was previous under ``Results''
Parameters in the brain, brainstem and eye models were trained
independently. The \brain~model parameters were retained from
% well - unchanged apart from the dopamine params
\mycite{alex_cope_integrative_2015}. The brainstem model
was hand trained so that populations had temporal responses to match
experimental data from the literature. After integration, the six
weight maps between the superior colliculus and the SBG input neurons
were trained.
% How the model was trained, results of training.
%% Because there is noise in the \brain~model, a given luminance input
%% sequence does not always produce the same activity in superior
%% colliculus. As a result, it's not possible to record the activity
%% produced in SC for a given target luminance and then run a training
%% procedure which involves only the brainstem and eye model; the entire
%% model must be run for each iteration of the training process. This
%% makes the application of a traditional neural network training
%% algorithm, in which each weight map is regarded as a 2500-D weight
%% vector, computationally expensive.  To simplify the problem, the
%% centroid of the activity in the SC is computed, populating a map
%% called SC$_{avg}$. Only a single location in the SC$_{avg}$ map is
%% ever active, which means that for a given target luminance, it is
%% possible to write the same scalar weight in every element of the
%% weight map, which reduces the dimensionality of the weight space to
%% three.
Because there is noise in the \brain~model's output (See
Fig. \ref{trajectory}, lower inset), it is necessary to run the
entire, integrated model to train the SC to SBG weight maps. This
makes the application of a traditional neural network training
algorithm, in which each weight map is regarded as a 2500-D weight
vector, computationally expensive.
%It is not feasible to run the
%integrated model, which requires approximately two minutes on a
%typical CPU to simulate a single saccade, the many thousands of times
%required to find the solution in this high dimensional parameter
%space.
To simplify the problem, the centroid of the activity in the SC is
computed, populating a map called SC$_{avg}$. Only a \e{single
location} in the SC$_{avg}$ map is ever active, which means that for a
given target luminance, it is possible to write the same scalar weight
in all 2500 elements of the weight map, which reduces the
dimensionality of the weight space to three (one weight map for each
of three active extraocular muscles).  Input was given to the model in
the form of a target luminance at a given $(\theta_{x},\theta_{y})$
location. The weight maps were then adjusted in a gradient descent
process until the rotational angle of the eye after the first saccade
matched $(\theta_{x},\theta_{y})$, with $\theta_{z}=0$. The process
was repeated for a range of $(\theta_{x},\theta_{y})$.

%% Some detail omitted:
%The procedure makes the
%assumption that the components of the weight vector and the error
%vector are mutually orthogonal. This is not generally true, and so the
%weight training will not always complete; some target locations need
%to be re-run with differing start weights.

%Inspection of the weight maps shows that the weight increases
%approximately exponentially as a function of radial eccentricity, $r$,
%due to an exponential reduction in retinal neural density towards the
%edge of the field of view. A geometric argument would suggest that the
%weight should vary sinusoidally with the directional angle
%$\phi$ \mycite{tabareau_geometry_2007}.

\section{Results}

Our result for the shape of the weight maps (as in
Fig.~\ref{left_map}) agrees with theoretical work by Tabareau et
al. \mycite{tabareau_geometry_2007} and with a previous study which
computed weight maps in a similar
model \mycite{arai_two-dimensional_1994}. Additionally, our result
demonstrates that weight maps for the oblique muscles can be found
such that the axial rotation (R$_{ax}$) of the eye may follow a fixed
function of elevation (R$_{el}$) and azimuth (R$_{az}$); in this case
we required R$_{ax}$ = F(R$_{el}$,R$_{az}$) = 0 for all
R$_{el}$,R$_{az}$.

Fig.~\ref{trajectory} shows a resulting eye movement to a single
luminance target. A fixation (with luminance value 0.5) is presented
to the model for 150 ms. At 150 ms, the fixation is replaced by a
target at $\theta_{x}$=8$\degree$, $\theta_{y}$=8$\degree$ (a target
eye rotation of 8$\degree$~left and 8$\degree$~up). The saccade has a
realistic latency of 175 ms and a movement time of approximately 50
ms.

\section{Discussion and Conclusions}

% Be sure to say that ``in future work, it will be possible to
% investigate saccade trajectory modifications in Parkinson's''
We have demonstrated the integration of a \brain~model with a
neuromuscular model of three degrees of freedom. This model forms a
platform for the study of internal brain state in Parkinson's disease
and how this relates to saccade behaviour.
% Could lose this:
In future work it will be
possible to study saccade trajectory modifications with the
modification of dopamine expression in the model. It will be possible
to extend the model to examine antisaccade behaviour. It forms a
platform to study the effect of a more detailed treatment of portions
of the model, such as the incorporation of spiking models of basal
ganglia, a striatal microcircuit or a detailed simulation of the
superior colliculus.

\section*{Acknowledgements}
This work is partially funded by the EC FP7 project NoTremor --- Virtual,
Physiological and Computational Neuromuscular Models for the
Predictive Treatment of Parkinson's Disease, Grant Agreement
No.~610391.

\selectlanguage{English}
\bibliographystyle{abbrvnotitle}
% The bibliography NoTremor.bib is the one exported from Zotero.
\bibliography{NoTremor}

%%% Upload the *bib file along with the *tex file and PDF on
%%% submission if the bibliography is not in the main *tex file

\end{document}

### 2017-05-03 batch_scripts/analysis/find_missing.sh

@@ -1,0 +1,15 @@
+#!/bin/sh
+
+# This script finds which runs from a weight finding session failed to
+# complete. Made obsolete by the fact that the Iceberg settings are
+# now good and the weight training runs complete reliably.
+
+for i in runwf3dmany*.out; do
+    tail -n 50 "$i" | grep Overall > /dev/null 2>&1
+    rtn=$?
+    if [ $rtn == "1" ]; then
+        # Then this one doesn't contain the "Overall best weights"
+        # line and needs to be re-computed.
+        echo -n "$i " |  sed 's/runwf3dmany//g' | tr --delete ".out"
+    fi
+done

### 2017-05-03 batch_scripts/analysis/fit_curve_down.m

@@ -1,0 +1,53 @@
+% Parameter search script. This is analogous to fit_curve_up.m
+
+% First run the load_allweights.m script to ensure that the working
+% environment contains e50, e50map, etc etc.
+
+addpath('include');
+
+% To get stdout scrolling past while this runs:
+page_screen_output(0);
+page_output_immediately(1);
+
+%
+% Algorithm parameters
+%
+
+% The fit threshold. If the objective function returns a value
+% below this number, then the fit is considered acceptable and the
+% algorithm ends.
+algo_params.fit_threshold = 0.2;
+
+% Temperature parameters
+algo_params.temp = 1;
+algo_params.coolrate = 0.02;
+algo_params.low_temp_threshold = 0.000000001;
+
+%
+% Parameter ranges. Parameters are discretized here, to give the
+% system many possible states.
+%
+
+% All iterators in range 1 to 1024.
+op.rangesz = 1024;
+
+% objective function parameters
+coarse_search = 1;
+if coarse_search>0
+    [op.a, op.ai] = make_param (0.005, 5, op.rangesz);
+    [op.k, op.ki] = make_param (0.001, 0.5125, op.rangesz);
+    [op.b, op.bi] = make_param (0.001, 5, op.rangesz);
+    [op.l, op.li] = make_param (0.001, 0.12, op.rangesz);
+    [op.os, op.osi] = make_param (23.4, 25.4, op.rangesz);
+    [op.wg, op.wgi] = make_param (0.8, 1.2, op.rangesz);
+else % finer search alternative
+    [op.a, op.ai] = make_param (0.005, 5, op.rangesz);
+    [op.k, op.ki] = make_param (0.01, 0.1, op.rangesz);
+    [op.b, op.bi] = make_param (2, 4, op.rangesz);
+    [op.l, op.li] = make_param (0.005, 0.1, op.rangesz);
+    [op.os, op.osi] = make_param (23.4, 24.4, op.rangesz);
+    [op.wg, op.wgi] = make_param (1, 1.1, op.rangesz);
+end
+
+% Group params here.
+fitcurve (e54map, e54means, op, algo_params);

### 2017-05-03 batch_scripts/analysis/fit_curve_up.m

@@ -1,0 +1,231 @@
+% This is a curve fitting script. It attempts to fit a curve of the
+% form:
+%
+% y(r,theta) = (a .* exp(k.*r) .- b .* exp(l.*r)) ...
+%               .* cos (2.*pi .* (wg.*(theta-os)./50));
+%
+% to data found in "e53" which is loaded with the load_allweights.m
+% script.
+%
+% Simulated annealing is used to search the parameter space of
+% y(r,theta) (a,k,b,l,wg and os).
+
+% First run the load_allweights.m script to ensure that the working
+% environment contains e50, e50map, etc etc.
+
+%% FIXME: Make this work with fitcurve.m
+
+% You will need the include dir containing weight_surface_one.m
+% (abrg_local/Oculomotor/batch_scripts/include) to be in your
+% matlab/octave path.
+
+% To get stdout scrolling past while this runs:
+page_screen_output(0);
+page_output_immediately(1);
+
+%
+% Algorithm parameters
+%
+
+% The fit threshold. If the objective function returns a value
+% below this number, then the fit is considered acceptable and the
+% algorithm ends.
+fit_threshold = 0.1;
+
+% Temperature parameters
+temp = 1;
+coolrate = 0.02;
+low_temp_threshold = 0.000000001;
+
+%
+% Parameter ranges. Parameters are discretized here, to give the
+% system many possible states.
+%
+
+% All iterators in range 1 to 1024.
+rangesz = 1024;
+
+[a, ai, afit] = make_param (0.005, 5, rangesz);
+
+[k, ki, kfit] = make_param (0.01, 0.1, rangesz);
+
+[b, bi, bfit] = make_param (2, 4, rangesz);
+%b = zeros(1,rangesz); bi = 40; bfit = b(bi);
+
+[l, li, lfit] = make_param (0.005, 0.10, rangesz);
+
+[os, osi, osfit] = make_param (23.4, 26.0, rangesz);
+
+[wg, wgi, wgfit] = make_param (1, 1.1, rangesz);
+
+% Full region for the surface; 50x50 grid
+r = 1:50;
+theta = 1:50;
+[R, THETA] = meshgrid (r, theta);
+
+
+% Function can start here.
+
+%
+% Compute first iteration and goodness of fit. Note our curve for
+% fitting in in weight_surface_one.m
+%
+
[…]

### 2017-05-03 batch_scripts/analysis/load_interp.m

@@ -1,0 +1,147 @@
+% This is the script with which to load and linearly interpolate
+% the weight training data.
+%
+% Load data, then interpolate to fill in gaps in the data, then
+% write out weight maps (explicitDataBinaryFiles).
+
+show_figures = 1
+
+% First:
+load_justdata
+
+% Use these to work on a portion of the map
+%mapside = 8;
+%mapstarttheta = 16;
+%mapstartr = 25;
+
+% Full map:
+mapside = 50;
+mapstarttheta = 1;
+mapstartr = 1;
+
+% For use in scatter graphs below
+[XX, YY] = meshgrid (1:mapside, 1:mapside);
+
+testmap = e57map(mapstarttheta:mapstarttheta+mapside-1,
+                 mapstartr:mapstartr+mapside-1);
+[interpmap, finalmap] = interpolate (testmap);
+if show_figures
+figure(1); scatter3(XX,YY,testmap,5,'filled'); title('initialmap e57');
+%%figure(2); scatter3(XX,YY,interpmap,5,'filled'); title('interp');
+figure(3); scatter3(XX,YY,finalmap,5,'filled'); title('finalmap e57');
+end
+final_e57 = finalmap;
+
+% For e58map, I need to interpolate over two rectangular regions.
+% Region 1:
+thetaside = 15;
+rside = 50;
+mapstarttheta = 35;
+mapstartr = 1;
+testmap = e58map(mapstarttheta:mapstarttheta+thetaside-1, ...
+                 mapstartr:mapstartr+rside-1);
+[interpmap, finalmap1] = interpolate (testmap);
+[XR, YR] = meshgrid (1:rside, mapstarttheta:mapstarttheta+thetaside-1);
+if show_figures
+figure(4); scatter3(XR,YR,testmap,5,'filled');
+title('initialmap e58 region 1');
+%%figure(5); scatter3(XR,YR,interpmap,5,'filled'); title('interp');
+figure(6); scatter3(XR,YR,finalmap1,5,'filled');
+title('finalmap e58 region 1');
+end
+% Region 2:
+thetaside2 = 20;
+mapstarttheta2 = 1;
+testmap = e58map(mapstarttheta2:mapstarttheta2+thetaside2-1, ...
+                 mapstartr:mapstartr+rside-1);
+[interpmap, finalmap2] = interpolate (testmap);
[…]

### 2017-05-03 batch_scripts/analysis/load_justdata.m

@@ -1,0 +1,38 @@
+% Load the file which contains the weights determined by the
+% rotations_weight_finder_centroid_3d.m
+%
+% /fast/pc1ssj/allweights.log
+%
+% This file has the following format:
+%
+% /var/spool/sge/node162/job_scripts/1048650 - Theta X range: -22 to 22; Theta Y range:  -22 to 22
+% /var/spool/sge/node162/job_scripts/1048650 - explicitDataBinaryFileN.bin: L:50 R:52 U:53 D:54 Z+:58 Z-:57
+% 53,1,11.000000,42,28,0.816035,40.807996,26.815072
+% 50,2,10.000000,42,28,0.698534,40.807996,26.815072
+%
+% Lines starting with a script path signify the "run set" range.
+%
+% Other lines have this format:
+% 
+% weight_file_number, axis(X/Y/Z), target angle, map positionX, map
+% positionY, best weight, scd centroid X, scd centroid Y.
+%
+% weight_file_number is the number in,
+% e.g. explicitDataBinaryFile50.bin. axis(X/Y/Z) is a number - 1 for
+% X, 2 for Y, 3 for Z.
+
+% 50,2,10.000000,32,27,0.643945,31.282605,25.800921
+allweights = dlmread ('allweights_mod.log');
+
+% Up
+[ e53map, e53means, e53 ] = justdata (allweights, 53);
+% Left
+[ e50map, e50means, e50 ] = justdata (allweights, 50);
+% Right
+[ e52map, e52means, e52 ] = justdata (allweights, 52);
+% Down
+[ e54map, e54means, e54 ] = justdata (allweights, 54);
+% Z-
+[ e57map, e57means, e57 ] = justdata (allweights, 57);
+% Z+
+[ e58map, e58means, e58 ] = justdata (allweights, 58);

### 2017-05-03 batch_scripts/analysis/load_ocm.m

@@ -1,0 +1,156 @@
+% A script to load in the relevant data from the SpineML output.
+%
+% This script is designed to load the data generated by experiment 0
+% of the Oculomotor SpineML model.
+%
+% All the data is returned in a structure called model_data.
+%
+% Usually called something like this:
+%
+% model_data = load_ocm ('/home/seb/src/SpineML_2_BRAHMS/temp');
+%
+function model_data = load_ocm (output_base_path)
+
+    isOctave = exist('OCTAVE_VERSION', 'builtin') ~= 0;
+
+    model_log_path = [output_base_path '/log/'];
+    model_run_path = [output_base_path '/run/'];
+
+    % Load in activation state vars for SpineML/SpineCreator model
+    [fef_add_noise, count] = load_sc_data ([model_log_path ...
+                        'FEF_add_noise_out_log.bin'], 2500);
+    [fef, count] = load_sc_data ([model_log_path ...
+                        'FEF_out_log.bin'], 2500);
+    [strd1, count] = load_sc_data ([model_log_path ...
+                        'Str_D1_out_log.bin'], 2500);
+    [strd2, count] = load_sc_data ([model_log_path ...
+                        'Str_D2_out_log.bin'], 2500);
+    [stn, count] = load_sc_data ([model_log_path ...
+                        'STN_out_log.bin'], 2500);
+    [snr, count] = load_sc_data ([model_log_path ...
+                        'SNr_out_log.bin'], 2500);
+    [gpe, count] = load_sc_data ([model_log_path ...
+                        'GPe_out_log.bin'], 2500);
+
+    [world, count] = load_sc_data ([model_log_path ...
+                        'World_out_log.bin'], 2500);
+
+    [ret1, count] = load_sc_data ([model_log_path ...
+                        'Retina_1_out_log.bin'], 2500);
+    [ret2, count] = load_sc_data ([model_log_path ...
+                        'Retina_2_out_log.bin'], 2500);
+
+    [scd, count] = load_sc_data ([model_log_path ...
+                        'SC_deep_out_log.bin'], 2500);
[…]

### 2017-05-03 batch_scripts/analysis/load_ocm_min.m

@@ -1,0 +1,47 @@
+% This is a minimum version of load_ocm.m to load data from a weight
+% training run (experiment 2, which logs from fewer populations).
+function model_data = load_ocm_min (output_base_path)
+
+    isOctave = exist('OCTAVE_VERSION', 'builtin') ~= 0;
+
+    model_log_path = [output_base_path '/log/'];
+    model_run_path = [output_base_path '/run/'];
+
+    % Load in activation state vars for SpineML/SpineCreator model
+    [scd, count] = load_sc_data ([model_log_path ...
+                        'SC_deep_out_log.bin'], 2500);
+    
+    [sca, count] = load_sc_data ([model_log_path ...
+                        'SC_avg_out_log.bin'], 2500);
+
+    [llbn_l, count] = load_sc_data ([model_log_path 'LLBN_left_a_log.bin'], 1);
+    [llbn_r, count] = load_sc_data ([model_log_path 'LLBN_right_a_log.bin'], 1);
+    [llbn_u, count] = load_sc_data ([model_log_path 'LLBN_up_a_log.bin'], 1);
+    [llbn_d, count] = load_sc_data ([model_log_path 'LLBN_down_a_log.bin'], 1);
+    %[llbn_zp, count] = load_sc_data ([model_log_path 'LLBN_zplus_a_log.bin'], 1);
+    %[llbn_zm, count] = load_sc_data ([model_log_path 'LLBN_zminus_a_log.bin'], 1);
+
+    scd = reshape (scd, 50, 50, []);
+    sca = reshape (sca, 50, 50, []);
+
+    % Eye rotations
+    SS = csvread ([model_run_path 'saccsim_side.log'], 1 , 0);
+    eyeRx = SS(:,8);
+    eyeRy = SS(:,9);
+    eyeRz = SS(:,10);
+    eyeTime = SS(:,1);
+    clear SS;
+
+    % Now build up the structure to return.
+    keySet = {'scd', 'sca', ...
+              'eyeRx', 'eyeRy', 'eyeRz', 'eyeTime', ...
+              'llbn_l', 'llbn_r', 'llbn_u', 'llbn_d'}; %, 'llbn_zp', 'llbn_zm'};
+    valueSet = {scd, sca, ...
+                eyeRx, eyeRy, eyeRz, eyeTime, ...
+                llbn_l, llbn_r, llbn_u, llbn_d}; %, llbn_zp, llbn_zm};
+    model_data = struct();
[…]

### 2017-05-03 batch_scripts/analysis/nsurf.m

@@ -1,0 +1,19 @@
+% nsurf - plot a neural surface from the model, scaling the phi axis
+% so that it runs from 0 to 360 degrees. r could also be scaled,
+% but I've left that commented out.
+function nsurf (neural_sheet)
+
+    phideg = pixtophidegrees([1:50]);
+
+    % You can scale r to show it in degrees:
+    %rdeg = pixtordegrees([1:50]);
+    %surf (rdeg,phideg,neural_sheet);
+    %xlabel('r (deg)');
+
+    % Or leave it as 1:50:
+    surf ([1:50],phideg,neural_sheet);
+    xlabel('r');
+
+    ylabel('phi (deg, 0=U, 90=L)')
+    set(gca,'YTick',0:90:360);
+end

### 2017-05-03 batch_scripts/analysis/view_omm.m

@@ -1,0 +1,145 @@
+function view_omm (data, t, fignum)
+%% View the model output 'data' in a customised multiple plot at time t. fignum
+%% is an optional argument so you can show several timesteps in
+%% different figures.
+
+    if nargin < 2
+       display ('at least 2 args required (data and time t)');
+       return;
+    end
+    
+    if nargin < 3
+        fignum = 75;
+    end
+
+    h_f = figure (fignum); clf;
+    
+    %set (h_f,'units','normalized','outerposition', [ 0 0.4 0.7 0.5]);
+    text (0, 0, ['Time = ' num2str(t) ' ms']);
+
+    % Spacing for subaxes
+    sa_spc = 0.03;
+    sa_pad = 0.01;
+    sa_pad_2d = 0.03;
+    sa_marg = 0.03;
+    
+    % Parameters for the view for 3D surf plots:
+    view_azi = 30;
+    view_elev = 20;
+
+    % Your favoured line width and marker size:
+    lw = 2;
+    ms = 20;
+    
+    h_world = subaxis (2,5,1, 'Spacing', sa_spc, 'Padding', sa_pad, 'Margin', sa_marg);
+    surf (data.world(:,:,t));
+    %colormap(h_world, 'autumn')
+    zlim([0 1]);
+    view([view_azi view_elev]);
+    title(['World @ ' num2str(t) ' ms']);
+
+    h_fef = subaxis (2,5,2, 'Spacing', sa_spc, 'Padding', sa_pad, 'Margin', sa_marg);
+    surf (data.fef(:,:,t));
+    %colormap(h_fef, 'winter')
+    zlim([0 1]);
+    view([view_azi view_elev]);
+    title('FEF');
+
+    subaxis (2,5,3, 'Spacing', sa_spc, 'Padding', sa_pad, 'Margin', sa_marg);
+    surf (data.thal(:,:,t));
+    %colormap('hot')
+    zlim([0 1]);
+    view([view_azi view_elev]);
+    title('Thalamus');
+
+    subaxis (2,5,6, 'Spacing', sa_spc, 'Padding', sa_pad, 'Margin', sa_marg);
+    surf (data.stn(:,:,t));
+    %colormap('hot')
+    zlim([0 1]);
+    view([view_azi view_elev]);
[…]

### 2017-05-03 batch_scripts/analysis/weightproving_errors.m

@@ -1,0 +1,16 @@
+% Show the error of the model from the weightproving.log file.
+
+alldata = dlmread ('weightproving_mod.log');
+
+RotX=alldata(:,1);
+RotY=alldata(:,2);
+
+AvX=alldata(:,4);
+AvY=alldata(:,6);
+Err = sqrt (power(AvX-RotX, 2) + power (AvY-RotY, 2));
+
+% No colour
+scatter3(AvX,AvY,Err,4,'filled');
+
+% With colour
+%scatter3(AvX,AvY,Err,4,Err,'filled');

### 2017-05-03 batch_scripts/cleanup.sh

@@ -1,0 +1,15 @@
+#!/bin/sh
+#$ -l mem=1G
+#$ -l rmem=1G
+#$ -l h_rt=64:59:00
+
+# This script cleans up /fastdata/pc1ssj following weight training or
+# other model runs. It can take a long time and should be qsubbed.
+
+pushd /fastdata/pc1ssj
+rm rwf3dmany*
+rm r[0-9]*_run_sim.sh
+rm logRX*
+mv allweights.log allweights.log.1
+find -maxdepth 1 -path './oculomotorRX*' -exec rm -rf {} \;
+popd

### 2017-05-03 batch_scripts/expt_antisaccades/baseline.m

@@ -1,0 +1,50 @@
+% Explore antisaccades with two luminances each side of the eye.  This
+% "baseline" run just plonks two luminances in the field of view with
+% a "step" from fixation to targets and allows the model to saccade to
+% one of them. Runs the expt numerous times and finds out the number
+% of lefts vs. rights and the latencies.
+
+% Fixed parameters
+params.targetThetaY = -12;
+params.targetThetaX = 0;
+params.num_par_runs = 8;
+params.dopamine = 0.3;
+params.targetCross=0; % 1 if target should be the cross shape.
+params.targetLuminance=4;
+params.targetWidthX=4;
+params.targetWidthY=4;
+params.fixCross=0;
+params.fixLuminance=0.2;
+params.fixWidthX=2;
+params.fixWidthY=2;
+params.fixOn=0.0;
+params.fixOff=0.2
+params.targetOn=0.2
+params.targetOff=1.0;
+params.use_insigneo=1; % Set to 1 to use Insigneo queues on Iceberg
+params.cleanup=1; % Set to 1 to clean up used files.
+params.model_dir = '/home/pc1ssj/abrg_local/Oculomotor';
+
+% At the end of the script you'll have a vector of mean latencies a
+% vector of latency SDs, a vector of final angle means and one of
+% SDs, and of course your fixation/target matrix which you set up.
+lat_mean = [];
+lat_sd = [];
+fa_mean = [];
+fa_sd = [];
+
+%for ft = fixtarg
+    
+    printf ('Finding latency for fixation off: %f  target on: %f', ft(1), ft(2));
+    
+    [avg, sd, finals, sm] = find_latency_dual (params);
+    lm = mean(sm);
+    ls_ = std(sm);
+    lat_mean = [lat_mean lm];
+    lat_sd = [lat_sd ls_];
+    fa_mean = [fa_mean avg];
+    fa_sd = [fa_sd sd];
+%end
+
+% Call the save results script
+%save_results

### 2017-05-03 batch_scripts/expt_antisaccades/explore_antisaccades.m

@@ -1,0 +1,54 @@
+% Explore antisaccades with two luminances each side of the eye.
+
+% You set these:
+target_angle_y = 12; % +ve.
+target_angle_x = 0;
+num_runs_per_point = 8;
+da = 0.3;
+
+% Here are the fixation off/target on numbers:
+fixtarg = [
+    0.30 0.15;
+    0.28 0.15;
+    0.26 0.15;
+    0.24 0.15;
+    0.22 0.15;
+    0.2 0.15;
+    0.2 0.17;
+    0.2 0.19;
+    0.2 0.21;
+    0.2 0.23;
+    0.2 0.25;
+    0.2 0.27;
+    0.2 0.29;
+    0.2 0.31;
+    0.2 0.33;
+    0.2 0.35;
+    0.2 0.37;
+    0.2 0.39;
+          ];
+% Turn the matrix round now (better for the loop and matches
+% lat_mean and friends):
+fixtarg = fixtarg';
+
+% At the end of the script you'll have a vector of mean latencies a
+% vector of latency SDs, a vector of final angle means and one of
+% SDs, and of course your fixation/target matrix which you set up.
+lat_mean = [];
+lat_sd = [];
+fa_mean = [];
+fa_sd = [];
+
+for ft = fixtarg
+    
+    printf ('Finding latency for fixation off: %f  target on: %f', ft(1), ft(2));
+    
+    [avg, sd, finals, sm] = find_latency (target_angle_x,target_angle_y,num_runs_per_point,...
+                                          da,ft(1),ft(2));
+    lm = mean(sm);
+    ls = std(sm);
+    lat_mean = [lat_mean lm];
+    lat_sd = [lat_sd ls];
+    fa_mean = [fa_mean avg];
+    fa_sd = [fa_sd sd];
+end

### 2017-05-03 batch_scripts/expt_antisaccades/save_results.m

@@ -1,0 +1,13 @@
+num_points = size(lat_mean)(2);
+% Make sure we save only the relevant content of fixtarg
+fixation_off = fixtarg(1,1:num_points);
+target_on = fixtarg(2,1:num_points);
+gap = target_on-fixation_off;
+
+% Save the data to a dated file
+res_file_name = sprintf ('%s_results_da_%f.mat', datestr(now(), ...
+                                                  'yyyymmdd_HHMMSS'), ...
+                         da);
+
+save (res_file_name, 'fixation_off', 'target_on', 'gap', 'lat_mean', ...
+      'lat_sd', 'params', 'finals');

### 2017-05-03 batch_scripts/expt_latency_vs_dopamine/save_results.m

@@ -1,0 +1,25 @@
+% Save the results produced by the find_latencies script.
+
+num_points = size(lat_mean)(2);
+
+
+% Save the data to a dated file
+res_file_name = sprintf ('%s_targlum%f_gap%f', datestr(now(), ...
+                                                  'yyyymmdd_HHMMSS'), ...
+                         params.targetLuminance, gap);
+
+save ([res_file_name '.mat'], 'da', 'lat_mean', 'lat_sd', 'params', 'fa_mean', 'fa_sd');
+
+csvwrite (['combined-' res_file_name '.csv'], [da' lat_mean' lat_sd']);
+
+% Let's have some figures, too.
+disp('figures')
+figure(1)
+errorbar (da, fa_mean(:,2), fa_sd(:,2), 'o-')
+xlabel ('DA parameter value')
+ylabel ('eyeRy (degrees)')
+
+figure(2)
+errorbar (da, lat_mean, lat_sd, 'ro-')
+xlabel ('DA parameter value')
+ylabel ('Latency (ms)')

### 2017-05-03 batch_scripts/expt_latency_vs_gap/find_latencies.m

@@ -1,0 +1,68 @@
+% Run find_latency several times to explore latency vs the
+% fixation-target gap.
+
+% Fixed parameters
+params.targetThetaY = -12;
+params.targetThetaX = 0;
+params.num_par_runs = 8;
+params.dopamine = 0.3;
+params.targetCross=0; % 1 if target should be the cross shape.
+params.targetLuminance=1.8;
+params.targetWidthX=4;
+params.targetWidthY=4;
+params.fixCross=0;
+params.fixLuminance=0.2;
+params.fixWidthX=2;
+params.fixWidthY=2;
+params.fixOn=0;
+params.targetOff=1;
+params.use_insigneo=1; % Set to 1 to use Insigneo queues on Iceberg
+params.cleanup=1; % Set to 1 to clean up used files.
+
+% Here are the fixation off/target on numbers:
+fixtarg = [
+    0.5 0.15;
+    0.45 0.15;
+    0.4 0.15;
+    0.35 0.15;
+    0.30 0.15;
+    0.26 0.15;
+    0.22 0.15;
+    0.2 0.17;
+    0.2 0.2;
+    0.2 0.25;
+    0.2 0.29;
+    0.2 0.31;
+    0.2 0.35;
+    0.2 0.39;
+    0.2 0.5;
+          ];
+% Turn the matrix round now (better for the loop and matches
+% lat_mean and friends):
+fixtarg = fixtarg';
+
+% At the end of the script you'll have a vector of mean latencies a
+% vector of latency SDs, a vector of final angle means and one of
+% SDs, and of course your fixation/target matrix which you set up.
+lat_mean = [];
+lat_sd = [];
+fa_mean = [];
+fa_sd = [];
+
+for ft = fixtarg
+    
+    printf ('Finding latency for fixation off: %f  target on: %f', ft(1), ft(2));
+    
+    params.fixOff = ft(1);
+    params.targetOn = ft(2);
+    [avg, sd, finals, sm] = find_latency (params);
+    lm = mean(sm);
+    ls_ = std(sm);
+    lat_mean = [lat_mean lm];
+    lat_sd = [lat_sd ls_];
+    fa_mean = [fa_mean avg];
+    fa_sd = [fa_sd sd];
+end
+
+% Call the save results script
+save_results

### 2017-05-03 batch_scripts/expt_latency_vs_gap/plot_combined.m

@@ -1,0 +1,34 @@
+## Copyright (C) 2015 S. James
+## 
+## This program is free software; you can redistribute it and/or modify it
+## under the terms of the GNU General Public License as published by
+## the Free Software Foundation; either version 3 of the License, or
+## (at your option) any later version.
+## 
+## This program is distributed in the hope that it will be useful,
+## but WITHOUT ANY WARRANTY; without even the implied warranty of
+## MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+## GNU General Public License for more details.
+## 
+## You should have received a copy of the GNU General Public License
+## along with this program.  If not, see <http://www.gnu.org/licenses/>.
+
+## Author: S. James <pc1ssj@node117.iceberg.shef.ac.uk>
+## Created: 2015-10-12
+
+
+figure(1)
+clf
+hold on;
+counter = 1;
+for lat_mean = lat_means'
+    fmtstr = ['o-' num2str(counter)];
+    plot (gap, lat_mean, fmtstr, 'linewidth', 2)
+    counter = mod(counter + 1, 6);
+end
+
+legend (num2str(lums(1)), num2str(lums(2)),num2str(lums(3)),num2str(lums(4)),num2str(lums(5)),num2str(lums(6)));
+
+xlabel('Gap (s)')
+ylabel('Latency to first movement (ms)')
+title('Latency vs. gap at different target luminances (1 to 4)')

### 2017-05-03 batch_scripts/expt_sacc_vs_luminance/plot_sacc_vs_l.m

@@ -1,0 +1,39 @@
+% Load the data generated by sacc_vs_luminance.sh runs
+r = struct();
+rr = [];
+
+num_runs=6
+
+figure(33);
+clf;
+
+colours = {'r','b','g','k','c','m','r--','b--','g--','k--','c--','m--'};
+colcount = 1;
+for i = [0.2 : 0.2 : 1.6]
+    resname = ['r_0_7_' num2str(i) '.dat'];
+    resdatname = ['r_0_7_' num2str(i)];
+    resdatname = strrep (resdatname, '.', '_');
+
+    load (resname); % loads struct variable called result
+    r = struct_merge (r, result);
+
+    rr = [rr; result.(resdatname)];
+
+    % Also plot each trajectory from the model run data
+    for j=1:num_runs
+        filepath=['/fastdata/pc1ssj/oculomotorRX0RY7_' num2str(i) '_' num2str(j)];
+        A=load_ocm_min(filepath);
+        figure(33);
+        hold on;
+        plot (A.eyeRy, colours{colcount})
+    end
+    colcount = colcount + 1;
+
+end
+
+% rr array contains these columns:
+% lumval, eyeRxAvg, eyeRyAvg, eyeRzAvg, eyeRxSD, eyeRySD, eyeRzSD
+rr
+
+figure(32);
+errorbar (rr(:,1),rr(:,3),rr(:,6),'o-')

### 2017-05-03 batch_scripts/expt_sacc_vs_luminance/sacc_vs_luminance.m

@@ -1,0 +1,33 @@
+%% Used by sacc_vs_luminance.sh. Runs the model num_par_runs times
+%% for a given lumval.
+%%
+%% Usage:
+%%
+%%   sacc_vs_luminance (targetThetaX, targetThetaY, num_par_runs,
+%%                      lumval)
+%%
+function sacc_vs_luminance (targetThetaX, targetThetaY, num_par_runs, lumval)
+
+    page_screen_output(0);
+    page_output_immediately(1);
+
+    cleanup = 0;
+    use_insigneo = 1;
+    model_dir = '/home/pc1ssj/abrg_local/Oculomotor';
+
+    write_single_luminance ([model_dir '/luminances.json'], targetThetaX, targetThetaY, lumval);
+
+    output_dirs = setup_model_directories ([targetThetaX, targetThetaY], lumval);
+    [ eyeRyAvg, eyeRySD, eyeRyFinals ] = run_simulation_multi (model_dir, output_dirs, num_par_runs, use_insigneo, cleanup);
+
+    resname = ['r_' num2str(targetThetaX) '_' num2str(targetThetaY) '_' num2str(lumval) '.dat'];
+    resdatname = ['r_' num2str(targetThetaX) '_' num2str(targetThetaY) '_' num2str(lumval)];
+    resdatname = strrep (resdatname, '.', '_');
+
+    vs = [lumval, eyeRyAvg, eyeRySD];
+    result = struct();
+    result.(resdatname) = vs;
+
+    save (resname, 'result');
+
+end

### 2017-05-03 batch_scripts/expt_sacc_vs_luminance/testscript.m

@@ -1,0 +1,18 @@
+run_index = 6
+
+model_dir = '/home/pc1ssj/abrg_local/Oculomotor';
+thepath = ['/fastdata/pc1ssj/oculomotorRX0RY7_0.8_' num2str(run_index)];
+output_dirs = setup_model_directories ([0, 7], 0.8)
+peaktime = find_peaktime ([output_dirs.root '_' num2str(run_index)])
+
+A=load_ocm_min(thepath);
+
+endsacc_x = find_saccade_end (A.eyeRx, peaktime);
+endsacc_y = find_saccade_end (A.eyeRy, peaktime);
+endsacc = round((endsacc_x + endsacc_y) ./ 2)
+
+[allc_x, allc_y, alla, allb, sca, scd] = find_saccade_location (output_dirs, 1, [],[],[],[]);
+alla
+allb
+allc_x
+allc_y

### 2017-05-03 batch_scripts/expt_spatial_scatter/find_output_scatter.m

@@ -1,0 +1,22 @@
+function [eyeRyAvg, eyeRySD, eyeRyFinals] = find_output_scatter ...
+        (targetThetaX, targetThetaY, num_par_runs)
+%% Run the model n times for a given target
+%% and collect the output angle each time. Use run_simulation_multi()
+%%
+%% Author: Seb James.
+
+    page_screen_output(0);
+    page_output_immediately(1);
+    
+    % The input model. Hardcoded.
+    model_dir = '/home/pc1ssj/abrg_local/Oculomotor';
+    % Add a write-out of the luminances file:
+    write_single_luminance ([model_dir '/luminances.json'], ...
+                            targetThetaX, targetThetaY);
+    output_dirs = setup_model_directories ([targetThetaX, targetThetaY], 1);
+    cleanup = 1;
+    use_insigneo = 1;
+    [ eyeRyAvg, eyeRySD, eyeRyFinals ] = run_simulation_multi ...
+        (model_dir, output_dirs, num_par_runs, use_insigneo, cleanup);
+
+end

### 2017-05-03 batch_scripts/include/centroid_linear.m

@@ -1,0 +1,17 @@
+function [centroid_x, centroid_y, sigma_a] = centroid_linear (sheet)
+%% Find simple linear centroid. Neural sheet is expected to be 50x50. Resize
+%% if necessary before calling this function.
+
+    % Linear centroid computation
+    x = 1:50;
+    [Y X] = meshgrid(x,x);
+    %centroids = zeros(50,50);
+
+    sigma_r_dot_a_x = sum(sum(X.*sheet));
+    sigma_r_dot_a_y = sum(sum(Y.*sheet));
+    sigma_a = sum(sum(sheet));
+    centroid_x = sigma_r_dot_a_x./double(sigma_a);
+    centroid_y = sigma_r_dot_a_y./double(sigma_a);
+    %centroids(round(centroid_x), round(centroid_y)) = sigma_a;
+
+end % multicentroid_compute

### 2017-05-03 batch_scripts/include/find_latency.m

@@ -1,0 +1,30 @@
+function [eyeRyAvg, eyeRySD, eyeRyFinals, latency] = find_latency (params)
+%% Run the model num_par_runs times for a given targetThetaX/Y
+%% and collect the time to first eye movement each time.
+%% Investigate fixation-target overlaps/gaps by
+%% controlling the fixation_off and target_on parameters and
+%% dopamine level via the da_param argument.
+%%
+%% Author: Seb James.
+
+    page_screen_output(0);
+    page_output_immediately(1);
+
+    % Ranges: -22<=x<=-6 and 6<=x<=22 -22<=y<=-6 and 6<=y<=22
+
+    % The input model. Hardcoded.
+    model_dir = '/home/pc1ssj/abrg_local/Oculomotor';
+    % Add a write-out of the luminances file:
+    write_single_luminance_with_fix ([model_dir '/luminances.json'], params);
+    output_dirs = setup_model_directories ([params.targetThetaX, params.targetThetaY], 1);
+    [ eyeRyAvg, eyeRySD, eyeRyFinals, peakPos, startMove ] = ...
+        run_sim_multi_for_latency (model_dir, output_dirs, params.num_par_runs, ...
+                                   params.use_insigneo, params.cleanup, params.dopamine);
+
+    latency = startMove.-(1000.*params.targetOn);
+    lat_mean = mean(latency);
+    lat_std = std(latency);
+    display (['Latency mean: ' num2str(lat_mean) ' SD: ' num2str(lat_std) ...
+             ' Final angle mean: ' num2str(eyeRyAvg) ' SD: ' num2str(eyeRySD)]);
+
+end

### 2017-05-03 batch_scripts/include/find_peaktime.m

@@ -1,0 +1,34 @@
+% Find the time of the first peak in activity in the LLBNs. This
+% will be the time of the peak in activity in SCa/SCdeep. This
+% "time" is actually an index into the time series. At the
+% time of writing 1 timestep = 1 ms.
+%
+function peaktime = find_peaktime (basepath)
+    peaktime = -1;
+    [llbn_left, count] = load_sc_data ([basepath '/log/' ...
+                        'LLBN_left_a_log.bin'], 1);
+
+    % We expect the run to have 450 datapoints - 0.45 s runtime
+    % with 1 ms per step.
+    if count < 450
+        display (['Only ' num2str(count) ...
+                  ' data points, won''t search for peak.']);
+        return
+    end
+
+    if isempty(peaktime = min (find (llbn_left>0)))
+        [llbn_right, count] = load_sc_data ([basepath '/log/' ...
+                            'LLBN_right_a_log.bin'], 1);
+        if isempty(peaktime = min (find (llbn_right>0)))
+            [llbn_up, count] = load_sc_data ([basepath '/log/' ...
+                                'LLBN_up_a_log.bin'], 1);
+            if isempty(peaktime = min (find (llbn_up>0)))
+                
+                [llbn_down, count] = load_sc_data ([basepath '/log/' ...
+                                    'LLBN_down_a_log.bin'], 1);
+                peaktime = min (find (llbn_down>0));
+            end
+        end
+    end
+    display (['peaktime = ' num2str(peaktime)]);
+end

### 2017-05-03 batch_scripts/include/find_saccade_end.m

@@ -1,0 +1,38 @@
+%% Author: Seb James <seb@PSY0001622>
+%% Created: 2015-11-05
+%%
+%% Find the iterator at which the saccade ends based on the eye velocity.
+function [endsacc] = find_saccade_end (eyeR, peaktime)
+    
+    % Find end of first saccade. Note the use of abs() - we don't
+    % care which direction the saccade is in here.
+    deyeR = diff(abs(eyeR(peaktime:end)));
+    ddeyeR = diff(deyeR);
+
+    %figure(50);
+    %clf;
+    %plot (abs(eyeR(peaktime:end)), 'b');
+    %hold on;    
+    %plot (deyeR, 'r');
+    %plot (ddeyeR, 'g');
+    
+    % Start looking for the end of the saccade by finding the
+    % peak velocity of the first saccade:
+    max_vel_iter = min(find (ddeyeR < 0));
+                                       
+    % From this point, find the end, which is defined here as
+    % the point where the vel drops below 0.0182 of the peak
+    % vel. By this time, the position of the eye is fairly close to
+    % where it will be at t=inf - the extra drift being about 0.4
+    % degrees if the model runs to 1 second.
+    endsacc = min (find (deyeR(max_vel_iter:end)<(deyeR(max_vel_iter).*0.0182))) ...
+              + peaktime;
+
+    % Check endsacc. What if there is no place where it gets that small?
+    if (isempty(endsacc))
+        % Set endsacc to peaktime+1, which for this function means "failed".
+        endsacc = peaktime+1;
+    end
+
+    %final_eyeR = eyeR(endsacc)
+end

### 2017-05-03 batch_scripts/include/find_saccade_location.m

@@ -1,0 +1,50 @@
+function [allc_x, allc_y, alla, allb] = find_saccade_location ...
+        (output_dirs, run_number, allc_x, allc_y, alla, allb)
+    % Find out where a single saccade occurred. Return coordinates
+
+    % First we need to find out what time the saccade occurred. Do this by
+    % looking at the llbn neurons
+    peaktime = find_peaktime ([output_dirs.root '_' ...
+                        num2str(run_number)]); % the time of the "peak in the superior
+                                               % colliculus" in ms.
+
+    % We expect the run to have 450 datapoints - 0.45 s runtime
+    % with 1 ms per step.
+    if peaktime == -1 || peaktime == 0
+        display (['No peak.' ...
+                  'Returning saccade location vectors (alla, etc) unmodified']);
+        return
+    end
+
+    % ok, we have a peak time, now find location of the
+    % peak
+    [sca, count] = load_sc_data ([ output_dirs.root '_' ...
+                        num2str(run_number) '/log/' ...
+                        'SC_avg_out_log.bin'], 2500);
+    sca = reshape (sca, 50, 50, []);
+    %display (['find in sca for time ' num2str(peaktime)]);
+    [a,b] = find (sca(:,:,peaktime));
+    alla = [ alla, a ];
+    allb = [ allb, b ];
+
+    % How about centroid location of scd?
+    [scd, count] = load_sc_data ([output_dirs.root '_' ...
+                        num2str(run_number) '/log/SC_deep_out_log.bin'], 2500);
+    scd = reshape (scd, 50, 50, []);
+    m = find(max(max(scd(:,:,:)))<1)
+    % Of the above, the last one as you count up before it
+    % stops.
+    saturate = find (diff(m)>2) % should be 1x1
+    if isempty(saturate) == 0
+        saturate = saturate(1) - 1
+    else
+        saturate = 1
+    end
+    [c_x, c_y, sigma_a] = centroid_linear (scd(:,:, saturate));
+    c_x
+    c_y
+    % etc etc; do something with c_x and c_y
+    allc_x = [ allc_x, c_x ];
+    allc_y = [ allc_y, c_y ];
+
+end % function find_saccade_location

### 2017-05-03 batch_scripts/include/find_scd_mask.m

@@ -1,0 +1,47 @@
+function [peak, peak_centroid, mask, points] = find_scd_mask (scd_log_bin_path)
+
+    nfs = 50;
+    display (['scd_log_bin_path: ' scd_log_bin_path]);
+    [scd, count] = load_sc_data (scd_log_bin_path, 2500);
+    scd = reshape (scd, nfs, nfs, []);
+    % Find maxima in activity wrt time in scd:
+    scd_time = sum(sum(scd));
+    % Ignore first 100 ms
+    scd_time_shifted = scd_time(100:end);
+    peak_s = find (scd_time_shifted == max(scd_time_shifted));
+    if scd_time_shifted(peak_s) > 4
+        % Then this is a reasonably big peak.
+        display (['Large peak in scd at time ' num2str(100+peak_s)]);
+    else
+        display ('No peak in scd found!');
+        peak = 0;
+        peak_centroid = [0,0];
+        mask = [];
+        points = [];
+        return;
+    end
+    peak = peak_s + 100;
+    points = find (scd(:,:,peak) > 0.2);
+    % Create a mask for setting the weights
+    mask = zeros(nfs,nfs);
+    mask(points) = 1;
+    display (['Number of points in the mask: ' ...
+              num2str(size(points)(1))]);
+    
+    % Show the mask like this:
+    % figure(84);
+    % surf (mask)
+    % title (['Location of SC deep activity at time ' num2str(peak) 'ms']);
+
+    % Compute centroid
+    R = nchoosek(1:nfs,2);
+    % add on the mirrored locations... and the diagonal elements.
+    R = [R;R(:,[2 1]);[(1:nfs)' (1:nfs)']];
+    % sort so that it lines up with the data in scd.
+    [s,I] = sort(R(:,2));
+    R = R(I,:);
+    [s,I] = sort(R(:,1));
+    R = R(I,:);
+    peak_centroid = centroid (R, scd (:,:,peak));
+
+end

### 2017-05-03 batch_scripts/include/justdata.m

@@ -1,0 +1,20 @@
+function [ map, means, cols ] = justdata (allweights, direction_identifier)
+    selected_rows = find (allweights(:,1) == direction_identifier);
+    means = [];
+    map = nan(50);
+    tlist = allweights(selected_rows,4:6);
+    for i = tlist'
+        if isnan(map(i(1),i(2)))
+            % Find all points in tlist which have the same x/y coords and
+            % compute a mean (there may only be 1):
+            i1 = find (tlist(:,1)==i(1));
+            i2 = find (tlist(:,2)==i(2));
+            points = intersect (i1,i2);
+            mp = mean(tlist(points,:), 1);
+            % Write the mean value into e54map
+            map(i(1),i(2)) = mp(3);
+            means = [means; i(1), i(2), mp(3)];
+        end
+    end
+    cols = allweights(selected_rows,4:6);
+end

### 2017-05-03 batch_scripts/include/make_param.m

@@ -1,0 +1,6 @@
+function [param, paramiter, randomvalue] = make_param (param_min, param_max, numpoints)
+    pointsize = (param_max - param_min) ./ numpoints;
+    param = [param_min:pointsize:param_max-pointsize];
+    paramiter = ceil(unifrnd(0,numpoints));
+    randomvalue = param(paramiter);
+end

### 2017-05-03 batch_scripts/include/octave_run_test.m

@@ -1,0 +1,1 @@
+display("Testing if Octave runs on this host.");

### 2017-05-03 batch_scripts/include/pixtophidegrees.m

@@ -1,0 +1,19 @@
+% matlab version of the retmap function in RetinotopicMapping.ipynb
+function phideg = pixtophidegrees (phipix)
+    % Here's the mapping from retinotopic radial component (r) and
+    % angular component (phi) to the eyeframe map thetaX/thetaY
+    % (rotation _about_ x and y axes)
+
+    E2 = 2.5; % radial angle at which neural density has halved 
+    nfs = 50; % 50x50 grid.
+    fieldOfView = 61; % 0 and +/- 30 degrees
+    % The Magnification factor
+    Mf = nfs./(E2.*log(((fieldOfView./2)./E2)+1));
+
+    % Produces output which gives us 0=U,90=L,180=D,270=R
+    phideg = (phipix.*360./nfs);
+    
+    %phideg = (phipix.*360./nfs)+90;
+    %indices = find(phideg > 360);
+    %phideg(indices) = phideg(indices)-360;
+end

### 2017-05-03 batch_scripts/include/pixtordegrees.m

@@ -1,0 +1,14 @@
+% Convert from the 1:50 pixel version of retinotopic radius to degrees.
+function [rdeg] = pixtordegrees (rpix)
+    % Here's the mapping from retinotopic radial component (r) and
+    % angular component (phi) to the eyeframe map thetaX/thetaY
+    % (rotation _about_ x and y axes)
+
+    E2 = 2.5; % radial angle at which neural density has halved 
+    nfs = 50; % 50x50 grid.
+    fieldOfView = 61; % 0 and +/- 30 degrees
+    % The Magnification factor
+    Mf = nfs./(E2.*log(((fieldOfView./2)./E2)+1));
+
+    rdeg = E2.*(-1+exp(rpix./(Mf.*E2)));
+end

### 2017-05-03 batch_scripts/include/rotations_report.m

@@ -1,0 +1,12 @@
+function rotations_report (dbgfile, lastangle, eyeRyAvg, eyeRySD, lasterror, error, reallylastweight, lastweight, weight, dedw)
+
+    printf (['RR: last_angle: %f cur_angle: %f (sd %f) last_error: %f cur_error: %f last_weight: %f ' ...
+             'cur_weight: %f next_weight: %f dedw:' ...
+             ' %f\n'], lastangle, eyeRyAvg, eyeRySD, lasterror, error, ...
+            reallylastweight, lastweight, weight, dedw);
+
+    fprintf (dbgfile, ['last_angle: %f cur_angle: %f (sd %f) last_error: %f cur_error: %f last_weight: %f ' ...
+                       'cur_weight: %f next_weight: %f dedw:' ...
+                       ' %f\n'], lastangle, eyeRyAvg, eyeRySD, lasterror, error, ...
+             reallylastweight, lastweight, weight, dedw);
+end

### 2017-05-03 batch_scripts/include/run_simulation_multi.m

@@ -1,0 +1,251 @@
+function [ eyeposAvg, eyeposSD, eyeposFinals, peakPos ] = run_simulation_multi ...
+        (model_dir, output_dirs, num_runs, insigneo, cleanup)
+%% Run a simulation specified in model_dir, sending results to
+%% output_dirs.root num_runs times. Do this by submitting using the
+%% qsub system and use calls to Qstat to determine when the runs
+%% have completed. Return the mean and sd of the result (at time of
+%% writing, this is the final rotation around the y axis of the
+%% biomechanical eye model). Note: Application, model and
+%% seb-specific code.
+
+    if ~exist (model_dir, 'dir')
+        display ('Uh oh - model directory doesn''t exist!');
+        return
+    end
+
+    tag = {};
+    for i = 1:num_runs
+
+        tag{i} = ['r' num2str(i-1) '_' num2str(round(rand * ...
+                                                   999999))];
+        display(['Starting sim run ' tag{i} ' in output dir: ' output_dirs.root '_' num2str(i)]);
+        scriptname=['/fastdata/pc1ssj/' tag{i} '_run_sim.sh'];
+        script=['pushd /home/pc1ssj/SpineML_2_BRAHMS && ./convert_script_s2b -g ' ...
+                '-p "Mirror to FEF Synapse 0 postsynapse:w:0" -p "FEF_add_noise to FEF Synapse 0 postsynapse:w:1" ' ...
+                '-m ' model_dir ' -e2 -o ' output_dirs.root '_' num2str(i) ' && popd'];
+
+        fid = fopen (scriptname, 'w');
+        fprintf (fid, '#!/bin/sh\n%s\n', script);
+        fclose (fid);
+
+        % For requests for two processors, use -pe openmp 2 and
+        % change mem to 1G (so that you get 1G * 2 = 2G per job)
+        
+        % Insigneo version
+        if insigneo
+            cmd=['mkdir -p ' output_dirs.qlog '_' num2str(i) ' && ' ...
+                 'qsub -o '  output_dirs.qlog '_' num2str(i) ...
+                 '/qsub.out -m a -M seb.james@sheffield.ac.uk ' ...
+                 '-j y -l mem=2G -l rmem=2G -l arch=intel* ' ...
+                 '-P insigneo-notremor ' scriptname];
+        else
+            % General submission:
+            cmd=['mkdir -p ' output_dirs.qlog '_' num2str(i) ' && ' ...
[…]

### 2017-05-03 batch_scripts/include/run_simulation_serial.m

@@ -1,0 +1,65 @@
+function [ eyeRyAvg, eyeRySD, eyeRyFinals ] = run_simulation_serial ...
+        (model_dir, output_dirs, num_runs)
+%% Run a simulation specified in model_dir, sending results to
+%% output_dirs.root num_runs times.
+%%
+%% This differs from run_simulation_multi.m in that it runs the
+%% sims in serial rather than using qsub to run them in parallel. I
+%% did this because it means I don't have to implement multiple
+%% concurrent connections to the networkserver
+%%
+%% Return the mean and sd of the result (at time of
+%% writing, this is the final rotation around the y axis of the
+%% biomechanical eye model). Note: Application, model and
+%% seb-specific code.
+
+    if ~exist (model_dir, 'dir')
+        display ('Uh oh - model directory doesn''t exist!');
+        return
+    end
+    
+    tag = {};
+    for i = 1:num_runs
+
+        tag{i} = ['r' num2str(i-1) '_' num2str(round(rand * ...
+                                                   999999))];
+        display(['Starting sim run ' tag{i}]);
+        scriptname=['/fastdata/pc1ssj/' tag{i} '_run_sim.sh'];
+        script=['pushd /home/pc1ssj/SpineML_2_BRAHMS && ./convert_script_s2b  ' ...
+                '-p "Mirror to FEF Synapse 0 postsynapse:w:0" ' ...
+                '-p "FEF_add_noise to FEF Synapse 0 postsynapse:w:1" ' ...
+                '-m ' model_dir ' -e3 -o ' output_dirs.root '_' num2str(i) ' && popd'];
+
+        fid = fopen (scriptname, "w");
+        fprintf (fid, '#!/bin/sh\n%s\n', script);
+        fclose (fid);
+
+        % Now execute the script "scriptname"
+        cmd = [ 'bash ' scriptname ];
+        [status, output] = system (cmd);
+    
+        pause (3);
+    end
+
+    % Clean up the run scripts
+    display ('Clean up run scripts...');
+    for i = 1:num_runs
+        scriptname=['/fastdata/pc1ssj/' tag{i} '_run_sim.sh'];
+        unlink (scriptname);
+    end
+
+    display ('Read output...');
+    eyeRyFinals = [];
+    for i = 1:num_runs        
+        % Eye rotations
[…]

### 2017-05-03 batch_scripts/include/setup_latency_directories.m

@@ -1,0 +1,20 @@
+function directories = setup_latency_directories (params, counter)
+
+    output_dir = ['/fastdata/pc1ssj/oculomotorRX' ...
+                  num2str(params.targetThetaX) 'RY' num2str(params.targetThetaY) ...
+                  '_F' num2str(params.fixOff) '_T' num2str(params.targetOn) ...
+                  '_D' num2str(params.dopamine) '_' num2str(counter)];
+    qlog_dir = output_dir;
+    
+    output_model_dir = [output_dir '/model'];
+    output_run_dir = [output_dir '/run/'];
+    output_log_dir = [output_dir '/log/'];
+
+    directories = struct ('root', output_dir, ...
+                          'qlog', qlog_dir, ...
+                          'model', output_model_dir, ...
+                          'run', output_run_dir, ...
+                          'log', output_log_dir ...
+                          );
+    
+end

### 2017-05-03 batch_scripts/include/setup_model_directories.m

@@ -1,0 +1,26 @@
+function directories = setup_model_directories (targetTheta, counter, parcount)
+
+    % Our output dir has to be on fastdata, because we submit the job
+    % to run somewhere else and then on the node we submitted the
+    % job from we'll consume the output, hence it has to be a
+    % shared directory, even though /scratch may be faster.
+    output_dir = ['/fastdata/pc1ssj/oculomotorRX' ...
+                  num2str(targetTheta(1)) 'RY' num2str(targetTheta(2)) ...
+                  '_' num2str(counter)];
+    % qlog dir has to be accessible from all nodes:
+    qlog_dir = ['/fastdata/pc1ssj/oculomotorRX' ...
+                num2str(targetTheta(1)) 'RY' num2str(targetTheta(2)) ...
+                '_' num2str(counter)];
+    
+    output_model_dir = [output_dir '/model'];
+    output_run_dir = [output_dir '/run/'];
+    output_log_dir = [output_dir '/log/'];
+
+    directories = struct ('root', output_dir, ...
+                          'qlog', qlog_dir, ...
+                          'model', output_model_dir, ...
+                          'run', output_run_dir, ...
+                          'log', output_log_dir ...
+    );
+    
+end

### 2017-05-03 batch_scripts/include/setup_model_output_directories.m

@@ -1,0 +1,15 @@
+function directories = setup_model_output_directories (out_dir_prefix)
+%% An improvement of setup_model_directories with an additional argument.
+    
+    output_dir = ['/fastdata/pc1ssj/' out_dir_prefix];
+    output_model_dir = [output_dir '/model'];
+    output_run_dir = [output_dir '/run/'];
+    output_log_dir = [output_dir '/log/'];
+
+    directories = struct ('root', output_dir, ...
+                          'model', output_model_dir, ...
+                          'run', output_run_dir, ...
+                          'log', output_log_dir ...
+    );
+    
+end

### 2017-05-03 batch_scripts/include/shiftiter.m

@@ -1,0 +1,8 @@
+function new_iter = shiftiter (current_iter, iter_shift, range_size)
+    new_iter = current_iter + iter_shift;
+    if new_iter < 1
+        new_iter = 1;
+    elseif new_iter > range_size
+        new_iter = range_size;
+    end
+end

### 2017-05-03 batch_scripts/include/subaxis.m

@@ -1,0 +1,278 @@
+function h=subaxis(varargin)
+%SUBAXIS Create axes in tiled positions. (just like subplot)
+%   Usage:
+%      h=subaxis(rows,cols,cellno[,settings])
+%      h=subaxis(rows,cols,cellx,celly[,settings])
+%      h=subaxis(rows,cols,cellx,celly,spanx,spany[,settings])
+%
+% SETTINGS: Spacing,SpacingHoriz,SpacingVert
+%           Padding,PaddingRight,PaddingLeft,PaddingTop,PaddingBottom
+%           Margin,MarginRight,MarginLeft,MarginTop,MarginBottom
+%           Holdaxis
+%
+%           all units are relative (i.e. from 0 to 1)
+%
+%           Abbreviations of parameters can be used.. (Eg MR instead of MarginRight)
+%           (holdaxis means that it wont delete any axes below.)
+%
+%
+% Example:
+%
+%   >> subaxis(2,1,1,'SpacingVert',0,'MR',0); 
+%   >> imagesc(magic(3))
+%   >> subaxis(2,'p',.02);
+%   >> imagesc(magic(4))
+%
+% 2001-2014 / Aslak Grinsted  (Feel free to modify this code.)
+
+    isOctave = exist('OCTAVE_VERSION', 'builtin') ~= 0;
+    
+    f=gcf;
+
+    UserDataArgsOK=0;
+    Args=get(f,'UserData');
+    if isstruct(Args) 
+        UserDataArgsOK=isfield(Args,'SpacingHorizontal')&isfield(Args,'Holdaxis')&isfield(Args,'rows')&isfield(Args,'cols');
+    end
+    OKToStoreArgs=isempty(Args)|UserDataArgsOK;
+
+    if isempty(Args)&&(~UserDataArgsOK)
+        Args=struct('Holdaxis',0, ...
+                    'SpacingVertical',0.05,'SpacingHorizontal',0.05, ...
+                    'PaddingLeft',0,'PaddingRight',0,'PaddingTop',0,'PaddingBottom',0, ...
+                    'MarginLeft',.1,'MarginRight',.1,'MarginTop',.1,'MarginBottom',.1, ...
+                    'rows',[],'cols',[]); 
+    end
+    Args=parseArgs(varargin,Args,{'Holdaxis'},{'Spacing' {'sh','sv'}; 'Padding' {'pl','pr','pt','pb'}; 'Margin' {'ml','mr','mt','mb'}});
+
[…]

### 2017-05-03 batch_scripts/include/weight_surface_one.m

@@ -1,0 +1,12 @@
+function ret = weight_surface_one (r,theta,a,k,b,l,os,wg)
+% os is an offset - the location of a peak of the cosine. wg is a
+% "gain on the width of the cosine".
+    
+    ret = [];
+    sz = size(a)(2);
+    for i = 1:sz
+        one = (a(i) .* exp(k(i).*r) .- b(i) .* exp(l(i).*r)) ...
+              .* cos (2.*pi .* (wg(i).*(theta-os(i))./50));
+        ret(:,:,i) = one;
+    end
+end

### 2017-05-03 batch_scripts/include/write_mirrored_luminances_with_fix.m

@@ -1,0 +1,31 @@
+% Like write_single_luminance but with a fixation point and writes
+% two luminances mirrored over the central meridian.
+function success = write_mirrored_luminances_with_fix (file_path, params)
+    lum_file = fopen (file_path, 'w');
+    if lum_file == -1
+        display ('Failed to open luminances.json file for writing.');
+        success = 0;
+        return
+    end
+    fprintf (lum_file, ['{"luminances":[' ...
+                        '{"shape":"square","thetaX":0,' ...
+                        '"thetaY":0,"widthThetaX":%d,"widthThetaY":%d,' ...
+                        '"luminance":%f,"timeOn":%f,"timeOff":%f},' ...
+                        '{"shape":"square","thetaX":%d,' ...
+                        '"thetaY":%d,"widthThetaX":%d,"widthThetaY":%d,' ...
+                        '"luminance":%f,"timeOn":%f,"timeOff":%f}, ' ...
+                        '{"shape":"square","thetaX":%d,' ...
+                        '"thetaY":%d,"widthThetaX":%d,"widthThetaY":%d,' ...
+                        '"luminance":%f,"timeOn":%f,"timeOff":%f} ' ...
+                        ']}'], ...
+             params.fixWidthX, params.fixWidthY, ...
+             params.fixLuminance, params.fixOn, params.fixOff, ...
+             params.targetThetaX, params.targetThetaY, ...
+             params.targetWidthX, params.targetWidthY, ...
+             params.targetLuminance, params.targetOn, params.targetOff, ...
+             params.targetThetaX, -params.targetThetaY, ...
+             params.targetWidthX, params.targetWidthY, ...
+             (0.8.*params.targetLuminance), params.targetOn, params.targetOff);
+    fclose (lum_file);
+    success = 1;
+end

### 2017-05-03 batch_scripts/include/write_onedim_binary.m

@@ -1,0 +1,35 @@
+% Write out a line of weights into an explicitDataBinaryFile, so
+% that the model can be trained.
+
+% The weights are output along indices 37 and 38.
+
+% The input to this script is the filepath of the target binary
+% file.
+function write_onedim_binary (file_path, singleval)
+
+    d = zeros (50, 50);
+    x = 1:50;
+    fov_dist_offset = 12;
+    sigmoid_narrowness = -4;
+    % Sigmoid to dampen down weights around fovea:
+    line = (1./(1 + exp(sigmoid_narrowness.*(x.-fov_dist_offset)))).*singleval;
+
+    d (37, :) = line;
+    d (38, :) = line;
+
+    d = reshape (d, 2500, 1, []);
+
+    [fid, errmsg] = fopen (file_path, 'w');
+    if fid == -1
+        display (errmsg);
+        return
+    end
+
+    for i = 0:2499
+        fwrite (fid, i, 'int32');
+        fwrite (fid, d(i+1), 'double');    
+    end
+
+    fclose (fid);
+
+end

### 2017-05-03 batch_scripts/include/write_plane_weights.m

@@ -1,0 +1,36 @@
+% Write out a line of weights into an explicitDataBinaryFile, so
+% that the model can be trained.
+
+% The weights are output on every point of the map, but attenuated
+% around the fovea.
+
+% The input to this script is the filepath of the target binary
+% file.
+function write_plane_weights (file_path, singleval)
+
+    d = zeros (50, 50);
+    x = 1:50;
+    fov_dist_offset = 12;
+    sigmoid_narrowness = -4;
+    % Sigmoid to dampen down weights around fovea:
+    line = (1./(1 + exp(sigmoid_narrowness.*(x.-fov_dist_offset)))).*singleval;
+
+    % Replicate line 50 times vertically, 1 times horizontally.
+    d = repmat (line, 50, 1);
+
+    d = reshape (d, 2500, 1, []);
+
+    [fid, errmsg] = fopen (file_path, 'w');
+    if fid == -1
+        display (errmsg);
+        return
+    end
+
+    for i = 0:2499
+        fwrite (fid, i, 'int32');
+        fwrite (fid, d(i+1), 'double');
+    end
+
+    fclose (fid);
+
+end

### 2017-05-03 batch_scripts/include/write_single_luminance_with_fix.m

@@ -1,0 +1,24 @@
+% Like write_single_luminance but with a fixation point
+% too. Fixation from 0 until fix_off_time. Target appears at targ_on_time.
+function success = write_single_luminance_with_fix (file_path, params)
+    lum_file = fopen (file_path, 'w');
+    if lum_file == -1
+        display ('Failed to open luminances.json file for writing.');
+        success = 0;
+        return
+    end
+    fprintf (lum_file, ['{"luminances":[' ...
+                        '{"shape":"square","thetaX":0,' ...
+                        '"thetaY":0,"widthThetaX":%d,"widthThetaY":%d,' ...
+                        '"luminance":%f,"timeOn":%f,"timeOff":%f},' ...
+                        '{"shape":"square","thetaX":%d,' ...
+                        '"thetaY":%d,"widthThetaX":%d,"widthThetaY":%d,' ...
+                        '"luminance":%f,"timeOn":%f,"timeOff":%f}]}'], ...
+             params.fixWidthX, params.fixWidthY, ...
+             params.fixLuminance, params.fixOn, params.fixOff, ...
+             params.targetThetaX, params.targetThetaY, ...
+             params.targetWidthX, params.targetWidthY, ...
+             params.targetLuminance, params.targetOn, params.targetOff);
+    fclose (lum_file);
+    success = 1;
+end

### 2017-05-03 batch_scripts/weight_finding/rotations_weight_finder_centroid_3d.m

@@ -1,0 +1,377 @@
+function [bestweight, lastangle] = rotations_weight_finder_centroid_3d (targetTheta,weight,num_runs,insigneo,cleanup)
+%% Explore the parameter space of SCdeep -> LLBN collicular mapping
+%% weight for a single target saccade.
+%%
+%% This expects the oculomotor model to be tuned to saccade to a stable
+%% final rotation for a single stimulus. It then records a rotation
+%% error: (finalAngle - targetAngle).
+%%
+%% This aims to calculate the best weight for a given
+%% targetThetaX/targetThetaY - it will carry out a gradient descent
+%% algorithm to find two weights for any target saccade.
+%%
+%% It also aims to train rotational weights to keep RotZ to a value
+%% 0 (noting that this may not fulfil Listing's Law).
+%%
+%% targetTheta is a row vector containing
+%% [targetThetaX,targetThetaY]. weight is row vector containing
+%% [initialWeightX,initialWeightY].
+%%
+%% Recall that targetThetaX is a rotation ABOUT the x axis.
+%%
+%% This version of the script is intended to be run on the centroid
+%% output of SC_avg
+%%
+%% Author: Seb James.
+
+    addpath ('./include');
+
+    % A script parameter - passed to run_simulation_multi(). Reduce
+    % when testing. 10 is typical for real work; 4 for testing.
+    % num_runs = 4;
+
+    % To get stdout scrolling past while this runs:
+    page_screen_output(0);
+    page_output_immediately(1);
+
+    explicitDataBinaryFileLEFT = '/explicitDataBinaryFile50.bin';
+    edbfNumLEFT = 50;
+    explicitDataBinaryFileRIGHT = '/explicitDataBinaryFile52.bin';
+    edbfNumRIGHT = 52;
+    explicitDataBinaryFileUP = '/explicitDataBinaryFile53.bin';
+    edbfNumUP = 53;
+    explicitDataBinaryFileDOWN = '/explicitDataBinaryFile54.bin';
+    edbfNumDOWN = 54;
+    explicitDataBinaryFileZPLUS = '/explicitDataBinaryFile58.bin';
+    edbfNumZPLUS = 58;
+    explicitDataBinaryFileZMINUS = '/explicitDataBinaryFile57.bin';
+    edbfNumZMINUS = 57;
+
+    %weightsBinaryFile to be set here:
+
+    display(['targetTheta: ' num2str(targetTheta)]);
+
[…]

### 2017-05-03 batch_scripts/weight_finding/rotations_weight_finder_hump_average.m

@@ -1,0 +1,277 @@
+function [bestweight, lastangle] = rotations_weight_finder_hump_average (targetThetaY,weight)
+%% Explore the parameter space of SCdeep -> LLBN collicular mapping
+%% weight for a single target saccade.
+%%
+%% This expects the oculomotor model to be tuned to saccade to a stable
+%% final rotation for a single stimulus. It then records a rotation
+%% error: (finalAngle - targetAngle).
+%%
+%% This aims to calculate the best weight for a given
+%% targetThetaY. Other versions of this script could be used to obtain
+%% the other collicular weight maps, but this is the first one.
+%%
+%% This version of the script (compare it with rotations_weight_finder.m)
+%% will find the location of the hump of activity in SC deep, and
+%% will determine weights for that "disc" of activity. THis will be
+%% the approach to take when calculating weights across the surface
+%% in 2-D, however, for now, this is still a 1-D finder.
+%%
+%% Author: Seb James.
+
+    addpath ('./include');
+    
+    % To get stdout scrolling past while this runs:
+    page_screen_output(0);
+    page_output_immediately(1);
+    
+    weightsBinaryFile = '/explicitDataBinaryFile51.bin';
+    exploratory_weight = 0.3 % This will need changing depending on
+                             % b in LLBN popn.
+    
+    dbgfile = fopen (['/fastdata/pc1ssj/dbgT' num2str(targetThetaY) ...
+                      '.log'], 'w');
+
+    %weight = 0.16; % starting weight. Hard coded.
+    error_threshold = 0.1; % This should be larger than the scatter
+                           % in the output angle for repeat runs for
+                           % the same weight. About 0.1 is good?
+
+    first_weight_step = 0.1; % Not really used.
+
+    learning_rate = 0.7;
+    default_dedw = 70;
+    
+    nfs = 50; % neural field size.
+    % The input model. Hardcoded.
+    orig_model_dir = '/home/pc1ssj/abrg_local/Oculomotor';
+    % This codes makes a copy here:
+    model_dir = '/fastdata/pc1ssj/input_models/';
+    cmd = ['mkdir -p ' model_dir];
+    system (cmd);
+    model_dir = [model_dir 'OculomotorT' num2str(targetThetaY)];
+    cmd = ['rm -rf ' model_dir];
+    system (cmd);
+    cmd = ['cp -Ra ' orig_model_dir ' ' model_dir];
+    system (cmd);
+    
[…]

### 2017-05-03 batch_scripts/weight_finding/run_model_for_single_weight.m

@@ -1,0 +1,43 @@
+addpath ('./include');
+
+targetThetaY = -10;
+weight = 0.47;
+
+insigneo = 1; % Use insigneo server
+num_parallel = 8; % How many times to run
+
+% The input model. Hardcoded.
+orig_model_dir = '/home/pc1ssj/abrg_local/Oculomotor';
+% This codes makes a copy here:
+model_dir = '/fastdata/pc1ssj/input_models/';
+cmd = ['mkdir -p ' model_dir];
+system (cmd);
+model_dir = [model_dir 'OculomotorT' num2str(targetThetaY)];
+cmd = ['rm -rf ' model_dir];
+system (cmd);
+cmd = ['cp -Ra ' orig_model_dir ' ' model_dir];
+system (cmd);
+
+% Write luminances.json into model dir:
+if (write_single_luminance ([model_dir '/luminances.json'], ...
+                            targetThetaY)) < 1
+    return
+end
+
+counter = 1;
+output_dirs = setup_model_directories (targetThetaY, counter);
+
+if targetThetaY < 0
+    % Saccade to right
+    weightsBinaryFile = '/explicitDataBinaryFile53.bin';
+else
+    % Saccade to left
+    weightsBinaryFile = '/explicitDataBinaryFile52.bin';
+end
+
+% With centroids we can always write a plane weight.
+write_plane_weights ([model_dir weightsBinaryFile], weight);
+
+display ('Running...');
+[ eyeRyAvg, eyeRySD ] = run_simulation_multi (model_dir, ...
+                                              output_dirs, num_parallel, insigneo);

### 2017-05-03 batch_scripts/weight_finding/run_weight_finding_3d_list.sh

@@ -1,0 +1,49 @@
+#!/bin/sh
+#$ -l mem=1G
+#$ -l rmem=1G
+#$ -l h_rt=127:59:00
+#$ -m ae
+#$ -M seb.james@sheffield.ac.uk
+
+# Things to check before running:
+# Is the luminance file correctly written out?
+# Are there any extra params to go in the convert_script_s2b call in run_simulation_multi.m?
+# Is the correct explicitDataBinaryFileN.bin being written into?
+
+# Simultaneously run the weight finding algorithm for all the eccentricities of interest:
+
+PARENT_LIMIT=28
+
+MIN_RAD=6
+MAX_RAD=22.5
+
+echo "$0 - Theta X range: list; Theta Y range: list" >> ~/fast/allweights.log
+echo "explicitDataBinaryFileN.bin: L:50 R:52 U:53 D:54 Z+:58 Z-:57" >> ~/fast/allweights.log
+echo -n "Start date: "
+date >> ~/fast/allweights.log
+
+#RX-15RY6 etc etc. Create this list with find_missing.sh
[…]

### 2017-05-03 batch_scripts/weight_finding/run_weight_finding_3d_many.sh

@@ -1,0 +1,65 @@
+#!/bin/sh
+#$ -l mem=1G
+#$ -l rmem=1G
+#$ -l h_rt=127:59:00
+#$ -m ae
+#$ -M seb.james@sheffield.ac.uk
+
+# Things to check before running:
+# Is the luminance file correctly written out?
+# Are there any extra params to go in the convert_script_s2b call in run_simulation_multi.m?
+# Is the correct explicitDataBinaryFileN.bin being written into?
+
+# Simultaneously run the weight finding algorithm for all the eccentricities of interest:
+
+XSTART=-22
+XEND=22
+YSTART=-22
+YEND=22
+
+PARENT_LIMIT=28
+
+MIN_RAD=6 # Can be down to 6
+MAX_RAD=22.5
+
+echo "$0 - Theta X range: ${XSTART} to ${XEND}; Theta Y range:  ${YSTART} to ${YEND}" >> ~/fast/allweights.log
+echo "explicitDataBinaryFileN.bin: L:50 R:52 U:53 D:54 Z+:58 Z-:57" >> ~/fast/allweights.log
+echo -n "Start date: "
+date >> ~/fast/allweights.log
+echo "Cols: weights file, axis, target angles (x/y/z), peakposn1, peakposn2, bestweight, meanpeakposn1, meanpeakposn2, eyeposAvg(SD) (x/y/z)." >> ~/fast/allweights.log
+
+# I'm going to have to add jobs and monitor them and keep only about
+# PARENT_LIMIT of these jobs running at once, otherwise I'll run out
+# of available hosts to run the "worker" jobs (those which actually
+# run the simulation).
+for i in `seq ${XSTART} ${XEND}`; do
+
+    for j in `seq ${YSTART} ${YEND}`; do
+
+        # Avoid the central region. Calculate distance to centre
+        d_lt=`echo "scale=10;sqrt(${i}*${i}+${j}*${j})<$MIN_RAD"|bc`
+        d_gt=`echo "scale=10;sqrt(${i}*${i}+${j}*${j})>$MAX_RAD"|bc`
+        if [ $d_lt -gt 0 ]; then
+            echo "Omit Theta X = $i, Theta Y = $j (within $MIN_RAD deg)"
+            continue
+        fi
+        if [ $d_gt -gt 0 ]; then
+            echo "Omit Theta X = $i, Theta Y = $j (outside $MAX_RAD deg)"
+            continue
+        fi
[…]

### 2017-05-03 batch_scripts/weight_finding/startweights.m

@@ -1,0 +1,67 @@
+function startweights (thetax, thetay, map_path)
+
+    addpath ('analysis');
+    addpath ('analysis/include');
+    addpath ('include');
+    
+    xweight = 0;
+    yweight = 0;
+    zweight = 0;
+    
+    % Problem with this scheme - r and phi within the model are
+    % skewed away from r and phi from the pure geometry. This is ok
+    % within the context of the model running, but it makes this
+    % conversion less useful.
+    %
+    % A solution to this would be to take the data directly from
+    % allweights.log, for which I will need to have the
+    % thetax/thetay data in each row of allweights.log. I hadn't
+    % implemented that with the 201509_RotZ runs, so this'll have
+    % to wait.
+    [ r, phi ] = mapret (thetax, thetay);
+    r = ceil (r)
+    phi = floor (phi)
+    
+    
+    % Load up the data
+    e50 = load_neural_sheet ([map_path '/explicitDataBinaryFile50.bin']);
+    e52 = load_neural_sheet ([map_path '/explicitDataBinaryFile52.bin']);
+    e53 = load_neural_sheet ([map_path '/explicitDataBinaryFile53.bin']);
+    e54 = load_neural_sheet ([map_path '/explicitDataBinaryFile54.bin']);
+    e57 = load_neural_sheet ([map_path '/explicitDataBinaryFile57.bin']);
+    e58 = load_neural_sheet ([map_path '/explicitDataBinaryFile58.bin']);
+    
+    e50 = reshape (e50, 50, 50, []);
+    e52 = reshape (e52, 50, 50, []);
+    e53 = reshape (e53, 50, 50, []);
+    e54 = reshape (e54, 50, 50, []);
+    e57 = reshape (e57, 50, 50, []);
+    e58 = reshape (e58, 50, 50, []);
+    
+    
+    if thetax >= 0 && thetay >= 0
+        % Up and left; e53 and e50
+        xweight = e53(phi,r);
+        figure(53); surf (e53); zlim([0,2]);
+        zweight = e58(phi,r);
+        yweight = e50(phi,r);
+        figure(50); surf (e50); zlim([0,2]);
+    elseif thetax >= 0 && thetay < 0
+        % Up and right; e53 and e52
+        xweight = e53(phi,r);
+        zweight = e58(phi,r);
+        yweight = e52(phi,r);
+    elseif thetax < 0 && theta y >= 0
+        % Down and left; e54 and e50
[…]

### 2017-05-03 batch_scripts/weight_proving/run_weight_proof.sh

@@ -1,0 +1,44 @@
+#!/bin/sh
+#$ -l mem=4G
+#$ -l rmem=4G
+#$ -l h_rt=4:59:00
+#$ -m ae
+#$ -M seb.james@sheffield.ac.uk
+
+if [ -z "$2" ]; then
+	echo "ThetaX/ThetaY please"
+	exit -1
+fi
+
+THETAX="$1"
+THETAY="$2"
+
+INSIGNEO=1
+CLEANUP=1
+NUM_RUNS=8
+
+# Things to check before running:
+# Is the luminance file correctly written out?
+# Are there any extra params to go in the convert_script_s2b call in run_simulation_multi.m?
+# Is the correct explicitDataBinaryFileN.bin being written into?
+
+pushd /home/pc1ssj/abrg_local/Oculomotor/batch_scripts
+
+/home/pc1ssj/usr/bin/octave -q --eval "octave_run_test"
+oct_run_rtn=$?
+if [ $oct_run_rtn -gt "0" ]; then
+    echo "Failed to run Octave on this host, exiting."
+    popd
+    exit 1
+fi
+
+# Get startweight from the weight maps. First load the maps, then
+# consider which quadrant we're in, then select the weight from the
+# relevant maps.
+## STARTWEIGHTS=`/home/pc1ssj/usr/bin/octave -q --eval "startweights(${THETAX},${THETAY},'/home/pc1ssj/abrg_local/Oculomotor/lab_book/201509_Combined_RotZ_Training')"`
+
+/home/pc1ssj/usr/bin/octave -q --eval \
+ "rotations_weight_prover([${THETAX},${THETAY},0],${NUM_RUNS},${INSIGNEO},${CLEANUP})"
+popd
+
+exit 0

### 2017-05-03 c++/centroid.cpp

@@ -1,0 +1,219 @@
+/*
+ * A C++ Brahms component for the Oculomotor model - this one computes
+ * a centroid.
+ *
+ * Author: Seb James.
+ * Date: March 2015.
+ */
+
+#define COMPONENT_CLASS_STRING "dev/NoTremor/centroid"
+#define COMPONENT_CLASS_CPP dev_notremor_centroid_0
+#define COMPONENT_RELEASE 0
+#define COMPONENT_REVISION 1
+#define COMPONENT_ADDITIONAL "Author=Seb James\n" "URL=Not supplied\n"
+#define COMPONENT_FLAGS (F_NOT_RATE_CHANGER)
+
+#define OVERLAY_QUICKSTART_PROCESS
+
+#include <brahms-1199.h>
+#include <iostream>
+#include <math.h>
+#include <vector>
+#include <stdlib.h>
+
+// Marsaglia and Tsang RNG algorithm (copied in from SpineML_2_BRAHMS,
+// also found in brahms itself, but not in the form I prefer)
+#include "rng.h"
+
+#ifdef __WIN__
+// Windows specific includes/apologies here.
+#else
+// Linux specific includes here.
+#endif
+
+namespace numeric = std_2009_data_numeric_0;
+using namespace std;
+using namespace brahms;
+
+/*!
+ * This is our Brahms component class declaration.
+ */
+class COMPONENT_CLASS_CPP : public Process
+{
+public:
+    COMPONENT_CLASS_CPP() {}
+    ~COMPONENT_CLASS_CPP() {}
+
+    /*!
+     * The framework event function
+     */
+    Symbol event (Event* event);
+
+private:
+
+    /*!
+     * Output port. Connects to a passthrough population in the model
+     * "SC_output"
+     */
+    numeric::Output centroid;
+
+    /*!
+     * Input - this will be the input from the SC deep population.
+     */
+    //@{
+    numeric::Input inputSheet;
+
+    /*!
+     * A sheet of neurons, most of which will be 0, one of which will
+     * be the location of the centroid, with its height the
+     * value. Memory allocated at startup and deallocated at shutdown.
+     */
+    double* outputstate;
+
+    /*!
+     * Number of neurons in a cortical sheet. Should be the square of
+     * an integer.
+     */
+    int neuronsPerPopulation;
+
+    /*!
+     * How much scatter to apply to the centroid position.
+     */
+    double scatterAmplitude;
+
+    /*!
[…]

### 2017-05-03 c++/doublehump.cpp

@@ -1,0 +1,39 @@
+/*
+ * This one creates a double hump in cortical map from a single
+ * luminance, but it's all down to numerical effects in the Euler
+ * rotation and subsequent rounding of luminances into the eye frame's
+ * "grid" of luminanceMap locations.
+ *
+ * View output using show_data.m
+ */
+
+#include "luminance.h"
+#include "worldframe.h"
+#include "eyeframe.h"
+#include <vector>
+#include <iostream>
+#include <fstream>
+
+#include "common.h"
+#include "debug.h"
+
+using namespace wdm;
+using namespace std;
+
+std::ofstream DBGSTREAM;
+
+int main()
+{
+    WorldFrame wf;
+    // Luminance (thetax, thetay, luminosity, time_on, time_off)
+    Luminance l1 (0, 10, 1, 0.0, 0.05);
+    wf.luminanceSeries.push_back (l1);
+    wf.setLuminanceThetaMap (0.01); // Set up the map for time=0.01s.
+
+    EyeFrame ef;
+    ef.setDistanceToScreen (wf.distanceToScreen);
+    ef.setOffset (0, 1.5, 0); // y rotn 1.5 causes the double hump
+    ef.setEyeField (wf.luminanceCoords);
+
+    return 0;
+}

### 2017-05-03 c++/eyeframe.cpp

@@ -1,0 +1,498 @@
+/*!
+ * Implementation of eye frame class.
+ */
+
+#include "eyeframe.h"
+#include <fstream>
+#include <iostream>
+#include <stdexcept>
+#include <math.h>
+
+// #define DEBUG_PIXEL_NEURONS 1
+#ifdef DEBUG_PIXEL_NEURONS
+#include <map>
+#include <utility>
+#endif
+
+#include "common.h"
+#include "debug.h"
+
+using namespace wdm;
+
+void
+EyeFrame::setOffset (const double& RotX, const double& RotY, const double& RotZ)
+{
+    this->offset(0) = RotX;
+    this->offset(1) = RotY;
+    this->offset(2) = RotZ;
+    this->offset(3) = RotX * DEG_TO_RADIANS;
+    this->offset(4) = RotY * DEG_TO_RADIANS;
+    this->offset(5) = RotZ * DEG_TO_RADIANS;
+}
+
+#define ROTX this->offset(3)
+#define ROTY this->offset(4)
+#define ROTZ this->offset(5)
+void
+EyeFrame::setEyeField (const MatrixXd& worldCoords)
+{
+    // 1. copy worldCoords onto luminanceCartesianCoords
+    this->luminanceCartesianCoords = worldCoords;
+    // We need to add some columns for use in EyeFrame (as eye_x, eye_y, eye_z):
+    NoChange_t nochange;
+    this->luminanceCartesianCoords.conservativeResize(nochange, 7);
+
+#ifdef DEBUG2
+    int nrows = worldCoords.rows();
+    DBG ("worldCoords nrows: " << nrows);
+    DBG ("worldCoords ncols: " << worldCoords.cols());
+    for (int i = 0; i < nrows; ++i) {
+        if (worldCoords (i, 3) > BACKGROUND_LUMINANCE) {
+            DBG("worldCoords luminance for row " << i << " is " << worldCoords (i, 3));
+        } else {
+            DBG("worldCoords luminance for row " << i << " is " << worldCoords (i, 3));
+        }
+    }
+#endif
+
+    // 2. Apply transform
+
+    // Construct rotation matrices
+    Matrix3d RMx, RMy, RMz;
+    RMx << 1, 0,         0,
+           0, cos(ROTX), sin(ROTX),
+           0, -sin(ROTX), cos(ROTX);
+
+    RMy << cos(ROTY), 0, sin(ROTY),
[…]

### 2017-05-03 c++/eyeframe.h

@@ -1,0 +1,294 @@
+/*
+ * The EyeFrame class.
+ */
+
+#ifndef _EYEFRAME_H_
+#define _EYEFRAME_H_
+
+#include <Eigen/Dense>
+#include "luminance.h"
+#include "common.h"
+
+using namespace std;
+using namespace Eigen;
+
+/*!
+ * "wdm" short for "world data maker".
+ */
+namespace wdm
+{
+    /*!
+     * Apparent location of objects in the eye's frame of reference.
+     */
+    class EyeFrame
+    {
+    public:
+        EyeFrame () { this->init (BACKGROUND_LUMINANCE); }
+        EyeFrame (const double& bglum) { this->init (bglum); }
+        ~EyeFrame() {}
+
+        /*!
+         * Initialise the eye frame
+         */
+        void init (const double& backgroundLum) {
+
+            IOFormat octfmt (StreamPrecision, 0, ",", "\n", "", "", "", "");
+            OctaveFmt = octfmt;
+
+            // Initialise the offset attribute as a 6x1 vector
+            this->offset.setZero (6, 1);
+
+            //this->luminanceMap.setConstant (WORLD_ANGULAR_WIDTH,
+            //                                WORLD_ANGULAR_HEIGHT,
+            //                                backgroundLuminance);
+            //this->luminanceCartesianCoords.setConstant (WORLD_ANGULAR_WIDTH*WORLD_ANGULAR_HEIGHT,
+            //                                   5, 0);
+
+            this->backgroundLuminance = backgroundLum;
+
+            this->neuralFieldSize = 50;
+            this->E2 = 2.5;
+            this->fieldOfView = 61; // Originally 151 degrees. -75 to 75. Offset is
+                                    // +75 on the luminanceMap. Make
+                                    // it odd.
+            this->fovOffset = (this->fieldOfView - 1) / 2;
+            this->distanceToScreen = 1;
+            this->screenShape = SCREENSHAPE_SPHERICAL;
+
+            // Generate/setup the locations of the 2500 neurons once only.
+            this->generateNeuronThetaCoords();
+        }
+
+        /*!
+         * Accessors for the offset. Note use of capital R in RotX/Y/Z
+         * to denote that these are the same Euler rotations delivered
+         * by the U. Patras biomechanical model. Note RotX, RotY and
+         * RotZ should be passed in degrees.
+         */
+        //@{
+        void setOffset (const double& RotX, const double& RotY, const double& RotZ);
+
[…]

### 2017-05-03 c++/leftrightupdown.cpp

@@ -1,0 +1,90 @@
+/*
+ * A tester for WorldFrame, EyeFrame etc.
+ */
+
+#include "luminance.h"
+#include "worldframe.h"
+#include "eyeframe.h"
+#include <vector>
+#include <iostream>
+#include <fstream>
+
+#include "common.h"
+#include "debug.h"
+
+using namespace wdm;
+using namespace std;
+
+std::ofstream DBGSTREAM;
+
+int main()
+{
+    WorldFrame wf;
+    // Straight ahead: thetax=0, thetay=0.
+    // Luminance (thetax, thetay, widthThX, widthThY, luminosity, time_on, time_off)
+
+    Luminance l0 (  0,   0,  2,   2, 1,  0.0, 0.01);
+    Luminance l1 ( 10,   0,  2,   2, 1,  0.01, 0.05);
+    Luminance l2 (-10,   0,  2,   2, 1,  0.05, 0.1);
+    Luminance l3 (  0,  10,  2,   2, 1,  0.1, 0.15);
+    Luminance l4 (  0, -10,  2,   2, 1,  0.15, 0.2);
+
+    wf.luminanceSeries.push_back (l0);
+    wf.luminanceSeries.push_back (l1);
+    wf.luminanceSeries.push_back (l2);
+    wf.luminanceSeries.push_back (l3);
+    wf.luminanceSeries.push_back (l4);
+
+    wf.setLuminanceThetaMap (0.005);
+
+    // Save maps/coords
+    wf.saveLuminanceThetaMap ("wf_lum_theta_origin.dat");
+    wf.saveLuminanceCoords ("wf_lum_coords_origin.dat");
+
+    EyeFrame ef;
+    ef.setDistanceToScreen (wf.distanceToScreen);
+    ef.setOffset (0, 0, 0);
+
+    ef.setEyeField (wf.luminanceCoords);
+
+    // Save things which are visualised with show_data.m
+    ef.saveLuminanceMap();
+    ef.saveLuminanceCartesianCoords();
+    ef.saveNeuronPixels();
+    ef.saveNeuronPrecise();
+    ef.saveCorticalSheet("ef_cort_sheet_origin.dat");
+
+    wf.setLuminanceThetaMap (0.04);
+    wf.saveLuminanceThetaMap ("wf_lum_theta_posX.dat");
+    wf.saveLuminanceCoords ("wf_lum_coords_posX.dat");
[…]

### 2017-05-03 c++/leftrightupdown.m

@@ -1,0 +1,36 @@
+load ef_cort_sheet_origin.dat 
+
+load ef_cort_sheet_posX.dat 
+load ef_cort_sheet_negX.dat 
+load ef_cort_sheet_posY.dat 
+load ef_cort_sheet_negY.dat 
+
+onX    = ef_cort_sheet_origin .+ ef_cort_sheet_posX;
+negOnX = ef_cort_sheet_origin .+ ef_cort_sheet_negX;
+negOnY = ef_cort_sheet_origin .+ ef_cort_sheet_negY;
+onY    = ef_cort_sheet_origin .+ ef_cort_sheet_posY;
+
+figure (6)
+surf (onX)
+title ('Pos X - UP')
+xlabel ('col encodes r');
+ylabel ('row encodes theta');
+
+figure (7)
+surf (negOnX)
+title ('Neg X - DOWN')
+xlabel ('col encodes r');
+ylabel ('row encodes theta');
+
+figure (8)
+surf (negOnY)
+title ('Neg Y - RIGHT')
+xlabel ('col encodes r');
+ylabel ('row encodes theta');
+
+figure (9)
+surf (onY)
+title ('Pos Y - LEFT')
+xlabel ('col encodes r');
+ylabel ('row encodes theta');
+

### 2017-05-03 c++/make_movie.m

@@ -1,0 +1,31 @@
+direction=[0 0 1];
+basedir='/home/seb/analysis/oculomotor/';
+b = csvread ([basedir 'wdm/cortmap0.dat']);
+fg1 = figure (1);
+set (fg1, 'position', [150 150 600 600]);
+h = surf (b);
+rotate (h, direction, 90);
+axis tight manual;
+ax = gca;
+ax.NextPlot = 'replaceChildren';
+
+
+loops = 600;
+F(loops) = struct('cdata',[],'colormap',[]);
+for i = 0:loops-1
+    a = [basedir 'wdm/cortmap' num2str(i)  '.dat'];
+    b = csvread (a);
+    h = surf (b);
+    rotate (h, direction, 90);
+    drawnow
+    F(i+1) = getframe;
+end
+
+[h, w, ~] = size (F(1).cdata);  % use 1st frame to get dimensions
+hf = figure;
+% resize figure based on frame's w x h, and place at (150, 150)
+set (hf, 'position', [150 150 w h]);
+axis off
+movie (hf, F);
+implay (F)
+movie2avi(F,'/home/seb/analysis/oculomotor/eyeframe_cortical_rep.avi')

### 2017-05-03 c++/multicentroid.cpp

@@ -1,0 +1,506 @@
+/*
+ * A C++ Brahms component for the Oculomotor model - this one computes
+ * multiple centroids so that if you have two or more luminances
+ * creating hills of activity in SC deep, you'll get multiple,
+ * separate signals transmitted into the saccade generating circuitry.
+ *
+ * This is coded based on the matlab prototype in
+ * multicentroid_compute.m
+ *
+ * Author: Seb James.
+ * Date: April 2015.
+ */
+
+#define COMPONENT_CLASS_STRING "dev/NoTremor/multicentroid"
+#define COMPONENT_CLASS_CPP dev_notremor_multicentroid_0
+#define COMPONENT_RELEASE 0
+#define COMPONENT_REVISION 1
+#define COMPONENT_ADDITIONAL "Author=Seb James\n" "URL=Not supplied\n"
+#define COMPONENT_FLAGS (F_NOT_RATE_CHANGER)
+
+#define OVERLAY_QUICKSTART_PROCESS
+
+#include <brahms-1199.h>
+#include <iostream>
+#include <math.h>
+#include <vector>
+#include <utility>
+#include <stdlib.h>
+#include <Eigen/Dense>
+
+#ifdef __WIN__
+// Windows specific includes/apologies here.
+#else
+// Linux specific includes here.
+#endif
+
+namespace numeric = std_2009_data_numeric_0;
+using namespace std;
+using namespace brahms;
+using namespace Eigen;
+
+// Use a shorthand for unsigned int in this code file.
+typedef unsigned int uint;
+
+// Define this to output the maps into files.
+//#define DEBUG_MAPS 1
+
+// Define this to show a START and FINISHED message for each neural
+// sheet processed.
+//#define PROFILE_CODE 1
+
+/*!
+ * Assume a square neural field. This is the side length. Make sure to
+ * update all of these together.
+ */
+//@{
+#define NFS         50
+#define NFS_SQUARED 2500
+#define NFS_MINUS_1 49
+#define NFS_MINUS_2 48
+//@}
+
+/*!
+ * This is our Brahms component class declaration.
+ */
+class COMPONENT_CLASS_CPP : public Process
+{
+public:
+    COMPONENT_CLASS_CPP() {}
+    ~COMPONENT_CLASS_CPP() {}
+
+    /*!
+     * The framework event function
+     */
+    Symbol event (Event* event);
+
+private:
+
+    /*!
+     * Output port. Connects to a passthrough population in the model
+     * "SC_output"
+     */
[…]

### 2017-05-03 c++/rng.h

@@ -1,0 +1,242 @@
+/*
+ * This code follows Marsaglia, George, and Wai Wan Tsang. "The
+ * ziggurat method for generating random variables." Journal of
+ * statistical software 5.8 (2000): 1-7., but with a passed-in data
+ * structure for mutable variables.
+ *
+ * (RngData modifications authored by Seb James, August 2014).
+ *
+ * Example usage:
+ *
+ * #include <stdio.h>
+ * #include "rng.h"
+ * #define DUMMY 11
+ *
+ * int main()
+ * {
+ *     RngData rd;
+ *     float rn;
+ *     int i;
+ *
+ *     rngDataInit (&rd);
+ *     zigset(&rd, DUMMY);
+ *     rd.seed = 102; // very important - DO set seed >0!
+ *
+ *     while (i < 10) {
+ *         rn = _randomNormal ((&rd)); // rn will be a number from a normal
+ *                                     // distribution centred at 0 with sigma=1?
+ *         printf ("%f\n", rn);
+ *         i++;
+ *     }
+ *     return i;
+ * }
+ *
+ * g++ -o testrng testrng.cpp -lm
+ *
+ * NB: Set seed (which is an unsigned int) to a non-zero (+ve)
+ * integer! See github.com/SpineML/SpineML_2_BRAHMS issue#21.
+ */
+
+#include <cstdlib>
+#include <cmath>
+#include <climits>
+#include <ctime>
+#include <sys/time.h>
+
+/*
+ * Definition of a data storage class for use with this code. Each
+ * thread wishing to call functions from this random number generator
+ * must manage an instance of RngData. All functions operate by taking
+ * a pointer to an instance of RngData.
+ *
+ * Prior to using one of the random number generators here, first call
+ * rngDataInit to set up your RngData instance (if you're compiling
+ * this with a c++-11 compatible compiler, you can move the
+ * initialisation into the struct).
+ */
+struct RngData {
+    // Some constants, which could go at global scope, but which I
+    // prefer to have in here.
+    const static int a_RNG = 1103515245;
+    const static int c_RNG = 12345;
[…]

### 2017-05-03 c++/weightmap.cpp

@@ -1,0 +1,73 @@
+/*
+ * A program to map a region of input for which weights will be set
+ * for SC_deep to LLBN. Outside this range (i.e. for large
+ * eccentricity saccades) the weights will be artificially attenuated,
+ * due to the problems with intrinsic noise triggering saccades when
+ * weights become large.
+ */
+
+#include "luminance.h"
+#include "worldframe.h"
+#include "eyeframe.h"
+#include <vector>
+#include <iostream>
+#include <fstream>
+#include <math.h>
+
+#include "common.h"
+#include "debug.h"
+
+using namespace wdm;
+using namespace std;
+
+std::ofstream DBGSTREAM;
+
+#define SEMICIRC_RAD 19
+#define DOT_WIDTH 6
+#define DOT_HEIGHT 2
+#define DOT_LUM 0.5
+int main()
+{
+    WorldFrame wf;
+
+    // Set up the semi-circle of the region for which thetaY is
+    // positive, up to 25 degrees:
+    // thetaX^2 + thetaY^2 = 25^2 = 625; 0 <= thetaY <= 25
+    int thetaXmax = 0;
+    float fThetaXmax;
+    for (int thetaY = 0; thetaY<=SEMICIRC_RAD; ++thetaY) {
+
+        fThetaXmax = rint (sqrt (static_cast<float>(SEMICIRC_RAD*SEMICIRC_RAD - thetaY*thetaY)));
+
+        // Positive quadrant
+        thetaXmax = static_cast<int>(fThetaXmax);
+        for (int thetaX = 0; thetaX <= thetaXmax; ++thetaX) {
+            CrossLuminance lum (thetaX, thetaY, DOT_WIDTH, DOT_HEIGHT, DOT_LUM, 0.0, 0.05);
+            wf.luminanceSeries.push_back (lum);
+        }
+
+        // Negative quadrant
+        thetaXmax = thetaXmax * -1;
+        for (int thetaX = -1; thetaX >= thetaXmax; --thetaX) {
+            CrossLuminance lum (thetaX, thetaY, DOT_WIDTH, DOT_HEIGHT, DOT_LUM, 0.0, 0.05);
+            wf.luminanceSeries.push_back (lum);
+        }
+    }
+
+    wf.setLuminanceThetaMap (0.01); // Set up the map for time=0.01s.
+    // Save maps/coords
+    wf.saveLuminanceThetaMap();
+    wf.saveLuminanceCoords();
[…]

### 2017-05-03 c++/worldseries.cpp

@@ -1,0 +1,53 @@
+/*
+ * A tester for WorldFrame, EyeFrame etc.
+ */
+
+#include "luminance.h"
+#include "worldframe.h"
+#include "eyeframe.h"
+#include <vector>
+#include <iostream>
+#include <fstream>
+
+#include "common.h"
+#include "debug.h"
+
+using namespace wdm;
+using namespace std;
+
+std::ofstream DBGSTREAM;
+
+int main()
+{
+    WorldFrame wf;
+    // Straight ahead: thetax=0, thetay=0.
+
+    // A moving luminance - moves around in thetaY
+    for (int i = 0; i<100; i++) {
+        // Luminance (thetax, thetay, luminosity, time_on, time_off)
+        Luminance l (0, i, 1, 10.0*i, 10.0*i+9.999);
+        wf.luminanceSeries.push_back (l);
+    }
+
+    EyeFrame ef;
+    ef.setDistanceToScreen (wf.distanceToScreen);
+    ef.setOffset (0, 0, 0);
+
+    for (unsigned int i = 0; i<100; i++) {
+
+        wf.setLuminanceThetaMap (10.0*i); // Set up the map for time=0.01s.
+        //stringstream wfss;
+        //wfss << "worldframe" << i << ".dat";
+        //wf.saveLuminanceThetaMap (wfss.str());
+
+        ef.setEyeField (wf.luminanceCoords);
+
+#if SAVE
+        stringstream cmss;
+        cmss << "cortmap" << i << ".dat";
+        ef.saveCorticalSheet (cmss.str());
+#endif
+    }
+
+    return 0;
+}

### 2017-05-03 c++/worldtest.cpp

@@ -1,0 +1,113 @@
+/*
+ * A tester for WorldFrame, EyeFrame etc.
+ */
+
+#include "luminance.h"
+#include "worldframe.h"
+#include "eyeframe.h"
+#include <vector>
+#include <iostream>
+#include <fstream>
+
+#include "common.h"
+#include "debug.h"
+
+#include <json/json.h>
+
+using namespace wdm;
+using namespace std;
+
+std::ofstream DBGSTREAM;
+
+void readLuminanceFile (WorldFrame& wf)
+{
+    Json::Value root;
+    Json::Reader reader;
+    std::ifstream jsonfile ("luminances.json", std::ifstream::binary);
+
+    bool parsingSuccessful = reader.parse (jsonfile, root);
+    if (!parsingSuccessful) {
+        // report to the user the failure and their locations in the document.
+        cerr << "Failed to parse JSON luminances: " << reader.getFormattedErrorMessages();
+        return;
+    }
+    const Json::Value plugins = root["luminances"];
+    for (int index = 0; index < plugins.size(); ++index) {  // Iterates over the sequence elements.
+        Json::Value v = plugins[index];
+        // args for Luminance are: (thX, thY, crosswidth, barthickness, brightness, timeOn, timeOff)
+        if (v.get ("shape", "cross").asString() == "cross") {
+            CrossLuminance cross_lum (v.get ("thetaX", 0.0).asInt(),
+                                      v.get ("thetaY", 0.0).asInt(),
+                                      v.get ("widthThetaX", 0.0).asInt(),
+                                      v.get ("widthThetaY", 0.0).asInt(),
+                                      v.get ("luminance", 0.0).asFloat(),
+                                      v.get ("timeOn", 0.0).asFloat(),
+                                      v.get ("timeOff", 0.0).asFloat());
+            wf.luminanceSeries.push_back (cross_lum);
+        } else {
+            Luminance rect_lum (v.get ("thetaX", 0.0).asInt(),
+                                v.get ("thetaY", 0.0).asInt(),
+                                v.get ("widthThetaX", 0.0).asInt(),
+                                v.get ("widthThetaY", 0.0).asInt(),
[…]

### 2017-05-03 c++/worldtest_coords.cpp

@@ -1,0 +1,135 @@
+/*
+ * A program to demonstrate the mapping between the eyeframe and the
+ * retinotopic map used throughout the oculomotor model.
+ */
+
+#include "luminance.h"
+#include "worldframe.h"
+#include "eyeframe.h"
+#include <vector>
+#include <iostream>
+#include <fstream>
+
+#include "common.h"
+#include "debug.h"
+
+#include <json/json.h>
+
+using namespace wdm;
+using namespace std;
+
+std::ofstream DBGSTREAM;
+
+#define DO_EYEFRAME 1
+//#define PRECLEAN 1
+
+// Play with these rotations to see how the mapping works
+#define ROTX 0
+#define ROTY 0
+#define ROTZ 0
+
+#define NUM_LUMS_PER_SPOKE 3
+#define NUM_DEGREES_PER_STEP 9
+
+#define RECT_WIDTH 4
+#define LUM_VALUE 1
+
+#define ORIGIN_RECT_WIDTH 4
+#define ORIGIN_LUM_VALUE 1.5
+
+int main()
+{
+    // I'll define the luminances in the world frame, and then I'll
+    // transfer them to the eyeframe, but with the eye always looking
+    // directly ahead, such that the world frame and the eye frame
+    // have no offset between them.
+    WorldFrame wf;
+
+    // NB: Something odd happens when you try to set blurmode to false.
+    //wf.setBlurMode(false);
+
+    // Straight ahead: thetax=0, thetay=0.
+    // Luminance (thetax, thetay, widthThX, widthThY, luminosity, time_on, time_off)
+    Luminance lum_origin (0, 0, ORIGIN_RECT_WIDTH, ORIGIN_RECT_WIDTH, ORIGIN_LUM_VALUE, 0.0, 1);
+    wf.luminanceSeries.push_back (lum_origin);
+
+    EyeFrame ef;
+    ef.setDistanceToScreen (wf.distanceToScreen);
+    ef.setOffset (ROTX, ROTY, ROTZ);
+    ef.setEyeField (wf.luminanceCoords);
+
+    // Save just the eyeframe map in cartesian coords and the corresponding cortical sheet.
+    ef.saveLuminanceMap ("eyeframe_origin.dat");
[…]

### 2017-05-03 c++/worldtest_coords.m

@@ -1,0 +1,52 @@
+% Short script to visualise the output of worldtest_coords.cpp, which
+% makes clear the eyeframe to retinotopic population mapping.
+
+clear
+clf
+
+load('eyeframe_right.dat');
+load('eyeframe_left.dat');
+load('eyeframe_up.dat');
+load('eyeframe_down.dat');
+
+load('eyeframe_neurons.dat');
+load('eyeframe_neurons_pixel.dat');
+% The neuron positions need to be shifted:
+efn = eyeframe_neurons .+ 31;
+efn_pix = eyeframe_neurons_pixel .+31;
+
+figure(1)
+hold off
+z=repmat(1.01, 1, 2500);
+% Present pixelised neuron locations:
+scatter3(efn_pix(:,1),efn_pix(:,2), z, 2, 'red', 'filled');
+hold on;
+% Uncomment to show also the precise neuron positions:
+%scatter3(efn(:,1),efn(:,2), z, 2, 'green', 'filled');
+surf(eyeframe_right);
+surf(eyeframe_left);
+surf(eyeframe_up);
+surf(eyeframe_down);
+xlabel('X'); ylabel('Y');
+title('9, 18, 27 degrees in each direction');
+
+load('corticalmap_right.dat');
+figure(2)
+surf(corticalmap_right); xlabel('radius'); ylabel('theta');
+title('9, 18, 27 degrees to the right');
+
+load('corticalmap_left.dat');
+figure(3)
+surf(corticalmap_left); xlabel('radius'); ylabel('theta');
+title('9, 18, 27 degrees to the left');
+
+load('corticalmap_up.dat');
+figure(4)
+surf(corticalmap_up); xlabel('radius'); ylabel('theta');
+title('9, 18, 27 degrees up');
+
+load('corticalmap_down.dat');
+figure(5)
+surf(corticalmap_down); xlabel('radius'); ylabel('theta');
+title('9, 18, 27 degrees down');
+

### 2017-05-03 c++/worldtest_singlelum.m

@@ -1,0 +1,30 @@
+% Short script to visualise the output of worldtest_singlelum.cpp, which
+% makes clear the eyeframe to retinotopic population mapping.
+
+%clf(1)
+%clf(2)
+
+load('eyeframe_single.dat');
+load('eyeframe_neurons.dat');
+load('eyeframe_neurons_pixel.dat');
+% The neuron positions need to be shifted:
+efn = eyeframe_neurons;% .+ 31;
+efn_pix = eyeframe_neurons_pixel;% .+ 31;
+
+figure(1)
+hold off
+z=repmat(1.01, 1, 2500);
+% Present pixelised neuron locations:
+scatter3(efn_pix(:,1),efn_pix(:,2), z, 2, 'red', 'filled');
+hold on;
+% Uncomment to show also the precise neuron positions:
+scatter3(efn(:,1),efn(:,2), z, 2, 'green', 'filled');
+surf([-30:30], [-30:30], eyeframe_single);
+xlabel('ThetaY; rotn about y axis');
+ylabel('ThetaX; rotn about x axis');
+title('eyeframe');
+
+load('corticalmap_single.dat');
+figure(2)
+surf(corticalmap_single); xlabel('radius'); ylabel('theta');
+title('cortical map');

### 2017-05-03 gauss_conn-1.py

@@ -1,0 +1,24 @@
+
+#PARNAME=sigma #LOC=1,1
+#HASWEIGHT
+
+def connectionFunc(srclocs,dstlocs,sigma):
+
+	import math
+	
+	normterm = 1/(sigma*math.sqrt(2*math.pi))
+
+	i = 0
+	out = []
+	for srcloc in srclocs:
+		j = 0
+		for dstloc in dstlocs:
+			dist = math.sqrt(math.pow((srcloc[0] - dstloc[0]),2) + math.pow((srcloc[1] - dstloc[1]),2) + math.pow((srcloc[2] - dstloc[2]),2))
+			gauss = normterm*math.exp(-0.5*math.pow(dist/sigma,2))
+			if gauss > 0.001:
+				conn = (i,j,0,gauss)
+				out.append(conn)
+			j = j + 1
+		i = i + 1
+	return out
+

### 2017-05-03 lab_book/201509_Combined_RotZ_Training/showdata.m

@@ -1,0 +1,9 @@
+function showdata(oneby2500, thetitle, mapnum)
+    map = reshape(oneby2500, 50, 50, []);
+    figure (mapnum); surf(map);
+    title (thetitle,'fontsize',28);
+    xlabel ('r','fontsize',24);
+    ylabel ('phi','fontsize',24);
+    zlabel ('weight','fontsize',20);
+    view([-65,30]);
+end

### 2017-05-03 lab_book/201511_Training/graphweights.m

@@ -1,0 +1,47 @@
+% Load and show the weight maps
+
+e50 = load_explicit_data ('explicitDataBinaryFile50.bin');
+e50 = showdata(e50, 'Left (e50)', 50);
+
+e52 = load_explicit_data ('explicitDataBinaryFile52.bin');
+e52 = showdata(e52, 'Right (e52)', 52);
+
+e53 = load_explicit_data ('explicitDataBinaryFile53.bin');
+e53 = showdata(e53, 'Up (e53)', 53);
+
+e54 = load_explicit_data ('explicitDataBinaryFile54.bin');
+e54 = showdata(e54, 'Down (e54)', 54);
+
+e57 = load_explicit_data ('explicitDataBinaryFile57.bin');
+e57 = showdata(e57, 'Z+ (e57)', 57);
+
+e58 = load_explicit_data ('explicitDataBinaryFile58.bin');
+e58 = showdata(e58, 'Z- (e58)', 58);
+
+% Last graph, all in one.
+h_f = figure (100);
+
+% Spacing for subaxes
+sa_spc = 0.05;
+sa_pad = 0.04;
+sa_marg = 0.039;
+
+h_e50 = subaxis (3,2,1, 'Spacing', sa_spc, 'Padding', sa_pad, 'Margin', sa_marg);
+e50 = showsubgraph (e50, 'Left', 50, h_e50);
+
+h_e52 = subaxis (3,2,2, 'Spacing', sa_spc, 'Padding', sa_pad, 'Margin', sa_marg);
+e52 = showsubgraph (e52, 'Right', 52, h_e52);
+
+h_e53 = subaxis (3,2,3, 'Spacing', sa_spc, 'Padding', sa_pad, 'Margin', sa_marg);
+e53 = showsubgraph (e53, 'Up', 53, h_e53);
+
+h_e54 = subaxis (3,2,4, 'Spacing', sa_spc, 'Padding', sa_pad, 'Margin', sa_marg);
+e54 = showsubgraph (e54, 'Down', 54, h_e54);
+
+h_e57 = subaxis (3,2,5, 'Spacing', sa_spc, 'Padding', sa_pad, 'Margin', sa_marg);
+e57 = showsubgraph (e57, 'Z+', 57, h_e57);
+
+h_e58 = subaxis (3,2,6, 'Spacing', sa_spc, 'Padding', sa_pad, 'Margin', sa_marg);
[…]

### 2017-05-03 lab_book/201511_Training/showsubgraph.m

@@ -1,0 +1,10 @@
+function fiftyby50 = showsubgraph(fiftyby50, thetitle, mapnum, axishandle)
+    h = surf(axishandle, fiftyby50);
+    %set(h,'LineStyle','none')
+    set(h,'LineWidth', 0.1)
+    title (thetitle,'fontsize',12);
+    xlabel ('r','fontsize',12);
+    ylabel ('phi','fontsize',12);
+    zlabel ('weight','fontsize',12);
+    view([-65,30]);
+end

### 2017-05-03 lab_book/const_weight_example.m

@@ -1,0 +1,57 @@
+# Created by Octave 3.8.2, Fri Feb 06 14:42:25 2015 GMT <pc1ssj@node117>
+# name: weights
+# type: matrix
+# rows: 50
+# columns: 50
+ 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0
+ 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0
+ 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0
+ 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0
+ 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0
+ 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0
+ 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0
+ 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0
[…]

### 2017-05-03 matlab/archivedAnalysis/analyse_file.m

@@ -1,0 +1,58 @@
+function [data] = analyse_file (file_path, num_neurons)
+% analyse_file Analyse a single file from the Oculomotor model BG experiment.
+
+% Note: load_sc_file is found in SpineCreator/analysis_utils/matlab
+% There are 2500 neurons per population in the Oculomotor BG expt.
+
+% FIXME: Can get num_neurons and num_timesteps from the xml file
+% associated with the bin file.
+    
+%clear
+%file_path='Str_D1_out_log.bin';
+%num_neurons = 3;
+
+fprintf ('analyse_file: Processing %s\n',file_path);
+
+[data, count] = load_sc_data (file_path, num_neurons);
+num_timesteps = count/num_neurons;
+
+% We have the data. Its size is 2500 x 300. We want to know
+% which of the 2500 rows has any significant changes. To this end,
+% compute the integral/sum of the row, and see which ones are far away
+% from the mean integral. This assumes we have mostly low activity,
+% with some small regions of activity.
+
+% Here, we sum on the second dimension, to sum along the 300 ms
+% time series.
+sums = sum (data, 2);
+
+% Statistics on the integrals. We want to show those which deviate
+% from the mean integral, because we have many self-similar traces.
+maxsum = max(sums)
+meansum = mean(sums)
+sd = std(sums)
+
+% Our indexes of interest are those for which the sum is some
+% distance from the mean sum.
+reasonable_distance_from_mean = 2*sd % Needs to be dynamic.
+absdiffs = abs (sums - meansum);
+%absdiffs(1:5)
+indexes = find (absdiffs>reasonable_distance_from_mean);
+si = size(indexes);
+shown_graphs = si(1); % Number of graphs showing.
+
+% indexes is now a list of the indexes into data which contain
+% something interesting. Can now plot these. On one graph?
+if shown_graphs > 0
+    fprintf ('Plotting %d graphs/%d traces\n', shown_graphs, num_neurons);
+    fig = figure;
+    h = plot (1:num_timesteps, data(indexes,:));
+    hold on;
+    plot(1:num_timesteps, data(1,:),'.r');
+    h = title (file_path);
+    set (h, 'interpreter', 'none');
+else
+    fprintf ('Plotting no graphs (from %d traces)\n', num_neurons);
+end
+
+end

### 2017-05-03 matlab/archivedAnalysis/analyse_output.m

@@ -1,0 +1,37 @@
+%
+% A script to consume the output of the Oculomotor BG-only model.
+%
+% This script is tied to the Experiment 
+%
+% It reads these files from your SpineML_2_BRAHMS temp directory
+% (or wherever your experiment output has gone):
+%
+% /home/seb/src/SpineML_2_BRAHMS/temp/GPe_out_log.bin
+% /home/seb/src/SpineML_2_BRAHMS/temp/SNr_a_log.bin
+% /home/seb/src/SpineML_2_BRAHMS/temp/SNr_in_log.bin
+% /home/seb/src/SpineML_2_BRAHMS/temp/SNr_out_log.bin
+% /home/seb/src/SpineML_2_BRAHMS/temp/STN_out_log.bin
+% /home/seb/src/SpineML_2_BRAHMS/temp/Str_D1_out_log.bin
+%
+
+clear;
+close all;
+
+spineml2brahms_path = '/home/seb/src/SpineML_2_BRAHMS/temp/';
+
+expt_files = {'FEF_out_log.bin';
+              'Retina_2_out_log.bin';
+              'GPe_out_log.bin';
+              'SC_deep_out_log.bin';
+              'SC_sup_out_log.bin';
+              'SNr_out_log.bin';
+              'Thalamus_out_log.bin';
+              'STN_out_log.bin';
+              'Str_D1_out_log.bin'};
+
+% Analyse each of the above files in turn:
+
+for i = 1:size(expt_files,1);
+    
+    analyse_file (expt_files{i}, 2500);
+end

### 2017-05-03 matlab/archivedAnalysis/shapeMovieData.m

@@ -1,0 +1,30 @@
+% Open a file, shape the data to 0-255 per pixel so that it's ready
+% for movie making.
+
+% Expects 50x50 format data, as generated by the Oculomotor model.
+
+logDir = '/home/seb/analysis/oculomotor/log/';
+population = 'SC_deep';
+
+% Load
+data = load_sc_data (char([logDir population '_out_log.bin']), 2500);
+
+% Scale and convert to uint8
+data = uint8(data.*256);
+
+% Save
+fid = fopen (char([logDir population '_out_uint8.bin']), 'w')
+fwrite (fid, data, 'uint8');
+
+% Then at the cmd line
+system (char(['mkdir -p ' logDir population]));
+system (char(['split -b 2500 ' logDir population '_out_uint8.bin ' ...
+                    logDir population '/frame_']));
+system (char(['convert -depth 8 -size 50x50 gray:' logDir population ...
+              '/frame_* ' logDir population '/frame.jpg']));
+% If you want to make it bigger (optional):
+system (char(['mogrify -resize 240x240 ' logDir population '/frame*.jpg']));
+% make the movie. rate of 50 fps requested. -y means overwrite
+% without asking.
+system (char(['avconv -y -f image2 -r 50 -i ' logDir population '/frame-%d.jpg ' ...
+              logDir population '.mpg']));

### 2017-05-03 matlab/movies/movieMaker1.m

@@ -1,0 +1,253 @@
+function   movieMaker(movFlag, nfs, R, SCd, STR, STN, GPi, FEF, Thalamus,SCs, LLBN, EBN, TN, MN)
+
+        dt = 0.5e-3;
+        T = 0.6;
+        tvec = 0:dt:T;
+        trnk = 1000;
+       
+        R = R(:,1:trnk);
+        SCd = SCd(:,1:trnk);
+        STR = STR(:,1:trnk);
+        STN = STN (:,1:trnk);
+        GPi = GPi(:,1:trnk);
+        FEF = FEF(:,1:trnk);
+        Thalamus = Thalamus(:,1:trnk);
+        SCs = SCs(:,1:trnk);
+        LLBN = LLBN(1:trnk);
+        EBN = EBN(1:trnk);
+        TN = TN(1:trnk);
+        MN = MN(1:trnk);
+        tvec = tvec(1:trnk);
+        
+% h = uicontrol('style','slider','position',...
+% 	[10 50 20 300],'Min',0subplot(3,4,1)
+figure(5); clf
+
+subplot(3,4,1)
+plot(R(2181,:));
+title('retina');
+set(gcf,'colormap',hot)
+axis tight square
+
+subplot(3,4,2)
+plot(FEF(2181,:));
+title('FEF');
+set(gcf,'colormap',hot)
+axis tight square
+
+subplot(3,4,3)
+plot(Thalamus(2181,:));
+title('thalamus');
+set(gcf,'colormap',hot)
+axis tight square
+
+subplot(3,4,4)
+plot(STR(2181,:));
+title('striatum d1');
+set(gcf,'colormap',hot)
+axis tight square
+
+subplot(3,4,5)
+plot(STN(2181,:));
+title('STN');
+set(gcf,'colormap',hot)
+axis tight square
+
+subplot(3,4,6)
+plot(GPi(2181,:));
+title('GPi');
+set(gcf,'colormap',hot)
+axis tight square
+
+subplot(3,4,7)
+plot(SCd(2181,:));
+title('SC deep');
+set(gcf,'colormap',hot)
+axis tight square
+
+subplot(3,4,8)
+plot(SCs(2181,:));
+title('SC sup');
+set(gcf,'colormap',hot)
+axis tight square
+
+subplot(3,4,9)
+plot(LLBN);
+title('LLBN');
+set(gcf,'colormap',hot)
+axis tight square
+
+subplot(3,4,10)
[…]

### 2017-05-03 matlab/movies/movieMakerReshape.m

@@ -1,0 +1,5 @@
+function reshaped = movieMakerReshape (data, nfs)
+    reshaped = data;
+    reshaped(1) = 0; reshaped(2) = 1;
+    reshaped = reshape (reshaped, nfs, nfs);
+end

### 2017-05-03 matlab/movies/movieMakerSubplot.m

@@ -1,0 +1,12 @@
+function movieMakerSubplot (subplot_title, data, subplot_index)
+    sz = size(data);
+    subplot (3,4,subplot_index)
+    if (sz(1) == 2500)
+        plot (data(2181,:));
+    else
+        plot (data(1,:));
+    end
+    title (subplot_title);
+    set (gcf,'colormap',hot)
+    axis tight square
+end

### 2017-05-03 matlab/movies/processMovieData.m

@@ -1,0 +1,28 @@
+% % Plot results of a model run. Data should have been stored into
+% files by SpineCreator/SpineML_2_BRAHMS.
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%spineml2brahms_workdir = '/home/seb/analysis/oculomotor/';
+spineml2brahms_workdir = '/fastdata/pc1ssj/oculomotor/';
+movFlag = 0;
+% Size of neural field.  Assumed to be square array Needs to be same as the
+% one in worldDataMaker.m
+nfs = 50;
+
+% These data sets are from the OM model, and have 2500 neurons per population.
+[ R, ~ ] = load_sc_data ([spineml2brahms_workdir, '/log/Retina_2_out_log.bin'], 2500);
+[ SCd, ~ ] = load_sc_data ([spineml2brahms_workdir '/log/SC_deep_out_log.bin'], 2500);
+[ STR, ~ ] = load_sc_data ([spineml2brahms_workdir '/log/Str_D1_out_log.bin'], 2500);
+[ STN, ~ ] = load_sc_data ([spineml2brahms_workdir '/log/STN_out_log.bin'], 2500);
+[ SNr, ~ ] = load_sc_data ([spineml2brahms_workdir '/log/SNr_out_log.bin'], 2500);
+[ FEF, ~ ] = load_sc_data ([spineml2brahms_workdir '/log/FEF_out_log.bin'], 2500);
+[ Thalamus, ~ ] = load_sc_data ([spineml2brahms_workdir '/log/Thalamus_out_log.bin'], 2500);
+[ SCs, ~ ] = load_sc_data ([spineml2brahms_workdir '/log/SC_sup_out_log.bin'], 2500);
+
+% These are the saccade generator model and have 1 neuron per population.
+[ LLBN, ~ ] = load_sc_data ([spineml2brahms_workdir '/log/LLBN_left_a_log.bin'], 1);
+[ EBN, ~ ] = load_sc_data ([spineml2brahms_workdir '/log/EBN_left_a_log.bin'], 1);
+[ TN, ~ ] = load_sc_data ([spineml2brahms_workdir '/log/TN_left_a_log.bin'], 1);
+[ MN, ~ ] = load_sc_data ([spineml2brahms_workdir '/log/MN_left_a_log.bin'], 1);
+
[…]

### 2017-05-03 matlab/movies/radial_to_neural_array_animation.m

@@ -1,0 +1,160 @@
+%
+% Create world, window and remapping and make a movie of it.
+%
+
+clear all; clc;  close all
+
+% Create world and visual field
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+nfs = 50;          % Size of neural field.  Assumed to be square array
+
+fp = [160 ;160];   % Focal point.  This vector has to come from spineCreator and is the 
+
+window_size = 150; % size of visual field in pixels
+
+E2 = 2.5;
+Mf = nfs/(E2*log(((window_size/2)/E2)+1));   % this parameter has an unknown value **** ASK ALEX COPE **** perhaps set such that the number of rows (max(D)) :=> number of rows in field of view ie. 150 => Mf = 1/((E2/D)*log(1+ E/E2)) ==> Mf 4.8651
+D = 1:50;  
+
+% parameters for the movie. Modify these to get different kinds of movie.
+target_size = 10;  % size of saccade target in pixels
+targetx_start = 155;
+targety_start = 155;
+xmovefn = 'sin';
+xmoveamp = 25;
+ymovefn = 'cos';
+ymoveamp = 15;
+avifilename = sprintf ('movies/start%d%d-x%s%d-y%s%d.avi', targetx_start, targety_start, xmovefn, xmoveamp, ymovefn, ymoveamp);
+mfilename = sprintf ('movies/start%d%d-x%s%d-y%s%d.mat', targetx_start, targety_start, xmovefn, xmoveamp, ymovefn, ymoveamp);
+caption = sprintf ('Start at %d %d x moves as %s amp. %d y moves as %s amp. %d', targetx_start, targety_start, xmovefn, xmoveamp, ymovefn, ymoveamp);
+
+SIN=sin(0:2*pi/150:2*pi);
+COS=cos(0:2*pi/150:2*pi);
+SAW=[ 0:1/37:1 1:-1/37:-1 -1+1/37:1/37:0 ];
+
+
+% how many frames will we run (150 is full movie)?
+numframes = 150;
+
+% Pre-allocate the MOV container.
+MOV(numframes) = struct('cdata',[],'colormap',[]);
+
+for frame = 1:numframes % should be 150
+    
+if strcmp (xmovefn,  'saw')
+    targetx = targetx_start+round(xmoveamp*SAW(frame));
+elseif strcmp (xmovefn,  'sin')
+    targetx = targetx_start+round(xmoveamp*SIN(frame));
+elseif strcmp (xmovefn,  'cos')
[…]

### 2017-05-03 matlab/multicentroid/multicentroid.m

@@ -1,0 +1,2 @@
+% Run the multi centroid function:
+multicentroid_sn_run();

### 2017-05-03 matlab/multicentroid/multicentroid_sn_run.m

@@ -1,0 +1,97 @@
+function multicentroid_sn_run ()
+%% Communicate with model to do multiple centroiding. Copy SD_deep
+%% data from model; apply multiple centroid algorithm; 
+    
+    % start the interface thread
+    display ('SpineMLNet mcent: initialising...');
+    context = spinemlnetStart (50091);
+    display ('SpineMLNet mcent: initialised.');
+
+    % Specify a cleanup function.
+    cleanupObj = onCleanup(@() spinemlnetCleanup(context));
+
+    % loop until the spinemlnet system has finished.
+    escaped = false;
+
+    % holding variable for our neural sheet, stored as a vector.
+    sheet = zeros(2500,1);
+    
+    % Is the spinemlnet main thread preventing octave from getting
+    % any further at this point? Perhaps spinemlnet main thread
+    % needs to allow some time for the main octave thread.
+    
+    display ('SpineMLNet mcent: Going into loop...');
+    while escaped == false
+   
+        % query for current state.
+        qrtn = spinemlnetQuery (context);
+        
+        % qrtn(1,1): threadFinished (possibly failure)
+        % qrtn(1,2): connectionsFinished - this means you can go ahead
+        % and collect data with spinemlnetGetData().
+        if qrtn(1,1) == 1
+            % The thread failed, so set escaped to true.
+            display ('SpineMLNet mcent: The TCP/IP I/O thread seems to have failed. Finishing.');
+            escaped = true;
+        elseif qrtn(1,2) == 1
+            % The connections completed, so we can collect any
+            % remaining data and then escape
+            %display (['SpineMLNet mcent: Finished; collect any ' ...
+            %          'remaining data...']);
+            sheet = spinemlnetGetData (context, 'SC_deep');
+            sz = size(sheet);
+            for i=1:sz(:,2)
+                [artn errormsg] = spinemlnetAddData (context, 'SC_deep_output', sheet(:,i));
+                if length(errormsg) > 0
+                    display (errormsg);
+                    escaped = true;
+                end
+            end
+            % Don't escape when connections are finished; allow
+            % another run of the model.
+            % escaped = true;
+        else
+            % Get data from model - this will be the SC_deep neural sheet.
+            sheet = spinemlnetGetData (context, 'SC_deep');
+
+            % use the result of spinemlnetGetData to determine
+            % whether there was data or no. We should get two zeros
+            % if the connection isn't yet ready.
+            sz = size(sheet);
[…]

### 2017-05-03 matlab/worldDataMaker/all_grid_coordinates.m

@@ -1,0 +1,19 @@
+function [ COORDINATES ] = all_grid_coordinates (square_grid_width)
+%ALL_GRID_COORDINATES Return a two col matrix containing all x,y positions
+% on a square grid of width square_grid_width.
+
+% create grid of positions of each neuron i.e. locations on the 50x50 grid
+% Use of meshgrid would be alternative here.
+COORDINATES = nchoosek(1:square_grid_width,2);
+% Following does 1) R itself, 2) then R with columns reversed (2 first, then 1,
+% which gives the mirrored locations, 3) then 1 1; 2 2; 3 3; etc (diag
+% elements).
+COORDINATES = [ COORDINATES; COORDINATES(:,[2 1]); [(1:square_grid_width)' (1:square_grid_width)'] ];
+
+% This code is useful for the visualisation but is not needed when
+% communicating with spineCreator.
+[s,I] = sort(COORDINATES(:,2));
+COORDINATES = COORDINATES(I,:);
+
+end
+

### 2017-05-03 matlab/worldDataMaker/make_target.m

@@ -1,0 +1,31 @@
+function [ target_frame ] = make_target (target_locns, target_size, target_luminance)
+%MAKE_TARGET Create a saccade target in world at location x, y.
+% Returns a 300 by 300 world view frame, containing target(s), of size
+% target_size located at (x,y) = target_locns(:,1), target_locns(:,2),
+% with Gaussian blur applied (blur parameters are hardcoded into this
+% function).
+
+% FINISH ME to allow for passing in >1 target.
+    target_locns
+
+    targetx_indices = target_locns(1)-target_size/2:target_locns(1)+target_size/2 % Create indices of target location
+    targety_indices = target_locns(2)-target_size/2:target_locns(2)+target_size/2;
+
+    targetx_indices
+    
+    target_frame = 0.01+zeros(300,300);    % Create background array of low luminance pixels
+
+    % For each targetx/targety:
+    sz=size(targetx_indices)
+    for idx=1:sz(1)
+        display('set brightspot...');
+        targetx(idx)
+        targety(idx)
+
+        % Create luminous spot at target location:
+        target_frame(targetx(idx),targety(idx)) = target_luminance; 
+    end
+
+    H = fspecial('gaussian',[2,2],0.5);      % Apply a 2 pixel sigma=0.5 gaussian blur to the image
+    target_frame = imfilter(target_frame,H); % This is now the input mask/filter
+end

### 2017-05-03 matlab/worldDataMaker/spinemlnet_run1.m

@@ -1,0 +1,126 @@
+function  [R, SCd, STR, STN, GPi, FEF, Thalamus,SCs] = spinemlnet_run1 (L,n)  %   [R, F, T, Sd1, S, GPe, GPi, SCd, SCs]
+% start the interface thread
+display ('SpineMLNet ML: initialising...');
+context = spinemlnetStart (50091);
+display ('SpineMLNet ML: initialised.');
+
+% Specify a cleanup function.
+cleanupObj = onCleanup(@() spinemlnetCleanup(context));
+
+% First job - add some data for a connection
+
+% % My sample experiment has 2 neurons in its single population and requires
+% % 3000 points for each neuron. Here are two sines with 3000 points an
+% % about 4 3/4 periods, one larger in amplitude than the other:
+% sine_array = 50 * sin([0:0.01:29.99]);
+% sine_array2 = 10 * sin([0:0.01:29.99]);
+
+% Now make an input_data matrix up with each time series in its own row.
+% Note: one row per member of the population. Time extends to the right
+% with increasing column.
+% input_data = [sine_array;sine_array2];
+
+% Add the sine_array data to spinemlnet for the first connection,
+% which is called realtime.
+[artn errormsg] = spinemlnetAddData (context, 'World Input', L);
+if length(errormsg) > 0
+    display (errormsg);
+end
+
+% % Add the sine_array data to spinemlnet for a second connection,
+% % which is called realtime2 (not used in my example lif_test2 expt).
+% [artn errormsg] = spinemlnetAddData (context, 'realtime2', input_data);
+% if length(errormsg) > 0
+%     display (errormsg);
+% end
+
+% loop until the spinemlnet system has finished.
+escaped = false;
+
+% OUT = zeros(size(L,1), size(L,2),n);
+    R = [];
+    FEF = [];
+    Thalamus = [];
+    STR = [];
+    STN = [];
+    GPi = [];
+    SCd = [];
+    SCs = [];
+    
+ 
+display ('SpineMLNet ML: Going into loop...');
+while escaped == false
+   
+    
+    %display ('SpineMLNet ML: Call spinemlnetQuery()');
+
+    % query for current state.
+    qrtn = spinemlnetQuery (context);
+    pause(10);
+    
+    % qrtn is:
+    % qrtn(1,1): threadFinished (possibly failure)
+    % qrtn(1,2): connectionsFinished - this means you can go ahead
+    % and collect data with spinemlnetGetData().
+    
+    % You can also call spinemlnetAddData() within the loop, as
[…]

### 2017-05-03 matlab/worldDataMaker/worldDataMaker.m

@@ -1,0 +1,187 @@
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% Create world, window and remapping for the Oculomotor model input.
+% 10/04/2014, to 17/09/2014
+%
+% This code requires access to spinemlnet mex or oct files found in
+% SpineCreator/networkserver/matlab/; a function from
+% SpineCreator/analysis_utils/matlab and matlab code from
+% abrg_local/Oculomotor/matlab. Add these to your octave/matlab path.
+%
+
+clear all; clc; close all
+
+% Create world and visual field
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+ftDelay = -20e-3;    % delay in seconds between the disappearance of
+                     % the fixation point and the appearance of the
+                     % target.  Negative value implies an
+                     % OVERLAP. Zero value implies a STEP.
+
+dt  = 0.5e-3;        % size of spineCreator solver timestep
+
+T = 0.3;             % Length of simulation
+
+Tstim = 70e-3;       % Time of target onset (seconds)
+
+nfs = 50;            % Size of neural field.  Assumed to be square
+                     % array
+
+background = 0.0;   % background luminance
+
+fp = [150 ;150];     % Focal point.  This vector has to come fromspineCreator and is the
+   
+luminance = 0.5;
+
+target_size = 4;     % size of target in pixels
+
+% Create indices of target location
+fixatex = fp(1)-target_size/2:fp(1)+target_size/2;
+fixatey = fp(2)-target_size/2:fp(2)+target_size/2;
+
+window_size = 150;   % size of visual field in pixels
+
+% Location of centre of target as indicies of the 300x300 world array
+targetX = str2num(getenv('XLOC'));
+targetY = 150; % str2num(getenv("YLOC"));
+
+% Create indices of target location
+targetx = targetX-target_size/2:targetX+target_size/2;
+targety = targetY-target_size/2:targetY+target_size/2;
+
+% Create world array of low luminance pixels
+worldBlank = background+zeros(300,300);
+
+% Create target image
+worldTarget = worldBlank;
[…]

### 2017-05-03 matlab/worldDataMaker/worldDataMaker1.m

@@ -1,0 +1,185 @@
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% Create world, window and remapping
+% 10/04/2014
+
+clear all; clc;  close all
+
+% Don't addpath in a script - makes it un-portable. Much better to put
+% paths in your matlab/octave configuration.
+% Make sure that the SpineCreator networkserver oct/mex files are
+% in your path.
+% addpath /home/seb/src/SpineCreator/networkserver/matlab
+
+% Create world and visual field
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+neural_fieldsize = 50;          % Size of neural field.  Assumed to be square array
+
+focal_point = [160 ;160];   % Focal point.  This vector has to come from spineCreator and is the
+
+window_size = 150; % size of visual field in pixels
+
+% world is 300x300, rather than 50x50, as will be sent to the experiment in
+% SpineCreator. Here, we make two target frames.
+target1 = make_target (215, 155, 10, 10);
+target2 = make_target (175, 125, 10, 10);
+
+% Create remapping
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+% What's E2, and why is it 2.5?
+E2 = 2.5;
+% this parameter has an unknown value **** ASK ALEX COPE ****
+% perhaps set such that the number of rows (max(D)) :=> number
+% of rows in field of view ie. 150 => Mf = 1/((E2/D)*log(1+ E/E2)) ==> Mf 4.8651
+Mf = neural_fieldsize/(E2*log(((window_size/2)/E2)+1))
+
+% We want to find out... where in the visual field does a particular
+% neuron's inputs come from? ....
+R = all_grid_coordinates (neural_fieldsize);
+
+% vectorised calculations of locations of x and y in x-y plane of visual
+% field from where the neuron at location R receives its inputs
+locx = E2.*(-1+exp(R(:,2)./(Mf.*E2))).*cos(R(:,1).*2.*pi./neural_fieldsize);
+locy = E2.*(-1+exp(R(:,2)./(Mf.*E2))).*sin(R(:,1).*2.*pi./neural_fieldsize);
+
+% plot
+
+showfigures = 0;
+if showfigures == 1
+    figure(1); clf; hold on;
+    imagesc(target1)
[…]

### 2017-05-03 matlab/worldDataMaker/worldDataMaker1_sn_run.m

@@ -1,0 +1,101 @@
+function [R, F, T, Sd1, S, GPe, GPi, SCd, SCs] = worldDataMaker1_sn_run (L)  %   
+% start the interface thread
+display ('SpineMLNet ML: initialising...');
+context = spinemlnetStart (50091);
+display ('SpineMLNet ML: initialised.');
+
+% Specify a cleanup function.
+cleanupObj = onCleanup(@() spinemlnetCleanup(context));
+
+% First job - add some data for a connection
+
+% % My sample experiment has 2 neurons in its single population and requires
+% % 3000 points for each neuron. Here are two sines with 3000 points an
+% % about 4 3/4 periods, one larger in amplitude than the other:
+% sine_array = 50 * sin([0:0.01:29.99]);
+% sine_array2 = 10 * sin([0:0.01:29.99]);
+
+% Now make an input_data matrix up with each time series in its own row.
+% Note: one row per member of the population. Time extends to the right
+% with increasing column.
+% input_data = [sine_array;sine_array2];
+
+% Add the sine_array data to spinemlnet for the first connection,
+% which is called realtime.
+[artn errormsg] = spinemlnetAddData (context, 'World Input', L);
+if length(errormsg) > 0
+    display (errormsg);
+end
+
+% % Add the sine_array data to spinemlnet for a second connection,
+% % which is called realtime2 (not used in my example lif_test2 expt).
+% [artn errormsg] = spinemlnetAddData (context, 'realtime2', input_data);
+% if length(errormsg) > 0
+%     display (errormsg);
+% end
+
+% loop until the spinemlnet system has finished.
+escaped = false;
+
+display ('SpineMLNet ML: Going into loop...');
+while escaped == false
+
+    %display ('SpineMLNet ML: Call spinemlnetQuery()');
+
+    % query for current state.
+    qrtn = spinemlnetQuery (context);
+    % qrtn is:
+    % qrtn(1,1): threadFinished (possibly failure)
+    % qrtn(1,2): connectionsFinished - this means you can go ahead
+    % and collect data with spinemlnetGetData().
+    
+    % You can also call spinemlnetAddData() within the loop, as
+    % often as you like to add to the data which will be passed to
+    % the SpineML experiment/simulation/execution.
+    
+    if qrtn(1,1) == 1
+        % The thread failed, so set escaped to true.
[…]

### 2017-05-03 matlab/worldDataMaker/worldDataMaker_sn_run.m

@@ -1,0 +1,50 @@
+function worldDataMaker_sn_run (L)
+% start the interface thread
+display ('SpineMLNet ML: initialising...');
+context = spinemlnetStart (50091);
+display ('SpineMLNet ML: initialised.');
+
+% Specify a cleanup function.
+cleanupObj = onCleanup(@() spinemlnetCleanup(context));
+
+% Add model input luminance data to the 'World Input' connection
+[artn errormsg] = spinemlnetAddData (context, 'World Input', L);
+if length(errormsg) > 0
+    display (errormsg);
+end
+
+% loop until the spinemlnet system has finished.
+escaped = false;
+
+display ('SpineMLNet ML: Going into loop...');
+while escaped == false
+   
+    % query for current state.
+    qrtn = spinemlnetQuery (context);
+    
+    % qrtn(1,1): threadFinished (possibly failure)
+    % qrtn(1,2): connectionsFinished - this means you can go ahead
+    % and collect data with spinemlnetGetData().
+    if qrtn(1,1) == 1
+        % The thread failed, so set escaped to true.
+        display ('SpineMLNet ML: The TCP/IP I/O thread seems to have failed. Finishing.');
+        escaped = true;
+    elseif qrtn(1,2) == 1
+        % The connections completed, so we can collect data and escape
+        display ('SpineMLNet ML: Finished');
+        escaped = true;
+    else
+        % Pass no data back to worldDataMaker - use the
+        % SpineCreator files for that; it's safer.
+    end
+    pause (3);
+end
+
+display ('SpineMLNet ML: Script finished');
+end
+
+function spinemlnetCleanup (context)
+    disp('SpineMLNet ML: spinemlnetCleanup: Calling spinemlnetStop');
+    spinemlnetStop(context);
+    disp('SpineMLNet ML: cleanup complete.');
+end

### 2017-05-03 movies/movieColour.sh

@@ -1,0 +1,135 @@
+#!/bin/bash
+
+set -m
+
+# As framewidth increases, memory requirements on the server go
+# up. The default for qrsh is enough for up to 200. 300 makes for nice big movies.
+FRAMEWIDTH="150"
+
+# How fast to make the movie go.
+FRAMERATE=25
+
+# MODIFY this to suit your environment.
+LOGDIR='/fastdata/pc1ssj/oculomotor/log/'
+
+POPULATIONS=('Retina_1' 'Retina_2' 'FEF' 'SC_deep' 'GPe' 'SC_sup' 'SNr' 'STN' 'Str_D1' 'Thalamus')
+#             0          1          2     3         4     5        6      7    8        9
+
+# The image type to use for the intermediate frames.
+# jpg works fine. For png - images are created by imageMagick, but
+# avconv doesn't convert 'em. pbm: in the convert call, the output
+# file isn't expanded out into many individual files - all the frames
+# are in the single file. (+adjoin fixes that but output is poor
+# quality). bmp works about as well a jpg.
+IMTYPE="jpg"
+
+# BMAX is number of batches to run the parallel imagemagick commands in.
+BMAX=60
+
+# Do the split in a multi processor friendly way
+for i in `seq 0 9`; do
+    mkdir -p "$LOGDIR${POPULATIONS[$i]}"
+    split -a 3 -b 5000 "$LOGDIR${POPULATIONS[$i]}"_out_uint16.bin  "$LOGDIR${POPULATIONS[$i]}"/frame_ &
+done
+while fg; do true; done
+
+# Make sure the colour gradient exists
+convert -size 10x50 gradient:gold-firebrick "$LOGDIR"gradient_burnished.jpg
+
+# Have to do this sort of thing to do colour lookup on a series of
+# images because clut applies to a series of inputs on the command
+# line.
+doParallelConvert() {
+    declare -a montagelist=(${!1})
+
+    local items item currentBatch=0
+    for item in ${montagelist[@]}; do
+        items[$currentBatch]="${items[$currentBatch]} $item"
+        shift
+        let currentBatch=$(( (currentBatch+1)%BMAX ))
+    done
+
+    FRCOUNT=1
+    for (( currentBatch=0; currentBatch<BMAX; currentBatch++ ))
+    do
[…]

### 2017-05-03 movies/movieFast.sh

@@ -1,0 +1,98 @@
+#!/bin/bash
+
+set -m
+
+# The output framewidth for each individual population.
+# As framewidth increases, memory requirements on the server go
+# up. The default for qrsh is enough for up to 200. 300 makes for nice big movies.
+FRAMEWIDTH="200"
+
+# How fast to make the movie go.
+FRAMERATE=25
+
+# MODIFY this to suit your environment.
+LOGDIR='/fastdata/pc1ssj/oculomotor/log/'
+
+# Paths to ImageMagick tools
+MONTAGE='/home/pc1ssj/usr/bin/montage'
+CONVERT='/home/pc1ssj/usr/bin/convert'
+
+POPULATIONS=('Retina_1' 'Retina_2' 'FEF' 'SC_deep' 'GPe' 'SC_sup' 'SNr' 'STN' 'Str_D1' 'Thalamus' 'FEF_add_noise' 'World')
+#             0          1          2     3         4     5        6      7    8        9          10             11
+# Length of the above array: ${#POPULATIONS[@]}
+LAST_ELEMENT=$((${#POPULATIONS[@]}-1))
+
+# The image type to use for the intermediate frames.
+# jpg works fine. For png - images are created by imageMagick, but
+# avconv doesn't convert 'em. pbm: in the convert call, the output
+# file isn't expanded out into many individual files - all the frames
+# are in the single file. (+adjoin fixes that but output is poor
+# quality). bmp works about as well a jpg.
+IMTYPE="jpg"
+
+# Do the split in a multi processor friendly way
+echo "split..."
+for i in `seq 0 $LAST_ELEMENT`; do
+    mkdir -p "$LOGDIR${POPULATIONS[$i]}"
+    split -a 3 -b 2500 "$LOGDIR${POPULATIONS[$i]}"_out_uint8.bin  "$LOGDIR${POPULATIONS[$i]}"/frame_ &
+done
+while fg; do true; done
+
+echo "convert..."
+for i in `seq 0 $LAST_ELEMENT`; do
+    # Convert line (or mogrify) with resize FIXME: Add quality for jpeg loss here.
+    $CONVERT -depth 8 -size 50x50 gray:"$LOGDIR${POPULATIONS[$i]}"/frame_* -resize $FRAMEWIDTHx$FRAMEWIDTH +adjoin "$LOGDIR${POPULATIONS[$i]}"/frame.$IMTYPE &
+done
+while fg; do true; done
+
+# BMAX is number of batches to run the montage commands in.
[…]

### 2017-05-03 movies/movieFast_sebpc.sh

@@ -1,0 +1,102 @@
+#!/bin/bash
+
+set -m
+
+# The output framewidth for each individual population.
+# As framewidth increases, memory requirements on the server go
+# up. The default for qrsh is enough for up to 200. 300 makes for nice big movies.
+FRAMEWIDTH="200"
+
+# How fast to make the movie go.
+FRAMERATE=25
+
+# MODIFY this to suit your environment.
+LOGDIR='/home/seb/src/SpineML_2_BRAHMS/temp/log/'
+
+# Paths to ImageMagick tools
+MONTAGE='/usr/bin/montage'
+CONVERT='/usr/bin/convert'
+
+POPULATIONS=('Retina_1' 'Retina_2' 'FEF' 'SC_deep' 'GPe' 'SC_avg' 'SNr' 'STN' 'Str_D1' 'Thalamus' 'FEF_add_noise' 'World')
+#             0          1          2     3         4     5        6      7    8        9          10             11
+# Length of the above array: ${#POPULATIONS[@]}
+LAST_ELEMENT=$((${#POPULATIONS[@]}-1))
+
+# The image type to use for the intermediate frames.
+# jpg works fine. For png - images are created by imageMagick, but
+# avconv doesn't convert 'em. pbm: in the convert call, the output
+# file isn't expanded out into many individual files - all the frames
+# are in the single file. (+adjoin fixes that but output is poor
+# quality). bmp works about as well a jpg.
+IMTYPE="jpg"
+
+# Do the split in a multi processor friendly way
+echo "split..."
+if [ ! -f "$LOGDIR${POPULATIONS[0]}"_out_uint8.bin ]; then
+    echo "No file $LOGDIR${POPULATIONS[0]}"_out_uint8.bin". Run convertLogs."
+    exit 1
+fi
+for i in `seq 0 $LAST_ELEMENT`; do
+    mkdir -p "$LOGDIR${POPULATIONS[$i]}"
+    split -a 3 -b 2500 "$LOGDIR${POPULATIONS[$i]}"_out_uint8.bin  "$LOGDIR${POPULATIONS[$i]}"/frame_ &
+done
+while fg; do true; done
+
+echo "convert..."
+for i in `seq 0 $LAST_ELEMENT`; do
+    # Convert line (or mogrify) with resize FIXME: Add quality for jpeg loss here.
[…]

### 2017-05-03 movies/qs_movieFast.sh

@@ -1,0 +1,5 @@
+#$ -l h_rt=120:00:00   -l mem=16G
+#$ -P insigneo-notremor
+#$ -q insigneo-notremor.q
+./convertLogs
+./movieFast.sh

### 2017-05-03 papers/vph_2016/abstract.sh

@@ -1,0 +1,7 @@
+#!/bin/bash
+
+# Something like:
+xelatex abstract.tex
+xelatex abstract.tex
+bibtex abstract.tex
+xelatex abstract.tex

### 2017-08-11 papers/integration/omm_integ.tex
Current state of paper with most of the figures now in place

@@
 \title[Integrated brain and biomechanics]{
-  Integrating brain and biomechanical models - a paradigm shift
-  towards neuro-muscular control
+Integrating brain and biomechanical models - a new paradigm
+for understanding  neuro-muscular control
 }
@@
              % and fill this in
-
-\maketitle
-
+%
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\maketitle
+\begin{abstract}
 
-\begin{abstract}
 \section{}
@@
 (FEF), the basal ganglia (BG), and the superior colliculus (SC). In
-the \ccg~model, the ``centre of mass'' of the activity in the deep
+the \ccg~model, the centroid of the activity in the deep
 layers of superior colliculus was assumed to accurately encode the
-location of the eye at the end of the saccade~\cite{someone}. This
-location was used to recalculate the positions of the luminances in
+location of the eye at the end of the
+saccade~(\cite{wurtz_activity_1972,robinson_eye_1972,van_gisbergen_collicular_1987,mcilwain_lateral_1982}).
+This location was used to recalculate the positions of the luminances in
 the eye's frame of reference at each time step. The model included no
@@
 
-To the \ccg~model, we have added a brainstem model (a ``saccadic burst
-generator''), and a biomechanical eye. These will be described below,
-but first we will give an explanation of the modelling framework used.
+To summarize, the \ccg~model takes as \emph{input} the positions of luminances on a topographic map and produces as output a saccade target.
+
+To the \ccg~model, we have added a rate-coded brainstem model (a ``saccadic burst
+generator''), and a biomechanical eye, implemented using the biomechanical modelling framework OpenSim. These will be described below,
+but first we will give a description of the modelling framework used.
 
@@
 used in the model, and how they are connected together. Finally, a
-number of SpineML \e{experiment layer} files describe how the model
+number of SpineML \e{experiment layer} files specify how the model
 described in the network layer can be executed. In the experiment
@@
 model. It was also used to generate the diagrams of the model
-(e.g. Fig.~\ref{brain_model}).
+(e.g. Fig.~\ref{fig:brain_model}).
 
 As a declarative format for model specification, SpineML is agnostic
-about how the model is executed. A number of SpineML simulation
-engines exist, including DAMSON (\mycite{richmond_damson_2015}), GeNN
+about how the model is executed. A number of simulation
+engines can be utilised, including DAMSON (\mycite{richmond_damson_2015}), GeNN
 (\mycite{nowotny_flexible_2011,nowotny_spineml_2014}) and BRAHMS (used
-here). The simulation engine for BRAHMS is called \stob~
+here). The simulation engine incorporating BRAHMS is called \stob~
 (\mycite{cope_spineml_2_brahms_2015-1}). \stob~is a collection of XSLT
@@
 components are integrated into the model: The biomechanical eye model;
-a component which computes the centroid of a neural layer; and a
-component which takes as inputs the eye's rotational state and the
-state of the experimental luminances and projects a retinotopic
+a component which computes the centroid of a neural layer; and a sensory input
+component. The sensory input component takes the eye's rotational state and the
+state of the experimental luminances as its inputs and projects a retinotopic
 activity map into the brain model. Each of these three BRAHMS
 components was hand written in C++. To incorporate these components
-into the present integrated model, a model-specific modification was
-made to the scripts in \stob~(\mycite{cope_spineml_2_brahms_2015}).
+into the SpineML model, a model-specific modification was
+applied in \stob~(\mycite{cope_spineml_2_brahms_2015}) making use of a \stob~feature designed for this purpose (The external.xsl file).
 
-Figure \ref{model_framework} shows the workflow, in which the model
+%\footnote{See the \branch{NoTremor\_Oculomotor\_201603} branch of \url{https://github.com/SpineML/SpineML\_2\_BRAHMS/}}.
+
+Figure \ref{fig:model_framework} shows the workflow, in which the model
 specification files (blue box), a combination of SpineML files and C++
@@
 The brain model, excluding the brainstem, is a re-implementation of
-the \ccg~model. Figure \ref{brain_model} shows the layout of the
+the \ccg~model. Figure \ref{fig:brain_model} shows the layout of the
 populations and the interconnections between them. Each population of
@@
 retinotopic co-ordinate system, roughly matching the known layout of
-the superior colliculus (SC). % FIXME: and frontal eye field?
+the superior colliculus~(\mycite{robinson_eye_1972}). % FIXME: and frontal eye field?
 
@@
 
-(\mycite{robinson_eye_1972}). With the exceptions of the World and
+With the exceptions of the World and
 FEF\_add\_noise populations, each neural element represents an
@@
 \]
-$R_N$ is a random number between 0 and 1 drawn from a
-normal distribution and introduces noise to the activation of the
-neural element.
+$R_N$ is a random number drawn from a
+standard normal distribution ($\sigma$=1, $\mu$=0) and introduces noise
+to the activation of the neural element.
 
-The output, $y$, of LINlinear is related to the activation by the
+The output, $y$, of LINlinear is related to the activation $a$ by the
 piecewise linear transfer function
@@
 positive rotation about the $x$ axis in a right-handed Cartesian
-coordinate system results in an "upward movement" of the fovea's view
+coordinate system results in an upward movement of the fovea's view
 of the environment. Note that a positive rotation about the $y$ axis
-results in a "leftward movement".
+results in a \emph{leftward} movement.
+
+Note that the mapping encompases the entire visual field. The value of
+$\phi$ is allowed to vary from 0 to 360\degrees along its axis.
+Effectively, the two contralateral colliculi are incorporated into a
+single, square map, avoiding the need to carry out `colliculus
+gluing'~\cite{tabareau_geometry_2007}.
 
@@
 
-Figure \ref{mapping} shows the result of the mapping for a view of two
+Figure \ref{fig:mapping} shows the result of the mapping for a view of two
 cross-shaped luminances. One cross illuminates the fovea, which
@@
 
-It is important to note that in practice there are edge effects within
-the model which prevent this theoretical mapping from holding
-perfectly. The most significant of these is the result of the diffuse
-excitation from STN to GPe... etc % FIXME Where are the edge effects
-                                  % most prevalent? In BG I think
-
 \subsubsection{Network}
@@
 Briefly, the model consists of input from the World population
-producing activity in an ``express'' pathway to superior colliculus
+producing activity in an `express' pathway to superior colliculus
 and simultaneously in cortex, represented here by the FEF
@@
 Connections shown in red are one to one connections; dark blue
-connections indicate a connectivity pattern which ``fans out'' with a 2-D
+connections indicate a connectivity pattern which `fans out' with a 2-D
 Gaussian kernel; lighter blue connections from STN to SNr and GPe are
@@
 activity in opposite hemispheres of the field of view (refs). The
-tecto-tectal inhibitory connection is \em{not} present in the \ccg
+tecto-tectal inhibitory connection is \emph{not} present in the \ccg
 model.
@@
 formation (ref). In this model, we implement a network based
-on \mycite{gancarz_neural_1998}.
+on \cite{gancarz_neural_1998}.
 
@@
 
-Patras work here.
+% Possibly introductory paragraph here.
+
+% Patras - what about a figure here?
+
+% EYE MODEL DESCRIPTION HERE
+The biomechanical eye model, implemented using the OpenSim framework
+\cite{seth_opensim:_2011}, is anatomically represented by a sphere of
+uniform mass distribution. The diameter of the eye is 24 mm for adults,
+with small variations between individuals; the mass of the eye is 7.5 grams.
+The eyeball is actuated by six extraocular muscles
+(EOMs). The EOMs are arranged in three pairs forming a cone inside the
+orbit with the apex being located inside the cranium in a tendonous
+ring called the annulus of Zinn. An important feature of the
+oculomotor system which greatly affects its overall behavior is the
+existence of dynamic EOM pulleys. Their role is to guide the pivot
+point of the EOMs. In our model, a pulley for each EOM has been
+modeled by a point on the orbit whose location depends on the current
+eye orientation.
+
+%EOM dynamics
+The force applied by EOMs is controlled by an excitatory signal
+supplied by motoneurons in the brainstem. The dynamics of muscular
+forces can be split into: 1) The elasticity of the muscles. 2) A delay
+between the onset of the afferent excitatory signal and the actual
+muscle contraction, caused by the transmission time of the action
+potentials and by the necessary calcium release at the muscle
+fibres. We developed a custom extraocular muscle model which captures
+these features.
+
+%Orbital fat force
+Passive forces due to the fatty tissues inside the eye orbit also
+affect eye dynamics. Their role is critical in eliminating the
+influence of head and body movements. We incorporated a custom torque, $\mathbf{t}$,
+which acts like a rotational spring-damper apparatus, resisting
+eyeball movements. It has elastic and viscous properties governed by
+$\mathbf{t} = -K\mathbf{R}-C\mathbf{U}$ where $\mathbf{R}$ is the
+eye's orientation and $\mathbf{U}$ is its angular velocity. $K$ and
+$C$ are constants.
 
 % Section - description of the integration
-\subsection{Integrating the models}
+\subsection{Integrating the models and closing the loop}
 
@@
 % dopamine, latency vs gap.
+%
+% The importance of an even sized hill of activity in SC_deep. The difficulties of achieving this.
 
@@
 developed the saccade generator brainstem model. SJ performed the
-technical integration of the biomechanical eye. DS, CP and KM
-developed the biomechanical eye model. SJ wrote the manuscript. KG
-conceived the experiment. % FIXME: This needs correcting/developing.
+technical and scientific integration of the biomechanical eye.
+DS, CP and KM developed the biomechanical eye model. SJ wrote the 
+manuscript. KG conceived the experiment. % FIXME: This needs correcting/developing.
 
@@
 \end{center}
-\textbf{\refstepcounter{figure}\label{intro_graphic} Figure \arabic{figure}.}
-{ An isolated brain model. Crafted inputs are introduced into one of
+\textbf{\refstepcounter{figure}\label{fig:intro_graphic} Figure \arabic{figure}.}
+{ \textbf{fig:intro\_graphic} An isolated brain model. Crafted inputs are introduced into one of
 the model's n state variables. The output of another of the state
@@
 \end{center}
-\textbf{\refstepcounter{figure}\label{model_framework} Figure \arabic{figure}.}
-{ The model framework. The model is specified using a combination of
+\textbf{\refstepcounter{figure}\label{fig:model_framework} Figure \arabic{figure}.}
+{ \textbf{fig:model\_framework} The model framework. The model is specified using a combination of
 declarative XML files and hand-coded C++. These original model
@@
 \end{center}
-\textbf{\refstepcounter{figure}\label{mapping} Figure \arabic{figure}.}
-{ Representative mapping from eye's frame of reference in cartesian
+\textbf{\refstepcounter{figure}\label{fig:mapping} Figure \arabic{figure}.}
+{ \textbf{fig:mapping} Representative mapping from eye's frame of reference in cartesian
 coordinates to retinotopic coordinates. (a) The mapping of luminances
@@
 
+\begin{figure}[h!]
+\begin{center}
+\includegraphics[width=0.5\textwidth]{./figures/Brain_Stem_1channel.png}
+\end{center}
+\textbf{\refstepcounter{figure}\label{fig:sbg} Figure \arabic{figure}.}
+{ \textbf{fig:sbg} One pair of channels of the saccadic burst generator (SBG) for left (cyan)
+or right (green) movements. Collicular activity in SC\_avg excites the channels
+via SBG weight maps. Each box represents a neural population and shows the
+population name, the number of neural elements (here 2500 or 1) and the SpineML
+component name; \emph{LIN} for Leaky integrator or \emph{integrator}. Key: LLBN:
+Long lead burst neurons; IBN: Inhibitory burst neurons; OPN: Omnipause neurons;
+EBN: Excitatory burst neurons; TN: Tonic neurons; MN: Motoneurons.}
+\end{figure}
+
 \begin{figure}[htb!]
@@
 \end{center}
-\textbf{\refstepcounter{figure}\label{brain_model} Figure \arabic{figure}.}
-{ This is the Brain Model}
+\textbf{\refstepcounter{figure}\label{fig:brain_model} Figure \arabic{figure}.}
+{ \textbf{fig:brain\_model}  The brain model.
+This is the SpineCreator `network layer' view of the model.
+Each box represents a neural population with 2500 elements, arranged in a 50$\times$50 grid.
+The SpineML component name is printed on the bottom right corner of each population box and the population name is at the top.
+The overall connectivity between populations is represented by the projection arrows with the colour indicating the connectivity scheme (one-to-one connections are red, gaussian kernel connections are dark blue and so on).
+Excitatory connections have arrowheads and inhibitory connections have circles, although for details of the behaviour of the connections, the weight-update and post-synapse components must be studied.
+Briefly, the model comprises a \emph{World} population, into which a retinotopically organised view of the world is introduced.
+This information is passed into cortical populations (FEF) and subcortical populations (SC) via a simple model of the retina.
+These feed a cortico-thalamo-basal ganglia loop, which selects which region of the deep layer of superior colliculus should be disinhibited, allowing activity to build up therein.
+The five populations comprising the basal ganglia are enclosed in a grey outline.
+Note that substantia nigra pars compacta is not modelled here, instead the level of dopamine in the striatum is set via a parameter in the Str\_D1 and Str\_D2 populations}
+\end{figure}
+
+\begin{figure}[htb!]
+\begin{center}
+\includegraphics[width=\textwidth]{./figures/weightmaps.png}
+\end{center}
+\textbf{\refstepcounter{figure}\label{fig:weightmaps} Figure \arabic{figure}.}
+{ \textbf{fig:weightmaps} Weight maps}
+\end{figure}
+
+\begin{figure}[htb!]
+\begin{center}
+\includegraphics[width=0.8\textwidth]{./figures/outmany.png}
+\end{center}
+\textbf{\refstepcounter{figure}\label{fig:outmany} Figure \arabic{figure}.}
+{ \textbf{fig:outmany} Representative single saccades.}
+\end{figure}
+
+\begin{figure}[htb!]
+\begin{center}
+\includegraphics[width=0.8\textwidth]{./figures/sacc_vs_targetpos.png}
+\end{center}
+\textbf{\refstepcounter{figure}\label{fig:sacc_vs_targ} Figure \arabic{figure}.}
+{ \textbf{fig:sacc\_vs\_targ} Accuracy at different target eccentricities for fixation luminance 0.2 and target luminance 0.3.}
+\end{figure}
+
+\begin{figure}[htb!]
+\begin{center}
+\includegraphics[width=0.8\textwidth]{./figures/outrtn.png}
+\end{center}
+\textbf{\refstepcounter{figure}\label{fig:outrtn} Figure \arabic{figure}.}
+{ \textbf{fig:outrtn} There and back - a saccade to a target, followed by return to the original fixation.}
+\end{figure}
+
+\begin{figure}[htb!]
+\begin{center}
+\includegraphics[width=0.9\textwidth]{./figures/errorsurface.png}
+\end{center}
+\textbf{\refstepcounter{figure}\label{fig:errorsurface} Figure \arabic{figure}.}
+{ \textbf{fig:errorsurface} Error surface}
+\end{figure}
+
+\begin{figure}[htb!]
+\begin{center}
+\includegraphics[width=0.45\textwidth]{./figures/lat_vs_dopamine.png}
+\end{center}
+\textbf{\refstepcounter{figure}\label{fig:lat_vs_dop} Figure \arabic{figure}.}
+{ \textbf{fig:lat\_vs\_dop} Latency vs.~dopamine.}
+\end{figure}
+
+\begin{figure}[htb!]
+\begin{center}
+\includegraphics[width=0.45\textwidth]{./figures/sacc_vs_lum.png}
+\end{center}
+\textbf{\refstepcounter{figure}\label{fig:lat_vs_lum} Figure \arabic{figure}.}
+{ \textbf{fig:lat\_vs\_lum} Latency vs.~luminance.}
+\end{figure}
+
+\begin{figure}[htb!]
+\begin{center}
+\includegraphics[width=0.8\textwidth]{./figures/targ_w_distr.png}
+\end{center}
+\textbf{\refstepcounter{figure}\label{fig:targ_w_distr} Figure \arabic{figure}.}
+{ \textbf{fig:targ\_w\_distr} Effect of a distractor on single saccade.}
 \end{figure}

### 2017-08-14 papers/integration/omm_integ.tex

@@
 \def\firstAuthorLast{James {et~al.}}
-\def\Authors{Sebastian James\,$^{1,2,*}$, Alexander Blenkinsop\,$^{1,2}$, \\
-  Alexander Cope\,$^3$, Sean Anderson\,$^{2,4}$, Dimitrios Stanev\,$^5$, \\
-  Chris Papapavlou\,$^5$, Konstantinos Moustakas\,$^5$, Kevin Gurney\,$^{1,2}$}
+\def\Authors{Sebastian James\,$^{1,2,*}$, Chris Papapavlou\,$^5$, Alexander Blenkinsop\,$^{1,2}$, \\
+  Alexander Cope\,$^3$,  \\
+  Sean Anderson\,$^{2,4}$, Konstantinos Moustakas\,$^5$, Kevin Gurney\,$^{1,2}$}
 % Affiliations should be keyed to the author's name with superscript
@@
 In addition to the brain model components, all of which are
-code-generated using \stob~as described above, three hand-written
-components are integrated into the model: The biomechanical eye model;
-a component which computes the centroid of a neural layer; and a sensory input
-component. The sensory input component takes the eye's rotational state and the
-state of the experimental luminances as its inputs and projects a retinotopic
-activity map into the brain model. Each of these three BRAHMS
-components was hand written in C++. To incorporate these components
-into the SpineML model, a model-specific modification was
-applied in \stob~(\mycite{cope_spineml_2_brahms_2015}) making use of a \stob~feature designed for this purpose (The external.xsl file).
-
-%\footnote{See the \branch{NoTremor\_Oculomotor\_201603} branch of \url{https://github.com/SpineML/SpineML\_2\_BRAHMS/}}.
-
-Figure \ref{fig:model_framework} shows the workflow, in which the model
-specification files (blue box), a combination of SpineML files and C++
-code, are processed (green box) into a BRAHMS system (red box).
+code-generated using \stob~as described above, two hand-written
+components are integrated into the model: The biomechanical eye model
+and a sensory input component. The sensory input component takes the
+eye's rotational state and the state of the experimental luminances
+and projects a retinotopic activity map into the brain model. Both of
+these BRAHMS components were hand-written in C++. To incorporate these
+components into the SpineML model, a model-specific modification was
+applied in \stob~(\mycite{cope_spineml_2_brahms_2015}) making use of
+a \stob~feature designed for this purpose (The external.xsl file).
+
+Figure \ref{fig:model_framework} shows the workflow, in which the
+model specification files (blue box - a combination of SpineML files
+and C++ code), are processed (green box) into a BRAHMS system (red
+box).
 
@@
 
-With the exceptions of the World and
-FEF\_add\_noise populations, each neural element represents an
-activation whose dynamics depend on the component definition. In the
-brain model, there are six different components in use; LINlinear,
-LINlinearNoisy, LINret, LINexp, D1MSN and D2MSN.
+With the exceptions of the World and FEF\_add\_noise populations, each
+neural element represents an activation; the activation is governed by
+a first order differential equation specified in the SpineML
+component. In the brain model, there are six different components in
+use: LINlinear; LINret; LINexp; D1MSN and D2MSN.
 
@@
 \[
-   a_{in} = A(1-s_a)+0.01 R_N
+   a_{in} = A(1-s_a)+\alpha R_N
 \]
@@
 \]
-$R_N$ is a random number drawn from a
-standard normal distribution ($\sigma$=1, $\mu$=0) and introduces noise
-to the activation of the neural element.
+$R_N$ is a random number drawn from a standard normal distribution
+($\sigma$=1, $\mu$=0) and introduces noise to the activation of the
+neural element, with the parameter $\alpha$ controlling the noise
+amplitude.
 
@@
 
-LINlinearNoisy is identical to LINlinear with the single exception
-that the level of noise is increased. This means that the equation for
-$a_{in}$ must be rewritten:
-\[
-   a_{in} = A(1-s_a)+0.2 R_N
-\]
 The LINret component used for the retinal populations is again similar
@@
 
+The D1MSN and D2MSN components are both leaky integrators, similar to
+LINlinear. They differ in that they have no shunting inhibition and a
+dopamine parameter dependent modulation of the input activation, so
+that their equations for $a_{in}$ are:
+\[
+   a_{in}^{D1} = (0.2 + d)A + 0.01 R_N
+\]
+for D1MSN, and
+\[
+   a_{in}^{D2} = (1 - d)A + 0.01 R_N
+\]
+for D2MSN, where $d$ is a dopamine parameter. Increasing dopamine from
+0 to 1 enhances the activation in the D1 model neurons, whereas it
+decreases the activation of the D2 model neurons, in line with
+experimental observations~\cite{refs}. Note that the equation for
+$a_{in}^{D1}$ differs from that used in the \ccg~model, for which the
+cortico-striatal weights are multiplied by $(1+d)$ rather than $(0.2+d)$
+
+The equations given above apply to each element in the population
+whose behaviour is defined by the component. The value of the
+activation $A$ (and where relevant the shunting input, $S$, also) is
+determined by summing the weighted inputs to the population:
+\[
+A = \sum_{i}w_i^{act} x_i^{act}
+\]
+\[
+S = \sum_{i}w_i^{sh} x_i^{sh}
+\]
+
 %
@@
 
-\subsubsection{Population activity}
+\subsubsection{Population activity and retinotopic mapping}
 
@@
 grid, with positions on the grid representing a retinotopic
-mapping. Locations on the grid specify radial and azimuthal angles r
+mapping. Locations on the grid specify radial and azimuthal angles $r$
 and $\phi$ for the location of activity on the retina relative to the
-fovea. r and $\phi$ can be converted into rotations about the $x$ and
+fovea. $r$ and $\phi$ can be converted into rotations about the $x$ and
 $y$ Cartesian axes ($\theta_x$ and $\theta_y$). The result of a
@@
 of the environment. Note that a positive rotation about the $y$ axis
-results in a \emph{leftward} movement.
+results in a \emph{leftward} movement of the eye's focal point, with
+respect to the world.
 
 Note that the mapping encompases the entire visual field. The value of
-$\phi$ is allowed to vary from 0 to 360\degrees along its axis.
+$\phi$ is allowed to vary from 0$\deg$ to 360$\deg$ along its axis.
 Effectively, the two contralateral colliculi are incorporated into a
@@
 The magnification factor, $M_f$, gives the relationship between the
-radial angle r and the retinal neural density. It is given by:
+radial angle $r$ and the retinal neural density. It is given by:
 \[
@@
 
-Figure \ref{fig:mapping} shows the result of the mapping for a view of two
-cross-shaped luminances. One cross illuminates the fovea, which
+Figure \ref{fig:mapping} shows the result of the mapping for a view of
+two cross-shaped luminances. One cross illuminates the fovea, which
 results in a large comb-shape of activity. The more peripheral cross
-produces an indistinct object centered at a larger value of r.
+produces (in FEF) an indistinct object centered at a larger value of
+r.
 
@@
 
-Briefly, the model consists of input from the World population
-producing activity in an `express' pathway to superior colliculus
-and simultaneously in cortex, represented here by the FEF
-population. The express pathway causes short latency activity in the
-superficial superior colliculus, which directly innervates the deeper
-layers of the superior colliculus (SC\_deep). Activity in FEF
-generates firing in a thalamo-cortico-basal ganglia loop. The output
-of the basal ganglia is the substantia nigra pars reticulata (SNr)
-which tonically inhibits SC\_deep. If a location of activity in FEF is
-able to dominate selection in the basal ganglia circuit, the
-corresponding location in SNr will dis-inhibit and activity will build
-up in SC\_deep encoding the saccade end point.
+Briefly, the model consists of input from the World population (see
+Fig.~\ref{fig:brain_model}, green population box) producing activity
+in an `express' pathway to superior colliculus (purple) and
+simultaneously in cortex, represented here by the FEF population (grey
+boxes in Fig.~\ref{fig:brain_model}). The express pathway causes short
+latency activity in the superficial superior colliculus, which
+directly innervates the deeper layers of the superior colliculus
+(SC\_deep). Activity in FEF generates firing in a
+thalamo-cortico-basal ganglia loop. The output of the basal ganglia is
+the substantia nigra pars reticulata (SNr) which tonically inhibits
+SC\_deep. If a location of activity in FEF is able to dominate
+selection in the basal ganglia circuit, the corresponding location in
+SNr will dis-inhibit and activity will build up in SC\_deep encoding
+the saccade end point.
 
 Connections shown in red are one to one connections; dark blue
-connections indicate a connectivity pattern which `fans out' with a 2-D
-Gaussian kernel; lighter blue connections from STN to SNr and GPe are
-diffuse, all to all connections and connections in green are one to one
-connections that decay towards the fovea so that foveal activity in
-FEF does not swamp the basal ganglia which would prevent peripheral
-luminances from being selected.
+projections indicate a connectivity pattern which `fans out' with a
+2-D Gaussian kernel; lighter blue connections from STN to SNr and GPe
+are diffuse, all-to-all connections and projections coloured green are
+one-to-one connections that decay towards the fovea so that foveal
+activity in FEF does not swamp the basal ganglia which would prevent
+peripheral luminances from ever being selected.
 
@@
 activity in opposite hemispheres of the field of view (refs). The
-tecto-tectal inhibitory connection is \emph{not} present in the \ccg
-model.
+tecto-tectal inhibitory connection is \emph{not} present in
+the \ccg~model.
 
@@
 
-Neurons in the deep layers of the superior colliculus called long lead
-burst neurons innervate excitatory burst neurons in the reticular
-formation (ref). In this model, we implement a network based
-on \cite{gancarz_neural_1998}.
+In this model, we implement a saccadic burst generator (SBG) based
+on \cite{gancarz_neural_1998}. The SBG network for two of the model's
+six channels is shown in Fig.~\ref{fig:sbg}. Activity from the output
+layer of superior colliculus (SC\_avg) is fed into each channel, which
+sums the activity it receives and processes it in populations each of
+a single neural element representing all the neurons in that
+population.
+
+Neurons in the deep
+layers of the superior colliculus called long lead burst neurons
+innervate excitatory burst neurons in the reticular formation (REF,
+and check if LLBNs are really in SC).
+
+Alex B to write this section?
+
+Note that inhibition from IBN populations is fed back - or is this
+detail for the `integration' subsection?
 
@@
 
-% Section - description of the integration
+% Section - description of the integration. scientific and
+% technical. Already
 \subsection{Integrating the models and closing the loop}
+
+The \ccg~model closed its loop by passing the centroid of activity in
+SC\_deep (once it had surpassed a threshold) back to the code that
+controlled the world, which would then use this location to
+instantaneously change the model's view of the world. In our extended
+model, it was necessary to connect the output of the brain model back
+to its input via the saccadic burst generator model and the
+biomechanical eye. The resulting state of the eye, rather than the
+centroid of the superior colliculus, was used to compute the input to
+the brain, given the luminances visible in the world.
+
+% Brain to SBG, seeing as that's how I explained it above.
+A number of studies have considered the form of the connection between
+the deeper layers of the superior colliculus and the saccadic burst
+generator~\cite{van_gisbergen_experimental_1985,ottes_visuomotor_1986,waitzman_superior_1991,groh_converting_2001,arai_model_2004,goossens_dynamic_2006,tabareau_geometry_2007,van_opstal_linear_2008,goossens_optimal_2012},
+which has become known as the spatial temporal transform (STT).  The
+spatial part of the STT is thought to be implemented by a
+weight-mapping~\cite{tabareau_geometry_2007,arai_model_2004} and we
+follow this idea.
+
+% Words along the lines of:
+Arai and co-workers trained their neural network model to discover the
+weight map~\cite{arai_model_2004}.
+
+% Then...
+Tabareau and co-workers wrote down the theoretical form of the weight
+map and found it matches well to the results of Arai et
+al.~\cite{tabareau_geometry_2007}.
+
+The approach of Arai~et.~al. was
+not feasible with the present model due to the length of time required
+to run the model, its stochasticity and the increased size of the maps
+here compared with those used by Arai~et.~al.
+
+The saccadic burst generator model was originally conceived with the
+assumption of a step input~\cite{gancarz_neural_1998}.
+
+% SBG to worldDataMaker
+The output signals from the six channels of the SBG were connected to
+the six motoneuron inputs of the biomechanical eye. The signal was
+normalised; a value of 1 meaning that all the motoneurons in the
+output population were firing at their maximum rate and the force
+exerted by the relevant extraocular muscle was maximal. Channels
+innervated extraocular muscles as follows: Up: superior rectus; Down:
+inferior rectus; Right: medial rectus; Left: lateral rectus; Z+:
+superior oblique; Z-: inferior oblique. Because the medial rectus
+induces a rightward rotation of the eye, our single virtual eye is
+a \emph{left} eye. The OpenSim implementation of the biomechanical eye
+was `wrapped' (in the software sense) in a BRAHMS component. This made
+it possible to integrate the OpenSim model into the BRAHMS
+framework. The wrapper ensured that the input and output signals were
+correctly transferred and, importantly, handled the disparity in the
+solver timesteps used in the OpenSim model (25~ms) and the neural
+model (1~ms). This was achieved by having the BRAHMS wrapper create a
+separate thread to run the OpenSim model. The BRAHMS wrapper component
+was called on each 1 ms timestep, receiving the instantaneous
+activations from the motoneurons in the SBG. These activations, and
+the current simulation time, were written into a shared memory area,
+accessible by the OpenSim thread. Running independently, the OpenSim
+thread would update its inputs (using the most recent values in the
+shared memory area) whenever the simulation time had increased by 25
+ms. It would then recompute its outputs (the rotational state of the
+eye) and write these into the same, shared memory. The BRAHMS wrapper
+would update its outputs whenever they were changed in the shared
+memory by the OpenSim thread. A direct connection of the six outputs
+of the BRAHMS eye model component to the six inputs of the
+worldDataMaker BRAHMS component was specified in
+the \stob~external.xsl file.
+
+% worldDataMaker to brain, but Re-work:
+The eye model outputs its rotational state at each
+timestep. The rotational state is used to compute the view of the
+world in the eye's frame of reference. To simplify
+the calculation, the luminances exist on a spherical surface at the
+centre of which is the eye. A hand-coded BRAHMS component called
+worldDataMaker computes the projection of the luminances into the
+eye's frame of reference and then converts this representation into a
+retinotopic map to pass into the brain model. The input to the brain
+model is thus able to change continuously, on every timestep, rather
+than in a step-wise fashion when a saccade occurs, as in the \ccg~model.
+
+In the worldDataMaker BRAHMS component, the rotational state of the
+eye was used to construct Euler rotation matrices which transformed
+between the world's frame of reference and the eye's frame of
+reference. The worldDataMaker component received a specification of
+the world luminances in a JSON file called luminances.json at the
+start of each simulation. luminances.json specified the position,
+shape, size, luminance, appearance time and disappearance time of an
+arbitrary number of luminances. With this information, the
+instantaneous rotational state of the eye and the parameters of the
+retinotopic transform, it was able to compute the instantaneous input
+to the brain model.
 
@@
 %
-% The importance of an even sized hill of activity in SC_deep. The difficulties of achieving this.
+% The importance of an even sized hill of activity in SC_deep. The
+% difficulties of achieving this.
+
+\subsection{Weight maps (here?)}
+
+\subsection{Single saccades}
 
@@
 developed the saccade generator brainstem model. SJ performed the
-technical and scientific integration of the biomechanical eye.
-DS, CP and KM developed the biomechanical eye model. SJ wrote the 
-manuscript. KG conceived the experiment. % FIXME: This needs correcting/developing.
+technical and scientific integration of the biomechanical eye.  CP and
+KM developed the biomechanical eye model. SJ wrote the manuscript; SA,
+AB, KG and KM contributed to the manuscript. KG conceived the
+project.
 
@@
 \textbf{\refstepcounter{figure}\label{fig:intro_graphic} Figure \arabic{figure}.}
-{ \textbf{fig:intro\_graphic} An isolated brain model. Crafted inputs are introduced into one of
-the model's n state variables. The output of another of the state
-variables implies behavioural change or onset.}
+{ \textbf{fig:intro\_graphic} An isolated brain model. Crafted inputs
+are introduced into one of the model's n state variables. The output
+of another of the state variables implies behavioural change or
+onset.}
 \end{figure}
@@
 \textbf{\refstepcounter{figure}\label{fig:mapping} Figure \arabic{figure}.}
-{ \textbf{fig:mapping} Representative mapping from eye's frame of reference in cartesian
-coordinates to retinotopic coordinates. (a) The mapping of luminances
-in the eye's frame of reference. The world input is pre-defined by a
-JSON configuration file. luminance position, size and shape can be
-defined in this file, along with the times at which luminances appear
-and disappear. The worldDataMaker.cpp code computes the locations of
-the luminances in the eye's frame of reference, given its rotational
-state. Here, there are two cross shaped luminances, one at the
-fixation point (0,0) and one at a peripheral position (4,-10). (b) The
-locations of the luminances in the eye's frame of reference are then
-converted into retinotopic coordinates, with centrally located
-luminances being represented at low values of $r$ and more peripheral
-luminances having higher values of $r$. $phi$ encodes rotational
-angle: 12.5 is up, [etc etc]. The output of the World component is fed
-into FEF\_add\_noise and into the retinal neuron populations. (c) The
-FEF\_add\_noise populations adds a level of noise to the signal
-representing processing of the signal in visual cortex. (d) The
-activity in FEF is the input to the basal ganglia and one input to
-superior collicus.}
+{ \textbf{fig:mapping} Representative mapping from eye's frame of
+reference in cartesian coordinates to retinotopic coordinates. (a) The
+mapping of luminances in the eye's frame of reference. The world input
+is pre-defined by a JSON configuration file. Luminance position, size
+and shape can be defined in this file, along with the times at which
+luminances appear and disappear. The worldDataMaker.cpp code computes
+the locations of the luminances in the eye's frame of reference, given
+its rotational state. It also computes a 2D gaussian convolution of
+the luminances. Here, there are two cross shaped luminances spanning
+10$\deg$, one of value 0.8 at the fixation point (0,0) and one of
+value 0.5 at a peripheral position (0,-12$\deg$). (b) The locations of
+the luminances in the eye's frame of reference are then converted into
+retinotopic coordinates, with centrally located luminances being
+represented at low values of $r$ and more peripheral luminances having
+higher values of $r$. $\phi$ encodes rotational angle: 1 and 50 encode
+upward movement; 13 is left; 25 is down; 37 is right. The output of
+the World component is fed into FEF\_add\_noise and into the retinal
+neuron populations. The colour map makes it possible to distinguish
+between the two crosses. (c) The FEF\_add\_noise populations adds a level
+of noise to the signal representing processing of the signal in visual
+cortex. (d) A Gaussian projection from FEF\_add\_noise to FEF further
+blurs the activity in FEF. FEF is the input to the basal ganglia and
+one input to superior collicus.}
+\end{figure}
+
+\begin{figure}[htb!]
+\begin{center}
+\includegraphics[width=0.9\textwidth]{./figures/Brain_Model.png}
+\end{center}
+\textbf{\refstepcounter{figure}\label{fig:brain_model} Figure \arabic{figure}.}
+{ \textbf{fig:brain\_model} The brain model. This is the SpineCreator
+`network layer' view of the model. Each box represents a neural
+population with 2500 elements, arranged in a 50$\times$50 grid. The
+SpineML component name is printed on the bottom right corner of each
+population box and the population name is at the top. The overall
+connectivity between populations is represented by the projection
+arrows with the colour indicating the connectivity scheme (one-to-one
+connections are red, gaussian kernel connections are dark blue and so
+on). Excitatory connections have arrowheads and inhibitory connections
+have circles, although for details of the behaviour of the
+connections, the weight-update and post-synapse components must be
+studied. Briefly, the model comprises a \emph{World} population, into
+which a retinotopically organised view of the world is
+introduced. This information is passed into cortical populations (FEF)
+and subcortical populations (SC) via a simple model of the
+retina. These feed a cortico-thalamo-basal ganglia loop, which selects
+which region of the deep layer of superior colliculus should be
+disinhibited, allowing activity to build up therein. The five
+populations comprising the basal ganglia are enclosed in a grey
+outline. Note that substantia nigra pars compacta is not modelled
+here, instead the level of dopamine in the striatum is set via a
+parameter in the Str\_D1 and Str\_D2 populations}
 \end{figure}
@@
 \textbf{\refstepcounter{figure}\label{fig:sbg} Figure \arabic{figure}.}
-{ \textbf{fig:sbg} One pair of channels of the saccadic burst generator (SBG) for left (cyan)
-or right (green) movements. Collicular activity in SC\_avg excites the channels
-via SBG weight maps. Each box represents a neural population and shows the
-population name, the number of neural elements (here 2500 or 1) and the SpineML
-component name; \emph{LIN} for Leaky integrator or \emph{integrator}. Key: LLBN:
-Long lead burst neurons; IBN: Inhibitory burst neurons; OPN: Omnipause neurons;
-EBN: Excitatory burst neurons; TN: Tonic neurons; MN: Motoneurons.}
+{ \textbf{fig:sbg} One pair of channels of the saccadic burst
+generator (SBG) for left (cyan) or right (green) movements. Collicular
+activity in SC\_avg excites the channels via SBG weight maps. Each box
+represents a neural population and shows the population name, the
+number of neural elements (here 2500 or 1) and the SpineML component
+name; \emph{LIN} for Leaky integrator or \emph{integrator}. Key: LLBN:
+Long lead burst neurons; IBN: Inhibitory burst neurons; OPN: Omnipause
+neurons; EBN: Excitatory burst neurons; TN: Tonic neurons; MN:
+Motoneurons.}
 \end{figure}
@@
 \begin{center}
-\includegraphics[width=0.9\textwidth]{./figures/Brain_Model.png}
-\end{center}
-\textbf{\refstepcounter{figure}\label{fig:brain_model} Figure \arabic{figure}.}
-{ \textbf{fig:brain\_model}  The brain model.
-This is the SpineCreator `network layer' view of the model.
-Each box represents a neural population with 2500 elements, arranged in a 50$\times$50 grid.
-The SpineML component name is printed on the bottom right corner of each population box and the population name is at the top.
-The overall connectivity between populations is represented by the projection arrows with the colour indicating the connectivity scheme (one-to-one connections are red, gaussian kernel connections are dark blue and so on).
-Excitatory connections have arrowheads and inhibitory connections have circles, although for details of the behaviour of the connections, the weight-update and post-synapse components must be studied.
-Briefly, the model comprises a \emph{World} population, into which a retinotopically organised view of the world is introduced.
-This information is passed into cortical populations (FEF) and subcortical populations (SC) via a simple model of the retina.
-These feed a cortico-thalamo-basal ganglia loop, which selects which region of the deep layer of superior colliculus should be disinhibited, allowing activity to build up therein.
-The five populations comprising the basal ganglia are enclosed in a grey outline.
-Note that substantia nigra pars compacta is not modelled here, instead the level of dopamine in the striatum is set via a parameter in the Str\_D1 and Str\_D2 populations}
+\includegraphics[width=\textwidth]{./figures/weightmaps.png}
+\end{center}
+\textbf{\refstepcounter{figure}\label{fig:weightmaps} Figure \arabic{figure}.}
+{ \textbf{fig:weightmaps} Weight maps for the connections between the
+output layer of superior colliculus and the six long lead burst
+neurons of the saccadic burst generator model. Each map increases
+exponentially with increasing $r$, multiplied by cosine($\phi$) about
+its `active' axis. \textbf{FIXME: Left \& Right are wrong way round}}
 \end{figure}
@@
 \begin{center}
-\includegraphics[width=\textwidth]{./figures/weightmaps.png}
-\end{center}
-\textbf{\refstepcounter{figure}\label{fig:weightmaps} Figure \arabic{figure}.}
-{ \textbf{fig:weightmaps} Weight maps}
-\end{figure}
-
-\begin{figure}[htb!]
-\begin{center}
 \includegraphics[width=0.8\textwidth]{./figures/outmany.png}
@@
 \textbf{\refstepcounter{figure}\label{fig:outmany} Figure \arabic{figure}.}
-{ \textbf{fig:outmany} Representative single saccades.}
+{ \textbf{fig:outmany} Representative single saccades. a) Trajectories
+from 9 saccades to a single target at 9 different locations. In each
+case, a fixation cross luminance of magnitude 0.2 was displayed at
+(0,0), the start position of the eye, until time 0.4~s. The target
+luminance, magnitude 0.3 was illuminated at time 0.4~s. Trajectory
+shape is dependent on the target position, and there is a variable
+amount of error in the end-points achieved by the model. Colour is
+used in this diagram as an aid to distinguishing different saccades
+and their targets; for a given saccade, the target location is given
+by the cross of the same colour closest to the end of the
+trajectory. b) The three rotational components of the `blue' saccade,
+to target location (-7,-7). c) The three rotational components of the
+`red' saccade, to target location (0,-10).}
 \end{figure}

### 2017-08-15 papers/integration/omm_integ.tex
Work in progress on paper, am now going to switch to sharelatex for the rest of the paper development

@@
 The integrated brain and biomechanical model described here is a
-development of the model in \mycite{alex_cope_integrative_2015},
+development of the model in \mycite{cope_basal_2017},
 referred to here as the \ccg~model. This was a rate-coded neural
@@
 LINlinear. They differ in that they have no shunting inhibition and a
-dopamine parameter dependent modulation of the input activation, so
-that their equations for $a_{in}$ are:
+dopamine parameter that modulates the input activation, so
+that their equations for $a_{in}$ are thus:
 \[
@@
 \]
-for D1MSN, and
 \[
@@
 \]
-for D2MSN, where $d$ is a dopamine parameter. Increasing dopamine from
-0 to 1 enhances the activation in the D1 model neurons, whereas it
-decreases the activation of the D2 model neurons, in line with
-experimental observations~\cite{refs}. Note that the equation for
-$a_{in}^{D1}$ differs from that used in the \ccg~model, for which the
-cortico-striatal weights are multiplied by $(1+d)$ rather than $(0.2+d)$
-
-The equations given above apply to each element in the population
-whose behaviour is defined by the component. The value of the
-activation $A$ (and where relevant the shunting input, $S$, also) is
-determined by summing the weighted inputs to the population:
+where $d$ is a dopamine parameter. Varying dopamine from 0 to 1
+enhances the activation in the D1 model, whereas it decreases
+the activation of the D2 model elements, in line with experimental
+observations~\cite{refs}. Note that the equation for $a_{in}^{D1}$
+differs from that used in the \ccg~model, for which the
+cortico-striatal weights are multiplied by $(1+d)$ rather than
+$(0.2+d)$.
+
+The equations given above are applied to each element in a
+population. The value of the activation $A$ (and where relevant, the
+shunting input, $S$) is determined by summing the weighted
+inputs to the population:
 \[
@@
 radial angle $r$ and the retinal neural density. It is given by:
-\[
+\[ \label{eq:mf}
    M_f = {W_{nfs} \over E_2 ln ({W_{fov} \over 2 E_2} + 1)}
@@
 which has become known as the spatial temporal transform (STT).  The
-spatial part of the STT is thought to be implemented by a
+spatial transform is thought to be implemented by a
 weight-mapping~\cite{tabareau_geometry_2007,arai_model_2004} and we
 follow this idea.
-
 % Words along the lines of:
-Arai and co-workers trained their neural network model to discover the
-weight map~\cite{arai_model_2004}.
-
-% Then...
-Tabareau and co-workers wrote down the theoretical form of the weight
-map and found it matches well to the results of Arai et
-al.~\cite{tabareau_geometry_2007}.
-
-The approach of Arai~et.~al. was
-not feasible with the present model due to the length of time required
-to run the model, its stochasticity and the increased size of the maps
-here compared with those used by Arai~et.~al.
+Arai and co-workers trained a 20x20 neural network model of the
+superior colliculs to discover the weight map under the assumption of
+2D Gaussian activation profiles~\cite{arai_model_2004}.
+%
+The training approach of Arai~et.~al. was not feasible in this study
+due to the length of time required to run our model and its
+stochasticity, which means multiple runs of the model were necessary
+in order to generate output statistics.
+%
+Tabareau and co-workers wrote down a theoretical form of the weight
+map, which follows from the mapping of \cite{ottes_visuomotor_1986}
+and the assumption of invariant 2D Gaussian activity profiles in
+SC~\cite{tabareau_geometry_2007}. As they found it closely resembles the
+results of Arai et al., and it is a simple formulation, we considered
+it as the means to generate the six weight maps in our own model.
+%
+One barrier to the use of the weight map
+in \cite{tabareau_geometry_2007} was the \ccg~model's violation of the
+\emph{invariant integral hypothesis}. This states that the number of spikes
+emitted by a neural element during a saccade (or in our model, the
+integral of the neuron's output during the saccade) should be a
+function only of its position within the hill of collicular
+activity. That is, for any time-dependent hill of activity
+$\mathcal{A}(\mathbf{z},t)$ at $\mathbf{z} = (r,\phi)$ on the collicular
+surface, the integrated activity  $A_{\mathbf{x}}$ in an element at a
+vector $\mathbf{x}$ away from $\mathbf{z}$ is
+\[
+A_{\mathbf{x}} = \int_t \mathcal{A}(\mathbf{z}-\mathbf{x}, t) dt
+\]
+which is invariant for all $\mathbf{z}$. However, the very mapping on
+which the \cite{tabareau_geometry_2007} result is based leads to a
+very \emph{variant} activity profile in the \ccg~model. A luminance of
+a given size which excites activity near to the fovea causes activity
+in a large number of neurons, whereas activity far from the fovea
+excites a much smaller region. This effect is clearly demonstrated in
+Fig.~\ref{fig:mapping} for equal sized targets both on and distal from
+the fovea.
+
+This led us to hypothesize that the retinotopic mapping be accompanied
+by an associated widening projection field such that the hill of
+activity in superior colliculus is invariant with position on the
+collicular surface. There are a number of locations in the system in
+which this widening projection field could exist. It could be
+implemented in the projections between the retinal populations and the
+superficial layer of SC along with the projection between the World
+and the FEF population. However, this would affect activity within the
+basal ganglia of the model, contradicting a result
+in \cite{cope_basal_2017} which explains the `hockey stick' profile
+for saccade latency as a function of saccade eccentricity. Instead, we
+suggest that a widening projection field is encoded within the
+superior colliculus itself, a complex, multi-layered structure which
+could quite plausibly support such a function. Indeed, such widening
+activity can be seen in the stimulation experiments
+in \cite{vokoun_intralaminar_2010}
+and \cite{vokoun_response_2014}. Although in this work we do not model
+the SC in detail, we extended the model with a third functional layer
+(\ccg has two layers; SC\_sup) and SC\_deep) named SC\_deep2. We
+introduced a widening projection based on a Gaussian projection field
+whose width varies in inverse proportion to the magnification factor.
+
+A further problem - the temporal profile of the hill? No - 6 channels
+not 4!
 

### 2017-08-19 papers/integration/omm_integ.tex
Current work in progress, downloaded from sharelatex draft

@@
 \usepackage[onehalfspacing]{setspace}
+\usepackage{gensymb} % For \degree
+
 \linenumbers
@@
 The field of computational neuroscience has provided
-many \emph{systems models} of the brain~\cite{several_models}. We
-refer to these as \emph{mechanistic computational models}, meaning
+many \e{systems models} of the brain~\cite{arai_two-dimensional_1994,gancarz_neural_1998,hazy_towards_2007,blenkinsop_frequency_2017}. We
+refer to these as \e{mechanistic computational models}, meaning
 models which consist of populations of neural elements, interconnected
@@
 % Short desc of mechanistic computational model
-By \emph{mechanistic computational model}, we mean a model which
+By \e{mechanistic computational model}, we mean a model which
 consists of populations of neural elements, interconnected in a
@@
 Ganglia model
-(\mycite{nambu_discharge_1990,kuhn_event-related_2004}). The decision
+(\cite{nambu_discharge_1990,kuhn_event-related_2004}). The decision
 to \e{go} is selected by a reduction of activity in this population;
@@
 colliculus which encodes an endpoint for the saccade trajectory
-(\mycite{wurtz_superior_1971,hepp_monkey_1993}); once initiated, the
+(\cite{wurtz_superior_1971,hepp_monkey_1993}); once initiated, the
 saccade proceeds in a relatively direct and stereotyped (though not
-always straight) trajectory (\mycite{van_der_stigchel_eye_2006}) to
+always straight) trajectory (\cite{van_der_stigchel_eye_2006}) to
 the endpoint.
@@
 However, numerous studies have shown that saccade trajectories are
-affected by distractors (\mycite{mcpeek_competition_2003,
+affected by distractors (\cite{mcpeek_competition_2003,
 port_sequential_2003, van_der_stigchel_recent_2010}) and may be
@@
 in decision making and action selection (ref), including the selection
-of saccadic eye movements (\mycite{hikosaka_role_2000}). In the later
+of saccadic eye movements (\cite{hikosaka_role_2000}). In the later
 stages of Parkinson's Disease, patients show more latent saccades to
@@
 
-%See \mycite{Rottach_dynamic_1996} for trajectory information in saccades.
+%See \cite{Rottach_dynamic_1996} for trajectory information in saccades.
 
@@
 movements, only a very brief overview is given here; for a recent
-review, see \mycite{munoz_commentary:_2002}. One pathway takes
+review, see \cite{munoz_commentary:_2002}. One pathway takes
 information from the retina directly into the superficial layers of
-the superior colliculus in the brainstem (\mycite{?}). Activity within
+the superior colliculus in the brainstem (\cite{sterling_receptive_1971,linden_massive_1983,wu_involvement_1994}).
+Activity within
 the superior colliculus then excites neurons in the pons, medulla and
-rostral midbrain (\mycite{sparks_brainstem_2002}) and then through
+rostral mid-brain (\cite{sparks_brainstem_2002}) and then through
 channels to the motor neurons which innervate the extraocular muscles
-(\mycite{fuchs_firing_1970,sparks_brainstem_2002}). This direct pathway
+(\cite{fuchs_firing_1970,sparks_brainstem_2002}). This direct pathway
 is responsible for the low latency saccades called express saccades
-(\mycite{?}).
-
-% FEF: \mycite{schall_neural_1999}
+(\cite{schiller_effect_1987,edelman_activity_1996}).
+
+% FEF: \cite{schall_neural_1999}
 Information from the retina is also processed by visual cortex which
@@
 to reflexive and voluntary
-saccades \mycite{schall_neural_1999}. Activity build up in the frontal
+saccades \cite{schall_neural_1999}. Activity build up in the frontal
 eye fields is transferred to the intermediate layers of the superior
 colliculus
-\mycite{?} and is also processed by the basal ganglia, which
+\cite{stanton_frontal_1988-1} and is also processed by the basal ganglia, which
 participates in the selection of the winning saccade end point
-\mycite{?}.
+\cite{stanton_frontal_1988}.
 
@@
 The integrated brain and biomechanical model described here is a
-development of the model in \mycite{cope_basal_2017},
+development of the model in \cite{cope_basal_2017},
 referred to here as the \ccg~model. This was a rate-coded neural
@@
 
-To summarize, the \ccg~model takes as \emph{input} the positions of luminances on a topographic map and produces as output a saccade target.
-
-To the \ccg~model, we have added a rate-coded brainstem model (a ``saccadic burst
-generator''), and a biomechanical eye, implemented using the biomechanical modelling framework OpenSim. These will be described below,
-but first we will give a description of the modelling framework used.
+To summarize, the \ccg~model takes as \e{input} the positions
+of luminances on a topographic map and produces as output a saccade 
+target.
+
+To the \ccg~model, we have added a rate-coded brainstem model (a ``saccadic
+burst generator''), and a biomechanical eye, implemented using the
+biomechanical modelling framework OpenSim. These will be described below,
+but first we will give a description of the co-ordinate systems and the
+modelling framework used.
+
+\subsubsection{Coordinates in the world}
+
+Before describing the biomechanical eye and the brain model, which consisted
+of retinotopically mapped neural sheets, we describe the coordinate system
+used in the world. The eye was located at the origin of a 3 dimensional, right-handed 
+Cartesian co-ordinate system, with its fovea directed in the $-z$ direction. 
+There was a notional spherical screen which was also centered at the origin of the
+co-ordinate system and had a radius of 50 (in arbitrary units). The \e{fixation 
+point} was the point on the
+screen at which the eye was initially directed.
+Onto the screen were projected luminances, each of which having a position 
+described by two co-ordinates; $\theta_x$, a 
+rotation of the horizon plane about the $x$ axis, and $\theta_y$, a rotation 
+of the meridian plane about the $y$ axis. The position is the intersection
+of these rotated planes with the spherical screen (disregarding
+the intersection point of these three surfaces behind the eye).
+%
+Note that a luminance with positive $\theta_x$ was above the horizon of this world; 
+one whose $\theta_y$ was positive lay to the left of the world's meridian.
+
+Luminances were crosses of height and width subtending 6$\degree$ and whose
+`bars' were 2$\degree$ thick. Luminances were oriented like $+$ symbols with
+their vertical bar aligned with the meridian plane and their horizontal bar 
+aligned with the horizon plane described above.
+
+The eye's frame of reference was initially aligned with the world's frame
+of reference. 
+At each timestep, the eye's rotational state ($R_x$, $R_y$, $R_z$) was 
+used to translate the three dimensional
+Cartesian co-ordinates of the luminances in the world frame into co-ordinates
+in the eye frame. The luminance coordinates in the eye's frame of reference
+were used to determine the input to the brain model.
 
@@
 execution framework
-(\mycite{mitchinson_brahms:_2010,mitchinson_brahms_2015}). To run a
+(\cite{mitchinson_brahms:_2010,mitchinson_brahms_2015}). To run a
 BRAHMS model, the researcher must develop \e{BRAHMS components} for
@@
 components connect together and how data is passed between them
-(\mycite{mitchinson_brahms:_2010}). The main BRAHMS program first
+(\cite{mitchinson_brahms:_2010}). The main BRAHMS program first
 reads the SystemML file, then dynamically loads all the required
@@
 In the current work, the \ccg~model was reproduced using the
-declarative SpineML markup language (\mycite{richmond_model_2014}),
+declarative SpineML markup language (\cite{richmond_model_2014}),
 with the help of the graphical SpineML model editing software
 called SpineCreator
-(\mycite{cope_spinecreator:_2016}). SpineML,
+(\cite{cope_spinecreator:_2016}). SpineML,
 which is a development of the NineML specification
-(\mycite{incf_task_force_on_multi-scale_modeling_network_2011}),
+(\cite{incf_task_force_on_multi-scale_modeling_network_2011}),
 describes neural populations and their projections in a highly
@@
 updates. A complete description of SpineML is given
-in \mycite{richmond_model_2014}.
+in \cite{richmond_model_2014}.
 
@@
 about how the model is executed. A number of simulation
-engines can be utilised, including DAMSON (\mycite{richmond_damson_2015}), GeNN
-(\mycite{nowotny_flexible_2011,nowotny_spineml_2014}) and BRAHMS (used
+engines can be utilised, including DAMSON (\cite{richmond_damson_2015}), GeNN
+(\cite{nowotny_flexible_2011,nowotny_spineml_2014}) and BRAHMS (used
 here). The simulation engine incorporating BRAHMS is called \stob~
-(\mycite{cope_spineml_2_brahms_2015-1}). \stob~is a collection of XSLT
+(\cite{cope_spineml_2_brahms_2015-1}). \stob~is a collection of XSLT
 stylesheets which first generate and compile C++ BRAHMS components
@@
 components into the SpineML model, a model-specific modification was
-applied in \stob~(\mycite{cope_spineml_2_brahms_2015}) making use of
+applied in \stob~(\cite{cope_spineml_2_brahms_2015}) making use of
 a \stob~feature designed for this purpose (The external.xsl file).
@@
 retinotopic co-ordinate system, roughly matching the known layout of
-the superior colliculus~(\mycite{robinson_eye_1972}). % FIXME: and frontal eye field?
+the superior colliculus~(\cite{robinson_eye_1972}). % FIXME: and frontal eye field?
 
@@
 leaky integrator differential equation:
-\[
-   \dot{a} = {1 \over \tau}(a_{in}-a)
-\]
+\begin{equation}
+   \dot{a} = \frac{1}{\tau}(a_{in}-a)
+\end{equation}
 where $\tau$ is the time constant for the neural activation and
@@
 activation input and a shunting inhibition input according to:
-\[
+\begin{equation}
    a_{in} = A(1-s_a)+\alpha R_N
-\]
+\end{equation}
 Here, $A$ is the activation input and $s_a$ is the shunting inhibition
 state variable whose value is related to the shunting input, $S$ by
-\[
+\begin{equation}
    s_a = \begin{cases}
@@
    \end{cases}
-\]
+\end{equation}
 $R_N$ is a random number drawn from a standard normal distribution
@@
 piecewise linear transfer function
-\[
+\begin{equation}
    y(a) = \begin{cases}
@@
    \end{cases}
-\]
+\end{equation}
 where $c$ is a parameter defining the slope of the transfer
@@
 the activation input $A$:
-\[
+\begin{equation}
    a_{in} = A
-\]
+\end{equation}
 The LINexp component is a leaky integrator with an exponential
@@
 element input $a_{in}$:
-\[
+\begin{equation}
    a_{in} = [A+N(a-V_{r}^{-})] (1-S) + 0.01 R_N
-\]
+\end{equation}
 where $A$ is the activation input and $N$ is an input which is
@@
 The output, $y$, of the LINexp component is given by
-\[
+\begin{equation}
    y(a) = \begin{cases}
@@
    \end{cases}
-\]
+\end{equation}
 This component is used in the STN population, as it gives a more
 physiologically accurate f-I
-behaviour \mycite{wilson_model_2004,bevan_mechanisms_1999,hallworth_apamin-sensitive_2003}
+behaviour \cite{wilson_model_2004,bevan_mechanisms_1999,hallworth_apamin-sensitive_2003}
 which has been shown to allow the mapping of the basal ganglia network
 architecture onto an optimal decision making
-model \mycite{bogacz_basal_2007}.
+model \cite{bogacz_basal_2007}.
 
@@
 that their equations for $a_{in}$ are thus:
-\[
+\begin{equation}
    a_{in}^{D1} = (0.2 + d)A + 0.01 R_N
-\]
-\[
+\end{equation}
+\begin{equation}
    a_{in}^{D2} = (1 - d)A + 0.01 R_N
-\]
+\end{equation}
 where $d$ is a dopamine parameter. Varying dopamine from 0 to 1
@@
 inputs to the population:
-\[
+\begin{equation}
 A = \sum_{i}w_i^{act} x_i^{act}
-\]
-\[
+\end{equation}
+\begin{equation}
 S = \sum_{i}w_i^{sh} x_i^{sh}
-\]
+\end{equation}
 
@@
 
-Each population of 2500 neural elements is arranged in a 50 by 50
+Each population of 2500 neural elements was arranged in a 50 by 50
 grid, with positions on the grid representing a retinotopic
-mapping. Locations on the grid specify radial and azimuthal angles $r$
-and $\phi$ for the location of activity on the retina relative to the
-fovea. $r$ and $\phi$ can be converted into rotations about the $x$ and
-$y$ Cartesian axes ($\theta_x$ and $\theta_y$). The result of a
-positive rotation about the $x$ axis in a right-handed Cartesian
-coordinate system results in an upward movement of the fovea's view
-of the environment. Note that a positive rotation about the $y$ axis
-results in a \emph{leftward} movement of the eye's focal point, with
-respect to the world.
+mapping similar to that found empirically both in the superior 
+colliculus (\cite{ottes_visuomotor_1986}) and in visual cortex (\cite{eric_l._schwartz_computational_1980}) and assumed in
+this work to persist throughout the oculomotor system.
+
+In a retinotopic mapping, the Cartesian coordinates of the light-sensitive
+cells in the retina, whose density varies with distance from the fovea,
+are transformed into the Cartesian co-ordinates of 
+the correspondingly active cells on the colliculus. The mapping ensures 
+that an even density of cells can be maintained in the colliculus, but 
+ensures that a single group of proximal, active, retinal neurons will 
+always activate a single, proximal group of neurons on the collicular 
+surface.
+
+The mapping turns out to resemble polar coordinates. That is, one 
+axis of the collicular surface specifies the eccentricity of
+a retinal location (how far it is from the fovea) and the second axis
+specifies the rotational angle of the retinal location; we therefore
+use the convention 
+of referring to the eccentricity axis on the colliculus as $r$ and the 
+rotation axis as $\phi$.
+
+The \e{cortical magnification factor}, $M(r)$, gives the relationship
+between the
+radial eccentricity $r$ and the retinal neural density. As in 
+\cite{cope_basal_2017}, we use a first-order approximation of the form
+for $M(r)$ given in  \cite{rovamo_estimation_1979}:
+\begin{equation} \label{eq:cmf}
+M(r) = \frac{M_f}{1+\frac{r}{E_2}}
+\end{equation}
+The foveal magnification, $M_f$, is the magnification of the most central
+region of the retina and has a value in the human of about
+7.8 mm/$\degree$~\cite{rovamo_estimation_1979}.
+
+In our model, $M_f$ is related to $W_{nfs}$, the width of the retinotopic neural 
+field, $W_{fov}$, the width of the eye's field of view and $E_2$, the 
+eccentricity at which the retinal density has halved by:
+\begin{equation} \label{eq:fm}
+   M_f = \frac {W_{nfs}} {E_2\;\ln\left(\frac{W_{fov}}{2 E_2} + 1\right)}
+\end{equation}
+Here, $W_{nfs}$ is 50, $W_{fov}$ is set to 61$\degree$, a
+reduction from the biophysically accurate 150$\degree$ due to the small
+number of neurons in the retinotopic neural field. $E_2$ is
+2.5~\cite{cope_basal_2017,slotnick_electrophysiological_2001}.
+
+The mapping from the retinotopic co-ordinates $r$ and
+$\phi$ to rotational co-ordinates $\theta_x$  and $\theta_y$ on
+the retina was written
+down by \cite{eric_l._schwartz_computational_1980} for striate cortex and 
+\cite{ottes_visuomotor_1986} for superior colliculus. We used the following
+statement of this mapping for all of the populations in
+the brain model:
+\begin{equation}
+   \theta_x = E_2 \left(e^{\frac{r}{M_f E_2}} - 1\right).\cos\left(\frac{2 \pi \phi}{W_{nfs}}\right)
+\end{equation}
+\begin{equation}
+   \theta_y = E_2 \left(e^{\frac{r}{M_f E_2}} - 1\right).\sin\left(\frac{2 \pi \phi}{W_{nfs}}\right)
+\end{equation}
 
 Note that the mapping encompases the entire visual field. The value of
-$\phi$ is allowed to vary from 0$\deg$ to 360$\deg$ along its axis.
-Effectively, the two contralateral colliculi are incorporated into a
-single, square map, avoiding the need to carry out `colliculus
-gluing'~\cite{tabareau_geometry_2007}.
-
-The magnification factor, $M_f$, gives the relationship between the
-radial angle $r$ and the retinal neural density. It is given by:
-\[ \label{eq:mf}
-   M_f = {W_{nfs} \over E_2 ln ({W_{fov} \over 2 E_2} + 1)}
-\]
-where $W_{nfs}$ is the width of the retinotopic neural fields (50),
-$W_{fov}$ is the eye's field of view, which is set to 61 degrees, a
-reduction from the biophysically accurate 150 degrees due to the small
-number of neurons in the retinotopic neural field. $E_2$ is the
-eccentricity (in degrees) at which the retinal neural density has
-halved compared with the foveal region.
-
-With $M_f$ calculated, the mapping from the retinotopic radial and
-angular components, $r$ and $\phi$ to $\theta_x$ and $\theta_y$ is:
-\[
-   \theta_x = E_2 (e^{{r \over M_f E_2}} - 1).\cos({2 \pi \phi \over
-   W_{nfs}}) \tag{1}
-\]
-\[
-   \theta_y = E_2 (e^{{r \over M_f E_2}} - 1).\sin({2 \pi \phi \over W_{nfs}}) \tag{2}
-\]
+$\phi$ is allowed to vary from 0$\degree$ to 360$\degree$ along its axis.
+Effectively, the two contralateral colliculi found in the biology are 
+incorporated into a
+single, square map, avoiding the need to carry out the kind of `colliculus
+gluing' described in \cite{tabareau_geometry_2007}.
 
 It is straightforward to show that the reverse mapping is given by:
-\[
-   \phi = {W_{nfs} \over 2 \pi}\arctan({\theta_y\over\theta_x}) \tag{3}
-\]
-\[
-   r = M_f E_2 \ln ({1\over E_2}\sqrt{{\theta_x}^2 + {\theta_y}^2}+1) \tag{4}
-\]
+\begin{equation}
+   \phi = \frac{W_{nfs}} {2 \pi}\arctan\left(\frac{\theta_y}{\theta_x}\right)
+\end{equation}
+\begin{equation}
+   r = M_fE_2\,\ln\left(\frac{1}{E_2}\sqrt{{\theta_x}^2 + {\theta_y}^2}+1\right)
+\end{equation}
 
@@
 produces (in FEF) an indistinct object centered at a larger value of
-r.
+$r$.
 
@@
 tecto-tectal inhibition, which increases the inhibition between
-activity in opposite hemispheres of the field of view (refs). The
-tecto-tectal inhibitory connection is \emph{not} present in
-the \ccg~model.
+activity in opposite hemispheres of the field of view (refs) helping
+to resolve competition between saccades to the left and right. The
+tecto-tectal inhibitory connection is \e{not} present in
+the \ccg~model. In all other respects the model is as described in 
+\cite{cope_basal_2017}.
 
@@
 %being representative of the end point of the saccade
-%trajectory \mycite{mays_dissociation_1980,lee_population_1988,van_Opstal_role_1990}.
+%trajectory \cite{mays_dissociation_1980,lee_population_1988,van_Opstal_role_1990}.
 
@@
 eye's orientation and $\mathbf{U}$ is its angular velocity. $K$ and
-$C$ are constants.
+$C$ are constants. A fuller description of the biomechanical model 
+can be found in \cite{papapavlou_physics-based_2014}.
 
@@
 the deeper layers of the superior colliculus and the saccadic burst
-generator~\cite{van_gisbergen_experimental_1985,ottes_visuomotor_1986,waitzman_superior_1991,groh_converting_2001,arai_model_2004,goossens_dynamic_2006,tabareau_geometry_2007,van_opstal_linear_2008,goossens_optimal_2012},
+generator~\cite{van_gisbergen_experimental_1985,ottes_visuomotor_1986,waitzman_superior_1991,groh_converting_2001,arai_two-dimensional_1994,goossens_dynamic_2006,tabareau_geometry_2007,van_opstal_linear_2008,goossens_optimal_2012},
 which has become known as the spatial temporal transform (STT).  The
-spatial transform is thought to be implemented by a
-weight-mapping~\cite{tabareau_geometry_2007,arai_model_2004} and we
+spatial aspect of the transform is thought to be implemented by a
+weight-mapping~\cite{tabareau_geometry_2007,arai_two-dimensional_1994} and we
 follow this idea.
@@
 superior colliculs to discover the weight map under the assumption of
-2D Gaussian activation profiles~\cite{arai_model_2004}.
+2D Gaussian activation profiles~\cite{arai_two-dimensional_1994}.
 %
@@
 in \cite{tabareau_geometry_2007} was the \ccg~model's violation of the
-\emph{invariant integral hypothesis}. This states that the number of spikes
+\e{invariant integral hypothesis}. This states that the number of spikes
 emitted by a neural element during a saccade (or in our model, the
@@
 vector $\mathbf{x}$ away from $\mathbf{z}$ is
-\[
+\begin{equation}
 A_{\mathbf{x}} = \int_t \mathcal{A}(\mathbf{z}-\mathbf{x}, t) dt
-\]
+\end{equation}
 which is invariant for all $\mathbf{z}$. However, the very mapping on
 which the \cite{tabareau_geometry_2007} result is based leads to a
-very \emph{variant} activity profile in the \ccg~model. A luminance of
+very \e{variant} activity profile in the \ccg~model. A luminance of
 a given size which excites activity near to the fovea causes activity
@@
 introduced a widening projection based on a Gaussian projection field
-whose width varies in inverse proportion to the magnification factor.
-
-A further problem - the temporal profile of the hill? No - 6 channels
-not 4!
+whose width, $\sigma(r)$ varies in inverse proportion to the 
+magnification factor, $M(r)$, given in Eq.~\ref{eq:cmf} according to:
+\begin{equation} \label{eq:sigmar}
+\sigma(r) = \frac{m_{\sigma}}{M(r)} - \frac{m_{\sigma}}{M^0} + \sigma_0 \qquad r > r_0
+\end{equation}
+$m_{\sigma}$ is a scalar parameter which determines the `magnitude
+of the widening'. $M^0$ is the `starting' magnification factor; 
+within the foveal region ($0 \leq r \leq r_0$), the projection field 
+is not allowed to widen and so
+\begin{equation} \label{eq:sigmar2}
+\sigma(r) = \sigma_0 \qquad r \leq r_0
+\end{equation}
+which makes $\sigma_0$ the width of the Gaussian projection field
+within the foveal region. Note that the width of the foveal region 
+for this projection is not identical to the foveal width used
+in \_\_\_\_ \cmnt{Where else?}.
+The \e{Widening Gaussian} projection weight, $w(r,d)$ is then 
+computed as:
+\begin{equation} \label{eq:widening}
+w(r,d) = e^{-\frac{d^2}{2\sigma\left(r\right)^2}}
+\end{equation}
+where $d$ is the distance between the source and destination 
+elements in the collicular plane.  $m_\sigma$ was set to 50, $\sigma_0$
+was 0.3, $M^0$ was 12.43 and $r_0$ was 20.
+% Could have a figure here, made from widening_gaussian.m
+
+A further issue regarding the use of the theoretical weight map
+in \cite{tabareau_geometry_2007} was that it does not consider the 
+existence of the oblique extraocular muscles. There is indeed evidence that
+only two dimensional information is encoded in superior
+colliculus~\cite{wurtz_activity_1972,van_opstal_two-rather_1991}, but the
+eye is actuated by six extraocular muscles. In order to find out a 
+possible form for the input to the oblique muscles we carried out a 
+training process described in supplementary material which depended on a
+centroid computation in SC\_deep. For the four rectus muscles, the 
+resulting weight maps resembled those found by Arai~et~al. The trained 
+maps for the oblique muscles had a form very close to those for the 
+inferior and superior rectus channels, but with a smaller magnitude.
+The inferior oblique map resembled the superior rectus map and the 
+superior oblique map resembled the inferior rectus. When parameterising 
+the theoretical weight maps, we set the inferior/superior 
+oblique maps to be 1/10$^{\mathrm{th}}$ of the superior/inferior rectus
+maps, respectively. Interestingly, this suggests that there is a built-in
+synergy between the vertical and oblique channels in the eye, although
+the results will show there is some systematic change in the oblique error
+with saccade end-point location.
+
+\cite{tabareau_geometry_2007} gives a formulation for the weight maps
+in which it is possible to project both a positive and a negative 
+weight. In our model, all projections from SC\_deep are excitatory. 
+This means that each channel has a weight which follows the form:
+\begin{equation} \label{eq:weightmaps}
+w(r,\phi) = i\;e\,^{jr}\;\sin\left(\frac{2\pi\phi}{W_{nfs}} + k\right)
+\end{equation}
+where $i$, $j$ and $k$ are per-channel parameters for the weight
+maps. $k$ is determined by the mapping. Only the positive part of the
+sine is utilised. $i$ and $j$ are parameters to be found.
 
 The saccadic burst generator model was originally conceived with the
-assumption of a step input~\cite{gancarz_neural_1998}.
+assumption of a step input, which returns to zero activity at a suitable
+time to curtail the saccade and avoid staircase
+saccades~\cite{gancarz_neural_1998}. In our model 
+there is no such mechanism to reduce activity in SC\_deep, and elsewhere. 
+Although a saccade towards target luminance will remove the excitation 
+which caused the activity in SC\_deep (bringing it within the masked, 
+foveal region), the activity in colliculus decays too slowly to avoid
+additional saccadic movements. We found it necessary to hypothesize 
+an inhibitory feedback mechanism from the SBG to the brain model. 
+This is shown in Fig.~\ref{fig:sbg}, which indicates how the output from 
+the inhibitory burst neurons  (IBN) of the SBG model are used to feed 
+back an inhibitory signal to the SC\_deep, thalamus and FEF populations
+in the brain model. 
+% Might have to justify the above a bit more.
 
@@
 induces a rightward rotation of the eye, our single virtual eye is
-a \emph{left} eye. The OpenSim implementation of the biomechanical eye
+a \e{left} eye. The OpenSim implementation of the biomechanical eye
 was `wrapped' (in the software sense) in a BRAHMS component. This made
@@
 
-\subsection{Weight maps (here?)}
-
-\subsection{Single saccades}
+\subsection{Weight maps}
+
+We found the best parameters for the exponential in Eq.~\ref{eq:weightmaps} 
+($i$ and $j$) by a manual tuning process. After selecting values for $i$ and $j$ 
+in either the horizontal or vertical/oblique channels, we ran the model 6 times 
+at each of 8 target eccentricities (7$\degree$--14$\degree$) which were purely
+in the direction of the
+newly parameterised channel. The training saccades were produced as described below in
+Sect.~\ref{sec:singlesaccades}, with the same fixation and target luminances
+(crosses of magnitude 0.2 and 0.3) but with
+the fixation offset and target onset occurring at 0.2~s. We measured the end-point
+of the saccade by
+detecting the location at which the saccade velocity had dropped below 
+0.005 of its peak. We iterated until the mean saccade endpoint plotted versus target
+was close to the ideal straight line---see Fig.~\ref{fig:sacc_vs_targ}(a) \& (c). We
+applied the same parameters to both directions of each channel; 
+$i_{up} = i_{down} = 0.00195$, $j_{up} = j_{down} = 0.075$, 
+$i_{left} = i_{right} = 0.0016$ and $j_{left} = j_{right} = 0.067$. The resulting
+weight maps (where the oblique maps are 1/10$^{\mathrm{th}}$ of the vertical maps,
+as described earlier) are shown in Fig.~\ref{fig:weightmaps}.
+% From map_modelling2.m:
+%    yh=0.0016*exp(0.067.*x);
+%    yv=0.00195*exp(0.075.*x);
+
+\subsection{Single saccades} \label{sec:singlesaccades}
+
+Having finalised the model by setting the weight maps, we then proceeded 
+to exercise the model, starting with saccades to a single target; 
+prosaccades. Fig.~\ref{fig:outmany}(a) shows 9 representative saccades
+to a single 
+target luminance. Initially, the eye had rotational state
+$\theta_x=\theta_y=\theta_z=0$ with its fovea directed at a 
+fixation luminance cross (span 6$\degree$, bar width 2$\degree$) of 
+magnitude 0.2 (in arbitrary units). At a 
+simulation time of 0.4~s, the fixation luminance was set to 0 and 
+a target luminance cross of the same dimensions as the fixation but with 
+magnitude 0.3 was illuminated at one of the 
+9 different locations, marked by crosses in Fig.~\ref{fig:outmany}(a).
+The resulting trajectories are plotted, with colour indicating the 
+relationship between trajectories and target crosses. The approximate 
+end-point error is visible in this figure, although the last point in 
+each trajectory is the saccade position at 0.8~s and not the velocity
+based end-point described above. Figs.~\ref{fig:outmany}(b) and (c)
+show the rotational components of the blue and red trajectories
+in Fig.~\ref{fig:outmany}(a) along with the target and fixation 
+luminance values. Rotations are the eye's Euler rotational components
+in the world frame of reference.
+
+\subsection{Saccade accuracy}
+
+Figs.~\ref{fig:sacc_vs_targ}(a) \& \ref{fig:sacc_vs_targ}(b) show
+the result of running the model to targets located on the principle
+axes, on which the model was trained. We then simulated single saccades
+to targets in one hemifield of the eye's field of view, with
+eccentricities between 6$\degree$ and 14.5$\degree$. As in the
+training, we ran the simulation 6 times for each target, 
+$\mathbf{\theta}^t = (\theta_{x}^t, \theta_{y}^t, 0)$ to obtain
+mean saccade end-points.
+Fig.~\ref{fig:errorsurface} shows the results, where the ratio of 
+the magnitude of the error vector to the magnitude of the target 
+vector is plotted as a colour map. This ratio is shown for the full,
+three dimensional error vector in Fig.~\ref{fig:errorsurface}(a) and
+for the $x$, $y$ and $z$ components in Figs.~\ref{fig:errorsurface}(b)--(c).
+Inspection of  Fig.~\ref{fig:errorsurface}(a) shows that the end-point 
+error is minimal along the principle axes ($\theta_{x}^t=\;$0 or
+$\theta_{y}^t=\;$0) and maximal near the 45$\degree$ oblique targets 
+(blue lines).
+% Mention \cite{thurat_biomimetic_2015} in discussion.
+The $x$ component error map in Fig.~\ref{fig:errorsurface}(b) 
+shows the same trend, mirrored about the `Target X' axis, whereas
+the $y$ component error map shows maximal error for targets around the
+45$\degree$ direction for negative $\theta_{x}^t$ and $\theta_{y}^t$ 
+(down and rightwards). $z$ component error is nearly absent for 
+horizontal saccades ($\theta_{x}^t=\;$0)
+
+The largest errors produced by the model are approximately 15\%, which are
+within the boundaries of what some authors have suggested would be regarded
+as an accurate saccade \cite{mcpeek_saccade_2002,mcpeek_incomplete_2006}
+(the magnitude of the largest error vector is approximately 1.5$\degree$).
+
+% These errors are larger than those in Thurat due to the hill of
+% activity not being `perfect'
+
+\subsection{Saccade sequences}
+
+\subsubsection{Out \& return}
+
+We investigated the behaviour of the model for saccade sequences.
+In one experiment, we illuminated a fixation
+cross from 0~s until 0.4~s, followed by a target at (-10$\degree$, 0)
+from 0.4~s until 0.8~s. Finally, the fixation was again shown from 0.8~s
+until the end of the simulation at 2~s. This induced a saccade to a
+10$\degree$ eccentricity, followed by a return saccade back to the
+null point. Fig.~\ref{fig:outrtn} shows the
+outward and return trajectories produced by the experiment. Panel (a) 
+shows the $x$ and $y$ rotation trajectory; panel (b) shows individual
+rotational components of the eye. The return trajectory shows a 
+distinctly different form from the outward trajectory; it has a dynamic
+overshoot, of the type described in \cite{bahill_trajectories_1979}.
+This is caused by the initial restorative force applied by the elastic
+extraocular muscles, which are not at their null point when the return
+saccade starts. Interestingly, if a sequence of out \& return saccades is
+programmed, dynamic overshoot is also observed in the second and
+subsequent `out' saccades. This occurs because at the start of the 
+second `out' saccade, the eye ball is rotated away from the null point,
+especially around the $x$ and $z$ axes.
+
+\subsubsection{Double steps}
+
+In another experiment, we...
+
+\subsection{Saccade Latencies}
+
+To verify that our implementation of the brain model has the same
+functionality as that reported in \cite{cope_basal_2017}, we 
+investigated the effect on saccadic response times of
+target eccentricity and any gap or overlap between fixation off-time 
+and target on-time. We showed that the full model reproduces the 
+`hockey stick' shape shown in Fig. 7 of \cite{cope_basal_2017} for
+horizontal [Fig.~\ref{fig:lat_vs_all}(a)], vertical
+[Fig.~\ref{fig:lat_vs_all}(b)] and oblique saccades.  \cmnt{Talk about shape here and briefly explain why we see this shape}
+
+Fig.~\ref{fig:lat_vs_all}(c) shows latencies achieved when varying the... etc etc
+
+\subsection{Saccade with distractor}
+
+Fig.~\ref{fig:targ_w_distr}(a) shows three horizontal saccades to a 
+target at $\theta_{y}=$-10$\degree$. The first saccade (blue 
+trajectory) had no distractor luminance, the second saccade (red) was
+modulated by the appearance of a distractor cross of magnitude 1
+located at $\theta_{x}=$-7$\degree$, $\theta_{y}=$-7$\degree$. 
+The distractor appeared 0.1~s after the target and 
+persisted for 0.1~s [Fig.~\ref{fig:targ_w_distr}(b)]. The third 
+saccade (green) had conditions identical to the red saccade, but 
+with a brighter distractor luminance, whose magnitude was 2.
+
+\subsection{Saccade to twin targets}
 
@@
 % investigate saccade trajectory modifications in Parkinson's''
-
-\subsection{Subsections}
 
@@
 
-% Equations:
-%\begin{equation}
-%\sum x+ y =Z\label{eq:01}
-%\end{equation}
-
 \section*{Disclosure/Conflict-of-Interest Statement}
@@
 
-\section*{Acknowledgments}
+\section*{Acknowledgements}
 
@@
 
-Models available on github - include details of branches, commits etc
-for running the model.
+The model specification, results and all code required to reproduce 
+the results of this work are available
+at: https://github.com/ABRG-Models/OMM\_NeuroMuscular
 
@@
 
-\begin{figure}[h!]
+\begin{figure}[htb!]
 \begin{center}
@@
 the luminances. Here, there are two cross shaped luminances spanning
-10$\deg$, one of value 0.8 at the fixation point (0,0) and one of
-value 0.5 at a peripheral position (0,-12$\deg$). (b) The locations of
+10$\degree$, one of value 0.8 at the fixation point (0,0) and one of
+value 0.5 at a peripheral position (0,-12$\degree$). Note that these
+crosses have the same `bar width' of 2$\degree$ as the crosses 
+used in the simulations, but their span of 10$\degree$ is greater
+than the 6$\degree$ used in the simulations, to make these
+images clearer. (b) The locations of
 the luminances in the eye's frame of reference are then converted into
@@
 blurs the activity in FEF. FEF is the input to the basal ganglia and
-one input to superior collicus.}
+one input to superior colliculus.}
 \end{figure}
@@
 arrows with the colour indicating the connectivity scheme (one-to-one
-connections are red, gaussian kernel connections are dark blue and so
+connections are red, Gaussian kernel connections are dark blue and so
 on). Excitatory connections have arrowheads and inhibitory connections
@@
 connections, the weight-update and post-synapse components must be
-studied. Briefly, the model comprises a \emph{World} population, into
+studied. Briefly, the model comprises a \e{World} population, into
 which a retinotopically organised view of the world is
@@
 number of neural elements (here 2500 or 1) and the SpineML component
-name; \emph{LIN} for Leaky integrator or \emph{integrator}. Key: LLBN:
+name; \e{LIN} for Leaky integrator or \e{integrator}. Key: LLBN:
 Long lead burst neurons; IBN: Inhibitory burst neurons; OPN: Omnipause
@@
 Motoneurons.}
+\end{figure}
+
+\begin{figure}[htb!]
+\begin{center}
+\includegraphics[width=0.5\textwidth]{./figures/SC_to_brainstem.png}
+\end{center}
+\textbf{\refstepcounter{figure}\label{fig:scdeep} Figure \arabic{figure}.}
+{ \textbf{fig:scdeep} Showing additional deep layer of superior colliculus 
+(SC\_deep2) and the output layer (SC\_avg, named for the fact that in an earlier
+version of the model, it received the output of the centroid of SC\_deep).}
+\end{figure}
+
+\begin{figure}[htb!]
+\begin{center}
+\includegraphics[width=0.8\textwidth]{./figures/sacc_vs_targetpos.png}
+\end{center}
+\textbf{\refstepcounter{figure}\label{fig:sacc_vs_targ} Figure \arabic{figure}.}
+{ \textbf{fig:sacc\_vs\_targ} Accuracy at different target eccentricities for fixation luminance 0.2 and target luminance 0.3.}
 \end{figure}
@@
 exponentially with increasing $r$, multiplied by cosine($\phi$) about
-its `active' axis. \textbf{FIXME: Left \& Right are wrong way round}}
+its `active' axis. \cmnt{Check whether Left \& Right are wrong way round}}
 \end{figure}
@@
 \begin{center}
-\includegraphics[width=0.8\textwidth]{./figures/sacc_vs_targetpos.png}
+\includegraphics[width=0.95\textwidth]{./figures/errorsurface_percent.png}
 \end{center}
-\textbf{\refstepcounter{figure}\label{fig:sacc_vs_targ} Figure \arabic{figure}.}
-{ \textbf{fig:sacc\_vs\_targ} Accuracy at different target eccentricities for fixation luminance 0.2 and target luminance 0.3.}
+\textbf{\refstepcounter{figure}\label{fig:errorsurface} Figure \arabic{figure}.}
+{ \textbf{fig:errorsurface} The end-point error surface. a) The 
+ratio of the magnitudes of the total error vector and the target 
+vector, expressed as a percentage. b) The ratio of the magnitude
+of the $x$ component of the error vector to the magnitude of the
+target vector, expressed as a percentage. c) As (b) but for the
+$y$ component. d) As (b), for $z$ component. All colour maps are
+shown with the same scale. The target rotations, $\theta_{x}^t$ and
+$\theta_{y}^t$ are denoted `Target X' and `Target Y' in the figure.}
 \end{figure}
@@
 \begin{center}
-\includegraphics[width=0.9\textwidth]{./figures/errorsurface.png}
+\includegraphics[width=0.8\textwidth]{./figures/lat_vs_everything.png}
 \end{center}
-\textbf{\refstepcounter{figure}\label{fig:errorsurface} Figure \arabic{figure}.}
-{ \textbf{fig:errorsurface} Error surface}
-\end{figure}
-
-\begin{figure}[htb!]
-\begin{center}
-\includegraphics[width=0.45\textwidth]{./figures/lat_vs_dopamine.png}
-\end{center}
-\textbf{\refstepcounter{figure}\label{fig:lat_vs_dop} Figure \arabic{figure}.}
-{ \textbf{fig:lat\_vs\_dop} Latency vs.~dopamine.}
-\end{figure}
-
-\begin{figure}[htb!]
-\begin{center}
-\includegraphics[width=0.45\textwidth]{./figures/sacc_vs_lum.png}
-\end{center}
-\textbf{\refstepcounter{figure}\label{fig:lat_vs_lum} Figure \arabic{figure}.}
-{ \textbf{fig:lat\_vs\_lum} Latency vs.~luminance.}
+\textbf{\refstepcounter{figure}\label{fig:lat_vs_all} Figure \arabic{figure}.}
+{ \textbf{fig:lat\_vs\_all} Exploring saccade latencies.}
 \end{figure}

### 2017-08-30 papers/integration/omm_integ.tex

@@
 
-%%% This is based on the Frontiers template.
+% The Frontiers template.
 \documentclass{frontiersSCNS}
@@
   The University of Sheffield, Sheffield, UK \\
-$^{5}$Department of Computer Science,
+$^{5}$Department of Electrical and Computer Engineering,
   The University of Patras, Patras, Greece \\
@@
 
+\cmnt{Background, gap, solution (cheers Sean!)}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-To the \ccg~model, we have added a rate-coded brainstem model (a ``saccadic
-burst generator''), and a biomechanical eye, implemented using the
+To the \ccg~model, we have added a rate-coded brainstem model (a `saccadic
+burst generator'), and a biomechanical eye, implemented using the
 biomechanical modelling framework OpenSim. These will be described below,
@@
 
-\subsubsection{Coordinates in the world}
+\subsubsection{Co-ordinates in the world}
 
 Before describing the biomechanical eye and the brain model, which consisted
-of retinotopically mapped neural sheets, we describe the coordinate system
+of retinotopically mapped neural sheets, we describe the co-ordinate system
 used in the world. The eye was located at the origin of a 3 dimensional, right-handed
@@
 Onto the screen were projected luminances, each of which having a position
-described by two co-ordinates; $\theta_x$, a 
-rotation of the horizon plane about the $x$ axis, and $\theta_y$, a rotation 
+described by two co-ordinates; $\theta_{x}^{t}$, a
+rotation of the horizon plane about the $x$ axis, and $\theta_{y}^{t}$, a rotation
 of the meridian plane about the $y$ axis. The position is the intersection
@@
 %
-Note that a luminance with positive $\theta_x$ was above the horizon of this world; 
-one whose $\theta_y$ was positive lay to the left of the world's meridian.
-
-Luminances were crosses of height and width subtending 6$\degree$ and whose
-`bars' were 2$\degree$ thick. Luminances were oriented like $+$ symbols with
+Note that a luminance with positive $\theta_{x}^{t}$ was above the horizon of this world;
+one whose $\theta_{y}^{t}$ was positive lay to the left of the world's meridian. For this
+reason, many of the figures in this paper are plotted with $-\theta_{y}$ on the
+$x$-axis and $\theta_{x}$ on the $y$-axis so that targets that lay up and to the right
+in the world do so in the graphs, also.
+
+Luminances were crosses of height and width subtending $\pm$3\dg~and whose
+`bars' were 2\dg~thick. Luminances were oriented like $+$ symbols with
 their vertical bar aligned with the meridian plane and their horizontal bar
@@
 of reference.
-At each timestep, the eye's rotational state ($R_x$, $R_y$, $R_z$) was 
+At each timestep, the eye's rotational state (described by the Euler
+rotations $\theta_x$, $\theta_y$, $\theta_z$) was
 used to translate the three dimensional
 Cartesian co-ordinates of the luminances in the world frame into co-ordinates
-in the eye frame. The luminance coordinates in the eye's frame of reference
+in the eye frame. The luminance co-ordinates in the eye's frame of reference
 were used to determine the input to the brain model.
@@
 mapping similar to that found empirically both in the superior
-colliculus (\cite{ottes_visuomotor_1986}) and in visual cortex (\cite{eric_l._schwartz_computational_1980}) and assumed in
+colliculus [\cite{ottes_visuomotor_1986}] and in visual cortex
+[\cite{eric_l._schwartz_computational_1980}] and assumed in
 this work to persist throughout the oculomotor system.
 
-In a retinotopic mapping, the Cartesian coordinates of the light-sensitive
+In a retinotopic mapping, the Cartesian co-ordinates of the light-sensitive
 cells in the retina, whose density varies with distance from the fovea,
@@
 
-The mapping turns out to resemble polar coordinates. That is, one 
+The mapping turns out to resemble polar co-ordinates. That is, one
 axis of the collicular surface specifies the eccentricity of
@@
 specifies the rotational angle of the retinal location; we therefore
-use the convention 
-of referring to the eccentricity axis on the colliculus as $r$ and the 
-rotation axis as $\phi$.
+use the convention of referring to the eccentricity axis on the
+colliculus as $r$ and the rotation axis as $\phi$.
 
@@
 region of the retina and has a value in the human of about
-7.8 mm/$\degree$~\cite{rovamo_estimation_1979}.
+7.8 mm/\dg~\cite{rovamo_estimation_1979}.
 
@@
 \end{equation}
-Here, $W_{nfs}$ is 50, $W_{fov}$ is set to 61$\degree$, a
-reduction from the biophysically accurate 150$\degree$ due to the small
+Here, $W_{nfs}$ is 50 (the side length of the 50x50 grid)
+and $W_{fov}$ is set to 61\dg, a
+reduction from the biophysically accurate 150\dg~due to the small
 number of neurons in the retinotopic neural field. $E_2$ is
-2.5~\cite{cope_basal_2017,slotnick_electrophysiological_2001}.
-
-The mapping from the retinotopic co-ordinates $r$ and
-$\phi$ to rotational co-ordinates $\theta_x$  and $\theta_y$ on
-the retina was written
-down by \cite{eric_l._schwartz_computational_1980} for striate cortex and 
-\cite{ottes_visuomotor_1986} for superior colliculus. We used the following
-statement of this mapping for all of the populations in
-the brain model:
-\begin{equation}
-   \theta_x = E_2 \left(e^{\frac{r}{M_f E_2}} - 1\right).\cos\left(\frac{2 \pi \phi}{W_{nfs}}\right)
-\end{equation}
-\begin{equation}
-   \theta_y = E_2 \left(e^{\frac{r}{M_f E_2}} - 1\right).\sin\left(\frac{2 \pi \phi}{W_{nfs}}\right)
-\end{equation}
+2.5 [\cite{cope_basal_2017,slotnick_electrophysiological_2001}].
+
+The mapping from the retinotopic co-ordinates in the brain to rotational
+co-ordinates of the stimulus/response was written down by
+\cite{schwartz_spatial_1977,eric_l._schwartz_computational_1980}
+for measurements of
+striate cortex [visual stimulus to electrophysiological response---\cite{daniel_representation_1961, talbot_physiological_1941}]
+and by \cite{ottes_visuomotor_1986} for superior colliculus data
+[electrophysiological SC stimulus to eye movement
+response---\cite{robinson_eye_1972}].
+% Ottes et al. fit to stimulus-to-movement data, and give a
+% movement-to-collicular-coordinate mapping in the paper.
+We used the following statement of this mapping to introduce stimuli
+into the `World' input population of the brain model:
+\begin{equation}\label{eq:thetas_to_phi}
+   \phi = \frac{W_{nfs}} {2 \pi}\arctan\left(\frac{\theta_{y}^{t}}{\theta_{x}^{t}}\right)
+\end{equation}
+\begin{equation}\label{eq:thetas_to_r}
+   r = M_fE_2\,\ln\left(\frac{1}{E_2}\sqrt{{\theta_{x}^{t}}^2 + {\theta_{y}^{t}}^2}+1\right)
+\end{equation}
+Note that we use $r$ and $\phi$ as the co-ordinates on the `collicular
+surface'. Schwartz uses $r$ and $\phi$ as the polar coordinates of the
+retinal stimulus; Ottes et al.~use $r$ and $\phi$ as polar coordinates
+for the eye movement response; both use $u$ and $v$ as the Cartesian co-ordinates of the neural map. We use $\theta_{x}^{t}$ and $\theta_{y}^{t}$
+to give Euler rotations for the retinal target stimulus. Note also that
+the form of Eqns.~\ref{eq:thetas_to_phi} \& \ref{eq:thetas_to_r} is slightly
+different from that given in
+\cite{ottes_visuomotor_1986} because our $\theta_{x}^{t}$ and
+$\theta_{y}^{t}$ are not the polar co-ordinates used in that work.
 
 Note that the mapping encompases the entire visual field. The value of
-$\phi$ is allowed to vary from 0$\degree$ to 360$\degree$ along its axis.
+$\phi$ is allowed to vary from 0\dg~to 360\dg~along its axis.
 Effectively, the two contralateral colliculi found in the biology are
@@
 \begin{equation}
-   \phi = \frac{W_{nfs}} {2 \pi}\arctan\left(\frac{\theta_y}{\theta_x}\right)
+   \theta_x = E_2 \left(e^{\frac{r}{M_f E_2}} - 1\right).\cos\left(\frac{2 \pi \phi}{W_{nfs}}\right)
 \end{equation}
 \begin{equation}
-   r = M_fE_2\,\ln\left(\frac{1}{E_2}\sqrt{{\theta_x}^2 + {\theta_y}^2}+1\right)
-\end{equation}
+   \theta_y = E_2 \left(e^{\frac{r}{M_f E_2}} - 1\right).\sin\left(\frac{2 \pi \phi}{W_{nfs}}\right)
+\end{equation}
+where we have dropped the $t$ superscript on $\theta_x$ \& $\theta_y$, as
+these equations transform a collicular location into rotations of the eye.
 
@@
 results in a large comb-shape of activity. The more peripheral cross
-produces (in FEF) an indistinct object centered at a larger value of
+produces (in FEF) an indistinct object centred at a larger value of
 $r$.
@@
 
-In this model, we implement a saccadic burst generator (SBG) based
-on \cite{gancarz_neural_1998}. The SBG network for two of the model's
+We implemented a saccadic burst generator (SBG) based
+on the connectivity outlined in \cite{gancarz_neural_1998}. The SBG network
+for two of the model's
 six channels is shown in Fig.~\ref{fig:sbg}. Activity from the output
@@
 a single neural element representing all the neurons in that
-population.
-
-Neurons in the deep
-layers of the superior colliculus called long lead burst neurons
-innervate excitatory burst neurons in the reticular formation (REF,
-and check if LLBNs are really in SC).
-
-Alex B to write this section?
-
-Note that inhibition from IBN populations is fed back - or is this
-detail for the `integration' subsection?
+population. Each channel of the SBG functions to create the motor neuron
+activations that are required to accelerate the eye in a particular
+direction, then hold the eye in its new position against the returning
+force generated by the elastic properties of the muscles.  The
+required motor neuron activations are therefore a brief burst of
+increased activity that accelerates the eye, followed by a period
+of activity that is less than the burst firing rate but higher than
+the tonic rate that exists when the eye is at the centre.  This
+holds the eye in its new position.
+
+The SBG connectivity produce each of the these elements separately,
+then sums them to create the desired `bump and tonic' activation
+time series.  The input to the first population in the SBG, the
+long-lead burst neurons (LLBNs), is conceived as originating from
+one of the deep layers of the superior colliculus.  The activity
+of the LLBNs are passed to excitatory burst neurons (EBNs) which,
+in turn, inhibit the LLBNs via the activity of the inhibitory
+burst neurons (IBNs).  This feedback loop has a transmission delay,
+which allows activity to build up in the EBNs before the inhibition
+is activated and the activity is then reduced again.  This mechanism
+generates the `bump'.
+
+The generation of the `tonic' phase of the required time series is
+achieved simply by integrating the bump over time and multiplying by a
+some small gain factor.  This is the function of the tonic neurons (TNs).
+The firing rate of the motor neuron defines the amount of force applied
+to the eye by that muscle.  Thus, the size of the `bump' defines how far
+the eye moves in that channel's direction.  The gain and delay parameters
+in the LLBN-EBN-IBN-LLBN feedback loop therefore have to be tuned such that
+the endpoint of the saccade is reasonably accurate.  Furthermore the
+restoring force generated by the elasticity of the muscles is dependent
+on the radial distance.  The value of the new tonic firing rate, after
+the `bump' is dependent on the end location of the eye.  If the ratio
+between the EBN firing rate and the TN firing rate is not exactly
+correct, the eye will drift away from the saccade endpoint after the
+saccade has been completed.  The EBN-TN connection strength is
+therefore tuned such that the TN firing rate yields a stable eye
+position across a range of eye eccentricities.
+
+The omnipause neurons (OPNs) are tonically active and inhibit the EBNs.
+The activity of the OPNs is itself inhibited by activity in the LLBNs.
+The purpose of this arrangement is to ensure the eye does not move in
+response to neural noise.
+
+Each mean activity of all the neurons in each SBG population (except the
+TNs) is defined by a single leaky integrator, first order differential equation.
+\begin{equation}\label{eq:thetas_to_r}
+   \frac{da}{dt} = \frac{1}{\tau}(y-a)
+\end{equation}
+where $a$ is the activation of the nucleus, and $\tau$ is the time constant
+of the nucleus. $y$ is a piecewise linear function of the weighted sum of
+inputs to the nucleus and is given by
+\begin{equation}
+       y(IN) = \begin{cases}
+       0    & IN \leq b \\
+      IN-b   & b \leq IN \leq 1+b \\
+      1   & IN \geq 1+b \\
+   \end{cases}
+\end{equation}
+where $b$ is the $IN$ axis offset.  $IN$ is the weighted sum of inputs to
+the nucleus and is given by,
+\begin{equation}
+    IN = \sum_{m}^{M} w_{mn} a_{m}
+\end{equation}
+where $a_{m}$ is the activation of the $m^{th}$ afferent nucleus.
+$w_{mn}$ is the connection strength between the $m^{th}$ afferent nucleus
+and the current nucleus. The activity of the TNs are defined as
+\begin{equation}
+   \frac{da}{dt} = \frac{1}{\tau}\,y
+\end{equation}
+with an identical piecewise linear transfer function as the other SBG populations.
+
+\cmnt{Note that inhibition from IBN populations is fed back - or is this
+detail for the `integration' subsection?}
 
@@
 % Possibly introductory paragraph here.
-
-% Patras - what about a figure here?
+The output signals of the brainstem are used to drive the biomechanical model.
+The latter is not only used to get tangible feedback on the simulated saccades including motion trajectories, but adds one more modeling dimension related to the inertial properties of the eye plant including muscle properties.
+
+% Patras - what about a figure here? --- WILL ADD TOMORROW TUESDAY
 
@@
 The force applied by EOMs is controlled by an excitatory signal
-supplied by motoneurons in the brainstem. The dynamics of muscular
+supplied by motoneurons in the brainstem.
+The neural drive to produce a saccadic eye movement can be characterized by a pulse component to overcome the viscoelasticity of the orbital plant, a step component to stabilize the eye in the new position, and a slide component that models the gradual transition between the pulse and step.
+
+The dynamics of muscular
 forces can be split into: 1) The elasticity of the muscles. 2) A delay
@@
 \begin{equation}
-A_{\mathbf{x}} = \int_t \mathcal{A}(\mathbf{z}-\mathbf{x}, t) dt
+A_{\mathbf{x}} = \int_t \mathcal{A}(\mathbf{z}-\mathbf{x}, t)\;dt
 \end{equation}
@@
 and \cite{vokoun_response_2014}. Although in this work we do not model
-the SC in detail, we extended the model with a third functional layer
-(\ccg has two layers; SC\_sup) and SC\_deep) named SC\_deep2. We
+the SC in detail, we extended the model with a third functional layer named SC\_deep2
+(\ccg~has only the two layers SC\_sup and SC\_deep). We
 introduced a widening projection based on a Gaussian projection field
@@
 which makes $\sigma_0$ the width of the Gaussian projection field
-within the foveal region. Note that the width of the foveal region 
-for this projection is not identical to the foveal width used
-in \_\_\_\_ \cmnt{Where else?}.
+within the foveal region. (Note that the value chosen for the width
+of the foveal region, $r_0$ is not identical to the foveal shift parameter used
+in the \e{DecayingAtFovea} projections into striatum.)
 The \e{Widening Gaussian} projection weight, $w(r,d)$ is then
@@
 centroid computation in SC\_deep. For the four rectus muscles, the
-resulting weight maps resembled those found by Arai~et~al. The trained 
+resulting weight maps resembled those found by
+\cite{arai_two-dimensional_1994}. The trained
 maps for the oblique muscles had a form very close to those for the
@@
 
+The final models, on which the results of this paper are based are
+named `TModel3', `TModel4' and `TModel5'. Descriptions of earlier
+versions of the model can be
+found in the code repository given in SUPPLEMENTAL DATA.
+
 %\end{methods}
@@
 in either the horizontal or vertical/oblique channels, we ran the model 6 times
-at each of 8 target eccentricities (7$\degree$--14$\degree$) which were purely
+at each of 8 target eccentricities (7\dg--14\dg) which were purely
 in the direction of the
@@
 $\theta_x=\theta_y=\theta_z=0$ with its fovea directed at a
-fixation luminance cross (span 6$\degree$, bar width 2$\degree$) of 
+fixation luminance cross (span 6\dg, bar width 2\dg) of
 magnitude 0.2 (in arbitrary units). At a
@@
 end-point error is visible in this figure, although the last point in
-each trajectory is the saccade position at 0.8~s and not the velocity
-based end-point described above. Figs.~\ref{fig:outmany}(b) and (c)
+each trajectory is the saccade position at 0.8~s and not the
+velocity-based end-point described above. Figs.~\ref{fig:outmany}(b) and (c)
 show the rotational components of the blue and red trajectories
@@
 
-Figs.~\ref{fig:sacc_vs_targ}(a) \& \ref{fig:sacc_vs_targ}(b) show
+Fig.~\ref{fig:sacc_vs_targ} shows
 the result of running the model to targets located on the principle
@@
 to targets in one hemifield of the eye's field of view, with
-eccentricities between 6$\degree$ and 14.5$\degree$. As in the
+eccentricities between 6\dg~and 14.5\dg. As in the
 training, we ran the simulation 6 times for each target,
@@
 mean saccade end-points.
-Fig.~\ref{fig:errorsurface} shows the results, where the ratio of 
+Fig.~\ref{fig:errorsurfaceTM3} shows saccade accuracy results for an
+entire hemifield in the naive model which passed the output of
+SC\_deep directly to SBG via the weight maps. The ratio of
 the magnitude of the error vector to the magnitude of the target
-vector is plotted as a colour map. This ratio is shown for the full,
-three dimensional error vector in Fig.~\ref{fig:errorsurface}(a) and
-for the $x$, $y$ and $z$ components in Figs.~\ref{fig:errorsurface}(b)--(c).
-Inspection of  Fig.~\ref{fig:errorsurface}(a) shows that the end-point 
+vector is plotted as colour maps. This ratio is shown for the full,
+three dimensional error vector in Fig.~\ref{fig:errorsurfaceTM3}(a) and
+for the $x$, $y$ and $z$ components in Figs.~\ref{fig:errorsurfaceTM3}(b)--(c).
+Inspection of  Fig.~\ref{fig:errorsurfaceTM3}(a) shows that the end-point
 error is minimal along the principle axes ($\theta_{x}^t=\;$0 or
-$\theta_{y}^t=\;$0) and maximal near the 45$\degree$ oblique targets 
-(blue lines).
+$\theta_{y}^t=\;$0) and maximal near the 45\dg~oblique targets
+(blue lines) with the end point error as high as 80\% of the
+programmed saccade magnitude.
 % Mention \cite{thurat_biomimetic_2015} in discussion.
-The $x$ component error map in Fig.~\ref{fig:errorsurface}(b) 
+The $x$ component error map in Fig.~\ref{fig:errorsurfaceTM3}(b)
 shows the same trend, mirrored about the `Target X' axis, whereas
-the $y$ component error map shows maximal error for targets around the
-45$\degree$ direction for negative $\theta_{x}^t$ and $\theta_{y}^t$ 
-(down and rightwards). $z$ component error is nearly absent for 
-horizontal saccades ($\theta_{x}^t=\;$0)
-
-The largest errors produced by the model are approximately 15\%, which are
+the $y$ and $z$ component errors are, relatively, much smaller.
+Because the $x$ component of the error is clearly contributing to
+end point errors which would not be considered `on target',
+especially for oblique saccades, we considered the effect of the
+non-uniform size of the hill of activity in SC\_deep.
+
+In our model, the location, \e{size} and shape of activity in FEF,
+the basal ganglia, thalamus and superior colliculus is eccentricity
+dependent, in line with the retinotopic mapping stated by
+\cite{ottes_visuomotor_1986}. More eccentric targets generate reduced
+activity, because fewer retinal neurons are excited far from the
+fovea. Cope et al.~showed that this relationship can explain
+increased saccadic latencies for distal targets, resulting from
+reduced activity in the decision making circuitry of the basal ganglia.
+However, the notion that activity in superior colliculus is
+eccentricity-dependent conflicts with the result of
+\cite{tabareau_geometry_2007}, who showed
+that an invariant hill of activity was required if this complex
+logarithmic weight mapping was to be used to drive a
+two-degree-of-freedom saccadic burst generator, and also with
+experimental findings, which do not show significant eccentricity
+dependence~\cite{ref}.
+
+To bring our model in line with these results, whilst maintaining the
+eccentricity dependent activity in basal ganglia, we hypothesised
+that a `widening projection' exists between two maps in superior
+colliculus. Activities in one SC\_deep layer remains eccentricity-dependent,
+with loops back to thalamus and cortex and through basal ganglia.
+This activity is then fed through a projection, which applies a
+Gaussian projection field, whose width increases with increasing
+stimulus eccentricity according to Eq.~\ref{eq:widening}.
+The activity in this second SC\_deep layer is then fed to the
+weight maps of the SBG. This model was called `TModel4'. TModel4
+was parameterised such that its horizontal and vertical error
+was similar---so that its equivalent of Fig.~\ref{fig:sacc_vs_targ}
+showed a similar sum of squares error.
+
+Figs.~\ref{fig:errorsurface}(a)--(d) show the same percentage errors
+for TModel4 as Fig.~\ref{fig:errorsurfaceTM3} shows for TModel3.
+First of all, note that the error magnitudes are much smaller;
+the colour bar applies to a range between 0 and 20\%. The mean
+errors are smaller for every axis. The largest errors produced by
+the model are approximately 15\%, which are
 within the boundaries of what some authors have suggested would be regarded
-as an accurate saccade \cite{mcpeek_saccade_2002,mcpeek_incomplete_2006}
-(the magnitude of the largest error vector is approximately 1.5$\degree$).
+as an accurate saccade [\cite{mcpeek_saccade_2002,mcpeek_incomplete_2006}].
+The magnitude of the largest error vector is approximately 1.5\dg.
+
+This result indicates that the
+exponential part of the Ottes et al.~weight maps from SC to the SBG cannot
+on its own compensate for the eccentricity-dependent size of the hill of
+activity. The introduction of a widening projection field substantially
+improves the mean accuracy of saccades across the field of view.
+We therefore suggest that the transformation between retinotopically mapped
+activity, and eccentricity-independent activity width occurs
+within the superior colliculus and works alongside a simple,
+monotonically increasing weight map between SC and the SBG channels.
 
 % These errors are larger than those in Thurat due to the hill of
-% activity not being `perfect'
-
-\subsection{Saccade sequences}
-
-\subsubsection{Out \& return}
-
-We investigated the behaviour of the model for saccade sequences.
-In one experiment, we illuminated a fixation
-cross from 0~s until 0.4~s, followed by a target at (-10$\degree$, 0)
-from 0.4~s until 0.8~s. Finally, the fixation was again shown from 0.8~s
-until the end of the simulation at 2~s. This induced a saccade to a
-10$\degree$ eccentricity, followed by a return saccade back to the
-null point. Fig.~\ref{fig:outrtn} shows the
-outward and return trajectories produced by the experiment. Panel (a) 
-shows the $x$ and $y$ rotation trajectory; panel (b) shows individual
-rotational components of the eye. The return trajectory shows a 
-distinctly different form from the outward trajectory; it has a dynamic
-overshoot, of the type described in \cite{bahill_trajectories_1979}.
-This is caused by the initial restorative force applied by the elastic
-extraocular muscles, which are not at their null point when the return
-saccade starts. Interestingly, if a sequence of out \& return saccades is
-programmed, dynamic overshoot is also observed in the second and
-subsequent `out' saccades. This occurs because at the start of the 
-second `out' saccade, the eye ball is rotated away from the null point,
-especially around the $x$ and $z$ axes.
-
-\subsubsection{Double steps}
-
-In another experiment, we...
+% activity not being `perfect' Discussion point.
 
@@
 functionality as that reported in \cite{cope_basal_2017}, we
-investigated the effect on saccadic response times of
-target eccentricity and any gap or overlap between fixation off-time 
+investigated the effect on saccadic response times of:
+target eccentricity; and any gap or overlap between fixation off-time
 and target on-time. We showed that the full model reproduces the
@@
 horizontal [Fig.~\ref{fig:lat_vs_all}(a)], vertical
-[Fig.~\ref{fig:lat_vs_all}(b)] and oblique saccades.  \cmnt{Talk about shape here and briefly explain why we see this shape}
-
-Fig.~\ref{fig:lat_vs_all}(c) shows latencies achieved when varying the... etc etc
-
-\subsection{Saccade with distractor}
-
-Fig.~\ref{fig:targ_w_distr}(a) shows three horizontal saccades to a 
-target at $\theta_{y}=$-10$\degree$. The first saccade (blue 
-trajectory) had no distractor luminance, the second saccade (red) was
-modulated by the appearance of a distractor cross of magnitude 1
-located at $\theta_{x}=$-7$\degree$, $\theta_{y}=$-7$\degree$. 
-The distractor appeared 0.1~s after the target and 
-persisted for 0.1~s [Fig.~\ref{fig:targ_w_distr}(b)]. The third 
-saccade (green) had conditions identical to the red saccade, but 
-with a brighter distractor luminance, whose magnitude was 2.
-
-\subsection{Saccade to twin targets}
+[Fig.~\ref{fig:lat_vs_all}(b)] and oblique saccades (not shown). The latency
+increases with eccentricity far from the fovea because the retinotopic mapping
+reduces the activity in the basal ganglia for more eccentric targets (this
+effect is described in detail in \cite{cope_basal_2017}). Closer to the fovea,
+the interaction between the foveal mask and the activity in FEF again leads
+to reduced input into into the basal ganglia and an increased time to
+achieve disinhibition in SNr.
+
+Fig.~\ref{fig:lat_vs_all}(c) shows latencies achieved when varying the time
+between fixation offset and target onset. This is termed the \e{gap condition};
+and is represented by a scalar value which, if positive, refers to a gap
+between fixation offset and target onset, and when negative, signifies an
+overlap, with the fixation luminance persisting past the time at which the
+target is illuminated. A negative gap is also termed an \e{overlap}.
+Again, we verify the behaviour
+presented in \cite{cope_basal_2017}, explained as resulting from the
+inhibition of the cortico-thalamic loop by SNr. In the gap condition, when
+the fixation luminance is removed, activity in STN immediately begins to
+decay, allowing SNr activity to reduce and thereby reducing inhibition on
+thalamus, allowing the target luminance to build up quickly in FEF, thalamus
+and through the basal ganglia's striatum and SNr. The shape of the curves in
+Fig.~\ref{fig:lat_vs_all}(c) matches the results in \cite{cope_basal_2017}
+for target luminances of 1 and 0.6; for overlaps longer than 100~ms
+(gap $<$ -100~ms), the latency becomes constant; the saccade is programmed
+whilst the fixation is present, with the target luminance inducing sufficient
+activity in striatum to `break through' the SNr inhibition caused by the
+fixation. If the target luminance is reduced to 0.3, the balance is altered
+in favour of the fixation and the latency vs.~gap becomes approximately
+linear and equal to the overlap time plus around 100~ms.
+
+Fig.~\ref{fig:lat_vs_all}(d) shows the effect of the dopamine parameter on
+saccade latencies in gap, step and overlap conditions. In general, the effect of
+decreasing the dopamine parameter was a smooth, monotonic and undramatic
+increase in saccade latency. However, the data for the overlap condition
+with a target luminance which was 3 times as bright as the fixation luminance
+was more interesting. Here we see a transition around a dopamine value if 0.7.
+Below this value,
+the basal ganglia is not able to select the target luminance until the fixation
+is removed, reducing the excitatory drive from STN to SNr, and consequently
+the inhibition from SNr to the thalamo-cortical loop. For the target
+luminance 0.6, 0.7 dopamine allows the basal ganglia to select sufficiently well
+so that the target can build up in the thalamo-cortical loop, in spite of
+the fixation overlap.
+
+Finally, the relationship between latency and the target luminance is given in
+Fig.~\ref{fig:lat_vs_all}(e). This shows latency for a 100~ms gap, step and
+100~ms overlap conditions for a given fixation luminance of 0.2,
+and a horizontally located target at $\theta_{y}^{t}=$-10\dg. For the
+gap condition, we see very short latencies for luminances of about 0.75 and above.
+The activity driving these express saccades is initiated by strong activity
+in the superficial layer of SC, which then drives activity in thalamus and
+through the basal ganglia. A gradual transition from express saccades to
+reflexive saccades is observed as the contribution of the SCs becomes weaker
+and the drive from FEF into the thalamo-cortical loop becomes necessary
+to elicit a saccade.
+%
+A similar gradual transition, albeit for higher latencies
+is seen for the step condition. At higher target luminances, the SCs has a
+greater effect on the acitivity in the thalamocortical loop, however, the
+activity in STN caused by the fixation luminance increases the latency at
+all luminance values compared with the gap condition.
+%
+The overlap condition leads to increased latencies for luminances below 2.5, but
+meets the step condition above this value, at which the 0.2 fixation
+luminance appears to have a negligible effect on the system.
+
+\subsection{Saccade sequences}
+
+We now present results derived from the fully parameterised and integrated
+model; where we took advantage of the fact that it is a closed loop system. This
+allowed us to present sequences of target luminances and allow the model to
+direct its fovea at the most salient target.
+
+\subsubsection{Out \& return}
+
+We investigated the behaviour of the model for saccade sequences.
+In one experiment, we illuminated a fixation
+cross from 0~s until 0.4~s, followed by a target at (0,-10\dg)
+from 0.4~s until 0.8~s. Finally, the fixation was again shown from 0.8~s
+until the end of the simulation at 2~s. This induced a saccade to a
+10\dg~eccentricity, followed by a return saccade back to the
+null point. We noticed some irregularities in the return saccades, which
+though surprisingly accurate, had a significant overshoot.
+More perplexingly, if the target was switched repeatedly between 0\dg~and
+10\dg, second and subsequent \e{outward} saccades also showed this
+overshoot. We found that the cause of these irregularties was the
+lack (in `TModel4') of any mechanism to reset the tonic neurons in the
+SBG after the first saccade. This resulted in TN activity in the left
+channel \e{and also} in the right channel. Interestingly, this ensured
+that, at  least for a few out-and-return saccades, the saccade accuracy was
+relatively good, with trajectories resembling experimental data
+(\cite{bahill_trajectories_1979}, p.~6). % Poss. figure.
+Nevertheless, the lack of a reset of TN activity was an oversight, and
+is indeed proposed and included in the connectivity of the
+\cite{gancarz_neural_1998} model. We implemented this feature by adding an
+additional inhibitory input to the `integrator' component of TModel4,
+driven by the contralateral EBN population, naming the new model `TModel5'.
+Now, when the eye is directed towards an eccentric target which is then
+exchanged with a target at the null point, the EBN activity toward the
+null point will tend to extinguish the TN activity which was holding
+the eye at the eccentric position.
+We verified that none of the single saccade results were affected
+by this modification.
+%
+% This doesn't account for *all* cases where you'd want to remove the TN
+% activity. Imagine a saccade purely UP then a saccade to a location
+% purely RIGHT. You'd need to remove the TN activity on the UP channel,
+% but you'd not be inducing any DOWN with the new target.
+
+Fig.~\ref{fig:outrtn} shows the
+outward and return trajectories produced by the experiment
+with the TN reset mechanism. Panel (a)
+shows the $x$ and $y$ rotation trajectory; panel (b) shows individual
+rotational components of the eye. Fig.~\ref{fig:outrtn}(c) shows
+out and return trajectories for three other saccade targets; horizontal,
+vertical and oblique. The trajectories have characteristic shapes and
+also show some stochastic variation caused by the noise in the model [see
+dashed trajectories in Fig.~\ref{fig:outrtn}(a)].
+
+The return trajectories (magenta lines) showed a
+distinctly different form from the outward trajectories. They overshot
+their destination (the null point) significantly. This resulted from the
+removal of the TN activity which was holding the eye at the eccentric
+target location. Removal of this activity, and thus the static force
+exerted by the corresponding extraocular muscle, meant that the eye
+was subject both to a new muscular force towards the null point
+\e{alongside} the restorative spring force of the lengthened rectus
+muscle. This stands as a shortcoming of the model.
+
+\subsubsection{Double steps}
+
+In another experiment, we probed the response of the model to double step
+stimuli of the type described in \cite{becker_analysis_1979}. In that
+work, the response of human subjects was investigated when shown stimuli
+at 15\dg~and 30\dg~eccentricity with variable delay between
+the stimuli. If the smaller eccentricity stimulus was shown first, followed
+by the more distal on the same side of the field of view, this was called
+a `staircase' presentation.
+%If the more distal stimulus preceded the 15\dg~stimulus (again with
+%both in the same hemifield), this was called `pulse undershoot'.
+We carried
+out a `staircase' presentation, shown in Fig.~\ref{fig:doublesteps},
+where our small eccentricity luminance was at 8\dg~and our more
+distal luminance was at 12\dg~(both to the right of centre). We
+found that there was a critical time delay between the luminances
+of about 30~ms. If they were presented with a delay smaller than this
+value, then a single, slightly hypermetric saccade was made. This
+response type is called a \e{final angle response}. A delay greater
+than 30~ms between the stimuli would lead to double step saccades
+(a so-called \e{initial angle response}),
+with the first saccade arriving at 8\dg~(though with greater
+variability than normal), and a second saccade being made
+to a location hypometric of 12\dg~after a pause of about 240~ms.
+Fig.~\ref{fig:doublesteps}(a) shows the mean trajectories from 5 simulations
+of the staircase doublestep presentation alongside the result for a
+single saccade to the final angle of 12\dg. Dash-dot lines show
+$\pm$1 standard deviation about the mean. The corresponding trajectories
+are shown in Fig.~\ref{fig:doublesteps}(b).
+
+Inspection of the activity maps in FEF and SC\_deep (not shown) indicates
+that when
+the 8\dg~target is illuminated for 30~ms or more, the activity
+associated with this target angle is able to dominate the activity,
+hence the execution of a reasonably accurate saccade. The inhibitory
+feedback from the SBG then extinguishes activity in FEF, Thalamus and
+SC, which means that a full 200~ms or more is required to allow
+activity in these populations to build up again in order to make the
+smaller saccade from 8\dg~to 12\dg. This is in contrast
+to experimental findings in which the corrective second saccade is
+often executed \e{more quickly} than if it were programmed on its own.
+
+%\subsection{Saccade with distractor} enough!
+
+%Our integrated model allows us to examine the effect of distractor
+%luminances on saccade dynamics. Fig.~\ref{fig:targ_w_distr}(a) shows
+%three horizontal saccades to a
+%target at $\theta_{y}=$-10\dg. The first saccade (blue
+%trajectory) had no distractor luminance, the second saccade (red) was
+%modulated by the appearance of a distractor cross of magnitude 1
+%located at $\theta_{x}=\,$-7\dg, $\theta_{y}=\,$-7\dg.
+%The distractor appeared 0.1~s after the target and
+%persisted for 0.1~s [Fig.~\ref{fig:targ_w_distr}(b)]. The third
+%saccade (green) had conditions identical to the red saccade, but
+%with a brighter distractor luminance, whose magnitude was 2.
+
+%\cmnt{Ok, now saccades can deviate TOWARDS a distractor - particularly
+%if the distractor is closer to the trajectory - see for example
+%~\cite{wang_distractor_2014}. This model doesn't seem to have any
+%mechanism to induce a deviation of trajectory away from the distractor. }
+
+%\subsection{Saccade to twin targets} enough!
 
@@
 
+The aim of this study was to demonstrate the importance of modelling
+neurological systems \e{in concert with} the biomechanical systems
+together with which they have evolved. We hypothesised that by combining
+existing neurophysiological models with an accurate
+model of a musculo-skeletal system, and then `closing the loop' by allowing
+the movements of the virtual muscles to modulate sensory feedback to
+the brain model, shortcomings in the constituent models would be
+revealed, leading to new knowledge. To demonstrate the validity
+of this hypothesis, we built an integrated model and then identified the
+modifications which were necessary to give it the ability to make
+accurate movements under one type of stimulus. We then
+examined its behaviour with other stimuli.
+
+% This is probably recapitulation of intro material.
+We chose the oculomotor model as a basis for this study because it has
+only three degrees of freedom~\cite{ref}, making it one of the simplest
+musculo-skeletal systems. Furthermore, eye movements fall into several
+well-defined categories, each being controlled by separate
+brain circuits~\cite{refs}, we were therefore justified in modelling a
+system which produced only saccadic eye movements. Nevertheless, we are
+aware that we did not create a complete model of the system; no treatment
+of Cerebellum was attempted, justified because Cerebellum appears to have
+only a minor effect on saccade accuracy [\cite{refs}], probably correcting
+for slow to medium timescale changes in the physical dynamics of the
+eyeball [\cite{refs}].
+
+To summarise our model integration: We combined
+the \ccg~model [\cite{cope_basal_2017}] with a saccadic burst generator
+model based on the work of \cite{gancarz_neural_1998}, using this to
+drive the input of a new biomechanical eye model. To achieve the spatial
+transformation from the retinotopic maps of the \ccg~model, to the six
+`muscle channel' inputs for the saccadic burst generator, we used
+the mapping of \cite{ottes_visuomotor_1986} to produce parameterised
+weight maps. We introduced an additional
+transformation to the brain model to achieve invariant sized hills of
+activity in superior colliculus to fulfil the invariant integral
+hypothesis of \cite{tabareau_geometry_2007}. We closed the loop using
+a software component which transformed a view of a world containing
+luminous cross shapes into the eye's frame of reference, given its
+instantaneous rotational state. This component also computed the inverse
+of the mapping from \cite{ottes_visuomotor_1986} to project the view
+retinotopically into the brain model.
+
+This paper serves to describe how we achieved the integration in
+order to test our hypothesis, and we intend that the material and
+methods section, along with the model code itself, will help others
+to carry out similar studies. However, we wish to devote the majority
+of this discussion to what can be learned from an integrated model
+of a combined brain and biomechanical system, using our oculomotor system
+as an example.
+
+Our integration approach revealed three ways in which this model fails
+to provide a full understanding of the saccadic system. In each case,
+the issue is made clear \e{as a result of the integration}. This is not
+to say that other approaches may not also reveal shortcomings; we will
+see that one of our cases has been independently identified
+[\cite{groh_effects_2011}]. Nonetheless, the
+
+\subsection{The need for a widening projection field}
+
+The original combination of the \ccg~model with the theoretical weight
+maps of Ottes et al.~and Tabareau et al.~resulted in a model which was
+able to produce accurate saccades only along the principle rotational
+axes (Fig.~\ref{fig:errorsurfaceTM3}). Thus, \e{the integration of
+the models} suggested that an additional
+layer was required to achieve accurate saccades for oblique, as well
+as for horizontal and vertical saccades. Although the \e{need} for an
+invariant integral is discussed in Tabareau et al.~as resulting from
+their theoretical study, the mechanism by which such an invariant
+Gaussian hill is generated is not. By combining the models, we were
+forced to consider this mechanism, and hypothesised that a widening
+projection field would be a candidate mechanism. The results of
+Fig.~\ref{fig:errorsurface} indicate that a substantial improvement
+in accuracy is indeed achieved by this new mechanism.
+
+\subsection{Saccades from non-null starting positions}
+
+The implementation of a biophysically accurate model of the eye, and
+the closed-loop nature of the model makes it very natural to consider
+how the model will behave making saccades from arbitrary starting
+positions, or how it would respond to a sequence of stimuli. This was
+the motivation for the out-and-return experiment (Fig~\ref{fig:outrtn})
+as well as for the double step experiment (Fig.~\ref{fig:doublesteps}).
+We found that return saccades were substantially affected by the
+biomechanics of the eye, as the brain and brainstem model had no
+mechanism to account for the position-dependent restoring forces applied
+by the eye. This question has been addressed by other authors;
+\cite{groh_effects_2011} investigates the effect of
+initial eye position on stimulated saccades
+and finds a need for the signal in superior colliculus to be modulated
+by an eye position signal. \cite{ling_effects_2007} shows the existence
+of a position dependent firing rate offset in abducens neurons. Though
+we will not speculate here on the mechanism by which return saccades
+may be made accurate whilst also resetting the activity of tonic
+neurons in the SBG, it is interesting that in the model in which we
+omitted to reset TN activity, we obtained relatively accurate
+out-and-return saccades which closely resembled experimental data.
+We suggest that residual activity in TN populations may offer an
+explanation for how the restorative force exerted by
+the elastic oculomotor muscles is compensated for. A comparison of
+this idea with that of \cite{groh_effects_2011} (that there is a
+modulation, from a brainstem signal, of the SC readout) would make
+a subject for a future study. Although these existing studies have
+highlighted this issue, the inaccurate return saccades which the
+model makes from eccentric starting positions provide a clear example
+of the way in which integrating known models into a closed-loop system
+can highlight deficiencies in the model.
+
+\subsection{Inhibitory feedback from saccadic burst generator to brain}
+
+The third issue raised by the integration of the component models of
+the saccadic system has, like the return saccades, to do with resetting
+activity. In this case, rather than the reset of activity in the TN
+population in the brainstem, it is the question of how the activity
+in the \e{brain} model should be reset after each saccade. When a target
+luminance is projected onto the World population in the model, this
+induces activity which `reverberates' in loops through FEF, basal
+ganglia, SC and thalamus. The brainstem contains a mechanism to limit
+the timescale of a saccade (inhibitory feedback from EBN, via IBN to
+LLBN; see Fig.~\ref{fig:sbg}). However, if the activity in SC is not
+reset, then following the completion of the first saccade, a series
+of subsequent `staircase' saccades will be executed. There needs to
+be a mechanism to extinguish activity in SC, but also in FEF and
+thalamus, as activity in either of these populations can build up
+and eventually cause repeat activity in SC and another saccade. We
+added hypothetical inhibitory feedback connections to our model,
+such that the IBN populations in the SBG would inhibit activity in
+FEF, thalamus and SC\_deep (Fig.~\ref{fig:sbg}), preventing the
+occurrence of staircase saccades.
+
+An examination of the behaviour of the model when presented with
+`double-step stimuli' reveals a problem with this scheme. We found
+that when double-step stimuli were presented (where an initial
+target at 8\dg~was replaced with a 12\dg~target after 30 or 40~ms)
+and a double saccade was made [Fig.~\ref{fig:doublesteps}(a), black
+lines] the second saccade latency was \e{longer} even than the
+initial saccade. This contrasts with \cite{becker_analysis_1979} who
+find that second, corrective saccades occur with \e{shorter} latencies.
+This suggests that the inhibitory reset signal implemented in
+this model is too strong or has the wrong timescales. This issue
+highlights the fact that connections \e{between} component models
+are quite as important as the connections within each model.
+
+\subsection{Concluding remarks}
+
+The omission of the cerebellum will not have escaped the reader's notice.
+Whilst many of the nuclei known to be involved in the production of
+saccadic eye movements are incorporated within the model, the cerebellum
+is not. The cerebellum is known to play an important r\^ole in saccade
+programming
+[\cite{dean_learning_1994, schweighofer_model_1996,quaia_extent_2000,kleine_saccade-related_2003}].
+It may be able to completely replace the functionality of the colliculus
+when lesioned [\cite{aizawa_reversible_1998,lefevre_distributed_1998}].
+However, this r\^ole is typically considered to be one of accuracy tuning
+[\cite{barash_saccadic_1999,dean_learning_1994}]; operating as an additive
+model. Furthermore, saccades made by individuals with cerebellar ataxias
+perform with only moderate loss of saccade accuracy
+[\cite{barash_saccadic_1999,federighi_differences_2011}]. Because we
+did not address learning in our model, and because our aim was to
+demonstrate the utility of integrating brain with biomechanics in order
+to highlight deficiencies, we considered the omission of the cerebellar
+nuclei acceptable in the present work.
+
+\cmnt{Need to remark that component stretching has not been addressed.}
+
+\cmnt{Omitted main sequence?}
+
+\cmnt{Explain significance of this work: We have integrated several models }
+
+\cmnt{Conclude with a statement something like `the Oculomotor system is well studied, with much being known about its operation, but it remains that a full understanding of this brain and biophysical system is far from complete.'}
+
 % Be sure to say that ``in future work, it will be possible to
-% investigate saccade trajectory modifications in Parkinson's''
+% investigate saccade trajectory modifications in Parkinson's'' - Jen's model.
 
@@
 
-\textit{Funding\textcolon} European Union FP7 Grant 610391 ``NoTremor''.
+\textit{Funding\textcolon} European Union FP7 Grant 610391 `NoTremor'.
 
@@
 at: https://github.com/ABRG-Models/OMM\_NeuroMuscular
+
+\cmnt{Get RRID for various software tools; SpineCreator Resource
+ID: SCR\_015637 SpineML\_2\_BRAHMS (SCR\_015640) SpineML (SCR\_015641) BRAHMS (SCR\_015642)}
+
+\cmnt{Could make movies as supp. data, too.}
 
@@
 { \textbf{fig:mapping} Representative mapping from eye's frame of
-reference in cartesian coordinates to retinotopic coordinates. (a) The
+reference in cartesian co-ordinates to retinotopic co-ordinates. (a) The
 mapping of luminances in the eye's frame of reference. The world input
@@
 the luminances. Here, there are two cross shaped luminances spanning
-10$\degree$, one of value 0.8 at the fixation point (0,0) and one of
-value 0.5 at a peripheral position (0,-12$\degree$). Note that these
-crosses have the same `bar width' of 2$\degree$ as the crosses 
-used in the simulations, but their span of 10$\degree$ is greater
-than the 6$\degree$ used in the simulations, to make these
+10\dg, one of value 0.8 at the fixation point (0,0) and one of
+value 0.5 at a peripheral position (0,-12\dg). Note that these
+crosses have the same `bar width' of 2\dg~as the crosses
+used in the simulations, but their span of 10\dg~is greater
+than the 6\dg~used in the simulations, to make these
 images clearer. (b) The locations of
 the luminances in the eye's frame of reference are then converted into
-retinotopic coordinates, with centrally located luminances being
+retinotopic co-ordinates, with centrally located luminances being
 represented at low values of $r$ and more peripheral luminances having
@@
 \begin{center}
-\includegraphics[width=0.95\textwidth]{./figures/errorsurface_percent.png}
+\includegraphics[width=0.95\textwidth]{./figures/errorsurface_TModel3.png}
 \end{center}
-\textbf{\refstepcounter{figure}\label{fig:errorsurface} Figure \arabic{figure}.}
-{ \textbf{fig:errorsurface} The end-point error surface. a) The 
+\textbf{\refstepcounter{figure}\label{fig:errorsurfaceTM3} Figure \arabic{figure}.}
+{ \textbf{fig:errorsurface} The end-point error surface for the original model (TModel3). a) The
 ratio of the magnitudes of the total error vector and the target
@@
 \begin{center}
-\includegraphics[width=0.8\textwidth]{./figures/outrtn.png}
+\includegraphics[width=0.95\textwidth]{./figures/errorsurface.png}
 \end{center}
-\textbf{\refstepcounter{figure}\label{fig:outrtn} Figure \arabic{figure}.}
-{ \textbf{fig:outrtn} There and back - a saccade to a target, followed by return to the original fixation.}
+\textbf{\refstepcounter{figure}\label{fig:errorsurface} Figure \arabic{figure}.}
+{ \textbf{fig:errorsurface} The end-point error surface for the model
+in which a widening projection field was added to the model of the
+superior colliculus. a) The
+ratio of the magnitudes of the total error vector and the target
+vector, expressed as a percentage. b) The ratio of the magnitude
+of the $x$ component of the error vector to the magnitude of the
+target vector, expressed as a percentage. c) As (b) but for the
+$y$ component. d) As (b), for $z$ component. All colour maps are
+shown with the same scale. The target rotations, $\theta_{x}^t$ and
+$\theta_{y}^t$ are denoted `Target X' and `Target Y' in the figure.
+Note that the range of the colour scale is 0 to 20\%, a much smaller
+range than the range in Fig~\ref{fig:errorsurfaceTM3}.}
 \end{figure}
@@
 \textbf{\refstepcounter{figure}\label{fig:lat_vs_all} Figure \arabic{figure}.}
-{ \textbf{fig:lat\_vs\_all} Exploring saccade latencies.}
+{ \textbf{fig:lat\_vs\_all} Exploring saccade latencies. a) Latency to first
+movement as a function of target eccentricity for horizontal targets. b) Latency
+vs. eccentricity for vertical targets. c) Latency vs. gap at three different
+luminance values. d) The effect of the dopamine parameter on saccade latencies
+in gap, step and overlap conditions, for two different target luminances.
+e) Saccade vs. luminance showing gradual transition between reflexive and
+express behaviour.}
 \end{figure}
@@
 \begin{center}
-\includegraphics[width=0.8\textwidth]{./figures/targ_w_distr.png}
+\includegraphics[width=0.8\textwidth]{./figures/outrtn.png}
 \end{center}
-\textbf{\refstepcounter{figure}\label{fig:targ_w_distr} Figure \arabic{figure}.}
-{ \textbf{fig:targ\_w\_distr} Effect of a distractor on single saccade.}
+\textbf{\refstepcounter{figure}\label{fig:outrtn} Figure \arabic{figure}.}
+{ \textbf{fig:outrtn} There and back - a saccade to a target, followed by
+return to
+the original fixation. a) Out and return saccade to a target at (0,-10\dg)
+b) Rotational components of the saccade shown in (a). c) Outward and return
+trajectories for the saccade shown in (a) alongside saccades to three other
+targets.}
 \end{figure}
 
+\begin{figure}[htb!]
+\begin{center}
+\includegraphics[width=0.8\textwidth]{./figures/doublesteps.png}
+\end{center}
+\textbf{\refstepcounter{figure}\label{fig:doublesteps} Figure \arabic{figure}.}
+{ \textbf{fig:doublesteps} Double steps. The effect of illuminating a first target
+at 8\dg~or 12\dg, followed by a second target at 12\dg~or 8\dg. a) Horizontal
+rotation of the eye plotted vs.~time for a saccade to the 12\dg~target only (red),
+and to an 8\dg~target at 0.4~s followed by a 12\dg~target after 30~ms (blue) or
+40~ms (black). The timings are indicated by vertical lines. When the second
+target is presented up to 30~ms after the initial target, the initial target
+has not had time to dominate the output saccade and a saccade to a location
+close to the second target is made. If the delay is 40~ms or more, the activity
+from the initial target has time to cause a built up of actiivty in SC\_deep
+and an initial saccade close to the first target is made, followed, after a
+longer than usual latency period, with a second saccade closer to the second
+target. In this graph, the mean of five separate simulations is plotted along
+with $\pm$1 standard deviation around the mean. b) The $\theta_{x}$/$\theta_{y}$
+trajectories corresponding to the data presented in (a).}
+\end{figure}
+
+%\begin{figure}[htb!]
+%\begin{center}
+%\includegraphics[width=0.8\textwidth]{./figures/targ_w_distr.png}
+%\end{center}
+%\textbf{\refstepcounter{figure}\label{fig:targ_w_distr} Figure \arabic{figure}.}
+%{ \textbf{fig:targ\_w\_distr} Effect of a distractor on single saccade.}
+%\end{figure}
+
 \end{document}

### 2017-09-01 papers/integration/omm_integ.tex
Updated, ready to submit paper

@@
 The construction of such closed-loop animal models constitutes a new
-paradigm of {\em computational neurobehaviour} and promises a more
+paradigm of \e{computational neurobehaviour} and promises a more
 thoroughgoing approach to our understanding of the brain's function as
@@
 % New introduction, tailored to the paradigm shift title.
-(New Introduction:)
-
+
+% Background
 The field of computational neuroscience has provided
-many \e{systems models} of the brain~\cite{arai_two-dimensional_1994,gancarz_neural_1998,hazy_towards_2007,blenkinsop_frequency_2017}. We
-refer to these as \e{mechanistic computational models}, meaning
+many \e{systems models} of the brain \citep{arai_two-dimensional_1994,gancarz_neural_1998,hazy_towards_2007,blenkinsop_frequency_2017}.
+We refer to these as \e{mechanistic computational models}, meaning
 models which consist of populations of neural elements, interconnected
 in a biologically plausible manner, which simulate the operation of
-the brain.
-
-Whilst they differ in scale and complexity, these models all seek to
+the brain. Whilst they differ in scale and complexity, these models
+all seek to
 describe the fundamental mechanisms behind common animal behaviours
 such as locomotion, threat evasion, reaching or feeding. However,
-almost none of the models cited here actually reproduce these
+none of the models cited here actually reproduce these
 behaviours. In each case, the activity in a certain population of
 neurons is taken to be representative of a behavioural outcome.
-
-\cmnt{Background, gap, solution (cheers Sean!)}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-(Old introduction, which became the VPH mini-paper intro:)
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-% Can make comparisons
-As mechanistic computational models of brain systems become more
-sophisticated we can aspire to make realistic comparisons between the
-behaviour of the model and that of the animal or human.
-
-% Short desc of mechanistic computational model
-By \e{mechanistic computational model}, we mean a model which
-consists of populations of neural elements, interconnected in a
-biologically plausible manner. Such a model may consist of neural
-elements that produce a time-dependent membrane voltage and realistic
-spiking behaviour (Hodgkin-Huxley, Fizhugh-Nagumo, Izhikevich, Leaky
-integrate and fire) in which case the neural element's activity can be
-obtained by counting action potentials (or considering their
-timing). Alternatively it may (as it does in this work) consist of
-rate-coded neural elements, whose activation variable is related to
-the spiking rate of a number of neurons (refs).
-
 % Sometimes, ok to just have a brain model
-In some cases, it is sufficient to take the activity of an internal
+In some cases, it \e{is} reasonable to take the activity of an internal
 population within the brain model as being representative of the
 induced behaviour. For example, a choice made in a \e{go/no-go} task
-could be determined from activity in a population within a Basal
-Ganglia model
-(\cite{nambu_discharge_1990,kuhn_event-related_2004}). The decision
+could be determined from activity in a population within a basal
+ganglia model
+\citep{nambu_discharge_1990,kuhn_event-related_2004}. The decision
 to \e{go} is selected by a reduction of activity in this population;
-maintenance of activity implies \e{no-go}. Error rates in this task
+maintenance of activity implies \e{no-go}. To validate the model, the
+error rates which it generates
 could be compared with experimentally determined error rates in
-primate subjects.
-% Brain model comparison validates model
-If the expression of behaviour by the model is similar when compared
-with the experimental data, this serves to validate the model for the
-healthy, neuro-typical subject.
-% Now describe comparison between model and expt. for diseased
-% subject.
-If we have confidence in the model's description of the behaviour for
-the healthy subject, we can now progress to a comparison between the
-model and an unhealthy subject. If we can identify a characteristic
-degradation in an aspect of the brain for an unhealthy subject, then
-we can seek to modify the model to mirror this degradation. By
-comparing the relationship between the model's behaviour as a function
-of the degradation parameter with the unhealthy individual's behaviour
-as a function of disease progression, we may be able to relate the
-disease progression state to the brain parameter and predict the
-time-course of the internal degradation of the brain.
-% Leave further discussion along these lines to the discussion
-% section.
-
-% But sometimes you might need brain and neuromuscular model
-Many behaviours are more complex and subtle than a decision. In the
-disease state, it may be the dynamics of the movement which is
-symptomatic rather than its outcome. A diagnostic task may produce an
-outcome whose error rate varies with disease state, but it may also
-produce movement characteristics which correlate with the disease
-progression such as the slow, jerky or inaccurate movements seen in
-Parkinson's Disease. In order to determine the validity of a model
-which seeks to describe more complex movements, it is necessary to
-express the movement commanded by the brain network as a realistic,
-simulated motion by means of a biomechanical model, driven by the
-brain model.
-
-% Motivation here is to study movement disorders by means of a
-% comparison between healthy subjects, the healthy model and diseased
-% subjects and the diseased model.
-Our motivation is to study movement disorders using our brain
-models. Because the challenge of integrating brain and biomechanical
-models has not, to our knowledge, previously been addressed, we chose
-to express some of the simplest, and most studied movements made by
-vertebrates: the rapid eye movements known as saccades. Saccades
-direct the fovea, the region of the eye with the highest spatial
-imaging resolution, towards putative targets of interest. Mammals make
-frequent saccades; many thousands every day. These movements are often
-described as ballistic: They are commanded by activity in the superior
-colliculus which encodes an endpoint for the saccade trajectory
-(\cite{wurtz_superior_1971,hepp_monkey_1993}); once initiated, the
-saccade proceeds in a relatively direct and stereotyped (though not
-always straight) trajectory (\cite{van_der_stigchel_eye_2006}) to
-the endpoint.
-% Why am I mentioning curved saccades? Because it shows that saccades
-% can exhibit rich behaviour and that modelling them is worthwhile.
-However, numerous studies have shown that saccade trajectories are
-affected by distractors (\cite{mcpeek_competition_2003,
-port_sequential_2003, van_der_stigchel_recent_2010}) and may be
-modified in-flight to the extent that saccades may be seen to perform
-significant, sometimes even U-shaped, curves towards or away from
-distractors. This shows that whilst saccades are simple compared to
-the movements of limbs, they still provide information about a number
-of mechanisms within the brain and an effort to model them accurately
-is worthwhile.
-
-% Say what we've done here, in short form.
-Parkinson's Disease is a progressive neurological disorder whose main
-symptoms relate to motor control. These include resting tremor,
-slowness of movements (bradykinesia), difficulty in initiating
-movement (akinesia) and rigidity (refs). It is considered to be a
-disease of the basal ganglia because during its progression, dopamine
-producing neurons in the substantia nigra pars compacta die away
-(ref), affecting the the striatum which depends on endogenous dopamine
-for correct operation (ref). The basal ganglia plays an important role
-in decision making and action selection (ref), including the selection
-of saccadic eye movements (\cite{hikosaka_role_2000}). In the later
-stages of Parkinson's Disease, patients show more latent saccades to
-targets of interest (ref). They have also been documented as showing
-poorer performance in the so-called anti-saccade protocol, in which
-the subject is instructed to make a saccade \e{away} from a visual
-target. Parkinson's Disease patients make significantly more errors;
-they will saccade \e{to} the visual target rather than \e{away} from
-it more often than healthy control subjects. To investigate the way in
-which degradation in the basal ganglia may be causing these defects we
-have developed an integrated brain and biomechanical eye model which
-we describe here. The model will initially be used to investigate the
-deterioration in anti-saccadic movements which is detectable even in
-relatively early-stage Parkinson's Disease.
-
-%See \cite{Rottach_dynamic_1996} for trajectory information in saccades.
+primate subjects. We refer
+to this as an \e{output assumption model} because the output is assumed
+to signify behaviour. (An \e{input assumption model} assumes that sensory
+input produces some particular form of neural activity in an input
+population of the model.)
+
+% Gap
+However,
+we may be interested in reproducing accurate simulated \e{trajectories},
+in order to find out how degradation of parts of the model affect
+movement. In Parkinson's Disease, degradation of the
+dopamine neurons originating in the substantia nigra pars compacta (SNc)
+causes diskinesia \citep{galvan_pathophysiology_2008}, as well as
+abnormal network activity in
+the basal ganglia \citep{brown_dopamine_2001,mccarthy_striatal_2011}.
+Sufferers of the disease would be
+expected to produce abnormal decision-making \e{and} movement trajectories
+in a reach-to-the-correct-target task such as the one described in
+\cite{james_target-distractor_2017}.
+%
+% Solution
+A model which
+sought to explore in detail the effects of the SNc degradation both on
+the decision making \e{and} on the movement dynamics would need a
+physically accurate virtual arm, as well as physically realistic sensory
+input for the brain. This is no less than a complete model of those sections
+of the brain and body which act to fulfil the task. Such a modelling
+effort, if successful, would result in a virtual robot capable of expressing
+behaviour \e{in response to sensory input from its environment}. This would
+represent a paradigm shift in the field of computational neuroscience
+worthy of the new name of \e{computational neurobehaviour}.
+
+% Existing models don't control movement unless they control either a mechanical
+% or virtual body.
+% Can't observe how learning in the model may effect it's evolution in time
+% We may miss features about the system
+% Brains exist to move muscles
+
+% Solution, build an integrated model. Also give background on OMM system here.
 
@@
 
+% Solution described means we now need to do background of eye movements:
+In an attempt to build a model combining brain, realistic
+biomechanics \e{and} sensory
+feedback, we sought to extend our previous work modelling the oculomotor system.
+The existing model \citep{cope_basal_2017} is already able to capture sensory input
+and convert it into a neural signal, assumed to specify the target of a
+\e{saccadic eye movement};
+a fast movement of the eyes which directs the fovea to a region of interest
+in the field of view.
+%
+The oculomotor system is an excellent candidate for modelling because
+its movements can  be specified with only three degrees of freedom,
+making it one of the simplest neuro-muscular system in the body.
+%
+It is nevertheless behaviourally
+interesting, as saccadic eye movements reveal information about decision making at
+a subconscious level
+\citep{deubel_saccade_1996,reppert_modulation_2015,marcos_determining_2016}.
+The modelling of the oculomotor system is served by a large body of
+behavioural data describing
+saccades \citep{tipper_reaching_2001,walker_effect_1997,casteau_effect_2012},
+many anatomical studies of the neural substrates involved
+\citep{meredith_intrinsic_1998,isa_intrinsic_2002,isa_exploring_2009}
+and electrophysiological data linking these together
+\citep{hepp_spatio-temporal_1983,dorris_neuronal_1997,mcpeek_competition_2003,vokoun_circuit_2011}.
+Furthermore, in the context
+of building \e{behaving} systems a
+necessary part of any model for which the behaviour requires visual attention
+and decision making is a realistic mechanism for gathering visual information.
+This is obvious from extrinsic considerations---a
+subject must look at a scene to make decisions or navigate within it. It
+also follows for \e{intrinsic} reasons. For example, \cite{howard_hand_1997}
+showed that visual cues affect reach trajectories and the same group later
+demonstrated that reaching affects the saccadic system
+\citep{tipper_reaching_2001} suggesting a close relationship between these
+neural systems. Building the simplest, behaving oculomotor system will
+therefore assist future computational neurobehavioural modelling efforts.
+
 Many neural populations are involved in the coding of saccadic eye
-movements, only a very brief overview is given here; for a recent
+movements, only a very brief overview is given here; for a
 review, see \cite{munoz_commentary:_2002}. One pathway takes
 information from the retina directly into the superficial layers of
-the superior colliculus in the brainstem (\cite{sterling_receptive_1971,linden_massive_1983,wu_involvement_1994}).
+the superior colliculus in the brainstem
+\citep{sterling_receptive_1971,linden_massive_1983,wu_involvement_1994}.
 Activity within
 the superior colliculus then excites neurons in the pons, medulla and
-rostral mid-brain (\cite{sparks_brainstem_2002}) and then through
+rostral mid-brain \citep{sparks_brainstem_2002} and then through
 channels to the motor neurons which innervate the extraocular muscles
-(\cite{fuchs_firing_1970,sparks_brainstem_2002}). This direct pathway
+\citep{fuchs_firing_1970,sparks_brainstem_2002}. This direct pathway
 is responsible for the low latency saccades called express saccades
-(\cite{schiller_effect_1987,edelman_activity_1996}).
-
-% FEF: \cite{schall_neural_1999}
+\citep{schiller_effect_1987,edelman_activity_1996}.
+%
 Information from the retina is also processed by visual cortex which
@@
 to reflexive and voluntary
-saccades \cite{schall_neural_1999}. Activity build up in the frontal
+saccades \citep{schall_neural_1999}. Activity build-up in the frontal
 eye fields is transferred to the intermediate layers of the superior
 colliculus
-\cite{stanton_frontal_1988-1} and is also processed by the basal ganglia, which
-participates in the selection of the winning saccade end point
-\cite{stanton_frontal_1988}.
-
-% On fact that SC doesn't encode oblique/torsional movements:
-% \cite{hepp_monkey_1993}
-
-% That means that you need both the expression of movement, and also a
-% means by which you can progress the disease in the model.
-
-%If such comparisons are to be made, then the behavioural output of the
-%model should be in the form of movements which can be directly
-%compared with the biological system. In order to express movements,
-%the brain model needs to drive biomechanical neuromuscular models.
-
-%\begin{methods}
+\citep{stanton_frontal_1988-1} and is also processed by the basal ganglia,
+which participates in the selection of the winning saccade end point
+\citep{stanton_frontal_1988}.
+%
+Although both cortical and subcortical paths produce a saccade
+target signal in the superior colliculus, it is also possible for
+animals to make relatively normal saccades even after the
+colliculus has been ablated
+\citep{wurtz_activity_1972,aizawa_reversible_1998},
+though express saccades are lost with collicular lesions
+\citep{schiller_effect_1987}. This makes the superior colliculus
+a perplexing structure, being both critically involved in saccade
+target specification \citep{sparks_sensory_1987} and saccade dynamic control
+\citep{waitzman_superior_1991,goossens_optimal_2012} and yet dispensible.
+The `backup pathway' likely incorporates the oculomotor vermis and
+fastigial oculomotor region of the
+cerebellum which are known to participate in the specification, dynamics
+and adaptation of saccadic eye movements
+\citep{kleine_saccade-related_2003,takagi_effects_1998}.
+
+There is a long history of modelling the oculomotor system. For a comprehensive
+review, see \cite{girard_brainstem_2005}. Models of individual systems have been proposed for brainstem \citep{robinson_oculomotor_1975,scudder_new_1988,gancarz_neural_1998},
+cerebellum \citep{quaia_model_1999,dean_modelling_1995,dean_learning_1994} and
+superior colliculus
+\citep{arai_two-dimensional_1994,moren_mechanism_2013,marino_spatial_2012}.
+More recently, combined models have also been
+developed incorporating sensory input \citep{cope_basal_2017} and driving simple
+physical plants representing the eye \citep{tabareau_geometry_2007,nguyen_saccade_2014,thurat_biomimetic_2015}.
+None of these models has yet fully closed the loop to produce a behaving system
+operating freely within its environment. We argue that developing
+integrated, closed-loop models of behaving systems offers insights into
+the operation of neural systems that are not available from
+input-~or output-assumption models.
+
 \section{Material \& Methods}
@@
 location of the eye at the end of the
-saccade~(\cite{wurtz_activity_1972,robinson_eye_1972,van_gisbergen_collicular_1987,mcilwain_lateral_1982}).
+saccade \citep{wurtz_activity_1972,robinson_eye_1972,van_gisbergen_collicular_1987,mcilwain_lateral_1982}.
 This location was used to recalculate the positions of the luminances in
@@
 
-To the \ccg~model, we have added a rate-coded brainstem model (a `saccadic
-burst generator'), and a biomechanical eye, implemented using the
-biomechanical modelling framework OpenSim. These will be described below,
-but first we will give a description of the co-ordinate systems and the
-modelling framework used.
+To the \ccg~model, we added a rate-coded brainstem model (a `saccadic
+burst generator') and a biomechanical eye, implemented using the
+biomechanical modelling framework OpenSim \citep{seth_opensim_2015}.
+These will be described below, but first we will give a description of
+the co-ordinate systems and the modelling framework used.
 
@@
 of retinotopically mapped neural sheets, we describe the co-ordinate system
-used in the world. The eye was located at the origin of a 3 dimensional, right-handed
+used in the world. The eye was located at the origin of a three-dimensional, right-handed
 Cartesian co-ordinate system, with its fovea directed in the $-z$ direction.
-There was a notional spherical screen which was also centered at the origin of the
+There was a notional spherical screen which was also centred at the origin of the
 co-ordinate system and had a radius of 50 (in arbitrary units). The \e{fixation
@@
 screen at which the eye was initially directed.
-Onto the screen were projected luminances, each of which having a position
+Onto the screen were projected target luminances, each of which having a position
 described by two co-ordinates; $\theta_{x}^{t}$, a
@@
 their vertical bar aligned with the meridian plane and their horizontal bar
-aligned with the horizon plane described above.
+aligned with the horizon.
 
@@
 execution framework
-(\cite{mitchinson_brahms:_2010,mitchinson_brahms_2015}). To run a
+\citep{mitchinson_brahms:_2010,mitchinson_brahms_2015}. To run a
 BRAHMS model, the researcher must develop \e{BRAHMS components} for
@@
 components connect together and how data is passed between them
-(\cite{mitchinson_brahms:_2010}). The main BRAHMS program first
+\citep{mitchinson_brahms:_2010}. The main BRAHMS program first
 reads the SystemML file, then dynamically loads all the required
@@
 In the current work, the \ccg~model was reproduced using the
-declarative SpineML markup language (\cite{richmond_model_2014}),
+declarative SpineML markup language \citep{alex_cope_spineml_2014,richmond_model_2014},
 with the help of the graphical SpineML model editing software
 called SpineCreator
-(\cite{cope_spinecreator:_2016}). SpineML,
+\citep{cope_spinecreator_2015,cope_spinecreator:_2016}. SpineML,
 which is a development of the NineML specification
-(\cite{incf_task_force_on_multi-scale_modeling_network_2011}),
+\citep{incf_task_force_on_multi-scale_modeling_network_2011},
 describes neural populations and their projections in a highly
@@
 with input conditions, connection lesions and component parameter
-updates. A complete description of SpineML is given
-in \cite{richmond_model_2014}.
-
+updates. A description of SpineML is given
+in \cite{richmond_model_2014}; the definitive definition is found
+in the schemas \citep{cope_spineml_2014}.
 SpineCreator, in its r\^ole as a graphical editor for the SpineML
 format, was used to generate the SpineML files describing the
-model. It was also used to generate the diagrams of the model
-(e.g. Fig.~\ref{fig:brain_model}).
+model. It was also used to generate the diagrams of the model.
 
@@
 about how the model is executed. A number of simulation
-engines can be utilised, including DAMSON (\cite{richmond_damson_2015}), GeNN
-(\cite{nowotny_flexible_2011,nowotny_spineml_2014}) and BRAHMS (used
+engines can be utilised, including DAMSON \citep{richmond_damson_2015}, GeNN
+\citep{nowotny_flexible_2011,nowotny_spineml_2014} and BRAHMS (used
 here). The simulation engine incorporating BRAHMS is called \stob~
-(\cite{cope_spineml_2_brahms_2015-1}). \stob~is a collection of XSLT
+\citep{cope_spineml_2_brahms_2015-1}. \stob~is a collection of XSLT
 stylesheets which first generate and compile C++ BRAHMS components
@@
 these BRAHMS components were hand-written in C++. To incorporate these
-components into the SpineML model, a model-specific modification was
-applied in \stob~(\cite{cope_spineml_2_brahms_2015}) making use of
-a \stob~feature designed for this purpose (The external.xsl file).
-
-Figure \ref{fig:model_framework} shows the workflow, in which the
+components into the SpineML model, a \stob~\e{external.xsl} file was used.
+The external.xsl file scheme for incorporating external BRAHMS components
+into a SpineML model was a new \stob~feature motivated by the current work.
+Fig.~\ref{model_framework} shows the workflow, in which the
 model specification files (blue box - a combination of SpineML files
@@
 The brain model, excluding the brainstem, is a re-implementation of
-the \ccg~model. Figure \ref{fig:brain_model} shows the layout of the
+the \ccg~model. Fig.~\ref{brain_model} shows the layout of the
 populations and the interconnections between them. Each population of
@@
 retinotopic co-ordinate system, roughly matching the known layout of
-the superior colliculus~(\cite{robinson_eye_1972}). % FIXME: and frontal eye field?
+the superior colliculus \citep{robinson_eye_1972}. % FIXME: and frontal eye field?
 
@@
 function. At this point, the naming scheme for the component becomes
-apparent; this is a Leaky Integrator with a linear transfer function.
-
-The LINret component used for the retinal populations is again similar
+apparent; this is a Leaky Integrator with a piecewise-linear transfer function.
+
+The LINret component used for the retinal populations is similar
 to the LINlinear component, but with no intrinsic noise and no
@@
 \end{equation}
-This component is used in the STN population, as it gives a more
+This component is used in the subthalamic nucleus (STN) population, as it gives a more
 physiologically accurate f-I
-behaviour \cite{wilson_model_2004,bevan_mechanisms_1999,hallworth_apamin-sensitive_2003}
+behaviour \citep{wilson_model_2004,bevan_mechanisms_1999,hallworth_apamin-sensitive_2003}
 which has been shown to allow the mapping of the basal ganglia network
 architecture onto an optimal decision making
-model \cite{bogacz_basal_2007}.
+model \citep{bogacz_basal_2007}.
 
 The D1MSN and D2MSN components are both leaky integrators, similar to
-LINlinear. They differ in that they have no shunting inhibition and a
+LINlinear. They differ in that they have no shunting inhibition. They
+are used in to model medium spiny neuron (MSN) populations in
+the striatum. As they model
+the fact that most MSN neurons fall into two groups; those expressing D1
+dopamine receptors and those expressing D2 receptors, they have a
 dopamine parameter that modulates the input activation, so
@@
 \end{equation}
-where $d$ is a dopamine parameter. Varying dopamine from 0 to 1
+where $d$ is the dopamine parameter. Varying dopamine from 0 to 1
 enhances the activation in the D1 model, whereas it decreases
 the activation of the D2 model elements, in line with experimental
-observations~\cite{refs}. Note that the equation for $a_{in}^{D1}$
+observations \citep{harsing_influence_1997,gonon_prolonged_1997}.
+Note that the equation for $a_{in}^{D1}$
 differs from that used in the \ccg~model, for which the
@@
 \end{equation}
-
+$w_i^{act}$ and $w_i^{sh}$ are, respectively, the weights
+of the $i^{th}$ activation or shunting connection; $x_i^{act}$
+and $x_i^{sh}$ are the signals input to the
+activation and shunting connections.
 %
@@
 mapping similar to that found empirically both in the superior
-colliculus [\cite{ottes_visuomotor_1986}] and in visual cortex
-[\cite{eric_l._schwartz_computational_1980}] and assumed in
+colliculus \citep{ottes_visuomotor_1986} and in visual cortex
+\citep{eric_l._schwartz_computational_1980} and assumed in
 this work to persist throughout the oculomotor system.
@@
 that an even density of cells can be maintained in the colliculus, but
-ensures that a single group of proximal, active, retinal neurons will
-always activate a single, proximal group of neurons on the collicular
+ensures that a group of adjoining, active, retinal neurons will
+always activate an adjoining group of neurons on the collicular
 surface.
@@
 region of the retina and has a value in the human of about
-7.8 mm/\dg~\cite{rovamo_estimation_1979}.
+7.8 mm/\dg~\citep{rovamo_estimation_1979}.
 
@@
 number of neurons in the retinotopic neural field. $E_2$ is
-2.5 [\cite{cope_basal_2017,slotnick_electrophysiological_2001}].
+2.5 \citep{cope_basal_2017,slotnick_electrophysiological_2001}.
 
@@
 
-Note that the mapping encompases the entire visual field. The value of
+The mapping encompases the entire visual field; the value of
 $\phi$ is allowed to vary from 0\dg~to 360\dg~along its axis.
@@
 
-Figure \ref{fig:mapping} shows the result of the mapping for a view of
+Fig.~\ref{fig:mapping} shows the result of the mapping for a view of
 two cross-shaped luminances. One cross illuminates the fovea, which
@@
 Briefly, the model consists of input from the World population (see
-Fig.~\ref{fig:brain_model}, green population box) producing activity
+Fig.~\ref{brain_model}, green population box) producing activity
 in an `express' pathway to superior colliculus (purple) and
 simultaneously in cortex, represented here by the FEF population (grey
-boxes in Fig.~\ref{fig:brain_model}). The express pathway causes short
+boxes in Fig.~\ref{brain_model}). The express pathway causes short
 latency activity in the superficial superior colliculus, which
@@
 projections indicate a connectivity pattern which `fans out' with a
-2-D Gaussian kernel; lighter blue connections from STN to SNr and GPe
+2-D Gaussian kernel; lighter blue connections from the subthalamic
+nucleus (STN) to SNr and globus pallidus externum (GPe)
 are diffuse, all-to-all connections and projections coloured green are
@@
 peripheral luminances from ever being selected.
-
+%
 Note that SC\_deep contains two recurrent connections; one is
@@
 tecto-tectal inhibition, which increases the inhibition between
-activity in opposite hemispheres of the field of view (refs) helping
+activity in opposite hemispheres of the field of view \citep{gian_g._mascetti_tectotectal_1981,olivier_evidence_2000} helping
 to resolve competition between saccades to the left and right. The
@@
 \cite{cope_basal_2017}.
-
-%However, it does not describe deeper, motor regions of the
-%brainstem, instead regarding the centroid of the activity in SC as
-%being representative of the end point of the saccade
-%trajectory \cite{mays_dissociation_1980,lee_population_1988,van_Opstal_role_1990}.
+%
+We have not listed the parameters of the network in tabular form here,
+instead, the reader is referred to the SpineML declarative
+specification of the model from the link given in SUPPLEMENTAL DATA.
+The easiest way to access this information is by using SpineCreator.
 
 % Section - description of new brainstem model
-\subsection{brainstem model}
+\subsection{Brainstem model}
 
@@
 for two of the model's
-six channels is shown in Fig.~\ref{fig:sbg}. Activity from the output
+six channels is shown in Fig.~\ref{sbg}. Activity from the output
 layer of superior colliculus (SC\_avg) is fed into each channel, which
@@
 force generated by the elastic properties of the muscles.  The
-required motor neuron activations are therefore a brief burst of
-increased activity that accelerates the eye, followed by a period
+required motor neuron activations are therefore a combination of features:
+a brief burst of
+increased activity that accelerates the eye; followed by a period
 of activity that is less than the burst firing rate but higher than
@@
 
-The SBG connectivity produce each of the these elements separately,
+The SBG connectivity produces each of the these features separately,
 then sums them to create the desired `bump and tonic' activation
@@
 TNs) is defined by a single leaky integrator, first order differential equation.
-\begin{equation}\label{eq:thetas_to_r}
+\begin{equation}\label{eq:LIN}
    \frac{da}{dt} = \frac{1}{\tau}(y-a)
@@
 
-\cmnt{Note that inhibition from IBN populations is fed back - or is this
-detail for the `integration' subsection?}
-
 % Section - description of biomechanical model
@@
 The output signals of the brainstem are used to drive the biomechanical model.
-The latter is not only used to get tangible feedback on the simulated saccades including motion trajectories, but adds one more modeling dimension related to the inertial properties of the eye plant including muscle properties.
-
-% Patras - what about a figure here? --- WILL ADD TOMORROW TUESDAY
+The latter is not only used to get tangible feedback on the simulated saccades
+including motion trajectories, but adds one more modelling dimension related to
+the inertial properties of the eye plant including muscle properties.
 
@@
 The biomechanical eye model, implemented using the OpenSim framework
-\cite{seth_opensim:_2011}, is anatomically represented by a sphere of
+\citep{seth_opensim:_2011,seth_opensim_2015}, is anatomically represented by a sphere of
 uniform mass distribution. The diameter of the eye is 24 mm for adults,
@@
 The force applied by EOMs is controlled by an excitatory signal
-supplied by motoneurons in the brainstem.
-The neural drive to produce a saccadic eye movement can be characterized by a pulse component to overcome the viscoelasticity of the orbital plant, a step component to stabilize the eye in the new position, and a slide component that models the gradual transition between the pulse and step.
+supplied by motoneurons in the brainstem. The neural drive to produce a saccadic
+eye movement can be characterized by a pulse component to overcome the
+viscoelasticity of the orbital plant, a step component to stabilize the eye in
+the new position, and a slide component that models the gradual transition
+between the pulse and step.
 
@@
 the deeper layers of the superior colliculus and the saccadic burst
-generator~\cite{van_gisbergen_experimental_1985,ottes_visuomotor_1986,waitzman_superior_1991,groh_converting_2001,arai_two-dimensional_1994,goossens_dynamic_2006,tabareau_geometry_2007,van_opstal_linear_2008,goossens_optimal_2012},
+generator \citep{van_gisbergen_experimental_1985,ottes_visuomotor_1986,waitzman_superior_1991,groh_converting_2001,arai_two-dimensional_1994,goossens_dynamic_2006,tabareau_geometry_2007,van_opstal_linear_2008,goossens_optimal_2012},
 which has become known as the spatial temporal transform (STT).  The
 spatial aspect of the transform is thought to be implemented by a
-weight-mapping~\cite{tabareau_geometry_2007,arai_two-dimensional_1994} and we
+weight-mapping \citep{tabareau_geometry_2007,arai_two-dimensional_1994} and we
 follow this idea.
@@
 Arai and co-workers trained a 20x20 neural network model of the
-superior colliculs to discover the weight map under the assumption of
-2D Gaussian activation profiles~\cite{arai_two-dimensional_1994}.
-%
-The training approach of Arai~et.~al. was not feasible in this study
+superior colliculus to discover the weight map under the assumption of
+2D Gaussian activation profiles~\citep{arai_two-dimensional_1994}.
+%
+The training approach of \cite{arai_two-dimensional_1994} was not feasible in this study
 due to the length of time required to run our model and its
-stochasticity, which means multiple runs of the model were necessary
+stochasticity, which meant multiple runs of the model were necessary
 in order to generate output statistics.
 %
-Tabareau and co-workers wrote down a theoretical form of the weight
+\cite{tabareau_geometry_2007} wrote down a theoretical form of the weight
 map, which follows from the mapping of \cite{ottes_visuomotor_1986}
 and the assumption of invariant 2D Gaussian activity profiles in
-SC~\cite{tabareau_geometry_2007}. As they found it closely resembles the
-results of Arai et al., and it is a simple formulation, we considered
+SC. As they found it closely resembles the
+results of \cite{arai_two-dimensional_1994}, and it is a simple
+formulation, we considered
 it as the means to generate the six weight maps in our own model.
@@
 and \cite{vokoun_response_2014}. Although in this work we do not model
-the SC in detail, we extended the model with a third functional layer named SC\_deep2
+the SC in detail, we extended the model with a third functional layer named SC\_deep2, shown in Fig.~\ref{scdeep}
 (\ccg~has only the two layers SC\_sup and SC\_deep). We
@@
 in \cite{tabareau_geometry_2007} was that it does not consider the
-existence of the oblique extraocular muscles. There is indeed evidence that
+existence of the oblique extraocular muscles. There is evidence that
 only two dimensional information is encoded in superior
-colliculus~\cite{wurtz_activity_1972,van_opstal_two-rather_1991}, but the
+colliculus \citep{wurtz_activity_1972,hepp_monkey_1993,van_opstal_two-rather_1991}, but the
 eye is actuated by six extraocular muscles. In order to find out a
 possible form for the input to the oblique muscles we carried out a
-training process described in supplementary material which depended on a
+training process
+% possibly descibe this training process in supplemental data
+which depended on a
 centroid computation in SC\_deep. For the four rectus muscles, the
@@
 time to curtail the saccade and avoid staircase
-saccades~\cite{gancarz_neural_1998}. In our model
+saccades \citep{gancarz_neural_1998}. In our model
 there is no such mechanism to reduce activity in SC\_deep, and elsewhere.
-Although a saccade towards target luminance will remove the excitation
-which caused the activity in SC\_deep (bringing it within the masked,
-foveal region), the activity in colliculus decays too slowly to avoid
+Although a successful, accurate saccade towards a target luminance will
+remove the excitation
+which caused the activity in SC\_deep by bringing the target luminance
+within the masked,
+foveal region, the activity in SC decays too slowly to avoid
 additional saccadic movements. We found it necessary to hypothesize
 an inhibitory feedback mechanism from the SBG to the brain model.
-This is shown in Fig.~\ref{fig:sbg}, which indicates how the output from
+This is shown in Fig.~\ref{sbg}, which indicates how the output from
 the inhibitory burst neurons (IBN) of the SBG model are used to feed
 back an inhibitory signal to the SC\_deep, thalamus and FEF populations
-in the brain model.
+in the brain model, resetting them ready for the next saccade.
 % Might have to justify the above a bit more.
@@
 ms. It would then recompute its outputs (the rotational state of the
-eye) and write these into the same, shared memory. The BRAHMS wrapper
+eye) and write these into the same shared memory. The BRAHMS wrapper
 would update its outputs whenever they were changed in the shared
@@
 The final models, on which the results of this paper are based are
-named `TModel3', `TModel4' and `TModel5'. Descriptions of earlier
+named `TModel3', `TModel4' and `TModel5'. Descriptions of these, and earlier
 versions of the model can be
 found in the code repository given in SUPPLEMENTAL DATA.
-
-%\end{methods}
 
@@
 0.005 of its peak. We iterated until the mean saccade endpoint plotted versus target
-was close to the ideal straight line---see Fig.~\ref{fig:sacc_vs_targ}(a) \& (c). We
+was close to the ideal straight line---see Fig.~\ref{sacc_vs_targ}(a) \& (c). We
 applied the same parameters to both directions of each channel;
@@
 weight maps (where the oblique maps are 1/10$^{\mathrm{th}}$ of the vertical maps,
-as described earlier) are shown in Fig.~\ref{fig:weightmaps}.
+as described earlier) are shown in Fig.~\ref{weightmaps}.
 % From map_modelling2.m:
@@
 
-\subsection{Single saccades} \label{sec:singlesaccades}
-
-Having finalised the model by setting the weight maps, we then proceeded
-to exercise the model, starting with saccades to a single target;
-prosaccades. Fig.~\ref{fig:outmany}(a) shows 9 representative saccades
-to a single
-target luminance. Initially, the eye had rotational state
-$\theta_x=\theta_y=\theta_z=0$ with its fovea directed at a
-fixation luminance cross (span 6\dg, bar width 2\dg) of
-magnitude 0.2 (in arbitrary units). At a
-simulation time of 0.4~s, the fixation luminance was set to 0 and
-a target luminance cross of the same dimensions as the fixation but with
-magnitude 0.3 was illuminated at one of the
-9 different locations, marked by crosses in Fig.~\ref{fig:outmany}(a).
-The resulting trajectories are plotted, with colour indicating the
-relationship between trajectories and target crosses. The approximate
-end-point error is visible in this figure, although the last point in
-each trajectory is the saccade position at 0.8~s and not the
-velocity-based end-point described above. Figs.~\ref{fig:outmany}(b) and (c)
-show the rotational components of the blue and red trajectories
-in Fig.~\ref{fig:outmany}(a) along with the target and fixation
-luminance values. Rotations are the eye's Euler rotational components
-in the world frame of reference.
-
 \subsection{Saccade accuracy}
 
-Fig.~\ref{fig:sacc_vs_targ} shows
+In Fig.~\ref{sacc_vs_targ}, we showed
 the result of running the model to targets located on the principle
@@
 mean saccade end-points.
-Fig.~\ref{fig:errorsurfaceTM3} shows saccade accuracy results for an
-entire hemifield in the naive model which passed the output of
+Fig.~\ref{errorsurfaceTM3} shows saccade accuracy results for an
+entire hemifield in the na\"ive model which passed the output of
 SC\_deep directly to SBG via the weight maps. The ratio of
 the magnitude of the error vector to the magnitude of the target
-vector is plotted as colour maps. This ratio is shown for the full,
-three dimensional error vector in Fig.~\ref{fig:errorsurfaceTM3}(a) and
-for the $x$, $y$ and $z$ components in Figs.~\ref{fig:errorsurfaceTM3}(b)--(c).
-Inspection of  Fig.~\ref{fig:errorsurfaceTM3}(a) shows that the end-point
+vector is plotted using a colour map. This ratio is shown for the full,
+three dimensional error vector in Fig.~\ref{errorsurfaceTM3}(a) and
+for the $x$, $y$ and $z$ components in Figs.~\ref{errorsurfaceTM3}(b)--(c).
+Inspection of  Fig.~\ref{errorsurfaceTM3}(a) shows that the end-point
 error is minimal along the principle axes ($\theta_{x}^t=\;$0 or
@@
 % Mention \cite{thurat_biomimetic_2015} in discussion.
-The $x$ component error map in Fig.~\ref{fig:errorsurfaceTM3}(b)
+The $x$ component error map in Fig.~\ref{errorsurfaceTM3}(b)
 shows the same trend, mirrored about the `Target X' axis, whereas
@@
 activity, because fewer retinal neurons are excited far from the
-fovea. Cope et al.~showed that this relationship can explain
+fovea. \cite{cope_basal_2017} showed that this relationship can explain
 increased saccadic latencies for distal targets, resulting from
@@
 experimental findings, which do not show significant eccentricity
-dependence~\cite{ref}.
+dependence, at least in the burst layer~\citep{anderson_two-dimensional_1998}.
+% Nice ref that - see Fig 16
 
@@
 was parameterised such that its horizontal and vertical error
-was similar---so that its equivalent of Fig.~\ref{fig:sacc_vs_targ}
+was similar---so that its equivalent of Fig.~\ref{sacc_vs_targ}
 showed a similar sum of squares error.
 
-Figs.~\ref{fig:errorsurface}(a)--(d) show the same percentage errors
-for TModel4 as Fig.~\ref{fig:errorsurfaceTM3} shows for TModel3.
-First of all, note that the error magnitudes are much smaller;
-the colour bar applies to a range between 0 and 20\%. The mean
+Figs.~\ref{errorsurface}(a)--(d) show the same percentage errors
+for TModel4 as Fig.~\ref{errorsurfaceTM3} shows for TModel3.
+First of all, note that the error magnitudes are much smaller. The mean
 errors are smaller for every axis. The largest errors produced by
@@
 within the boundaries of what some authors have suggested would be regarded
-as an accurate saccade [\cite{mcpeek_saccade_2002,mcpeek_incomplete_2006}].
+as an accurate saccade \citep{mcpeek_saccade_2002,mcpeek_incomplete_2006}.
 The magnitude of the largest error vector is approximately 1.5\dg.
@@
 This result indicates that the
-exponential part of the Ottes et al.~weight maps from SC to the SBG cannot
+exponential part of the Ottes et al.~weight map from SC to the SBG cannot
 on its own compensate for the eccentricity-dependent size of the hill of
@@
 
+\subsection{Single saccades} \label{sec:singlesaccades}
+
+Having finalised the model by setting the weight maps, we then proceeded
+to exercise the model (TModel4), starting with saccades to a single target;
+prosaccades. Fig.~\ref{outmany}(a) shows 9 representative saccades
+to a single
+target luminance. Initially, the eye had rotational state
+$\theta_x=\theta_y=\theta_z=0$ with its fovea directed at a
+fixation luminance cross (span 6\dg, bar width 2\dg) of
+magnitude 0.2 (in arbitrary units). At a
+simulation time of 0.4~s, the fixation luminance was set to 0 and
+a target luminance cross of the same dimensions as the fixation but with
+magnitude 0.3 was illuminated at one of the
+9 different locations, marked by crosses in Fig.~\ref{outmany}(a).
+The resulting trajectories are plotted, with colour indicating the
+relationship between trajectories and target crosses. The approximate
+end-point error is visible in this figure, although the last point in
+each trajectory is the saccade position at 0.8~s and not the
+velocity-based end-point described above. Figs.~\ref{outmany}(b) and (c)
+show the rotational components of the blue and red trajectories
+in Fig.~\ref{outmany}(a) along with the target and fixation
+luminance values. Rotations are the eye's Euler rotational components
+in the world frame of reference.
+
 % These errors are larger than those in Thurat due to the hill of
@@
 `hockey stick' shape shown in Fig. 7 of \cite{cope_basal_2017} for
-horizontal [Fig.~\ref{fig:lat_vs_all}(a)], vertical
-[Fig.~\ref{fig:lat_vs_all}(b)] and oblique saccades (not shown). The latency
+horizontal [Fig.~\ref{lat_vs_all}(a)], vertical
+[Fig.~\ref{lat_vs_all}(b)] and oblique saccades (not shown). The latency
 increases with eccentricity far from the fovea because the retinotopic mapping
@@
 
-Fig.~\ref{fig:lat_vs_all}(c) shows latencies achieved when varying the time
+Fig.~\ref{lat_vs_all}(c) shows latencies achieved when varying the time
 between fixation offset and target onset. This is termed the \e{gap condition};
@@
 and through the basal ganglia's striatum and SNr. The shape of the curves in
-Fig.~\ref{fig:lat_vs_all}(c) matches the results in \cite{cope_basal_2017}
+Fig.~\ref{lat_vs_all}(c) matches the results in \cite{cope_basal_2017}
 for target luminances of 1 and 0.6; for overlaps longer than 100~ms
@@
 
-Fig.~\ref{fig:lat_vs_all}(d) shows the effect of the dopamine parameter on
+Fig.~\ref{lat_vs_all}(d) shows the effect of the dopamine parameter on
 saccade latencies in gap, step and overlap conditions. In general, the effect of
@@
 
-Finally, the relationship between latency and the target luminance is given in
-Fig.~\ref{fig:lat_vs_all}(e). This shows latency for a 100~ms gap, step and
+The relationship between latency and the target luminance is given in
+Fig.~\ref{lat_vs_all}(e). This shows latency for a 100~ms gap, step and
 100~ms overlap conditions for a given fixation luminance of 0.2,
@@
 gap condition, we see very short latencies for luminances of about 0.75 and above.
-The activity driving these express saccades is initiated by strong activity
-in the superficial layer of SC, which then drives activity in thalamus and
+Finally, the activity driving these express saccades is initiated by high firing rates
+in the superficial layer of SC (SCs), which then drives activity in thalamus and
 through the basal ganglia. A gradual transition from express saccades to
@@
 is seen for the step condition. At higher target luminances, the SCs has a
-greater effect on the acitivity in the thalamocortical loop, however, the
+greater effect on the activity in the thalamo-cortical loop. However, the
 activity in STN caused by the fixation luminance increases the latency at
@@
 channel \e{and also} in the right channel. Interestingly, this ensured
-that, at  least for a few out-and-return saccades, the saccade accuracy was
+that, at  least for a few, consecutive out-and-return saccades, the saccade accuracy was
 relatively good, with trajectories resembling experimental data
@@
 
-Fig.~\ref{fig:outrtn} shows the
+Fig.~\ref{outrtn} shows the
 outward and return trajectories produced by the experiment
@@
 shows the $x$ and $y$ rotation trajectory; panel (b) shows individual
-rotational components of the eye. Fig.~\ref{fig:outrtn}(c) shows
+rotational components of the eye. Fig.~\ref{outrtn}(c) shows
 out and return trajectories for three other saccade targets; horizontal,
@@
 also show some stochastic variation caused by the noise in the model [see
-dashed trajectories in Fig.~\ref{fig:outrtn}(a)].
+dashed trajectories in Fig.~\ref{outrtn}(a)].
 
@@
 We carried
-out a `staircase' presentation, shown in Fig.~\ref{fig:doublesteps},
+out a `staircase' presentation, shown in Fig.~\ref{doublesteps},
 where our small eccentricity luminance was at 8\dg~and our more
@@
 to a location hypometric of 12\dg~after a pause of about 240~ms.
-Fig.~\ref{fig:doublesteps}(a) shows the mean trajectories from 5 simulations
+Fig.~\ref{doublesteps}(a) shows the mean trajectories from 5 simulations
 of the staircase doublestep presentation alongside the result for a
@@
 $\pm$1 standard deviation about the mean. The corresponding trajectories
-are shown in Fig.~\ref{fig:doublesteps}(b).
+are shown in Fig.~\ref{doublesteps}(b).
 
@@
 hence the execution of a reasonably accurate saccade. The inhibitory
-feedback from the SBG then extinguishes activity in FEF, Thalamus and
+feedback from the SBG then extinguishes activity in FEF, thalamus and
 SC, which means that a full 200~ms or more is required to allow
@@
 to experimental findings in which the corrective second saccade is
-often executed \e{more quickly} than if it were programmed on its own.
+often executed \e{more quickly} than if it were programmed on its
+own~\citep{becker_analysis_1979}.
 
@@
 %Our integrated model allows us to examine the effect of distractor
-%luminances on saccade dynamics. Fig.~\ref{fig:targ_w_distr}(a) shows
+%luminances on saccade dynamics. Fig.~\ref{targ_w_distr}(a) shows
 %three horizontal saccades to a
@@
 %The distractor appeared 0.1~s after the target and
-%persisted for 0.1~s [Fig.~\ref{fig:targ_w_distr}(b)]. The third
+%persisted for 0.1~s [Fig.~\ref{targ_w_distr}(b)]. The third
 %saccade (green) had conditions identical to the red saccade, but
@@
 neurological systems \e{in concert with} the biomechanical systems
-together with which they have evolved. We hypothesised that by combining
+with which they have evolved in parallel. We hypothesised that by combining
 existing neurophysiological models with an accurate
@@
 We chose the oculomotor model as a basis for this study because it has
-only three degrees of freedom~\cite{ref}, making it one of the simplest
+only three degrees of freedom, making it one of the simplest
 musculo-skeletal systems. Furthermore, eye movements fall into several
 well-defined categories, each being controlled by separate
-brain circuits~\cite{refs}, we were therefore justified in modelling a
+brain circuits, we were therefore justified in modelling a
 system which produced only saccadic eye movements. Nevertheless, we are
 aware that we did not create a complete model of the system; no treatment
-of Cerebellum was attempted, justified because Cerebellum appears to have
-only a minor effect on saccade accuracy [\cite{refs}], probably correcting
+of the cerebellum was attempted, justified because cerebellum appears to have
+only a minor effect on saccade accuracy \citep{dean_adaptive_2008}, probably correcting
 for slow to medium timescale changes in the physical dynamics of the
-eyeball [\cite{refs}].
+eyeball \citep{dean_learning_1994}.
 
 To summarise our model integration: We combined
-the \ccg~model [\cite{cope_basal_2017}] with a saccadic burst generator
+the \ccg~model \citep{cope_basal_2017} with a saccadic burst generator
 model based on the work of \cite{gancarz_neural_1998}, using this to
 drive the input of a new biomechanical eye model. To achieve the spatial
-transformation from the retinotopic maps of the \ccg~model, to the six
+transformation from the retinotopic maps of the \ccg~model to the six
 `muscle channel' inputs for the saccadic burst generator, we used
 the mapping of \cite{ottes_visuomotor_1986} to produce parameterised
+weight maps along with an empirically discovered synergy for the torsional
 weight maps. We introduced an additional
@@
 retinotopically into the brain model.
-
+%
 This paper serves to describe how we achieved the integration in
@@
 see that one of our cases has been independently identified
-[\cite{groh_effects_2011}]. Nonetheless, the
+\citep{groh_effects_2011}.
 
@@
 The original combination of the \ccg~model with the theoretical weight
-maps of Ottes et al.~and Tabareau et al.~resulted in a model which was
+maps of \cite{ottes_visuomotor_1986} and \cite{tabareau_geometry_2007}
+resulted in a model which was
 able to produce accurate saccades only along the principle rotational
-axes (Fig.~\ref{fig:errorsurfaceTM3}). Thus, \e{the integration of
+axes (Fig.~\ref{errorsurfaceTM3}). Thus, \e{the integration of
 the models} suggested that an additional
@@
 as for horizontal and vertical saccades. Although the \e{need} for an
-invariant integral is discussed in Tabareau et al.~as resulting from
+invariant integral is discussed in \cite{tabareau_geometry_2007} as resulting from
 their theoretical study, the mechanism by which such an invariant
@@
 projection field would be a candidate mechanism. The results of
-Fig.~\ref{fig:errorsurface} indicate that a substantial improvement
+Fig.~\ref{errorsurface} indicate that a substantial improvement
 in accuracy is indeed achieved by this new mechanism.
@@
 positions, or how it would respond to a sequence of stimuli. This was
-the motivation for the out-and-return experiment (Fig~\ref{fig:outrtn})
-as well as for the double step experiment (Fig.~\ref{fig:doublesteps}).
+the motivation for the out-and-return experiment (Fig.~\ref{outrtn})
+as well as for the double step experiment (Fig.~\ref{doublesteps}).
 We found that return saccades were substantially affected by the
@@
 neurons in the SBG, it is interesting that in the model in which we
-omitted to reset TN activity, we obtained relatively accurate
+omitted to reset TN activity (TModel4), we obtained relatively accurate
 out-and-return saccades which closely resembled experimental data.
@@
 the timescale of a saccade (inhibitory feedback from EBN, via IBN to
-LLBN; see Fig.~\ref{fig:sbg}). However, if the activity in SC is not
+LLBN; see Fig.~\ref{sbg}). However, if the activity in SC is not
 reset, then following the completion of the first saccade, a series
@@
 such that the IBN populations in the SBG would inhibit activity in
-FEF, thalamus and SC\_deep (Fig.~\ref{fig:sbg}), preventing the
+FEF, thalamus and SC\_deep (Fig.~\ref{sbg}), preventing the
 occurrence of staircase saccades.
@@
 target at 8\dg~was replaced with a 12\dg~target after 30 or 40~ms)
-and a double saccade was made [Fig.~\ref{fig:doublesteps}(a), black
+and a double saccade was made [Fig.~\ref{doublesteps}(a), black
 lines] the second saccade latency was \e{longer} even than the
@@
 
+% Cerebellum omitted
 The omission of the cerebellum will not have escaped the reader's notice.
@@
 programming
-[\cite{dean_learning_1994, schweighofer_model_1996,quaia_extent_2000,kleine_saccade-related_2003}].
+\citep{dean_learning_1994, schweighofer_model_1996,quaia_extent_2000,kleine_saccade-related_2003}.
 It may be able to completely replace the functionality of the colliculus
-when lesioned [\cite{aizawa_reversible_1998,lefevre_distributed_1998}].
+when lesioned \citep{aizawa_reversible_1998,lefevre_distributed_1998}.
 However, this r\^ole is typically considered to be one of accuracy tuning
-[\cite{barash_saccadic_1999,dean_learning_1994}]; operating as an additive
+\citep{barash_saccadic_1999,dean_learning_1994}; operating as an additive
 model. Furthermore, saccades made by individuals with cerebellar ataxias
 perform with only moderate loss of saccade accuracy
-[\cite{barash_saccadic_1999,federighi_differences_2011}]. Because we
+\citep{barash_saccadic_1999,federighi_differences_2011}. Because we
 did not address learning in our model, and because our aim was to
@@
 
-\cmnt{Need to remark that component stretching has not been addressed.}
-
-\cmnt{Omitted main sequence?}
-
-\cmnt{Explain significance of this work: We have integrated several models }
-
-\cmnt{Conclude with a statement something like `the Oculomotor system is well studied, with much being known about its operation, but it remains that a full understanding of this brain and biophysical system is far from complete.'}
-
-% Be sure to say that ``in future work, it will be possible to
-% investigate saccade trajectory modifications in Parkinson's'' - Jen's model.
+% Component stretching/main sequence not addressed
+We have not addressed the question of saccade duration in this paper.
+Saccade duration is of interest in models which produce two (or three)
+dimensional saccades, because the dynamics of a saccade follow well known
+relationships with the saccade eccentricity, regardless of the saccade
+angle. This causes a problem for models (such as the present one) for which
+some of the dynamic behaviour is generated within orthogonal components.
+For example, saccade duration increases with target eccentricity. A
+10\dg~eccentricity oblique (45\dg~up and right) saccade is composed
+(approximately) of a 7\dg~upwards component and a 7\dg~rightwards
+component. If the component based model is responsible for the dynamics,
+then the 10\dg~oblique saccade would be expected to have the dynamics
+of a 7\dg~up or 7\dg~right saccade. This is not found in practice, and
+the components are said to have been stretched, hence the name for this
+effect `component stretching'. The \cite{gancarz_neural_1998} model is
+reported to take account of the component stretching effect via the OPN
+neuron population. We did not find this effect in our implementation of
+the model; the duration of oblique saccades at a given eccentricity was
+always substantially different from the duration of the corresponding
+purely vertical or horizontal saccade. Because there is a somewhat
+complicated interplay between the dynamics of the superior colliculus
+driving the dynamic system of the SBG, we feel this is outside the scope
+of the current work and a subject for a future paper.
+
+% Significance of this work.
+This work represents a step forward in the modelling of neuromuscular systems,
+not because it significantly advances any of the constituent models, but
+because it \e{integrates} the models into a complete, \e{behaving} system.
+This is not the first integrated brain model composed of separately developed
+components. The works of \cite{nguyen_saccade_2014} and
+\cite{thurat_biomimetic_2015} are both based
+on an example of a brain model which drives a simple, second order model of the
+eye. \cite{dewolf_spiking_2016} describes a reach model which integrates models
+of cortex and cerebellum to drive a two degree-of-freedom arm model. Both of
+these example systems nevertheless operate using `curated' inputs supplied
+by the modeller.
+
+In contrast, the current work allows the state of the system to determine the
+input delivered to the model. The modeller only curates the state of the world
+at each time point, but the actual input to the model depends on the eye's
+rotational state.
+This is, to our knowledge, the first model which integrates the brain with an
+accurate biophysical system and closes the loop in this way, enabling the
+system to reproduce behaviour.
+As such, it offers a platform for testing more complex saccadic behaviour such as
+antisaccades or saccades in the presence of distractor stimuli. We believe
+that by building closed loop systems which express behaviour, we, and others
+will develop a new field of \e{computational neurobehaviour}, which will share
+themes from neuroscience, artificial intelligence, decision science and embodied
+robotics.
 
@@
 
-\cmnt{Get RRID for various software tools; SpineCreator Resource
-ID: SCR\_015637 SpineML\_2\_BRAHMS (SCR\_015640) SpineML (SCR\_015641) BRAHMS (SCR\_015642)}
-
-\cmnt{Could make movies as supp. data, too.}
-
 \selectlanguage{English}
@@
 %\end{center}
-% \textbf{\refstepcounter{figure}\label{fig:01} Figure \arabic{figure}.}{ Enter the caption for your figure here.  Repeat as  necessary for each of your figures }
+% \textbf{\refstepcounter{figure}\label{01} Figure \arabic{figure}.}{ Enter the caption for your figure here.  Repeat as  necessary for each of your figures }
 %\end{figure}
@@
 %\end{center}
-%\textbf{\refstepcounter{figure}\label{fig:02} Figure \arabic{figure}.}{ Enter the caption for your figure here.  Repeat as  necessary for each of your figures }
+%\textbf{\refstepcounter{figure}\label{02} Figure \arabic{figure}.}{ Enter the caption for your figure here.  Repeat as  necessary for each of your figures }
 %\end{figure}
@@
 
-\begin{figure}[htb!]
-\begin{center}
-\includegraphics[width=0.9\textwidth]{./figures/intro_graphic.png}
-\end{center}
-\textbf{\refstepcounter{figure}\label{fig:intro_graphic} Figure \arabic{figure}.}
-{ \textbf{fig:intro\_graphic} An isolated brain model. Crafted inputs
-are introduced into one of the model's n state variables. The output
-of another of the state variables implies behavioural change or
-onset.}
-\end{figure}
+%\begin{figure}[htb!]
+%\begin{center}
+%\includegraphics[width=0.9\textwidth]{./figures/intro_graphic.png}
+%\end{center}
+%\textbf{\refstepcounter{figure}\label{intro_graphic} Figure \arabic{figure}.}
+%{ \textbf{intro\_graphic} An isolated brain model. Crafted inputs
+%are introduced into one of the model's n state variables. The output
+%of another of the state variables implies behavioural change or
+%onset.}
+%\end{figure}
 
@@
 \end{center}
-\textbf{\refstepcounter{figure}\label{fig:model_framework} Figure \arabic{figure}.}
-{ \textbf{fig:model\_framework} The model framework. The model is specified using a combination of
+\textbf{\refstepcounter{figure}\label{model_framework} Figure \arabic{figure}.}
+{ The model framework. The model is specified using a combination of
 declarative XML files and hand-coded C++. These original model
@@
 the BRAHMS system. Most of the process is defined within the scripts
-which make up \stob, but the three hand-written components must be
+which make up \stob, but the hand-written components must be
 manually compiled and installed within the BRAHMS Namespace, allowing
@@
 \begin{center}
-\includegraphics[width=0.9\textwidth]{./figures/mapping.png}
-\end{center}
-\textbf{\refstepcounter{figure}\label{fig:mapping} Figure \arabic{figure}.}
-{ \textbf{fig:mapping} Representative mapping from eye's frame of
-reference in cartesian co-ordinates to retinotopic co-ordinates. (a) The
-mapping of luminances in the eye's frame of reference. The world input
-is pre-defined by a JSON configuration file. Luminance position, size
-and shape can be defined in this file, along with the times at which
-luminances appear and disappear. The worldDataMaker.cpp code computes
-the locations of the luminances in the eye's frame of reference, given
-its rotational state. It also computes a 2D gaussian convolution of
-the luminances. Here, there are two cross shaped luminances spanning
-10\dg, one of value 0.8 at the fixation point (0,0) and one of
-value 0.5 at a peripheral position (0,-12\dg). Note that these
-crosses have the same `bar width' of 2\dg~as the crosses
-used in the simulations, but their span of 10\dg~is greater
-than the 6\dg~used in the simulations, to make these
-images clearer. (b) The locations of
-the luminances in the eye's frame of reference are then converted into
-retinotopic co-ordinates, with centrally located luminances being
-represented at low values of $r$ and more peripheral luminances having
-higher values of $r$. $\phi$ encodes rotational angle: 1 and 50 encode
-upward movement; 13 is left; 25 is down; 37 is right. The output of
-the World component is fed into FEF\_add\_noise and into the retinal
-neuron populations. The colour map makes it possible to distinguish
-between the two crosses. (c) The FEF\_add\_noise populations adds a level
-of noise to the signal representing processing of the signal in visual
-cortex. (d) A Gaussian projection from FEF\_add\_noise to FEF further
-blurs the activity in FEF. FEF is the input to the basal ganglia and
-one input to superior colliculus.}
-\end{figure}
-
-\begin{figure}[htb!]
-\begin{center}
 \includegraphics[width=0.9\textwidth]{./figures/Brain_Model.png}
 \end{center}
-\textbf{\refstepcounter{figure}\label{fig:brain_model} Figure \arabic{figure}.}
-{ \textbf{fig:brain\_model} The brain model. This is the SpineCreator
+\textbf{\refstepcounter{figure}\label{brain_model} Figure \arabic{figure}.}
+{ The brain model. This is the SpineCreator
 `network layer' view of the model. Each box represents a neural
@@
 \begin{center}
+\includegraphics[width=0.9\textwidth]{./figures/mapping.png}
+\end{center}
+\textbf{\refstepcounter{figure}\label{fig:mapping} Figure \arabic{figure}.}
+{ Representative mapping from eye's frame of
+reference in Cartesian co-ordinates to retinotopic co-ordinates. (a) The
+mapping of luminances in the eye's frame of reference. The world input
+is pre-defined by a JSON configuration file. Luminance position, size
+and shape can be defined in this file, along with the times at which
+luminances appear and disappear. The worldDataMaker.cpp code computes
+the locations of the luminances in the eye's frame of reference, given
+its rotational state. It also computes a 2D Gaussian convolution of
+the luminances. Here, there are two cross shaped luminances spanning
+10\dg, one of value 0.8 at the fixation point (0,0) and one of
+value 0.5 at a peripheral position (0,-12\dg). Note that these
+crosses have the same `bar width' of 2\dg~as the crosses
+used in the simulations, but their span of 10\dg~is greater
+than the 6\dg~used in the simulations, to make these
+images clearer. (b) The locations of
+the luminances in the eye's frame of reference are then converted into
+retinotopic co-ordinates, with centrally located luminances being
+represented at low values of $r$ and more peripheral luminances having
+higher values of $r$. $\phi$ encodes rotational angle: 1 and 50 encode
+upward movement; 13 is left; 25 is down; 37 is right. The output of
+the World component is fed into FEF\_add\_noise and into the retinal
+neuron populations. The colour map makes it possible to distinguish
+between the two crosses. (c) The FEF\_add\_noise populations adds a level
+of noise to the signal representing processing of the signal in visual
+cortex. (d) A Gaussian projection from FEF\_add\_noise to FEF further
+blurs the activity in FEF. FEF is the input to the basal ganglia and
+one input to superior colliculus.}
+\end{figure}
+
+\begin{figure}[htb!]
+\begin{center}
 \includegraphics[width=0.5\textwidth]{./figures/Brain_Stem_1channel.png}
 \end{center}
-\textbf{\refstepcounter{figure}\label{fig:sbg} Figure \arabic{figure}.}
-{ \textbf{fig:sbg} One pair of channels of the saccadic burst
+\textbf{\refstepcounter{figure}\label{sbg} Figure \arabic{figure}.}
+{ One pair of channels of the saccadic burst
 generator (SBG) for left (cyan) or right (green) movements. Collicular
@@
 \end{center}
-\textbf{\refstepcounter{figure}\label{fig:scdeep} Figure \arabic{figure}.}
-{ \textbf{fig:scdeep} Showing additional deep layer of superior colliculus
+\textbf{\refstepcounter{figure}\label{scdeep} Figure \arabic{figure}.}
+{ Showing the additional deep layer of superior colliculus
 (SC\_deep2) and the output layer (SC\_avg, named for the fact that in an earlier
-version of the model, it received the output of the centroid of SC\_deep).}
+version of the model, it received the output of the centroid of SC\_deep).
+The widening Gaussian projection is shown as the arrow between SC\_deep
+and SC\_deep2.}
 \end{figure}
@@
 \end{center}
-\textbf{\refstepcounter{figure}\label{fig:sacc_vs_targ} Figure \arabic{figure}.}
-{ \textbf{fig:sacc\_vs\_targ} Accuracy at different target eccentricities for fixation luminance 0.2 and target luminance 0.3.}
+\textbf{\refstepcounter{figure}\label{sacc_vs_targ} Figure \arabic{figure}.}
+{ Accuracy at different target eccentricities for fixation luminance 0.2 and target luminance 0.3.}
 \end{figure}
@@
 \end{center}
-\textbf{\refstepcounter{figure}\label{fig:weightmaps} Figure \arabic{figure}.}
-{ \textbf{fig:weightmaps} Weight maps for the connections between the
+\textbf{\refstepcounter{figure}\label{weightmaps} Figure \arabic{figure}.}
+{ Weight maps for the connections between the
 output layer of superior colliculus and the six long lead burst
@@
 \begin{center}
+\includegraphics[width=0.95\textwidth]{./figures/errorsurface_TModel3.png}
+\end{center}
+\textbf{\refstepcounter{figure}\label{errorsurfaceTM3} Figure \arabic{figure}.}
+{ The end-point error surface for the original,
+na\"ive model (TModel3). a) The
+ratio of the magnitudes of the total error vector and the target
+vector, expressed as a percentage. b) The ratio of the magnitude
+of the $x$ component of the error vector to the magnitude of the
+target vector, expressed as a percentage. c) As (b) but for the
+$y$ component. d) As (b), for $z$ component. All colour maps are
+shown with the same scale. The target rotations, $\theta_{x}^t$ and
+$\theta_{y}^t$ are denoted `Target X' and `Target Y' in the figure.}
+\end{figure}
+
+\begin{figure}[htb!]
+\begin{center}
+\includegraphics[width=0.95\textwidth]{./figures/errorsurface.png}
+\end{center}
+\textbf{\refstepcounter{figure}\label{errorsurface} Figure \arabic{figure}.}
+{ The end-point error surface for the model
+in which a widening projection field was added to the model of the
+superior colliculus. a) The
+ratio of the magnitudes of the total error vector and the target
+vector, expressed as a percentage. b) The ratio of the magnitude
+of the $x$ component of the error vector to the magnitude of the
+target vector, expressed as a percentage. c) As (b) but for the
+$y$ component. d) As (b), for $z$ component. All colour maps are
+shown with the same scale. The target rotations, $\theta_{x}^t$ and
+$\theta_{y}^t$ are denoted `Target X' and `Target Y' in the figure.
+Note that the range of the colour scale is 0 to 20\%, a much smaller
+range than the range in Fig~\ref{errorsurfaceTM3}.}
+\end{figure}
+
+\begin{figure}[htb!]
+\begin{center}
 \includegraphics[width=0.8\textwidth]{./figures/outmany.png}
 \end{center}
-\textbf{\refstepcounter{figure}\label{fig:outmany} Figure \arabic{figure}.}
-{ \textbf{fig:outmany} Representative single saccades. a) Trajectories
+\textbf{\refstepcounter{figure}\label{outmany} Figure \arabic{figure}.}
+{ Representative single saccades. a) Trajectories
 from 9 saccades to a single target at 9 different locations. In each
@@
 \begin{center}
-\includegraphics[width=0.95\textwidth]{./figures/errorsurface_TModel3.png}
-\end{center}
-\textbf{\refstepcounter{figure}\label{fig:errorsurfaceTM3} Figure \arabic{figure}.}
-{ \textbf{fig:errorsurface} The end-point error surface for the original model (TModel3). a) The
-ratio of the magnitudes of the total error vector and the target
-vector, expressed as a percentage. b) The ratio of the magnitude
-of the $x$ component of the error vector to the magnitude of the
-target vector, expressed as a percentage. c) As (b) but for the
-$y$ component. d) As (b), for $z$ component. All colour maps are
-shown with the same scale. The target rotations, $\theta_{x}^t$ and
-$\theta_{y}^t$ are denoted `Target X' and `Target Y' in the figure.}
-\end{figure}
-
-\begin{figure}[htb!]
-\begin{center}
-\includegraphics[width=0.95\textwidth]{./figures/errorsurface.png}
-\end{center}
-\textbf{\refstepcounter{figure}\label{fig:errorsurface} Figure \arabic{figure}.}
-{ \textbf{fig:errorsurface} The end-point error surface for the model
-in which a widening projection field was added to the model of the
-superior colliculus. a) The
-ratio of the magnitudes of the total error vector and the target
-vector, expressed as a percentage. b) The ratio of the magnitude
-of the $x$ component of the error vector to the magnitude of the
-target vector, expressed as a percentage. c) As (b) but for the
-$y$ component. d) As (b), for $z$ component. All colour maps are
-shown with the same scale. The target rotations, $\theta_{x}^t$ and
-$\theta_{y}^t$ are denoted `Target X' and `Target Y' in the figure.
-Note that the range of the colour scale is 0 to 20\%, a much smaller
-range than the range in Fig~\ref{fig:errorsurfaceTM3}.}
-\end{figure}
-
-\begin{figure}[htb!]
-\begin{center}
 \includegraphics[width=0.8\textwidth]{./figures/lat_vs_everything.png}
 \end{center}
-\textbf{\refstepcounter{figure}\label{fig:lat_vs_all} Figure \arabic{figure}.}
-{ \textbf{fig:lat\_vs\_all} Exploring saccade latencies. a) Latency to first
+\textbf{\refstepcounter{figure}\label{lat_vs_all} Figure \arabic{figure}.}
+{ Exploring saccade latencies. a) Latency to first
 movement as a function of target eccentricity for horizontal targets. b) Latency
@@
 e) Saccade vs. luminance showing gradual transition between reflexive and
-express behaviour.}
+express behaviour.
+%f) Saccade duration vs. saccade eccentricity for horizontal
+%(rightwards), vertical (downwards) and 45\dg~oblique (down \& right) saccades.
+}
 \end{figure}
@@
 \end{center}
-\textbf{\refstepcounter{figure}\label{fig:outrtn} Figure \arabic{figure}.}
-{ \textbf{fig:outrtn} There and back - a saccade to a target, followed by
+\textbf{\refstepcounter{figure}\label{outrtn} Figure \arabic{figure}.}
+{ There and back - a saccade to a target, followed by
 return to
@@
 \end{center}
-\textbf{\refstepcounter{figure}\label{fig:doublesteps} Figure \arabic{figure}.}
-{ \textbf{fig:doublesteps} Double steps. The effect of illuminating a first target
+\textbf{\refstepcounter{figure}\label{doublesteps} Figure \arabic{figure}.}
+{ Double steps. The effect of illuminating a first target
 at 8\dg~or 12\dg, followed by a second target at 12\dg~or 8\dg. a) Horizontal
@@
 %\end{center}
-%\textbf{\refstepcounter{figure}\label{fig:targ_w_distr} Figure \arabic{figure}.}
-%{ \textbf{fig:targ\_w\_distr} Effect of a distractor on single saccade.}
+%\textbf{\refstepcounter{figure}\label{targ_w_distr} Figure \arabic{figure}.}
+%{ \textbf{targ\_w\_distr} Effect of a distractor on single saccade.}
 %\end{figure}

### 2017-09-01 papers/integration/omm_integ.tex
Removes a citation I can live without

@@
 burst generator') and a biomechanical eye, implemented using the
-biomechanical modelling framework OpenSim \citep{seth_opensim_2015}.
+biomechanical modelling framework OpenSim.
 These will be described below, but first we will give a description of
@@
 The biomechanical eye model, implemented using the OpenSim framework
-\citep{seth_opensim:_2011,seth_opensim_2015}, is anatomically represented by a sphere of
+\citep{seth_opensim:_2011}, is anatomically represented by a sphere of
 uniform mass distribution. The diameter of the eye is 24 mm for adults,

### 2017-09-04 papers/integration/body_text.tex
The body_text.tex file that I uploaded to the Frontiers web interface

--- 2017-09-01 papers/integration/omm_integ.tex
@@
-% While writing, don't stop for errors
-\nonstopmode
-
-% The Frontiers template.
-\documentclass{frontiersSCNS}
-
-\usepackage{url,hyperref,lineno,microtype}
-\usepackage[english]{babel}
-\usepackage{amsmath}
-\usepackage[onehalfspacing]{setspace}
-\usepackage{gensymb} % For \degree
-
-\linenumbers
-
-% Trick to define a language alias and permit language = {en} in the .bib file.
-% From: http://tex.stackexchange.com/questions/199254/babel-define-language-synonym
-\usepackage{letltxmacro}
-\LetLtxMacro{\ORIGselectlanguage}{\selectlanguage}
-\makeatletter
-\DeclareRobustCommand{\selectlanguage}[1]{%
-  \@ifundefined{alias@\string#1}
-    {\ORIGselectlanguage{#1}}
-    {\begingroup\edef\x{\endgroup
-       \noexpand\ORIGselectlanguage{\@nameuse{alias@#1}}}\x}%
-}
-\newcommand{\definelanguagealias}[2]{%
-  \@namedef{alias@#1}{#2}%
-}
-\makeatother
-\definelanguagealias{en}{english}
-\definelanguagealias{eng}{english}
-% End language alias trick
-
-\def\keyFont{\fontsize{8}{11}\helveticabold }
-\def\firstAuthorLast{James {et~al.}}
-\def\Authors{Sebastian James\,$^{1,2,*}$, Chris Papapavlou\,$^5$, Alexander Blenkinsop\,$^{1,2}$, \\
-  Alexander Cope\,$^3$,  \\
-  Sean Anderson\,$^{2,4}$, Konstantinos Moustakas\,$^5$, Kevin Gurney\,$^{1,2}$}
-% Affiliations should be keyed to the author's name with superscript
-% numbers and be listed as follows: Laboratory, Institute, Department,
-% Organization, City, State abbreviation (USA, Canada, Australia), and
-% Country (without detailed address information such as city zip codes
-% or street names).
-%
-% If one of the authors has a change of address, list the new address
-% below the correspondence details using a superscript symbol and use
-% the same symbol to indicate the author in the author list.
-\def\Address{\\
-$^{1}$Adaptive Behaviour Research Group, Department of Psychology,
-  The University of Sheffield, Sheffield, UK \\
-$^{2}$Insigneo Institute for in-silico Medicine,
-  The University of Sheffield, Sheffield, UK \\
-$^{3}$Department of Computer Science,
-  The University of Sheffield, Sheffield, UK \\
-$^{4}$Department of Automatic Control Systems Engineering,
-  The University of Sheffield, Sheffield, UK \\
-$^{5}$Department of Electrical and Computer Engineering,
-  The University of Patras, Patras, Greece \\
-}
-% The Corresponding Author should be marked with an asterisk. Provide
-% the exact contact address (this time including street name and city
-% zip code) and email of the corresponding author
-\def\corrAuthor{Kevin Gurney}
-\def\corrAddress{Department of Psychology, The University of Sheffield,
-  Western Bank, Sheffield, S10 2TP, UK}
-\def\corrEmail{k.gurney@sheffield.ac.uk}
-
-\begin{document}
-
-% A place for aliases:
-\input{sebcommands.tex}
-
-\onecolumn
-\firstpage{1}
-
-\title[Integrated brain and biomechanics]{
-Integrating brain and biomechanical models - a new paradigm
-for understanding  neuro-muscular control
-}
-
-\author[\firstAuthorLast ]{\Authors}
-\address{}
-\correspondance{}
-\extraAuth{} % If more than 1 corr. author refer to original template
-             % and fill this in
-%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%% The sections below are for reference only.
-%%%
-%%% For Original Research Articles, Clinical Trial Articles, and
-%%% Technology Reports the section headings should be those
-%%% appropriate for your field and the research itself. It is
-%%% recommended to organize your manuscript in the following sections
-%%% or their equivalents for your field:
-%%%
-%%% Abstract, Introduction, Material and Methods, Results, and Discussion.
-%%%
-%%% Please note that the Material and Methods section can be placed in
-%%% any of the following ways: before Results, before Discussion or
-%%% after Discussion.
-%%%
-%%% For information about Clinical Trial Registration, please go to
-%%% http://www.frontiersin.org/about/AuthorGuidelines#ClinicalTrialRegistration
-%%%
-%%% For Clinical Case Studies the following sections are mandatory:
-%%% Abstract, Introduction, Background, Discussion, and Concluding
-%%% Remarks.
-%%%
-%%% For all other article types there are no mandatory sections.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\maketitle
-\begin{abstract}
-
-\section{}
-To date, realistic models of how the central nervous system governs
-behaviour have been restricted in scope to the brain, brainstem or
-spinal column, as if these existed as disembodied organs.
-Further, the model is often exercised in relation to an in vivo
-physiological experiment with input comprising an impulse, a periodic
-signal or constant activation, and output as a pattern of neural
-activity in one or more neural populations. Any link to behaviour is
-inferred only indirectly via these activity patterns.
-%
-We argue that to discover the principles of operation of neural
-systems, it is necessary to express their behaviour in terms of
-physical movements of a realistic motor system, and to supply inputs
-that mimic sensory experience. To do this with confidence, we must
-connect our brain models to neuro-muscular models and provide relevant
-visual and proprioceptive feedback signals, thereby closing the loop
-of the simulation.
-%
-This paper describes an effort to develop just such an integrated
-brain and biomechanical system using a number of pre-existing
-models. It describes a model of the saccadic oculomotor system
-incorporating a neuromuscular model of the eye and its six extraocular
-muscles. The position of the eye determines how illumination of a
-retinotopic input population projects information about the location
-of a saccade target into the system.
-%
-A pre-existing saccadic burst generator model was incorporated into
-the system, which generated motoneuron activity patterns suitable for
-driving the biomechanical eye. The model was demonstrated to make
-accurate saccades to a target luminance under a set of environmental
-constraints.
-%
-Challenges encountered in the development of this model showed the
-importance of this integrated modelling approach. Thus, we exposed
-shortcomings in individual model components which were only apparent
-when these were supplied with the more plausible inputs available in a
-closed loop design. Consequently we were able to suggest missing
-functionality which the system would require to reproduce more
-realistic behaviour.
-%
-The construction of such closed-loop animal models constitutes a new
-paradigm of \e{computational neurobehaviour} and promises a more
-thoroughgoing approach to our understanding of the brain's function as
-a controller for movement and behaviour.
-
-\tiny
- \keyFont{
-   \section{Keywords:}
-   integrated brain biomechanics neuromuscular oculomotor saccade basal ganglia
- } % 5 to 8 keywords
-\end{abstract}
-
 \section{Introduction}
 
-% New introduction, tailored to the paradigm shift title.
-
-% Background
 The field of computational neuroscience has provided
@@
 neurons is taken to be representative of a behavioural outcome.
-% Sometimes, ok to just have a brain model
 In some cases, it \e{is} reasonable to take the activity of an internal
@@
 
-% Gap
 However,
@@
 \cite{james_target-distractor_2017}.
-%
-% Solution
 A model which
@@
 
-% Existing models don't control movement unless they control either a mechanical
-% or virtual body.
-% Can't observe how learning in the model may effect it's evolution in time
-% We may miss features about the system
-% Brains exist to move muscles
-
-% Solution, build an integrated model. Also give background on OMM system here.
-
-%% End of intro here? Or carry on with a description of the physiology
-%% of saccadic eye movements?
-
-% Solution described means we now need to do background of eye movements:
 In an attempt to build a model combining brain, realistic
@@
 in the field of view.
-%
 The oculomotor system is an excellent candidate for modelling because
@@
 making it one of the simplest neuro-muscular system in the body.
-%
 It is nevertheless behaviourally
@@
 \citep{schiller_effect_1987,edelman_activity_1996}.
-%
 Information from the retina is also processed by visual cortex which
@@
 \citep{stanton_frontal_1988}.
-%
 Although both cortical and subcortical paths produce a saccade
@@
 
-% A very short introduction to the section.
 The integrated brain and biomechanical model described here is a
@@
 
-% Section - description of how the model fits together - which
-% components it's made from.
 \subsection{Model development framework}
 
-% Say the \ccg~model was implemented in matlab-brahms & this one is SpineML.
 The \ccg~model was originally developed to run on the BRAHMS model
@@
 activation and shunting connections.
-%
-% That's the components described. Next up is to have a figure of the
-% activity for representative input to the model.
-%
 
@@
 response---\cite{robinson_eye_1972}].
-% Ottes et al. fit to stimulus-to-movement data, and give a
-% movement-to-collicular-coordinate mapping in the paper.
 We used the following statement of this mapping to introduce stimuli
@@
 
-% Section - description of new brainstem model
 \subsection{Brainstem model}
@@
 
-% Section - description of biomechanical model
 \subsection{biomechanical eye}
 
-% Possibly introductory paragraph here.
 The output signals of the brainstem are used to drive the biomechanical model.
@@
 
-% EYE MODEL DESCRIPTION HERE
 The biomechanical eye model, implemented using the OpenSim framework
@@
 
-%EOM dynamics
 The force applied by EOMs is controlled by an excitatory signal
@@
 
-%Orbital fat force
 Passive forces due to the fatty tissues inside the eye orbit also
@@
 
-% Section - description of the integration. scientific and
-% technical. Already
 \subsection{Integrating the models and closing the loop}
@@
 
-% Brain to SBG, seeing as that's how I explained it above.
 A number of studies have considered the form of the connection between
@@
 follow this idea.
-% Words along the lines of:
 Arai and co-workers trained a 20x20 neural network model of the
@@
 2D Gaussian activation profiles~\citep{arai_two-dimensional_1994}.
-%
 The training approach of \cite{arai_two-dimensional_1994} was not feasible in this study
@@
 in order to generate output statistics.
-%
 \cite{tabareau_geometry_2007} wrote down a theoretical form of the weight
@@
 it as the means to generate the six weight maps in our own model.
-%
 One barrier to the use of the weight map
@@
 was 0.3, $M^0$ was 12.43 and $r_0$ was 20.
-% Could have a figure here, made from widening_gaussian.m
 
@@
 training process
-% possibly descibe this training process in supplemental data
 which depended on a
@@
 in the brain model, resetting them ready for the next saccade.
-% Might have to justify the above a bit more.
-
-% SBG to worldDataMaker
+
 The output signals from the six channels of the SBG were connected to
@@
 
-% worldDataMaker to brain, but Re-work:
 The eye model outputs its rotational state at each
@@
 \section{Results}
-
-% trajectories, neuron activations (esp. brainstem). latency vs
-% dopamine, latency vs gap.
-%
-% The importance of an even sized hill of activity in SC_deep. The
-% difficulties of achieving this.
 
@@
 as described earlier) are shown in Fig.~\ref{weightmaps}.
-% From map_modelling2.m:
-%    yh=0.0016*exp(0.067.*x);
-%    yv=0.00195*exp(0.075.*x);
 
@@
 programmed saccade magnitude.
-% Mention \cite{thurat_biomimetic_2015} in discussion.
 The $x$ component error map in Fig.~\ref{errorsurfaceTM3}(b)
@@
 dependence, at least in the burst layer~\citep{anderson_two-dimensional_1998}.
-% Nice ref that - see Fig 16
 
@@
 in the world frame of reference.
-
-% These errors are larger than those in Thurat due to the hill of
-% activity not being `perfect' Discussion point.
 
@@
 by this modification.
-%
-% This doesn't account for *all* cases where you'd want to remove the TN
-% activity. Imagine a saccade purely UP then a saccade to a location
-% purely RIGHT. You'd need to remove the TN activity on the UP channel,
-% but you'd not be inducing any DOWN with the new target.
 
@@
 a `staircase' presentation.
-%If the more distal stimulus preceded the 15\dg~stimulus (again with
-%both in the same hemifield), this was called `pulse undershoot'.
 We carried
@@
 
-%\subsection{Saccade with distractor} enough!
-
-%Our integrated model allows us to examine the effect of distractor
-%luminances on saccade dynamics. Fig.~\ref{targ_w_distr}(a) shows
-%three horizontal saccades to a
-%target at $\theta_{y}=$-10\dg. The first saccade (blue
-%trajectory) had no distractor luminance, the second saccade (red) was
-%modulated by the appearance of a distractor cross of magnitude 1
-%located at $\theta_{x}=\,$-7\dg, $\theta_{y}=\,$-7\dg.
-%The distractor appeared 0.1~s after the target and
-%persisted for 0.1~s [Fig.~\ref{targ_w_distr}(b)]. The third
-%saccade (green) had conditions identical to the red saccade, but
-%with a brighter distractor luminance, whose magnitude was 2.
-
-%\cmnt{Ok, now saccades can deviate TOWARDS a distractor - particularly
-%if the distractor is closer to the trajectory - see for example
-%~\cite{wang_distractor_2014}. This model doesn't seem to have any
-%mechanism to induce a deviation of trajectory away from the distractor. }
-
-%\subsection{Saccade to twin targets} enough!
-
 \section{Discussion}
@@
 
-% This is probably recapitulation of intro material.
 We chose the oculomotor model as a basis for this study because it has
@@
 robotics.
-
-% Frontiers requires figures to be submitted individually, in the same
-% order as they are referred to in the manuscript. Figures will then
-% be automatically embedded at the bottom of the submitted
-% manuscript. Kindly ensure that each table and figure is mentioned in
-% the text and in numerical order. Permission must be obtained for use
-% of copyrighted material from other sources (including the
-% web). Please note that it is compulsory to follow figure
-% instructions. Figures which are not according to the guidelines will
-% cause substantial delay during the production process.
-
-% To take part in the Resource Identification Initiative, please cite
-% antibodies, genetically modified organisms, software tools, data,
-% databases and services using the corresponding catalog number and
-% RRID in your current manuscript. For more information about the
-% project and for steps on how to search for an RRID, please click
-% \href{http://www.frontiersin.org/files/pdf/letter_to_author.pdf}.
-
-\section*{Disclosure/Conflict-of-Interest Statement}
-
-The authors declare that the research was conducted in the absence of
-any commercial or financial relationships that could be construed as a
-potential conflict of interest.
-
-\section*{Author Contributions}
-%When determining authorship the following criteria should be observed:
-%•	Substantial contributions to the conception or design of the work; or the acquisition, analysis, or interpretation of data for the work; AND
-%•	Drafting the work or revising it critically for important intellectual content; AND
-%•	Final approval of the version to be published ; AND
-%•	Agreement to be accountable for all aspects of the work in ensuring that questions related to the accuracy or integrity of any part of the work are appropriately investigated and resolved.
-%Contributors who meet fewer than all 4 of the above criteria for authorship should not be listed as authors, but they should be acknowledged. (http://www.icmje.org/roles_a.html)
-
-SJ, AB and AC implemented existing parts of the model in SpineML. AB
-developed the saccade generator brainstem model. SJ performed the
-technical and scientific integration of the biomechanical eye.  CP and
-KM developed the biomechanical eye model. SJ wrote the manuscript; SA,
-AB, KG and KM contributed to the manuscript. KG conceived the
-project.
-
-\section*{Acknowledgements}
-
-\textit{Funding\textcolon} European Union FP7 Grant 610391 `NoTremor'.
-
-\section*{Supplemental Data}
-
-The model specification, results and all code required to reproduce
-the results of this work are available
-at: https://github.com/ABRG-Models/OMM\_NeuroMuscular
-
-\selectlanguage{English}
-\bibliographystyle{frontiersinSCNS_ENG_HUMS}
-% The bibliography NoTremor.bib is the one exported from Zotero.
-\bibliography{NoTremor}
-
-%%% Upload the *bib file along with the *tex file and PDF on
-%%% submission if the bibliography is not in the main *tex file
-
-\section*{Figures}
-
-%%% Use this if adding the figures directly in the mansucript, if so,
-%%% please remember to also upload the files when submitting your
-%%% article There is no need for adding the file termination, as long
-%%% as you indicate where the file is saved. In the examples below the
-%%% files (logo1.jpg and logo2.eps) are in the Frontiers LaTeX folder
-%%% If using *.tif files convert them to .jpg or .png
-
-%\begin{figure}[h!]
-%\begin{center}
-%\includegraphics[width=10cm]{logo1.jpg}% This is a *.jpg file
-%\end{center}
-% \textbf{\refstepcounter{figure}\label{01} Figure \arabic{figure}.}{ Enter the caption for your figure here.  Repeat as  necessary for each of your figures }
-%\end{figure}
-
-%\begin{figure}
-%\begin{center}
-%\includegraphics[width=10cm]{logo2}% This is an *.eps file
-%\end{center}
-%\textbf{\refstepcounter{figure}\label{02} Figure \arabic{figure}.}{ Enter the caption for your figure here.  Repeat as  necessary for each of your figures }
-%\end{figure}
-
-%%% If you don't add the figures in the LaTeX files, please upload
-%%% them when submitting the article.
-
-%%% Frontiers will add the figures at the end of the provisional pdf
-%%% automatically
-
-%%% The use of LaTeX coding to draw Diagrams/Figures/Structures should
-%%% be avoided. They should be external callouts including graphics.
-
-%\begin{figure}[htb!]
-%\begin{center}
-%\includegraphics[width=0.9\textwidth]{./figures/intro_graphic.png}
-%\end{center}
-%\textbf{\refstepcounter{figure}\label{intro_graphic} Figure \arabic{figure}.}
-%{ \textbf{intro\_graphic} An isolated brain model. Crafted inputs
-%are introduced into one of the model's n state variables. The output
-%of another of the state variables implies behavioural change or
-%onset.}
-%\end{figure}
-
-\begin{figure}[htb!]
-\begin{center}
-\includegraphics[width=0.9\textwidth]{./figures/model_framework.png}
-\end{center}
-\textbf{\refstepcounter{figure}\label{model_framework} Figure \arabic{figure}.}
-{ The model framework. The model is specified using a combination of
-declarative XML files and hand-coded C++. These original model
-specifications are shown within the blue box. b) The green box shows
-the processes which are applied to the model specification to produce
-the BRAHMS system. Most of the process is defined within the scripts
-which make up \stob, but the hand-written components must be
-manually compiled and installed within the BRAHMS Namespace, allowing
-the BRAHMS executable to locate them at runtime. c) The red box shows
-the resulting BRAHMS system ready to be executed by the BRAHMS
-executable. In practice, this call is made by \stob.}
-\end{figure}
-
-\begin{figure}[htb!]
-\begin{center}
-\includegraphics[width=0.9\textwidth]{./figures/Brain_Model.png}
-\end{center}
-\textbf{\refstepcounter{figure}\label{brain_model} Figure \arabic{figure}.}
-{ The brain model. This is the SpineCreator
-`network layer' view of the model. Each box represents a neural
-population with 2500 elements, arranged in a 50$\times$50 grid. The
-SpineML component name is printed on the bottom right corner of each
-population box and the population name is at the top. The overall
-connectivity between populations is represented by the projection
-arrows with the colour indicating the connectivity scheme (one-to-one
-connections are red, Gaussian kernel connections are dark blue and so
-on). Excitatory connections have arrowheads and inhibitory connections
-have circles, although for details of the behaviour of the
-connections, the weight-update and post-synapse components must be
-studied. Briefly, the model comprises a \e{World} population, into
-which a retinotopically organised view of the world is
-introduced. This information is passed into cortical populations (FEF)
-and subcortical populations (SC) via a simple model of the
-retina. These feed a cortico-thalamo-basal ganglia loop, which selects
-which region of the deep layer of superior colliculus should be
-disinhibited, allowing activity to build up therein. The five
-populations comprising the basal ganglia are enclosed in a grey
-outline. Note that substantia nigra pars compacta is not modelled
-here, instead the level of dopamine in the striatum is set via a
-parameter in the Str\_D1 and Str\_D2 populations}
-\end{figure}
-
-\begin{figure}[htb!]
-\begin{center}
-\includegraphics[width=0.9\textwidth]{./figures/mapping.png}
-\end{center}
-\textbf{\refstepcounter{figure}\label{fig:mapping} Figure \arabic{figure}.}
-{ Representative mapping from eye's frame of
-reference in Cartesian co-ordinates to retinotopic co-ordinates. (a) The
-mapping of luminances in the eye's frame of reference. The world input
-is pre-defined by a JSON configuration file. Luminance position, size
-and shape can be defined in this file, along with the times at which
-luminances appear and disappear. The worldDataMaker.cpp code computes
-the locations of the luminances in the eye's frame of reference, given
-its rotational state. It also computes a 2D Gaussian convolution of
-the luminances. Here, there are two cross shaped luminances spanning
-10\dg, one of value 0.8 at the fixation point (0,0) and one of
-value 0.5 at a peripheral position (0,-12\dg). Note that these
-crosses have the same `bar width' of 2\dg~as the crosses
-used in the simulations, but their span of 10\dg~is greater
-than the 6\dg~used in the simulations, to make these
-images clearer. (b) The locations of
-the luminances in the eye's frame of reference are then converted into
-retinotopic co-ordinates, with centrally located luminances being
-represented at low values of $r$ and more peripheral luminances having
-higher values of $r$. $\phi$ encodes rotational angle: 1 and 50 encode
-upward movement; 13 is left; 25 is down; 37 is right. The output of
-the World component is fed into FEF\_add\_noise and into the retinal
-neuron populations. The colour map makes it possible to distinguish
-between the two crosses. (c) The FEF\_add\_noise populations adds a level
-of noise to the signal representing processing of the signal in visual
-cortex. (d) A Gaussian projection from FEF\_add\_noise to FEF further
-blurs the activity in FEF. FEF is the input to the basal ganglia and
-one input to superior colliculus.}
-\end{figure}
-
-\begin{figure}[htb!]
-\begin{center}
-\includegraphics[width=0.5\textwidth]{./figures/Brain_Stem_1channel.png}
-\end{center}
-\textbf{\refstepcounter{figure}\label{sbg} Figure \arabic{figure}.}
-{ One pair of channels of the saccadic burst
-generator (SBG) for left (cyan) or right (green) movements. Collicular
-activity in SC\_avg excites the channels via SBG weight maps. Each box
-represents a neural population and shows the population name, the
-number of neural elements (here 2500 or 1) and the SpineML component
-name; \e{LIN} for Leaky integrator or \e{integrator}. Key: LLBN:
-Long lead burst neurons; IBN: Inhibitory burst neurons; OPN: Omnipause
-neurons; EBN: Excitatory burst neurons; TN: Tonic neurons; MN:
-Motoneurons.}
-\end{figure}
-
-\begin{figure}[htb!]
-\begin{center}
-\includegraphics[width=0.5\textwidth]{./figures/SC_to_brainstem.png}
-\end{center}
-\textbf{\refstepcounter{figure}\label{scdeep} Figure \arabic{figure}.}
-{ Showing the additional deep layer of superior colliculus
-(SC\_deep2) and the output layer (SC\_avg, named for the fact that in an earlier
-version of the model, it received the output of the centroid of SC\_deep).
-The widening Gaussian projection is shown as the arrow between SC\_deep
-and SC\_deep2.}
-\end{figure}
-
-\begin{figure}[htb!]
-\begin{center}
-\includegraphics[width=0.8\textwidth]{./figures/sacc_vs_targetpos.png}
-\end{center}
-\textbf{\refstepcounter{figure}\label{sacc_vs_targ} Figure \arabic{figure}.}
-{ Accuracy at different target eccentricities for fixation luminance 0.2 and target luminance 0.3.}
-\end{figure}
-
-\begin{figure}[htb!]
-\begin{center}
-\includegraphics[width=\textwidth]{./figures/weightmaps.png}
-\end{center}
-\textbf{\refstepcounter{figure}\label{weightmaps} Figure \arabic{figure}.}
-{ Weight maps for the connections between the
-output layer of superior colliculus and the six long lead burst
-neurons of the saccadic burst generator model. Each map increases
-exponentially with increasing $r$, multiplied by cosine($\phi$) about
-its `active' axis. \cmnt{Check whether Left \& Right are wrong way round}}
-\end{figure}
-
-\begin{figure}[htb!]
-\begin{center}
-\includegraphics[width=0.95\textwidth]{./figures/errorsurface_TModel3.png}
-\end{center}
-\textbf{\refstepcounter{figure}\label{errorsurfaceTM3} Figure \arabic{figure}.}
-{ The end-point error surface for the original,
-na\"ive model (TModel3). a) The
-ratio of the magnitudes of the total error vector and the target
-vector, expressed as a percentage. b) The ratio of the magnitude
-of the $x$ component of the error vector to the magnitude of the
-target vector, expressed as a percentage. c) As (b) but for the
-$y$ component. d) As (b), for $z$ component. All colour maps are
-shown with the same scale. The target rotations, $\theta_{x}^t$ and
-$\theta_{y}^t$ are denoted `Target X' and `Target Y' in the figure.}
-\end{figure}
-
-\begin{figure}[htb!]
-\begin{center}
-\includegraphics[width=0.95\textwidth]{./figures/errorsurface.png}
-\end{center}
-\textbf{\refstepcounter{figure}\label{errorsurface} Figure \arabic{figure}.}
-{ The end-point error surface for the model
-in which a widening projection field was added to the model of the
-superior colliculus. a) The
-ratio of the magnitudes of the total error vector and the target
-vector, expressed as a percentage. b) The ratio of the magnitude
-of the $x$ component of the error vector to the magnitude of the
-target vector, expressed as a percentage. c) As (b) but for the
-$y$ component. d) As (b), for $z$ component. All colour maps are
-shown with the same scale. The target rotations, $\theta_{x}^t$ and
-$\theta_{y}^t$ are denoted `Target X' and `Target Y' in the figure.
-Note that the range of the colour scale is 0 to 20\%, a much smaller
-range than the range in Fig~\ref{errorsurfaceTM3}.}
-\end{figure}
-
-\begin{figure}[htb!]
-\begin{center}
-\includegraphics[width=0.8\textwidth]{./figures/outmany.png}
-\end{center}
-\textbf{\refstepcounter{figure}\label{outmany} Figure \arabic{figure}.}
-{ Representative single saccades. a) Trajectories
-from 9 saccades to a single target at 9 different locations. In each
-case, a fixation cross luminance of magnitude 0.2 was displayed at
-(0,0), the start position of the eye, until time 0.4~s. The target
-luminance, magnitude 0.3 was illuminated at time 0.4~s. Trajectory
-shape is dependent on the target position, and there is a variable
-amount of error in the end-points achieved by the model. Colour is
-used in this diagram as an aid to distinguishing different saccades
-and their targets; for a given saccade, the target location is given
-by the cross of the same colour closest to the end of the
-trajectory. b) The three rotational components of the `blue' saccade,
-to target location (-7,-7). c) The three rotational components of the
-`red' saccade, to target location (0,-10).}
-\end{figure}
-
-\begin{figure}[htb!]
-\begin{center}
-\includegraphics[width=0.8\textwidth]{./figures/lat_vs_everything.png}
-\end{center}
-\textbf{\refstepcounter{figure}\label{lat_vs_all} Figure \arabic{figure}.}
-{ Exploring saccade latencies. a) Latency to first
-movement as a function of target eccentricity for horizontal targets. b) Latency
-vs. eccentricity for vertical targets. c) Latency vs. gap at three different
-luminance values. d) The effect of the dopamine parameter on saccade latencies
-in gap, step and overlap conditions, for two different target luminances.
-e) Saccade vs. luminance showing gradual transition between reflexive and
-express behaviour.
-%f) Saccade duration vs. saccade eccentricity for horizontal
-%(rightwards), vertical (downwards) and 45\dg~oblique (down \& right) saccades.
-}
-\end{figure}
-
-\begin{figure}[htb!]
-\begin{center}
-\includegraphics[width=0.8\textwidth]{./figures/outrtn.png}
-\end{center}
-\textbf{\refstepcounter{figure}\label{outrtn} Figure \arabic{figure}.}
-{ There and back - a saccade to a target, followed by
-return to
-the original fixation. a) Out and return saccade to a target at (0,-10\dg)
-b) Rotational components of the saccade shown in (a). c) Outward and return
-trajectories for the saccade shown in (a) alongside saccades to three other
-targets.}
-\end{figure}
-
-\begin{figure}[htb!]
-\begin{center}
-\includegraphics[width=0.8\textwidth]{./figures/doublesteps.png}
-\end{center}
-\textbf{\refstepcounter{figure}\label{doublesteps} Figure \arabic{figure}.}
-{ Double steps. The effect of illuminating a first target
-at 8\dg~or 12\dg, followed by a second target at 12\dg~or 8\dg. a) Horizontal
-rotation of the eye plotted vs.~time for a saccade to the 12\dg~target only (red),
-and to an 8\dg~target at 0.4~s followed by a 12\dg~target after 30~ms (blue) or
-40~ms (black). The timings are indicated by vertical lines. When the second
-target is presented up to 30~ms after the initial target, the initial target
-has not had time to dominate the output saccade and a saccade to a location
-close to the second target is made. If the delay is 40~ms or more, the activity
-from the initial target has time to cause a built up of actiivty in SC\_deep
-and an initial saccade close to the first target is made, followed, after a
-longer than usual latency period, with a second saccade closer to the second
-target. In this graph, the mean of five separate simulations is plotted along
-with $\pm$1 standard deviation around the mean. b) The $\theta_{x}$/$\theta_{y}$
-trajectories corresponding to the data presented in (a).}
-\end{figure}
-
-%\begin{figure}[htb!]
-%\begin{center}
-%\includegraphics[width=0.8\textwidth]{./figures/targ_w_distr.png}
-%\end{center}
-%\textbf{\refstepcounter{figure}\label{targ_w_distr} Figure \arabic{figure}.}
-%{ \textbf{targ\_w\_distr} Effect of a distractor on single saccade.}
-%\end{figure}
-
-\end{document}

### 2017-09-04 papers/integration/omm_integ.tex
Incorporates my aliases into the manuscript
Re-justification of the TeX source, removal of extraneous comments and Frontiers class-file notes

@@
   Sean Anderson\,$^{2,4}$, Konstantinos Moustakas\,$^5$, Kevin Gurney\,$^{1,2}$}
-% Affiliations should be keyed to the author's name with superscript
-% numbers and be listed as follows: Laboratory, Institute, Department,
-% Organization, City, State abbreviation (USA, Canada, Australia), and
-% Country (without detailed address information such as city zip codes
-% or street names).
-%
-% If one of the authors has a change of address, list the new address
-% below the correspondence details using a superscript symbol and use
-% the same symbol to indicate the author in the author list.
+
 \def\Address{\\
@@
 }
-% The Corresponding Author should be marked with an asterisk. Provide
-% the exact contact address (this time including street name and city
-% zip code) and email of the corresponding author
+
 \def\corrAuthor{Kevin Gurney}
@@
 
-% A place for aliases:
-\input{sebcommands.tex}
+% Aliases
+\newcommand{\ccg}{Cope-Chambers-Prescott-Gurney}
+\newcommand{\stob}{SpineML\_2\_BRAHMS}
+% Emphasis and bold.
+\newcommand{\e}{\emph}
+\newcommand{\bol}{\textbf}
+\newcommand{\blue}{\textcolor{blue}}
+% I like my citations in blue
+\newcommand{\mycite}[1]{\blue{\cite{#1}}}
+% expon function is roman e
+\newcommand{\expon}{\mathrm{e}}
+% A font to indicate a branch of a github repository
+\newcommand{\branch}[1]{\textbf{\texttt{#1}}}
+\newcommand{\cmnt}[1]{\blue{#1}}
+\newcommand{\dg}{$\degree$}
 
@@
              % and fill this in
-%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%% The sections below are for reference only.
-%%%
-%%% For Original Research Articles, Clinical Trial Articles, and
-%%% Technology Reports the section headings should be those
-%%% appropriate for your field and the research itself. It is
-%%% recommended to organize your manuscript in the following sections
-%%% or their equivalents for your field:
-%%%
-%%% Abstract, Introduction, Material and Methods, Results, and Discussion.
-%%%
-%%% Please note that the Material and Methods section can be placed in
-%%% any of the following ways: before Results, before Discussion or
-%%% after Discussion.
-%%%
-%%% For information about Clinical Trial Registration, please go to
-%%% http://www.frontiersin.org/about/AuthorGuidelines#ClinicalTrialRegistration
-%%%
-%%% For Clinical Case Studies the following sections are mandatory:
-%%% Abstract, Introduction, Background, Discussion, and Concluding
-%%% Remarks.
-%%%
-%%% For all other article types there are no mandatory sections.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \maketitle
@@
 behaviour have been restricted in scope to the brain, brainstem or
-spinal column, as if these existed as disembodied organs.
-Further, the model is often exercised in relation to an in vivo
-physiological experiment with input comprising an impulse, a periodic
-signal or constant activation, and output as a pattern of neural
-activity in one or more neural populations. Any link to behaviour is
-inferred only indirectly via these activity patterns.
+spinal column, as if these existed as disembodied organs.  Further,
+the model is often exercised in relation to an in vivo physiological
+experiment with input comprising an impulse, a periodic signal or
+constant activation, and output as a pattern of neural activity in one
+or more neural populations. Any link to behaviour is inferred only
+indirectly via these activity patterns.
 %
@@
 
-% New introduction, tailored to the paradigm shift title.
-
 % Background
-The field of computational neuroscience has provided
-many \e{systems models} of the brain \citep{arai_two-dimensional_1994,gancarz_neural_1998,hazy_towards_2007,blenkinsop_frequency_2017}.
+The field of computational neuroscience has provided many \e{systems
+models} of the
+brain \citep{arai_two-dimensional_1994,gancarz_neural_1998,hazy_towards_2007,blenkinsop_frequency_2017}.
 We refer to these as \e{mechanistic computational models}, meaning
@@
 the brain. Whilst they differ in scale and complexity, these models
-all seek to
-describe the fundamental mechanisms behind common animal behaviours
-such as locomotion, threat evasion, reaching or feeding. However,
-none of the models cited here actually reproduce these
-behaviours. In each case, the activity in a certain population of
-neurons is taken to be representative of a behavioural outcome.
+all seek to describe the fundamental mechanisms behind common animal
+behaviours such as locomotion, threat evasion, reaching or
+feeding. However, none of the models cited here actually reproduce
+these behaviours. In each case, the activity in a certain population
+of neurons is taken to be representative of a behavioural outcome.
 % Sometimes, ok to just have a brain model
-In some cases, it \e{is} reasonable to take the activity of an internal
-population within the brain model as being representative of the
-induced behaviour. For example, a choice made in a \e{go/no-go} task
-could be determined from activity in a population within a basal
+In some cases, it \e{is} reasonable to take the activity of an
+internal population within the brain model as being representative of
+the induced behaviour. For example, a choice made in a \e{go/no-go}
+task could be determined from activity in a population within a basal
 ganglia model
@@
 maintenance of activity implies \e{no-go}. To validate the model, the
-error rates which it generates
-could be compared with experimentally determined error rates in
-primate subjects. We refer
-to this as an \e{output assumption model} because the output is assumed
-to signify behaviour. (An \e{input assumption model} assumes that sensory
+error rates which it generates could be compared with experimentally
+determined error rates in primate subjects. We refer to this as
+an \e{output assumption model} because the output is assumed to
+signify behaviour. (An \e{input assumption model} assumes that sensory
 input produces some particular form of neural activity in an input
@@
 % Gap
-However,
-we may be interested in reproducing accurate simulated \e{trajectories},
-in order to find out how degradation of parts of the model affect
-movement. In Parkinson's Disease, degradation of the
-dopamine neurons originating in the substantia nigra pars compacta (SNc)
-causes diskinesia \citep{galvan_pathophysiology_2008}, as well as
-abnormal network activity in
-the basal ganglia \citep{brown_dopamine_2001,mccarthy_striatal_2011}.
-Sufferers of the disease would be
-expected to produce abnormal decision-making \e{and} movement trajectories
-in a reach-to-the-correct-target task such as the one described in
+However, we may be interested in reproducing accurate
+simulated \e{trajectories}, in order to find out how degradation of
+parts of the model affect movement. In Parkinson's Disease,
+degradation of the dopamine neurons originating in the substantia
+nigra pars compacta (SNc) causes
+diskinesia \citep{galvan_pathophysiology_2008}, as well as abnormal
+network activity in the basal
+ganglia \citep{brown_dopamine_2001,mccarthy_striatal_2011}.  Sufferers
+of the disease would be expected to produce abnormal
+decision-making \e{and} movement trajectories in a
+reach-to-the-correct-target task such as the one described in
 \cite{james_target-distractor_2017}.
@@
 % Solution
-A model which
-sought to explore in detail the effects of the SNc degradation both on
-the decision making \e{and} on the movement dynamics would need a
-physically accurate virtual arm, as well as physically realistic sensory
-input for the brain. This is no less than a complete model of those sections
-of the brain and body which act to fulfil the task. Such a modelling
-effort, if successful, would result in a virtual robot capable of expressing
-behaviour \e{in response to sensory input from its environment}. This would
-represent a paradigm shift in the field of computational neuroscience
-worthy of the new name of \e{computational neurobehaviour}.
-
-% Existing models don't control movement unless they control either a mechanical
-% or virtual body.
-% Can't observe how learning in the model may effect it's evolution in time
-% We may miss features about the system
-% Brains exist to move muscles
-
-% Solution, build an integrated model. Also give background on OMM system here.
-
-%% End of intro here? Or carry on with a description of the physiology
-%% of saccadic eye movements?
+A model which sought to explore in detail the effects of the SNc
+degradation both on the decision making \e{and} on the movement
+dynamics would need a physically accurate virtual arm, as well as
+physically realistic sensory input for the brain. This is no less than
+a complete model of those sections of the brain and body which act to
+fulfil the task. Such a modelling effort, if successful, would result
+in a virtual robot capable of expressing behaviour \e{in response to
+sensory input from its environment}. This would represent a paradigm
+shift in the field of computational neuroscience worthy of the new
+name of \e{computational neurobehaviour}.
 
@@
 In an attempt to build a model combining brain, realistic
-biomechanics \e{and} sensory
-feedback, we sought to extend our previous work modelling the oculomotor system.
-The existing model \citep{cope_basal_2017} is already able to capture sensory input
-and convert it into a neural signal, assumed to specify the target of a
-\e{saccadic eye movement};
-a fast movement of the eyes which directs the fovea to a region of interest
-in the field of view.
+biomechanics \e{and} sensory feedback, we sought to extend our
+previous work modelling the oculomotor system.  The existing
+model \citep{cope_basal_2017} is already able to capture sensory input
+and convert it into a neural signal, assumed to specify the target of
+a \e{saccadic eye movement}; a fast movement of the eyes which directs
+the fovea to a region of interest in the field of view.
 %
@@
 %
-It is nevertheless behaviourally
-interesting, as saccadic eye movements reveal information about decision making at
-a subconscious level
+It is nevertheless behaviourally interesting, as saccadic eye
+movements reveal information about decision making at a subconscious
+level
 \citep{deubel_saccade_1996,reppert_modulation_2015,marcos_determining_2016}.
@@
 \citep{hepp_spatio-temporal_1983,dorris_neuronal_1997,mcpeek_competition_2003,vokoun_circuit_2011}.
-Furthermore, in the context
-of building \e{behaving} systems a
-necessary part of any model for which the behaviour requires visual attention
-and decision making is a realistic mechanism for gathering visual information.
-This is obvious from extrinsic considerations---a
-subject must look at a scene to make decisions or navigate within it. It
-also follows for \e{intrinsic} reasons. For example, \cite{howard_hand_1997}
-showed that visual cues affect reach trajectories and the same group later
-demonstrated that reaching affects the saccadic system
+Furthermore, in the context of building \e{behaving} systems a
+necessary part of any model for which the behaviour requires visual
+attention and decision making is a realistic mechanism for gathering
+visual information.  This is obvious from extrinsic considerations---a
+subject must look at a scene to make decisions or navigate within
+it. It also follows for \e{intrinsic} reasons. For
+example, \cite{howard_hand_1997} showed that visual cues affect reach
+trajectories and the same group later demonstrated that reaching
+affects the saccadic system
 \citep{tipper_reaching_2001} suggesting a close relationship between these
 neural systems. Building the simplest, behaving oculomotor system will
-therefore assist future computational neurobehavioural modelling efforts.
+therefore assist future computational neurobehavioural modelling
+efforts.
 
 Many neural populations are involved in the coding of saccadic eye
-movements, only a very brief overview is given here; for a
-review, see \cite{munoz_commentary:_2002}. One pathway takes
-information from the retina directly into the superficial layers of
-the superior colliculus in the brainstem
+movements, only a very brief overview is given here; for a review,
+see \cite{munoz_commentary:_2002}. One pathway takes information from
+the retina directly into the superficial layers of the superior
+colliculus in the brainstem
 \citep{sterling_receptive_1971,linden_massive_1983,wu_involvement_1994}.
-Activity within
-the superior colliculus then excites neurons in the pons, medulla and
-rostral mid-brain \citep{sparks_brainstem_2002} and then through
-channels to the motor neurons which innervate the extraocular muscles
+Activity within the superior colliculus then excites neurons in the
+pons, medulla and rostral mid-brain \citep{sparks_brainstem_2002} and
+then through channels to the motor neurons which innervate the
+extraocular muscles
 \citep{fuchs_firing_1970,sparks_brainstem_2002}. This direct pathway
@@
 %
-Although both cortical and subcortical paths produce a saccade
-target signal in the superior colliculus, it is also possible for
-animals to make relatively normal saccades even after the
-colliculus has been ablated
+Although both cortical and subcortical paths produce a saccade target
+signal in the superior colliculus, it is also possible for animals to
+make relatively normal saccades even after the colliculus has been
+ablated
 \citep{wurtz_activity_1972,aizawa_reversible_1998},
@@
 The `backup pathway' likely incorporates the oculomotor vermis and
-fastigial oculomotor region of the
-cerebellum which are known to participate in the specification, dynamics
-and adaptation of saccadic eye movements
-\citep{kleine_saccade-related_2003,takagi_effects_1998}.
-
-There is a long history of modelling the oculomotor system. For a comprehensive
-review, see \cite{girard_brainstem_2005}. Models of individual systems have been proposed for brainstem \citep{robinson_oculomotor_1975,scudder_new_1988,gancarz_neural_1998},
-cerebellum \citep{quaia_model_1999,dean_modelling_1995,dean_learning_1994} and
-superior colliculus
+fastigial oculomotor region of the cerebellum which are known to
+participate in the specification, dynamics and adaptation of saccadic
+eye movements \citep{kleine_saccade-related_2003,takagi_effects_1998}.
+
+There is a long history of modelling the oculomotor system. For a
+comprehensive review, see \cite{girard_brainstem_2005}. Models of
+individual systems have been proposed for brainstem
+\citep{robinson_oculomotor_1975,scudder_new_1988,gancarz_neural_1998},
+cerebellum \citep{quaia_model_1999,dean_modelling_1995,dean_learning_1994}
+and superior colliculus
 \citep{arai_two-dimensional_1994,moren_mechanism_2013,marino_spatial_2012}.
-More recently, combined models have also been
-developed incorporating sensory input \citep{cope_basal_2017} and driving simple
-physical plants representing the eye \citep{tabareau_geometry_2007,nguyen_saccade_2014,thurat_biomimetic_2015}.
-None of these models has yet fully closed the loop to produce a behaving system
-operating freely within its environment. We argue that developing
-integrated, closed-loop models of behaving systems offers insights into
-the operation of neural systems that are not available from
-input-~or output-assumption models.
+More recently, combined models have also been developed incorporating
+sensory input \citep{cope_basal_2017} and driving simple physical
+plants representing the eye
+\citep{tabareau_geometry_2007,nguyen_saccade_2014,thurat_biomimetic_2015}.
+None of these models has yet fully closed the loop to produce a
+behaving system operating freely within its environment. We argue that
+developing integrated, closed-loop models of behaving systems offers
+insights into the operation of neural systems that are not available
+from input-~or output-assumption models.
 
@@
 layers of superior colliculus was assumed to accurately encode the
-location of the eye at the end of the
-saccade \citep{wurtz_activity_1972,robinson_eye_1972,van_gisbergen_collicular_1987,mcilwain_lateral_1982}.
-This location was used to recalculate the positions of the luminances in
-the eye's frame of reference at each time step. The model included no
-brainstem populations other than superior colliculus, nor a
+location of the eye at the end of the saccade
+\citep{wurtz_activity_1972,robinson_eye_1972,van_gisbergen_collicular_1987,mcilwain_lateral_1982}.
+This location was used to recalculate the positions of the luminances
+in the eye's frame of reference at each time step. The model included
+no brainstem populations other than superior colliculus, nor a
 neuromuscular model.
 
-To summarize, the \ccg~model takes as \e{input} the positions
-of luminances on a topographic map and produces as output a saccade
+To summarize, the \ccg~model takes as \e{input} the positions of
+luminances on a topographic map and produces as output a saccade
 target.
@@
 burst generator') and a biomechanical eye, implemented using the
-biomechanical modelling framework OpenSim.
-These will be described below, but first we will give a description of
-the co-ordinate systems and the modelling framework used.
+biomechanical modelling framework OpenSim.  These will be described
+below, but first we will give a description of the co-ordinate systems
+and the modelling framework used.
 
@@
 
-Before describing the biomechanical eye and the brain model, which consisted
-of retinotopically mapped neural sheets, we describe the co-ordinate system
-used in the world. The eye was located at the origin of a three-dimensional, right-handed
-Cartesian co-ordinate system, with its fovea directed in the $-z$ direction.
-There was a notional spherical screen which was also centred at the origin of the
-co-ordinate system and had a radius of 50 (in arbitrary units). The \e{fixation
-point} was the point on the
-screen at which the eye was initially directed.
-Onto the screen were projected target luminances, each of which having a position
-described by two co-ordinates; $\theta_{x}^{t}$, a
-rotation of the horizon plane about the $x$ axis, and $\theta_{y}^{t}$, a rotation
-of the meridian plane about the $y$ axis. The position is the intersection
-of these rotated planes with the spherical screen (disregarding
-the intersection point of these three surfaces behind the eye).
-%
-Note that a luminance with positive $\theta_{x}^{t}$ was above the horizon of this world;
-one whose $\theta_{y}^{t}$ was positive lay to the left of the world's meridian. For this
-reason, many of the figures in this paper are plotted with $-\theta_{y}$ on the
-$x$-axis and $\theta_{x}$ on the $y$-axis so that targets that lay up and to the right
-in the world do so in the graphs, also.
-
-Luminances were crosses of height and width subtending $\pm$3\dg~and whose
-`bars' were 2\dg~thick. Luminances were oriented like $+$ symbols with
-their vertical bar aligned with the meridian plane and their horizontal bar
-aligned with the horizon.
-
-The eye's frame of reference was initially aligned with the world's frame
-of reference.
-At each timestep, the eye's rotational state (described by the Euler
-rotations $\theta_x$, $\theta_y$, $\theta_z$) was
-used to translate the three dimensional
-Cartesian co-ordinates of the luminances in the world frame into co-ordinates
-in the eye frame. The luminance co-ordinates in the eye's frame of reference
-were used to determine the input to the brain model.
-
-% Section - description of how the model fits together - which
-% components it's made from.
+Before describing the biomechanical eye and the brain model, which
+consisted of retinotopically mapped neural sheets, we describe the
+co-ordinate system used in the world. The eye was located at the
+origin of a three-dimensional, right-handed Cartesian co-ordinate
+system, with its fovea directed in the $-z$ direction.  There was a
+notional spherical screen which was also centred at the origin of the
+co-ordinate system and had a radius of 50 (in arbitrary
+units). The \e{fixation point} was the point on the screen at which
+the eye was initially directed.  Onto the screen were projected target
+luminances, each of which having a position described by two
+co-ordinates; $\theta_{x}^{t}$, a rotation of the horizon plane about
+the $x$ axis, and $\theta_{y}^{t}$, a rotation of the meridian plane
+about the $y$ axis. The position is the intersection of these rotated
+planes with the spherical screen (disregarding the intersection point
+of these three surfaces behind the eye).
+%
+Note that a luminance with positive $\theta_{x}^{t}$ was above the
+horizon of this world; one whose $\theta_{y}^{t}$ was positive lay to
+the left of the world's meridian. For this reason, many of the figures
+in this paper are plotted with $-\theta_{y}$ on the $x$-axis and
+$\theta_{x}$ on the $y$-axis so that targets that lay up and to the
+right in the world do so in the graphs, also.
+
+Luminances were crosses of height and width subtending $\pm$3\dg~and
+whose `bars' were 2\dg~thick. Luminances were oriented like $+$
+symbols with their vertical bar aligned with the meridian plane and
+their horizontal bar aligned with the horizon.
+
+The eye's frame of reference was initially aligned with the world's
+frame of reference.  At each timestep, the eye's rotational state
+(described by the Euler rotations $\theta_x$, $\theta_y$, $\theta_z$)
+was used to translate the three dimensional Cartesian co-ordinates of
+the luminances in the world frame into co-ordinates in the eye
+frame. The luminance co-ordinates in the eye's frame of reference were
+used to determine the input to the brain model.
+
 \subsection{Model development framework}
 
-% Say the \ccg~model was implemented in matlab-brahms & this one is SpineML.
 The \ccg~model was originally developed to run on the BRAHMS model
@@
 In the current work, the \ccg~model was reproduced using the
-declarative SpineML markup language \citep{alex_cope_spineml_2014,richmond_model_2014},
-with the help of the graphical SpineML model editing software
-called SpineCreator
+declarative SpineML markup
+language \citep{alex_cope_spineml_2014,richmond_model_2014}, with the
+help of the graphical SpineML model editing software called
+SpineCreator
 \citep{cope_spinecreator_2015,cope_spinecreator:_2016}. SpineML,
@@
 updates. A description of SpineML is given
-in \cite{richmond_model_2014}; the definitive definition is found
-in the schemas \citep{cope_spineml_2014}.
-SpineCreator, in its r\^ole as a graphical editor for the SpineML
-format, was used to generate the SpineML files describing the
-model. It was also used to generate the diagrams of the model.
+in \cite{richmond_model_2014}; the definitive definition is found in
+the schemas \citep{cope_spineml_2014}.  SpineCreator, in its r\^ole as
+a graphical editor for the SpineML format, was used to generate the
+SpineML files describing the model. It was also used to generate the
+diagrams of the model.
 
 As a declarative format for model specification, SpineML is agnostic
-about how the model is executed. A number of simulation
-engines can be utilised, including DAMSON \citep{richmond_damson_2015}, GeNN
+about how the model is executed. A number of simulation engines can be
+utilised, including DAMSON \citep{richmond_damson_2015}, GeNN
 \citep{nowotny_flexible_2011,nowotny_spineml_2014} and BRAHMS (used
@@
 these BRAHMS components were hand-written in C++. To incorporate these
-components into the SpineML model, a \stob~\e{external.xsl} file was used.
-The external.xsl file scheme for incorporating external BRAHMS components
-into a SpineML model was a new \stob~feature motivated by the current work.
-Fig.~\ref{model_framework} shows the workflow, in which the
-model specification files (blue box - a combination of SpineML files
-and C++ code), are processed (green box) into a BRAHMS system (red
-box).
+components into the SpineML model, a \stob~\e{external.xsl} file was
+used.  The external.xsl file scheme for incorporating external BRAHMS
+components into a SpineML model was a new \stob~feature motivated by
+the current work.  Fig.~\ref{model_framework} shows the workflow, in
+which the model specification files (blue box - a combination of
+SpineML files and C++ code), are processed (green box) into a BRAHMS
+system (red box).
 
@@
 retinotopic co-ordinate system, roughly matching the known layout of
-the superior colliculus \citep{robinson_eye_1972}. % FIXME: and frontal eye field?
+the superior colliculus \citep{robinson_eye_1972}.
+% and frontal eye field?
 
@@
 function. At this point, the naming scheme for the component becomes
-apparent; this is a Leaky Integrator with a piecewise-linear transfer function.
-
-The LINret component used for the retinal populations is similar
-to the LINlinear component, but with no intrinsic noise and no
-shunting inhibitory input. It has a neural input which is identical to
-the activation input $A$:
+apparent; this is a Leaky Integrator with a piecewise-linear transfer
+function.
+
+The LINret component used for the retinal populations is similar to
+the LINlinear component, but with no intrinsic noise and no shunting
+inhibitory input. It has a neural input which is identical to the
+activation input $A$:
 \begin{equation}
@@
 \end{equation}
-This component is used in the subthalamic nucleus (STN) population, as it gives a more
-physiologically accurate f-I
-behaviour \citep{wilson_model_2004,bevan_mechanisms_1999,hallworth_apamin-sensitive_2003}
+This component is used in the subthalamic nucleus (STN) population, as
+it gives a more physiologically accurate f-I
+behaviour
+\citep{wilson_model_2004,bevan_mechanisms_1999,hallworth_apamin-sensitive_2003}
 which has been shown to allow the mapping of the basal ganglia network
@@
 LINlinear. They differ in that they have no shunting inhibition. They
-are used in to model medium spiny neuron (MSN) populations in
-the striatum. As they model
-the fact that most MSN neurons fall into two groups; those expressing D1
-dopamine receptors and those expressing D2 receptors, they have a
-dopamine parameter that modulates the input activation, so
-that their equations for $a_{in}$ are thus:
+are used in to model medium spiny neuron (MSN) populations in the
+striatum. As they model the fact that most MSN neurons fall into two
+groups; those expressing D1 dopamine receptors and those expressing D2
+receptors, they have a dopamine parameter that modulates the input
+activation, so that their equations for $a_{in}$ are thus:
 \begin{equation}
@@
 where $d$ is the dopamine parameter. Varying dopamine from 0 to 1
-enhances the activation in the D1 model, whereas it decreases
-the activation of the D2 model elements, in line with experimental
+enhances the activation in the D1 model, whereas it decreases the
+activation of the D2 model elements, in line with experimental
 observations \citep{harsing_influence_1997,gonon_prolonged_1997}.
-Note that the equation for $a_{in}^{D1}$
-differs from that used in the \ccg~model, for which the
-cortico-striatal weights are multiplied by $(1+d)$ rather than
-$(0.2+d)$.
+Note that the equation for $a_{in}^{D1}$ differs from that used in
+the \ccg~model, for which the cortico-striatal weights are multiplied
+by $(1+d)$ rather than $(0.2+d)$.
 
@@
 population. The value of the activation $A$ (and where relevant, the
-shunting input, $S$) is determined by summing the weighted
-inputs to the population:
+shunting input, $S$) is determined by summing the weighted inputs to
+the population:
 \begin{equation}
@@
 \end{equation}
-$w_i^{act}$ and $w_i^{sh}$ are, respectively, the weights
-of the $i^{th}$ activation or shunting connection; $x_i^{act}$
-and $x_i^{sh}$ are the signals input to the
-activation and shunting connections.
-%
-% That's the components described. Next up is to have a figure of the
-% activity for representative input to the model.
-%
+$w_i^{act}$ and $w_i^{sh}$ are, respectively, the weights of the
+$i^{th}$ activation or shunting connection; $x_i^{act}$ and $x_i^{sh}$
+are the signals input to the activation and shunting connections.
 
@@
 Each population of 2500 neural elements was arranged in a 50 by 50
-grid, with positions on the grid representing a retinotopic
-mapping similar to that found empirically both in the superior
+grid, with positions on the grid representing a retinotopic mapping
+similar to that found empirically both in the superior
 colliculus \citep{ottes_visuomotor_1986} and in visual cortex
-\citep{eric_l._schwartz_computational_1980} and assumed in
-this work to persist throughout the oculomotor system.
-
-In a retinotopic mapping, the Cartesian co-ordinates of the light-sensitive
-cells in the retina, whose density varies with distance from the fovea,
-are transformed into the Cartesian co-ordinates of
-the correspondingly active cells on the colliculus. The mapping ensures
-that an even density of cells can be maintained in the colliculus, but
-ensures that a group of adjoining, active, retinal neurons will
-always activate an adjoining group of neurons on the collicular
-surface.
+\citep{eric_l._schwartz_computational_1980}
+and assumed in this work to persist throughout the oculomotor system.
+
+In a retinotopic mapping, the Cartesian co-ordinates of the
+light-sensitive cells in the retina, whose density varies with
+distance from the fovea, are transformed into the Cartesian
+co-ordinates of the correspondingly active cells on the
+colliculus. The mapping ensures that an even density of cells can be
+maintained in the colliculus, but ensures that a group of adjoining,
+active, retinal neurons will always activate an adjoining group of
+neurons on the collicular surface.
 
 The mapping turns out to resemble polar co-ordinates. That is, one
-axis of the collicular surface specifies the eccentricity of
-a retinal location (how far it is from the fovea) and the second axis
-specifies the rotational angle of the retinal location; we therefore
-use the convention of referring to the eccentricity axis on the
-colliculus as $r$ and the rotation axis as $\phi$.
+axis of the collicular surface specifies the eccentricity of a retinal
+location (how far it is from the fovea) and the second axis specifies
+the rotational angle of the retinal location; we therefore use the
+convention of referring to the eccentricity axis on the colliculus as
+$r$ and the rotation axis as $\phi$.
 
 The \e{cortical magnification factor}, $M(r)$, gives the relationship
-between the
-radial eccentricity $r$ and the retinal neural density. As in
+between the radial eccentricity $r$ and the retinal neural density. As
+in
 \cite{cope_basal_2017}, we use a first-order approximation of the form
@@
 \end{equation}
-The foveal magnification, $M_f$, is the magnification of the most central
-region of the retina and has a value in the human of about
-7.8 mm/\dg~\citep{rovamo_estimation_1979}.
-
-In our model, $M_f$ is related to $W_{nfs}$, the width of the retinotopic neural
-field, $W_{fov}$, the width of the eye's field of view and $E_2$, the
-eccentricity at which the retinal density has halved by:
+The foveal magnification, $M_f$, is the magnification of the most
+central region of the retina and has a value in the human of about 7.8
+mm/\dg~\citep{rovamo_estimation_1979}.
+
+In our model, $M_f$ is related to $W_{nfs}$, the width of the
+retinotopic neural field, $W_{fov}$, the width of the eye's field of
+view and $E_2$, the eccentricity at which the retinal density has
+halved by:
 \begin{equation} \label{eq:fm}
@@
 \end{equation}
-Here, $W_{nfs}$ is 50 (the side length of the 50x50 grid)
-and $W_{fov}$ is set to 61\dg, a
-reduction from the biophysically accurate 150\dg~due to the small
-number of neurons in the retinotopic neural field. $E_2$ is
+Here, $W_{nfs}$ is 50 (the side length of the 50x50 grid) and
+$W_{fov}$ is set to 61\dg, a reduction from the biophysically accurate
+150\dg~due to the small number of neurons in the retinotopic neural
+field. $E_2$ is
 2.5 \citep{cope_basal_2017,slotnick_electrophysiological_2001}.
 
-The mapping from the retinotopic co-ordinates in the brain to rotational
-co-ordinates of the stimulus/response was written down by
+The mapping from the retinotopic co-ordinates in the brain to
+rotational co-ordinates of the stimulus/response was written down by
 \cite{schwartz_spatial_1977,eric_l._schwartz_computational_1980}
-for measurements of
-striate cortex [visual stimulus to electrophysiological response---\cite{daniel_representation_1961, talbot_physiological_1941}]
-and by \cite{ottes_visuomotor_1986} for superior colliculus data
-[electrophysiological SC stimulus to eye movement
-response---\cite{robinson_eye_1972}].
+for measurements of striate cortex [visual stimulus to
+electrophysiological response---\cite{daniel_representation_1961,
+talbot_physiological_1941}] and by \cite{ottes_visuomotor_1986} for
+superior colliculus data [electrophysiological SC stimulus to eye
+movement response---\cite{robinson_eye_1972}].
 % Ottes et al. fit to stimulus-to-movement data, and give a
@@
 retinal stimulus; Ottes et al.~use $r$ and $\phi$ as polar coordinates
-for the eye movement response; both use $u$ and $v$ as the Cartesian co-ordinates of the neural map. We use $\theta_{x}^{t}$ and $\theta_{y}^{t}$
-to give Euler rotations for the retinal target stimulus. Note also that
-the form of Eqns.~\ref{eq:thetas_to_phi} \& \ref{eq:thetas_to_r} is slightly
+for the eye movement response; both use $u$ and $v$ as the Cartesian
+co-ordinates of the neural map. We use $\theta_{x}^{t}$ and
+$\theta_{y}^{t}$ to give Euler rotations for the retinal target
+stimulus. Note also that the form of
+Eqns.~\ref{eq:thetas_to_phi} \& \ref{eq:thetas_to_r} is slightly
 different from that given in
@@
 
-The mapping encompases the entire visual field; the value of
-$\phi$ is allowed to vary from 0\dg~to 360\dg~along its axis.
-Effectively, the two contralateral colliculi found in the biology are
-incorporated into a
-single, square map, avoiding the need to carry out the kind of `colliculus
-gluing' described in \cite{tabareau_geometry_2007}.
+The mapping encompases the entire visual field; the value of $\phi$ is
+allowed to vary from 0\dg~to 360\dg~along its axis.  Effectively, the
+two contralateral colliculi found in the biology are incorporated into
+a single, square map, avoiding the need to carry out the kind of
+`colliculus gluing' described in \cite{tabareau_geometry_2007}.
 
@@
 \end{equation}
-where we have dropped the $t$ superscript on $\theta_x$ \& $\theta_y$, as
-these equations transform a collicular location into rotations of the eye.
+where we have dropped the $t$ superscript on $\theta_x$ \& $\theta_y$,
+as these equations transform a collicular location into rotations of
+the eye.
 
@@
 Briefly, the model consists of input from the World population (see
-Fig.~\ref{brain_model}, green population box) producing activity
-in an `express' pathway to superior colliculus (purple) and
-simultaneously in cortex, represented here by the FEF population (grey
-boxes in Fig.~\ref{brain_model}). The express pathway causes short
-latency activity in the superficial superior colliculus, which
-directly innervates the deeper layers of the superior colliculus
+Fig.~\ref{brain_model}, green population box) producing activity in an
+`express' pathway to superior colliculus (purple) and simultaneously
+in cortex, represented here by the FEF population (grey boxes in
+Fig.~\ref{brain_model}). The express pathway causes short latency
+activity in the superficial superior colliculus, which directly
+innervates the deeper layers of the superior colliculus
 (SC\_deep). Activity in FEF generates firing in a
@@
 2-D Gaussian kernel; lighter blue connections from the subthalamic
-nucleus (STN) to SNr and globus pallidus externum (GPe)
-are diffuse, all-to-all connections and projections coloured green are
-one-to-one connections that decay towards the fovea so that foveal
-activity in FEF does not swamp the basal ganglia which would prevent
-peripheral luminances from ever being selected.
+nucleus (STN) to SNr and globus pallidus externum (GPe) are diffuse,
+all-to-all connections and projections coloured green are one-to-one
+connections that decay towards the fovea so that foveal activity in
+FEF does not swamp the basal ganglia which would prevent peripheral
+luminances from ever being selected.
 %
@@
 tecto-tectal inhibition, which increases the inhibition between
-activity in opposite hemispheres of the field of view \citep{gian_g._mascetti_tectotectal_1981,olivier_evidence_2000} helping
-to resolve competition between saccades to the left and right. The
-tecto-tectal inhibitory connection is \e{not} present in
+activity in opposite hemispheres of the field of
+view \citep{gian_g._mascetti_tectotectal_1981,olivier_evidence_2000}
+helping to resolve competition between saccades to the left and
+right. The tecto-tectal inhibitory connection is \e{not} present in
 the \ccg~model. In all other respects the model is as described in
@@
 
-We implemented a saccadic burst generator (SBG) based
-on the connectivity outlined in \cite{gancarz_neural_1998}. The SBG network
-for two of the model's
-six channels is shown in Fig.~\ref{sbg}. Activity from the output
-layer of superior colliculus (SC\_avg) is fed into each channel, which
-sums the activity it receives and processes it in populations each of
-a single neural element representing all the neurons in that
-population. Each channel of the SBG functions to create the motor neuron
-activations that are required to accelerate the eye in a particular
-direction, then hold the eye in its new position against the returning
-force generated by the elastic properties of the muscles.  The
-required motor neuron activations are therefore a combination of features:
-a brief burst of
-increased activity that accelerates the eye; followed by a period
-of activity that is less than the burst firing rate but higher than
-the tonic rate that exists when the eye is at the centre. This
-holds the eye in its new position.
+We implemented a saccadic burst generator (SBG) based on the
+connectivity outlined in \cite{gancarz_neural_1998}. The SBG network
+for two of the model's six channels is shown in
+Fig.~\ref{sbg}. Activity from the output layer of superior colliculus
+(SC\_avg) is fed into each channel, which sums the activity it
+receives and processes it in populations each of a single neural
+element representing all the neurons in that population. Each channel
+of the SBG functions to create the motor neuron activations that are
+required to accelerate the eye in a particular direction, then hold
+the eye in its new position against the returning force generated by
+the elastic properties of the muscles.  The required motor neuron
+activations are therefore a combination of features: a brief burst of
+increased activity that accelerates the eye; followed by a period of
+activity that is less than the burst firing rate but higher than the
+tonic rate that exists when the eye is at the centre. This holds the
+eye in its new position.
 
 The SBG connectivity produces each of the these features separately,
-then sums them to create the desired `bump and tonic' activation
-time series.  The input to the first population in the SBG, the
-long-lead burst neurons (LLBNs), is conceived as originating from
-one of the deep layers of the superior colliculus.  The activity
-of the LLBNs are passed to excitatory burst neurons (EBNs) which,
-in turn, inhibit the LLBNs via the activity of the inhibitory
-burst neurons (IBNs).  This feedback loop has a transmission delay,
-which allows activity to build up in the EBNs before the inhibition
-is activated and the activity is then reduced again.  This mechanism
-generates the `bump'.
+then sums them to create the desired `bump and tonic' activation time
+series.  The input to the first population in the SBG, the long-lead
+burst neurons (LLBNs), is conceived as originating from one of the
+deep layers of the superior colliculus.  The activity of the LLBNs are
+passed to excitatory burst neurons (EBNs) which, in turn, inhibit the
+LLBNs via the activity of the inhibitory burst neurons (IBNs).  This
+feedback loop has a transmission delay, which allows activity to build
+up in the EBNs before the inhibition is activated and the activity is
+then reduced again.  This mechanism generates the `bump'.
 
@@
 achieved simply by integrating the bump over time and multiplying by a
-some small gain factor.  This is the function of the tonic neurons (TNs).
-The firing rate of the motor neuron defines the amount of force applied
-to the eye by that muscle.  Thus, the size of the `bump' defines how far
-the eye moves in that channel's direction.  The gain and delay parameters
-in the LLBN-EBN-IBN-LLBN feedback loop therefore have to be tuned such that
-the endpoint of the saccade is reasonably accurate.  Furthermore the
-restoring force generated by the elasticity of the muscles is dependent
-on the radial distance.  The value of the new tonic firing rate, after
-the `bump' is dependent on the end location of the eye.  If the ratio
-between the EBN firing rate and the TN firing rate is not exactly
-correct, the eye will drift away from the saccade endpoint after the
-saccade has been completed.  The EBN-TN connection strength is
-therefore tuned such that the TN firing rate yields a stable eye
-position across a range of eye eccentricities.
-
-The omnipause neurons (OPNs) are tonically active and inhibit the EBNs.
-The activity of the OPNs is itself inhibited by activity in the LLBNs.
-The purpose of this arrangement is to ensure the eye does not move in
-response to neural noise.
-
-Each mean activity of all the neurons in each SBG population (except the
-TNs) is defined by a single leaky integrator, first order differential equation.
+some small gain factor.  This is the function of the tonic neurons
+(TNs).  The firing rate of the motor neuron defines the amount of
+force applied to the eye by that muscle.  Thus, the size of the `bump'
+defines how far the eye moves in that channel's direction.  The gain
+and delay parameters in the LLBN-EBN-IBN-LLBN feedback loop therefore
+have to be tuned such that the endpoint of the saccade is reasonably
+accurate.  Furthermore the restoring force generated by the elasticity
+of the muscles is dependent on the radial distance.  The value of the
+new tonic firing rate, after the `bump' is dependent on the end
+location of the eye.  If the ratio between the EBN firing rate and the
+TN firing rate is not exactly correct, the eye will drift away from
+the saccade endpoint after the saccade has been completed.  The EBN-TN
+connection strength is therefore tuned such that the TN firing rate
+yields a stable eye position across a range of eye eccentricities.
+
+The omnipause neurons (OPNs) are tonically active and inhibit the
+EBNs.  The activity of the OPNs is itself inhibited by activity in the
+LLBNs.  The purpose of this arrangement is to ensure the eye does not
+move in response to neural noise.
+
+Each mean activity of all the neurons in each SBG population (except
+the TNs) is defined by a single leaky integrator, first order
+differential equation.
 \begin{equation}\label{eq:LIN}
@@
 \end{equation}
-where $a$ is the activation of the nucleus, and $\tau$ is the time constant
-of the nucleus. $y$ is a piecewise linear function of the weighted sum of
-inputs to the nucleus and is given by
+where $a$ is the activation of the nucleus, and $\tau$ is the time
+constant of the nucleus. $y$ is a piecewise linear function of the
+weighted sum of inputs to the nucleus and is given by
 \begin{equation}
@@
 \end{equation}
-where $b$ is the $IN$ axis offset.  $IN$ is the weighted sum of inputs to
-the nucleus and is given by,
+where $b$ is the $IN$ axis offset.  $IN$ is the weighted sum of inputs
+to the nucleus and is given by,
 \begin{equation}
@@
 where $a_{m}$ is the activation of the $m^{th}$ afferent nucleus.
-$w_{mn}$ is the connection strength between the $m^{th}$ afferent nucleus
-and the current nucleus. The activity of the TNs are defined as
+$w_{mn}$ is the connection strength between the $m^{th}$ afferent
+nucleus and the current nucleus. The activity of the TNs are defined
+as
 \begin{equation}
@@
 \end{equation}
-with an identical piecewise linear transfer function as the other SBG populations.
+with an identical piecewise linear transfer function as the other SBG
+populations.
 
@@
 
-% Possibly introductory paragraph here.
-The output signals of the brainstem are used to drive the biomechanical model.
-The latter is not only used to get tangible feedback on the simulated saccades
-including motion trajectories, but adds one more modelling dimension related to
-the inertial properties of the eye plant including muscle properties.
-
-% EYE MODEL DESCRIPTION HERE
+The output signals of the brainstem are used to drive the
+biomechanical model.  The latter is not only used to get tangible
+feedback on the simulated saccades including motion trajectories, but
+adds one more modelling dimension related to the inertial properties
+of the eye plant including muscle properties.
+
 The biomechanical eye model, implemented using the OpenSim framework
 \citep{seth_opensim:_2011}, is anatomically represented by a sphere of
-uniform mass distribution. The diameter of the eye is 24 mm for adults,
-with small variations between individuals; the mass of the eye is 7.5 grams.
-The eyeball is actuated by six extraocular muscles
+uniform mass distribution. The diameter of the eye is 24 mm for
+adults, with small variations between individuals; the mass of the eye
+is 7.5 grams.  The eyeball is actuated by six extraocular muscles
 (EOMs). The EOMs are arranged in three pairs forming a cone inside the
@@
 The force applied by EOMs is controlled by an excitatory signal
-supplied by motoneurons in the brainstem. The neural drive to produce a saccadic
-eye movement can be characterized by a pulse component to overcome the
-viscoelasticity of the orbital plant, a step component to stabilize the eye in
-the new position, and a slide component that models the gradual transition
-between the pulse and step.
-
-The dynamics of muscular
-forces can be split into: 1) The elasticity of the muscles. 2) A delay
-between the onset of the afferent excitatory signal and the actual
-muscle contraction, caused by the transmission time of the action
-potentials and by the necessary calcium release at the muscle
-fibres. We developed a custom extraocular muscle model which captures
-these features.
-
-%Orbital fat force
+supplied by motoneurons in the brainstem. The neural drive to produce
+a saccadic eye movement can be characterized by a pulse component to
+overcome the viscoelasticity of the orbital plant, a step component to
+stabilize the eye in the new position, and a slide component that
+models the gradual transition between the pulse and step.
+
+The dynamics of muscular forces can be split into: 1) The elasticity
+of the muscles. 2) A delay between the onset of the afferent
+excitatory signal and the actual muscle contraction, caused by the
+transmission time of the action potentials and by the necessary
+calcium release at the muscle fibres. We developed a custom
+extraocular muscle model which captures these features.
+
+% Orbital fat force
 Passive forces due to the fatty tissues inside the eye orbit also
 affect eye dynamics. Their role is critical in eliminating the
-influence of head and body movements. We incorporated a custom torque, $\mathbf{t}$,
-which acts like a rotational spring-damper apparatus, resisting
-eyeball movements. It has elastic and viscous properties governed by
-$\mathbf{t} = -K\mathbf{R}-C\mathbf{U}$ where $\mathbf{R}$ is the
-eye's orientation and $\mathbf{U}$ is its angular velocity. $K$ and
-$C$ are constants. A fuller description of the biomechanical model
+influence of head and body movements. We incorporated a custom torque,
+$\mathbf{t}$, which acts like a rotational spring-damper apparatus,
+resisting eyeball movements. It has elastic and viscous properties
+governed by $\mathbf{t} = -K\mathbf{R}-C\mathbf{U}$ where $\mathbf{R}$
+is the eye's orientation and $\mathbf{U}$ is its angular velocity. $K$
+and $C$ are constants. A fuller description of the biomechanical model
 can be found in \cite{papapavlou_physics-based_2014}.
@@
 spatial aspect of the transform is thought to be implemented by a
-weight-mapping \citep{tabareau_geometry_2007,arai_two-dimensional_1994} and we
-follow this idea.
-% Words along the lines of:
+weight-mapping \citep{tabareau_geometry_2007,arai_two-dimensional_1994}
+and we follow this idea.
+%
 Arai and co-workers trained a 20x20 neural network model of the
@@
 %
-The training approach of \cite{arai_two-dimensional_1994} was not feasible in this study
-due to the length of time required to run our model and its
-stochasticity, which meant multiple runs of the model were necessary
-in order to generate output statistics.
+The training approach of \cite{arai_two-dimensional_1994} was not
+feasible in this study due to the length of time required to run our
+model and its stochasticity, which meant multiple runs of the model
+were necessary in order to generate output statistics.
 %
@@
 and the assumption of invariant 2D Gaussian activity profiles in
-SC. As they found it closely resembles the
-results of \cite{arai_two-dimensional_1994}, and it is a simple
-formulation, we considered
-it as the means to generate the six weight maps in our own model.
+SC. As they found it closely resembles the results
+of \cite{arai_two-dimensional_1994}, and it is a simple formulation,
+we considered it as the means to generate the six weight maps in our
+own model.
 %
@@
 which the \cite{tabareau_geometry_2007} result is based leads to a
-very \e{variant} activity profile in the \ccg~model. A luminance of
-a given size which excites activity near to the fovea causes activity
-in a large number of neurons, whereas activity far from the fovea
-excites a much smaller region. This effect is clearly demonstrated in
+very \e{variant} activity profile in the \ccg~model. A luminance of a
+given size which excites activity near to the fovea causes activity in
+a large number of neurons, whereas activity far from the fovea excites
+a much smaller region. This effect is clearly demonstrated in
 Fig.~\ref{fig:mapping} for equal sized targets both on and distal from
@@
 and \cite{vokoun_response_2014}. Although in this work we do not model
-the SC in detail, we extended the model with a third functional layer named SC\_deep2, shown in Fig.~\ref{scdeep}
-(\ccg~has only the two layers SC\_sup and SC\_deep). We
-introduced a widening projection based on a Gaussian projection field
-whose width, $\sigma(r)$ varies in inverse proportion to the
-magnification factor, $M(r)$, given in Eq.~\ref{eq:cmf} according to:
+the SC in detail, we extended the model with a third functional layer
+named SC\_deep2, shown in Fig.~\ref{scdeep} (\ccg~has only the two
+layers SC\_sup and SC\_deep). We introduced a widening projection
+based on a Gaussian projection field whose width, $\sigma(r)$ varies
+in inverse proportion to the magnification factor, $M(r)$, given in
+Eq.~\ref{eq:cmf} according to:
 \begin{equation} \label{eq:sigmar}
@@
 \end{equation}
-$m_{\sigma}$ is a scalar parameter which determines the `magnitude
-of the widening'. $M^0$ is the `starting' magnification factor;
-within the foveal region ($0 \leq r \leq r_0$), the projection field
-is not allowed to widen and so
+$m_{\sigma}$ is a scalar parameter which determines the `magnitude of
+the widening'. $M^0$ is the `starting' magnification factor; within
+the foveal region ($0 \leq r \leq r_0$), the projection field is not
+allowed to widen and so
 \begin{equation} \label{eq:sigmar2}
@@
 which makes $\sigma_0$ the width of the Gaussian projection field
-within the foveal region. (Note that the value chosen for the width
-of the foveal region, $r_0$ is not identical to the foveal shift parameter used
-in the \e{DecayingAtFovea} projections into striatum.)
-The \e{Widening Gaussian} projection weight, $w(r,d)$ is then
-computed as:
+within the foveal region. (Note that the value chosen for the width of
+the foveal region, $r_0$ is not identical to the foveal shift
+parameter used in the \e{DecayingAtFovea} projections into striatum.)
+The \e{Widening Gaussian} projection weight, $w(r,d)$ is then computed
+as:
 \begin{equation} \label{eq:widening}
@@
 \end{equation}
-where $d$ is the distance between the source and destination
-elements in the collicular plane.  $m_\sigma$ was set to 50, $\sigma_0$
-was 0.3, $M^0$ was 12.43 and $r_0$ was 20.
+where $d$ is the distance between the source and destination elements
+in the collicular plane.  $m_\sigma$ was set to 50, $\sigma_0$ was
+0.3, $M^0$ was 12.43 and $r_0$ was 20.
 % Could have a figure here, made from widening_gaussian.m
@@
 only two dimensional information is encoded in superior
-colliculus \citep{wurtz_activity_1972,hepp_monkey_1993,van_opstal_two-rather_1991}, but the
-eye is actuated by six extraocular muscles. In order to find out a
-possible form for the input to the oblique muscles we carried out a
-training process
+colliculus
+\citep{wurtz_activity_1972,hepp_monkey_1993,van_opstal_two-rather_1991},
+but the eye is actuated by six extraocular muscles. In order to find
+out a possible form for the input to the oblique muscles we carried
+out a training process
 % possibly descibe this training process in supplemental data
-which depended on a
-centroid computation in SC\_deep. For the four rectus muscles, the
-resulting weight maps resembled those found by
+which depended on a centroid computation in SC\_deep. For the four
+rectus muscles, the resulting weight maps resembled those found by
 \cite{arai_two-dimensional_1994}. The trained
@@
 The saccadic burst generator model was originally conceived with the
-assumption of a step input, which returns to zero activity at a suitable
-time to curtail the saccade and avoid staircase
-saccades \citep{gancarz_neural_1998}. In our model
-there is no such mechanism to reduce activity in SC\_deep, and elsewhere.
-Although a successful, accurate saccade towards a target luminance will
-remove the excitation
-which caused the activity in SC\_deep by bringing the target luminance
-within the masked,
-foveal region, the activity in SC decays too slowly to avoid
-additional saccadic movements. We found it necessary to hypothesize
-an inhibitory feedback mechanism from the SBG to the brain model.
-This is shown in Fig.~\ref{sbg}, which indicates how the output from
-the inhibitory burst neurons (IBN) of the SBG model are used to feed
-back an inhibitory signal to the SC\_deep, thalamus and FEF populations
-in the brain model, resetting them ready for the next saccade.
+assumption of a step input, which returns to zero activity at a
+suitable time to curtail the saccade and avoid staircase
+saccades \citep{gancarz_neural_1998}. In our model there is no such
+mechanism to reduce activity in SC\_deep, and elsewhere.  Although a
+successful, accurate saccade towards a target luminance will remove
+the excitation which caused the activity in SC\_deep by bringing the
+target luminance within the masked, foveal region, the activity in SC
+decays too slowly to avoid additional saccadic movements. We found it
+necessary to hypothesize an inhibitory feedback mechanism from the SBG
+to the brain model.  This is shown in Fig.~\ref{sbg}, which indicates
+how the output from the inhibitory burst neurons (IBN) of the SBG
+model are used to feed back an inhibitory signal to the SC\_deep,
+thalamus and FEF populations in the brain model, resetting them ready
+for the next saccade.
 % Might have to justify the above a bit more.
@@
 % worldDataMaker to brain, but Re-work:
-The eye model outputs its rotational state at each
-timestep. The rotational state is used to compute the view of the
-world in the eye's frame of reference. To simplify
-the calculation, the luminances exist on a spherical surface at the
-centre of which is the eye. A hand-coded BRAHMS component called
-worldDataMaker computes the projection of the luminances into the
-eye's frame of reference and then converts this representation into a
-retinotopic map to pass into the brain model. The input to the brain
-model is thus able to change continuously, on every timestep, rather
-than in a step-wise fashion when a saccade occurs, as in the \ccg~model.
+The eye model outputs its rotational state at each timestep. The
+rotational state is used to compute the view of the world in the eye's
+frame of reference. To simplify the calculation, the luminances exist
+on a spherical surface at the centre of which is the eye. A hand-coded
+BRAHMS component called worldDataMaker computes the projection of the
+luminances into the eye's frame of reference and then converts this
+representation into a retinotopic map to pass into the brain
+model. The input to the brain model is thus able to change
+continuously, on every timestep, rather than in a step-wise fashion
+when a saccade occurs, as in the \ccg~model.
 
@@
 The final models, on which the results of this paper are based are
-named `TModel3', `TModel4' and `TModel5'. Descriptions of these, and earlier
-versions of the model can be
-found in the code repository given in SUPPLEMENTAL DATA.
+named `TModel3', `TModel4' and `TModel5'. Descriptions of these, and
+earlier versions of the model can be found in the code repository
+given in SUPPLEMENTAL DATA.
 
@@
 
-% trajectories, neuron activations (esp. brainstem). latency vs
-% dopamine, latency vs gap.
-%
-% The importance of an even sized hill of activity in SC_deep. The
-% difficulties of achieving this.
-
 \subsection{Weight maps}
 
-We found the best parameters for the exponential in Eq.~\ref{eq:weightmaps}
-($i$ and $j$) by a manual tuning process. After selecting values for $i$ and $j$
-in either the horizontal or vertical/oblique channels, we ran the model 6 times
-at each of 8 target eccentricities (7\dg--14\dg) which were purely
-in the direction of the
-newly parameterised channel. The training saccades were produced as described below in
-Sect.~\ref{sec:singlesaccades}, with the same fixation and target luminances
-(crosses of magnitude 0.2 and 0.3) but with
-the fixation offset and target onset occurring at 0.2~s. We measured the end-point
-of the saccade by
-detecting the location at which the saccade velocity had dropped below
-0.005 of its peak. We iterated until the mean saccade endpoint plotted versus target
-was close to the ideal straight line---see Fig.~\ref{sacc_vs_targ}(a) \& (c). We
-applied the same parameters to both directions of each channel;
-$i_{up} = i_{down} = 0.00195$, $j_{up} = j_{down} = 0.075$,
-$i_{left} = i_{right} = 0.0016$ and $j_{left} = j_{right} = 0.067$. The resulting
-weight maps (where the oblique maps are 1/10$^{\mathrm{th}}$ of the vertical maps,
-as described earlier) are shown in Fig.~\ref{weightmaps}.
+We found the best parameters for the exponential in
+Eq.~\ref{eq:weightmaps} ($i$ and $j$) by a manual tuning
+process. After selecting values for $i$ and $j$ in either the
+horizontal or vertical/oblique channels, we ran the model 6 times at
+each of 8 target eccentricities (7\dg--14\dg) which were purely in the
+direction of the newly parameterised channel. The training saccades
+were produced as described below in Sect.~\ref{sec:singlesaccades},
+with the same fixation and target luminances (crosses of magnitude 0.2
+and 0.3) but with the fixation offset and target onset occurring at
+0.2~s. We measured the end-point of the saccade by detecting the
+location at which the saccade velocity had dropped below 0.005 of its
+peak. We iterated until the mean saccade endpoint plotted versus
+target was close to the ideal straight line---see
+Fig.~\ref{sacc_vs_targ}(a) \& (c). We applied the same parameters to
+both directions of each channel; $i_{up} = i_{down} = 0.00195$,
+$j_{up} = j_{down} = 0.075$, $i_{left} = i_{right} = 0.0016$ and
+$j_{left} = j_{right} = 0.067$. The resulting weight maps (where the
+oblique maps are 1/10$^{\mathrm{th}}$ of the vertical maps, as
+described earlier) are shown in Fig.~\ref{weightmaps}.
 % From map_modelling2.m:
@@
 
-In Fig.~\ref{sacc_vs_targ}, we showed
-the result of running the model to targets located on the principle
-axes, on which the model was trained. We then simulated single saccades
-to targets in one hemifield of the eye's field of view, with
-eccentricities between 6\dg~and 14.5\dg. As in the
-training, we ran the simulation 6 times for each target,
-$\mathbf{\theta}^t = (\theta_{x}^t, \theta_{y}^t, 0)$ to obtain
-mean saccade end-points.
-Fig.~\ref{errorsurfaceTM3} shows saccade accuracy results for an
-entire hemifield in the na\"ive model which passed the output of
-SC\_deep directly to SBG via the weight maps. The ratio of
-the magnitude of the error vector to the magnitude of the target
-vector is plotted using a colour map. This ratio is shown for the full,
-three dimensional error vector in Fig.~\ref{errorsurfaceTM3}(a) and
-for the $x$, $y$ and $z$ components in Figs.~\ref{errorsurfaceTM3}(b)--(c).
-Inspection of  Fig.~\ref{errorsurfaceTM3}(a) shows that the end-point
-error is minimal along the principle axes ($\theta_{x}^t=\;$0 or
-$\theta_{y}^t=\;$0) and maximal near the 45\dg~oblique targets
-(blue lines) with the end point error as high as 80\% of the
-programmed saccade magnitude.
-% Mention \cite{thurat_biomimetic_2015} in discussion.
-The $x$ component error map in Fig.~\ref{errorsurfaceTM3}(b)
-shows the same trend, mirrored about the `Target X' axis, whereas
-the $y$ and $z$ component errors are, relatively, much smaller.
-Because the $x$ component of the error is clearly contributing to
-end point errors which would not be considered `on target',
-especially for oblique saccades, we considered the effect of the
-non-uniform size of the hill of activity in SC\_deep.
-
-In our model, the location, \e{size} and shape of activity in FEF,
-the basal ganglia, thalamus and superior colliculus is eccentricity
+In Fig.~\ref{sacc_vs_targ}, we showed the result of running the model
+to targets located on the principle axes, on which the model was
+trained. We then simulated single saccades to targets in one hemifield
+of the eye's field of view, with eccentricities between 6\dg~and
+14.5\dg. As in the training, we ran the simulation 6 times for each
+target, $\mathbf{\theta}^t = (\theta_{x}^t, \theta_{y}^t, 0)$ to
+obtain mean saccade end-points.  Fig.~\ref{errorsurfaceTM3} shows
+saccade accuracy results for an entire hemifield in the na\"ive model
+which passed the output of SC\_deep directly to SBG via the weight
+maps. The ratio of the magnitude of the error vector to the magnitude
+of the target vector is plotted using a colour map. This ratio is
+shown for the full, three dimensional error vector in
+Fig.~\ref{errorsurfaceTM3}(a) and for the $x$, $y$ and $z$ components
+in Figs.~\ref{errorsurfaceTM3}(b)--(c).  Inspection of
+Fig.~\ref{errorsurfaceTM3}(a) shows that the end-point error is
+minimal along the principle axes ($\theta_{x}^t=\;$0 or
+$\theta_{y}^t=\;$0) and maximal near the 45\dg~oblique targets (blue
+lines) with the end point error as high as 80\% of the programmed
+saccade magnitude.  The $x$ component error map in
+Fig.~\ref{errorsurfaceTM3}(b) shows the same trend, mirrored about the
+`Target X' axis, whereas the $y$ and $z$ component errors are,
+relatively, much smaller.  Because the $x$ component of the error is
+clearly contributing to end point errors which would not be considered
+`on target', especially for oblique saccades, we considered the effect
+of the non-uniform size of the hill of activity in SC\_deep.
+
+In our model, the location, \e{size} and shape of activity in FEF, the
+basal ganglia, thalamus and superior colliculus is eccentricity
 dependent, in line with the retinotopic mapping stated by
@@
 activity, because fewer retinal neurons are excited far from the
-fovea. \cite{cope_basal_2017} showed that this relationship can explain
-increased saccadic latencies for distal targets, resulting from
-reduced activity in the decision making circuitry of the basal ganglia.
-However, the notion that activity in superior colliculus is
+fovea. \cite{cope_basal_2017} showed that this relationship can
+explain increased saccadic latencies for distal targets, resulting
+from reduced activity in the decision making circuitry of the basal
+ganglia.  However, the notion that activity in superior colliculus is
 eccentricity-dependent conflicts with the result of
@@
 experimental findings, which do not show significant eccentricity
-dependence, at least in the burst layer~\citep{anderson_two-dimensional_1998}.
+dependence, at least in the burst
+layer~\citep{anderson_two-dimensional_1998}.
 % Nice ref that - see Fig 16
@@
 To bring our model in line with these results, whilst maintaining the
-eccentricity dependent activity in basal ganglia, we hypothesised
-that a `widening projection' exists between two maps in superior
-colliculus. Activities in one SC\_deep layer remains eccentricity-dependent,
-with loops back to thalamus and cortex and through basal ganglia.
-This activity is then fed through a projection, which applies a
-Gaussian projection field, whose width increases with increasing
-stimulus eccentricity according to Eq.~\ref{eq:widening}.
-The activity in this second SC\_deep layer is then fed to the
-weight maps of the SBG. This model was called `TModel4'. TModel4
-was parameterised such that its horizontal and vertical error
-was similar---so that its equivalent of Fig.~\ref{sacc_vs_targ}
-showed a similar sum of squares error.
-
-Figs.~\ref{errorsurface}(a)--(d) show the same percentage errors
-for TModel4 as Fig.~\ref{errorsurfaceTM3} shows for TModel3.
-First of all, note that the error magnitudes are much smaller. The mean
-errors are smaller for every axis. The largest errors produced by
-the model are approximately 15\%, which are
-within the boundaries of what some authors have suggested would be regarded
-as an accurate saccade \citep{mcpeek_saccade_2002,mcpeek_incomplete_2006}.
-The magnitude of the largest error vector is approximately 1.5\dg.
-
-This result indicates that the
-exponential part of the Ottes et al.~weight map from SC to the SBG cannot
-on its own compensate for the eccentricity-dependent size of the hill of
-activity. The introduction of a widening projection field substantially
-improves the mean accuracy of saccades across the field of view.
-We therefore suggest that the transformation between retinotopically mapped
-activity, and eccentricity-independent activity width occurs
-within the superior colliculus and works alongside a simple,
-monotonically increasing weight map between SC and the SBG channels.
+eccentricity dependent activity in basal ganglia, we hypothesised that
+a `widening projection' exists between two maps in superior
+colliculus. Activities in one SC\_deep layer remains
+eccentricity-dependent, with loops back to thalamus and cortex and
+through basal ganglia.  This activity is then fed through a
+projection, which applies a Gaussian projection field, whose width
+increases with increasing stimulus eccentricity according to
+Eq.~\ref{eq:widening}.  The activity in this second SC\_deep layer is
+then fed to the weight maps of the SBG. This model was called
+`TModel4'. TModel4 was parameterised such that its horizontal and
+vertical error was similar---so that its equivalent of
+Fig.~\ref{sacc_vs_targ} showed a similar sum of squares error.
+
+Figs.~\ref{errorsurface}(a)--(d) show the same percentage errors for
+TModel4 as Fig.~\ref{errorsurfaceTM3} shows for TModel3.  First of
+all, note that the error magnitudes are much smaller. The mean errors
+are smaller for every axis. The largest errors produced by the model
+are approximately 15\%, which are within the boundaries of what some
+authors have suggested would be regarded as an accurate
+saccade \citep{mcpeek_saccade_2002,mcpeek_incomplete_2006}.  The
+magnitude of the largest error vector is approximately 1.5\dg.
+
+This result indicates that the exponential part of the Ottes et
+al.~weight map from SC to the SBG cannot on its own compensate for the
+eccentricity-dependent size of the hill of activity. The introduction
+of a widening projection field substantially improves the mean
+accuracy of saccades across the field of view.  We therefore suggest
+that the transformation between retinotopically mapped activity, and
+eccentricity-independent activity width occurs within the superior
+colliculus and works alongside a simple, monotonically increasing
+weight map between SC and the SBG channels.
 
@@
 
-Having finalised the model by setting the weight maps, we then proceeded
-to exercise the model (TModel4), starting with saccades to a single target;
-prosaccades. Fig.~\ref{outmany}(a) shows 9 representative saccades
-to a single
-target luminance. Initially, the eye had rotational state
-$\theta_x=\theta_y=\theta_z=0$ with its fovea directed at a
-fixation luminance cross (span 6\dg, bar width 2\dg) of
-magnitude 0.2 (in arbitrary units). At a
-simulation time of 0.4~s, the fixation luminance was set to 0 and
-a target luminance cross of the same dimensions as the fixation but with
-magnitude 0.3 was illuminated at one of the
-9 different locations, marked by crosses in Fig.~\ref{outmany}(a).
-The resulting trajectories are plotted, with colour indicating the
-relationship between trajectories and target crosses. The approximate
-end-point error is visible in this figure, although the last point in
-each trajectory is the saccade position at 0.8~s and not the
-velocity-based end-point described above. Figs.~\ref{outmany}(b) and (c)
-show the rotational components of the blue and red trajectories
-in Fig.~\ref{outmany}(a) along with the target and fixation
-luminance values. Rotations are the eye's Euler rotational components
-in the world frame of reference.
+Having finalised the model by setting the weight maps, we then
+proceeded to exercise the model (TModel4), starting with saccades to a
+single target; prosaccades. Fig.~\ref{outmany}(a) shows 9
+representative saccades to a single target luminance. Initially, the
+eye had rotational state $\theta_x=\theta_y=\theta_z=0$ with its fovea
+directed at a fixation luminance cross (span 6\dg, bar width 2\dg) of
+magnitude 0.2 (in arbitrary units). At a simulation time of 0.4~s, the
+fixation luminance was set to 0 and a target luminance cross of the
+same dimensions as the fixation but with magnitude 0.3 was illuminated
+at one of the 9 different locations, marked by crosses in
+Fig.~\ref{outmany}(a).  The resulting trajectories are plotted, with
+colour indicating the relationship between trajectories and target
+crosses. The approximate end-point error is visible in this figure,
+although the last point in each trajectory is the saccade position at
+0.8~s and not the velocity-based end-point described
+above. Figs.~\ref{outmany}(b) and (c) show the rotational components
+of the blue and red trajectories in Fig.~\ref{outmany}(a) along with
+the target and fixation luminance values. Rotations are the eye's
+Euler rotational components in the world frame of reference.
 
@@
 functionality as that reported in \cite{cope_basal_2017}, we
-investigated the effect on saccadic response times of:
-target eccentricity; and any gap or overlap between fixation off-time
-and target on-time. We showed that the full model reproduces the
-`hockey stick' shape shown in Fig. 7 of \cite{cope_basal_2017} for
-horizontal [Fig.~\ref{lat_vs_all}(a)], vertical
-[Fig.~\ref{lat_vs_all}(b)] and oblique saccades (not shown). The latency
-increases with eccentricity far from the fovea because the retinotopic mapping
-reduces the activity in the basal ganglia for more eccentric targets (this
-effect is described in detail in \cite{cope_basal_2017}). Closer to the fovea,
-the interaction between the foveal mask and the activity in FEF again leads
-to reduced input into into the basal ganglia and an increased time to
-achieve disinhibition in SNr.
-
-Fig.~\ref{lat_vs_all}(c) shows latencies achieved when varying the time
-between fixation offset and target onset. This is termed the \e{gap condition};
-and is represented by a scalar value which, if positive, refers to a gap
-between fixation offset and target onset, and when negative, signifies an
-overlap, with the fixation luminance persisting past the time at which the
-target is illuminated. A negative gap is also termed an \e{overlap}.
-Again, we verify the behaviour
-presented in \cite{cope_basal_2017}, explained as resulting from the
-inhibition of the cortico-thalamic loop by SNr. In the gap condition, when
-the fixation luminance is removed, activity in STN immediately begins to
-decay, allowing SNr activity to reduce and thereby reducing inhibition on
-thalamus, allowing the target luminance to build up quickly in FEF, thalamus
-and through the basal ganglia's striatum and SNr. The shape of the curves in
-Fig.~\ref{lat_vs_all}(c) matches the results in \cite{cope_basal_2017}
-for target luminances of 1 and 0.6; for overlaps longer than 100~ms
-(gap $<$ -100~ms), the latency becomes constant; the saccade is programmed
-whilst the fixation is present, with the target luminance inducing sufficient
-activity in striatum to `break through' the SNr inhibition caused by the
-fixation. If the target luminance is reduced to 0.3, the balance is altered
-in favour of the fixation and the latency vs.~gap becomes approximately
-linear and equal to the overlap time plus around 100~ms.
+investigated the effect on saccadic response times of: target
+eccentricity; and any gap or overlap between fixation off-time and
+target on-time. We showed that the full model reproduces the `hockey
+stick' shape shown in Fig. 7 of \cite{cope_basal_2017} for horizontal
+[Fig.~\ref{lat_vs_all}(a)], vertical [Fig.~\ref{lat_vs_all}(b)] and
+oblique saccades (not shown). The latency increases with eccentricity
+far from the fovea because the retinotopic mapping reduces the
+activity in the basal ganglia for more eccentric targets (this effect
+is described in detail in \cite{cope_basal_2017}). Closer to the
+fovea, the interaction between the foveal mask and the activity in FEF
+again leads to reduced input into into the basal ganglia and an
+increased time to achieve disinhibition in SNr.
+
+Fig.~\ref{lat_vs_all}(c) shows latencies achieved when varying the
+time between fixation offset and target onset. This is termed
+the \e{gap condition}; and is represented by a scalar value which, if
+positive, refers to a gap between fixation offset and target onset,
+and when negative, signifies an overlap, with the fixation luminance
+persisting past the time at which the target is illuminated. A
+negative gap is also termed an \e{overlap}.  Again, we verify the
+behaviour presented in \cite{cope_basal_2017}, explained as resulting
+from the inhibition of the cortico-thalamic loop by SNr. In the gap
+condition, when the fixation luminance is removed, activity in STN
+immediately begins to decay, allowing SNr activity to reduce and
+thereby reducing inhibition on thalamus, allowing the target luminance
+to build up quickly in FEF, thalamus and through the basal ganglia's
+striatum and SNr. The shape of the curves in Fig.~\ref{lat_vs_all}(c)
+matches the results in \cite{cope_basal_2017} for target luminances of
+1 and 0.6; for overlaps longer than 100~ms (gap $<$ -100~ms), the
+latency becomes constant; the saccade is programmed whilst the
+fixation is present, with the target luminance inducing sufficient
+activity in striatum to `break through' the SNr inhibition caused by
+the fixation. If the target luminance is reduced to 0.3, the balance
+is altered in favour of the fixation and the latency vs.~gap becomes
+approximately linear and equal to the overlap time plus around 100~ms.
 
 Fig.~\ref{lat_vs_all}(d) shows the effect of the dopamine parameter on
-saccade latencies in gap, step and overlap conditions. In general, the effect of
-decreasing the dopamine parameter was a smooth, monotonic and undramatic
-increase in saccade latency. However, the data for the overlap condition
-with a target luminance which was 3 times as bright as the fixation luminance
-was more interesting. Here we see a transition around a dopamine value if 0.7.
-Below this value,
-the basal ganglia is not able to select the target luminance until the fixation
-is removed, reducing the excitatory drive from STN to SNr, and consequently
-the inhibition from SNr to the thalamo-cortical loop. For the target
-luminance 0.6, 0.7 dopamine allows the basal ganglia to select sufficiently well
-so that the target can build up in the thalamo-cortical loop, in spite of
-the fixation overlap.
+saccade latencies in gap, step and overlap conditions. In general, the
+effect of decreasing the dopamine parameter was a smooth, monotonic
+and undramatic increase in saccade latency. However, the data for the
+overlap condition with a target luminance which was 3 times as bright
+as the fixation luminance was more interesting. Here we see a
+transition around a dopamine value if 0.7.  Below this value, the
+basal ganglia is not able to select the target luminance until the
+fixation is removed, reducing the excitatory drive from STN to SNr,
+and consequently the inhibition from SNr to the thalamo-cortical
+loop. For the target luminance 0.6, 0.7 dopamine allows the basal
+ganglia to select sufficiently well so that the target can build up in
+the thalamo-cortical loop, in spite of the fixation overlap.
 
 The relationship between latency and the target luminance is given in
-Fig.~\ref{lat_vs_all}(e). This shows latency for a 100~ms gap, step and
-100~ms overlap conditions for a given fixation luminance of 0.2,
+Fig.~\ref{lat_vs_all}(e). This shows latency for a 100~ms gap, step
+and 100~ms overlap conditions for a given fixation luminance of 0.2,
 and a horizontally located target at $\theta_{y}^{t}=$-10\dg. For the
-gap condition, we see very short latencies for luminances of about 0.75 and above.
-Finally, the activity driving these express saccades is initiated by high firing rates
-in the superficial layer of SC (SCs), which then drives activity in thalamus and
-through the basal ganglia. A gradual transition from express saccades to
-reflexive saccades is observed as the contribution of the SCs becomes weaker
-and the drive from FEF into the thalamo-cortical loop becomes necessary
-to elicit a saccade.
-%
-A similar gradual transition, albeit for higher latencies
-is seen for the step condition. At higher target luminances, the SCs has a
-greater effect on the activity in the thalamo-cortical loop. However, the
-activity in STN caused by the fixation luminance increases the latency at
-all luminance values compared with the gap condition.
-%
-The overlap condition leads to increased latencies for luminances below 2.5, but
-meets the step condition above this value, at which the 0.2 fixation
-luminance appears to have a negligible effect on the system.
+gap condition, we see very short latencies for luminances of about
+0.75 and above.  Finally, the activity driving these express saccades
+is initiated by high firing rates in the superficial layer of SC
+(SCs), which then drives activity in thalamus and through the basal
+ganglia. A gradual transition from express saccades to reflexive
+saccades is observed as the contribution of the SCs becomes weaker and
+the drive from FEF into the thalamo-cortical loop becomes necessary to
+elicit a saccade.
+%
+A similar gradual transition, albeit for higher latencies is seen for
+the step condition. At higher target luminances, the SCs has a greater
+effect on the activity in the thalamo-cortical loop. However, the
+activity in STN caused by the fixation luminance increases the latency
+at all luminance values compared with the gap condition.
+%
+The overlap condition leads to increased latencies for luminances
+below 2.5, but meets the step condition above this value, at which the
+0.2 fixation luminance appears to have a negligible effect on the
+system.
 
@@
 
-We now present results derived from the fully parameterised and integrated
-model; where we took advantage of the fact that it is a closed loop system. This
-allowed us to present sequences of target luminances and allow the model to
-direct its fovea at the most salient target.
+We now present results derived from the fully parameterised and
+integrated model; where we took advantage of the fact that it is a
+closed loop system. This allowed us to present sequences of target
+luminances and allow the model to direct its fovea at the most salient
+target.
 
@@
 
-We investigated the behaviour of the model for saccade sequences.
-In one experiment, we illuminated a fixation
-cross from 0~s until 0.4~s, followed by a target at (0,-10\dg)
-from 0.4~s until 0.8~s. Finally, the fixation was again shown from 0.8~s
-until the end of the simulation at 2~s. This induced a saccade to a
-10\dg~eccentricity, followed by a return saccade back to the
-null point. We noticed some irregularities in the return saccades, which
-though surprisingly accurate, had a significant overshoot.
-More perplexingly, if the target was switched repeatedly between 0\dg~and
-10\dg, second and subsequent \e{outward} saccades also showed this
-overshoot. We found that the cause of these irregularties was the
-lack (in `TModel4') of any mechanism to reset the tonic neurons in the
-SBG after the first saccade. This resulted in TN activity in the left
-channel \e{and also} in the right channel. Interestingly, this ensured
-that, at  least for a few, consecutive out-and-return saccades, the saccade accuracy was
+We investigated the behaviour of the model for saccade sequences.  In
+one experiment, we illuminated a fixation cross from 0~s until 0.4~s,
+followed by a target at (0,-10\dg) from 0.4~s until 0.8~s. Finally,
+the fixation was again shown from 0.8~s until the end of the
+simulation at 2~s. This induced a saccade to a 10\dg~eccentricity,
+followed by a return saccade back to the null point. We noticed some
+irregularities in the return saccades, which though surprisingly
+accurate, had a significant overshoot.  More perplexingly, if the
+target was switched repeatedly between 0\dg~and 10\dg, second and
+subsequent \e{outward} saccades also showed this overshoot. We found
+that the cause of these irregularties was the lack (in `TModel4') of
+any mechanism to reset the tonic neurons in the SBG after the first
+saccade. This resulted in TN activity in the left channel \e{and also}
+in the right channel. Interestingly, this ensured that, at least for a
+few, consecutive out-and-return saccades, the saccade accuracy was
 relatively good, with trajectories resembling experimental data
@@
 additional inhibitory input to the `integrator' component of TModel4,
-driven by the contralateral EBN population, naming the new model `TModel5'.
-Now, when the eye is directed towards an eccentric target which is then
-exchanged with a target at the null point, the EBN activity toward the
-null point will tend to extinguish the TN activity which was holding
-the eye at the eccentric position.
-We verified that none of the single saccade results were affected
-by this modification.
-%
-% This doesn't account for *all* cases where you'd want to remove the TN
-% activity. Imagine a saccade purely UP then a saccade to a location
-% purely RIGHT. You'd need to remove the TN activity on the UP channel,
-% but you'd not be inducing any DOWN with the new target.
-
-Fig.~\ref{outrtn} shows the
-outward and return trajectories produced by the experiment
-with the TN reset mechanism. Panel (a)
-shows the $x$ and $y$ rotation trajectory; panel (b) shows individual
-rotational components of the eye. Fig.~\ref{outrtn}(c) shows
-out and return trajectories for three other saccade targets; horizontal,
-vertical and oblique. The trajectories have characteristic shapes and
-also show some stochastic variation caused by the noise in the model [see
-dashed trajectories in Fig.~\ref{outrtn}(a)].
-
-The return trajectories (magenta lines) showed a
-distinctly different form from the outward trajectories. They overshot
-their destination (the null point) significantly. This resulted from the
-removal of the TN activity which was holding the eye at the eccentric
-target location. Removal of this activity, and thus the static force
-exerted by the corresponding extraocular muscle, meant that the eye
-was subject both to a new muscular force towards the null point
+driven by the contralateral EBN population, naming the new model
+`TModel5'.  Now, when the eye is directed towards an eccentric target
+which is then exchanged with a target at the null point, the EBN
+activity toward the null point will tend to extinguish the TN activity
+which was holding the eye at the eccentric position.  We verified that
+none of the single saccade results were affected by this modification.
+% This doesn't account for *all* cases where you'd want to remove the
+% TN activity. Imagine a saccade purely UP then a saccade to a
+% location purely RIGHT. You'd need to remove the TN activity on the
+% UP channel, but you'd not be inducing any DOWN with the new target.
+
+Fig.~\ref{outrtn} shows the outward and return trajectories produced
+by the experiment with the TN reset mechanism. Panel (a) shows the $x$
+and $y$ rotation trajectory; panel (b) shows individual rotational
+components of the eye. Fig.~\ref{outrtn}(c) shows out and return
+trajectories for three other saccade targets; horizontal, vertical and
+oblique. The trajectories have characteristic shapes and also show
+some stochastic variation caused by the noise in the model [see dashed
+trajectories in Fig.~\ref{outrtn}(a)].
+
+The return trajectories (magenta lines) showed a distinctly different
+form from the outward trajectories. They overshot their destination
+(the null point) significantly. This resulted from the removal of the
+TN activity which was holding the eye at the eccentric target
+location. Removal of this activity, and thus the static force exerted
+by the corresponding extraocular muscle, meant that the eye was
+subject both to a new muscular force towards the null point
 \e{alongside} the restorative spring force of the lengthened rectus
@@
 
-In another experiment, we probed the response of the model to double step
-stimuli of the type described in \cite{becker_analysis_1979}. In that
-work, the response of human subjects was investigated when shown stimuli
-at 15\dg~and 30\dg~eccentricity with variable delay between
-the stimuli. If the smaller eccentricity stimulus was shown first, followed
-by the more distal on the same side of the field of view, this was called
-a `staircase' presentation.
-%If the more distal stimulus preceded the 15\dg~stimulus (again with
-%both in the same hemifield), this was called `pulse undershoot'.
-We carried
-out a `staircase' presentation, shown in Fig.~\ref{doublesteps},
-where our small eccentricity luminance was at 8\dg~and our more
-distal luminance was at 12\dg~(both to the right of centre). We
-found that there was a critical time delay between the luminances
-of about 30~ms. If they were presented with a delay smaller than this
-value, then a single, slightly hypermetric saccade was made. This
-response type is called a \e{final angle response}. A delay greater
-than 30~ms between the stimuli would lead to double step saccades
-(a so-called \e{initial angle response}),
-with the first saccade arriving at 8\dg~(though with greater
-variability than normal), and a second saccade being made
-to a location hypometric of 12\dg~after a pause of about 240~ms.
-Fig.~\ref{doublesteps}(a) shows the mean trajectories from 5 simulations
-of the staircase doublestep presentation alongside the result for a
-single saccade to the final angle of 12\dg. Dash-dot lines show
-$\pm$1 standard deviation about the mean. The corresponding trajectories
-are shown in Fig.~\ref{doublesteps}(b).
-
-Inspection of the activity maps in FEF and SC\_deep (not shown) indicates
-that when
-the 8\dg~target is illuminated for 30~ms or more, the activity
-associated with this target angle is able to dominate the activity,
-hence the execution of a reasonably accurate saccade. The inhibitory
-feedback from the SBG then extinguishes activity in FEF, thalamus and
-SC, which means that a full 200~ms or more is required to allow
-activity in these populations to build up again in order to make the
-smaller saccade from 8\dg~to 12\dg. This is in contrast
-to experimental findings in which the corrective second saccade is
-often executed \e{more quickly} than if it were programmed on its
+In another experiment, we probed the response of the model to double
+step stimuli of the type described in \cite{becker_analysis_1979}. In
+that work, the response of human subjects was investigated when shown
+stimuli at 15\dg~and 30\dg~eccentricity with variable delay between
+the stimuli. If the smaller eccentricity stimulus was shown first,
+followed by the more distal on the same side of the field of view,
+this was called a `staircase' presentation.
+% If the more distal stimulus preceded the 15\dg~stimulus (again with
+% both in the same hemifield), this was called `pulse undershoot'.
+We carried out a `staircase' presentation, shown in
+Fig.~\ref{doublesteps}, where our small eccentricity luminance was at
+8\dg~and our more distal luminance was at 12\dg~(both to the right of
+centre). We found that there was a critical time delay between the
+luminances of about 30~ms. If they were presented with a delay smaller
+than this value, then a single, slightly hypermetric saccade was
+made. This response type is called a \e{final angle response}. A delay
+greater than 30~ms between the stimuli would lead to double step
+saccades (a so-called \e{initial angle response}), with the first
+saccade arriving at 8\dg~(though with greater variability than
+normal), and a second saccade being made to a location hypometric of
+12\dg~after a pause of about 240~ms.  Fig.~\ref{doublesteps}(a) shows
+the mean trajectories from 5 simulations of the staircase doublestep
+presentation alongside the result for a single saccade to the final
+angle of 12\dg. Dash-dot lines show $\pm$1 standard deviation about
+the mean. The corresponding trajectories are shown in
+Fig.~\ref{doublesteps}(b).
+
+Inspection of the activity maps in FEF and SC\_deep (not shown)
+indicates that when the 8\dg~target is illuminated for 30~ms or more,
+the activity associated with this target angle is able to dominate the
+activity, hence the execution of a reasonably accurate saccade. The
+inhibitory feedback from the SBG then extinguishes activity in FEF,
+thalamus and SC, which means that a full 200~ms or more is required to
+allow activity in these populations to build up again in order to make
+the smaller saccade from 8\dg~to 12\dg. This is in contrast to
+experimental findings in which the corrective second saccade is often
+executed \e{more quickly} than if it were programmed on its
 own~\citep{becker_analysis_1979}.
-
-%\subsection{Saccade with distractor} enough!
-
-%Our integrated model allows us to examine the effect of distractor
-%luminances on saccade dynamics. Fig.~\ref{targ_w_distr}(a) shows
-%three horizontal saccades to a
-%target at $\theta_{y}=$-10\dg. The first saccade (blue
-%trajectory) had no distractor luminance, the second saccade (red) was
-%modulated by the appearance of a distractor cross of magnitude 1
-%located at $\theta_{x}=\,$-7\dg, $\theta_{y}=\,$-7\dg.
-%The distractor appeared 0.1~s after the target and
-%persisted for 0.1~s [Fig.~\ref{targ_w_distr}(b)]. The third
-%saccade (green) had conditions identical to the red saccade, but
-%with a brighter distractor luminance, whose magnitude was 2.
-
-%\cmnt{Ok, now saccades can deviate TOWARDS a distractor - particularly
-%if the distractor is closer to the trajectory - see for example
-%~\cite{wang_distractor_2014}. This model doesn't seem to have any
-%mechanism to induce a deviation of trajectory away from the distractor. }
-
-%\subsection{Saccade to twin targets} enough!
 
@@
 neurological systems \e{in concert with} the biomechanical systems
-with which they have evolved in parallel. We hypothesised that by combining
-existing neurophysiological models with an accurate
-model of a musculo-skeletal system, and then `closing the loop' by allowing
-the movements of the virtual muscles to modulate sensory feedback to
-the brain model, shortcomings in the constituent models would be
-revealed, leading to new knowledge. To demonstrate the validity
-of this hypothesis, we built an integrated model and then identified the
+with which they have evolved in parallel. We hypothesised that by
+combining existing neurophysiological models with an accurate model of
+a musculo-skeletal system, and then `closing the loop' by allowing the
+movements of the virtual muscles to modulate sensory feedback to the
+brain model, shortcomings in the constituent models would be revealed,
+leading to new knowledge. To demonstrate the validity of this
+hypothesis, we built an integrated model and then identified the
 modifications which were necessary to give it the ability to make
-accurate movements under one type of stimulus. We then
-examined its behaviour with other stimuli.
-
-% This is probably recapitulation of intro material.
+accurate movements under one type of stimulus. We then examined its
+behaviour with other stimuli.
+
 We chose the oculomotor model as a basis for this study because it has
@@
 musculo-skeletal systems. Furthermore, eye movements fall into several
-well-defined categories, each being controlled by separate
-brain circuits, we were therefore justified in modelling a
-system which produced only saccadic eye movements. Nevertheless, we are
-aware that we did not create a complete model of the system; no treatment
-of the cerebellum was attempted, justified because cerebellum appears to have
-only a minor effect on saccade accuracy \citep{dean_adaptive_2008}, probably correcting
-for slow to medium timescale changes in the physical dynamics of the
-eyeball \citep{dean_learning_1994}.
+well-defined categories, each being controlled by separate brain
+circuits, we were therefore justified in modelling a system which
+produced only saccadic eye movements. Nevertheless, we are aware that
+we did not create a complete model of the system; no treatment of the
+cerebellum was attempted, justified because cerebellum appears to have
+only a minor effect on saccade accuracy \citep{dean_adaptive_2008},
+probably correcting for slow to medium timescale changes in the
+physical dynamics of the eyeball \citep{dean_learning_1994}.
 
@@
 model based on the work of \cite{gancarz_neural_1998}, using this to
-drive the input of a new biomechanical eye model. To achieve the spatial
-transformation from the retinotopic maps of the \ccg~model to the six
-`muscle channel' inputs for the saccadic burst generator, we used
-the mapping of \cite{ottes_visuomotor_1986} to produce parameterised
-weight maps along with an empirically discovered synergy for the torsional
-weight maps. We introduced an additional
+drive the input of a new biomechanical eye model. To achieve the
+spatial transformation from the retinotopic maps of the \ccg~model to
+the six `muscle channel' inputs for the saccadic burst generator, we
+used the mapping of \cite{ottes_visuomotor_1986} to produce
+parameterised weight maps along with an empirically discovered synergy
+for the torsional weight maps. We introduced an additional
 transformation to the brain model to achieve invariant sized hills of
@@
 luminous cross shapes into the eye's frame of reference, given its
-instantaneous rotational state. This component also computed the inverse
-of the mapping from \cite{ottes_visuomotor_1986} to project the view
-retinotopically into the brain model.
-%
-This paper serves to describe how we achieved the integration in
-order to test our hypothesis, and we intend that the material and
-methods section, along with the model code itself, will help others
-to carry out similar studies. However, we wish to devote the majority
-of this discussion to what can be learned from an integrated model
-of a combined brain and biomechanical system, using our oculomotor system
+instantaneous rotational state. This component also computed the
+inverse of the mapping from \cite{ottes_visuomotor_1986} to project
+the view retinotopically into the brain model.
+%
+This paper serves to describe how we achieved the integration in order
+to test our hypothesis, and we intend that the material and methods
+section, along with the model code itself, will help others to carry
+out similar studies. However, we wish to devote the majority of this
+discussion to what can be learned from an integrated model of a
+combined brain and biomechanical system, using our oculomotor system
 as an example.
@@
 to provide a full understanding of the saccadic system. In each case,
-the issue is made clear \e{as a result of the integration}. This is not
-to say that other approaches may not also reveal shortcomings; we will
-see that one of our cases has been independently identified
+the issue is made clear \e{as a result of the integration}. This is
+not to say that other approaches may not also reveal shortcomings; we
+will see that one of our cases has been independently identified
 \citep{groh_effects_2011}.
@@
 maps of \cite{ottes_visuomotor_1986} and \cite{tabareau_geometry_2007}
-resulted in a model which was
-able to produce accurate saccades only along the principle rotational
-axes (Fig.~\ref{errorsurfaceTM3}). Thus, \e{the integration of
-the models} suggested that an additional
-layer was required to achieve accurate saccades for oblique, as well
-as for horizontal and vertical saccades. Although the \e{need} for an
-invariant integral is discussed in \cite{tabareau_geometry_2007} as resulting from
-their theoretical study, the mechanism by which such an invariant
-Gaussian hill is generated is not. By combining the models, we were
-forced to consider this mechanism, and hypothesised that a widening
-projection field would be a candidate mechanism. The results of
-Fig.~\ref{errorsurface} indicate that a substantial improvement
-in accuracy is indeed achieved by this new mechanism.
+resulted in a model which was able to produce accurate saccades only
+along the principle rotational axes
+(Fig.~\ref{errorsurfaceTM3}). Thus, \e{the integration of the models}
+suggested that an additional layer was required to achieve accurate
+saccades for oblique, as well as for horizontal and vertical
+saccades. Although the \e{need} for an invariant integral is discussed
+in \cite{tabareau_geometry_2007} as resulting from their theoretical
+study, the mechanism by which such an invariant Gaussian hill is
+generated is not. By combining the models, we were forced to consider
+this mechanism, and hypothesised that a widening projection field
+would be a candidate mechanism. The results of Fig.~\ref{errorsurface}
+indicate that a substantial improvement in accuracy is indeed achieved
+by this new mechanism.
 
@@
 biomechanics of the eye, as the brain and brainstem model had no
-mechanism to account for the position-dependent restoring forces applied
-by the eye. This question has been addressed by other authors;
+mechanism to account for the position-dependent restoring forces
+applied by the eye. This question has been addressed by other authors;
 \cite{groh_effects_2011} investigates the effect of
-initial eye position on stimulated saccades
-and finds a need for the signal in superior colliculus to be modulated
-by an eye position signal. \cite{ling_effects_2007} shows the existence
-of a position dependent firing rate offset in abducens neurons. Though
-we will not speculate here on the mechanism by which return saccades
-may be made accurate whilst also resetting the activity of tonic
-neurons in the SBG, it is interesting that in the model in which we
-omitted to reset TN activity (TModel4), we obtained relatively accurate
-out-and-return saccades which closely resembled experimental data.
-We suggest that residual activity in TN populations may offer an
-explanation for how the restorative force exerted by
-the elastic oculomotor muscles is compensated for. A comparison of
-this idea with that of \cite{groh_effects_2011} (that there is a
-modulation, from a brainstem signal, of the SC readout) would make
-a subject for a future study. Although these existing studies have
-highlighted this issue, the inaccurate return saccades which the
-model makes from eccentric starting positions provide a clear example
-of the way in which integrating known models into a closed-loop system
-can highlight deficiencies in the model.
+initial eye position on stimulated saccades and finds a need for the
+signal in superior colliculus to be modulated by an eye position
+signal. \cite{ling_effects_2007} shows the existence of a position
+dependent firing rate offset in abducens neurons. Though we will not
+speculate here on the mechanism by which return saccades may be made
+accurate whilst also resetting the activity of tonic neurons in the
+SBG, it is interesting that in the model in which we omitted to reset
+TN activity (TModel4), we obtained relatively accurate out-and-return
+saccades which closely resembled experimental data.  We suggest that
+residual activity in TN populations may offer an explanation for how
+the restorative force exerted by the elastic oculomotor muscles is
+compensated for. A comparison of this idea with that
+of \cite{groh_effects_2011} (that there is a modulation, from a
+brainstem signal, of the SC readout) would make a subject for a future
+study. Although these existing studies have highlighted this issue,
+the inaccurate return saccades which the model makes from eccentric
+starting positions provide a clear example of the way in which
+integrating known models into a closed-loop system can highlight
+deficiencies in the model.
 
@@
 The third issue raised by the integration of the component models of
-the saccadic system has, like the return saccades, to do with resetting
-activity. In this case, rather than the reset of activity in the TN
-population in the brainstem, it is the question of how the activity
-in the \e{brain} model should be reset after each saccade. When a target
-luminance is projected onto the World population in the model, this
-induces activity which `reverberates' in loops through FEF, basal
-ganglia, SC and thalamus. The brainstem contains a mechanism to limit
-the timescale of a saccade (inhibitory feedback from EBN, via IBN to
-LLBN; see Fig.~\ref{sbg}). However, if the activity in SC is not
-reset, then following the completion of the first saccade, a series
-of subsequent `staircase' saccades will be executed. There needs to
-be a mechanism to extinguish activity in SC, but also in FEF and
-thalamus, as activity in either of these populations can build up
-and eventually cause repeat activity in SC and another saccade. We
-added hypothetical inhibitory feedback connections to our model,
-such that the IBN populations in the SBG would inhibit activity in
-FEF, thalamus and SC\_deep (Fig.~\ref{sbg}), preventing the
-occurrence of staircase saccades.
+the saccadic system has, like the return saccades, to do with
+resetting activity. In this case, rather than the reset of activity in
+the TN population in the brainstem, it is the question of how the
+activity in the \e{brain} model should be reset after each
+saccade. When a target luminance is projected onto the World
+population in the model, this induces activity which `reverberates' in
+loops through FEF, basal ganglia, SC and thalamus. The brainstem
+contains a mechanism to limit the timescale of a saccade (inhibitory
+feedback from EBN, via IBN to LLBN; see Fig.~\ref{sbg}). However, if
+the activity in SC is not reset, then following the completion of the
+first saccade, a series of subsequent `staircase' saccades will be
+executed. There needs to be a mechanism to extinguish activity in SC,
+but also in FEF and thalamus, as activity in either of these
+populations can build up and eventually cause repeat activity in SC
+and another saccade. We added hypothetical inhibitory feedback
+connections to our model, such that the IBN populations in the SBG
+would inhibit activity in FEF, thalamus and SC\_deep (Fig.~\ref{sbg}),
+preventing the occurrence of staircase saccades.
 
@@
 `double-step stimuli' reveals a problem with this scheme. We found
-that when double-step stimuli were presented (where an initial
-target at 8\dg~was replaced with a 12\dg~target after 30 or 40~ms)
-and a double saccade was made [Fig.~\ref{doublesteps}(a), black
-lines] the second saccade latency was \e{longer} even than the
-initial saccade. This contrasts with \cite{becker_analysis_1979} who
-find that second, corrective saccades occur with \e{shorter} latencies.
-This suggests that the inhibitory reset signal implemented in
-this model is too strong or has the wrong timescales. This issue
-highlights the fact that connections \e{between} component models
-are quite as important as the connections within each model.
+that when double-step stimuli were presented (where an initial target
+at 8\dg~was replaced with a 12\dg~target after 30 or 40~ms) and a
+double saccade was made [Fig.~\ref{doublesteps}(a), black lines] the
+second saccade latency was \e{longer} even than the initial
+saccade. This contrasts with \cite{becker_analysis_1979} who find that
+second, corrective saccades occur with \e{shorter} latencies.  This
+suggests that the inhibitory reset signal implemented in this model is
+too strong or has the wrong timescales. This issue highlights the fact
+that connections \e{between} component models are quite as important
+as the connections within each model.
 
@@
 % Cerebellum omitted
-The omission of the cerebellum will not have escaped the reader's notice.
-Whilst many of the nuclei known to be involved in the production of
-saccadic eye movements are incorporated within the model, the cerebellum
-is not. The cerebellum is known to play an important r\^ole in saccade
-programming
+The omission of the cerebellum will not have escaped the reader's
+notice.  Whilst many of the nuclei known to be involved in the
+production of saccadic eye movements are incorporated within the
+model, the cerebellum is not. The cerebellum is known to play an
+important r\^ole in saccade programming
 \citep{dean_learning_1994, schweighofer_model_1996,quaia_extent_2000,kleine_saccade-related_2003}.
-It may be able to completely replace the functionality of the colliculus
-when lesioned \citep{aizawa_reversible_1998,lefevre_distributed_1998}.
-However, this r\^ole is typically considered to be one of accuracy tuning
+It may be able to completely replace the functionality of the
+colliculus when
+lesioned \citep{aizawa_reversible_1998,lefevre_distributed_1998}.
+However, this r\^ole is typically considered to be one of accuracy
+tuning
 \citep{barash_saccadic_1999,dean_learning_1994}; operating as an additive
-model. Furthermore, saccades made by individuals with cerebellar ataxias
-perform with only moderate loss of saccade accuracy
+model. Furthermore, saccades made by individuals with cerebellar
+ataxias perform with only moderate loss of saccade accuracy
 \citep{barash_saccadic_1999,federighi_differences_2011}. Because we
 did not address learning in our model, and because our aim was to
-demonstrate the utility of integrating brain with biomechanics in order
-to highlight deficiencies, we considered the omission of the cerebellar
-nuclei acceptable in the present work.
+demonstrate the utility of integrating brain with biomechanics in
+order to highlight deficiencies, we considered the omission of the
+cerebellar nuclei acceptable in the present work.
 
@@
 Saccade duration is of interest in models which produce two (or three)
-dimensional saccades, because the dynamics of a saccade follow well known
-relationships with the saccade eccentricity, regardless of the saccade
-angle. This causes a problem for models (such as the present one) for which
-some of the dynamic behaviour is generated within orthogonal components.
-For example, saccade duration increases with target eccentricity. A
-10\dg~eccentricity oblique (45\dg~up and right) saccade is composed
-(approximately) of a 7\dg~upwards component and a 7\dg~rightwards
-component. If the component based model is responsible for the dynamics,
-then the 10\dg~oblique saccade would be expected to have the dynamics
-of a 7\dg~up or 7\dg~right saccade. This is not found in practice, and
-the components are said to have been stretched, hence the name for this
-effect `component stretching'. The \cite{gancarz_neural_1998} model is
-reported to take account of the component stretching effect via the OPN
-neuron population. We did not find this effect in our implementation of
-the model; the duration of oblique saccades at a given eccentricity was
+dimensional saccades, because the dynamics of a saccade follow well
+known relationships with the saccade eccentricity, regardless of the
+saccade angle. This causes a problem for models (such as the present
+one) for which some of the dynamic behaviour is generated within
+orthogonal components.  For example, saccade duration increases with
+target eccentricity. A 10\dg~eccentricity oblique (45\dg~up and right)
+saccade is composed (approximately) of a 7\dg~upwards component and a
+7\dg~rightwards component. If the component based model is responsible
+for the dynamics, then the 10\dg~oblique saccade would be expected to
+have the dynamics of a 7\dg~up or 7\dg~right saccade. This is not
+found in practice, and the components are said to have been stretched,
+hence the name for this effect `component
+stretching'. The \cite{gancarz_neural_1998} model is reported to take
+account of the component stretching effect via the OPN neuron
+population. We did not find this effect in our implementation of the
+model; the duration of oblique saccades at a given eccentricity was
 always substantially different from the duration of the corresponding
@@
 complicated interplay between the dynamics of the superior colliculus
-driving the dynamic system of the SBG, we feel this is outside the scope
-of the current work and a subject for a future paper.
+driving the dynamic system of the SBG, we feel this is outside the
+scope of the current work and a subject for a future paper.
 
 % Significance of this work.
-This work represents a step forward in the modelling of neuromuscular systems,
-not because it significantly advances any of the constituent models, but
-because it \e{integrates} the models into a complete, \e{behaving} system.
-This is not the first integrated brain model composed of separately developed
-components. The works of \cite{nguyen_saccade_2014} and
+This work represents a step forward in the modelling of neuromuscular
+systems, not because it significantly advances any of the constituent
+models, but because it \e{integrates} the models into a
+complete, \e{behaving} system.  This is not the first integrated brain
+model composed of separately developed components. The works
+of \cite{nguyen_saccade_2014} and
 \cite{thurat_biomimetic_2015} are both based
-on an example of a brain model which drives a simple, second order model of the
-eye. \cite{dewolf_spiking_2016} describes a reach model which integrates models
-of cortex and cerebellum to drive a two degree-of-freedom arm model. Both of
-these example systems nevertheless operate using `curated' inputs supplied
-by the modeller.
-
-In contrast, the current work allows the state of the system to determine the
-input delivered to the model. The modeller only curates the state of the world
-at each time point, but the actual input to the model depends on the eye's
-rotational state.
-This is, to our knowledge, the first model which integrates the brain with an
-accurate biophysical system and closes the loop in this way, enabling the
-system to reproduce behaviour.
-As such, it offers a platform for testing more complex saccadic behaviour such as
-antisaccades or saccades in the presence of distractor stimuli. We believe
-that by building closed loop systems which express behaviour, we, and others
-will develop a new field of \e{computational neurobehaviour}, which will share
-themes from neuroscience, artificial intelligence, decision science and embodied
-robotics.
-
-% Frontiers requires figures to be submitted individually, in the same
-% order as they are referred to in the manuscript. Figures will then
-% be automatically embedded at the bottom of the submitted
-% manuscript. Kindly ensure that each table and figure is mentioned in
-% the text and in numerical order. Permission must be obtained for use
-% of copyrighted material from other sources (including the
-% web). Please note that it is compulsory to follow figure
-% instructions. Figures which are not according to the guidelines will
-% cause substantial delay during the production process.
-
-% To take part in the Resource Identification Initiative, please cite
-% antibodies, genetically modified organisms, software tools, data,
-% databases and services using the corresponding catalog number and
-% RRID in your current manuscript. For more information about the
-% project and for steps on how to search for an RRID, please click
-% \href{http://www.frontiersin.org/files/pdf/letter_to_author.pdf}.
+on an example of a brain model which drives a simple, second order
+model of the eye. \cite{dewolf_spiking_2016} describes a reach model
+which integrates models of cortex and cerebellum to drive a two
+degree-of-freedom arm model. Both of these example systems
+nevertheless operate using `curated' inputs supplied by the modeller.
+
+In contrast, the current work allows the state of the system to
+determine the input delivered to the model. The modeller only curates
+the state of the world at each time point, but the actual input to the
+model depends on the eye's rotational state.  This is, to our
+knowledge, the first model which integrates the brain with an accurate
+biophysical system and closes the loop in this way, enabling the
+system to reproduce behaviour.  As such, it offers a platform for
+testing more complex saccadic behaviour such as antisaccades or
+saccades in the presence of distractor stimuli. We believe that by
+building closed loop systems which express behaviour, we, and others
+will develop a new field of \e{computational neurobehaviour}, which
+will share themes from neuroscience, artificial intelligence, decision
+science and embodied robotics.
 
@@
 \section*{Author Contributions}
-%When determining authorship the following criteria should be observed:
-%•	Substantial contributions to the conception or design of the work; or the acquisition, analysis, or interpretation of data for the work; AND
-%•	Drafting the work or revising it critically for important intellectual content; AND
-%•	Final approval of the version to be published ; AND
-%•	Agreement to be accountable for all aspects of the work in ensuring that questions related to the accuracy or integrity of any part of the work are appropriately investigated and resolved.
-%Contributors who meet fewer than all 4 of the above criteria for authorship should not be listed as authors, but they should be acknowledged. (http://www.icmje.org/roles_a.html)
 
@@
 KM developed the biomechanical eye model. SJ wrote the manuscript; SA,
-AB, KG and KM contributed to the manuscript. KG conceived the
-project.
+AB, KG and KM contributed to the manuscript. KG conceived the project.
 
@@
 The model specification, results and all code required to reproduce
-the results of this work are available
-at: https://github.com/ABRG-Models/OMM\_NeuroMuscular
+the results of this work are available at:
+https://github.com/ABRG-Models/OMM\_NeuroMuscular
 
@@
 
-%%% Upload the *bib file along with the *tex file and PDF on
-%%% submission if the bibliography is not in the main *tex file
-
 \section*{Figures}
-
-%%% Use this if adding the figures directly in the mansucript, if so,
-%%% please remember to also upload the files when submitting your
-%%% article There is no need for adding the file termination, as long
-%%% as you indicate where the file is saved. In the examples below the
-%%% files (logo1.jpg and logo2.eps) are in the Frontiers LaTeX folder
-%%% If using *.tif files convert them to .jpg or .png
-
-%\begin{figure}[h!]
-%\begin{center}
-%\includegraphics[width=10cm]{logo1.jpg}% This is a *.jpg file
-%\end{center}
-% \textbf{\refstepcounter{figure}\label{01} Figure \arabic{figure}.}{ Enter the caption for your figure here.  Repeat as  necessary for each of your figures }
-%\end{figure}
-
-%\begin{figure}
-%\begin{center}
-%\includegraphics[width=10cm]{logo2}% This is an *.eps file
-%\end{center}
-%\textbf{\refstepcounter{figure}\label{02} Figure \arabic{figure}.}{ Enter the caption for your figure here.  Repeat as  necessary for each of your figures }
-%\end{figure}
-
-%%% If you don't add the figures in the LaTeX files, please upload
-%%% them when submitting the article.
-
-%%% Frontiers will add the figures at the end of the provisional pdf
-%%% automatically
-
-%%% The use of LaTeX coding to draw Diagrams/Figures/Structures should
-%%% be avoided. They should be external callouts including graphics.
-
-%\begin{figure}[htb!]
-%\begin{center}
-%\includegraphics[width=0.9\textwidth]{./figures/intro_graphic.png}
-%\end{center}
-%\textbf{\refstepcounter{figure}\label{intro_graphic} Figure \arabic{figure}.}
-%{ \textbf{intro\_graphic} An isolated brain model. Crafted inputs
-%are introduced into one of the model's n state variables. The output
-%of another of the state variables implies behavioural change or
-%onset.}
-%\end{figure}
 
@@
 the BRAHMS system. Most of the process is defined within the scripts
-which make up \stob, but the hand-written components must be
-manually compiled and installed within the BRAHMS Namespace, allowing
-the BRAHMS executable to locate them at runtime. c) The red box shows
-the resulting BRAHMS system ready to be executed by the BRAHMS
+which make up \stob, but the hand-written components must be manually
+compiled and installed within the BRAHMS Namespace, allowing the
+BRAHMS executable to locate them at runtime. c) The red box shows the
+resulting BRAHMS system ready to be executed by the BRAHMS
 executable. In practice, this call is made by \stob.}
@@
 \textbf{\refstepcounter{figure}\label{brain_model} Figure \arabic{figure}.}
-{ The brain model. This is the SpineCreator
-`network layer' view of the model. Each box represents a neural
-population with 2500 elements, arranged in a 50$\times$50 grid. The
-SpineML component name is printed on the bottom right corner of each
-population box and the population name is at the top. The overall
-connectivity between populations is represented by the projection
-arrows with the colour indicating the connectivity scheme (one-to-one
-connections are red, Gaussian kernel connections are dark blue and so
-on). Excitatory connections have arrowheads and inhibitory connections
-have circles, although for details of the behaviour of the
-connections, the weight-update and post-synapse components must be
-studied. Briefly, the model comprises a \e{World} population, into
-which a retinotopically organised view of the world is
-introduced. This information is passed into cortical populations (FEF)
-and subcortical populations (SC) via a simple model of the
-retina. These feed a cortico-thalamo-basal ganglia loop, which selects
-which region of the deep layer of superior colliculus should be
-disinhibited, allowing activity to build up therein. The five
+{ The brain model. This is the SpineCreator `network layer' view of
+the model. Each box represents a neural population with 2500 elements,
+arranged in a 50$\times$50 grid. The SpineML component name is printed
+on the bottom right corner of each population box and the population
+name is at the top. The overall connectivity between populations is
+represented by the projection arrows with the colour indicating the
+connectivity scheme (one-to-one connections are red, Gaussian kernel
+connections are dark blue and so on). Excitatory connections have
+arrowheads and inhibitory connections have circles, although for
+details of the behaviour of the connections, the weight-update and
+post-synapse components must be studied. Briefly, the model comprises
+a \e{World} population, into which a retinotopically organised view of
+the world is introduced. This information is passed into cortical
+populations (FEF) and subcortical populations (SC) via a simple model
+of the retina. These feed a cortico-thalamo-basal ganglia loop, which
+selects which region of the deep layer of superior colliculus should
+be disinhibited, allowing activity to build up therein. The five
 populations comprising the basal ganglia are enclosed in a grey
@@
 \textbf{\refstepcounter{figure}\label{fig:mapping} Figure \arabic{figure}.}
-{ Representative mapping from eye's frame of
-reference in Cartesian co-ordinates to retinotopic co-ordinates. (a) The
-mapping of luminances in the eye's frame of reference. The world input
-is pre-defined by a JSON configuration file. Luminance position, size
-and shape can be defined in this file, along with the times at which
+{ Representative mapping from eye's frame of reference in Cartesian
+co-ordinates to retinotopic co-ordinates. (a) The mapping of
+luminances in the eye's frame of reference. The world input is
+pre-defined by a JSON configuration file. Luminance position, size and
+shape can be defined in this file, along with the times at which
 luminances appear and disappear. The worldDataMaker.cpp code computes
@@
 the luminances. Here, there are two cross shaped luminances spanning
-10\dg, one of value 0.8 at the fixation point (0,0) and one of
-value 0.5 at a peripheral position (0,-12\dg). Note that these
-crosses have the same `bar width' of 2\dg~as the crosses
-used in the simulations, but their span of 10\dg~is greater
-than the 6\dg~used in the simulations, to make these
-images clearer. (b) The locations of
-the luminances in the eye's frame of reference are then converted into
+10\dg, one of value 0.8 at the fixation point (0,0) and one of value
+0.5 at a peripheral position (0,-12\dg). Note that these crosses have
+the same `bar width' of 2\dg~as the crosses used in the simulations,
+but their span of 10\dg~is greater than the 6\dg~used in the
+simulations, to make these images clearer. (b) The locations of the
+luminances in the eye's frame of reference are then converted into
 retinotopic co-ordinates, with centrally located luminances being
@@
 neuron populations. The colour map makes it possible to distinguish
-between the two crosses. (c) The FEF\_add\_noise populations adds a level
-of noise to the signal representing processing of the signal in visual
-cortex. (d) A Gaussian projection from FEF\_add\_noise to FEF further
-blurs the activity in FEF. FEF is the input to the basal ganglia and
-one input to superior colliculus.}
+between the two crosses. (c) The FEF\_add\_noise populations adds a
+level of noise to the signal representing processing of the signal in
+visual cortex. (d) A Gaussian projection from FEF\_add\_noise to FEF
+further blurs the activity in FEF. FEF is the input to the basal
+ganglia and one input to superior colliculus.}
 \end{figure}
@@
 \textbf{\refstepcounter{figure}\label{sbg} Figure \arabic{figure}.}
-{ One pair of channels of the saccadic burst
-generator (SBG) for left (cyan) or right (green) movements. Collicular
-activity in SC\_avg excites the channels via SBG weight maps. Each box
-represents a neural population and shows the population name, the
-number of neural elements (here 2500 or 1) and the SpineML component
-name; \e{LIN} for Leaky integrator or \e{integrator}. Key: LLBN:
-Long lead burst neurons; IBN: Inhibitory burst neurons; OPN: Omnipause
-neurons; EBN: Excitatory burst neurons; TN: Tonic neurons; MN:
-Motoneurons.}
+{ One pair of channels of the saccadic burst generator (SBG) for left
+(cyan) or right (green) movements. Collicular activity in SC\_avg
+excites the channels via SBG weight maps. Each box represents a neural
+population and shows the population name, the number of neural
+elements (here 2500 or 1) and the SpineML component name; \e{LIN} for
+Leaky integrator or \e{integrator}. Key: LLBN: Long lead burst
+neurons; IBN: Inhibitory burst neurons; OPN: Omnipause neurons; EBN:
+Excitatory burst neurons; TN: Tonic neurons; MN: Motoneurons.}
 \end{figure}
@@
 \textbf{\refstepcounter{figure}\label{scdeep} Figure \arabic{figure}.}
-{ Showing the additional deep layer of superior colliculus
-(SC\_deep2) and the output layer (SC\_avg, named for the fact that in an earlier
-version of the model, it received the output of the centroid of SC\_deep).
-The widening Gaussian projection is shown as the arrow between SC\_deep
-and SC\_deep2.}
+{ Showing the additional deep layer of superior colliculus (SC\_deep2)
+and the output layer (SC\_avg, named for the fact that in an earlier
+version of the model, it received the output of the centroid of
+SC\_deep).  The widening Gaussian projection is shown as the arrow
+between SC\_deep and SC\_deep2.}
 \end{figure}
@@
 \textbf{\refstepcounter{figure}\label{sacc_vs_targ} Figure \arabic{figure}.}
-{ Accuracy at different target eccentricities for fixation luminance 0.2 and target luminance 0.3.}
+{ Accuracy at different target eccentricities for fixation luminance
+0.2 and target luminance 0.3.}
 \end{figure}
@@
 \textbf{\refstepcounter{figure}\label{weightmaps} Figure \arabic{figure}.}
-{ Weight maps for the connections between the
-output layer of superior colliculus and the six long lead burst
-neurons of the saccadic burst generator model. Each map increases
-exponentially with increasing $r$, multiplied by cosine($\phi$) about
-its `active' axis. \cmnt{Check whether Left \& Right are wrong way round}}
+{ Weight maps for the connections between the output layer of superior
+colliculus and the six long lead burst neurons of the saccadic burst
+generator model. Each map increases exponentially with increasing $r$,
+multiplied by cosine($\phi$) about its `active' axis. \cmnt{Check
+whether Left \& Right are wrong way round}}
 \end{figure}
@@
 \textbf{\refstepcounter{figure}\label{errorsurfaceTM3} Figure \arabic{figure}.}
-{ The end-point error surface for the original,
-na\"ive model (TModel3). a) The
-ratio of the magnitudes of the total error vector and the target
-vector, expressed as a percentage. b) The ratio of the magnitude
-of the $x$ component of the error vector to the magnitude of the
-target vector, expressed as a percentage. c) As (b) but for the
-$y$ component. d) As (b), for $z$ component. All colour maps are
-shown with the same scale. The target rotations, $\theta_{x}^t$ and
+{ The end-point error surface for the original, na\"ive model
+(TModel3). a) The ratio of the magnitudes of the total error vector
+and the target vector, expressed as a percentage. b) The ratio of the
+magnitude of the $x$ component of the error vector to the magnitude of
+the target vector, expressed as a percentage. c) As (b) but for the
+$y$ component. d) As (b), for $z$ component. All colour maps are shown
+with the same scale. The target rotations, $\theta_{x}^t$ and
 $\theta_{y}^t$ are denoted `Target X' and `Target Y' in the figure.}
@@
 \textbf{\refstepcounter{figure}\label{errorsurface} Figure \arabic{figure}.}
-{ The end-point error surface for the model
-in which a widening projection field was added to the model of the
-superior colliculus. a) The
-ratio of the magnitudes of the total error vector and the target
-vector, expressed as a percentage. b) The ratio of the magnitude
-of the $x$ component of the error vector to the magnitude of the
-target vector, expressed as a percentage. c) As (b) but for the
-$y$ component. d) As (b), for $z$ component. All colour maps are
-shown with the same scale. The target rotations, $\theta_{x}^t$ and
+{ The end-point error surface for the model in which a widening
+projection field was added to the model of the superior colliculus. a)
+The ratio of the magnitudes of the total error vector and the target
+vector, expressed as a percentage. b) The ratio of the magnitude of
+the $x$ component of the error vector to the magnitude of the target
+vector, expressed as a percentage. c) As (b) but for the $y$
+component. d) As (b), for $z$ component. All colour maps are shown
+with the same scale. The target rotations, $\theta_{x}^t$ and
 $\theta_{y}^t$ are denoted `Target X' and `Target Y' in the figure.
@@
 \textbf{\refstepcounter{figure}\label{outmany} Figure \arabic{figure}.}
-{ Representative single saccades. a) Trajectories
-from 9 saccades to a single target at 9 different locations. In each
-case, a fixation cross luminance of magnitude 0.2 was displayed at
-(0,0), the start position of the eye, until time 0.4~s. The target
-luminance, magnitude 0.3 was illuminated at time 0.4~s. Trajectory
-shape is dependent on the target position, and there is a variable
-amount of error in the end-points achieved by the model. Colour is
-used in this diagram as an aid to distinguishing different saccades
-and their targets; for a given saccade, the target location is given
-by the cross of the same colour closest to the end of the
-trajectory. b) The three rotational components of the `blue' saccade,
-to target location (-7,-7). c) The three rotational components of the
-`red' saccade, to target location (0,-10).}
+{ Representative single saccades. a) Trajectories from 9 saccades to a
+single target at 9 different locations. In each case, a fixation cross
+luminance of magnitude 0.2 was displayed at (0,0), the start position
+of the eye, until time 0.4~s. The target luminance, magnitude 0.3 was
+illuminated at time 0.4~s. Trajectory shape is dependent on the target
+position, and there is a variable amount of error in the end-points
+achieved by the model. Colour is used in this diagram as an aid to
+distinguishing different saccades and their targets; for a given
+saccade, the target location is given by the cross of the same colour
+closest to the end of the trajectory. b) The three rotational
+components of the `blue' saccade, to target location (-7,-7). c) The
+three rotational components of the `red' saccade, to target location
+(0,-10).}
 \end{figure}
@@
 \textbf{\refstepcounter{figure}\label{lat_vs_all} Figure \arabic{figure}.}
-{ Exploring saccade latencies. a) Latency to first
-movement as a function of target eccentricity for horizontal targets. b) Latency
-vs. eccentricity for vertical targets. c) Latency vs. gap at three different
-luminance values. d) The effect of the dopamine parameter on saccade latencies
-in gap, step and overlap conditions, for two different target luminances.
-e) Saccade vs. luminance showing gradual transition between reflexive and
-express behaviour.
+{ Exploring saccade latencies. a) Latency to first movement as a
+function of target eccentricity for horizontal targets. b) Latency
+vs. eccentricity for vertical targets. c) Latency vs. gap at three
+different luminance values. d) The effect of the dopamine parameter on
+saccade latencies in gap, step and overlap conditions, for two
+different target luminances.  e) Saccade vs. luminance showing gradual
+transition between reflexive and express behaviour.
 %f) Saccade duration vs. saccade eccentricity for horizontal
@@
 \textbf{\refstepcounter{figure}\label{outrtn} Figure \arabic{figure}.}
-{ There and back - a saccade to a target, followed by
-return to
-the original fixation. a) Out and return saccade to a target at (0,-10\dg)
-b) Rotational components of the saccade shown in (a). c) Outward and return
-trajectories for the saccade shown in (a) alongside saccades to three other
-targets.}
+{ There and back - a saccade to a target, followed by return to the
+original fixation. a) Out and return saccade to a target at (0,-10\dg)
+b) Rotational components of the saccade shown in (a). c) Outward and
+return trajectories for the saccade shown in (a) alongside saccades to
+three other targets.}
 \end{figure}
@@
 \textbf{\refstepcounter{figure}\label{doublesteps} Figure \arabic{figure}.}
-{ Double steps. The effect of illuminating a first target
-at 8\dg~or 12\dg, followed by a second target at 12\dg~or 8\dg. a) Horizontal
-rotation of the eye plotted vs.~time for a saccade to the 12\dg~target only (red),
-and to an 8\dg~target at 0.4~s followed by a 12\dg~target after 30~ms (blue) or
-40~ms (black). The timings are indicated by vertical lines. When the second
-target is presented up to 30~ms after the initial target, the initial target
-has not had time to dominate the output saccade and a saccade to a location
-close to the second target is made. If the delay is 40~ms or more, the activity
-from the initial target has time to cause a built up of actiivty in SC\_deep
-and an initial saccade close to the first target is made, followed, after a
-longer than usual latency period, with a second saccade closer to the second
-target. In this graph, the mean of five separate simulations is plotted along
-with $\pm$1 standard deviation around the mean. b) The $\theta_{x}$/$\theta_{y}$
-trajectories corresponding to the data presented in (a).}
+{ Double steps. The effect of illuminating a first target at 8\dg~or
+12\dg, followed by a second target at 12\dg~or 8\dg. a) Horizontal
+rotation of the eye plotted vs.~time for a saccade to the 12\dg~target
+only (red), and to an 8\dg~target at 0.4~s followed by a 12\dg~target
+after 30~ms (blue) or 40~ms (black). The timings are indicated by
+vertical lines. When the second target is presented up to 30~ms after
+the initial target, the initial target has not had time to dominate
+the output saccade and a saccade to a location close to the second
+target is made. If the delay is 40~ms or more, the activity from the
+initial target has time to cause a built up of actiivty in SC\_deep
+and an initial saccade close to the first target is made, followed,
+after a longer than usual latency period, with a second saccade closer
+to the second target. In this graph, the mean of five separate
+simulations is plotted along with $\pm$1 standard deviation around the
+mean. b) The $\theta_{x}$/$\theta_{y}$ trajectories corresponding to
+the data presented in (a).}
 \end{figure}
 
-%\begin{figure}[htb!]
-%\begin{center}
-%\includegraphics[width=0.8\textwidth]{./figures/targ_w_distr.png}
-%\end{center}
-%\textbf{\refstepcounter{figure}\label{targ_w_distr} Figure \arabic{figure}.}
-%{ \textbf{targ\_w\_distr} Effect of a distractor on single saccade.}
-%\end{figure}
-
 \end{document}

### 2017-11-08 papers/integration/omm_integ.tex
Adds changes based on Reviewer 1's comments on Q6, INTRODUCTION

@@
 biomechanics \e{and} sensory feedback, we sought to extend our
-previous work modelling the oculomotor system.  The existing
+previous work modelling the oculomotor system by adding a virtual,
+biomechanical eye model able to make physically realistic
+movements. The rotational state of the eye would then determine how
+visual features in the virtual world were projected back into the
+brain model.
+%
+The existing
 model \citep{cope_basal_2017} is already able to capture sensory input
@@
 its movements can be specified with only three degrees of freedom,
-making it one of the simplest neuro-muscular system in the body.
+making it one of the simplest neuro-muscular systems in the body.
 %
@@
 \citep{hepp_spatio-temporal_1983,dorris_neuronal_1997,mcpeek_competition_2003,vokoun_circuit_2011}.
-Furthermore, in the context of building \e{behaving} systems a
+Furthermore, in the context of building \e{behaving} systems, a
 necessary part of any model for which the behaviour requires visual
@@
 \citep{tipper_reaching_2001} suggesting a close relationship between these
-neural systems. Building the simplest, behaving oculomotor system will
+neural systems. Building a behaving oculomotor system will
 therefore assist future computational neurobehavioural modelling
-efforts.
+efforts that involve reaching.
 
@@
 Activity within the superior colliculus then excites neurons in the
-pons, medulla and rostral mid-brain \citep{sparks_brainstem_2002} and
-then through channels to the motor neurons which innervate the
-extraocular muscles
+pons, medulla and rostral mid-brain \citep{sparks_brainstem_2002}.
+and finally the motor neurons which innervate the extraocular muscles
 \citep{fuchs_firing_1970,sparks_brainstem_2002}. This direct pathway
@@
 comprehensive review, see \cite{girard_brainstem_2005}. Models of
-individual systems have been proposed for brainstem
+individual subsystems have been proposed for brainstem
 \citep{robinson_oculomotor_1975,scudder_new_1988,gancarz_neural_1998},
@@
 More recently, combined models have also been developed incorporating
-sensory input \citep{cope_basal_2017} and driving simple physical
-plants representing the eye
+sensory input \citep{cope_basal_2017} and driving a second order
+differential equation representing the eye
 \citep{tabareau_geometry_2007,nguyen_saccade_2014,thurat_biomimetic_2015}.
@@
 biomechanical modelling framework OpenSim.  These will be described
-below, but first we will give a description of the co-ordinate systems
-and the modelling framework used.
+below, along with a review of the \ccg~model, but first we will give a
+description of the co-ordinate systems and the modelling framework
+used.
 
@@
 LINlinear. They differ in that they have no shunting inhibition. They
-are used in to model medium spiny neuron (MSN) populations in the
+are used to model medium spiny neuron (MSN) populations in the
 striatum. As they model the fact that most MSN neurons fall into two
@@
 connectivity outlined in \cite{gancarz_neural_1998}. The SBG network
-for two of the model's six channels is shown in
-Fig.~\ref{sbg}. Activity from the output layer of superior colliculus
+for two of the model's six channels is shown in Fig.~\ref{sbg}. We use
+the word `channel' to mean a set of populations of neurons which are
+involved in actuating a single extraocular muscle). Activity from the
+output layer of superior colliculus
+%
 (SC\_avg) is fed into each channel, which sums the activity it

### 2017-11-08 papers/integration/omm_integ.tex
WIP on Reviewer 1's comments, along with a copy of my responses in comments.txt

@@
 
-To the \ccg~model, we added a rate-coded brainstem model (a `saccadic
-burst generator') and a biomechanical eye, implemented using the
-biomechanical modelling framework OpenSim.  These will be described
-below, along with a review of the \ccg~model, but first we will give a
-description of the co-ordinate systems and the modelling framework
-used.
+To the \ccg~model, we added a brainstem model and a biomechanical
+eye model. The rate-coded brainstem model was taken from the
+literature~\cite{gancarz_neural_1998} as the best-of-breed saccadic
+burst generator~\cite{girard_brainstem_2005}.  The biomechanical eye
+was implemented using the biomechanical modelling framework OpenSim.
+These will be described below, along with a review of the \ccg~model,
+but first we will give a description of the co-ordinate systems and
+the modelling framework used.
 
@@
 (TNs).  The firing rate of the motor neuron defines the amount of
-force applied to the eye by that muscle.  Thus, the size of the `bump'
+force applied to the eye by that muscle.  Thus, the integral of the `bump'
 defines how far the eye moves in that channel's direction.  The gain
@@
 target was close to the ideal straight line---see
-Fig.~\ref{sacc_vs_targ}(a) \& (c). We applied the same parameters to
+Fig.~\ref{sacc_vs_targ}(a) \& (b). We applied the same parameters to
 both directions of each channel; $i_{up} = i_{down} = 0.00195$,
@@
 generator model. Each map increases exponentially with increasing $r$,
-multiplied by cosine($\phi$) about its `active' axis. \cmnt{Check
-whether Left \& Right are wrong way round}}
+multiplied by cosine($\phi$) about its `active' axis.}
 \end{figure}

### 2017-11-09 papers/integration/omm_integ.tex
Adds reviewer colouring to review changes (nice) plus additional prose about channels

@@
 \usepackage{gensymb} % For \degree
+\usepackage[usenames, dvipsnames]{color}
 
@@
 
+% Use colour to indicate changes made following review. Can be
+% set to this 'black' colour prior to final publication:
+\newcommand{\black}{\textcolor{black}}
+% Colour for reviewer 1 changes:
+\newcommand{\rvwcolour}{\textcolor{OrangeRed}}
+% Colour for reviewer 2 changes:
+\newcommand{\rvwcolourtwo}{\textcolor{Cerulean}}
+% Commands to use in the text. Change 'rvwcolour/rvwcolourtwo' to
+% 'black' to hide review changes.
+\newcommand{\rvw}[1]{\rvwcolour{#1}}
+\newcommand{\rvwt}[1]{\rvwcolourtwo{#1}}
+
 \onecolumn
@@
 \section{Introduction}
+
+% Remove after review:
+Note: Changes based on Reviewer 1's comments \rvw{are in this colour}. For
+Reviewer 2 \rvwt{we use this colour}.
 
@@
 biomechanics \e{and} sensory feedback, we sought to extend our
-previous work modelling the oculomotor system by adding a virtual,
+\rvw{previous work modelling the oculomotor system by adding a virtual,
 biomechanical eye model able to make physically realistic
@@
 visual features in the virtual world were projected back into the
-brain model.
+brain model.}
 %
@@
 \citep{tipper_reaching_2001} suggesting a close relationship between these
-neural systems. Building a behaving oculomotor system will
+neural systems. \rvw{Building a behaving oculomotor system will
 therefore assist future computational neurobehavioural modelling
-efforts that involve reaching.
+efforts that involve reaching.}
 
@@
 pons, medulla and rostral mid-brain \citep{sparks_brainstem_2002}.
-and finally the motor neurons which innervate the extraocular muscles
+and \rvw{finally the motor neurons} which innervate the extraocular muscles
 \citep{fuchs_firing_1970,sparks_brainstem_2002}. This direct pathway
@@
 comprehensive review, see \cite{girard_brainstem_2005}. Models of
-individual subsystems have been proposed for brainstem
+individual \rvw{subsystems} have been proposed for brainstem
 \citep{robinson_oculomotor_1975,scudder_new_1988,gancarz_neural_1998},
@@
 More recently, combined models have also been developed incorporating
-sensory input \citep{cope_basal_2017} and driving a second order
-differential equation representing the eye
+sensory input \citep{cope_basal_2017} and driving \rvw{a second order
+differential equation} representing the eye
 \citep{tabareau_geometry_2007,nguyen_saccade_2014,thurat_biomimetic_2015}.
@@
 
-To the \ccg~model, we added a brainstem model and a biomechanical
-eye model. The rate-coded brainstem model was taken from the
-literature~\cite{gancarz_neural_1998} as the best-of-breed saccadic
+To the \ccg~model, we added a brainstem model and a biomechanical eye
+model. \rvw{The rate-coded brainstem model was taken from the
+literature}~\cite{gancarz_neural_1998} as the best-of-breed saccadic
 burst generator~\cite{girard_brainstem_2005}.  The biomechanical eye
 was implemented using the biomechanical modelling framework OpenSim.
-These will be described below, along with a review of the \ccg~model,
-but first we will give a description of the co-ordinate systems and
-the modelling framework used.
+These will be described below, \rvwt{along with a review of
+the \ccg~model}, but first we will give a description of the
+co-ordinate systems and the modelling framework used.
 
@@
 connectivity outlined in \cite{gancarz_neural_1998}. The SBG network
-for two of the model's six channels is shown in Fig.~\ref{sbg}. We use
-the word `channel' to mean a set of populations of neurons which are
-involved in actuating a single extraocular muscle). Activity from the
-output layer of superior colliculus
+for two of the model's six channels is shown in
+Fig.~\ref{sbg}. \rvw{We use the word `channel' to mean a set of
+populations of neurons which are involved in actuating a single
+extraocular muscle. SBG channels are arranged in pairs, actuating
+opposing muscles. There is one pair of channels which actuates the
+superior and inferior rectus muscles, causing vertical rotations of
+the eye in a roughly parasaggital plane (the eye moves up or
+down). Another pair actuates the lateral and medial rectus muscles,
+causing horizontal rotations of the eye. The third pair actuates the
+superior and inferior oblique muscles which contribute to vertical as
+well as oblique rotations.} Activity from the output layer of superior
+colliculus
 %
@@
 (TNs).  The firing rate of the motor neuron defines the amount of
-force applied to the eye by that muscle.  Thus, the integral of the `bump'
+force applied to the eye by that muscle.  Thus, \rvw{the integral}
+of the `bump'
 defines how far the eye moves in that channel's direction.  The gain
@@
 target was close to the ideal straight line---see
-Fig.~\ref{sacc_vs_targ}(a) \& (b). We applied the same parameters to
+Fig.~\ref{sacc_vs_targ}(a) \& \rvw{(b)}. We applied the same parameters to
 both directions of each channel; $i_{up} = i_{down} = 0.00195$,

### 2017-11-09 papers/integration/omm_integ.tex
Responds to the comment from R1 about widening projections

@@
 \usepackage{gensymb} % For \degree
-\usepackage[usenames, dvipsnames]{color}
 
@@
 
-This led us to hypothesize that the retinotopic mapping be accompanied
+This led us to hypothesise that the retinotopic mapping be accompanied
 by an associated widening projection field such that the hill of
@@
 activity can be seen in the stimulation experiments
-in \cite{vokoun_intralaminar_2010}
-and \cite{vokoun_response_2014}. Although in this work we do not model
+in \cite{vokoun_intralaminar_2010} and \cite{vokoun_response_2014}.
+%
+\rvw{In \cite{ghitani_excitatory_2014}, from the same research group,
+evidence is presented for an excitatory and widely projecting pathway
+from the stratum griseum intermediale (equivalent to our SC\_deep) to
+the more superficial layers stratum opticum and stratum griseum
+superficiale. Although this pathway is a `wide' projecting field, the
+experiments do not indicate whether the projection \e{widens} along
+the rostral-caudal axis of the SC. \cite{bayguinov_hard-wired_2015}
+presents evidence for another projecting field within SC whose
+connectivity pattern \e{does} change along the rostral-caudal
+axis. This projection is inhibitory in nature. Although neither of
+these results precisely match the widening, excitatory projection
+field hypothesised here, they do indicate that such connection
+patterns are plausible.}
+%
+Although in this work we do not model
 the SC in detail, we extended the model with a third functional layer
@@
 decays too slowly to avoid additional saccadic movements. We found it
-necessary to hypothesize an inhibitory feedback mechanism from the SBG
+necessary to hypothesise an inhibitory feedback mechanism from the SBG
 to the brain model.  This is shown in Fig.~\ref{sbg}, which indicates
@@
 a `widening projection' exists between two maps in superior
-colliculus. Activities in one SC\_deep layer remains
+colliculus. \rvw{As described in the Methods section, there is
+now experimental evidence for similar projections
+\citep{ghitani_excitatory_2014,bayguinov_hard-wired_2015} making this
+a plausible suggestion.}  Activities in one SC\_deep layer remains
 eccentricity-dependent, with loops back to thalamus and cortex and

### 2017-11-09 papers/integration/omm_integ.tex
Nearly done with Reviewer 1's comments on the RESULTS section

@@
 
-Figs.~\ref{errorsurface}(a)--(d) show the same percentage errors for
-TModel4 as Fig.~\ref{errorsurfaceTM3} shows for TModel3.  First of
+Figs.~\ref{errorsurface}(a)--(d) show the \rvw{percentage errors for
+TModel4}.  First of
 all, note that the error magnitudes are much smaller. The mean errors
@@
 followed by a return saccade back to the null point. We noticed some
-irregularities in the return saccades, which though surprisingly
-accurate, had a significant overshoot.  More perplexingly, if the
+irregularities in the return saccades, which \rvw{were
+accurate}, but had a significant overshoot.  More perplexingly, if the
 target was switched repeatedly between 0\dg~and 10\dg, second and
@@
 few, consecutive out-and-return saccades, the saccade accuracy was
-relatively good, with trajectories resembling experimental data
-(\cite{bahill_trajectories_1979}, p.~6). % Poss. figure.
-Nevertheless, the lack of a reset of TN activity was an oversight, and
+accidently relatively good, with trajectories resembling experimental data
+(\cite{bahill_trajectories_1979}, p.~6). \rvw{Had the return accuracy not
+been so accurate, we may have noticed the lack of a tonic neuron reset
+mechanism and corrected this oversight earlier.} Such a mechanism
 is indeed proposed and included in the connectivity of the

### 2017-11-10 papers/integration/omm_integ.tex
Adds start of section describing weight maps

@@
 described earlier) are shown in Fig.~\ref{weightmaps}.
+
+\rvw{Fig.~\ref{weightmaps}(a) shows the weight map for the muscle
+which rotates the eye to the left. As we modelled a left eye, this
+actuates the lateral rectus muscle. The exponential rise is seen in
+the $r$ direction; as $r$ increases, so the connection strength to the
+SBG channel rises exponentially. The connection strength is greatest
+along the centre line, for a value of $\phi$ which corresponds to a
+purely leftward movement. Note that $\phi$ is presented in neural
+coordinates, and not in degrees or radians. $\phi=$37.5 corresponds
+to movements left. In regions of the map for which there is no
+leftward movement, that is, in the half of the map which corresponds
+to any movement with a rightward component, the `left' weight map is
+0. Fig.~\ref{weightmaps}(d) shows the weight map for rightward
+movements, actuating the medial rectus muscle of the eye. The map is a
+mirror of Fig.~\ref{weightmaps}(a), reflected about the line
+$phi$=25. ETC ETC for DOWN UP and Z+, Z-.}
 % From map_modelling2.m:

### 2017-11-10 papers/integration/omm_integ.tex
Adds section labels, and completes the section on weight maps in results

@@
 
-\section{Introduction}
+\section{Introduction} \label{sec:introduction}
 
@@
 
-\section{Material \& Methods}
+\section{Material \& Methods} \label{sec:methods}
 
@@
 
-\subsubsection{Co-ordinates in the world}
+\subsubsection{Co-ordinates in the world} \label{sec:methods:coords}
 
@@
 
-\subsection{Model development framework}
+\subsection{Model development framework} \label{sec:methods:framework}
 
@@
 
-\subsection{Existing brain model}
+\subsection{Existing brain model} \label{sec:methods:existing}
 
@@
 \subsubsection{Population activity and retinotopic mapping}
+\label{sec:mapping}
 
@@
 % Section - description of new brainstem model
-\subsection{Brainstem model}
+\subsection{Brainstem model} \label{sec:methods:brainstem}
 
@@
 % Section - description of biomechanical model
-\subsection{biomechanical eye}
+\subsection{biomechanical eye} \label{sec:methods:eye}
 
@@
 \subsection{Integrating the models and closing the loop}
+\label{sec:methods:integrating}
 
@@
 
-\section{Results}
-
-\subsection{Weight maps}
+\section{Results} \label{sec:results}
+
+\subsection{Weight maps} \label{sec:results:weightmaps}
 
@@
 direction of the newly parameterised channel. The training saccades
-were produced as described below in Sect.~\ref{sec:singlesaccades},
+were produced as described below in Sect.~\ref{sec:results:singlesaccades},
 with the same fixation and target luminances (crosses of magnitude 0.2
@@
 $j_{up} = j_{down} = 0.075$, $i_{left} = i_{right} = 0.0016$ and
-$j_{left} = j_{right} = 0.067$. The resulting weight maps (where the
-oblique maps are 1/10$^{\mathrm{th}}$ of the vertical maps, as
-described earlier) are shown in Fig.~\ref{weightmaps}.
-
-\rvw{Fig.~\ref{weightmaps}(a) shows the weight map for the muscle
-which rotates the eye to the left. As we modelled a left eye, this
-actuates the lateral rectus muscle. The exponential rise is seen in
-the $r$ direction; as $r$ increases, so the connection strength to the
-SBG channel rises exponentially. The connection strength is greatest
-along the centre line, for a value of $\phi$ which corresponds to a
-purely leftward movement. Note that $\phi$ is presented in neural
-coordinates, and not in degrees or radians. $\phi=$37.5 corresponds
-to movements left. In regions of the map for which there is no
-leftward movement, that is, in the half of the map which corresponds
-to any movement with a rightward component, the `left' weight map is
-0. Fig.~\ref{weightmaps}(d) shows the weight map for rightward
-movements, actuating the medial rectus muscle of the eye. The map is a
-mirror of Fig.~\ref{weightmaps}(a), reflected about the line
-$phi$=25. ETC ETC for DOWN UP and Z+, Z-.}
+$j_{left} = j_{right} = 0.067$.
+
+The resulting weight maps (where the oblique maps are
+1/10$^{\mathrm{th}}$ of the vertical maps, as described earlier) are
+shown in Fig.~\ref{weightmaps}.
+%
+\rvw{First, recall that the $r$ axis of the neural surface corresponds
+to the amplitude of a saccade and the $\phi$ axis indicates the polar
+direction of the saccade, as described in Sect.~\ref{sec:mapping} and
+Fig.~\ref{fig:mapping}. Fig.~\ref{weightmaps}(a) shows the weight map
+for the muscle which rotates the eye to the left. As we modelled a
+left eye, this actuates the lateral rectus muscle. The exponential
+rise of Eq.~\ref{eq:weightmaps} is seen in the $r$ direction; as $r$
+increases, so the connection strength to the SBG channel rises
+exponentially. The connection strength is greatest along the centre
+line, for a value of $\phi$ which corresponds to a purely leftward
+movement. Note that $\phi$ is presented in neural coordinates, and not
+in degrees or radians; 1$\leq\phi\leq$50 corresponds to a range of
+0\dg~to 360\dg; $\phi=$38.5 corresponds to movements left. The
+connections strength drops away sinusoidally as $\phi$ moves away from
+the centre line at $\phi=$38.5. In regions of the map for which there
+is no leftward movement, that is, in the half of the map which
+corresponds to any movement with a rightward component, the `left'
+weight map is 0. Fig.~\ref{weightmaps}(d) shows the weight map for
+rightward movements, actuating the medial rectus muscle of the
+eye. The line of maximum connection strength is along $\phi=$13.5. The
+map is a mirror of Fig.~\ref{weightmaps}(a), reflected about the line
+$\phi$=26. The `left' and `right' weight maps are orthogonal; the
+non-zero region of the `left' map is zero in the `right' map and vice
+versa. Fig~\ref{weightmaps}(b) \& (d) show the weight maps for
+downward and upward eye movements; the `down' map activates the SBG
+channel for the inferior rectus muscle, the `up' map activates the
+superior rectus. Note that `down' is not orthogonal either to `left'
+or `right' because a saccade down and left is achieved by
+simultaneously activating both the lateral and inferior rectus
+muscles. However, the `up' map \e{is} orthogonal to the `down' map and
+spans the edges of the surface where $\phi$ rolls over from 1 to
+50. The line of maximum connection strength for the `up' map is along
+$\phi=$1; for `down' $\phi=$26. Based on the training described in
+Sect.~\ref{sec:methods:integrating}, the maps driving the superior
+oblique (`Z+') and inferior oblique (`Z-') muscles were set to
+1/10$^{\mathrm{th}}$ of the `down' and `up' maps.}
 % From map_modelling2.m:
@@
 
-\subsection{Saccade accuracy}
+\subsection{Saccade accuracy} \label{sec:results:accuracy}
 
@@
 a `widening projection' exists between two maps in superior
-colliculus. \rvw{As described in the Methods section, there is
+colliculus. \rvw{As described in
+Sect.~\ref{sec:methods:integrating}, there is
 now experimental evidence for similar projections
@@
 
-\subsection{Single saccades} \label{sec:singlesaccades}
+\subsection{Single saccades} \label{sec:results:singlesaccades}
 
@@
 
-\subsection{Saccade Latencies}
+\subsection{Saccade Latencies} \label{sec:results:latencies}
 
@@
 
-\subsection{Saccade sequences}
+\subsection{Saccade sequences} \label{sec:results:sequences}
 
@@
 
-\section{Discussion}
+\section{Discussion} \label{sec:discussion}
 

### 2017-11-15 papers/integration/omm_integ.tex
Work in progress towards reviewer2's request to enhance the description of the brain model

@@
 model. \rvw{The rate-coded brainstem model was taken from the
-literature}~\cite{gancarz_neural_1998} as the best-of-breed saccadic
-burst generator~\cite{girard_brainstem_2005}.  The biomechanical eye
+literature} \citep{gancarz_neural_1998} as the best-of-breed saccadic
+burst generator \citep{girard_brainstem_2005}.  The biomechanical eye
 was implemented using the biomechanical modelling framework OpenSim.
@@
 The brain model, excluding the brainstem, is a re-implementation of
-the \ccg~model. Fig.~\ref{brain_model} shows the layout of the
-populations and the interconnections between them. Each population of
+the \ccg~model, \rvwt{of reflexive saccadic behaviour}.
+%
+\rvwt{Reflexive saccades are elicited by peripheral changes in the visual
+scene and are distinct from voluntary saccades. Reflexive saccades can
+occur also as a result of auditory and somatosensory stimuli, but
+these modalities are ignored in this work and
+in \cite{cope_basal_2017}. The functionality reproduced by
+the \ccg~model is `the selection of the best target end-point for a
+reflexive saccade'. A competition such as this between competing,
+incompatible movements is often referred to as an \e{action selection}
+problem. The brain must choose one location to foveate, because the
+eyes of most animals can only look in one direction at a time.} % Maybe cite norman_attention_1986, maes_dynamics_1989 on action selection.
+
+\rvwt{It is thought that in vertebrates, the basal ganglia (BG) play an important
+r\^ole in action
+selection~\citep{redgrave,graybiel,grillner,hikosaka after the
+evolutionary paper}. The \ccg~model
+places the BG at the centre of the oculomotor system, adopting a
+`channel based' model from previous
+work~\citep{gurney_basal_2004,etc}. Within the context of the basal
+ganglia model, a `channel' is a sub-set of neurons which are
+associated with an action. In the oculomotor model, an action
+corresponds to a distinct saccade end point. It can be seen that the
+action space for reflexive saccade end points is therefore a
+continuous space, rather than being selection between distinct
+acts. Etc etc. }
+
+Fig.~\ref{brain_model} shows the layout of the populations in the
+brain model and the interconnections between them. Each population of
 2500 elements is arranged as a 50 by 50 grid which forms a map in a

### 2017-11-16 papers/integration/omm_integ.tex
Work in progress on Rev2 comments

--- 2017-11-10 papers/integration/omm_integ.tex
@@
 The brain model, excluding the brainstem, is a re-implementation of
-the \ccg~model. Fig.~\ref{brain_model} shows the layout of the
-populations and the interconnections between them. Each population of
+the \ccg~model, \rvwt{of reflexive saccadic behaviour}.
+%
+\rvwt{Reflexive saccades are fast eye movements elicited by abrupt
+changes in the peripheral visual scene (reflexive saccades can occur
+also as a result of auditory and somatosensory stimuli, but these
+modalities are ignored here are in \cite{cope_basal_2017}). A
+reflexive saccade has a starting position defined by the initial
+orientation of the eye and an end-point position in which the eye is
+directed towards a new target. Regardless of the number of targets
+within the visual scene, the brain must choose one location as the
+end-point, because the eyes can only look in one direction at a
+time. The functionality reproduced by the \ccg~model is `the selection
+of the best target end-point for a reflexive saccade'. A competition
+such as this between competing, incompatible movements is often
+referred to as an \e{action selection}
+problem \citep{norman_attention_1986,maes_dynamics_1989,redgrave_basal_1999}.}
+
+\rvwt{It is thought that in vertebrates, the basal ganglia (BG) play
+an important r\^ole in action selection
+\citep{mink_basal_1996,graybiel_basal_1998,hikosaka_role_2000}.
+The \ccg~model places the BG at the centre of the oculomotor system,
+following the known anatomy of the region.  The BG receives excitatory
+inputs directly from retinotopic regions of the cortex including the
+frontal eye fields (FEF), supplementary eye fields (SEF), lateral
+intraparietal cortex (LIP) and dorsolateral prefrontal cortex. The BG
+receives input indirectly from the superior colliculus, which also has
+a retinotopic arrangement. The dorsolateral prefrontal cortex, which
+participates in voluntary saccades
+\citep{funahashi_prefrontal_1993,munoz_look_2004}, is not
+modelled because the model concerns reflexive rather than voluntary
+eye movements. Several other regions of the brain that are associated
+with eye movements are also omitted from the model. The early visual
+processing stream in cortex, from V1, through to the LIP is subsumed
+into a `sustained retinal' signal. The justification here is that the
+model reacts to simple luminant targets and does not need to carry out
+the feature extraction performed by these visual areas. The
+supplementary eye fields are involved in the programming of
+saccades \citep{} and memory guided saccades \citep{}. Lesions of SEF
+do not affect visually guided saccades \citep{} and so the SEF is also
+omitted from the model.
+%
+% Figure here is the ``macroscopic architecture'' one.
+%
+The
+BG's output is inhibitory and shapes the build-up of activity in both
+of these regions.
+%
+The \ccg~model adopts a `channel based' model from previous
+work~\citep{redgrave_basal_1999,gurney_basal_2004}. Within the context
+of the basal ganglia model, a `channel' is a sub-set of neurons which
+are associated with an individual action. Each channel in BG loops back via
+relays in the thalamus through cortex. Input into this
+thalamo-cortical loop is
+termed `salience'. Because it is a loop, input salience to the channel
+may originate cortically or sub-cortically. The higher the salience of
+the channel, the greater is the behavioural relevance of the
+associated action.
+
+In the oculomotor model, an action
+corresponds to a distinct saccade end point. It can be seen that the
+action space for reflexive saccade end points is therefore
+continuous rather than descrete.}
+
+Fig.~\ref{brain_model} shows the layout of the populations in the
+brain model and the interconnections between them. Each population of
 2500 elements is arranged as a 50 by 50 grid which forms a map in a

### 2017-11-17 papers/integration/omm_integ.tex
Work in progress on changes responding to R2's comments

@@
 \def\firstAuthorLast{James {et~al.}}
-\def\Authors{Sebastian James\,$^{1,2,*}$, Chris Papapavlou\,$^5$, Alexander Blenkinsop\,$^{1,2}$, \\
+\def\Authors{Sebastian James\,$^{1,2}$, Chris Papapavlou\,$^5$, Alexander Blenkinsop\,$^{1,2}$, \\
   Alexander Cope\,$^3$,  \\
-  Sean Anderson\,$^{2,4}$, Konstantinos Moustakas\,$^5$, Kevin Gurney\,$^{1,2}$}
+  Sean Anderson\,$^{2,4}$, Konstantinos Moustakas\,$^5$, Kevin Gurney\,$^{1,2,*}$}
 
@@
 which participates in the selection of the winning saccade end point
-\citep{stanton_frontal_1988}.
+\citep{stanton_frontal_1988,hikosaka_role_2000}.
 %
@@
 The integrated brain and biomechanical model described here is a
-development of the model in \cite{cope_basal_2017},
-referred to here as the \ccg~model. This was a rate-coded neural
-network model incorporating retinal populations, frontal eye fields
-(FEF), the basal ganglia (BG), and the superior colliculus (SC). In
-the \ccg~model, the centroid of the activity in the deep
-layers of superior colliculus was assumed to accurately encode the
-location of the eye at the end of the saccade
-\citep{wurtz_activity_1972,robinson_eye_1972,van_gisbergen_collicular_1987,mcilwain_lateral_1982}.
-This location was used to recalculate the positions of the luminances
-in the eye's frame of reference at each time step. The model included
-no brainstem populations other than superior colliculus, nor a
-neuromuscular model.
-
-To summarize, the \ccg~model takes as \e{input} the positions of
-luminances on a topographic map and produces as output a saccade
-target.
+development of the model in \cite{cope_basal_2017}, referred to here
+as the \ccg~model. This was a rate-coded neural network model
+incorporating retinal populations, frontal eye fields (FEF), the basal
+ganglia (BG), and the superior colliculus (SC).  The \ccg~model takes
+as \e{input} the positions of luminances \rvwt{(of fixed shape and
+intensity)} on a topographic map. \rvwt{Whilst certain assumptions
+were made about the input---that a luminant input excites activity on
+a retinotopic layer, with computer code carrying out the
+transformation achieved in the brain by a neural connectivity
+map \citep{thivierge_topographic_2007}---it is nonetheless \e{not} an
+input-assumption model according to our definition because the
+activity generated in the neural input layer is modelled as a response
+to the luminances, rather than being crafted.}  In the \ccg~model, the
+centroid of the activity in the deep layers of superior colliculus was
+assumed to accurately encode the location of the eye at the end of the
+saccade
+\citep{wurtz_activity_1972,robinson_eye_1972,van_gisbergen_collicular_1987,mcilwain_lateral_1982}.  This location was used to
+recalculate the positions of the luminances in the eye's frame of
+reference at each time step. \rvwt{Because a pattern of neural
+activity in the output population was assumed to have a behavioural
+outcome, it was thus an \e{output-assumption model}}.  The model
+included no brainstem populations other than superior colliculus, nor
+a neuromuscular model.
 
@@
 
+% Describe what is modelled first
 The brain model, excluding the brainstem, is a re-implementation of
-the \ccg~model, \rvwt{of reflexive saccadic behaviour}.
-%
+the \ccg~model, \rvwt{of reflexive saccadic behaviour \citep{cope_basal_2017}}.
 \rvwt{Reflexive saccades are fast eye movements elicited by abrupt
@@
 also as a result of auditory and somatosensory stimuli, but these
-modalities are ignored here are in \cite{cope_basal_2017}). A
-reflexive saccade has a starting position defined by the initial
-orientation of the eye and an end-point position in which the eye is
-directed towards a new target. Regardless of the number of targets
-within the visual scene, the brain must choose one location as the
-end-point, because the eyes can only look in one direction at a
-time. The functionality reproduced by the \ccg~model is `the selection
-of the best target end-point for a reflexive saccade'. A competition
-such as this between competing, incompatible movements is often
-referred to as an \e{action selection}
+modalities are ignored in this model). A reflexive saccade has a
+starting position defined by the initial orientation of the eye and an
+end-point position in which the eye is directed towards a new
+target. Regardless of the number of targets within the visual scene,
+the brain must choose one location as the end-point, because the eyes
+can look only in one direction at a time. The functionality reproduced
+by the \ccg~model is `the selection of the best target end-point for a
+reflexive saccade'. A competition such as this between incompatible
+movements is often referred to as an \e{action selection}
 problem \citep{norman_attention_1986,maes_dynamics_1989,redgrave_basal_1999}.}
 
-\rvwt{It is thought that in vertebrates, the basal ganglia (BG) play
-an important r\^ole in action selection
-\citep{mink_basal_1996,graybiel_basal_1998,hikosaka_role_2000}.
+\rvwt{One hypothesis for the r\^ole played by the basal ganglia (BG)
+is that the system performs \e{action selection}
+\citep{mink_basal_1996,redgrave_basal_1999,hikosaka_role_2000}.
 The \ccg~model places the BG at the centre of the oculomotor system,
-following the known anatomy of the region.  The BG receives excitatory
+following the known anatomy of the
+region \citep{hikosaka_role_2000}. The BG receives input indirectly
+from the superior colliculus, which has a retinotopic
+arrangement \citep{ottes_visuomotor_1986}.
+%and a signal which is associated with saccadic eye
+%movements \citep{wurtz_superior_1971}, specifying the saccade
+%end-point.
+The BG receives excitatory
 inputs directly from retinotopic regions of the cortex including the
 frontal eye fields (FEF), supplementary eye fields (SEF), lateral
-intraparietal cortex (LIP) and dorsolateral prefrontal cortex. The BG
-receives input indirectly from the superior colliculus, which also has
-a retinotopic arrangement. The dorsolateral prefrontal cortex, which
-participates in voluntary saccades
+intraparietal cortex (LIP) and dorsolateral prefrontal cortex. The
+dorsolateral prefrontal cortex, which participates in voluntary
+saccades
 \citep{funahashi_prefrontal_1993,munoz_look_2004}, is not
@@
 the feature extraction performed by these visual areas. The
-supplementary eye fields are involved in the programming of
-saccades \citep{} and memory guided saccades \citep{}. Lesions of SEF
-do not affect visually guided saccades \citep{} and so the SEF is also
-omitted from the model.
+supplementary eye fields are involved in the programming of saccade
+sequences \citep{tehovnik_eye_2000} and memory guided
+saccades \citep{chen_supplementary_1995,schlag_neurons_2002}. Lesions
+of SEF do not affect visually guided
+saccades \citep{gaymard_cortical_1998} and so the SEF is also omitted
+from the model.}
 %
@@
 %
-The
-BG's output is inhibitory and shapes the build-up of activity in both
-of these regions.
-%
-The \ccg~model adopts a `channel based' model from previous
-work~\citep{redgrave_basal_1999,gurney_basal_2004}. Within the context
-of the basal ganglia model, a `channel' is a sub-set of neurons which
-are associated with an individual action. Each channel in BG loops back via
-relays in the thalamus through cortex. Input into this
-thalamo-cortical loop is
-termed `salience'. Because it is a loop, input salience to the channel
-may originate cortically or sub-cortically. The higher the salience of
-the channel, the greater is the behavioural relevance of the
-associated action.
-
-In the oculomotor model, an action
+
+% Now describe each bit a little more, with help of the figure.
+\rvwt{Fig.~\ref{fig:ccg_model}(a) shows the macroscopic architecture of
+the \ccg~model. The figure shows the relationships between the retinal
+input populations, the FEF, the populations comprising the BG
+sub-system (the red border indicates that the box represents a number
+of populations as a sub-system), the thalamus and the superior
+colliculus. Excitatory connections are indicated with arrow heads;
+inhibitory connections with circles in place of the arrow heads. The
+blue and green connection lines indicate two thalamo-basal ganglia
+loops, one cortical loop through FEF (green), the other a sub-cortical
+loop through SC. It is important to note that although they are given
+different colours in the diagram, these loops are in no way
+independent, with loop activity combining both in thalamus and in the
+basal ganglia and a direct excitatory, feed-forward connection from
+FEF to SC.}
+
+% More on BG model here
+\rvwt{The basal ganglia sub-system is the most complex component of
+the \ccg~model. The BG model is based on previous
+work \citep{gurney_computational_2001,gurney_computational_2001-1} and is referred to as the GPR
+model. The GPR model incorporates the following main components of the
+primate BG \citep{mink_basal_1996,wickens_basal_1997}: (i) The
+striatum (the main input station to the BG) which is divided into two
+iterdigitated poulations of projection neurons expressing primarily D1
+or D2-type dopaminergic receptors (named Str\_D1 and Str\_D2); (ii)
+The subthalamic nucleus (STN); (iii) the external segment of the
+globus pallidus (GPe); (iv) the output nucleus relevant for saccadic
+control---the substantia nigra pars reticulata
+(SNr) \citep{hikosaka_role_2000}.}
+
+\rvwt{The connectivity of the GPR model (Fig.~\ref{fig:ccg_model}(b)
+is constrained by the known anatomy and physiology of the
+BG~\citep{bolam_synaptic_2000}. Physiologically, the only source of
+glutamate within the BG is the STN, whose projections are therefore
+excitatory; all other nuclei have GABAergic projection neurons and are
+therefore inhibitory. The cortex sends glutamatergic projections to
+both the Str\_D1 striatal population, which projects preferentially to
+the SNr, and to Str\_D2, which projects primarily to
+GPe \citep{gerfen_d1_1990}. The cortex also projects to the STN, which
+sends diffuse projections to the SNr and
+GPe \citep{parent_anatomical_1993}. The GPe projects to the SNr and
+also projects back to the STN, completing a GPe--STN loop.}
+
+\rvwt{Within the BG, there are several mechanisms supporting
+competitive processing for selecting channels whose inhibitory output
+is reduced. The selection mechanism of the GPR model is the
+`off-centre, on-surround' scheme proposed
+by \cite{mink_basal_1993}. The `on-surround' is provided by
+diffuse, excitatory projections from the STN to the SNr. Focussed
+inhibition from the Str\_D1 neurons in striatum contributes the
+`off-centre' part of the mechanism. This arrangement leads to
+selection behaviour via a release of target inhibition, since
+channels that have strong saliencel (input) have weak output at the
+level of SNr, and channels with weak salience have enhanced output.}
+
+\rvwt{The GPe is not included in the centre-surround circuit described
+above, but still plays a key r\^ole in selection. Operating alone, the
+Str\_D1/STN/SNr circuit can suffer from the following problem: if the
+input for all channels is relatively high, then the diffuse projection
+from STN, which effectively supplies a sum of the STN inputs to each
+channel in SNr, will provide so much excitation that Str\_D1 may
+become unable to inhibit one of the channels in SNr and selection may
+become
+impossible. \cite{gurney_computational_2001,gurney_computational_2001-1}
+showed that the inhibitory feedback from GPe to STN acts as an
+`automatic gain control' to help prevent this from occurring.}
+
+\rvwt{At the neuronal level, the STN, GPe and SNr have tonic output
+levels \citep{chevalier_disinhibition_1990,delong_primate_1985,kita_intracellular_1991}. This
+is modelled using piecewise linear output functions with zero offsets,
+$c$ (see Eq.~\ref{eq:lintransfunc}). In striatum, Str\_D1 and Str\_D2
+have positive offset $c$, mimicking the so-called `down-state' of
+medium spiny neurons which have a resting potential far below spiking
+threshold and require co-ordinated input to generate action
+potentials \citep{wilson_origins_1996}.
+% Note, in Cope's paper, there is an error with the offsets for
+% D1,D2. These are set to -0.05 instead of 0.05. A quick trial with
+% the model suggests this doesn't make a very large difference to the
+% operation, and I have the sign correct in any case.
+In addition, the Str\_D1 and Str\_D2 neurons are influenced by
+dopamine in different ways; facilitating cortico-striatal transmission
+at medium spiny neurons with D1 receptors \citep{hernandez-lopez_D1_1997,gonon_prolonged_1997} and reducing
+transmission at those with D2 receptors \citep{delgado_inhibitory_1999}. These effects are
+modelled using a dopamine parameter which modulates the input
+activation as described below in Eqs~\ref{eq:a_in_d1} \& \ref{eq:a_in_d2}.}
+
+% Change this - we already talked about channels?
+\rvwt{The \ccg~model adopts a `channel based' model from previous
+work~\citep{redgrave_basal_1999,gurney_computational_2001}.
+Within the context of the basal ganglia model, a `channel' is a
+sub-set of neurons which are associated with an individual
+action. Each channel in BG loops back via relays in the thalamus
+through cortex. Input into this thalamo-cortical loop is termed
+`salience'. Because it is a loop, input salience to the channel may
+originate cortically or sub-cortically. The higher the salience of the
+channel, the greater is the behavioural relevance of the associated
+action.}
+
+\rvwt{In the oculomotor model, an action
 corresponds to a distinct saccade end point. It can be seen that the
 action space for reflexive saccade end points is therefore
-continuous rather than descrete.}
+continuous rather than discrete. MORE HERE}
+
+% FEF stuff taken from Alex's pre-pub
 
 Fig.~\ref{brain_model} shows the layout of the populations in the
-brain model and the interconnections between them. Each population of
-2500 elements is arranged as a 50 by 50 grid which forms a map in a
-retinotopic co-ordinate system, roughly matching the known layout of
-the superior colliculus \citep{robinson_eye_1972}.
+brain model, as implemented in SpineCreator, and the interconnections
+between them. Each population of 2500 elements is arranged as a 50 by
+50 grid which forms a map in a retinotopic co-ordinate system, roughly
+matching the known layout of the superior
+colliculus \citep{robinson_eye_1972}.
 % and frontal eye field?
@@
 piecewise linear transfer function
-\begin{equation}
+\begin{equation} \label{eq:lintransfunc}
    y(a) = \begin{cases}
@@
 \end{equation}
-where $c$ is a parameter defining the slope of the transfer
-function. At this point, the naming scheme for the component becomes
-apparent; this is a Leaky Integrator with a piecewise-linear transfer
-function.
+where $c$ is a parameter defining the offset of the transfer
+function. \rvwt{If $c<0$, then for zero activation ($a=0$), the output
+will be positive. This simulates the effect of a neural population
+having tonic firing. If $c>0$ then the output will be zero until the
+activation exceeds $c$, simulating neurons which only fire when driven
+by excitatory input.} At this point, the naming scheme for the
+component becomes apparent; this is a Leaky Integrator with a
+piecewise-linear transfer function.
 
@@
 activation, so that their equations for $a_{in}$ are thus:
-\begin{equation}
+\begin{equation} \label{eq:a_in_d1}
    a_{in}^{D1} = (0.2 + d)A + 0.01 R_N
 \end{equation}
-\begin{equation}
+\begin{equation} \label{eq:a_in_d2}
    a_{in}^{D2} = (1 - d)A + 0.01 R_N
@@
 
-\cite{tabareau_geometry_2007} gives a formulation for the weight maps
+\cite{tabareau_geometry_2007} give a formulation for the weight maps
 in which it is possible to project both a positive and a negative
@@
 
-% worldDataMaker to brain, but Re-work:
+% worldDataMaker to brain:
 The eye model outputs its rotational state at each timestep. The
@@
 \begin{center}
+\includegraphics[width=0.9\textwidth]{./figures/ccg_model.png}
+\end{center}
+\textbf{\refstepcounter{figure}\label{fig:ccg_model} Figure \arabic{figure}.}
+{ The macroscopic architecture of the \ccg~model. The main nuclei
+modelled as brain systems are: basal ganglia (BG), frontal eye fields
+(FEF), thalamus (THAL) and superior colliculus (SC). The retinal input
+is presented via non-biologically plausible retinal populations. The
+loops through basal ganglia, which define the architecture, are shown
+with coloured lines: the cortical loop (through FEF and THAL) in green
+and the sub-cortical loop (through SC and THAL) in blue. Connections
+with arrowheads indicate excitatory connections, those with circles
+are inhibitory. A red border indicates that the box represents a
+sub-system of two or more populations; a black box indicates,
+within the context of the model, a single neural population.}
+\end{figure}
+
+\begin{figure}[htb!]
+\begin{center}
 \includegraphics[width=0.9\textwidth]{./figures/Brain_Model.png}

### 2017-11-17 papers/integration/bbl_utf8_to_latex.sh

@@ -1,0 +1,42 @@
+#!/bin/bash
+
+# Replace various utf-8 characters with the tex/latex equivalents
+# because Frontiers doesn't like utf-8 in .bbl files.
+
+if [ -z ${1} ]; then
+    echo "Please supply path to the .bbl file"
+    exit 1
+fi
+
+mkdir -p /tmp/utf8tolatex
+e=$?
+if [ ${e} -ne "0" ]; then
+    echo "Failed to make /tmp/utf8tolatex dir. Exiting."
+    exit 1
+fi
+
+# Backup
+cp ${1} /tmp/utf8tolatex/${1}.backup
+e=$?
+if [ ${e} -ne "0" ]; then
+    echo "Failed to make backup. Exiting."
+    exit 1
+fi
+
+# Search/replace u umlauts
+sed 's/\xc3\xbc/\\"u/g' < "$1" > /tmp/utf8tolatex/1.bbl
+
+# e acute (Moren)
+sed 's/\xc3\xa9/\\'\''e/g' < /tmp/utf8tolatex/1.bbl >  /tmp/utf8tolatex/2.bbl
+
+# e grave (Lefevre)
+sed 's/\xc3\xa8/\\\`e/g' < /tmp/utf8tolatex/2.bbl >  /tmp/utf8tolatex/3.bbl
+
+# Reg
+sed 's/\xc2\xae/\\textsuperscript\{\\textregistered\}/g' < /tmp/utf8tolatex/3.bbl >  /tmp/utf8tolatex/4.bbl
+
+# TM
+sed 's/\xe2\x84\xa2/\\textsuperscript\{TM\}/g' < /tmp/utf8tolatex/4.bbl >  /tmp/utf8tolatex/5.bbl
+
+# Copy back
+cp /tmp/utf8tolatex/5.bbl ${1}

### 2017-11-18 papers/integration/omm_integ.tex
Further WIP

@@
 comprehensive review, see \cite{girard_brainstem_2005}. Models of
-individual \rvw{subsystems} have been proposed for brainstem
+individual \rvw{sub-systems} have been proposed for brainstem
 \citep{robinson_oculomotor_1975,scudder_new_1988,gancarz_neural_1998},
@@
 burst generator \citep{girard_brainstem_2005}.  The biomechanical eye
-was implemented using the biomechanical modelling framework OpenSim.
+was implemented using the biomechanical modelling framework OpenSim;
+the brain and brainstem were modelled using the SpineML toolchain.
 These will be described below, \rvwt{along with a review of
 the \ccg~model}, but first we will give a description of the
-co-ordinate systems and the modelling framework used.
-
-\subsubsection{Co-ordinates in the world} \label{sec:methods:coords}
+co-ordinate systems.
+
+\subsection{Co-ordinates in the world} \label{sec:methods:coords}
 
@@
 used to determine the input to the brain model.
+
+\subsection{Existing brain model} \label{sec:methods:existing}
+
+% Describe what is modelled first
+The brain model, excluding the brainstem, is a re-implementation of
+the \ccg~model, \rvwt{of reflexive saccadic behaviour \citep{cope_basal_2017}}.
+\rvwt{Reflexive saccades are fast eye movements elicited by abrupt
+changes in the peripheral visual scene (reflexive saccades can occur
+also as a result of auditory and somatosensory stimuli, but these
+modalities are ignored in this model). A reflexive saccade has a
+starting position defined by the initial orientation of the eye and an
+end-point position in which the eye is directed towards a new
+target. Regardless of the number of targets within the visual scene,
+the brain must choose one location as the end-point, because the eyes
+can look only in one direction at a time. The functionality reproduced
+by the \ccg~model is `the selection of the best target end-point for a
+reflexive saccade'. A competition such as this between incompatible
+movements is often referred to as an \e{action selection}
+problem \citep{norman_attention_1986,maes_dynamics_1989,redgrave_basal_1999}.}
+
+\rvwt{One hypothesis for the r\^ole played by the basal ganglia (BG)
+is that the system performs \e{action selection}
+\citep{mink_basal_1996,redgrave_basal_1999,hikosaka_role_2000}.
+The \ccg~model places the BG at the centre of the oculomotor system,
+following the known anatomy of the
+region \citep{hikosaka_role_2000}. The BG receives input indirectly
+from the superior colliculus, which has a retinotopic
+arrangement \citep{ottes_visuomotor_1986}.
+%and a signal which is associated with saccadic eye
+%movements \citep{wurtz_superior_1971}, specifying the saccade
+%end-point.
+The BG receives excitatory
+inputs directly from retinotopic regions of the cortex including the
+frontal eye fields (FEF), supplementary eye fields (SEF), lateral
+intraparietal cortex (LIP) and dorsolateral prefrontal cortex. The
+dorsolateral prefrontal cortex, which participates in voluntary
+saccades
+\citep{funahashi_prefrontal_1993,munoz_look_2004}, is not
+modelled because the model concerns reflexive rather than voluntary
+eye movements. Several other regions of the brain that are associated
+with eye movements are also omitted from the model. The early visual
+processing stream in cortex, from V1, through to the LIP is subsumed
+into a `sustained retinal' signal which arrives at FEF. The
+justification here is that the model reacts to simple luminant targets
+and does not need to carry out the feature extraction performed by
+these visual areas. The supplementary eye fields are involved in the
+programming of saccade sequences \citep{tehovnik_eye_2000} and memory
+guided
+saccades \citep{chen_supplementary_1995,schlag_neurons_2002}. Lesions
+of SEF do not affect visually guided
+saccades \citep{gaymard_cortical_1998} and so the SEF is also omitted
+from the model.}
+
+% Now describe each bit a little more, with help of the CCG
+% macroscopic architecture figure.
+\rvwt{Fig.~\ref{fig:ccg_model}(a) shows the macroscopic architecture of
+the \ccg~model. The figure shows the relationships between the retinal
+input populations, the FEF, the populations comprising the BG
+sub-system (the red border indicates that the box represents a number
+of populations as a sub-system), the thalamus and the superior
+colliculus. Excitatory connections are indicated with arrow heads;
+inhibitory connections with circles in place of the arrow heads. The
+blue and green connection lines indicate two thalamo-basal ganglia
+loops, one cortical loop through FEF (green), the other a sub-cortical
+loop through SC. It is important to note that although they are given
+different colours in the diagram, these loops are in no way
+independent, with loop activity combining both in thalamus and in the
+basal ganglia and a direct excitatory, feed-forward connection from
+FEF to SC.}
+
+% More on BG model here
+\rvwt{The basal ganglia sub-system is the most complex component of
+the \ccg~model. The BG model is based on previous
+work \citep{gurney_computational_2001,gurney_computational_2001-1} and is referred to as the GPR
+model. The GPR model incorporates the following main components of the
+primate BG \citep{mink_basal_1996,wickens_basal_1997}: (i) The
+striatum (the main input station to the BG) which is divided into two
+iterdigitated populations of projection neurons expressing primarily D1
+or D2-type dopaminergic receptors (named Str\_D1 and Str\_D2); (ii)
+The subthalamic nucleus (STN); (iii) the external segment of the
+globus pallidus (GPe); (iv) the output nucleus relevant for saccadic
+control---the substantia nigra pars reticulata
+(SNr) \citep{hikosaka_role_2000}.}
+
+\rvwt{The connectivity of the GPR model [Fig.~\ref{fig:ccg_model}(b)]
+is constrained by the known anatomy and physiology of the
+BG~\citep{bolam_synaptic_2000}. Physiologically, the only source of
+glutamate within the BG is the STN, whose projections are therefore
+excitatory; all other nuclei have GABAergic projection neurons and are
+therefore inhibitory. The cortex sends glutamatergic projections to
+both the Str\_D1 striatal population, which projects preferentially to
+the SNr, and to Str\_D2, which projects primarily to
+GPe \citep{gerfen_d1_1990}. The cortex also projects to the STN, which
+sends diffuse projections to the SNr and
+GPe \citep{parent_anatomical_1993}. The GPe projects to the SNr and
+also projects back to the STN, completing a GPe--STN loop.}
+
+\rvwt{The GPR model is arranged into `action channels';
+Fig.~\ref{fig:ccg_model}(b) shows an example network containing three
+channels. It is between these channels that competition occurs, with
+the winning channel succeeding in reducing activity in the output
+nucleus, SNr, and thereby disinhibiting its target. The complete
+connectivity pattern for this small network is shown in
+Fig.~\ref{fig:ccg_model}(b); the left channel in cortex innervates the
+left channels of Str\_D1, STN and Str\_D2. Connections are one-to-one,
+so it follows that the middle channel of cortex innervates the middle
+channels of STN and the striatal populations and the right channel of
+cortex innervates right channels in striatum and STN. Striatal
+population channels also inhibit SNr and GPe on a one-to-one basis and
+GPe feeds inhibition to SNr and STN in a one-to-one manner. The
+outputs from STN however are not one-to-one. The output from all
+channels of STN is summed together and then the sum is fed into each
+channel of SNr and GPe. This models the diffuse excitation from STN
+which has been observed in the BG \citep{parent_anatomical_1993}.}
+
+\rvwt{Within the BG, there are several mechanisms supporting
+competitive processing for selecting channels whose inhibitory output
+should be reduced. The selection mechanism of the GPR model is the
+`off-centre, on-surround' scheme proposed
+by \cite{mink_basal_1993}. The `on-surround' is provided by
+diffuse, excitatory projections from the STN to the SNr. Focussed
+inhibition from the Str\_D1 neurons in striatum contributes the
+`off-centre' part of the mechanism. This arrangement leads to
+selection behaviour via a release of target inhibition, since
+channels that have strong salience (input) have weak output at the
+level of SNr, and channels with weak salience have enhanced output.}
+
+\rvwt{The GPe is not included in the centre-surround circuit described
+above, but still plays a key r\^ole in selection. Operating alone, the
+Str\_D1/STN/SNr circuit can suffer from the following problem: if the
+input for all channels is relatively high, then the diffuse projection
+from STN, which effectively supplies a sum of \e{all} of the STN inputs to each
+channel in SNr, will provide so much excitation that Str\_D1 may
+become unable to inhibit one of the channels in SNr and selection may
+become
+impossible. \cite{gurney_computational_2001,gurney_computational_2001-1}
+showed that the inhibitory feedback from GPe to STN acts as an
+`automatic gain control' to help prevent this from occurring.}
+
+\rvwt{At the neuronal level, the STN, GPe and SNr have tonic output
+levels \citep{chevalier_disinhibition_1990,delong_primate_1985,kita_intracellular_1991}. This
+is modelled using piecewise linear output functions with zero offsets,
+$c$ (see Eq.~\ref{eq:lintransfunc}) but with noise added to the
+input. In striatum, Str\_D1 and Str\_D2 have positive offset $c$,
+mimicking the so-called `down-state' of medium spiny neurons which
+have a resting potential far below spiking threshold and require
+co-ordinated input to generate action
+potentials \citep{wilson_origins_1996}.
+% Note, in Alex's paper, there is an error with the offsets for D1,
+% D2. These are set to -0.05 instead of 0.05. A quick trial with the
+% model suggests this doesn't make a very large difference to the
+% overall operation (you just see a background of noise around the
+% signals in Str), and I have the sign correct in any case.
+In addition, the Str\_D1 and Str\_D2 neurons are influenced by
+dopamine in different ways; facilitating cortico-striatal transmission
+at medium spiny neurons with D1 receptors \citep{hernandez-lopez_D1_1997,gonon_prolonged_1997} and reducing
+transmission at those with D2 receptors \citep{delgado_inhibitory_1999}. These effects are
+modelled using a dopamine parameter which modulates the input
+activation as described below in
+Eqs~\ref{eq:a_in_d1} \& \ref{eq:a_in_d2}; Str\_D1 activation is enhanced;
+Str\_D2 activation is suppressed.}
+
+% Change this - we already talked about channels in the context of the
+% three channel model show. Perhaps modify to talk about how we have a
+% map of channels - almost a continuous space in the \ccg model. This
+% can then lead on to Fig 3.
+\rvwt{Expand along lines of `the
+action space for reflexive saccade end points is therefore
+continuous rather than discrete' (FIXME).}
+
+% Now some FEF stuff taken from Alex's pre-pub
+\rvwt{Add description of FEF. (FIXME).}
+
+Fig.~\ref{brain_model} shows the layout of the populations in the
+brain model, as implemented in SpineCreator, and the interconnections
+between them. \rvwt{Describe this figure in more detail. (FIXME).}
+% and frontal eye field?
+
+\subsubsection{Components}
+
+With the exceptions of the World and FEF\_add\_noise populations, each
+neural element represents an activation; the activation is governed by
+a first order differential equation specified in the SpineML
+component. In the brain model, there are six different components in
+use: LINlinear; LINret; LINexp; D1MSN and D2MSN.
+
+The LINlinear component governs the activation $a$ with a first order
+leaky integrator differential equation:
+\begin{equation}
+   \dot{a} = \frac{1}{\tau}(a_{in}-a)
+\end{equation}
+where $\tau$ is the time constant for the neural activation and
+$a_{in}$ is the input to the neural element. $a_{in}$ is defined by an
+activation input and a shunting inhibition input according to:
+\begin{equation}
+   a_{in} = A(1-s_a)+\alpha R_N
+\end{equation}
+Here, $A$ is the activation input and $s_a$ is the shunting inhibition
+state variable whose value is related to the shunting input, $S$ by
+\begin{equation}
+   s_a = \begin{cases}
+      S & S\leq 1 \\
+      1 & S > 1
+   \end{cases}
+\end{equation}
+$R_N$ is a random number drawn from a standard normal distribution
+($\sigma$=1, $\mu$=0) and introduces noise to the activation of the
+neural element, with the parameter $\alpha$ controlling the noise
+amplitude.
+
+The output, $y$, of LINlinear is related to the activation $a$ by the
+piecewise linear transfer function
+\begin{equation} \label{eq:lintransfunc}
+   y(a) = \begin{cases}
+      0   & a < c \\
+      a-c & c \leq a \leq 1+c \\
+      1   & a > 1+c
+   \end{cases}
+\end{equation}
+where $c$ is a parameter defining the offset of the transfer
+function. \rvwt{If $c<0$, then for zero activation ($a=0$), the output
+will be positive. This simulates the effect of a neural population
+having tonic firing. If $c>0$ then the output will be zero until the
+activation exceeds $c$, simulating neurons which only fire when driven
+by excitatory input.} At this point, the naming scheme for the
+component becomes apparent; this is a Leaky Integrator with a
+piecewise-linear transfer function.
+
+The LINret component used for the retinal populations is similar to
+the LINlinear component, but with no intrinsic noise and no shunting
+inhibitory input. It has a neural input which is identical to the
+activation input $A$:
+\begin{equation}
+   a_{in} = A
+\end{equation}
+The LINexp component is a leaky integrator with an exponential
+transfer function. It shares the same differential equation with
+LINlinear, but has a different input equation and a different output
+transfer function. It has the following equation for the neural
+element input $a_{in}$:
+\begin{equation}
+   a_{in} = [A+N(a-V_{r}^{-})] (1-S) + 0.01 R_N
+\end{equation}
+where $A$ is the activation input and $N$ is an input which is
+modulated by $V_{r}^{-}$, a reversal potential, and $a$, the current
+activation of the element. These inputs are summed and then reduced by
+a factor which is dependent on $S$, the shunting input. As in
+LINlinear, $R_N$ introduces normally distributed noise to the element.
+
+The output, $y$, of the LINexp component is given by
+\begin{equation}
+   y(a) = \begin{cases}
+      \mathrm{e}^{a}-0.9   & \mathrm{e}^a \leq 1+0.9 \\
+      1   & \mathrm{e}^a > 1+0.9
+   \end{cases}
+\end{equation}
+This component is used in the subthalamic nucleus (STN) population, as
+it gives a more physiologically accurate f-I
+behaviour
+\citep{wilson_model_2004,bevan_mechanisms_1999,hallworth_apamin-sensitive_2003}
+which has been shown to allow the mapping of the basal ganglia network
+architecture onto an optimal decision making
+model \citep{bogacz_basal_2007}.
+
+The D1MSN and D2MSN components are both leaky integrators, similar to
+LINlinear. They differ in that they have no shunting inhibition. They
+are used to model medium spiny neuron (MSN) populations in the
+striatum. As they model the fact that most MSN neurons fall into two
+groups; those expressing D1 dopamine receptors and those expressing D2
+receptors, they have a dopamine parameter that modulates the input
+activation, so that their equations for $a_{in}$ are thus:
+\begin{equation} \label{eq:a_in_d1}
+   a_{in}^{D1} = (0.2 + d)A + 0.01 R_N
+\end{equation}
+\begin{equation} \label{eq:a_in_d2}
+   a_{in}^{D2} = (1 - d)A + 0.01 R_N
+\end{equation}
+where $d$ is the dopamine parameter. Varying dopamine from 0 to 1
+enhances the activation in the D1 model, whereas it decreases the
+activation of the D2 model elements, in line with experimental
+observations \citep{harsing_influence_1997,gonon_prolonged_1997}.
+Note that the equation for $a_{in}^{D1}$ differs from that used in
+the \ccg~model, for which the cortico-striatal weights are multiplied
+by $(1+d)$ rather than $(0.2+d)$.
+
+The equations given above are applied to each element in a
+population. The value of the activation $A$ (and where relevant, the
+shunting input, $S$) is determined by summing the weighted inputs to
+the population:
+\begin{equation}
+A = \sum_{i}w_i^{act} x_i^{act}
+\end{equation}
+\begin{equation}
+S = \sum_{i}w_i^{sh} x_i^{sh}
+\end{equation}
+$w_i^{act}$ and $w_i^{sh}$ are, respectively, the weights of the
+$i^{th}$ activation or shunting connection; $x_i^{act}$ and $x_i^{sh}$
+are the signals input to the activation and shunting connections.
+
+\subsubsection{Population activity and retinotopic mapping}
+\label{sec:mapping}
+
+Each population of 2500 neural elements was arranged in a 50 by 50
+grid, with positions on the grid representing a retinotopic mapping
+similar to that found empirically both in the superior
+colliculus \citep{ottes_visuomotor_1986} and in visual cortex
+\citep{eric_l._schwartz_computational_1980}
+and assumed in this work to persist throughout the oculomotor system.
+
+In a retinotopic mapping, the Cartesian co-ordinates of the
+light-sensitive cells in the retina, whose density varies with
+distance from the fovea, are transformed into the Cartesian
+co-ordinates of the correspondingly active cells on the
+colliculus. The mapping ensures that an even density of cells can be
+maintained in the colliculus, but ensures that a group of adjoining,
+active, retinal neurons will always activate an adjoining group of
+neurons on the collicular surface.
+
+The mapping turns out to resemble polar co-ordinates. That is, one
+axis of the collicular surface specifies the eccentricity of a retinal
+location (how far it is from the fovea) and the second axis specifies
+the rotational angle of the retinal location; we therefore use the
+convention of referring to the eccentricity axis on the colliculus as
+$r$ and the rotation axis as $\phi$.
+
+The \e{cortical magnification factor}, $M(r)$, gives the relationship
+between the radial eccentricity $r$ and the retinal neural density. As
+in
+\cite{cope_basal_2017}, we use a first-order approximation of the form
+for $M(r)$ given in \cite{rovamo_estimation_1979}:
+\begin{equation} \label{eq:cmf}
+M(r) = \frac{M_f}{1+\frac{r}{E_2}}
+\end{equation}
+The foveal magnification, $M_f$, is the magnification of the most
+central region of the retina and has a value in the human of about 7.8
+mm/\dg~\citep{rovamo_estimation_1979}.
+
+In our model, $M_f$ is related to $W_{nfs}$, the width of the
+retinotopic neural field, $W_{fov}$, the width of the eye's field of
+view and $E_2$, the eccentricity at which the retinal density has
+halved by:
+\begin{equation} \label{eq:fm}
+   M_f = \frac {W_{nfs}} {E_2\;\ln\left(\frac{W_{fov}}{2 E_2} + 1\right)}
+\end{equation}
+Here, $W_{nfs}$ is 50 (the side length of the 50x50 grid) and
+$W_{fov}$ is set to 61\dg, a reduction from the biophysically accurate
+150\dg~due to the small number of neurons in the retinotopic neural
+field. $E_2$ is
+2.5 \citep{cope_basal_2017,slotnick_electrophysiological_2001}.
+
+The mapping from the retinotopic co-ordinates in the brain to
+rotational co-ordinates of the stimulus/response was written down by
+\cite{schwartz_spatial_1977,eric_l._schwartz_computational_1980}
+for measurements of striate cortex [visual stimulus to
+electrophysiological response---\cite{daniel_representation_1961,
+talbot_physiological_1941}] and by \cite{ottes_visuomotor_1986} for
+superior colliculus data [electrophysiological SC stimulus to eye
+movement response---\cite{robinson_eye_1972}].
+% Ottes et al. fit to stimulus-to-movement data, and give a
+% movement-to-collicular-coordinate mapping in the paper.
+We used the following statement of this mapping to introduce stimuli
+into the `World' input population of the brain model:
+\begin{equation}\label{eq:thetas_to_phi}
+   \phi = \frac{W_{nfs}} {2 \pi}\arctan\left(\frac{\theta_{y}^{t}}{\theta_{x}^{t}}\right)
+\end{equation}
+\begin{equation}\label{eq:thetas_to_r}
+   r = M_fE_2\,\ln\left(\frac{1}{E_2}\sqrt{{\theta_{x}^{t}}^2 + {\theta_{y}^{t}}^2}+1\right)
+\end{equation}
+Note that we use $r$ and $\phi$ as the co-ordinates on the `collicular
+surface'. Schwartz uses $r$ and $\phi$ as the polar coordinates of the
+retinal stimulus; Ottes et al.~use $r$ and $\phi$ as polar coordinates
+for the eye movement response; both use $u$ and $v$ as the Cartesian
+co-ordinates of the neural map. We use $\theta_{x}^{t}$ and
+$\theta_{y}^{t}$ to give Euler rotations for the retinal target
+stimulus. Note also that the form of
+Eqns.~\ref{eq:thetas_to_phi} \& \ref{eq:thetas_to_r} is slightly
+different from that given in
+\cite{ottes_visuomotor_1986} because our $\theta_{x}^{t}$ and
+$\theta_{y}^{t}$ are not the polar co-ordinates used in that work.
+
+The mapping encompases the entire visual field; the value of $\phi$ is
+allowed to vary from 0\dg~to 360\dg~along its axis.  Effectively, the
+two contralateral colliculi found in the biology are incorporated into
+a single, square map, avoiding the need to carry out the kind of
+`colliculus gluing' described in \cite{tabareau_geometry_2007}.
+
+It is straightforward to show that the reverse mapping is given by:
+\begin{equation}
+   \theta_x = E_2 \left(e^{\frac{r}{M_f E_2}} - 1\right).\cos\left(\frac{2 \pi \phi}{W_{nfs}}\right)
+\end{equation}
+\begin{equation}
+   \theta_y = E_2 \left(e^{\frac{r}{M_f E_2}} - 1\right).\sin\left(\frac{2 \pi \phi}{W_{nfs}}\right)
+\end{equation}
+where we have dropped the $t$ superscript on $\theta_x$ \& $\theta_y$,
+as these equations transform a collicular location into rotations of
+the eye.
+
+Fig.~\ref{fig:mapping} shows the result of the mapping for a view of
+two cross-shaped luminances. One cross illuminates the fovea, which
+results in a large comb-shape of activity. The more peripheral cross
+produces (in FEF) an indistinct object centred at a larger value of
+$r$.
+
+\subsubsection{Network}
+
+Briefly, the model consists of input from the World population (see
+Fig.~\ref{brain_model}, green population box) producing activity in an
+`express' pathway to superior colliculus (purple) and simultaneously
+in cortex, represented here by the FEF population (grey boxes in
+Fig.~\ref{brain_model}). The express pathway causes short latency
+activity in the superficial superior colliculus, which directly
+innervates the deeper layers of the superior colliculus
+(SC\_deep). Activity in FEF generates firing in a
+thalamo-cortico-basal ganglia loop. The output of the basal ganglia is
+the substantia nigra pars reticulata (SNr) which tonically inhibits
+SC\_deep. If a location of activity in FEF is able to dominate
+selection in the basal ganglia circuit, the corresponding location in
+SNr will dis-inhibit and activity will build up in SC\_deep encoding
+the saccade end point.
+
+Connections shown in red are one to one connections; dark blue
+projections indicate a connectivity pattern which `fans out' with a
+2-D Gaussian kernel; lighter blue connections from the subthalamic
+nucleus (STN) to SNr and globus pallidus externum (GPe) are diffuse,
+all-to-all connections and projections coloured green are one-to-one
+connections that decay towards the fovea so that foveal activity in
+FEF does not swamp the basal ganglia which would prevent peripheral
+luminances from ever being selected.
+%
+Note that SC\_deep contains two recurrent connections; one is
+excitatory, with a Gaussian kernel mapping and the other implements
+tecto-tectal inhibition, which increases the inhibition between
+activity in opposite hemispheres of the field of
+view \citep{gian_g._mascetti_tectotectal_1981,olivier_evidence_2000}
+helping to resolve competition between saccades to the left and
+right. The tecto-tectal inhibitory connection is \e{not} present in
+the \ccg~model. In all other respects the model is as described in
+\cite{cope_basal_2017}.
+%
+We have not listed the parameters of the network in tabular form here,
+instead, the reader is referred to the SpineML declarative
+specification of the model from the link given in SUPPLEMENTAL DATA.
+The easiest way to access this information is by using SpineCreator.
+
+% Section - description of new brainstem model
+\subsection{Brainstem model} \label{sec:methods:brainstem}
+
+We implemented a saccadic burst generator (SBG) based on the
+connectivity outlined in \cite{gancarz_neural_1998}. The SBG network
+for two of the model's six channels is shown in
+Fig.~\ref{sbg}. \rvw{We use the word `channel' to mean a set of
+populations of neurons which are involved in actuating a single
+extraocular muscle. SBG channels are arranged in pairs, actuating
+opposing muscles. There is one pair of channels which actuates the
+superior and inferior rectus muscles, causing vertical rotations of
+the eye in a roughly parasaggital plane (the eye moves up or
+down). Another pair actuates the lateral and medial rectus muscles,
+causing horizontal rotations of the eye. The third pair actuates the
+superior and inferior oblique muscles which contribute to vertical as
+well as oblique rotations.} Activity from the output layer of superior
+colliculus
+%
+(SC\_avg) is fed into each channel, which sums the activity it
+receives and processes it in populations each of a single neural
+element representing all the neurons in that population. Each channel
+of the SBG functions to create the motor neuron activations that are
+required to accelerate the eye in a particular direction, then hold
+the eye in its new position against the returning force generated by
+the elastic properties of the muscles.  The required motor neuron
+activations are therefore a combination of features: a brief burst of
+increased activity that accelerates the eye; followed by a period of
+activity that is less than the burst firing rate but higher than the
+tonic rate that exists when the eye is at the centre. This holds the
+eye in its new position.
+
+The SBG connectivity produces each of the these features separately,
+then sums them to create the desired `bump and tonic' activation time
+series.  The input to the first population in the SBG, the long-lead
+burst neurons (LLBNs), is conceived as originating from one of the
+deep layers of the superior colliculus.  The activity of the LLBNs are
+passed to excitatory burst neurons (EBNs) which, in turn, inhibit the
+LLBNs via the activity of the inhibitory burst neurons (IBNs).  This
+feedback loop has a transmission delay, which allows activity to build
+up in the EBNs before the inhibition is activated and the activity is
+then reduced again.  This mechanism generates the `bump'.
+
+The generation of the `tonic' phase of the required time series is
+achieved simply by integrating the bump over time and multiplying by a
+some small gain factor.  This is the function of the tonic neurons
+(TNs).  The firing rate of the motor neuron defines the amount of
+force applied to the eye by that muscle.  Thus, \rvw{the integral}
+of the `bump'
+defines how far the eye moves in that channel's direction.  The gain
+and delay parameters in the LLBN-EBN-IBN-LLBN feedback loop therefore
+have to be tuned such that the endpoint of the saccade is reasonably
+accurate.  Furthermore the restoring force generated by the elasticity
+of the muscles is dependent on the radial distance.  The value of the
+new tonic firing rate, after the `bump' is dependent on the end
+location of the eye.  If the ratio between the EBN firing rate and the
+TN firing rate is not exactly correct, the eye will drift away from
+the saccade endpoint after the saccade has been completed.  The EBN-TN
+connection strength is therefore tuned such that the TN firing rate
+yields a stable eye position across a range of eye eccentricities.
+
+The omnipause neurons (OPNs) are tonically active and inhibit the
+EBNs.  The activity of the OPNs is itself inhibited by activity in the
+LLBNs.  The purpose of this arrangement is to ensure the eye does not
+move in response to neural noise.
+
+Each mean activity of all the neurons in each SBG population (except
+the TNs) is defined by a single leaky integrator, first order
+differential equation.
+\begin{equation}\label{eq:LIN}
+   \frac{da}{dt} = \frac{1}{\tau}(y-a)
+\end{equation}
+where $a$ is the activation of the nucleus, and $\tau$ is the time
+constant of the nucleus. $y$ is a piecewise linear function of the
+weighted sum of inputs to the nucleus and is given by
+\begin{equation}
+       y(IN) = \begin{cases}
+       0    & IN \leq b \\
+      IN-b   & b \leq IN \leq 1+b \\
+      1   & IN \geq 1+b \\
+   \end{cases}
+\end{equation}
+where $b$ is the $IN$ axis offset.  $IN$ is the weighted sum of inputs
+to the nucleus and is given by,
+\begin{equation}
+    IN = \sum_{m}^{M} w_{mn} a_{m}
+\end{equation}
+where $a_{m}$ is the activation of the $m^{th}$ afferent nucleus.
+$w_{mn}$ is the connection strength between the $m^{th}$ afferent
+nucleus and the current nucleus. The activity of the TNs are defined
+as
+\begin{equation}
+   \frac{da}{dt} = \frac{1}{\tau}\,y
+\end{equation}
+with an identical piecewise linear transfer function as the other SBG
+populations.
+
+% Section - description of biomechanical model
+\subsection{biomechanical eye} \label{sec:methods:eye}
+
+The output signals of the brainstem are used to drive the
+biomechanical model.  The latter is not only used to get tangible
+feedback on the simulated saccades including motion trajectories, but
+adds one more modelling dimension related to the inertial properties
+of the eye plant including muscle properties.
+
+The biomechanical eye model, implemented using the OpenSim framework
+\citep{seth_opensim:_2011}, is anatomically represented by a sphere of
+uniform mass distribution. The diameter of the eye is 24 mm for
+adults, with small variations between individuals; the mass of the eye
+is 7.5 grams.  The eyeball is actuated by six extraocular muscles
+(EOMs). The EOMs are arranged in three pairs forming a cone inside the
+orbit with the apex being located inside the cranium in a tendonous
+ring called the annulus of Zinn. An important feature of the
+oculomotor system which greatly affects its overall behavior is the
+existence of dynamic EOM pulleys. Their role is to guide the pivot
+point of the EOMs. In our model, a pulley for each EOM has been
+modeled by a point on the orbit whose location depends on the current
+eye orientation.
+
+%EOM dynamics
+The force applied by EOMs is controlled by an excitatory signal
+supplied by motoneurons in the brainstem. The neural drive to produce
+a saccadic eye movement can be characterized by a pulse component to
+overcome the viscoelasticity of the orbital plant, a step component to
+stabilize the eye in the new position, and a slide component that
+models the gradual transition between the pulse and step.
+
+The dynamics of muscular forces can be split into: 1) The elasticity
+of the muscles. 2) A delay between the onset of the afferent
+excitatory signal and the actual muscle contraction, caused by the
+transmission time of the action potentials and by the necessary
+calcium release at the muscle fibres. We developed a custom
+extraocular muscle model which captures these features.
+
+% Orbital fat force
+Passive forces due to the fatty tissues inside the eye orbit also
+affect eye dynamics. Their role is critical in eliminating the
+influence of head and body movements. We incorporated a custom torque,
+$\mathbf{t}$, which acts like a rotational spring-damper apparatus,
+resisting eyeball movements. It has elastic and viscous properties
+governed by $\mathbf{t} = -K\mathbf{R}-C\mathbf{U}$ where $\mathbf{R}$
+is the eye's orientation and $\mathbf{U}$ is its angular velocity. $K$
+and $C$ are constants. A fuller description of the biomechanical model
+can be found in \cite{papapavlou_physics-based_2014}.
 
@@
 system (red box).
-
-\subsection{Existing brain model} \label{sec:methods:existing}
-
-% Describe what is modelled first
-The brain model, excluding the brainstem, is a re-implementation of
-the \ccg~model, \rvwt{of reflexive saccadic behaviour \citep{cope_basal_2017}}.
-\rvwt{Reflexive saccades are fast eye movements elicited by abrupt
-changes in the peripheral visual scene (reflexive saccades can occur
-also as a result of auditory and somatosensory stimuli, but these
-modalities are ignored in this model). A reflexive saccade has a
-starting position defined by the initial orientation of the eye and an
-end-point position in which the eye is directed towards a new
-target. Regardless of the number of targets within the visual scene,
-the brain must choose one location as the end-point, because the eyes
-can look only in one direction at a time. The functionality reproduced
-by the \ccg~model is `the selection of the best target end-point for a
-reflexive saccade'. A competition such as this between incompatible
-movements is often referred to as an \e{action selection}
-problem \citep{norman_attention_1986,maes_dynamics_1989,redgrave_basal_1999}.}
-
-\rvwt{One hypothesis for the r\^ole played by the basal ganglia (BG)
-is that the system performs \e{action selection}
-\citep{mink_basal_1996,redgrave_basal_1999,hikosaka_role_2000}.
-The \ccg~model places the BG at the centre of the oculomotor system,
-following the known anatomy of the
-region \citep{hikosaka_role_2000}. The BG receives input indirectly
-from the superior colliculus, which has a retinotopic
-arrangement \citep{ottes_visuomotor_1986}.
-%and a signal which is associated with saccadic eye
-%movements \citep{wurtz_superior_1971}, specifying the saccade
-%end-point.
-The BG receives excitatory
-inputs directly from retinotopic regions of the cortex including the
-frontal eye fields (FEF), supplementary eye fields (SEF), lateral
-intraparietal cortex (LIP) and dorsolateral prefrontal cortex. The
-dorsolateral prefrontal cortex, which participates in voluntary
-saccades
-\citep{funahashi_prefrontal_1993,munoz_look_2004}, is not
-modelled because the model concerns reflexive rather than voluntary
-eye movements. Several other regions of the brain that are associated
-with eye movements are also omitted from the model. The early visual
-processing stream in cortex, from V1, through to the LIP is subsumed
-into a `sustained retinal' signal. The justification here is that the
-model reacts to simple luminant targets and does not need to carry out
-the feature extraction performed by these visual areas. The
-supplementary eye fields are involved in the programming of saccade
-sequences \citep{tehovnik_eye_2000} and memory guided
-saccades \citep{chen_supplementary_1995,schlag_neurons_2002}. Lesions
-of SEF do not affect visually guided
-saccades \citep{gaymard_cortical_1998} and so the SEF is also omitted
-from the model.}
-%
-% Figure here is the ``macroscopic architecture'' one.
-%
-
-% Now describe each bit a little more, with help of the figure.
-\rvwt{Fig.~\ref{fig:ccg_model}(a) shows the macroscopic architecture of
-the \ccg~model. The figure shows the relationships between the retinal
-input populations, the FEF, the populations comprising the BG
-sub-system (the red border indicates that the box represents a number
-of populations as a sub-system), the thalamus and the superior
-colliculus. Excitatory connections are indicated with arrow heads;
-inhibitory connections with circles in place of the arrow heads. The
-blue and green connection lines indicate two thalamo-basal ganglia
-loops, one cortical loop through FEF (green), the other a sub-cortical
-loop through SC. It is important to note that although they are given
-different colours in the diagram, these loops are in no way
-independent, with loop activity combining both in thalamus and in the
-basal ganglia and a direct excitatory, feed-forward connection from
-FEF to SC.}
-
-% More on BG model here
-\rvwt{The basal ganglia sub-system is the most complex component of
-the \ccg~model. The BG model is based on previous
-work \citep{gurney_computational_2001,gurney_computational_2001-1} and is referred to as the GPR
-model. The GPR model incorporates the following main components of the
-primate BG \citep{mink_basal_1996,wickens_basal_1997}: (i) The
-striatum (the main input station to the BG) which is divided into two
-iterdigitated poulations of projection neurons expressing primarily D1
-or D2-type dopaminergic receptors (named Str\_D1 and Str\_D2); (ii)
-The subthalamic nucleus (STN); (iii) the external segment of the
-globus pallidus (GPe); (iv) the output nucleus relevant for saccadic
-control---the substantia nigra pars reticulata
-(SNr) \citep{hikosaka_role_2000}.}
-
-\rvwt{The connectivity of the GPR model (Fig.~\ref{fig:ccg_model}(b)
-is constrained by the known anatomy and physiology of the
-BG~\citep{bolam_synaptic_2000}. Physiologically, the only source of
-glutamate within the BG is the STN, whose projections are therefore
-excitatory; all other nuclei have GABAergic projection neurons and are
-therefore inhibitory. The cortex sends glutamatergic projections to
-both the Str\_D1 striatal population, which projects preferentially to
-the SNr, and to Str\_D2, which projects primarily to
-GPe \citep{gerfen_d1_1990}. The cortex also projects to the STN, which
-sends diffuse projections to the SNr and
-GPe \citep{parent_anatomical_1993}. The GPe projects to the SNr and
-also projects back to the STN, completing a GPe--STN loop.}
-
-\rvwt{Within the BG, there are several mechanisms supporting
-competitive processing for selecting channels whose inhibitory output
-is reduced. The selection mechanism of the GPR model is the
-`off-centre, on-surround' scheme proposed
-by \cite{mink_basal_1993}. The `on-surround' is provided by
-diffuse, excitatory projections from the STN to the SNr. Focussed
-inhibition from the Str\_D1 neurons in striatum contributes the
-`off-centre' part of the mechanism. This arrangement leads to
-selection behaviour via a release of target inhibition, since
-channels that have strong saliencel (input) have weak output at the
-level of SNr, and channels with weak salience have enhanced output.}
-
-\rvwt{The GPe is not included in the centre-surround circuit described
-above, but still plays a key r\^ole in selection. Operating alone, the
-Str\_D1/STN/SNr circuit can suffer from the following problem: if the
-input for all channels is relatively high, then the diffuse projection
-from STN, which effectively supplies a sum of the STN inputs to each
-channel in SNr, will provide so much excitation that Str\_D1 may
-become unable to inhibit one of the channels in SNr and selection may
-become
-impossible. \cite{gurney_computational_2001,gurney_computational_2001-1}
-showed that the inhibitory feedback from GPe to STN acts as an
-`automatic gain control' to help prevent this from occurring.}
-
-\rvwt{At the neuronal level, the STN, GPe and SNr have tonic output
-levels \citep{chevalier_disinhibition_1990,delong_primate_1985,kita_intracellular_1991}. This
-is modelled using piecewise linear output functions with zero offsets,
-$c$ (see Eq.~\ref{eq:lintransfunc}). In striatum, Str\_D1 and Str\_D2
-have positive offset $c$, mimicking the so-called `down-state' of
-medium spiny neurons which have a resting potential far below spiking
-threshold and require co-ordinated input to generate action
-potentials \citep{wilson_origins_1996}.
-% Note, in Cope's paper, there is an error with the offsets for
-% D1,D2. These are set to -0.05 instead of 0.05. A quick trial with
-% the model suggests this doesn't make a very large difference to the
-% operation, and I have the sign correct in any case.
-In addition, the Str\_D1 and Str\_D2 neurons are influenced by
-dopamine in different ways; facilitating cortico-striatal transmission
-at medium spiny neurons with D1 receptors \citep{hernandez-lopez_D1_1997,gonon_prolonged_1997} and reducing
-transmission at those with D2 receptors \citep{delgado_inhibitory_1999}. These effects are
-modelled using a dopamine parameter which modulates the input
-activation as described below in Eqs~\ref{eq:a_in_d1} \& \ref{eq:a_in_d2}.}
-
-% Change this - we already talked about channels?
-\rvwt{The \ccg~model adopts a `channel based' model from previous
-work~\citep{redgrave_basal_1999,gurney_computational_2001}.
-Within the context of the basal ganglia model, a `channel' is a
-sub-set of neurons which are associated with an individual
-action. Each channel in BG loops back via relays in the thalamus
-through cortex. Input into this thalamo-cortical loop is termed
-`salience'. Because it is a loop, input salience to the channel may
-originate cortically or sub-cortically. The higher the salience of the
-channel, the greater is the behavioural relevance of the associated
-action.}
-
-\rvwt{In the oculomotor model, an action
-corresponds to a distinct saccade end point. It can be seen that the
-action space for reflexive saccade end points is therefore
-continuous rather than discrete. MORE HERE}
-
-% FEF stuff taken from Alex's pre-pub
-
-Fig.~\ref{brain_model} shows the layout of the populations in the
-brain model, as implemented in SpineCreator, and the interconnections
-between them. Each population of 2500 elements is arranged as a 50 by
-50 grid which forms a map in a retinotopic co-ordinate system, roughly
-matching the known layout of the superior
-colliculus \citep{robinson_eye_1972}.
-% and frontal eye field?
-
-\subsubsection{Components}
-
-With the exceptions of the World and FEF\_add\_noise populations, each
-neural element represents an activation; the activation is governed by
-a first order differential equation specified in the SpineML
-component. In the brain model, there are six different components in
-use: LINlinear; LINret; LINexp; D1MSN and D2MSN.
-
-The LINlinear component governs the activation $a$ with a first order
-leaky integrator differential equation:
-\begin{equation}
-   \dot{a} = \frac{1}{\tau}(a_{in}-a)
-\end{equation}
-where $\tau$ is the time constant for the neural activation and
-$a_{in}$ is the input to the neural element. $a_{in}$ is defined by an
-activation input and a shunting inhibition input according to:
-\begin{equation}
-   a_{in} = A(1-s_a)+\alpha R_N
-\end{equation}
-Here, $A$ is the activation input and $s_a$ is the shunting inhibition
-state variable whose value is related to the shunting input, $S$ by
-\begin{equation}
-   s_a = \begin{cases}
-      S & S\leq 1 \\
-      1 & S > 1
-   \end{cases}
-\end{equation}
-$R_N$ is a random number drawn from a standard normal distribution
-($\sigma$=1, $\mu$=0) and introduces noise to the activation of the
-neural element, with the parameter $\alpha$ controlling the noise
-amplitude.
-
-The output, $y$, of LINlinear is related to the activation $a$ by the
-piecewise linear transfer function
-\begin{equation} \label{eq:lintransfunc}
-   y(a) = \begin{cases}
-      0   & a < c \\
-      a-c & c \leq a \leq 1+c \\
-      1   & a > 1+c
-   \end{cases}
-\end{equation}
-where $c$ is a parameter defining the offset of the transfer
-function. \rvwt{If $c<0$, then for zero activation ($a=0$), the output
-will be positive. This simulates the effect of a neural population
-having tonic firing. If $c>0$ then the output will be zero until the
-activation exceeds $c$, simulating neurons which only fire when driven
-by excitatory input.} At this point, the naming scheme for the
-component becomes apparent; this is a Leaky Integrator with a
-piecewise-linear transfer function.
-
-The LINret component used for the retinal populations is similar to
-the LINlinear component, but with no intrinsic noise and no shunting
-inhibitory input. It has a neural input which is identical to the
-activation input $A$:
-\begin{equation}
-   a_{in} = A
-\end{equation}
-The LINexp component is a leaky integrator with an exponential
-transfer function. It shares the same differential equation with
-LINlinear, but has a different input equation and a different output
-transfer function. It has the following equation for the neural
-element input $a_{in}$:
-\begin{equation}
-   a_{in} = [A+N(a-V_{r}^{-})] (1-S) + 0.01 R_N
-\end{equation}
-where $A$ is the activation input and $N$ is an input which is
-modulated by $V_{r}^{-}$, a reversal potential, and $a$, the current
-activation of the element. These inputs are summed and then reduced by
-a factor which is dependent on $S$, the shunting input. As in
-LINlinear, $R_N$ introduces normally distributed noise to the element.
-
-The output, $y$, of the LINexp component is given by
-\begin{equation}
-   y(a) = \begin{cases}
-      \mathrm{e}^{a}-0.9   & \mathrm{e}^a \leq 1+0.9 \\
-      1   & \mathrm{e}^a > 1+0.9
-   \end{cases}
-\end{equation}
-This component is used in the subthalamic nucleus (STN) population, as
-it gives a more physiologically accurate f-I
-behaviour
-\citep{wilson_model_2004,bevan_mechanisms_1999,hallworth_apamin-sensitive_2003}
-which has been shown to allow the mapping of the basal ganglia network
-architecture onto an optimal decision making
-model \citep{bogacz_basal_2007}.
-
-The D1MSN and D2MSN components are both leaky integrators, similar to
-LINlinear. They differ in that they have no shunting inhibition. They
-are used to model medium spiny neuron (MSN) populations in the
-striatum. As they model the fact that most MSN neurons fall into two
-groups; those expressing D1 dopamine receptors and those expressing D2
-receptors, they have a dopamine parameter that modulates the input
-activation, so that their equations for $a_{in}$ are thus:
-\begin{equation} \label{eq:a_in_d1}
-   a_{in}^{D1} = (0.2 + d)A + 0.01 R_N
-\end{equation}
-\begin{equation} \label{eq:a_in_d2}
-   a_{in}^{D2} = (1 - d)A + 0.01 R_N
-\end{equation}
-where $d$ is the dopamine parameter. Varying dopamine from 0 to 1
-enhances the activation in the D1 model, whereas it decreases the
-activation of the D2 model elements, in line with experimental
-observations \citep{harsing_influence_1997,gonon_prolonged_1997}.
-Note that the equation for $a_{in}^{D1}$ differs from that used in
-the \ccg~model, for which the cortico-striatal weights are multiplied
-by $(1+d)$ rather than $(0.2+d)$.
-
-The equations given above are applied to each element in a
-population. The value of the activation $A$ (and where relevant, the
-shunting input, $S$) is determined by summing the weighted inputs to
-the population:
-\begin{equation}
-A = \sum_{i}w_i^{act} x_i^{act}
-\end{equation}
-\begin{equation}
-S = \sum_{i}w_i^{sh} x_i^{sh}
-\end{equation}
-$w_i^{act}$ and $w_i^{sh}$ are, respectively, the weights of the
-$i^{th}$ activation or shunting connection; $x_i^{act}$ and $x_i^{sh}$
-are the signals input to the activation and shunting connections.
-
-\subsubsection{Population activity and retinotopic mapping}
-\label{sec:mapping}
-
-Each population of 2500 neural elements was arranged in a 50 by 50
-grid, with positions on the grid representing a retinotopic mapping
-similar to that found empirically both in the superior
-colliculus \citep{ottes_visuomotor_1986} and in visual cortex
-\citep{eric_l._schwartz_computational_1980}
-and assumed in this work to persist throughout the oculomotor system.
-
-In a retinotopic mapping, the Cartesian co-ordinates of the
-light-sensitive cells in the retina, whose density varies with
-distance from the fovea, are transformed into the Cartesian
-co-ordinates of the correspondingly active cells on the
-colliculus. The mapping ensures that an even density of cells can be
-maintained in the colliculus, but ensures that a group of adjoining,
-active, retinal neurons will always activate an adjoining group of
-neurons on the collicular surface.
-
-The mapping turns out to resemble polar co-ordinates. That is, one
-axis of the collicular surface specifies the eccentricity of a retinal
-location (how far it is from the fovea) and the second axis specifies
-the rotational angle of the retinal location; we therefore use the
-convention of referring to the eccentricity axis on the colliculus as
-$r$ and the rotation axis as $\phi$.
-
-The \e{cortical magnification factor}, $M(r)$, gives the relationship
-between the radial eccentricity $r$ and the retinal neural density. As
-in
-\cite{cope_basal_2017}, we use a first-order approximation of the form
-for $M(r)$ given in \cite{rovamo_estimation_1979}:
-\begin{equation} \label{eq:cmf}
-M(r) = \frac{M_f}{1+\frac{r}{E_2}}
-\end{equation}
-The foveal magnification, $M_f$, is the magnification of the most
-central region of the retina and has a value in the human of about 7.8
-mm/\dg~\citep{rovamo_estimation_1979}.
-
-In our model, $M_f$ is related to $W_{nfs}$, the width of the
-retinotopic neural field, $W_{fov}$, the width of the eye's field of
-view and $E_2$, the eccentricity at which the retinal density has
-halved by:
-\begin{equation} \label{eq:fm}
-   M_f = \frac {W_{nfs}} {E_2\;\ln\left(\frac{W_{fov}}{2 E_2} + 1\right)}
-\end{equation}
-Here, $W_{nfs}$ is 50 (the side length of the 50x50 grid) and
-$W_{fov}$ is set to 61\dg, a reduction from the biophysically accurate
-150\dg~due to the small number of neurons in the retinotopic neural
-field. $E_2$ is
-2.5 \citep{cope_basal_2017,slotnick_electrophysiological_2001}.
-
-The mapping from the retinotopic co-ordinates in the brain to
-rotational co-ordinates of the stimulus/response was written down by
-\cite{schwartz_spatial_1977,eric_l._schwartz_computational_1980}
-for measurements of striate cortex [visual stimulus to
-electrophysiological response---\cite{daniel_representation_1961,
-talbot_physiological_1941}] and by \cite{ottes_visuomotor_1986} for
-superior colliculus data [electrophysiological SC stimulus to eye
-movement response---\cite{robinson_eye_1972}].
-% Ottes et al. fit to stimulus-to-movement data, and give a
-% movement-to-collicular-coordinate mapping in the paper.
-We used the following statement of this mapping to introduce stimuli
-into the `World' input population of the brain model:
-\begin{equation}\label{eq:thetas_to_phi}
-   \phi = \frac{W_{nfs}} {2 \pi}\arctan\left(\frac{\theta_{y}^{t}}{\theta_{x}^{t}}\right)
-\end{equation}
-\begin{equation}\label{eq:thetas_to_r}
-   r = M_fE_2\,\ln\left(\frac{1}{E_2}\sqrt{{\theta_{x}^{t}}^2 + {\theta_{y}^{t}}^2}+1\right)
-\end{equation}
-Note that we use $r$ and $\phi$ as the co-ordinates on the `collicular
-surface'. Schwartz uses $r$ and $\phi$ as the polar coordinates of the
-retinal stimulus; Ottes et al.~use $r$ and $\phi$ as polar coordinates
-for the eye movement response; both use $u$ and $v$ as the Cartesian
-co-ordinates of the neural map. We use $\theta_{x}^{t}$ and
-$\theta_{y}^{t}$ to give Euler rotations for the retinal target
-stimulus. Note also that the form of
-Eqns.~\ref{eq:thetas_to_phi} \& \ref{eq:thetas_to_r} is slightly
-different from that given in
-\cite{ottes_visuomotor_1986} because our $\theta_{x}^{t}$ and
-$\theta_{y}^{t}$ are not the polar co-ordinates used in that work.
-
-The mapping encompases the entire visual field; the value of $\phi$ is
-allowed to vary from 0\dg~to 360\dg~along its axis.  Effectively, the
-two contralateral colliculi found in the biology are incorporated into
-a single, square map, avoiding the need to carry out the kind of
-`colliculus gluing' described in \cite{tabareau_geometry_2007}.
-
-It is straightforward to show that the reverse mapping is given by:
-\begin{equation}
-   \theta_x = E_2 \left(e^{\frac{r}{M_f E_2}} - 1\right).\cos\left(\frac{2 \pi \phi}{W_{nfs}}\right)
-\end{equation}
-\begin{equation}
-   \theta_y = E_2 \left(e^{\frac{r}{M_f E_2}} - 1\right).\sin\left(\frac{2 \pi \phi}{W_{nfs}}\right)
-\end{equation}
-where we have dropped the $t$ superscript on $\theta_x$ \& $\theta_y$,
-as these equations transform a collicular location into rotations of
-the eye.
-
-Fig.~\ref{fig:mapping} shows the result of the mapping for a view of
-two cross-shaped luminances. One cross illuminates the fovea, which
-results in a large comb-shape of activity. The more peripheral cross
-produces (in FEF) an indistinct object centred at a larger value of
-$r$.
-
-\subsubsection{Network}
-
-Briefly, the model consists of input from the World population (see
-Fig.~\ref{brain_model}, green population box) producing activity in an
-`express' pathway to superior colliculus (purple) and simultaneously
-in cortex, represented here by the FEF population (grey boxes in
-Fig.~\ref{brain_model}). The express pathway causes short latency
-activity in the superficial superior colliculus, which directly
-innervates the deeper layers of the superior colliculus
-(SC\_deep). Activity in FEF generates firing in a
-thalamo-cortico-basal ganglia loop. The output of the basal ganglia is
-the substantia nigra pars reticulata (SNr) which tonically inhibits
-SC\_deep. If a location of activity in FEF is able to dominate
-selection in the basal ganglia circuit, the corresponding location in
-SNr will dis-inhibit and activity will build up in SC\_deep encoding
-the saccade end point.
-
-Connections shown in red are one to one connections; dark blue
-projections indicate a connectivity pattern which `fans out' with a
-2-D Gaussian kernel; lighter blue connections from the subthalamic
-nucleus (STN) to SNr and globus pallidus externum (GPe) are diffuse,
-all-to-all connections and projections coloured green are one-to-one
-connections that decay towards the fovea so that foveal activity in
-FEF does not swamp the basal ganglia which would prevent peripheral
-luminances from ever being selected.
-%
-Note that SC\_deep contains two recurrent connections; one is
-excitatory, with a Gaussian kernel mapping and the other implements
-tecto-tectal inhibition, which increases the inhibition between
-activity in opposite hemispheres of the field of
-view \citep{gian_g._mascetti_tectotectal_1981,olivier_evidence_2000}
-helping to resolve competition between saccades to the left and
-right. The tecto-tectal inhibitory connection is \e{not} present in
-the \ccg~model. In all other respects the model is as described in
-\cite{cope_basal_2017}.
-%
-We have not listed the parameters of the network in tabular form here,
-instead, the reader is referred to the SpineML declarative
-specification of the model from the link given in SUPPLEMENTAL DATA.
-The easiest way to access this information is by using SpineCreator.
-
-% Section - description of new brainstem model
-\subsection{Brainstem model} \label{sec:methods:brainstem}
-
-We implemented a saccadic burst generator (SBG) based on the
-connectivity outlined in \cite{gancarz_neural_1998}. The SBG network
-for two of the model's six channels is shown in
-Fig.~\ref{sbg}. \rvw{We use the word `channel' to mean a set of
-populations of neurons which are involved in actuating a single
-extraocular muscle. SBG channels are arranged in pairs, actuating
-opposing muscles. There is one pair of channels which actuates the
-superior and inferior rectus muscles, causing vertical rotations of
-the eye in a roughly parasaggital plane (the eye moves up or
-down). Another pair actuates the lateral and medial rectus muscles,
-causing horizontal rotations of the eye. The third pair actuates the
-superior and inferior oblique muscles which contribute to vertical as
-well as oblique rotations.} Activity from the output layer of superior
-colliculus
-%
-(SC\_avg) is fed into each channel, which sums the activity it
-receives and processes it in populations each of a single neural
-element representing all the neurons in that population. Each channel
-of the SBG functions to create the motor neuron activations that are
-required to accelerate the eye in a particular direction, then hold
-the eye in its new position against the returning force generated by
-the elastic properties of the muscles.  The required motor neuron
-activations are therefore a combination of features: a brief burst of
-increased activity that accelerates the eye; followed by a period of
-activity that is less than the burst firing rate but higher than the
-tonic rate that exists when the eye is at the centre. This holds the
-eye in its new position.
-
-The SBG connectivity produces each of the these features separately,
-then sums them to create the desired `bump and tonic' activation time
-series.  The input to the first population in the SBG, the long-lead
-burst neurons (LLBNs), is conceived as originating from one of the
-deep layers of the superior colliculus.  The activity of the LLBNs are
-passed to excitatory burst neurons (EBNs) which, in turn, inhibit the
-LLBNs via the activity of the inhibitory burst neurons (IBNs).  This
-feedback loop has a transmission delay, which allows activity to build
-up in the EBNs before the inhibition is activated and the activity is
-then reduced again.  This mechanism generates the `bump'.
-
-The generation of the `tonic' phase of the required time series is
-achieved simply by integrating the bump over time and multiplying by a
-some small gain factor.  This is the function of the tonic neurons
-(TNs).  The firing rate of the motor neuron defines the amount of
-force applied to the eye by that muscle.  Thus, \rvw{the integral}
-of the `bump'
-defines how far the eye moves in that channel's direction.  The gain
-and delay parameters in the LLBN-EBN-IBN-LLBN feedback loop therefore
-have to be tuned such that the endpoint of the saccade is reasonably
-accurate.  Furthermore the restoring force generated by the elasticity
-of the muscles is dependent on the radial distance.  The value of the
-new tonic firing rate, after the `bump' is dependent on the end
-location of the eye.  If the ratio between the EBN firing rate and the
-TN firing rate is not exactly correct, the eye will drift away from
-the saccade endpoint after the saccade has been completed.  The EBN-TN
-connection strength is therefore tuned such that the TN firing rate
-yields a stable eye position across a range of eye eccentricities.
-
-The omnipause neurons (OPNs) are tonically active and inhibit the
-EBNs.  The activity of the OPNs is itself inhibited by activity in the
-LLBNs.  The purpose of this arrangement is to ensure the eye does not
-move in response to neural noise.
-
-Each mean activity of all the neurons in each SBG population (except
-the TNs) is defined by a single leaky integrator, first order
-differential equation.
-\begin{equation}\label{eq:LIN}
-   \frac{da}{dt} = \frac{1}{\tau}(y-a)
-\end{equation}
-where $a$ is the activation of the nucleus, and $\tau$ is the time
-constant of the nucleus. $y$ is a piecewise linear function of the
-weighted sum of inputs to the nucleus and is given by
-\begin{equation}
-       y(IN) = \begin{cases}
-       0    & IN \leq b \\
-      IN-b   & b \leq IN \leq 1+b \\
-      1   & IN \geq 1+b \\
-   \end{cases}
-\end{equation}
-where $b$ is the $IN$ axis offset.  $IN$ is the weighted sum of inputs
-to the nucleus and is given by,
-\begin{equation}
-    IN = \sum_{m}^{M} w_{mn} a_{m}
-\end{equation}
-where $a_{m}$ is the activation of the $m^{th}$ afferent nucleus.
-$w_{mn}$ is the connection strength between the $m^{th}$ afferent
-nucleus and the current nucleus. The activity of the TNs are defined
-as
-\begin{equation}
-   \frac{da}{dt} = \frac{1}{\tau}\,y
-\end{equation}
-with an identical piecewise linear transfer function as the other SBG
-populations.
-
-% Section - description of biomechanical model
-\subsection{biomechanical eye} \label{sec:methods:eye}
-
-The output signals of the brainstem are used to drive the
-biomechanical model.  The latter is not only used to get tangible
-feedback on the simulated saccades including motion trajectories, but
-adds one more modelling dimension related to the inertial properties
-of the eye plant including muscle properties.
-
-The biomechanical eye model, implemented using the OpenSim framework
-\citep{seth_opensim:_2011}, is anatomically represented by a sphere of
-uniform mass distribution. The diameter of the eye is 24 mm for
-adults, with small variations between individuals; the mass of the eye
-is 7.5 grams.  The eyeball is actuated by six extraocular muscles
-(EOMs). The EOMs are arranged in three pairs forming a cone inside the
-orbit with the apex being located inside the cranium in a tendonous
-ring called the annulus of Zinn. An important feature of the
-oculomotor system which greatly affects its overall behavior is the
-existence of dynamic EOM pulleys. Their role is to guide the pivot
-point of the EOMs. In our model, a pulley for each EOM has been
-modeled by a point on the orbit whose location depends on the current
-eye orientation.
-
-%EOM dynamics
-The force applied by EOMs is controlled by an excitatory signal
-supplied by motoneurons in the brainstem. The neural drive to produce
-a saccadic eye movement can be characterized by a pulse component to
-overcome the viscoelasticity of the orbital plant, a step component to
-stabilize the eye in the new position, and a slide component that
-models the gradual transition between the pulse and step.
-
-The dynamics of muscular forces can be split into: 1) The elasticity
-of the muscles. 2) A delay between the onset of the afferent
-excitatory signal and the actual muscle contraction, caused by the
-transmission time of the action potentials and by the necessary
-calcium release at the muscle fibres. We developed a custom
-extraocular muscle model which captures these features.
-
-% Orbital fat force
-Passive forces due to the fatty tissues inside the eye orbit also
-affect eye dynamics. Their role is critical in eliminating the
-influence of head and body movements. We incorporated a custom torque,
-$\mathbf{t}$, which acts like a rotational spring-damper apparatus,
-resisting eyeball movements. It has elastic and viscous properties
-governed by $\mathbf{t} = -K\mathbf{R}-C\mathbf{U}$ where $\mathbf{R}$
-is the eye's orientation and $\mathbf{U}$ is its angular velocity. $K$
-and $C$ are constants. A fuller description of the biomechanical model
-can be found in \cite{papapavlou_physics-based_2014}.
 
@@
 \begin{center}
-\includegraphics[width=0.9\textwidth]{./figures/model_framework.png}
-\end{center}
-\textbf{\refstepcounter{figure}\label{model_framework} Figure \arabic{figure}.}
-{ The model framework. The model is specified using a combination of
-declarative XML files and hand-coded C++. These original model
-specifications are shown within the blue box. b) The green box shows
-the processes which are applied to the model specification to produce
-the BRAHMS system. Most of the process is defined within the scripts
-which make up \stob, but the hand-written components must be manually
-compiled and installed within the BRAHMS Namespace, allowing the
-BRAHMS executable to locate them at runtime. c) The red box shows the
-resulting BRAHMS system ready to be executed by the BRAHMS
-executable. In practice, this call is made by \stob.}
-\end{figure}
-
-\begin{figure}[htb!]
-\begin{center}
-\includegraphics[width=0.9\textwidth]{./figures/ccg_model.png}
+\includegraphics[width=0.8\textwidth]{./figures/ccg_model.png}
 \end{center}
 \textbf{\refstepcounter{figure}\label{fig:ccg_model} Figure \arabic{figure}.}
-{ The macroscopic architecture of the \ccg~model. The main nuclei
-modelled as brain systems are: basal ganglia (BG), frontal eye fields
-(FEF), thalamus (THAL) and superior colliculus (SC). The retinal input
-is presented via non-biologically plausible retinal populations. The
-loops through basal ganglia, which define the architecture, are shown
-with coloured lines: the cortical loop (through FEF and THAL) in green
-and the sub-cortical loop (through SC and THAL) in blue. Connections
-with arrowheads indicate excitatory connections, those with circles
-are inhibitory. A red border indicates that the box represents a
-sub-system of two or more populations; a black box indicates,
-within the context of the model, a single neural population.}
+{ \bol{a) The macroscopic architecture of the \ccg~model.} The main
+nuclei modelled as brain systems are: basal ganglia (BG), frontal eye
+fields (FEF), thalamus (THAL) and superior colliculus (SC). The
+retinal input is presented via non-biologically plausible retinal
+populations. The loops through basal ganglia, which define the
+architecture, are shown with coloured lines: the cortical loop
+(through FEF and THAL) in green and the sub-cortical loop (through SC
+and THAL) in blue. Connections with arrowheads indicate excitatory
+connections, those with circles are inhibitory. A red border indicates
+that the box represents a sub-system of two or more populations; a
+black box indicates (at least, within the context of the model) a
+single neural population. The BG box is expanded in: \bol{b) The basal
+ganglia model component.}
+%
+This shows a basal ganglia comprising striatum (Str\_D1 \& Str\_D2),
+subthalamic nucleus (STN), globus pallidum externum (GPe) and
+substantia nigra reticulata (SNr). The model has three action channels
+shown as black boxes within each blue population border. Three
+channels of cortical input to the BG are also depicted. Red indicates
+the activation level of a given channel, helping to illustrate the
+selection mechanism. For example, the channel indicated by the
+leftmost bar has a high salience (cortical input) and excites activity
+in Str\_D1 which then inhibits the leftmost bar in SNr. The diffuse
+projection from STN is equivalent to summing its projections
+channel-wise, and then projecting the sum to all channels of its
+target populations (the blue arrows indicate that all channels of GPe
+and SNr are targeted by the connection). Dopaminergic modulation of
+the inputs to the striatum are indicated by the blue circles labelled
+`d' and the dotted lines. The SNr sends inhibitory output projections
+to its targets.}
 \end{figure}
@@
 \begin{center}
+\includegraphics[width=0.9\textwidth]{./figures/model_framework.png}
+\end{center}
+\textbf{\refstepcounter{figure}\label{model_framework} Figure \arabic{figure}.}
+{ The model framework. The model is specified using a combination of
+declarative XML files and hand-coded C++. These original model
+specifications are shown within the blue box. b) The green box shows
+the processes which are applied to the model specification to produce
+the BRAHMS system. Most of the process is defined within the scripts
+which make up \stob, but the hand-written components must be manually
+compiled and installed within the BRAHMS Namespace, allowing the
+BRAHMS executable to locate them at runtime. c) The red box shows the
+resulting BRAHMS system ready to be executed by the BRAHMS
+executable. In practice, this call is made by \stob.}
+\end{figure}
+
+\begin{figure}[htb!]
+\begin{center}
 \includegraphics[width=0.5\textwidth]{./figures/SC_to_brainstem.png}

### 2017-11-19 papers/integration/omm_integ.tex
A few more lines...

@@
 % can then lead on to Fig 3.
-\rvwt{Expand along lines of `the
-action space for reflexive saccade end points is therefore
-continuous rather than discrete' (FIXME).}
+\rvwt{The GPR model in Fig.~\ref{ccg_model}(b) has only three
+channels with focussed inhibition from striatum to SNr and GPe defined
+by a simple one-to-one scheme. The action channels represent discrete,
+incompatible motor action choices. In the oculomotor model, an action
+channel might represent the end-point of saccade, and the competition
+carried out in the basal ganglia is between potential saccade
+end-points. However, eye movements have a \e{continuous} end-point
+space; the eye can rotate to any orientation within its
+biomechanically permissible range. Some end-points within this range
+are certainly mutually exclusive---it's not possible to look to the
+left and to the right simultaneously---but \e{nearby} end-points are
+not necessarily incompatible. A small enough error in the end-point of
+a saccade will not prevent the eye from foveating on a target as the
+fovea is not infinitesimally small. To cope with this requirement,
+the populations within the oculomotor basal ganglia are conceived of
+as two-dimensional topographic grids of neural elements. Activity in
+each element corresponds to a spatial location in the visual
+field. \cite{someref} here.}
 

### 2017-11-19 papers/integration/omm_integ.tex
Adds KM's reviewer response contribution

@@
 
+% KM
+An illustration of the biomechanical eye model is given in
+Figure \ref{fig:eye_muscles}, while Figure \ref{fig:eye_head} depicts
+the head model used in the proposed framework.
+
+\begin{figure}[htb!]
+\begin{center}
+\includegraphics[width=0.5\textwidth]{./figures/bio_eye1.png}
+\end{center}
+\textbf{\refstepcounter{figure}\label{fig:eye_muscles} Figure \arabic{figure}.}
+{Example of the biomechanical eye model.}
+\end{figure}
+
+\begin{figure}[htb!]
+\begin{center}
+\includegraphics[width=0.5\textwidth]{./figures/bio_eye2.png}
+\end{center}
+\textbf{\refstepcounter{figure}\label{fig:eye_head} Figure \arabic{figure}.}
+{Example of the head model used.}
+\end{figure}
+
+% KM
+Two types of muscle models of different complexity are supported. The
+first models muscles using linear path actuators. This simplistic
+model of ideal muscles can be easily integrated with high level brain
+models. As described above the muscles are wrapped around the eye.
+The more complex model supported is based on the Thelen model
+[Thelen_ref.ris] that is also supported by OpenSim and implements
+Hill-type muscles. It includes realistic muscle wrapping geometric
+entities of the muscle fibers, while it accommodates for both
+activation and contraction dynamics.  The dynamics of muscular forces
+can be split into: 1) The elasticity of the muscles. 2) A delay
+between the onset of the afferent excitatory signal and the actual
+muscle contraction, caused by the transmission time of the action
+potentials and by the necessary calcium release at the muscle fibres.
+
 %EOM dynamics
@@
 models the gradual transition between the pulse and step.
-
-The dynamics of muscular forces can be split into: 1) The elasticity
-of the muscles. 2) A delay between the onset of the afferent
-excitatory signal and the actual muscle contraction, caused by the
-transmission time of the action potentials and by the necessary
-calcium release at the muscle fibres. We developed a custom
-extraocular muscle model which captures these features.
 
@@
 system (red box).
+
+% KM
+Finally, numerical integration of the biomechanical eye model is based
+on the Kutta-Merson integration method.
+
+% KM
+Figure \ref{fig:eye_sim0} illustrates an example of the experimental
+set-up of the proposed framework, while Figures \ref{fig:eye_sim1}
+and \ref{fig:eye_sim2} depict the developed eye oculomotor simulation
+system.
+
+\begin{figure}[htb!]
+\begin{center}
+\includegraphics[width=0.5\textwidth]{./figures/Eye_sim0.png}
+\end{center}
+\textbf{\refstepcounter{figure}\label{fig:eye_sim0} Figure \arabic{figure}.}
+{Example of the experimental set-up.}
+\end{figure}
+
+\begin{figure}[htb!]
+\begin{center}
+\includegraphics[width=0.5\textwidth]{./figures/Eye_sim1.png}
+\end{center}
+\textbf{\refstepcounter{figure}\label{fig:eye_sim1} Figure \arabic{figure}.}
+{Example of the eye simulator system.}
+\end{figure}
+
+\begin{figure}[htb!]
+\begin{center}
+\includegraphics[width=0.5\textwidth]{./figures/Eye_sim2.png}
+\end{center}
+\textbf{\refstepcounter{figure}\label{fig:eye_sim2} Figure \arabic{figure}.}
+{Example of use of the eye simulator system.}
+\end{figure}
 

### 2017-11-20 papers/integration/omm_integ.tex
Current work in progress, Mon morning switching from laptop to desktop

@@
 % Section - description of biomechanical model
-\subsection{biomechanical eye} \label{sec:methods:eye}
+\subsection{Biomechanical eye} \label{sec:methods:eye}
 
@@
 % KM
-An illustration of the biomechanical eye model is given in
+\rvwt{An illustration of the biomechanical eye model is given in
 Figure \ref{fig:eye_muscles}, while Figure \ref{fig:eye_head} depicts
-the head model used in the proposed framework.
-
+the head model used in the proposed framework.}
+
+% To be moved in due course
 \begin{figure}[htb!]
@@
 % KM
-Two types of muscle models of different complexity are supported. The
+\rvwt{Two types of muscle models of different complexity are supported. The
 first models muscles using linear path actuators. This simplistic
@@
 The more complex model supported is based on the Thelen model
-[Thelen_ref.ris] that is also supported by OpenSim and implements
+\citep{thelen_adjustment_2003} that is also supported by OpenSim and implements
 Hill-type muscles. It includes realistic muscle wrapping geometric
@@
 muscle contraction, caused by the transmission time of the action
-potentials and by the necessary calcium release at the muscle fibres.
-
-%EOM dynamics
+potentials and by the necessary calcium release at the muscle fibres.}
+
+% EOM dynamics
 The force applied by EOMs is controlled by an excitatory signal
@@
 % KM
-Finally, numerical integration of the biomechanical eye model is based
-on the Kutta-Merson integration method.
+\rvwt{Finally, numerical integration of the biomechanical eye model is based
+on the Kutta-Merson integration method.}
 
 % KM
-Figure \ref{fig:eye_sim0} illustrates an example of the experimental
+\rvwt{Figure \ref{fig:eye_sim0} illustrates an example of the experimental
 set-up of the proposed framework, while Figures \ref{fig:eye_sim1}
 and \ref{fig:eye_sim2} depict the developed eye oculomotor simulation
-system.
-
+system.}
+
+% Figures to merge together into a single panel or move.
 \begin{figure}[htb!]
@@
 % Section - description of the integration. scientific and
-% technical. Already
+% technical.
 \subsection{Integrating the models and closing the loop}

### 2017-11-20 papers/integration/omm_integ.tex
Monday work on revisions

@@
 % Aliases
-\newcommand{\ccg}{Cope-Chambers-Prescott-Gurney}
+\newcommand{\ccg}{Cope-Chambers} % Omit Prescott-Gurney from the name,
+                                % too unweildy.
 \newcommand{\stob}{SpineML\_2\_BRAHMS}
@@
 
-% Describe what is modelled first
+% Describe what is modelled first. This para is 'The OM system
+% performs action selection and the BG will do that for us.'
 The brain model, excluding the brainstem, is a re-implementation of
@@
 movements is often referred to as an \e{action selection}
-problem \citep{norman_attention_1986,maes_dynamics_1989,redgrave_basal_1999}.}
-
-\rvwt{One hypothesis for the r\^ole played by the basal ganglia (BG)
-is that the system performs \e{action selection}
+problem \citep{norman_attention_1986,maes_dynamics_1989,redgrave_basal_1999}.
+The \ccg~model is therefore a model of action-selection in the
+oculomotor system for reflexive saccades.  One hypothesis for the
+r\^ole played by the basal ganglia (BG) is that the system
+performs \e{action selection}
 \citep{mink_basal_1996,redgrave_basal_1999,hikosaka_role_2000}.
-The \ccg~model places the BG at the centre of the oculomotor system,
-following the known anatomy of the
-region \citep{hikosaka_role_2000}. The BG receives input indirectly
-from the superior colliculus, which has a retinotopic
-arrangement \citep{ottes_visuomotor_1986}.
-%and a signal which is associated with saccadic eye
-%movements \citep{wurtz_superior_1971}, specifying the saccade
-%end-point.
-The BG receives excitatory
-inputs directly from retinotopic regions of the cortex including the
-frontal eye fields (FEF), supplementary eye fields (SEF), lateral
-intraparietal cortex (LIP) and dorsolateral prefrontal cortex. The
-dorsolateral prefrontal cortex, which participates in voluntary
-saccades
+The \ccg~model places the BG at the centre of the oculomotor system;
+this follows the known anatomy of the
+region \citep{hikosaka_role_2000} and provides a mechanism for action
+selection of the best saccade. The BG receives input indirectly from
+the superior colliculus, which has a retinotopic
+arrangement \citep{ottes_visuomotor_1986}.}
+
+% This para describes some anatomical stuff, and talks about what was
+% omitted from the ccg model.
+\rvwt{The BG receives excitatory inputs directly from retinotopic regions of
+the cortex including the frontal eye fields (FEF), supplementary eye
+fields (SEF), lateral intraparietal cortex (LIP) and dorsolateral
+prefrontal cortex. The dorsolateral prefrontal cortex, which
+participates in voluntary saccades
 \citep{funahashi_prefrontal_1993,munoz_look_2004}, is not
@@
 
-% More on BG model here
+% More on BG model and mechanism; GPR recap
 \rvwt{The basal ganglia sub-system is the most complex component of
@@
 
+% More GPR recap
 \rvwt{The connectivity of the GPR model [Fig.~\ref{fig:ccg_model}(b)]
@@
 
+% GPR model and action channels
 \rvwt{The GPR model is arranged into `action channels';
@@
 
+% BG selection mechanism in GPR model
 \rvwt{Within the BG, there are several mechanisms supporting
@@
 
+% BG mechanism - GPe's role
 \rvwt{The GPe is not included in the centre-surround circuit described
@@
 
+% Dopamine, tonic output.
 \rvwt{At the neuronal level, the STN, GPe and SNr have tonic output
@@
 dopamine in different ways; facilitating cortico-striatal transmission
-at medium spiny neurons with D1 receptors \citep{hernandez-lopez_D1_1997,gonon_prolonged_1997} and reducing
-transmission at those with D2 receptors \citep{delgado_inhibitory_1999}. These effects are
-modelled using a dopamine parameter which modulates the input
-activation as described below in
-Eqs~\ref{eq:a_in_d1} \& \ref{eq:a_in_d2}; Str\_D1 activation is enhanced;
-Str\_D2 activation is suppressed.}
+at medium spiny neurons with D1
+receptors \citep{hernandez-lopez_D1_1997,gonon_prolonged_1997} and
+reducing transmission at those with D2
+receptors \citep{delgado_inhibitory_1999}. These effects are modelled
+using a dopamine parameter, $d$, which modulates the input activations
+$a_{in}^D1$ and $a_{in}^D1$ as:
+\begin{equation}
+   a_{in}^{D1} = (0.2 + d)A
+\end{equation}
+\begin{equation}
+   a_{in}^{D2} = (1 - d)A
+\end{equation}
+where $A$ is the input activation (see also
+Eqns.~\ref{eq:a_in_d1} \& \ref{eq:a_in_d2}). For the `normal, healthy'
+value for $d$ of 0.7, Str\_D1 activation is relatively enhanced
+(0.9$A$); Str\_D2 activation is one third of this value (0.3$A$). The
+major effect of this difference in the relative strength of the
+activity in Str\_D1 versus Str\_D2 is simply that a change in the
+level of activity in Str\_D1 affects the off-centre, on-surround
+mechanism. The effect of varying the input into Str\_D2 is much more
+subtle, with only a small change in the amount of inhibition fed from
+GPe into STN (via a focussed, one to one connection) being affected by
+the change, along with a small change in the inhibition fed into SNr
+from GPe (also via a one to one connection). It is not possible to
+clearly describe the dynamic effect of the dopamine parameter as being
+due to any single population, because the activity is recurrently
+connected through multiple loops. Thus, a line of reasoning such as
+``reduced activity for a luminance in Str\_D2 will lead to less
+inhibition in that region in GPe, which means that there will be
+higher activity there, and hence more inhibition for that region
+passed to STN leading us to expect less activity in STN'' is verified
+by running a suitable simulation with the model, but the effect is
+small. }
+%
+\rvwt{Note that
+the effect of dopamine in the model is only to modulate the strength
+of cortico-striatal synapses; no learning is modelled and so the
+significance of dopamine as a prediction error signal is outside the
+scope of the current work.}
 
 % Change this - we already talked about channels in the context of the
-% three channel model show. Perhaps modify to talk about how we have a
-% map of channels - almost a continuous space in the \ccg model. This
-% can then lead on to Fig 3.
+% three channel model shown. Now talk about how we have a map of
+% channels - a continuous space in the \ccg model. This can then lead
+% on to Fig 3.
 \rvwt{The GPR model in Fig.~\ref{ccg_model}(b) has only three
-channels with focussed inhibition from striatum to SNr and GPe defined
-by a simple one-to-one scheme. The action channels represent discrete,
-incompatible motor action choices. In the oculomotor model, an action
-channel might represent the end-point of saccade, and the competition
-carried out in the basal ganglia is between potential saccade
-end-points. However, eye movements have a \e{continuous} end-point
-space; the eye can rotate to any orientation within its
+channels, with the focussed inhibition from striatum to SNr and GPe
+defined by a simple one-to-one scheme. The action channels represent
+discrete, incompatible motor action choices. In the oculomotor model,
+an action channel represents the end-point of saccade, and the
+competition carried out in the basal ganglia is between potential
+saccade end-points. However, eye movements have a \e{continuous}
+end-point space; the eye can rotate to any orientation within its
 biomechanically permissible range. Some end-points within this range
-are certainly mutually exclusive---it's not possible to look to the
-left and to the right simultaneously---but \e{nearby} end-points are
-not necessarily incompatible. A small enough error in the end-point of
-a saccade will not prevent the eye from foveating on a target as the
-fovea is not infinitesimally small. To cope with this requirement,
-the populations within the oculomotor basal ganglia are conceived of
-as two-dimensional topographic grids of neural elements. Activity in
-each element corresponds to a spatial location in the visual
-field. \cite{someref} here.}
+are mutually exclusive---it's not possible to look to the left and to
+the right simultaneously---but \e{nearby} end-points are not
+necessarily incompatible. A small enough error in the end-point of a
+saccade will not prevent the eye from foveating on a target as the
+foveal region of high visual acuity is not infinitesimally small. To
+cope with this requirement, the populations within the oculomotor
+basal ganglia are conceived of as two-dimensional topographic grids of
+leaky integrator neural elements. Activity in each element corresponds
+to a spatial location in the visual field. Neighbouring elements
+correspond to locations which are close to each other in the visual
+field. Focussed one-to-one projections in the GPR model are replaced
+by projective fields with many weighted connections. Specifically,
+each unit in Str\_D1 projected to a counterpart SNr$_j$ in SNr with
+some weight $w_{max}$, but also connected to neighbouring nodes in SNr
+with a weight given by $w_{max}.G(d)$, where $G(d)$ is a circularly
+symmetric, 2D-Gaussian which is a function of distance $d$ from
+SNr$_j$ [Fig.~\ref{fig:ccg_model}(c)]. A similar scheme applied for
+the connectivity from Str\_D2 to GPe and for a number of the other
+connections in the \ccg~model; in the SpineML implementation of the
+model, this connectivity scheme is named `GaussianKernel'.
+% NB - having this Fig. ref here is important for figure ordering!
+Fig.~\ref{brain_model} shows a schematic of the SpineML implementation
+of the model, based on a diagram output directly from
+SpineCreator. Populations for Str\_D1, Str\_D2, STN, SNr and GPe are
+shown within the `Basal Ganglia' box. Input comes into the model via
+the `World' population and the output population is SC\_deep. Compare
+this diagram with Figs.~\ref{ccg_model}(a) \&
+(b). Fig.~\ref{brain_model} expands the `SC', `BG' and `slow retinal'
+boxes from Fig.~\ref{ccg_model}(a).}
 
 % Now some FEF stuff taken from Alex's pre-pub
-\rvwt{Add description of FEF. (FIXME).}
-
-Fig.~\ref{brain_model} shows the layout of the populations in the
-brain model, as implemented in SpineCreator, and the interconnections
-between them. \rvwt{Describe this figure in more detail. (FIXME).}
-% and frontal eye field?
+\rvwt{The frontal eye fields (FEF) are a key cortical area for the
+generation of saccadic eye movements
+\citep{hikosaka_role_2000,tehovnik_eye_2000,robinson_eye_1969,bruce_primate_1985}.
+Saccadic targets are mapped retinotopically over its
+surface \citep{robinson_eye_1969,bruce_primate_1985,sabes_parietal_2002},
+and increased neural activity at a location in the map precedes a
+saccade to that location. Importantly, the FEF is also associated with
+visual decision making
+\citep{thompson_visual_2005,schall_saccade_1995,monosov_measurements_2008,cohen_neural_2009}.
+Thus, in a saccade choice, increased FEF activity is predictive of the
+eye movement whether correct or
+incorrect \citep{thompson_frontal_2005}, rather than of the correct
+response.}
+
+\rvwt{FEF neurons can be divided in to three functional groups,
+related to whether their activity corresponds with visual stimuli,
+motor action, or both \citep{segraves_functional_1987}. The \ccg~model
+simplifies this categorisation using a single layer of 50 by 50 units
+representing the mean of all three groups. This layer therefore
+responds to both visual stimuli and the buildup of activity associated
+with motor (saccadic) action. The retina provides a persistent
+luminance signal into the FEF through the dorsal visual
+pathway \citep{ungerleider_two_1982} which is abbreviated in this
+model to a direct connection with delay.}
+
+\rvwt{The FEF provides input into the
+BG \citep{saint-cyr_organization_1990} (to Str\_D1, Str\_D2 and STN)
+which, in turn, projects back to thalamus in a retinotopically
+organised way \citep{middleton_basal_2000,lynch_input_1994}. In
+addition, the thalamic targets of this path are regions with strong
+reciprocal connections to the FEF \citep{mcfarland_thalamic_2002}. In
+this way, the FEF forms channel-based loops through basal ganglia of
+the kind described above. Such circuits formed the basis of the model
+of \cite{humphries_role_2002}.
+%In that model, the
+%thalamic component included the thalamic reticular nucleus which
+%implemented an additional selection mechanism (via a feed-forward
+%competitive network within the cortico-thalamic loop). However, in the
+%interests of model simplicity, this was not implemented in the \ccg
+%oculomotor architecture.
+The thalamo-cortical loop may be thought of as an integrator of
+information, whose gain is modulated by inhibition from basal
+ganglia \citep{chambers_mechanisms_2012,cope_biologically_2011}.}
+
+\rvwt{The superior colliculus (SC) is a sub-cortical nucleus which
+also plays a critical r\^ole in the generation of
+saccades \citep{hikosaka_visual_1983}. Both FEF and SC have direct
+connections to the saccadic burst generator (SBG, see
+Sect.~\ref{sec:methods:brainstem}). If either is lesioned, the other
+can direct gaze, following a period of
+adjustement \citep{latto_effects_1977}, albeit with some persistent
+deficits. The SC is also a direct target of output from the
+SNr \citep{jayaraman_nigrotectal_1977,jiang_opposing_2003} and can be
+influenced by the action selection mechanisms of the BG. In
+particular, it forms a loop with BG, but unlike its cortical
+counterpart in FEF, the input to basal ganglia comes via the thalamus
+[Fig~\ref{fig:ccg_model}(a), blue arrows].}
+
+\rvwt{While the SC has seven alternating cell-~and fibre-rich
+layers \citep{wurtz_visual-motor_1980}, in most cases these are
+divided into the `superficial' and `deep' layers, which have
+significantly different response properties. Cells in the superficial
+layers, which receive input from the retina, are mainly visually
+responsive, with a preferred response to phasic events (luminance
+onsets and offsets) and movement on the visual
+field \citep{goldberg_activity_1972}. In contrast, cells in the deep
+layers receive multi-modal input, including inhibitory input from the
+output structures of the BG \citep{jayaraman_nigrotectal_1977}, and
+are directly involved in the generation of saccadic eye
+movements. Saccade related activity in the deep layers appears to
+generate saccades through `population coding', with a weighted sum of
+activity across the retinotopy of SC determining the saccade target
+\citep{lee_population_1988,van_opstal_role_1990,mays_dissociation_1980}.
+The deep layers of SC receive input from the FEF in a topographic
+manner \citep{stanton_frontal_1988,sommer_composition_2000}.}
+
+\rvwt{The SC in the \ccg~model is based on the the model described
+in \cite{arai_model_2005}, with the difference that the SNr input to
+the SC is generated by the BG model, rather than being
+hand-crafted. The SC model has a superficial and a deep layer, each of
+which is a 2-D array of 50 by 50 leaky integrator units arranged in
+the same retinotopic manner as the
+FEF \citep{wurtz_visual-motor_1980}.}
+
+% Foveal mask
+\rvwt{The \ccg~model incorporates a special connectivity pattern for
+visual input via cortical (FEF) and sub-cortical (thalamus)
+pathways. Due to the retinotopic mapping (Sect.~\ref{sec:mapping}),
+foveal luminances deliver a strong signal to the BG; roughly one third
+of the map is activated for the foveal targets used in this work
+(Fig.~\ref{mapping}, red cross). This makes it virtually impossible
+for a peripheral target (Fig.~\ref{mapping}, yellow cross) to win
+selection in the BG. Even if the peripheral target competed
+successfully to generate a saccade, this process would cause a
+significant delay, leading to latencies much larger than those
+observed experimentally. To overcome this problem, the \ccg~model
+incorporates a mechanism in which the synaptic strength of connections
+between FEF, thalamus and striatum are reduced close to the fovea
+according to a shifted hyperbolic tangent. This connection is named
+`DecayingAtFovea' in the SpineML implementation and follows a modified
+sigmoidal curve rather than tanh. In either case, the relation is
+`S-shaped' and normalised to the range [0 1]. Far from the fovea
+(where the S-shaped curve has the value $\approx$1), the connectivity
+pattern looks almost identical to a one-to-one connection.}
+
+% Retinal model
+\rvwt{Input to the \ccg~model is provided through a simple retina
+model which directly samples from a larger `world array' of pixel
+values. In the current model, the input for the retina is named
+`World' and is the retinotopic projection [Fig.~\ref{brain_model}(b)]
+of the eye's field of view of the world [Fig.~\ref{brain_model}(a)]
+and the luminant targets therein. The raw input in `World' is fed into
+a population which adds noise, and then via a delayed connection to
+FEF (the sustained retinal input path), to simulate processing through
+the dorsal visual stream. It is also fed, without substantial delay,
+into two leaky integrator layers (Retina\_1 and Retina\_2) with
+different time constants, with the more slowly reacting layer
+(Retina\_2) inhibiting its faster counterpart. The faster layer
+responds quickly to the appearance of a prolonged stimulus before it
+is inhibited by the slow layer, forming a phasic response to stimulus
+onset. The mechanism ensures that phasic rather than tonic responses
+arrive at the superficial SC from the retina.}
+
+% CCG model output
+\rvwt{The output of the \ccg~model is determined by the activity in the
+SC\_deep population. The activity in SC\_deep is first transformed
+from retinotopic co-ordinates into the Cartesian co-ordinates. The
+centroid of the activity is then computed. The position of this
+centroid in the Cartesian frame determines the saccadic end-point. The
+current model differs in that it does not compute a centroid, instead
+feeding the SC\_deep activity into the saccadic burst generator.}
+
+% Parameterisation here?
+\rvwt{The \ccg~model was parameterised by tuning the model to perform
+a prosaccade task in which a fixed luminance point is fixated by teh
+model. After a fixed duration, the fixation point was extinguished and
+a target point of fixed luminance was presented. The model was tuned
+so that the latency between the presentation of the target and the
+initiation of an eye movement matched experimental data, while also
+matching the electrophysiological evidence of activity in a variety of
+brain regions. The tuning of the BG model attempted to preserve as
+closely as possible the weights used in the original paper. Further
+details on the parameterisation of the \ccg~model are
+in \cite{cope_basal_2017}.}
+% Differences between ccg and existing brain model or can I do that
+% above? Better in the preceding text, I think and wherever it crops
+% up.
 
@@
 the \ccg~model, for which the cortico-striatal weights are multiplied
-by $(1+d)$ rather than $(0.2+d)$.
-
-The equations given above are applied to each element in a
-population. The value of the activation $A$ (and where relevant, the
-shunting input, $S$) is determined by summing the weighted inputs to
-the population:
+by $(1+d)$ rather than $(0.2+d)$. A value of $d=$0.7
+
+The equations given above are applied to each element in a population
+\rvwt{based on the D1MSN or D2MSN component}. The value of the activation
+$A$ (and where relevant, the shunting input, $S$) is determined by
+summing the weighted inputs to the population:
 \begin{equation}
@@
 $w_i^{act}$ and $w_i^{sh}$ are, respectively, the weights of the
-$i^{th}$ activation or shunting connection; $x_i^{act}$ and $x_i^{sh}$
-are the signals input to the activation and shunting connections.
+$i^{th}$ activation or shunting connections \rvwt{received by the component};
+$x_i^{act}$ and $x_i^{sh}$ are the signals input to the activation and
+shunting connections.
 
@@
 
+\rvwt{Thus, the information flow in the model is as follows:
+Luminances in the world have their locations computed in the eye's
+frame of reference, based on the rotational state of the eye. The
+locations of the luminances on the retina are transformed into a
+retinotopic co-ordinate system which determines the activity in the
+`World' population (named to mean the `world as the eye sees it',
+rather than the world frame of reference) which is the input for the
+brain model. The target luminance for a saccade is selected, as
+described earlier, via cortical and sub-cortical loops through the
+basal ganglia model and activity for the winning end-point builds up
+in the deep layer of superior colliculus. This activity excites
+activity in the correct proportions within the 6 channels of the
+saccadic burst generator whose output state, the motoneurons send a
+rate-code signal (normalised between 0 and 1) into the biomechanical
+eye model. The rotational state of the eye model is fed back to
+participate in the computation of the retinotopic luminance activity
+in `World', completing the loop.}
+
 % Brain to SBG, seeing as that's how I explained it above.
@@
 the fovea.
+% Try to make this clearer for Reviewer 2, Methods Comments, point 5.
 
@@
 ganglia to select sufficiently well so that the target can build up in
-the thalamo-cortical loop, in spite of the fixation overlap.
+the thalamo-cortical loop, in spite of the fixation
+overlap.
 
@@
 \begin{center}
-\includegraphics[width=0.8\textwidth]{./figures/ccg_model.png}
+\includegraphics[width=0.9\textwidth]{./figures/ccg_model.png}
 \end{center}

### 2017-11-20 papers/integration/omm_integ.tex
Adds eye screen figures

@@
 \rvwt{An illustration of the biomechanical eye model is given in
-Figure \ref{fig:eye_muscles}, while Figure \ref{fig:eye_head} depicts
+Figure \ref{fig:bioeye}, while Figure \ref{fig:bioeye} depicts
 the head model used in the proposed framework.}
-
-% To be moved in due course
-\begin{figure}[htb!]
-\begin{center}
-\includegraphics[width=0.5\textwidth]{./figures/bio_eye1.png}
-\end{center}
-\textbf{\refstepcounter{figure}\label{fig:eye_muscles} Figure \arabic{figure}.}
-{Example of the biomechanical eye model.}
-\end{figure}
-
-\begin{figure}[htb!]
-\begin{center}
-\includegraphics[width=0.5\textwidth]{./figures/bio_eye2.png}
-\end{center}
-\textbf{\refstepcounter{figure}\label{fig:eye_head} Figure \arabic{figure}.}
-{Example of the head model used.}
-\end{figure}
 
@@
 on the Kutta-Merson integration method.}
-
-% KM
-\rvwt{Figure \ref{fig:eye_sim0} illustrates an example of the experimental
-set-up of the proposed framework, while Figures \ref{fig:eye_sim1}
-and \ref{fig:eye_sim2} depict the developed eye oculomotor simulation
-system.}
-
-% Figures to merge together into a single panel or move.
-\begin{figure}[htb!]
-\begin{center}
-\includegraphics[width=0.5\textwidth]{./figures/Eye_sim0.png}
-\end{center}
-\textbf{\refstepcounter{figure}\label{fig:eye_sim0} Figure \arabic{figure}.}
-{Example of the experimental set-up.}
-\end{figure}
-
-\begin{figure}[htb!]
-\begin{center}
-\includegraphics[width=0.5\textwidth]{./figures/Eye_sim1.png}
-\end{center}
-\textbf{\refstepcounter{figure}\label{fig:eye_sim1} Figure \arabic{figure}.}
-{Example of the eye simulator system.}
-\end{figure}
-
-\begin{figure}[htb!]
-\begin{center}
-\includegraphics[width=0.5\textwidth]{./figures/Eye_sim2.png}
-\end{center}
-\textbf{\refstepcounter{figure}\label{fig:eye_sim2} Figure \arabic{figure}.}
-{Example of use of the eye simulator system.}
-\end{figure}
 
@@
 \begin{center}
+\includegraphics[width=0.5\textwidth]{./figures/eye_screen_plus.png}
+\end{center}
+\textbf{\refstepcounter{figure}\label{fig:bioeye} Figure \arabic{figure}.}
+{ The biomechanical eye. a) an OpenSim rendering of a pair of
+biomechanical eyes showing the positions of the extraocular
+muscles. b) OpenSim rendering of biomechanical eye within a head
+model c) Top-down schematic cross-sectional view of the biomechanical eye situated
+within a spherical screen, with a horizontal rotation towards a
+luminances at an angle of $-\theta_{y}$ about the $y$ axis, which
+points up out of the page.}
+\end{figure}
+
+\begin{figure}[htb!]
+\begin{center}
 \includegraphics[width=0.9\textwidth]{./figures/model_framework.png}

### 2017-11-21 papers/integration/omm_integ.tex
These changes add figures and text changes to (almost) complete the responses to the reviewers materials and results comments. Discussion re-write is still pending.

@@
 % Remove after review:
-Note: Changes based on Reviewer 1's comments \rvw{are in this colour}. For
+\bol{Note:} Changes based on Reviewer 1's comments \rvw{are in this colour}. For
 Reviewer 2 \rvwt{we use this colour}.
@@
 so that the latency between the presentation of the target and the
-initiation of an eye movement matched experimental data, while also
-matching the electrophysiological evidence of activity in a variety of
-brain regions. The tuning of the BG model attempted to preserve as
-closely as possible the weights used in the original paper. Further
-details on the parameterisation of the \ccg~model are
-in \cite{cope_basal_2017}.}
+initiation of an eye movement matched experimental
+data \citep{reulen_latency_1984}, while also matching the
+electrophysiological evidence of activity in a variety of brain
+regions. The tuning of the BG model attempted to preserve as closely
+as possible the weights used in the original paper. Further details on
+the parameterisation of the \ccg~model are in \cite{cope_basal_2017}.}
 % Differences between ccg and existing brain model or can I do that
@@
 2.5 \citep{cope_basal_2017,slotnick_electrophysiological_2001}.
+
+% Was looking for somewhere for this, possibly:
+%The precision of the model to distinguish between
+%targets, especially towards the periphery of the field of view was
+%limited by the 50$\times$50 size of the neural layers. In order to optimise
+%this precision, both the \ccg~model and our implementation of
+%it had their effective eccentricity range limited. Our implementation
+%was limited more than the Cope-Chambers model, because hills of
+%activity in SC_deep had to be kept fully within each layer. When a
+%hill `falls off the edge' of the layer, the amount of activation being
+%passed to the SBG is reduced and the saccades become inaccurate. I
+%didn't want to investigate effects at the edge of the SC, so I had an
+%effective limit of the model of about 22 degrees of eccentricity for a
+%saccade.
 
@@
 for two of the model's six channels is shown in
-Fig.~\ref{sbg}. \rvw{We use the word `channel' to mean a set of
-populations of neurons which are involved in actuating a single
-extraocular muscle. SBG channels are arranged in pairs, actuating
-opposing muscles. There is one pair of channels which actuates the
-superior and inferior rectus muscles, causing vertical rotations of
-the eye in a roughly parasaggital plane (the eye moves up or
-down). Another pair actuates the lateral and medial rectus muscles,
+Fig.~\ref{sbg}. \rvw{In the brainstem model, we use the word `channel'
+to mean a set of populations of neurons which are involved in
+actuating a single extraocular muscle. SBG channels are arranged in
+pairs, actuating opposing muscles. There is one pair of channels which
+actuates the superior and inferior rectus muscles, causing vertical
+rotations of the eye in a roughly parasaggital plane (the eye moves up
+or down). Another pair actuates the lateral and medial rectus muscles,
 causing horizontal rotations of the eye. The third pair actuates the
@@
 
-The output signals of the brainstem are used to drive the
-biomechanical model.  The latter is not only used to get tangible
-feedback on the simulated saccades including motion trajectories, but
-adds one more modelling dimension related to the inertial properties
-of the eye plant including muscle properties.
+The output signals of the brainstem's \rvwt{motoneuron (MN)
+populations} are used to drive the biomechanical model. \rvwt{The MN
+output signal in each brainstem channel is normalised in the range [0
+1] and represents the mean firing rate of the neurons that innervate
+the extraocular muscle for that channel.} The biomechanics are used
+not only to get tangible feedback on the simulated saccades including
+motion trajectories, but to add one more modelling dimension related
+to the inertial properties of the eye plant including muscle
+properties.
 
@@
 superior colliculus to discover the weight map under the assumption of
-2D Gaussian activation profiles~\citep{arai_two-dimensional_1994}.
+2D Gaussian activation
+profiles~\citep{arai_two-dimensional_1994}---\rvwt{that is, they
+assumed that the activity in superior colliculus for any saccade was a
+size-invariant 2D Gaussian hill of activity}.
 %
@@
 \cite{tabareau_geometry_2007} wrote down a theoretical form of the weight
-map, which follows from the mapping of \cite{ottes_visuomotor_1986}
-and the assumption of invariant 2D Gaussian activity profiles in
-SC. As they found it closely resembles the results
+map, \rvwt{obtained by inverting the mapping} of \cite{ottes_visuomotor_1986}
+and the assumption of invariant 2D Gaussian activity profiles in SC,
+\rvwt{which is equivalent to:}
+%
+\begin{equation} \label{eq:tabareau_eq3}
+w(r,\phi) = i\;e\,^{jr}\;\sin\left(l\phi + k\right)
+\end{equation}
+\rvwt{where $r$ and $\phi$ are co-ordinates on the collicular map and
+$i$, $j$, $k$ and $l$ are parameters of the
+function (compare with Eq.~3 of \cite{tabareau_geometry_2007}).}
+%
+As they found it closely resembles the results
 of \cite{arai_two-dimensional_1994}, and it is a simple formulation,
@@
 %
-One barrier to the use of the weight map
-in \cite{tabareau_geometry_2007} was the \ccg~model's violation of the
+One barrier to the use of this weight map was the \ccg~model's
+violation of the
 \e{invariant integral hypothesis}. This states that the number of spikes
@@
 \end{equation}
-which is invariant for all $\mathbf{z}$. However, the very mapping on
-which the \cite{tabareau_geometry_2007} result is based leads to a
-very \e{variant} activity profile in the \ccg~model. A luminance of a
-given size which excites activity near to the fovea causes activity in
-a large number of neurons, whereas activity far from the fovea excites
-a much smaller region. This effect is clearly demonstrated in
-Fig.~\ref{fig:mapping} for equal sized targets both on and distal from
-the fovea.
+which is invariant for all $\mathbf{z}$. \rvwt{This requirement is
+fulfilled by spatially invariant 2D Gaussian profiles, whose
+time-course (how quickly they grow and then diminish) is always the
+same.}
+
+However, the very mapping on which the \cite{tabareau_geometry_2007}
+result is based leads to a very \e{variant} activity profile \rvwt{in
+the SC\_deep layer} of the \ccg~model. A luminance of a given size
+which excites activity near to the fovea causes activity in a large
+number of neurons in each retinotopic layer, whereas activity far from
+the fovea excites a much smaller region. This effect is clearly
+demonstrated in Fig.~\ref{fig:mapping} for equal sized targets both on
+and distal from the fovea.
+
 % Try to make this clearer for Reviewer 2, Methods Comments, point 5.
-
-This led us to hypothesise that the retinotopic mapping be accompanied
-by an associated widening projection field such that the hill of
-activity in superior colliculus is invariant with position on the
-collicular surface. There are a number of locations in the system in
-which this widening projection field could exist. It could be
-implemented in the projections between the retinal populations and the
-superficial layer of SC along with the projection between the World
-and the FEF population. However, this would affect activity within the
-basal ganglia of the model, contradicting a result
+\rvwt{To understand the need for this invariance,
+consider the effect of a 2D Gaussian hill in SC\_deep which elicits a
+successful horizontal saccade of 10\dg. Activity from the 2D Gaussian,
+passing through the weight maps will excite the superior and inferior
+rectus channels by an equal, balanced amount, so these cancel out,
+allowing the eye movement to be horizontal. The amount of activation
+passed to the lateral rectus muscle results from a convolution of the
+Gaussian and the exponential component of the weight map relationship
+in Eq.~\ref{eq:tabareau_eq3}. If the Gaussian hill now appears further
+along the collicular surface, coding for a 20\dg~saccade, \e{and also
+becomes smaller}, we can still argue that the vertical component
+signals to superior/inferior rectus muscles will cancel out, and we
+could imagine that the exponential component of
+Eq.~\ref{eq:tabareau_eq3} is correctly parameterised to compensate for
+the smaller hill. However. Now consider a 2-D Gaussian hill which
+codes for a 10\dg saccade which is `up, and to the right' in equal
+proportions. That means that the hill will sit on the boundary between
+the weight maps for the `up', and the `right' muscles. Now, if the
+hill moves to the $r=$20\dg~location on the colliculus, \e{and also
+reduces in size}, it will excite only the periphery of the sine; the
+exponential increase of the map along $r$ is not guaranteed to
+compensate for the reduction in the convolution of the Gaussian hill
+and the sinusoidal component of the weight map.}
+% Add figure for this.
+
+This led us to hypothesise that the retinotopic mapping \rvwt{to the
+SBG be preceded} by an associated widening projection field such that
+the hill of activity in \rvwt{a `final' deep layer of superior
+colliculus is invariant with position on the map}. There are a number of
+locations in the system in which this widening projection field could
+exist. It could be implemented in the projections between the retinal
+populations and the superficial layer of SC along with the projection
+between the World and the FEF population. However, this would affect
+activity within the basal ganglia of the model, contradicting a result
 in \cite{cope_basal_2017} which explains the `hockey stick' profile
@@
 the SC in detail, we extended the model with a third functional layer
-named SC\_deep2, shown in Fig.~\ref{scdeep} (\ccg~has only the two
+named SC\_deep2, shown in Fig.~\ref{scdeep}(b) (\ccg~has only the two
 layers SC\_sup and SC\_deep). We introduced a widening projection
@@
 far from the fovea because the retinotopic mapping reduces the
-activity in the basal ganglia for more eccentric targets (this effect
-is described in detail in \cite{cope_basal_2017}). Closer to the
-fovea, the interaction between the foveal mask and the activity in FEF
-again leads to reduced input into into the basal ganglia and an
-increased time to achieve disinhibition in SNr.
+activity in the basal ganglia for more eccentric targets (see
+Fig.~\ref{mapping}). Closer to the fovea, the \rvwt{effect of} the
+foveal mask \rvwt{on} the activity in FEF again leads to reduced input
+into the basal ganglia and an increased time to achieve disinhibition
+in SNr.
 
@@
 8\dg~and our more distal luminance was at 12\dg~(both to the right of
-centre). We found that there was a critical time delay between the
+centre). \rvwt{The stimuli could not be presented at 15\dg and 30\dg
+to match the experiment, because 30\dg saccades were outside the range
+of the model.}
+
+We found that there was a critical time delay between the
 luminances of about 30~ms. If they were presented with a delay smaller
@@
 \begin{center}
-\includegraphics[width=0.9\textwidth]{./figures/ccg_model.png}
+\includegraphics[width=\textwidth]{./figures/ccg_model.png}
 \end{center}
@@
 `d' and the dotted lines. The SNr sends inhibitory output projections
-to its targets.}
+to its targets. \bol{c) 2D Gaussian weights.} The `GaussianKernel'
+connectivity pattern is based on the horizontal distance between the
+location of a neural element in one layer, and the location of a
+target neural element in the target layer for the connection. The
+potential weight of the connection is given by a 2D Gaussian function,
+which is maximum for the target neuron which exactly corresponds to
+the source neuron, and drops down for target neurons which are
+horizontally displaced from the source neuron. A threshold is applied
+to avoid a computationally expensive all-to-all connectivity (with
+most of these connections having negligible weight values).  If the
+weight is non-zero, then a connection is made from source to target,
+otherwise no connection is made. \bol{d) Gaussian connectivity.} This
+image shows connectivity (green rays) from two source neurons (in
+Str\_D2, brown spheres) to target neurons (in GPe, blue spheres). The
+circular connectivity pattern is seen. This does not show the weights,
+which reduce `towards the edge of the circle' and follow the
+relationship shown in (c).}
 \end{figure}
@@
 biomechanical eyes showing the positions of the extraocular
-muscles. b) OpenSim rendering of biomechanical eye within a head
-model c) Top-down schematic cross-sectional view of the biomechanical eye situated
-within a spherical screen, with a horizontal rotation towards a
-luminances at an angle of $-\theta_{y}$ about the $y$ axis, which
-points up out of the page.}
+muscles. Note that i) volume visualization of muscles should not be
+confused with FEM muscle models; it is provided for user feedback
+purposes, i.e. shape and color change depending on the muscle
+activation, ii) superior and inferior oblique are visualized up to
+their respective muscle pulleys. b) OpenSim rendering of biomechanical
+eye within a head model c) Top-down schematic cross-sectional view of
+the biomechanical eye situated within a spherical screen, with a
+horizontal rotation towards a luminances at an angle of $-\theta_{y}$
+about the $y$ axis. The $y$ axis points up, out of the page.}
 \end{figure}
@@
 \begin{center}
-\includegraphics[width=0.5\textwidth]{./figures/SC_to_brainstem.png}
+\includegraphics[width=0.9\textwidth]{./figures/scdeep_plus.png}
 \end{center}
 \textbf{\refstepcounter{figure}\label{scdeep} Figure \arabic{figure}.}
-{ Showing the additional deep layer of superior colliculus (SC\_deep2)
+{ a) \& b) Tabareau-style weight maps for `left' and `down' components
+of a saccade. c) The two weight maps in a) and b) shown on the same
+graph, viewed from above. Circles show the locations of potential
+hills of activity. Purple, dashed circles encode saccades down;
+red circles encode saccades with both a left and a down component. d)
+Showing the additional deep layer of superior colliculus (SC\_deep2)
 and the output layer (SC\_avg, named for the fact that in an earlier
@@
 vs. eccentricity for vertical targets. c) Latency vs. gap at three
-different luminance values. d) The effect of the dopamine parameter on
-saccade latencies in gap, step and overlap conditions, for two
-different target luminances.  e) Saccade vs. luminance showing gradual
-transition between reflexive and express behaviour.
+different luminance values. The data are shown alongside
+the \ccg~model results from Fig.~5 of \cite{cope_basal_2017} in blue,
+and the experimental results used in that model in red. The fixation
+luminance for the \ccg~curve was 0.5, the target lumianance 0.6 and
+the target eccentricity was 8\dg. The difference between
+the \ccg~model data and the data from the current model results from
+the different mechanism by which activity in SC\_deep causes a
+movement, the differing target angle and the reduced fixation
+luminance used here. d) The effect
+of the dopamine parameter on saccade latencies in gap, step and
+overlap conditions, for two different target luminances.  e) Saccade
+vs. luminance showing gradual transition between reflexive and express
+behaviour.
 %f) Saccade duration vs. saccade eccentricity for horizontal

### 2017-11-21 batch_scripts/foveal_mask/fovmask.m

@@ -1,0 +1,30 @@
+% The Foveal mask
+
+% The neural field size - never changes in this model, so this is
+% not a parameter.
+W_nfs = 50;
+
+% E2 participates in the magnification factor.
+E2 = 2.5
+
+r = [1:50]; % 1-50 range here.
+
+M_f = 4.87
+
+sh = 12 % shift
+
+E = E2 .* exp(r./(M_f.*E2)) - E2;
+
+res = 1./(1 + exp(2.*(sh-E)));
+
+res2 = 1./(1 + exp(2.*(sh-r)));
+
+figure(1)
+plot (r, E, 'r');
+title('E')
+
+figure(2)
+plot (r,res,'b');
+hold on;
+plot (r,res2,'k');
+title('res')

### 2017-11-21 batch_scripts/weight_theoretical/weight_maps_theory.m

@@ -1,0 +1,304 @@
+%
+% Build weight maps for paper illustration.
+%
+%
+
+% Modelling left map - double exponential. This is matched to
+% left(15,:) where left is loaded with load_sbgmaps.m.
+x=[1:50];
+
+yh=0.004*exp(0.11.*x);
+yv=0.004*exp(0.11.*x);
+
+figure(110); clf;
+plot (x,yh,'b');
+hold on;
+%plot (x,yhcmp,'b--');
+%plot (x,yhcmp2,'b..');
+plot (x,yv,'r');
+%plot (x,yvcmp,'r--');
+xlim([18 40]);
+%ylim([0 5]);
+legend('yh','yv')
+omsetgrid([1,0]);
+
+% A parameter for graphing
+zlim_max=1;
+
+% Do the sine part in higher precision first, to ensure symmetry
+% (rather than having circ commands of 12 and 13). Use 5000 pixels
+% rather than 50.
+%
+% Here's half a sine wave. Both at 1900 was my starting point.
+sine_width1 = 5000/2;
+sine_width2 = sine_width1;
+
+% Create Y from yh and yv.
+YH = repmat(yh,50,1);
+YV = repmat(yv,50,1);
+
+zer=zeros(1,5000);
+
+x2=[0:4999];
+z1 = sin(x2.*pi./sine_width1);
+z2 = sin(x2.*pi./sine_width2);
+
+mask1A = find(x2<sine_width1);
+mask1AL = find(x2<sine_width1/2);
+mask1AR = find(x2<sine_width1 & x2>=sine_width1/2);
+mask1B = find(x2>=sine_width1);
+
+mask2A = find(x2<sine_width2);
+mask2AL = find(x2<sine_width2/2);
+mask2AR = find(x2<sine_width2 & x2>=sine_width2/2);
+mask2B = find(x2>=sine_width2);
+
+maxpoint1 = sine_width1/2; % Peak of sine1
+crosspoint1L = maxpoint1 - 5000/8;
+crosspoint1R = maxpoint1 + 5000/8;
+maxpoint2 = sine_width1/2;
+crosspoint2L = maxpoint2- 5000/8;
+crosspoint2R = maxpoint2 + 5000/8;
+
+% Empirically determined suitable multiplier to give a -7,-7 saccade
[…]

### 2017-11-21 papers/integration/figures/gaussian_twod.m

@@ -1,0 +1,38 @@
+% Plot a 2d gaussian in 3d
+N = 2.0;
+x=linspace(-N, N, 50);
+y=x;
+[X,Y]=meshgrid(x,y);
+function offsetzlabel (h)
+    xpos = get(h, 'position');
+    xpos(1) = xpos(1)-0.2; % Out
+    halfwidth = 0.0; % up/down
+    xpos(3) = xpos(3)+halfwidth;
+    set(h, 'position', xpos);
+end
+
+figure(1)
+clf
+
+z=(2/sqrt(2*pi).*exp(-(X.^2/2)-(Y.^2/2)));
+z(z<=0.2) = 0;
+%size(zz);
+%size(zzz);
+colormap('autumn')
+surf(X,Y,z);
+%shading interp
+%axis tight
+
+ax=gca
+set(ax, 'fontsize', fs1)
+axpos=get(ax,'position');
+axpos=[axpos(1)+0.08,axpos(2)+0.05,axpos(3),axpos(4)];
+set(ax, 'position', axpos)
+
+fs1=32
+
+xlabel('d (x)', 'fontsize', fs1)
+ylabel('d (y)', 'fontsize', fs1)
+h = zlabel('weight', 'fontsize', fs1)
+
+offsetzlabel(h);

### 2017-12-04 papers/integration/omm_integ.tex
Adds work in progress on discussion

@@
 % on to Fig 3.
-\rvwt{The GPR model in Fig.~\ref{ccg_model}(b) has only three
+\rvwt{The GPR model in Fig.~\ref{fig:ccg_model}(b) has only three
 channels, with the focussed inhibition from striatum to SNr and GPe
@@
 the `World' population and the output population is SC\_deep. Compare
-this diagram with Figs.~\ref{ccg_model}(a) \&
+this diagram with Figs.~\ref{fig:ccg_model}(a) \&
 (b). Fig.~\ref{brain_model} expands the `SC', `BG' and `slow retinal'
-boxes from Fig.~\ref{ccg_model}(a).}
+boxes from Fig.~\ref{fig:ccg_model}(a).}
 
@@
 of the map is activated for the foveal targets used in this work
-(Fig.~\ref{mapping}, red cross). This makes it virtually impossible
-for a peripheral target (Fig.~\ref{mapping}, yellow cross) to win
+(Fig.~\ref{fig:mapping}, red cross). This makes it virtually impossible
+for a peripheral target (Fig.~\ref{fig:mapping}, yellow cross) to win
 selection in the BG. Even if the peripheral target competed
@@
 for two of the model's six channels is shown in
-Fig.~\ref{sbg}. \rvw{In the brainstem model, we use the word `channel'
+Fig.~\ref{fig:sbg}. \rvw{In the brainstem model, we use the word `channel'
 to mean a set of populations of neurons which are involved in
@@
 here). The simulation engine incorporating BRAHMS is called \stob~
-\citep{cope_spineml_2_brahms_2015-1}. \stob~is a collection of XSLT
+\citep{cope_spineml_2_brahms_2015}. \stob~is a collection of XSLT
 stylesheets which first generate and compile C++ BRAHMS components
@@
 necessary to hypothesise an inhibitory feedback mechanism from the SBG
-to the brain model.  This is shown in Fig.~\ref{sbg}, which indicates
+to the brain model.  This is shown in Fig.~\ref{fig:sbg}, which indicates
 how the output from the inhibitory burst neurons (IBN) of the SBG
@@
 neurological systems \e{in concert with} the biomechanical systems
-with which they have evolved in parallel. We hypothesised that by
+with which they have evolved. We hypothesised that by
 combining existing neurophysiological models with an accurate model of
@@
 brain model, shortcomings in the constituent models would be revealed,
-leading to new knowledge. To demonstrate the validity of this
-hypothesis, we built an integrated model and then identified the
+leading to new knowledge.
+%
+\rvw{We call this closed-loop approach \e{computational
+neurobehaviour}, meaning a complete, behaving model, with attention
+paid to the biological accuracy of each brain and biomechanical
+sub-system. There already exist many closed-loop \e{robotic} systems which
+receive sensory input from the world, process that input and generate
+behaviour by activating motor
+systems
+\citep{yu_development_2004,fend_artificial_2004,pearson_whiskerbot:_2007}. We
+now consider whether robotic systems which model biological
+components \e{in hardware} could fall within our new category.
+%
+Using a number of examples, we will attempt to illustrate what we mean
+by computational neurobehaviour. We'll consider which examples fall
+into the new category and which are covered by other fields of
+robotics or computational neuroscience. We will then attempt to
+provide a definition of computational neurobehaviour.}
+
+\rvw{\cite{pearson_whiskerbot:_2007} describes a wheeled robot which has a
+biomimetic whisker sensory system, along with a biomimetic neural
+system imitating the behaviour of the rat's sensory processing systems
+and controlling the movement of the robot. \cite{fend_artificial_2004}
+is a similar, wheeled, whiskered robot, with a repertoire of three
+behaviours organised in a subsumption architecture. In both robots,
+actions that are selected within the brain model drive a
+non-biologically accurate wheel motor control algorithm to achieve
+rotational and translational movements. Although both have
+sensory and processing systems which are guided by biology, the
+non-biological motor control stage prevents us from considering these
+as being studies of computational neurobehaviour.}
+%
+\rvw{\cite{yu_development_2004} report on a biomimetic fish robot,
+whose motor system closely resembles that of the real fish. The robot
+is able to operate in a closed-loop mode, where sensory input is
+provided to the non-biomimetic control algorithms from overhead
+cameras, but its control system is also able to operate in open-loop
+mode. Neither the control system, nor the sensory system are
+biophysically accurate and we would not describe this study as
+computational neurobehaviour. Nevertheless, the biophysically accurate
+motor system could certainly form part of a computational
+neurobehavioural study of swimming behaviour in the fish, if it were
+combined with suitable sensory input and sensory processing models.}
+%
+\rvw{\cite{knips_neural_2017} is a report of a reach-and-grasp robot
+arm controlled via a dynamic neural field brain model. The sensory
+input for this system---its `eyes'---is a Microsoft Kinect sensor; it
+also has somatosensory feedback from the fingers of the robot's
+hand. The neural field `brain' controls the seven degrees of freedom
+of the arm to carry out the reach-and-grasp action. While this robot
+has closed-loop control and is clearly inspired by biology, it remains
+a study of robotics and of the improvement of the control of the
+robot's reach-and-grasp function, rather than a study which aims to
+learn more about the biology of a primate arm. For this reason, we
+would describe the study of \cite{knips_neural_2017} as embodied
+robotics or neuro-robotics.}
+%
+\rvw{\cite{arena_motor-skill_2017} describes a
+robotic insect system based on the fly species \e{Drosophila
+Melanogaster}. It has biomimetic insect legs implemented in a virtual
+robot and a neuro-mimetic brain. Closing the loop is a visual sensory
+input system which is able to determine the distance between the robot
+and an obstacle and the obstacle's height. The visual system is not
+described in detail and may not be biologically modelled (much in the
+way that the visual processing stream is not modelled in detail in the
+present work). Nevertheless, this study may reasonably be described as
+compuational neurobehaviour; the authors demonstrate that the virtual
+robot is able to learn to climb obstacles in a realistic manner and
+suggest that the model may be compared with experimental data from
+future Drosophila experiments addressing obstacle climbing and
+learning.}
+
+\rvw{To summarise, we give a definition of computational
+neurobehaviour as \e{the study of biological sensory-motor system
+behaviour using biophysically accurate models of sensory input, brain
+and motor sub-systems operating in a closed-loop}. The sub-system
+models may be implemented in software or hardware, provided that they
+attempt to reproduce and explain features of the biological
+sub-system.}
+
+To demonstrate the validity of the computational neurobehaviour
+approach, we built an integrated model and then identified the
 modifications which were necessary to give it the ability to make
 accurate movements under one type of stimulus. We then examined its
-behaviour with other stimuli.
-
-We chose the oculomotor model as a basis for this study because it has
-only three degrees of freedom, making it one of the simplest
-musculo-skeletal systems. Furthermore, eye movements fall into several
-well-defined categories, each being controlled by separate brain
-circuits, we were therefore justified in modelling a system which
-produced only saccadic eye movements. Nevertheless, we are aware that
-we did not create a complete model of the system; no treatment of the
-cerebellum was attempted, justified because cerebellum appears to have
-only a minor effect on saccade accuracy \citep{dean_adaptive_2008},
-probably correcting for slow to medium timescale changes in the
-physical dynamics of the eyeball \citep{dean_learning_1994}.
+behaviour with other stimuli. We chose the oculomotor model as a basis
+for this study because it has only three degrees of freedom, making it
+one of the simplest musculo-skeletal systems. Furthermore, eye
+movements fall into several well-defined categories, each being
+controlled by separate brain circuits, we were therefore justified in
+modelling a system which produced only saccadic eye
+movements. Nevertheless, we are aware that we did not create a
+complete model of the system; no treatment of the cerebellum was
+attempted, justified because cerebellum appears to have only a minor
+effect on saccade accuracy \citep{dean_adaptive_2008}, probably
+correcting for slow to medium timescale changes in the physical
+dynamics of the eyeball \citep{dean_learning_1994}.
 
@@
 contains a mechanism to limit the timescale of a saccade (inhibitory
-feedback from EBN, via IBN to LLBN; see Fig.~\ref{sbg}). However, if
+feedback from EBN, via IBN to LLBN; see Fig.~\ref{fig:sbg}). However, if
 the activity in SC is not reset, then following the completion of the
@@
 connections to our model, such that the IBN populations in the SBG
-would inhibit activity in FEF, thalamus and SC\_deep (Fig.~\ref{sbg}),
+would inhibit activity in FEF, thalamus and SC\_deep (Fig.~\ref{fig:sbg}),
 preventing the occurrence of staircase saccades.
@@
 \subsection{Concluding remarks}
+
+% Reviewer 1's point 2.
+\rvw{Address reviewer's question of ``whether inaccuracies in the
+biomechanical model may introduce
+errors that propagate through the closed loop system and cannot be
+counteracted by the nervous system part of the simulation. How can you
+(or someone using this or related models) exclude introducing
+(biomechanical) properties that are not present in the biological
+system, or make sure to not miss critical biomechanical properties
+that might help remedy some of the shortcomings of the closed loop
+model?''.}
 
@@
 \begin{center}
-\includegraphics[width=0.5\textwidth]{./figures/Brain_Stem_1channel.png}
+\includegraphics[width=0.6\textwidth]{./figures/Brain_Stem_1channel.png}
 \end{center}
-\textbf{\refstepcounter{figure}\label{sbg} Figure \arabic{figure}.}
+\textbf{\refstepcounter{figure}\label{fig:sbg} Figure \arabic{figure}.}
 { One pair of channels of the saccadic burst generator (SBG) for left

### 2017-12-04 papers/integration/omm_integ.tex
More work in progress towards the post-review re-draft

@@
 into the new category and which are covered by other fields of
-robotics or computational neuroscience. We will then attempt to
-provide a definition of computational neurobehaviour.}
+robotics or computational neuroscience.}
 
@@
 robotics or neuro-robotics.}
-%
-\rvw{\cite{arena_motor-skill_2017} describes a
-robotic insect system based on the fly species \e{Drosophila
-Melanogaster}. It has biomimetic insect legs implemented in a virtual
-robot and a neuro-mimetic brain. Closing the loop is a visual sensory
-input system which is able to determine the distance between the robot
-and an obstacle and the obstacle's height. The visual system is not
-described in detail and may not be biologically modelled (much in the
-way that the visual processing stream is not modelled in detail in the
-present work). Nevertheless, this study may reasonably be described as
-compuational neurobehaviour; the authors demonstrate that the virtual
-robot is able to learn to climb obstacles in a realistic manner and
-suggest that the model may be compared with experimental data from
-future Drosophila experiments addressing obstacle climbing and
-learning.}
-
-\rvw{To summarise, we give a definition of computational
-neurobehaviour as \e{the study of biological sensory-motor system
+
+\rvw{Modern programming platforms, often originating from the world
+of computer gaming, make it relatively easy to model a virtual
+environment. Consequently, an increasing number of studies into
+robotic or neuro-mimetic control are carried out with virtual robots
+operating within a virtual environment. \cite{arena_motor-skill_2017}
+describes a robotic insect system based on the fly
+species \e{Drosophila Melanogaster}. It has biomimetic insect legs
+implemented in a virtual robot and a neuro-mimetic brain. Closing the
+loop is a visual sensory input system which is able to determine the
+distance between the robot and an obstacle and the obstacle's
+height. The visual system is not described in detail and may not be
+biologically modelled (much in the way that the visual processing
+stream is not modelled in detail in the present work). Nevertheless,
+this study may reasonably be described as compuational neurobehaviour;
+the authors demonstrate that the virtual robot is able to learn to
+climb obstacles in a realistic manner and suggest that the model may
+be compared with experimental data from future Drosophila experiments
+addressing obstacle climbing and learning.}
+%
+\rvw{\cite{nguyen_saccade_2014} and
+\cite{thurat_biomimetic_2015} are two studies of the oculomotor system
+which model sensory input, neural control and motor output. These
+studies fall outside the remit of computational neurobehaviour only
+because they omit to close the sensory
+loop. \cite{dewolf_spiking_2016} describes a reach model comprising a
+simplified virtual arm (with fewere degrees of freedom than a primate
+arm), and a biologically inspired brain model. This model also omits
+to close the sensory feedback loop and we consider it a traditional
+computational neuroscience study.}
+
+\rvw{We can now offer a definition of computational
+neurobehaviour as: \e{The study of biological sensory-motor system
 behaviour using biophysically accurate models of sensory input, brain
@@
 attempt to reproduce and explain features of the biological
-sub-system.}
+sub-system. We favour virtual biomechanics, for the ease with which
+the biomechanical model can be modified and the flexibility of
+computational modelling over hardware modelling.}
 
@@
 % Reviewer 1's point 2.
-\rvw{Address reviewer's question of ``whether inaccuracies in the
-biomechanical model may introduce
-errors that propagate through the closed loop system and cannot be
-counteracted by the nervous system part of the simulation. How can you
-(or someone using this or related models) exclude introducing
-(biomechanical) properties that are not present in the biological
-system, or make sure to not miss critical biomechanical properties
-that might help remedy some of the shortcomings of the closed loop
-model?''.}
+\rvw{\bol{FIXME}. We should consider whether inaccuracies within one sub-system,
+such as the musculo-skeletal model, may introduce errors that
+propagate through the closed loop system and cannot be counteracted by
+the nervous system part of the simulation.  My thoughts: You have to
+do this alongside other research so that sub-systems are informed by
+the best knowledge available.
+%
+How can you (or someone using this or related models)
+exclude introducing (biomechanical) properties that are not present in
+the biological system, or make sure to not miss critical biomechanical
+properties that might help remedy some of the shortcomings of the
+closed loop model?.}
+
+% Reviewer 1's point 4.
+\rvw{There are also experimental closed-loop approaches to
+understanding sensorimotor control. \cite{ejaz_closed-loop_2013}
+places a fly in a fixed position, and couples it with a free-to-move
+robot. The sensory input collected by the robot is projected onto the
+eyes of the fly, and activity from a selected neuron in the fly's
+brain is used to drive a control system for the robot's
+movements. This allows the experimenters to study the behaviour of the
+fly's brain operating in a closed-loop condition that is more natural
+than the open-loop condition that many other experimental techniques
+mandate. The results from closed-loop experiments will undoubtedly
+inform future neurobehavioural models.}
 
@@
 to its targets. \bol{c) 2D Gaussian weights.} The `GaussianKernel'
-connectivity pattern is based on the horizontal distance between the
-location of a neural element in one layer, and the location of a
+connectivity pattern is based on the `in-plane displacement' between
+the location of a neural element in one layer, and the location of a
 target neural element in the target layer for the connection. The
@@
 Str\_D2, brown spheres) to target neurons (in GPe, blue spheres). The
-circular connectivity pattern is seen. This does not show the weights,
-which reduce `towards the edge of the circle' and follow the
+circular connectivity pattern is seen. This does not show the weight
+\e{values}, which reduce `towards the edge of the circle' and follow the
 relationship shown in (c).}

### 2017-12-05 papers/integration/omm_integ.tex
Completes revision of discussion

@@
 
-\def\Address{\\
+\def\Address{
 $^{1}$Adaptive Behaviour Research Group, Department of Psychology,
@@
 $^{5}$Department of Electrical and Computer Engineering,
-  The University of Patras, Patras, Greece \\
+  The University of Patras, Patras, Greece
 }
@@
 and superior colliculus
-\citep{arai_two-dimensional_1994,moren_mechanism_2013,marino_spatial_2012}.
+\citep{massone_neural-network_1994,arai_two-dimensional_1994,moren_mechanism_2013,marino_spatial_2012}.
 More recently, combined models have also been developed incorporating
@@
 necessary to hypothesise an inhibitory feedback mechanism from the SBG
-to the brain model.  This is shown in Fig.~\ref{fig:sbg}, which indicates
-how the output from the inhibitory burst neurons (IBN) of the SBG
-model are used to feed back an inhibitory signal to the SC\_deep,
-thalamus and FEF populations in the brain model, resetting them ready
-for the next saccade.
-% Might have to justify the above a bit more.
+to the brain model.  This is shown in Fig.~\ref{fig:sbg}, which
+indicates how the output from the inhibitory burst neurons (IBN) of
+the SBG model are used to feed back an inhibitory signal to the
+SC\_deep, thalamus and FEF populations in the brain model, resetting
+them ready for the next saccade. \rvw{There is evidence for inhibitory
+projections to SC from the propositus
+hypoglossi nucleus \citep{corvisier_possible_1991}, which lies within the
+brainstem, upstream from motoneurons, and has been shown to encode eye
+velocity \citep{dale_nucleus_2013}.}
 
@@
 activity in the basal ganglia for more eccentric targets (see
-Fig.~\ref{mapping}). Closer to the fovea, the \rvwt{effect of} the
+Fig.~\ref{fig:mapping}). Closer to the fovea, the \rvwt{effect of} the
 foveal mask \rvwt{on} the activity in FEF again leads to reduced input
@@
 
-\rvw{Modern programming platforms, often originating from the world
-of computer gaming, make it relatively easy to model a virtual
+\rvw{Modern programming platforms, often originating from the
+computer game industry, make it relatively easy to model a virtual
 environment. Consequently, an increasing number of studies into
@@
 the closed-loop nature of the model makes it very natural to consider
-how the model will behave making saccades from arbitrary starting
+how the model will behave when making saccades from arbitrary starting
 positions, or how it would respond to a sequence of stimuli. This was
@@
 An examination of the behaviour of the model when presented with
-`double-step stimuli' reveals a problem with this scheme. We found
-that when double-step stimuli were presented (where an initial target
-at 8\dg~was replaced with a 12\dg~target after 30 or 40~ms) and a
-double saccade was made [Fig.~\ref{doublesteps}(a), black lines] the
-second saccade latency was \e{longer} even than the initial
+`double-step stimuli' reveals a problem with our inhibitory feedback
+connections. We found that when double-step stimuli were presented (where
+an initial target at 8\dg~was replaced with a 12\dg~target after 30 or
+40~ms) and a double saccade was made [Fig.~\ref{doublesteps}(a), black
+lines] the second saccade latency was \e{longer} even than the initial
 saccade. This contrasts with \cite{becker_analysis_1979} who find that
@@
 
+% Inhibition experimental evidence
+\rvw{There is some evidence for an inhibitory projection to SC from the
+brainstem. \cite{corvisier_possible_1991} offer evidence for a
+projection from the propositus hypoglossi nucleus. This lies upstream
+from motoneurons and (in primates) encodes eye
+velocity \citep{dale_nucleus_2013}, rather than head movement
+velocity. Although the propositus hypoglossi does not lie in exactly
+the same functional location as our IBN population (instead it sits
+between TN and MN), it offers a possible inhibitory feedback signal
+proportional to eye velocity and may help to reduce activity in SC
+post-saccade.}
+%
+\rvwt{Alternatively, it is possible that activity in
+FEF and thalamus are reset via a `timed signal'. Feasibly, after
+activity in FEF exceeds a threshold, an internal, inhibitory feedback
+signal could be activated. This inhibition should have a timescale of
+sufficient duration to reduce activity in FEF, thalamus and, via an
+increase in inhibitory output from SNr, also in SC. Indeed, the
+cortical microcircuit contains a variety of morphologically distinct
+gabaergic neurons \citep{douglas_neuronal_2004} which could fulfil
+this functionality. A similar mechanism would then be required in SC,
+to reset activity generated by direct excitation via the
+retinal-collicular pathway which generates express saccades. Again, SC
+is a multi-layered structure, containing gabaergic interneurons
+\citep{munoz_lateral_1998,meredith_intrinsic_1998,helms_organization_2004,sooksawate_organization_2011}
+and there is mounting evidence that saccade dynamics are generated
+within
+SC \citep{kaneda_regulation_2008,goossens_optimal_2012,bayguinov_hard-wired_2015}. Thus,
+a more complex treatment of the SC and FEF regions in the model may
+well obviate the need for inhibitory feedback from brainstem to SC,
+FEF and thalamus.}
+
+% Reviewer 1's point 2.
+\rvw{Considering whether a feedback connection, or internal,
+recurrent inhibition is responsible for activity-reset in the brain
+model raises a more general question about modelling the central
+nervous system. We should consider whether inaccuracies within one
+part of the model may propagate errors through the closed-loop system
+that cannot be counteracted by another part of the simulation. There
+is no way to know, from integrating sub-systems, which properties hold
+true, and which are false. However, by integrating models and
+examining the behaviour of the combined model, we are presented with
+the right questions to ask of the model and the experimental data. In
+the case of activity-reset, this is to re-assess whether there exists
+inhibitory feedback from brainstem to the SC and FEF regions, and to
+find out how an integrated model with self-regulatory mechanisms in SC
+and FEF may perform.}
+
+% In a model of SC, \cite{massone_neural-network_1994} suggests that
+% internal mechanisms, learned via a supervised method, are sufficient
+% to generate dynamics.
+
 \subsection{Concluding remarks}
-
-% Reviewer 1's point 2.
-\rvw{\bol{FIXME}. We should consider whether inaccuracies within one sub-system,
-such as the musculo-skeletal model, may introduce errors that
-propagate through the closed loop system and cannot be counteracted by
-the nervous system part of the simulation.  My thoughts: You have to
-do this alongside other research so that sub-systems are informed by
-the best knowledge available.
-%
-How can you (or someone using this or related models)
-exclude introducing (biomechanical) properties that are not present in
-the biological system, or make sure to not miss critical biomechanical
-properties that might help remedy some of the shortcomings of the
-closed loop model?.}
 
@@
 
-\begin{figure}[htb!]
+% Figure 1
+\begin{figure}[t]
 \begin{center}
@@
 
-\begin{figure}[htb!]
+% Figure 2
+\begin{figure}[t]
 \begin{center}
@@
 
-\begin{figure}[htb!]
+% Figure 3
+\begin{figure}[t]
 \begin{center}
@@
 
-\begin{figure}[htb!]
+% Figure 4
+\begin{figure}[t]
 \begin{center}
@@
 
-\begin{figure}[htb!]
+% Figure 5
+\begin{figure}[t]
 \begin{center}
@@
 
-\begin{figure}[htb!]
+\begin{figure}[t]
 \begin{center}

### 2017-12-05 papers/integration/bbl_utf8_to_latex.sh

@@ -23,20 +23,40 @@ if [ ${e} -ne "0" ]; then
     exit 1
 fi
 
+count=0
+
 # Search/replace u umlauts
-sed 's/\xc3\xbc/\\"u/g' < "$1" > /tmp/utf8tolatex/1.bbl
+sed 's/\xc3\xbc/\\"u/g' < "$1" > /tmp/utf8tolatex/$((count+1)).bbl
+count=$((count+1))
+
+# Search/replace U umlauts
+sed 's/\xc3\x9c/\\"U/g' < "$1" > /tmp/utf8tolatex/$((count+1)).bbl
+count=$((count+1))
+
+# o umlaut
+sed 's/\xc3\xb6/\\"o/g' < /tmp/utf8tolatex/${count}.bbl > /tmp/utf8tolatex/$((count+1)).bbl
+count=$((count+1))
+
+# O umlaut
+sed 's/\xc3\x96/\\"O/g' < /tmp/utf8tolatex/${count}.bbl > /tmp/utf8tolatex/$((count+1)).bbl
+count=$((count+1))
 
 # e acute (Moren)
-sed 's/\xc3\xa9/\\'\''e/g' < /tmp/utf8tolatex/1.bbl >  /tmp/utf8tolatex/2.bbl
+sed 's/\xc3\xa9/\\'\''e/g' < /tmp/utf8tolatex/${count}.bbl >  /tmp/utf8tolatex/$((count+1)).bbl
+count=$((count+1))
 
 # e grave (Lefevre)
-sed 's/\xc3\xa8/\\\`e/g' < /tmp/utf8tolatex/2.bbl >  /tmp/utf8tolatex/3.bbl
+sed 's/\xc3\xa8/\\\`e/g' < /tmp/utf8tolatex/${count}.bbl >  /tmp/utf8tolatex/$((count+1)).bbl
+count=$((count+1))
 
 # Reg
-sed 's/\xc2\xae/\\textsuperscript\{\\textregistered\}/g' < /tmp/utf8tolatex/3.bbl >  /tmp/utf8tolatex/4.bbl
+sed 's/\xc2\xae/\\textsuperscript\{\\textregistered\}/g' < /tmp/utf8tolatex/${count}.bbl >  /tmp/utf8tolatex/$((count+1)).bbl
+count=$((count+1))
 
 # TM
[…]

### 2017-12-05 papers/integration/omm_integ.tex
Figure label refactoring

@@
 % NB - having this Fig. ref here is important for figure ordering!
-Fig.~\ref{brain_model} shows a schematic of the SpineML implementation
+Fig.~\ref{fig:brainmodel} shows a schematic of the SpineML implementation
 of the model, based on a diagram output directly from
@@
 this diagram with Figs.~\ref{fig:ccg_model}(a) \&
-(b). Fig.~\ref{brain_model} expands the `SC', `BG' and `slow retinal'
+(b). Fig.~\ref{fig:brainmodel} expands the `SC', `BG' and `slow retinal'
 boxes from Fig.~\ref{fig:ccg_model}(a).}
@@
 values. In the current model, the input for the retina is named
-`World' and is the retinotopic projection [Fig.~\ref{brain_model}(b)]
-of the eye's field of view of the world [Fig.~\ref{brain_model}(a)]
+`World' and is the retinotopic projection [Fig.~\ref{fig:brainmodel}(b)]
+of the eye's field of view of the world [Fig.~\ref{fig:brainmodel}(a)]
 and the luminant targets therein. The raw input in `World' is fed into
@@
 Briefly, the model consists of input from the World population (see
-Fig.~\ref{brain_model}, green population box) producing activity in an
+Fig.~\ref{fig:brainmodel}, green population box) producing activity in an
 `express' pathway to superior colliculus (purple) and simultaneously
 in cortex, represented here by the FEF population (grey boxes in
-Fig.~\ref{brain_model}). The express pathway causes short latency
+Fig.~\ref{fig:brainmodel}). The express pathway causes short latency
 activity in the superficial superior colliculus, which directly
@@
 components into a SpineML model was a new \stob~feature motivated by
-the current work.  Fig.~\ref{model_framework} shows the workflow, in
+the current work.  Fig.~\ref{fig:modelframework} shows the workflow, in
 which the model specification files (blue box - a combination of
@@
 the SC in detail, we extended the model with a third functional layer
-named SC\_deep2, shown in Fig.~\ref{scdeep}(b) (\ccg~has only the two
+named SC\_deep2, shown in Fig.~\ref{fig:scdeep}(b) (\ccg~has only the two
 layers SC\_sup and SC\_deep). We introduced a widening projection
@@
 target was close to the ideal straight line---see
-Fig.~\ref{sacc_vs_targ}(a) \& \rvw{(b)}. We applied the same parameters to
+Fig.~\ref{fig:saccvstarg}(a) \& \rvw{(b)}. We applied the same parameters to
 both directions of each channel; $i_{up} = i_{down} = 0.00195$,
@@
 1/10$^{\mathrm{th}}$ of the vertical maps, as described earlier) are
-shown in Fig.~\ref{weightmaps}.
+shown in Fig.~\ref{fig:weightmaps}.
 %
@@
 direction of the saccade, as described in Sect.~\ref{sec:mapping} and
-Fig.~\ref{fig:mapping}. Fig.~\ref{weightmaps}(a) shows the weight map
+Fig.~\ref{fig:mapping}. Fig.~\ref{fig:weightmaps}(a) shows the weight map
 for the muscle which rotates the eye to the left. As we modelled a
@@
 corresponds to any movement with a rightward component, the `left'
-weight map is 0. Fig.~\ref{weightmaps}(d) shows the weight map for
+weight map is 0. Fig.~\ref{fig:weightmaps}(d) shows the weight map for
 rightward movements, actuating the medial rectus muscle of the
 eye. The line of maximum connection strength is along $\phi=$13.5. The
-map is a mirror of Fig.~\ref{weightmaps}(a), reflected about the line
+map is a mirror of Fig.~\ref{fig:weightmaps}(a), reflected about the line
 $\phi$=26. The `left' and `right' weight maps are orthogonal; the
 non-zero region of the `left' map is zero in the `right' map and vice
-versa. Fig~\ref{weightmaps}(b) \& (d) show the weight maps for
+versa. Fig~\ref{fig:weightmaps}(b) \& (d) show the weight maps for
 downward and upward eye movements; the `down' map activates the SBG
@@
 
-In Fig.~\ref{sacc_vs_targ}, we showed the result of running the model
+In Fig.~\ref{fig:saccvstarg}, we showed the result of running the model
 to targets located on the principle axes, on which the model was
@@
 target, $\mathbf{\theta}^t = (\theta_{x}^t, \theta_{y}^t, 0)$ to
-obtain mean saccade end-points.  Fig.~\ref{errorsurfaceTM3} shows
+obtain mean saccade end-points.  Fig.~\ref{fig:errorsurfaceTM3} shows
 saccade accuracy results for an entire hemifield in the na\"ive model
@@
 shown for the full, three dimensional error vector in
-Fig.~\ref{errorsurfaceTM3}(a) and for the $x$, $y$ and $z$ components
-in Figs.~\ref{errorsurfaceTM3}(b)--(c).  Inspection of
-Fig.~\ref{errorsurfaceTM3}(a) shows that the end-point error is
+Fig.~\ref{fig:errorsurfaceTM3}(a) and for the $x$, $y$ and $z$ components
+in Figs.~\ref{fig:errorsurfaceTM3}(b)--(c).  Inspection of
+Fig.~\ref{fig:errorsurfaceTM3}(a) shows that the end-point error is
 minimal along the principle axes ($\theta_{x}^t=\;$0 or
@@
 saccade magnitude.  The $x$ component error map in
-Fig.~\ref{errorsurfaceTM3}(b) shows the same trend, mirrored about the
+Fig.~\ref{fig:errorsurfaceTM3}(b) shows the same trend, mirrored about the
 `Target X' axis, whereas the $y$ and $z$ component errors are,
@@
 vertical error was similar---so that its equivalent of
-Fig.~\ref{sacc_vs_targ} showed a similar sum of squares error.
-
-Figs.~\ref{errorsurface}(a)--(d) show the \rvw{percentage errors for
+Fig.~\ref{fig:saccvstarg} showed a similar sum of squares error.
+
+Figs.~\ref{fig:errorsurface}(a)--(d) show the \rvw{percentage errors for
 TModel4}.  First of
@@
 proceeded to exercise the model (TModel4), starting with saccades to a
-single target; prosaccades. Fig.~\ref{outmany}(a) shows 9
+single target; prosaccades. Fig.~\ref{fig:outmany}(a) shows 9
 representative saccades to a single target luminance. Initially, the
@@
 at one of the 9 different locations, marked by crosses in
-Fig.~\ref{outmany}(a).  The resulting trajectories are plotted, with
+Fig.~\ref{fig:outmany}(a).  The resulting trajectories are plotted, with
 colour indicating the relationship between trajectories and target
@@
 0.8~s and not the velocity-based end-point described
-above. Figs.~\ref{outmany}(b) and (c) show the rotational components
-of the blue and red trajectories in Fig.~\ref{outmany}(a) along with
+above. Figs.~\ref{fig:outmany}(b) and (c) show the rotational components
+of the blue and red trajectories in Fig.~\ref{fig:outmany}(a) along with
 the target and fixation luminance values. Rotations are the eye's
@@
 stick' shape shown in Fig. 7 of \cite{cope_basal_2017} for horizontal
-[Fig.~\ref{lat_vs_all}(a)], vertical [Fig.~\ref{lat_vs_all}(b)] and
+[Fig.~\ref{fig:latvsall}(a)], vertical [Fig.~\ref{fig:latvsall}(b)] and
 oblique saccades (not shown). The latency increases with eccentricity
@@
 
-Fig.~\ref{lat_vs_all}(c) shows latencies achieved when varying the
+Fig.~\ref{fig:latvsall}(c) shows latencies achieved when varying the
 time between fixation offset and target onset. This is termed
@@
 to build up quickly in FEF, thalamus and through the basal ganglia's
-striatum and SNr. The shape of the curves in Fig.~\ref{lat_vs_all}(c)
+striatum and SNr. The shape of the curves in Fig.~\ref{fig:latvsall}(c)
 matches the results in \cite{cope_basal_2017} for target luminances of
@@
 
-Fig.~\ref{lat_vs_all}(d) shows the effect of the dopamine parameter on
+Fig.~\ref{fig:latvsall}(d) shows the effect of the dopamine parameter on
 saccade latencies in gap, step and overlap conditions. In general, the
@@
 The relationship between latency and the target luminance is given in
-Fig.~\ref{lat_vs_all}(e). This shows latency for a 100~ms gap, step
+Fig.~\ref{fig:latvsall}(e). This shows latency for a 100~ms gap, step
 and 100~ms overlap conditions for a given fixation luminance of 0.2,
@@
 
-Fig.~\ref{outrtn} shows the outward and return trajectories produced
+Fig.~\ref{fig:outrtn} shows the outward and return trajectories produced
 by the experiment with the TN reset mechanism. Panel (a) shows the $x$
 and $y$ rotation trajectory; panel (b) shows individual rotational
-components of the eye. Fig.~\ref{outrtn}(c) shows out and return
+components of the eye. Fig.~\ref{fig:outrtn}(c) shows out and return
 trajectories for three other saccade targets; horizontal, vertical and
@@
 some stochastic variation caused by the noise in the model [see dashed
-trajectories in Fig.~\ref{outrtn}(a)].
+trajectories in Fig.~\ref{fig:outrtn}(a)].
 
@@
 We carried out a `staircase' presentation, shown in
-Fig.~\ref{doublesteps}, where our small eccentricity luminance was at
+Fig.~\ref{fig:doublesteps}, where our small eccentricity luminance was at
 8\dg~and our more distal luminance was at 12\dg~(both to the right of
@@
 normal), and a second saccade being made to a location hypometric of
-12\dg~after a pause of about 240~ms.  Fig.~\ref{doublesteps}(a) shows
+12\dg~after a pause of about 240~ms.  Fig.~\ref{fig:doublesteps}(a) shows
 the mean trajectories from 5 simulations of the staircase doublestep
@@
 the mean. The corresponding trajectories are shown in
-Fig.~\ref{doublesteps}(b).
+Fig.~\ref{fig:doublesteps}(b).
 
@@
 along the principle rotational axes
-(Fig.~\ref{errorsurfaceTM3}). Thus, \e{the integration of the models}
+(Fig.~\ref{fig:errorsurfaceTM3}). Thus, \e{the integration of the models}
 suggested that an additional layer was required to achieve accurate
@@
 this mechanism, and hypothesised that a widening projection field
-would be a candidate mechanism. The results of Fig.~\ref{errorsurface}
+would be a candidate mechanism. The results of Fig.~\ref{fig:errorsurface}
 indicate that a substantial improvement in accuracy is indeed achieved
@@
 positions, or how it would respond to a sequence of stimuli. This was
-the motivation for the out-and-return experiment (Fig.~\ref{outrtn})
-as well as for the double step experiment (Fig.~\ref{doublesteps}).
+the motivation for the out-and-return experiment (Fig.~\ref{fig:outrtn})
+as well as for the double step experiment (Fig.~\ref{fig:doublesteps}).
 We found that return saccades were substantially affected by the
@@
 an initial target at 8\dg~was replaced with a 12\dg~target after 30 or
-40~ms) and a double saccade was made [Fig.~\ref{doublesteps}(a), black
+40~ms) and a double saccade was made [Fig.~\ref{fig:doublesteps}(a), black
 lines] the second saccade latency was \e{longer} even than the initial
@@
 \end{center}
-\textbf{\refstepcounter{figure}\label{brain_model} Figure \arabic{figure}.}
+\textbf{\refstepcounter{figure}\label{fig:brainmodel} Figure \arabic{figure}.}
 { The brain model. This is the SpineCreator `network layer' view of
@@
 \end{center}
-\textbf{\refstepcounter{figure}\label{model_framework} Figure \arabic{figure}.}
+\textbf{\refstepcounter{figure}\label{fig:modelframework} Figure \arabic{figure}.}
 { The model framework. The model is specified using a combination of
@@
 \end{center}
-\textbf{\refstepcounter{figure}\label{scdeep} Figure \arabic{figure}.}
+\textbf{\refstepcounter{figure}\label{fig:scdeep} Figure \arabic{figure}.}
 { a) \& b) Tabareau-style weight maps for `left' and `down' components
@@
 \end{center}
-\textbf{\refstepcounter{figure}\label{sacc_vs_targ} Figure \arabic{figure}.}
+\textbf{\refstepcounter{figure}\label{fig:saccvstarg} Figure \arabic{figure}.}
 { Accuracy at different target eccentricities for fixation luminance
@@
 \end{center}
-\textbf{\refstepcounter{figure}\label{weightmaps} Figure \arabic{figure}.}
+\textbf{\refstepcounter{figure}\label{fig:weightmaps} Figure \arabic{figure}.}
 { Weight maps for the connections between the output layer of superior
@@
 \end{center}
-\textbf{\refstepcounter{figure}\label{errorsurfaceTM3} Figure \arabic{figure}.}
+\textbf{\refstepcounter{figure}\label{fig:errorsurfaceTM3} Figure \arabic{figure}.}
 { The end-point error surface for the original, na\"ive model
@@
 \end{center}
-\textbf{\refstepcounter{figure}\label{errorsurface} Figure \arabic{figure}.}
+\textbf{\refstepcounter{figure}\label{fig:errorsurface} Figure \arabic{figure}.}
 { The end-point error surface for the model in which a widening
@@
 Note that the range of the colour scale is 0 to 20\%, a much smaller
-range than the range in Fig~\ref{errorsurfaceTM3}.}
+range than the range in Fig~\ref{fig:errorsurfaceTM3}.}
 \end{figure}
@@
 \end{center}
-\textbf{\refstepcounter{figure}\label{outmany} Figure \arabic{figure}.}
+\textbf{\refstepcounter{figure}\label{fig:outmany} Figure \arabic{figure}.}
 { Representative single saccades. a) Trajectories from 9 saccades to a
@@
 \end{center}
-\textbf{\refstepcounter{figure}\label{lat_vs_all} Figure \arabic{figure}.}
+\textbf{\refstepcounter{figure}\label{fig:latvsall} Figure \arabic{figure}.}
 { Exploring saccade latencies. a) Latency to first movement as a
@@
 \end{center}
-\textbf{\refstepcounter{figure}\label{outrtn} Figure \arabic{figure}.}
+\textbf{\refstepcounter{figure}\label{fig:outrtn} Figure \arabic{figure}.}
 { There and back - a saccade to a target, followed by return to the
@@
 \end{center}
-\textbf{\refstepcounter{figure}\label{doublesteps} Figure \arabic{figure}.}
+\textbf{\refstepcounter{figure}\label{fig:doublesteps} Figure \arabic{figure}.}
 { Double steps. The effect of illuminating a first target at 8\dg~or

### 2017-12-05 papers/integration/omm_integ.tex
Change to use of caption in captions, as per most recent Frontiers sample file

@@
 % Figure 1
-\begin{figure}[t]
+\begin{figure}[h!]
 \begin{center}
@@
 \end{center}
-\textbf{\refstepcounter{figure}\label{fig:ccg_model} Figure \arabic{figure}.}
-{ \bol{a) The macroscopic architecture of the \ccg~model.} The main
+\caption{ \bol{a) The macroscopic architecture of the \ccg~model.} The main
 nuclei modelled as brain systems are: basal ganglia (BG), frontal eye
@@
 relationship shown in (c).}
+\label{fig:ccg_model}
 \end{figure}
@@
 % Figure 2
-\begin{figure}[t]
+\begin{figure}[h!]
 \begin{center}
@@
 \end{center}
-\textbf{\refstepcounter{figure}\label{fig:brainmodel} Figure \arabic{figure}.}
-{ The brain model. This is the SpineCreator `network layer' view of
+\caption{ The brain model. This is the SpineCreator `network layer' view of
 the model. Each box represents a neural population with 2500 elements,
@@
 parameter in the Str\_D1 and Str\_D2 populations}
+\label{fig:brainmodel}
 \end{figure}
@@
 % Figure 3
-\begin{figure}[t]
+\begin{figure}[h!]
 \begin{center}
@@
 \end{center}
-\textbf{\refstepcounter{figure}\label{fig:mapping} Figure \arabic{figure}.}
-{ Representative mapping from eye's frame of reference in Cartesian
+\caption{ Representative mapping from eye's frame of reference in Cartesian
 co-ordinates to retinotopic co-ordinates. (a) The mapping of
@@
 ganglia and one input to superior colliculus.}
+\label{fig:mapping}
 \end{figure}
@@
 % Figure 4
-\begin{figure}[t]
+\begin{figure}[h!]
 \begin{center}
@@
 \end{center}
-\textbf{\refstepcounter{figure}\label{fig:sbg} Figure \arabic{figure}.}
-{ One pair of channels of the saccadic burst generator (SBG) for left
+\caption{ One pair of channels of the saccadic burst generator (SBG) for left
 (cyan) or right (green) movements. Collicular activity in SC\_avg
@@
 Excitatory burst neurons; TN: Tonic neurons; MN: Motoneurons.}
+\label{fig:sbg}
 \end{figure}
@@
 % Figure 5
-\begin{figure}[t]
+\begin{figure}[h!]
 \begin{center}
@@
 \end{center}
-\textbf{\refstepcounter{figure}\label{fig:bioeye} Figure \arabic{figure}.}
-{ The biomechanical eye. a) an OpenSim rendering of a pair of
+\caption{ The biomechanical eye. a) an OpenSim rendering of a pair of
 biomechanical eyes showing the positions of the extraocular
@@
 about the $y$ axis. The $y$ axis points up, out of the page.}
+\label{fig:bioeye}
 \end{figure}
 
-\begin{figure}[t]
+\begin{figure}[h!]
 \begin{center}
@@
 \end{center}
-\textbf{\refstepcounter{figure}\label{fig:modelframework} Figure \arabic{figure}.}
-{ The model framework. The model is specified using a combination of
+\caption{ The model framework. The model is specified using a combination of
 declarative XML files and hand-coded C++. These original model
@@
 executable. In practice, this call is made by \stob.}
+\label{fig:modelframework}
 \end{figure}
 
-\begin{figure}[t]
+\begin{figure}[h!]
 \begin{center}
@@
 \end{center}
-\textbf{\refstepcounter{figure}\label{fig:scdeep} Figure \arabic{figure}.}
-{ a) \& b) Tabareau-style weight maps for `left' and `down' components
+\caption{ a) \& b) Tabareau-style weight maps for `left' and `down' components
 of a saccade. c) The two weight maps in a) and b) shown on the same
@@
 between SC\_deep and SC\_deep2.}
+\label{fig:scdeep}
 \end{figure}
 
-\begin{figure}[t]
+\begin{figure}[h!]
 \begin{center}
@@
 \end{center}
-\textbf{\refstepcounter{figure}\label{fig:saccvstarg} Figure \arabic{figure}.}
-{ Accuracy at different target eccentricities for fixation luminance
+\caption{ Accuracy at different target eccentricities for fixation luminance
 0.2 and target luminance 0.3.}
+\label{fig:saccvstarg}
 \end{figure}
 
-\begin{figure}[t]
+\begin{figure}[h!]
 \begin{center}
@@
 \end{center}
-\textbf{\refstepcounter{figure}\label{fig:weightmaps} Figure \arabic{figure}.}
-{ Weight maps for the connections between the output layer of superior
+\caption{ Weight maps for the connections between the output layer of superior
 colliculus and the six long lead burst neurons of the saccadic burst
@@
 multiplied by cosine($\phi$) about its `active' axis.}
+\label{fig:weightmaps}
 \end{figure}
 
-\begin{figure}[t]
+\begin{figure}[h!]
 \begin{center}
@@
 \end{center}
-\textbf{\refstepcounter{figure}\label{fig:errorsurfaceTM3} Figure \arabic{figure}.}
-{ The end-point error surface for the original, na\"ive model
+\caption{ The end-point error surface for the original, na\"ive model
 (TModel3). a) The ratio of the magnitudes of the total error vector
@@
 $\theta_{y}^t$ are denoted `Target X' and `Target Y' in the figure.}
+\label{fig:errorsurfaceTM3}
 \end{figure}
 
-\begin{figure}[t]
+\begin{figure}[h!]
 \begin{center}
@@
 \end{center}
-\textbf{\refstepcounter{figure}\label{fig:errorsurface} Figure \arabic{figure}.}
-{ The end-point error surface for the model in which a widening
+\caption{ The end-point error surface for the model in which a widening
 projection field was added to the model of the superior colliculus. a)
@@
 range than the range in Fig~\ref{fig:errorsurfaceTM3}.}
+\label{fig:errorsurface}
 \end{figure}
 
-\begin{figure}[t]
+\begin{figure}[h!]
 \begin{center}
@@
 \end{center}
-\textbf{\refstepcounter{figure}\label{fig:outmany} Figure \arabic{figure}.}
-{ Representative single saccades. a) Trajectories from 9 saccades to a
+\caption{ Representative single saccades. a) Trajectories from 9 saccades to a
 single target at 9 different locations. In each case, a fixation cross
@@
 (0,-10).}
+\label{fig:outmany}
 \end{figure}
 
-\begin{figure}[t]
+\begin{figure}[h!]
 \begin{center}
@@
 \end{center}
-\textbf{\refstepcounter{figure}\label{fig:latvsall} Figure \arabic{figure}.}
-{ Exploring saccade latencies. a) Latency to first movement as a
+\caption{ Exploring saccade latencies. a) Latency to first movement as a
 function of target eccentricity for horizontal targets. b) Latency
@@
 }
+\label{fig:latvsall}
 \end{figure}
 
-\begin{figure}[t]
+\begin{figure}[h!]
 \begin{center}
@@
 \end{center}
-\textbf{\refstepcounter{figure}\label{fig:outrtn} Figure \arabic{figure}.}
-{ There and back - a saccade to a target, followed by return to the
+\caption{ There and back - a saccade to a target, followed by return to the
 original fixation. a) Out and return saccade to a target at (0,-10\dg)
@@
 three other targets.}
+\label{fig:outrtn}
 \end{figure}
 
-\begin{figure}[t]
+\begin{figure}[h!]
 \begin{center}
@@
 \end{center}
-\textbf{\refstepcounter{figure}\label{fig:doublesteps} Figure \arabic{figure}.}
-{ Double steps. The effect of illuminating a first target at 8\dg~or
+\caption{ Double steps. The effect of illuminating a first target at 8\dg~or
 12\dg, followed by a second target at 12\dg~or 8\dg. a) Horizontal
@@
 the data presented in (a).}
+\label{fig:doublesteps}
 \end{figure}

### 2017-12-07 papers/integration/omm_integ.tex
Couple of minor tweaks.

@@
 neural element represents an activation; the activation is governed by
-a first order differential equation specified in the SpineML
-component. In the brain model, there are six different components in
-use: LINlinear; LINret; LINexp; D1MSN and D2MSN.
-
-The LINlinear component governs the activation $a$ with a first order
+a first order differential equation specified in a \e{SpineML
+component}. SpineML, which will be outlined in
+Sect.~\ref{sec:methods:framework}, provides a means to mathematically
+define the five distinct components in use in the brain model.
+
+The \e{LINlinear} component governs the activation $a$ with a first order
 leaky integrator differential equation:
@@
 activation exceeds $c$, simulating neurons which only fire when driven
-by excitatory input.} At this point, the naming scheme for the
-component becomes apparent; this is a Leaky Integrator with a
-piecewise-linear transfer function.
-
-The LINret component used for the retinal populations is similar to
+by excitatory input.}
+
+The \e{LINret} component used for the retinal populations is similar to
 the LINlinear component, but with no intrinsic noise and no shunting
@@
 \end{equation}
-The LINexp component is a leaky integrator with an exponential
+The \e{LINexp} component is a leaky integrator with an exponential
 transfer function. It shares the same differential equation with
@@
 
-The D1MSN and D2MSN components are both leaky integrators, similar to
+The \e{D1MSN} and \e{D2MSN} components are both leaky integrators, similar to
 LINlinear. They differ in that they have no shunting inhibition. They
@@
 
+% FIXME: Add reference to weight maps neuroscience if possible.
 We found the best parameters for the exponential in
@@
 combining existing neurophysiological models with an accurate model of
-a musculo-skeletal system, and then `closing the loop' by allowing the
+a musculo-skeletal system, and then \rvw{closing the
+`agent-environment-agent' loop} by allowing the
 movements of the virtual muscles to modulate sensory feedback to the
@@
 biomimetic whisker sensory system, along with a biomimetic neural
-system imitating the behaviour of the rat's sensory processing systems
+system imitating the operation of the rat's sensory processing
 and controlling the movement of the robot. \cite{fend_artificial_2004}

### 2017-12-07 papers/integration/omm_integ.tex
Changes to discussion  additions after talking to Kevin, results of lit search for variable weights in STT

@@
 spatial aspect of the transform is thought to be implemented by a
-weight-mapping \citep{tabareau_geometry_2007,arai_two-dimensional_1994}
-and we follow this idea.
+weight-mapping \citep{tabareau_geometry_2007,arai_two-dimensional_1994}.
+\rvwt{Although there is no definitive experimental proof for such a mapping,
+there exists evidence for spatially variable synapse
+density \citep{moschovakis_anatomical_1998,herrero_influence_1998} and
+connection density \citep{grantyn_density_2002} and we therefore adopt
+the idea.}
 %
@@
 % possibly descibe this training process in supplemental data
-which depended on a centroid computation in SC\_deep. For the four
-rectus muscles, the resulting weight maps resembled those found by
+which depended on a centroid computation in SC\_deep and was designed
+to maintain a null torsional eye rotation for all saccade
+end-points. For the four rectus muscles, the resulting weight map
+solutions resembled those found by
 \cite{arai_two-dimensional_1994}. The trained
@@
 with saccade end-point location.
+% Could elaborate here on Listings Law, and why I didn't train to
+% Listings Law. Do this in the chapter, rather than here in the paper.
 
@@
 
-% FIXME: Add reference to weight maps neuroscience if possible.
 We found the best parameters for the exponential in
@@
 direction of the saccade, as described in Sect.~\ref{sec:mapping} and
-Fig.~\ref{fig:mapping}. Fig.~\ref{fig:weightmaps}(a) shows the weight map
-for the muscle which rotates the eye to the left. As we modelled a
+Fig.~\ref{fig:mapping}. Fig.~\ref{fig:weightmaps}(a) shows the weight
+map for the muscle which rotates the eye to the left. As we modelled a
 left eye, this actuates the lateral rectus muscle. The exponential
-rise of Eq.~\ref{eq:weightmaps} is seen in the $r$ direction; as $r$
-increases, so the connection strength to the SBG channel rises
-exponentially. The connection strength is greatest along the centre
-line, for a value of $\phi$ which corresponds to a purely leftward
-movement. Note that $\phi$ is presented in neural coordinates, and not
-in degrees or radians; 1$\leq\phi\leq$50 corresponds to a range of
-0\dg~to 360\dg; $\phi=$38.5 corresponds to movements left. The
-connections strength drops away sinusoidally as $\phi$ moves away from
-the centre line at $\phi=$38.5. In regions of the map for which there
-is no leftward movement, that is, in the half of the map which
-corresponds to any movement with a rightward component, the `left'
-weight map is 0. Fig.~\ref{fig:weightmaps}(d) shows the weight map for
-rightward movements, actuating the medial rectus muscle of the
-eye. The line of maximum connection strength is along $\phi=$13.5. The
-map is a mirror of Fig.~\ref{fig:weightmaps}(a), reflected about the line
-$\phi$=26. The `left' and `right' weight maps are orthogonal; the
-non-zero region of the `left' map is zero in the `right' map and vice
+rise of Eq.~\ref{eq:weightmaps} [for experimental evidence,
+see Figs.~7 \& 8 of \cite{herrero_influence_1998}] is seen in the
+$r$ direction; as $r$ increases, so the connection strength to the SBG
+channel rises exponentially. The connection strength is greatest along
+the centre line, for a value of $\phi$ which corresponds to a purely
+leftward movement. Note that $\phi$ is presented in neural
+coordinates, and not in degrees or radians; 1$\leq\phi\leq$50
+corresponds to a range of 0\dg~to 360\dg; $\phi=$38.5 corresponds to
+movements left. The connections strength drops away sinusoidally as
+$\phi$ moves away from the centre line at $\phi=$38.5. In regions of
+the map for which there is no leftward movement, that is, in the half
+of the map which corresponds to any movement with a rightward
+component, the `left' weight map is 0. Fig.~\ref{fig:weightmaps}(d)
+shows the weight map for rightward movements, actuating the medial
+rectus muscle of the eye. The line of maximum connection strength is
+along $\phi=$13.5. The map is a mirror of
+Fig.~\ref{fig:weightmaps}(a), reflected about the line $\phi$=26. The
+`left' and `right' weight maps are orthogonal; the non-zero region of
+the `left' map is zero in the `right' map and vice
 versa. Fig~\ref{fig:weightmaps}(b) \& (d) show the weight maps for
@@
 target on-time. We showed that the full model reproduces the `hockey
-stick' shape shown in Fig. 7 of \cite{cope_basal_2017} for horizontal
+stick' shape shown in Fig. 7 of \cite{cope_basal_2017} and discovered in
+experimental data \citep{reulen_latency_1984} for horizontal
 [Fig.~\ref{fig:latvsall}(a)], vertical [Fig.~\ref{fig:latvsall}(b)] and
@@
 leading to new knowledge.
-%
-\rvw{We call this closed-loop approach \e{computational
-neurobehaviour}, meaning a complete, behaving model, with attention
-paid to the biological accuracy of each brain and biomechanical
-sub-system. There already exist many closed-loop \e{robotic} systems which
-receive sensory input from the world, process that input and generate
-behaviour by activating motor
-systems
-\citep{yu_development_2004,fend_artificial_2004,pearson_whiskerbot:_2007}. We
-now consider whether robotic systems which model biological
-components \e{in hardware} could fall within our new category.
-%
-Using a number of examples, we will attempt to illustrate what we mean
-by computational neurobehaviour. We'll consider which examples fall
-into the new category and which are covered by other fields of
-robotics or computational neuroscience.}
-
-\rvw{\cite{pearson_whiskerbot:_2007} describes a wheeled robot which has a
-biomimetic whisker sensory system, along with a biomimetic neural
-system imitating the operation of the rat's sensory processing
-and controlling the movement of the robot. \cite{fend_artificial_2004}
-is a similar, wheeled, whiskered robot, with a repertoire of three
-behaviours organised in a subsumption architecture. In both robots,
-actions that are selected within the brain model drive a
-non-biologically accurate wheel motor control algorithm to achieve
-rotational and translational movements. Although both have
-sensory and processing systems which are guided by biology, the
-non-biological motor control stage prevents us from considering these
-as being studies of computational neurobehaviour.}
-%
-\rvw{\cite{yu_development_2004} report on a biomimetic fish robot,
-whose motor system closely resembles that of the real fish. The robot
-is able to operate in a closed-loop mode, where sensory input is
-provided to the non-biomimetic control algorithms from overhead
-cameras, but its control system is also able to operate in open-loop
-mode. Neither the control system, nor the sensory system are
-biophysically accurate and we would not describe this study as
-computational neurobehaviour. Nevertheless, the biophysically accurate
-motor system could certainly form part of a computational
-neurobehavioural study of swimming behaviour in the fish, if it were
-combined with suitable sensory input and sensory processing models.}
-%
-\rvw{\cite{knips_neural_2017} is a report of a reach-and-grasp robot
-arm controlled via a dynamic neural field brain model. The sensory
-input for this system---its `eyes'---is a Microsoft Kinect sensor; it
-also has somatosensory feedback from the fingers of the robot's
-hand. The neural field `brain' controls the seven degrees of freedom
-of the arm to carry out the reach-and-grasp action. While this robot
-has closed-loop control and is clearly inspired by biology, it remains
-a study of robotics and of the improvement of the control of the
-robot's reach-and-grasp function, rather than a study which aims to
-learn more about the biology of a primate arm. For this reason, we
-would describe the study of \cite{knips_neural_2017} as embodied
-robotics or neuro-robotics.}
-
-\rvw{Modern programming platforms, often originating from the
-computer game industry, make it relatively easy to model a virtual
-environment. Consequently, an increasing number of studies into
-robotic or neuro-mimetic control are carried out with virtual robots
-operating within a virtual environment. \cite{arena_motor-skill_2017}
-describes a robotic insect system based on the fly
-species \e{Drosophila Melanogaster}. It has biomimetic insect legs
-implemented in a virtual robot and a neuro-mimetic brain. Closing the
-loop is a visual sensory input system which is able to determine the
-distance between the robot and an obstacle and the obstacle's
-height. The visual system is not described in detail and may not be
-biologically modelled (much in the way that the visual processing
-stream is not modelled in detail in the present work). Nevertheless,
-this study may reasonably be described as compuational neurobehaviour;
-the authors demonstrate that the virtual robot is able to learn to
-climb obstacles in a realistic manner and suggest that the model may
-be compared with experimental data from future Drosophila experiments
-addressing obstacle climbing and learning.}
-%
-\rvw{\cite{nguyen_saccade_2014} and
-\cite{thurat_biomimetic_2015} are two studies of the oculomotor system
-which model sensory input, neural control and motor output. These
-studies fall outside the remit of computational neurobehaviour only
-because they omit to close the sensory
-loop. \cite{dewolf_spiking_2016} describes a reach model comprising a
-simplified virtual arm (with fewere degrees of freedom than a primate
-arm), and a biologically inspired brain model. This model also omits
-to close the sensory feedback loop and we consider it a traditional
-computational neuroscience study.}
-
-\rvw{We can now offer a definition of computational
-neurobehaviour as: \e{The study of biological sensory-motor system
-behaviour using biophysically accurate models of sensory input, brain
-and motor sub-systems operating in a closed-loop}. The sub-system
-models may be implemented in software or hardware, provided that they
-attempt to reproduce and explain features of the biological
-sub-system. We favour virtual biomechanics, for the ease with which
-the biomechanical model can be modified and the flexibility of
-computational modelling over hardware modelling.}
-
-To demonstrate the validity of the computational neurobehaviour
+
+To demonstrate the validity of this closed-loop
 approach, we built an integrated model and then identified the
@@
 section, along with the model code itself, will help others to carry
-out similar studies. However, we wish to devote the majority of this
-discussion to what can be learned from an integrated model of a
-combined brain and biomechanical system, using our oculomotor system
-as an example.
+out similar studies. We will discuss what can be learned from an
+integrated model of a combined brain and biomechanical system, using
+our oculomotor system as an example and then consider how this study
+compares with other modelling and robotic studies of closed-loop
+systems.
 
@@
 
+%
+% A couple of last points to round up the discussion of THIS model
+%
+
 % Reviewer 1's point 2.
@@
 % to generate dynamics.
-
-\subsection{Concluding remarks}
-
-% Reviewer 1's point 4.
-\rvw{There are also experimental closed-loop approaches to
-understanding sensorimotor control. \cite{ejaz_closed-loop_2013}
-places a fly in a fixed position, and couples it with a free-to-move
-robot. The sensory input collected by the robot is projected onto the
-eyes of the fly, and activity from a selected neuron in the fly's
-brain is used to drive a control system for the robot's
-movements. This allows the experimenters to study the behaviour of the
-fly's brain operating in a closed-loop condition that is more natural
-than the open-loop condition that many other experimental techniques
-mandate. The results from closed-loop experiments will undoubtedly
-inform future neurobehavioural models.}
 
@@
 
+\subsection{Comparison with other studies}
+
+\rvw{We have called this closed-loop, biomimetic modelling approach \e{computational
+neurobehaviour}, in which a complete, behaving model is constructed,
+with attention paid to the biological accuracy of each brain and
+biomechanical sub-system. There already exist many
+closed-loop \e{robotic} systems which receive sensory input from the
+world, process that input and generate behaviour by activating motor
+systems
+\citep{yu_development_2004,fend_artificial_2004,pearson_whiskerbot:_2007}. We
+now consider whether robotic systems which model biological
+components \e{in hardware} could fall within our new category.
+%
+Using a number of examples, we will attempt to illustrate what we mean
+by computational neurobehaviour. We'll consider which examples fall
+into the new category and which are covered by other fields of
+robotics or computational neuroscience.}
+
+\rvw{\cite{pearson_whiskerbot:_2007} describes a wheeled robot which has a
+biomimetic whisker sensory system, along with a biomimetic neural
+system imitating the operation of the rat's sensory processing and
+controlling the movement of the robot. \cite{fend_artificial_2004} is
+a similar, wheeled, whiskered robot, with a repertoire of three
+behaviours organised in a subsumption architecture. In both robots,
+actions that are selected within the brain model drive a
+non-biologically accurate wheel motor control algorithm to achieve
+rotational and translational movements. Although both have sensory and
+processing systems which are guided by biology, the non-biological
+motor control stage prevents us from considering these as being
+studies of computational neurobehaviour. Instead, we would refer to
+these as \e{embodied models}, as described
+in \cite{bolado-gomez_biologically_2013}, a study in which the
+learning behaviour of a biomimetic `core' model is embedded within an
+engineered `architecture' (a wheeled robot) which closes the
+agent-environment loop.}
+%
+\rvw{\cite{yu_development_2004} report on a biomimetic fish robot,
+whose motor system closely resembles that of the real fish. The robot
+is able to operate in a closed-loop mode, where sensory input is
+provided to the non-biomimetic control algorithms from overhead
+cameras, but its control system is also able to operate in open-loop
+mode. Neither the control system, nor the sensory system are
+biophysically accurate and we would not describe this study as
+computational neurobehaviour. Nevertheless, the biophysically accurate
+motor system they describe has the potential to form part of a
+computational neurobehavioural study of swimming behaviour in the
+fish, if it were combined in a loop with suitable sensory input and
+sensory processing models.}
+%
+\rvw{\cite{knips_neural_2017} is a report of a reach-and-grasp robot
+arm controlled via a dynamic neural field brain model. The sensory
+input for this system---its `eyes'---is a Microsoft Kinect sensor; it
+also has somatosensory feedback from the fingers of the robot's
+hand. The neural field `brain' controls the seven degrees of freedom
+of the arm to carry out the reach-and-grasp action. While this robot
+has closed-loop control and is clearly inspired by biology, it remains
+a study of robotics and of the improvement of the control of the
+robot's reach-and-grasp function, rather than a study which aims to
+learn more about the biology of a primate arm. For this reason, we
+would describe the study of \cite{knips_neural_2017} as an embodied
+model.}
+
+\rvw{To summarise, in most closed-loop robotic studies which
+incorporate neuro-mimetic models, the hardware forms an `engineered
+surround architecture', allowing for the examination of the behaviour
+of the embodied model. However, suitably \e{biomimetic} hardware such as
+the fish in \cite{yu_development_2004} would not be excluded from
+computational neurobehavioural studies.}
+
+\rvw{Modern programming platforms, often originating from the
+computer game industry, make it relatively easy to model a virtual
+environment. Consequently, an increasing number of studies into
+robotic or neuro-mimetic control are carried out with virtual robots
+operating within a virtual environment.}
+%
+\rvw{\cite{nguyen_saccade_2014} and
+\cite{thurat_biomimetic_2015} are two studies of the oculomotor system
+which model sensory input, neural control \e{and} motor output in
+software. These studies fall outside the remit of computational
+neurobehaviour only because they omit to close the sensory
+loop. \cite{dewolf_spiking_2016} describes a reach model comprising a
+simplified virtual arm (with fewer degrees of freedom than a primate
+arm), and a biologically inspired brain model. This model also omits
+to close the sensory feedback loop and we consider it a computational
+neuroscience study of a (virtually) embodied model.}
+%
+
+% Reviewer 1's point 4.
+\rvw{There are also experimental closed-loop approaches to
+understanding sensorimotor control. \cite{ejaz_closed-loop_2013}
+places a fly in a fixed position, and couples it with a free-to-move
+robot. The sensory input collected by the robot is projected onto the
+eyes of the fly, and activity from a selected neuron in the fly's
+brain is used to drive a control system for the robot's
+movements. This allows the experimenters to study the behaviour of the
+fly's brain operating in a closed-loop condition that is more natural
+than the open-loop condition that many other experimental techniques
+mandate. The results from closed-loop experiments will undoubtedly
+inform future neurobehavioural models.}
+
+%
+% Now the closing section of the discussion.
+%
+
+\rvw{Thus, while there are many models that close the
+agent-environment loop and display partial biological plausibility,
+the biomimetic features are usually confined to a sub-system of the
+entire model. This leads us to formalise a definition of computational
+neurobehaviour as: \e{The study of biological sensory-motor system
+behaviour using biologically accurate models of sensory input, brain
+and motor sub-systems operating in a closed-loop}.}
+%
+% Another computational neurobehavioural study?
+\rvw{We believe our oculomotor model is one of the first such models
+using this approach and shares many features with that
+of \cite{arena_motor-skill_2017} which describes a robotic insect
+system based on the fly species \e{Drosophila Melanogaster}. It has
+biomimetic insect legs implemented in a virtual robot and a
+neuro-mimetic brain. Closing the loop is a visual sensory input system
+which is able to determine the distance between the robot and an
+obstacle and the obstacle's height. The authors demonstrate that the
+virtual robot is able to learn to climb obstacles in a realistic
+manner and suggest that the model may be compared with experimental
+data from future Drosophila experiments addressing obstacle climbing
+and learning. The visual system is not described in detail, but if it
+is modelled in a biologically plausible manner, then this work may
+reasonably be described as a computational neurobehaviour study,
+contemporaneous with our own.}
+
 % Significance of this work.
-This work represents a step forward in the modelling of neuromuscular
-systems, not because it significantly advances any of the constituent
-models, but because it \e{integrates} the models into a
-complete, \e{behaving} system.  This is not the first integrated brain
-model composed of separately developed components. The works
-of \cite{nguyen_saccade_2014} and
-\cite{thurat_biomimetic_2015} are both based
-on an example of a brain model which drives a simple, second order
-model of the eye. \cite{dewolf_spiking_2016} describes a reach model
-which integrates models of cortex and cerebellum to drive a two
-degree-of-freedom arm model. Both of these example systems
-nevertheless operate using `curated' inputs supplied by the modeller.
-
-In contrast, the current work allows the state of the system to
-determine the input delivered to the model. The modeller only curates
-the state of the world at each time point, but the actual input to the
-model depends on the eye's rotational state.  This is, to our
-knowledge, the first model which integrates the brain with an accurate
-biophysical system and closes the loop in this way, enabling the
-system to reproduce behaviour.  As such, it offers a platform for
-testing more complex saccadic behaviour such as antisaccades or
-saccades in the presence of distractor stimuli. We believe that by
-building closed loop systems which express behaviour, we, and others
-will develop a new field of \e{computational neurobehaviour}, which
-will share themes from neuroscience, artificial intelligence, decision
-science and embodied robotics.
+%% This work represents a step forward in the modelling of neuromuscular
+%% systems, not because it significantly advances any of the constituent
+%% models, but because it \e{integrates} the models into a
+%% complete, \e{behaving} system.  This is not the first integrated brain
+%% model composed of separately developed components. The works
+%% of \cite{nguyen_saccade_2014} and
+%% \cite{thurat_biomimetic_2015} are both based
+%% on an example of a brain model which drives a simple, second order
+%% model of the eye. \cite{dewolf_spiking_2016} describes a reach model
+%% which integrates models of cortex and cerebellum to drive a two
+%% degree-of-freedom arm model. Both of these example systems
+%% nevertheless operate using `curated' inputs supplied by the modeller.
+
+%% In contrast, the current work allows the state of the system to
+%% determine the input delivered to the model. The modeller only curates
+%% the state of the world at each time point, but the actual input to the
+%% model depends on the eye's rotational state.  This is, to our
+%% knowledge, the first model which integrates the brain with an accurate
+%% biophysical system and closes the loop in this way, enabling the
+%% system to reproduce behaviour.  As such, it offers a platform for
+%% testing more complex saccadic behaviour such as antisaccades or
+%% saccades in the presence of distractor stimuli. We believe that by
+%% building closed loop systems which express behaviour, we, and others
+%% will develop a new field of \e{computational neurobehaviour}, which
+%% will share themes from neuroscience, artificial intelligence, decision
+%% science and embodied robotics.
 

### 2017-12-08 papers/integration/omm_integ.tex
Minor fixes, following proof-read of manuscript

@@
 Furthermore, in the context of building \e{behaving} systems, a
-necessary part of any model for which the behaviour requires visual
-attention and decision making is a realistic mechanism for gathering
-visual information.  This is obvious from extrinsic considerations---a
-subject must look at a scene to make decisions or navigate within
-it. It also follows for \e{intrinsic} reasons. For
+realistic mechanism for gathering visual information is a necessary
+part of any model for which the behaviour requires visual attention
+and decision making.  This is obvious from extrinsic
+considerations---a subject must look at a scene to make decisions or
+navigate within it. It also follows for \e{intrinsic} reasons. For
 example, \cite{howard_hand_1997} showed that visual cues affect reach
@@
 Activity within the superior colliculus then excites neurons in the
-pons, medulla and rostral mid-brain \citep{sparks_brainstem_2002}.
-and \rvw{finally the motor neurons} which innervate the extraocular muscles
+pons, medulla and rostral mid-brain \citep{sparks_brainstem_2002}
+and \rvw{finally the motor neurons}, which innervate the extraocular
+muscles
 \citep{fuchs_firing_1970,sparks_brainstem_2002}. This direct pathway
@@
 development of the model in \cite{cope_basal_2017}, referred to here
-as the \ccg~model. This was a rate-coded neural network model
+as the \e{\ccg~model}. This was a rate-coded neural network model
 incorporating retinal populations, frontal eye fields (FEF), the basal
@@
 as \e{input} the positions of luminances \rvwt{(of fixed shape and
-intensity)} on a topographic map. \rvwt{Whilst certain assumptions
+intensity)} on a topographic map. \rvwt{While certain assumptions
 were made about the input---that a luminant input excites activity on
@@
 the \ccg~model}, but first we will give a description of the
-co-ordinate systems.
+co-ordinate systems that were used.
 
@@
 The brain model, excluding the brainstem, is a re-implementation of
-the \ccg~model, \rvwt{of reflexive saccadic behaviour \citep{cope_basal_2017}}.
+the \ccg~model \rvwt{of reflexive saccadic behaviour \citep{cope_basal_2017}}.
 \rvwt{Reflexive saccades are fast eye movements elicited by abrupt
@@
 of populations as a sub-system), the thalamus and the superior
-colliculus. Excitatory connections are indicated with arrow heads;
-inhibitory connections with circles in place of the arrow heads. The
+colliculus. Excitatory connections are indicated with arrowheads;
+inhibitory connections with circles in place of the arrowheads. The
 blue and green connection lines indicate two thalamo-basal ganglia
@@
 the \ccg~model. The BG model is based on previous
-work \citep{gurney_computational_2001,gurney_computational_2001-1} and is referred to as the GPR
-model. The GPR model incorporates the following main components of the
-primate BG \citep{mink_basal_1996,wickens_basal_1997}: (i) The
-striatum (the main input station to the BG) which is divided into two
-iterdigitated populations of projection neurons expressing primarily D1
-or D2-type dopaminergic receptors (named Str\_D1 and Str\_D2); (ii)
-The subthalamic nucleus (STN); (iii) the external segment of the
-globus pallidus (GPe); (iv) the output nucleus relevant for saccadic
+work \citep{gurney_computational_2001,gurney_computational_2001-1} and
+is referred to as the GPR model. The GPR model incorporates the
+following main components of the primate
+BG \citep{mink_basal_1996,wickens_basal_1997}: (i) The striatum (the
+main input station to the BG) which is divided into two iterdigitated
+populations of projection neurons expressing primarily D1 or D2-type
+dopaminergic receptors (named Str\_D1 and Str\_D2); (ii) The
+subthalamic nucleus (STN); (iii) the external segment of the globus
+pallidus (GPe); (iv) the output nucleus relevant for saccadic
 control---the substantia nigra pars reticulata
@@
 input for all channels is relatively high, then the diffuse projection
-from STN, which effectively supplies a sum of \e{all} of the STN inputs to each
-channel in SNr, will provide so much excitation that Str\_D1 may
-become unable to inhibit one of the channels in SNr and selection may
-become
+from STN, which effectively supplies a sum of \e{all} of the STN
+inputs to each channel in SNr, will provide so much excitation that
+Str\_D1 may become unable to inhibit one of the channels in SNr and
+selection may become
 impossible. \cite{gurney_computational_2001,gurney_computational_2001-1}
@@
 \rvwt{At the neuronal level, the STN, GPe and SNr have tonic output
-levels \citep{chevalier_disinhibition_1990,delong_primate_1985,kita_intracellular_1991}. This
+activity \citep{chevalier_disinhibition_1990,delong_primate_1985,kita_intracellular_1991}. This
 is modelled using piecewise linear output functions with zero offsets,
@@
 using a dopamine parameter, $d$, which modulates the input activations
-$a_{in}^D1$ and $a_{in}^D1$ as:
+$a_{in}^{D1}$ and $a_{in}^{D2}$ as:
 \begin{equation}
@@
 subtle, with only a small change in the amount of inhibition fed from
-GPe into STN (via a focussed, one to one connection) being affected by
+GPe into STN (via a focussed, one-to-one connection) being affected by
 the change, along with a small change in the inhibition fed into SNr
-from GPe (also via a one to one connection). It is not possible to
-clearly describe the dynamic effect of the dopamine parameter as being
-due to any single population, because the activity is recurrently
+from GPe (also via a one-to-one connection). It is not possible to
+ascribe the dynamic effect of the dopamine parameter to any single
+population, because the activity is recurrently
 connected through multiple loops. Thus, a line of reasoning such as
@@
 by projective fields with many weighted connections. Specifically,
-each unit in Str\_D1 projected to a counterpart SNr$_j$ in SNr with
-some weight $w_{max}$, but also connected to neighbouring nodes in SNr
+each unit in Str\_D1 projects to a counterpart SNr$_j$ in SNr with
+some weight $w_{max}$, but also connects to neighbouring nodes in SNr
 with a weight given by $w_{max}.G(d)$, where $G(d)$ is a circularly
 symmetric, 2D-Gaussian which is a function of distance $d$ from
-SNr$_j$ [Fig.~\ref{fig:ccg_model}(c)]. A similar scheme applied for
+SNr$_j$ [Fig.~\ref{fig:ccg_model}(c)]. A similar scheme applies for
 the connectivity from Str\_D2 to GPe and for a number of the other
@@
 Fig.~\ref{fig:brainmodel} shows a schematic of the SpineML implementation
-of the model, based on a diagram output directly from
-SpineCreator. Populations for Str\_D1, Str\_D2, STN, SNr and GPe are
+of the model, based on a diagram produced by SpineCreator. Populations
+for Str\_D1, Str\_D2, STN, SNr and GPe are
 shown within the `Basal Ganglia' box. Input comes into the model via
@@
 \citep{hikosaka_role_2000,tehovnik_eye_2000,robinson_eye_1969,bruce_primate_1985}.
-Saccadic targets are mapped retinotopically over its
+Saccadic targets are retinotopically mapped on its
 surface \citep{robinson_eye_1969,bruce_primate_1985,sabes_parietal_2002},
-and increased neural activity at a location in the map precedes a
+and increased neural activity at a location on the map precedes a
 saccade to that location. Importantly, the FEF is also associated with
@@
 
-\rvwt{FEF neurons can be divided in to three functional groups,
+\rvwt{FEF neurons can be divided into three functional groups,
 related to whether their activity corresponds with visual stimuli,
@@
 pathway \citep{ungerleider_two_1982} which is abbreviated in this
-model to a direct connection with delay.}
+model to a direct connection with delay and noise.}
 
@@
 can direct gaze, following a period of
-adjustement \citep{latto_effects_1977}, albeit with some persistent
+adjustment \citep{latto_effects_1977}, albeit with some persistent
 deficits. The SC is also a direct target of output from the
@@
 layers \citep{wurtz_visual-motor_1980}, in most cases these are
-divided into the `superficial' and `deep' layers, which have
+categorised as the `superficial' and `deep' layers, which have
 significantly different response properties. Cells in the superficial
@@
 \rvwt{The \ccg~model incorporates a special connectivity pattern for
-visual input via cortical (FEF) and sub-cortical (thalamus)
+visual input to the BG via cortical (FEF) and sub-cortical (thalamus)
 pathways. Due to the retinotopic mapping (Sect.~\ref{sec:mapping}),
@@
 SC\_deep population. The activity in SC\_deep is first transformed
-from retinotopic co-ordinates into the Cartesian co-ordinates. The
+from retinotopic co-ordinates into Cartesian co-ordinates. The
 centroid of the activity is then computed. The position of this
@@
 \rvwt{The \ccg~model was parameterised by tuning the model to perform
-a prosaccade task in which a fixed luminance point is fixated by teh
+a prosaccade task in which a central luminance point was fixated by the
 model. After a fixed duration, the fixation point was extinguished and
@@
 regions. The tuning of the BG model attempted to preserve as closely
-as possible the weights used in the original paper. Further details on
-the parameterisation of the \ccg~model are in \cite{cope_basal_2017}.}
+as possible the weights used in the original paper
+\citep{gurney_computational_2001}. Further details on
+the parameterisation of the \ccg~model are given in \cite{cope_basal_2017}.}
 % Differences between ccg and existing brain model or can I do that
@@
 
-The \e{LINlinear} component governs the activation $a$ with a first order
+The \e{LINlinear} component, which is used in FEF, Thalamus, SC, SNr
+and GPe populations, governs the activation $a$ with a first order
 leaky integrator differential equation:
@@
 the \ccg~model, for which the cortico-striatal weights are multiplied
-by $(1+d)$ rather than $(0.2+d)$. A value of $d=$0.7
-
-The equations given above are applied to each element in a population
-\rvwt{based on the D1MSN or D2MSN component}. The value of the activation
-$A$ (and where relevant, the shunting input, $S$) is determined by
-summing the weighted inputs to the population:
+by $(1+d)$ rather than $(0.2+d)$. A typical value of $d$ is 0.7.
+
+In the typical components given above, the value of the activation $A$
+(and where relevant, the shunting input, $S$) is determined by summing
+the weighted inputs to the population:
 \begin{equation}
@@
 Here, $W_{nfs}$ is 50 (the side length of the 50x50 grid) and
-$W_{fov}$ is set to 61\dg, a reduction from the biophysically accurate
+$W_{fov}$ is set to 61\dg, a reduction from the biologically accurate
 150\dg~due to the small number of neurons in the retinotopic neural
@@
 
-Connections shown in red are one to one connections; dark blue
+Connections shown in red are one-to-one connections; dark blue
 projections indicate a connectivity pattern which `fans out' with a
-2-D Gaussian kernel; lighter blue connections from the subthalamic
-nucleus (STN) to SNr and globus pallidus externum (GPe) are diffuse,
-all-to-all connections and projections coloured green are one-to-one
-connections that decay towards the fovea so that foveal activity in
-FEF does not swamp the basal ganglia which would prevent peripheral
-luminances from ever being selected.
+2-D Gaussian kernel [Fig.~\ref{fig:ccg_model}(c)]; lighter blue
+connections from the STN to SNr and GPe are diffuse, all-to-all
+connections and projections coloured green are one-to-one connections
+that decay towards the fovea so that foveal activity in FEF does not
+swamp the basal ganglia which would prevent peripheral luminances from
+ever being selected.
 %
@@
 \end{equation}
-with an identical piecewise linear transfer function as the other SBG
+with the same piecewise linear transfer function as in the other SBG
 populations.
@@
 \rvwt{An illustration of the biomechanical eye model is given in
-Figure \ref{fig:bioeye}, while Figure \ref{fig:bioeye} depicts
+Figure \ref{fig:bioeye}(a), while Figure \ref{fig:bioeye}(b) depicts
 the head model used in the proposed framework.}
@@
 
+% KM
+\rvwt{Finally, numerical integration of the biomechanical eye model is based
+on the Kutta-Merson integration method.}
+
 \subsection{Model development framework} \label{sec:methods:framework}
@@
 arbitrary number of inputs and outputs and may be written in C, C++,
-Python or MATLAB. The \ccg~model's components were hand written in C++
+Python or MATLAB. The \ccg~model components were hand written in C++
 and MATLAB. A BRAHMS \e{SystemML} file describes how the different
@@
 stylesheets which first generate and compile C++ BRAHMS components
-from the SpineML component layer description files. \stob~then uses
-the SpineML network and experiment layer files to generate a BRAHMS
-SystemML description of the model. Finally, \stob~executes the model,
-now described entirely as a BRAHMS system, via a call to the BRAHMS
-binary. A number of additional hand-written components are present
+(which implement a simple, Forward-Euler solver) from the SpineML
+component layer description files. \stob~then uses the SpineML
+network and experiment layer files to generate a BRAHMS SystemML
+description of the model. Finally, \stob~executes the model now
+described entirely as a BRAHMS system, via a call to the BRAHMS
+binary. A number of additional, hand-written components are present
 in \stob~providing the inputs (constant inputs, time-varying inputs,
@@
 
-% KM
-\rvwt{Finally, numerical integration of the biomechanical eye model is based
-on the Kutta-Merson integration method.}
-
 % Section - description of the integration. scientific and
@@
 
-The \ccg~model closed its loop by passing the centroid of activity in
-SC\_deep (once it had surpassed a threshold) back to the code that
-controlled the world, which would then use this location to
+The \ccg~model closes its loop by passing the centroid of activity in
+SC\_deep (once it has surpassed a threshold) back to the code that
+controls the world, which then uses this location to
 instantaneously change the model's view of the world. In our extended
@@
 retinotopic co-ordinate system which determines the activity in the
-`World' population (named to mean the `world as the eye sees it',
+`World' population (named to mean the `world as the brain sees it',
 rather than the world frame of reference) which is the input for the
@@
 basal ganglia model and activity for the winning end-point builds up
-in the deep layer of superior colliculus. This activity excites
-activity in the correct proportions within the 6 channels of the
-saccadic burst generator whose output state, the motoneurons send a
-rate-code signal (normalised between 0 and 1) into the biomechanical
-eye model. The rotational state of the eye model is fed back to
-participate in the computation of the retinotopic luminance activity
-in `World', completing the loop.}
+in the deep layer of superior colliculus. This activity excites the 6
+channels of the saccadic burst generator in the correct proportions
+for the saccade. The motoneurons, which are the output of the SBG,
+send a rate-code signal (normalised between 0 and 1) into the
+biomechanical eye model. The rotational state of the eye model is fed
+back to participate in the computation of the retinotopic luminance
+activity in `World', completing the loop.}
 
@@
 %
-Arai and co-workers trained a 20x20 neural network model of the
+Arai and co-workers trained a 20 by 20 neural network model of the
 superior colliculus to discover the weight map under the assumption of
@@
 the smaller hill. However. Now consider a 2-D Gaussian hill which
-codes for a 10\dg saccade which is `up, and to the right' in equal
+codes for a 10\dg~saccade which is `up, and to the right' in equal
 proportions. That means that the hill will sit on the boundary between
 the weight maps for the `up', and the `right' muscles. Now, if the
-hill moves to the $r=$20\dg~location on the colliculus, \e{and also
+hill moves to the $r=\mathrm{20}$\dg~location on the colliculus, \e{and also
 reduces in size}, it will excite only the periphery of the sine; the
@@
 the rostral-caudal axis of the SC. \cite{bayguinov_hard-wired_2015}
-presents evidence for another projecting field within SC whose
+present evidence for another projecting field within SC whose
 connectivity pattern \e{does} change along the rostral-caudal
@@
 $m_{\sigma}$ is a scalar parameter which determines the `magnitude of
-the widening'. $M^0$ is the `starting' magnification factor; within
+the widening'. $M^0$ is the `starting' magnification factor. Within
 the foveal region ($0 \leq r \leq r_0$), the projection field is not
@@
 the world luminances in a JSON file called luminances.json at the
-start of each simulation. luminances.json specified the position,
+start of each simulation. This file specified the position,
 shape, size, luminance, appearance time and disappearance time of an
@@
 leftward movement. Note that $\phi$ is presented in neural
-coordinates, and not in degrees or radians; 1$\leq\phi\leq$50
-corresponds to a range of 0\dg~to 360\dg; $\phi=$38.5 corresponds to
-movements left. The connections strength drops away sinusoidally as
-$\phi$ moves away from the centre line at $\phi=$38.5. In regions of
+coordinates, and not in degrees or radians; $\mathrm{1}\leq\phi\leq\mathrm{50}$
+corresponds to a range of 0\dg~to 360\dg; $\phi=\mathrm{38.5}$ corresponds to
+movements left. The connection strength drops away sinusoidally as
+$\phi$ moves away from the centre line at $\phi=\mathrm{38.5}$. In regions of
 the map for which there is no leftward movement, that is, in the half
@@
 rectus muscle of the eye. The line of maximum connection strength is
-along $\phi=$13.5. The map is a mirror of
-Fig.~\ref{fig:weightmaps}(a), reflected about the line $\phi$=26. The
+along $\phi=\mathrm{13.5}$. The map is a mirror of
+Fig.~\ref{fig:weightmaps}(a), reflected about the line $\phi\mathrm{26}$. The
 `left' and `right' weight maps are orthogonal; the non-zero region of
@@
 50. The line of maximum connection strength for the `up' map is along
-$\phi=$1; for `down' $\phi=$26. Based on the training described in
+$\phi=\mathrm{1}$; for `down' $\phi=\mathrm{26}$. Based on the training described in
 Sect.~\ref{sec:methods:integrating}, the maps driving the superior
@@
 are approximately 15\%, which are within the boundaries of what some
-authors have suggested would be regarded as an accurate
+authors regard as an accurate
 saccade \citep{mcpeek_saccade_2002,mcpeek_incomplete_2006}.  The
@@
 accidently relatively good, with trajectories resembling experimental data
-(\cite{bahill_trajectories_1979}, p.~6). \rvw{Had the return accuracy not
+(\cite{bahill_trajectories_1979}, p.~6). \rvw{Had the return saccades not
 been so accurate, we may have noticed the lack of a tonic neuron reset
@@
 \cite{gancarz_neural_1998} model. We implemented this feature by adding an
-additional inhibitory input to the `integrator' component of TModel4,
+additional inhibitory input to the `integrator' SBG component of TModel4,
 driven by the contralateral EBN population, naming the new model
@@
 We carried out a `staircase' presentation, shown in
-Fig.~\ref{fig:doublesteps}, where our small eccentricity luminance was at
-8\dg~and our more distal luminance was at 12\dg~(both to the right of
-centre). \rvwt{The stimuli could not be presented at 15\dg and 30\dg
-to match the experiment, because 30\dg saccades were outside the range
-of the model.}
+Fig.~\ref{fig:doublesteps}, where our small eccentricity luminance was
+at 8\dg~and our more distal luminance was at 12\dg~(both to the right
+of centre). \rvwt{The stimuli could not be presented at 15\dg~and
+30\dg~to match the experiment, because 30\dg~saccades were outside the
+range of the model.}
 
@@
 
-The implementation of a biophysically accurate model of the eye, and
+The implementation of a biologically accurate model of the eye, and
 the closed-loop nature of the model makes it very natural to consider
@@
 cortical microcircuit contains a variety of morphologically distinct
-gabaergic neurons \citep{douglas_neuronal_2004} which could fulfil
+GABAergic neurons \citep{douglas_neuronal_2004} which could fulfil
 this functionality. A similar mechanism would then be required in SC,
@@
 retinal-collicular pathway which generates express saccades. Again, SC
-is a multi-layered structure, containing gabaergic interneurons
+is a multi-layered structure, containing GABAergic interneurons
 \citep{munoz_lateral_1998,meredith_intrinsic_1998,helms_organization_2004,sooksawate_organization_2011}
@@
 mode. Neither the control system, nor the sensory system are
-biophysically accurate and we would not describe this study as
-computational neurobehaviour. Nevertheless, the biophysically accurate
+biologically accurate and we would not describe this study as
+computational neurobehaviour. Nevertheless, the biomechanically accurate
 motor system they describe has the potential to form part of a
@@
 \rvw{To summarise, in most closed-loop robotic studies which
-incorporate neuro-mimetic models, the hardware forms an `engineered
+incorporate neuromimetic models, the hardware forms an `engineered
 surround architecture', allowing for the examination of the behaviour
@@
 environment. Consequently, an increasing number of studies into
-robotic or neuro-mimetic control are carried out with virtual robots
+robotic or neuromimetic control are carried out with virtual robots
 operating within a virtual environment.}
@@
 biomimetic insect legs implemented in a virtual robot and a
-neuro-mimetic brain. Closing the loop is a visual sensory input system
+neuromimetic brain. Closing the loop is a visual sensory input system
 which is able to determine the distance between the robot and an
@@
 %% knowledge, the first model which integrates the brain with an accurate
-%% biophysical system and closes the loop in this way, enabling the
+%% biological system and closes the loop in this way, enabling the
 %% system to reproduce behaviour.  As such, it offers a platform for

### 2017-12-08 papers/integration/omm_integ.tex
More very small tweaks based on proofing

@@
 $R_N$ is a random number drawn from a standard normal distribution
-($\sigma$=1, $\mu$=0) and introduces noise to the activation of the
+($\sigma=\mathrm{1}$, $\mu=\mathrm{0}$) and introduces noise to the activation of the
 neural element, with the parameter $\alpha$ controlling the noise
@@
 Note that we use $r$ and $\phi$ as the co-ordinates on the `collicular
-surface'. Schwartz uses $r$ and $\phi$ as the polar coordinates of the
-retinal stimulus; Ottes et al.~use $r$ and $\phi$ as polar coordinates
+surface'. Schwartz uses $r$ and $\phi$ as the polar co-ordinates of the
+retinal stimulus; Ottes et al.~use $r$ and $\phi$ as polar co-ordinates
 for the eye movement response; both use $u$ and $v$ as the Cartesian
@@
 leftward movement. Note that $\phi$ is presented in neural
-coordinates, and not in degrees or radians; $\mathrm{1}\leq\phi\leq\mathrm{50}$
+co-ordinates, and not in degrees or radians; $\mathrm{1}\leq\phi\leq\mathrm{50}$
 corresponds to a range of 0\dg~to 360\dg; $\phi=\mathrm{38.5}$ corresponds to
@@
 along $\phi=\mathrm{13.5}$. The map is a mirror of
-Fig.~\ref{fig:weightmaps}(a), reflected about the line $\phi\mathrm{26}$. The
+Fig.~\ref{fig:weightmaps}(a), reflected about the line $\phi=\mathrm{26}$. The
 `left' and `right' weight maps are orthogonal; the non-zero region of
@@
 and 100~ms overlap conditions for a given fixation luminance of 0.2,
-and a horizontally located target at $\theta_{y}^{t}=$-10\dg. For the
+and a horizontally located target at $\theta_{y}^{t}=\mathrm{-10}$\dg. For the
 gap condition, we see very short latencies for luminances of about

### 2017-12-08 papers/integration/omm_integ.tex
Changes based on proof reading the last section of the discussion and the figure captions.

@@
 
-\rvw{\cite{pearson_whiskerbot:_2007} describes a wheeled robot which has a
+\rvw{\cite{pearson_whiskerbot:_2007} describe a wheeled robot which has a
 biomimetic whisker sensory system, along with a biomimetic neural
@@
 actions that are selected within the brain model drive a
-non-biologically accurate wheel motor control algorithm to achieve
+non-biologically accurate motor control algorithm to achieve
 rotational and translational movements. Although both have sensory and
@@
 incorporate neuromimetic models, the hardware forms an `engineered
-surround architecture', allowing for the examination of the behaviour
+surround architecture' allowing for the examination of the behaviour
 of the embodied model. However, suitably \e{biomimetic} hardware such as
 the fish in \cite{yu_development_2004} would not be excluded from
-computational neurobehavioural studies.}
+computational neurobehavioural studies, especially if movement is by
+biomimetic muscle actuators \citep{wilson_cerebellar-inspired_2016,ohalloran_review_2008}.}
 
@@
 neuromimetic brain. Closing the loop is a visual sensory input system
-which is able to determine the distance between the robot and an
-obstacle and the obstacle's height. The authors demonstrate that the
-virtual robot is able to learn to climb obstacles in a realistic
-manner and suggest that the model may be compared with experimental
+which is able to determine the distance to an
+on-coming obstacle and the obstacle's height. The authors demonstrate that the
+virtual robot is able to learn to climb in a realistic
+manner and suggest it may be compared with experimental
 data from future Drosophila experiments addressing obstacle climbing
@@
 % Figure 1
-\begin{figure}[h!]
+\begin{figure}[!ht]
 \begin{center}
@@
 fields (FEF), thalamus (THAL) and superior colliculus (SC). The
-retinal input is presented via non-biologically plausible retinal
+retinal input is presented via non-biologically accurate retinal
 populations. The loops through basal ganglia, which define the
@@
 to its targets. \bol{c) 2D Gaussian weights.} The `GaussianKernel'
-connectivity pattern is based on the `in-plane displacement' between
+connectivity pattern is based on the in-plane component of the
+displacement between
 the location of a neural element in one layer, and the location of a
@@
 % Figure 2
-\begin{figure}[h!]
+\begin{figure}[!ht]
 \begin{center}
@@
 arrowheads and inhibitory connections have circles, although for
-details of the behaviour of the connections, the weight-update and
-post-synapse components must be studied. Briefly, the model comprises
+full details of the behaviour of the connections, the weight-update and
+post-synapse component associated with each connection must be
+referred to. Briefly, the model comprises
 a \e{World} population, into which a retinotopically organised view of
@@
 here, instead the level of dopamine in the striatum is set via a
-parameter in the Str\_D1 and Str\_D2 populations}
+parameter in the Str\_D1 and Str\_D2
+populations. \bol{a)} Fixation cross input in Cartesian eye
+frame. \bol{b)} Fixation cross input in retinotopic
+co-ordinates. \bol{c)} Fixation cross with noise added. \bol{d)}
+After blurring, input is passed to BG populations.}
 \label{fig:brainmodel}
@@
 % Figure 3
-\begin{figure}[h!]
+\begin{figure}[!ht]
 \begin{center}
@@
 \caption{ Representative mapping from eye's frame of reference in Cartesian
-co-ordinates to retinotopic co-ordinates. (a) The mapping of
+co-ordinates to retinotopic co-ordinates. \bol{a)} The mapping of
 luminances in the eye's frame of reference. The world input is
@@
 but their span of 10\dg~is greater than the 6\dg~used in the
-simulations, to make these images clearer. (b) The locations of the
+simulations, to make these images clearer. \bol{b)} The locations of the
 luminances in the eye's frame of reference are then converted into
@@
 higher values of $r$. $\phi$ encodes rotational angle: 1 and 50 encode
-upward movement; 13 is left; 25 is down; 37 is right. The output of
+upward movement; 13.5 is left; 26 is down; 38.5 is right. The output of
 the World component is fed into FEF\_add\_noise and into the retinal
 neuron populations. The colour map makes it possible to distinguish
-between the two crosses. (c) The FEF\_add\_noise populations adds a
+between the two crosses. \bol{c)} The FEF\_add\_noise populations adds a
 level of noise to the signal representing processing of the signal in
-visual cortex. (d) A Gaussian projection from FEF\_add\_noise to FEF
+visual cortex. \bol{d)} A Gaussian projection from FEF\_add\_noise to FEF
 further blurs the activity in FEF. FEF is the input to the basal
@@
 % Figure 4
-\begin{figure}[h!]
+\begin{figure}[!ht]
 \begin{center}
@@
 (cyan) or right (green) movements. Collicular activity in SC\_avg
-excites the channels via SBG weight maps. Each box represents a neural
+excites the channels via SBG weight maps, which are encoded as
+explicit lists of connection weights in the blue connection arrows
+from SC\_avg to the LLBN populations. Each box represents a neural
 population and shows the population name, the number of neural
@@
 % Figure 5
-\begin{figure}[h!]
+\begin{figure}[!ht]
 \begin{center}
@@
 \end{center}
-\caption{ The biomechanical eye. a) an OpenSim rendering of a pair of
+\caption{ The biomechanical eye. \bol{a)} an OpenSim rendering of a pair of
 biomechanical eyes showing the positions of the extraocular
@@
 activation, ii) superior and inferior oblique are visualized up to
-their respective muscle pulleys. b) OpenSim rendering of biomechanical
-eye within a head model c) Top-down schematic cross-sectional view of
+their respective muscle pulleys. \bol{b)} OpenSim rendering of biomechanical
+eye within a head model \bol{c)} Top-down schematic cross-sectional view of
 the biomechanical eye situated within a spherical screen, with a
-horizontal rotation towards a luminances at an angle of $-\theta_{y}$
+horizontal rotation towards a luminance at an angle of $-\theta_{y}$
 about the $y$ axis. The $y$ axis points up, out of the page.}
@@
 
-\begin{figure}[h!]
+\begin{figure}[!ht]
 \begin{center}
@@
 declarative XML files and hand-coded C++. These original model
-specifications are shown within the blue box. b) The green box shows
+specifications are shown within the blue box. \bol{b)} The green box shows
 the processes which are applied to the model specification to produce
@@
 compiled and installed within the BRAHMS Namespace, allowing the
-BRAHMS executable to locate them at runtime. c) The red box shows the
+BRAHMS executable to locate them at runtime. \bol{c)} The red box shows the
 resulting BRAHMS system ready to be executed by the BRAHMS
@@
 \end{center}
-\caption{ a) \& b) Tabareau-style weight maps for `left' and `down' components
-of a saccade. c) The two weight maps in a) and b) shown on the same
+\caption{ \bol{a)} \& \bol{b)} Tabareau-style weight maps for `left' and `down' components
+of a saccade. \bol{c)} The two weight maps in (a) and (b) shown on the same
 graph, viewed from above. Circles show the locations of potential
 hills of activity. Purple, dashed circles encode saccades down;
-red circles encode saccades with both a left and a down component. d)
+red circles encode saccades with both a left and a down component. \bol{d)}
 Showing the additional deep layer of superior colliculus (SC\_deep2)
@@
 \end{center}
-\caption{ Accuracy at different target eccentricities for fixation luminance
+\caption{ Accuracy of single saccades at different target eccentricities for fixation luminance
 0.2 and target luminance 0.3.}
@@
 \caption{ The end-point error surface for the original, na\"ive model
-(TModel3). a) The ratio of the magnitudes of the total error vector
-and the target vector, expressed as a percentage. b) The ratio of the
+(TModel3). \bol{a)} The ratio of the magnitudes of the total error vector
+and the target vector, expressed as a percentage. \bol{b)} The ratio of the
 magnitude of the $x$ component of the error vector to the magnitude of
-the target vector, expressed as a percentage. c) As (b) but for the
-$y$ component. d) As (b), for $z$ component. All colour maps are shown
+the target vector, expressed as a percentage. \bol{c)} As (b) but for the
+$y$ component. \bol{d)} As (b), for $z$ component. All colour maps are shown
 with the same scale. The target rotations, $\theta_{x}^t$ and
@@
 \caption{ The end-point error surface for the model in which a widening
-projection field was added to the model of the superior colliculus. a)
+projection field was added to the model of the superior colliculus. \bol{a)}
 The ratio of the magnitudes of the total error vector and the target
-vector, expressed as a percentage. b) The ratio of the magnitude of
+vector, expressed as a percentage. \bol{b)} The ratio of the magnitude of
 the $x$ component of the error vector to the magnitude of the target
-vector, expressed as a percentage. c) As (b) but for the $y$
-component. d) As (b), for $z$ component. All colour maps are shown
+vector, expressed as a percentage. \bol{c)} As (b) but for the $y$
+component. \bol{d)} As (b), for $z$ component. All colour maps are shown
 with the same scale. The target rotations, $\theta_{x}^t$ and
@@
 \end{center}
-\caption{ Representative single saccades. a) Trajectories from 9 saccades to a
+\caption{ Representative single saccades. \bol{a)} Trajectories from 9 saccades to a
 single target at 9 different locations. In each case, a fixation cross
 luminance of magnitude 0.2 was displayed at (0,0), the start position
-of the eye, until time 0.4~s. The target luminance, magnitude 0.3 was
+of the eye, until time 0.4~s. The target luminance, magnitude 0.3, was
 illuminated at time 0.4~s. Trajectory shape is dependent on the target
@@
 saccade, the target location is given by the cross of the same colour
-closest to the end of the trajectory. b) The three rotational
-components of the `blue' saccade, to target location (-7,-7). c) The
+closest to the end of the trajectory. \bol{b)} The three rotational
+components of the `dark blue' saccade, to target location (-7,-7). \bol{c)} The
 three rotational components of the `red' saccade, to target location
@@
 \end{center}
-\caption{ Exploring saccade latencies. a) Latency to first movement as a
-function of target eccentricity for horizontal targets. b) Latency
-vs. eccentricity for vertical targets. c) Latency vs. gap at three
+\caption{ Exploring saccade latencies. \bol{a)} Latency to first movement as a
+function of target eccentricity for horizontal targets. \bol{b)} Latency
+vs. eccentricity for vertical targets. \bol{c)} Latency vs. gap at three
 different luminance values. The data are shown alongside
@@
 and the experimental results used in that model in red. The fixation
-luminance for the \ccg~curve was 0.5, the target lumianance 0.6 and
+luminance for the \ccg~curve was 0.5, the target luminance 0.6 and
 the target eccentricity was 8\dg. The difference between
@@
 movement, the differing target angle and the reduced fixation
-luminance used here. d) The effect
+luminance used here. \bol{d)} The effect
 of the dopamine parameter on saccade latencies in gap, step and
-overlap conditions, for two different target luminances.  e) Saccade
+overlap conditions, for two different target luminances.  \bol{e)} Saccade
 vs. luminance showing gradual transition between reflexive and express
@@
 \caption{ There and back - a saccade to a target, followed by return to the
-original fixation. a) Out and return saccade to a target at (0,-10\dg)
-b) Rotational components of the saccade shown in (a). c) Outward and
+original fixation. \bol{a)} Out and return saccade to a target at
+(0,-10\dg). The outward trajectory is shown in blue, the return in pink.
+\bol{b)} Rotational components of the saccade shown in (a). \bol{c)} Outward and
 return trajectories for the saccade shown in (a) alongside saccades to
@@
 \caption{ Double steps. The effect of illuminating a first target at 8\dg~or
-12\dg, followed by a second target at 12\dg~or 8\dg. a) Horizontal
+12\dg, followed by a second target at 12\dg~or 8\dg. \bol{a)} Horizontal
 rotation of the eye plotted vs.~time for a saccade to the 12\dg~target
@@
 simulations is plotted along with $\pm$1 standard deviation around the
-mean. b) The $\theta_{x}$/$\theta_{y}$ trajectories corresponding to
+mean. \bol{b)} The $\theta_{x}$/$\theta_{y}$ trajectories corresponding to
 the data presented in (a).}

### 2018-01-12 papers/integration/omm_integ.tex
Addresses Reviewer 1 final comment

@@
 
-% Use colour to indicate changes made following review. Can be
-% set to this 'black' colour prior to final publication:
-\newcommand{\black}{\textcolor{black}}
-% Colour for reviewer 1 changes:
-\newcommand{\rvwcolour}{\textcolor{OrangeRed}}
-% Colour for reviewer 2 changes:
-\newcommand{\rvwcolourtwo}{\textcolor{Cerulean}}
-% Commands to use in the text. Change 'rvwcolour/rvwcolourtwo' to
-% 'black' to hide review changes.
-\newcommand{\rvw}[1]{\rvwcolour{#1}}
-\newcommand{\rvwt}[1]{\rvwcolourtwo{#1}}
+% Used colour to indicate changes made following review.
+% These commands are now defined to be no-ops
+\newcommand{\rvw}[1]{#1}  % Reviewer 1.
+\newcommand{\rvwf}[1]{#1} % Reviewer 1, final comment
+\newcommand{\rvwt}[1]{#1} % Reviwer 2.
 
@@
    \section{Keywords:}
-   integrated brain biomechanics neuromuscular oculomotor saccade basal ganglia
+   integrated brain biomechanics neuromuscular neuromechanics oculomotor saccade basal-ganglia
  } % 5 to 8 keywords
@@
 \section{Introduction} \label{sec:introduction}
-
-% Remove after review:
-\bol{Note:} Changes based on Reviewer 1's comments \rvw{are in this colour}. For
-Reviewer 2 \rvwt{we use this colour}.
 
@@
 with attention paid to the biological accuracy of each brain and
-biomechanical sub-system. There already exist many
+biomechanical sub-system.
+% Address final comment from Reviewer 1
+\rvwf{We are by no means the first researchers to consider this
+interaction between brain and biomechanics. Integrative approaches to
+motor control have been referred to as \e{neuromechanics} by some
+authors~\citep{nishikawa_neuromechanics:_2007}. This field appears to
+have developed from detailed and low level studies of the mechanics of
+muscle control systems, focussing on the neural systems `closest' to
+the muscle~\citep{chiel_brain_2009}. It is evident that a recognition
+of the importance of sensory input to these systems has evolved within
+this field. Indeed, \cite{edwards_neuromechanical_2010} specifically
+reviews closed-loop, \e{neuromechanical simulations} of behaviour in
+three organisms; fly, locust and cat. The term neuromechanical
+simulation \citep{pearson_assessing_2006,edwards_neuromechanical_2010}
+is analogous to our computational neurobehaviour, although it does not
+emphasise the important \e{behavioural} aspect of the works.}
+
+There also exist many
 closed-loop \e{robotic} systems which receive sensory input from the
@@
 operating within a virtual environment.}
+%
+\rvwf{This approach is taken in the studies described
+in \cite{edwards_neuromechanical_2010}. \cite{dickson_integrative_2006}
+describes an integrated model of Drosophila flight in which visual
+input is processed by an algorithmic (that is, non-neural) `brain' to
+control a biomechanically accurate representation of the fly. As the
+virtual fly traverses its environment, its visual input updates,
+closing the loop of the simulation. \cite{cope_model_2016} is a recent
+study which omits the biomechanically accurate component of the model
+but could provide the biologically plausible brain to make a
+computational neurobehavioural fly
+model. \cite{cofer_neuromechanical_2010} use an environment called
+AnimatLab \citep{cofer_animatlab:_2010} to simulate the locust's
+jumping mechanism in an open-loop, software-only investigation. As
+this appears to be a feed-forward model without sensory feedback, we
+would describe it as an input-assumption model.}
 %

### 2018-01-12 papers/integration/bbl_utf8_to_latex.sh

@@ -41,6 +41,10 @@ count=$((count+1))
 sed 's/\xc3\x96/\\"O/g' < /tmp/utf8tolatex/${count}.bbl > /tmp/utf8tolatex/$((count+1)).bbl
 count=$((count+1))
 
+# O umlaut 2
+sed 's/\xc3\x2e/\\"O/g' < /tmp/utf8tolatex/${count}.bbl > /tmp/utf8tolatex/$((count+1)).bbl
+count=$((count+1))
+
 # e acute (Moren)
 sed 's/\xc3\xa9/\\'\''e/g' < /tmp/utf8tolatex/${count}.bbl >  /tmp/utf8tolatex/$((count+1)).bbl
 count=$((count+1))

### 2018-01-24 papers/integration/omm_integ.tex
Adds Figure N labels to all the figure sections
Changes which should correspond to those made after accepting the Authors proof.

@@
 \def\firstAuthorLast{James {et~al.}}
-\def\Authors{Sebastian James\,$^{1,2}$, Chris Papapavlou\,$^5$, Alexander Blenkinsop\,$^{1,2}$, \\
-  Alexander Cope\,$^3$,  \\
-  Sean Anderson\,$^{2,4}$, Konstantinos Moustakas\,$^5$, Kevin Gurney\,$^{1,2,*}$}
+\def\Authors{Sebastian S.~James\,$^{1,2}$, Chris Papapavlou\,$^5$, Alexander Blenkinsop\,$^{1,2}$, \\
+  Alexander J.~Cope\,$^3$,  \\
+  Sean Anderson\,$^{2,4}$, Konstantinos Moustakas\,$^5$, Kevin N.~Gurney\,$^{1,2,*}$}
 
@@
 
-\def\corrAuthor{Kevin Gurney}
+\def\corrAuthor{Kevin N.~Gurney}
 \def\corrAddress{Department of Psychology, The University of Sheffield,
@@
 symmetric, 2D-Gaussian which is a function of distance $d$ from
-SNr$_j$ [Fig.~\ref{fig:ccg_model}(c)]. A similar scheme applies for
+SNr$_j$ [Figs.~\ref{fig:ccg_model}(c)\&(d)]. A similar scheme applies for
 the connectivity from Str\_D2 to GPe and for a number of the other
@@
 Figure \ref{fig:bioeye}(a), while Figure \ref{fig:bioeye}(b) depicts
-the head model used in the proposed framework.}
+the head model used in the proposed
+framework. Figure \ref{fig:bioeye}(c) shows a cross-sectional view of
+the eye and the spherical screen on which targets were projected.}
 
@@
 consider the effect of a 2D Gaussian hill in SC\_deep which elicits a
-successful horizontal saccade of 10\dg. Activity from the 2D Gaussian,
-passing through the weight maps will excite the superior and inferior
-rectus channels by an equal, balanced amount, so these cancel out,
+successful horizontal saccade of 10\dg~using the weight maps shown in
+Figures 7(a)--(c). Activity from the 2D Gaussian (schematically
+represented as the large purple dashed circle in Figure 7C),
+passing through the weight maps will excite the superior (not shown) and inferior
+rectus [Figure 7(b)] channels by an equal, balanced amount, so these cancel out,
 allowing the eye movement to be horizontal. The amount of activation
@@
 along the collicular surface, coding for a 20\dg~saccade, \e{and also
-becomes smaller}, we can still argue that the vertical component
+becomes smaller} (small purple dashed circle), we can still argue that the vertical component
 signals to superior/inferior rectus muscles will cancel out, and we
@@
 Eq.~\ref{eq:tabareau_eq3} is correctly parameterised to compensate for
-the smaller hill. However. Now consider a 2-D Gaussian hill which
-codes for a 10\dg~saccade which is `up, and to the right' in equal
-proportions. That means that the hill will sit on the boundary between
-the weight maps for the `up', and the `right' muscles. Now, if the
-hill moves to the $r=\mathrm{20}$\dg~location on the colliculus, \e{and also
+the smaller hill. Now consider a 2-D Gaussian hill which
+codes for a 10\dg~saccade which is `down, and to the left' in equal
+proportions (large red circle). That means that the hill will sit on the boundary between
+the weight maps for the `down', and the `left' muscles. Now, if the
+hill moves to the $r=\mathrm{20}$\dg~location on the colliculus (small
+red circle), \e{and also
 reduces in size}, it will excite only the periphery of the sine; the
@@
 compensate for the reduction in the convolution of the Gaussian hill
-and the sinusoidal component of the weight map.}
+and the sinusoidally varying component of the weight map along the $\phi$ axis in
+Figure 7(a).}
 % Add figure for this.
@@
 
+% Figure 6
 \begin{figure}[!ht]
@@
 \end{center}
-\caption{ The model framework. The model is specified using a combination of
+\caption{ The model framework. \bol{a)} The model is specified using a combination of
 declarative XML files and hand-coded C++. These original model
@@
 
+% Figure 7
 \begin{figure}[!ht]
@@
 graph, viewed from above. Circles show the locations of potential
-hills of activity. Purple, dashed circles encode saccades down;
+hills of activity. Purple, dashed circles encode saccades left;
 red circles encode saccades with both a left and a down component. \bol{d)}
@@
 
+% Figure 8
 \begin{figure}[!ht]
@@
 \caption{ Accuracy of single saccades at different target eccentricities for fixation luminance
-0.2 and target luminance 0.3.}
+0.2 and target luminance 0.3. \bol{a)} Horizontal rotations about the
+y axis. \bol{b)} Vertical rotations of the eye about the x axis.}
 \label{fig:saccvstarg}
@@
 
+% Figure 9
 \begin{figure}[!ht]
@@
 generator model. Each map increases exponentially with increasing $r$,
-multiplied by cosine($\phi$) about its `active' axis.}
+multiplied by cosine($\phi$) about its `active' axis. \bol{a)} Weight
+map for leftward movements which innervates the lateral rectus in this
+single left-eye model. \bol{b)} Map for downward movements; innervates
+the inferior rectus. \bol{c)} Superior oblique muscle weight
+map. \bol{d)} Weight map for rightward movements/medial rectus
+muscle. \bol{e)} Weight map for the superior rectus muscle which
+generates upward movements. \bol{f)} Inferior oblique map.}
 \label{fig:weightmaps}
@@
 
+% Figure 10
 \begin{figure}[!ht]
@@
 
+% Figure 11
 \begin{figure}[!ht]
@@
 
+% Figure 12
 \begin{figure}[!ht]
@@
 
+% Figure 13
 \begin{figure}[!ht]
@@
 
+% Figure 14
 \begin{figure}[!ht]
@@
 
+% Figure 15
 \begin{figure}[!ht]

### 2018-01-24 papers/integration/omm_integ.tex
A couple of further corrections based on the final proofing process

@@
 successful horizontal saccade of 10\dg~using the weight maps shown in
-Figures 7(a)--(c). Activity from the 2D Gaussian (schematically
-represented as the large purple dashed circle in Figure 7C),
-passing through the weight maps will excite the superior (not shown) and inferior
-rectus [Figure 7(b)] channels by an equal, balanced amount, so these cancel out,
-allowing the eye movement to be horizontal. The amount of activation
-passed to the lateral rectus muscle results from a convolution of the
-Gaussian and the exponential component of the weight map relationship
-in Eq.~\ref{eq:tabareau_eq3}. If the Gaussian hill now appears further
-along the collicular surface, coding for a 20\dg~saccade, \e{and also
-becomes smaller} (small purple dashed circle), we can still argue that the vertical component
-signals to superior/inferior rectus muscles will cancel out, and we
-could imagine that the exponential component of
-Eq.~\ref{eq:tabareau_eq3} is correctly parameterised to compensate for
-the smaller hill. Now consider a 2-D Gaussian hill which
-codes for a 10\dg~saccade which is `down, and to the left' in equal
-proportions (large red circle). That means that the hill will sit on the boundary between
-the weight maps for the `down', and the `left' muscles. Now, if the
-hill moves to the $r=\mathrm{20}$\dg~location on the colliculus (small
-red circle), \e{and also
-reduces in size}, it will excite only the periphery of the sine; the
-exponential increase of the map along $r$ is not guaranteed to
-compensate for the reduction in the convolution of the Gaussian hill
-and the sinusoidally varying component of the weight map along the $\phi$ axis in
-Figure 7(a).}
+Figs.~\ref{fig:scdeep}(a)--(c). Activity from the 2D Gaussian
+(schematically represented as the large purple dashed circle in
+Fig.~\ref{fig:scdeep}(c)), passing through the weight maps will excite
+the superior (not shown) and inferior rectus
+[Fig.~\ref{fig:scdeep}(b)] channels by an equal, balanced amount, so
+these cancel out, allowing the eye movement to be horizontal. The
+amount of activation passed to the lateral rectus muscle results from
+a convolution of the Gaussian and the exponential component of the
+weight map relationship in Eq.~\ref{eq:tabareau_eq3}. If the Gaussian
+hill now appears further along the collicular surface, coding for a
+20\dg~saccade, \e{and also becomes smaller} (small purple dashed
+circle), we can still argue that the vertical component signals to
+superior/inferior rectus muscles will cancel out, and we could imagine
+that the exponential component of Eq.~\ref{eq:tabareau_eq3} is
+correctly parameterised to compensate for the smaller hill. Now
+consider a 2-D Gaussian hill which codes for a 10\dg~saccade which is
+`down, and to the left' in equal proportions (large red circle). That
+means that the hill will sit on the boundary between the weight maps
+for the `down', and the `left' muscles. Now, if the hill moves to the
+$r=\mathrm{20}$\dg~location on the colliculus (small red
+circle), \e{and also reduces in size}, it will excite only the
+periphery of the sine; the exponential increase of the map along $r$
+is not guaranteed to compensate for the reduction in the convolution
+of the Gaussian hill and the sinusoidally varying component of the
+weight map along the $\phi$ axis in Fig.~\ref{fig:scdeep}(a).}
 % Add figure for this.
@@
 the SC in detail, we extended the model with a third functional layer
-named SC\_deep2, shown in Fig.~\ref{fig:scdeep}(b) (\ccg~has only the two
+named SC\_deep2, shown in Fig.~\ref{fig:scdeep}(d) (\ccg~has only the two
 layers SC\_sup and SC\_deep). We introduced a widening projection
